### 2021-10-17 paper.tex
update

\documentclass[twocolumn]{aastex63}
\usepackage{mathtools}
\usepackage{natbib}
\bibliographystyle{abbrvnat}
\setcitestyle{authoryear,open={(},close={)}}
\usepackage{txfonts}
\usepackage{lipsum, babel}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cleveref}
\usepackage{physics}
\usepackage{empheq}
%\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{array}
\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\usepackage{multirow}
\usepackage[flushleft]{threeparttable}
\usepackage{mathrsfs}
\usepackage{soul}
\pdfminorversion=5

\newcommand{\MyDiamond}[1][fill=black]{
\begin{tikzpicture}[x=1.2ex,y=1.2ex,line width=.1ex,line join=round, yshift=0.0ex] \draw  [#1]  (0,.5) -- (.5,1) -- (1,.5) -- (.5,0);
\end{tikzpicture}
}

\newcommand{\MyPlus}[1][fill=black]
{
\begin{tikzpicture}[x=1.5ex,y=1.5ex,line width=0.5ex]
\draw[#1] (0,.5) -- (1,.5);
\draw[#1] (.5,0) -- (.5,1);
\end{tikzpicture}
}

\newcommand{\MyCross}[1][fill=black]
{
\begin{tikzpicture}[x=1.ex,y=1.ex,line width=0.5ex]
\draw[#1] (0,0) -- (1,1);
\draw[#1] (0,1) -- (1,0);
\end{tikzpicture}
}

\newcommand{\MyTriangle}[1][fill=black]
{
\begin{tikzpicture}[x=1.ex,y=1.ex,line width=0.2ex]
\draw[#1] (0,1) -- (1,1);
\draw[#1] (1,1) -- (.5,0);
\draw[#1] (.5,0) -- (0,1);
\fill[#1] (0,1) -- (1,1) -- (.5,0) -- cycle;
\end{tikzpicture}
}

\newcommand{\MySolidLine}[1][fill=black]
{
\begin{tikzpicture}[x=2.ex,y=1.ex,line width=0.5ex]
\draw[#1] (0,.5) -- (2.5,.5);
\end{tikzpicture}
}

\newcommand{\MyDashedLine}[1][fill=black]
{
\begin{tikzpicture}[x=2.ex,y=1.ex,line width=0.5ex]
\draw [#1,dashed] (0,.5) -- (2.5,.5);
\end{tikzpicture}
}

\newcommand{\MyDashedDottedLine}[1][fill=black]
{
\begin{tikzpicture}[x=2.ex,y=1.ex,line width=0.5ex]
\draw [#1,dash dot] (0,.5) -- (2.5,.5);
\end{tikzpicture}
}

\newcommand{\MyDottedLine}[1][fill=black]
{
\begin{tikzpicture}[x=2.ex,y=1.ex,line width=0.5ex]
\draw [#1,dotted] (0,.5) -- (2.5,.5);
\end{tikzpicture}
}

\begin{document}
\title{TITLE}

\author[0000-0002-1868-0660]{Po-Hsun Tseng}
\affiliation{Institute of Astrophysics, National Taiwan University, Taipei 10617, Taiwan}

\author[0000-0003-3269-4660]{H.-Y. Karen Yang}
\affiliation{Institute of Astronomy and Department of Physics, National Tsing Hua University, Hsinchu 30013, Taiwan}

\author[0000-0002-1249-279X]{Hsi-Yu Schive}
\affiliation{Institute of Astrophysics, National Taiwan University, Taipei 10617, Taiwan}
\affiliation{Department of Physics, National Taiwan University, Taipei 10617, Taiwan}
\affiliation{Center for Theoretical Physics, National Taiwan University, Taipei 10617, Taiwan}
\affiliation{Physics Division, National Center for Theoretical Sciences, Taipei 10617, Taiwan}

\author[0000-0003-2654-8763]{Tzihong Chiueh}
\affiliation{Institute of Astrophysics, National Taiwan University, Taipei 10617, Taiwan}
\affiliation{Department of Physics, National Taiwan University, Taipei 10617, Taiwan}
\affiliation{Center for Theoretical Physics, National Taiwan University, Taipei 10617, Taiwan}

\correspondingauthor{Po-Hsun Tseng}
\email{zengbs@gmail.com}

\keywords{keywords}

\begin{abstract}
\end{abstract}

\section{Introduction}

\section{Methodology}
We simulate 3D special relativistic hydrodynamics with passive CR injections from the GC using \
the GPU code \textsc{gamer-sr} \citep{tseng2021}.

\begin{subequations}
  \label{conservative-form}
  \begin{align}
   &\partial_{t} D+\partial_{j} \left(DU^{j}/\gamma\right)=0,\label{D evolution}\\
   &\partial_{t} M^{i}+\partial_{j} \left(M^{i}U^{j}/\gamma+p\delta^{ij}\right)=0,\label{M evolution}\\
   &\partial_{t} \tilde{E}+\partial_j \left[\left(\tilde{E}+p\right)U^{j}/\gamma\right]=0, \label{E evoltion}\\
   &\partial_{t} \left(\gamma e_{\text{cr}}\right) + \partial_{j} \left(e_{\text{cr}}U^{j}\right)=-p_{\text{cr}}\left(\frac{\partial\gamma}{\partial t} + \frac{1}{c}\partial_{j} U^{j}\right),\label{D evolution}
  \end{align}
\end{subequations}
where the five conserved quantities of gas $D$, $M^{i}$, and $\tilde{E}$ are the mass density, \
the momentum densities, and the reduced energy density, respectively. \
$\gamma$ and $U^{j}$ are the temporal and spatial component of four-velocity of gas. \
$p_{\text{cr}}$ and $e_{\text{cr}}$ are the CR pressure and CR energy density. \
$c$ is the speed of light, and $\delta^{ij}$ is the Kronecker delta notation.

\subsection{Assumptions and Numerical Techniques}
\subsection{The Galactic Model}
\subsection{Jet injection}

\section{conclusions}

\section*{Data Availability}
The data underlying this article are available in the article and in its online supplementary material.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:

\bibliographystyle{mnras}
\bibliography{paper} % if your bibtex file is called example.bib

% Alternatively you could enter them by hand, like this:
% This method is tedious and prone to error if you have lots of references
%\begin{thebibliography}{99}
%\bibitem[\protect\citeauthoryear{Munz, Claus-Dieter and Núñez-de la Rosa, Jonatan}{2016}]{XTROEM}
%Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
%\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
%Others S., 2012, Journal of Interesting Stuff, 17, 198
%\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

\appendix

\end{document}

### 2021-10-17 paper.tex
update

@@
    &\partial_{t} D+\partial_{j} \left(DU^{j}/\gamma\right)=0,\label{D evolution}\\
-   &\partial_{t} M^{i}+\partial_{j} \left(M^{i}U^{j}/\gamma+p\delta^{ij}\right)=0,\label{M evolution}\\
-   &\partial_{t} \tilde{E}+\partial_j \left[\left(\tilde{E}+p\right)U^{j}/\gamma\right]=0, \label{E evoltion}\\
+   &\partial_{t} M^{i}+\partial_{j} \left(M^{i}U^{j}/\gamma+p_{\text{gas}}\delta^{ij}\right)=0,\label{M evolution}\\
+   &\partial_{t} \tilde{E}+\partial_j \left[\left(\tilde{E}+p_{\text{gas}}\right)U^{j}/\gamma\right]=0, \label{E evoltion}\\
    &\partial_{t} \left(\gamma e_{\text{cr}}\right) + \partial_{j} \left(e_{\text{cr}}U^{j}\right)=-p_{\text{cr}}\left(\frac{\partial\gamma}{\partial t} + \frac{1}{c}\partial_{j} U^{j}\right),\label{D evolution}
@@
 $\gamma$ and $U^{j}$ are the temporal and spatial component of four-velocity of gas. \
+$p_{\text{gas}}$ is the gas pressure.\
 $p_{\text{cr}}$ and $e_{\text{cr}}$ are the CR pressure and CR energy density. \
-$c$ is the speed of light, and $\delta^{ij}$ is the Kronecker delta notation.
+$c$ is the speed of light, and $\delta^{ij}$ is the Kronecker delta notation. \
+Throughout this paper, Latin indices run from 1 to 3, except when stated otherwise.
 

### 2021-10-18 paper.tex
update

--- 2021-10-17 paper.tex
@@
-\documentclass[twocolumn]{aastex63}
+\documentclass[twocolumn]{aastex631}
 \usepackage{mathtools}
@@
    &\partial_{t} D+\partial_{j} \left(DU^{j}/\gamma\right)=0,\label{D evolution}\\
-   &\partial_{t} M^{i}+\partial_{j} \left(M^{i}U^{j}/\gamma+p\delta^{ij}\right)=0,\label{M evolution}\\
-   &\partial_{t} \tilde{E}+\partial_j \left[\left(\tilde{E}+p\right)U^{j}/\gamma\right]=0, \label{E evoltion}\\
-   &\partial_{t} \left(\gamma e_{\text{cr}}\right) + \partial_{j} \left(e_{\text{cr}}U^{j}\right)=-p_{\text{cr}}\left(\frac{\partial\gamma}{\partial t} + \frac{1}{c}\partial_{j} U^{j}\right),\label{D evolution}
+   &\partial_{t} M^{i}+\partial_{j} \left(M^{i}U^{j}/\gamma+p_{\text{gas}}\delta^{ij}\right)=0,\label{M evolution}\\
+   &\partial_{t} \tilde{E}+\partial_j \left[\left(\tilde{E}+p_{\text{gas}}\right)U^{j}/\gamma\right]=0, \label{E evoltion}\\
+   &\partial_{t} \left(\gamma e_{\text{cr}}\right) + \partial_{j} \left(e_{\text{cr}}U^{j}\right)=-p_{\text{cr}} \partial_{j} U^{j},\label{D evolution}
   \end{align}
 \end{subequations}
-where the five conserved quantities of gas $D$, $M^{i}$, and $\tilde{E}$ are the mass density, \
-the momentum densities, and the reduced energy density, respectively. \
-$\gamma$ and $U^{j}$ are the temporal and spatial component of four-velocity of gas. \
-$p_{\text{cr}}$ and $e_{\text{cr}}$ are the CR pressure and CR energy density. \
-$c$ is the speed of light, and $\delta^{ij}$ is the Kronecker delta notation.
+where the five conserved quantities of gas $D$, $M^{i}$, and $\tilde{E}$ are the mass density,\
+the momentum densities, and the reduced energy density, respectively.\
+The reduced energy density is defined by subtracting the rest mass energy density of gas\
+from the total energy density of gas.\
+$\gamma$ and $U^{j}$ are the temporal and spatial component of four-velocity of gas.\
+$p_{\text{gas}}$ is the gas pressure.\
+$p_{\text{cr}}$ and $e_{\text{cr}}$ are the CR pressure and CR energy density measured in the local rest frame.\
+$c$ is the speed of light, and $\delta^{ij}$ is the Kronecker delta notation.\
+Throughout this paper, Latin indices run from 1 to 3, except when stated otherwise.
 

### 2021-10-21 paper.tex
udpate

@@
 \begin{document}
-\title{TITLE}
+\title{Fermi and eROSITA bubbles}
 
@@
 \section{Methodology}
+\subsection{Assumptions and Numerical Techniques}
+\begin{enumerate}
+  \item Cosmic-ray
+\begin{enumerate}
+  \item We treat CRs as a second fluid and solve directly for the evolution of CR pressure $p_{\text{cr}}$\
+        as a function of $\mathbf{r}$ and $t$.
+  \item We did not model the CR energy spectrum.
+  \item We neglected the cooling and heating processes of CRs, such as energy losses due to synchrotron\
+        and inverse Compton emission, and reacceleration in shocks.
+  \item We have assumed cosmic-ray is passive. (i.e. $p_{\text{cr}}\ll p_{\text{gas}}$)
+  \item We have assumed $\mathbf{B}$ is zero within the simulation box as the field inside\
+        the bubbles should be weak due to adiabatic expansion, and thus the magnetic fields has\
+        little effect on the overall dynamics.\
+        It might somewhat affect the instabilities near the bubble's surface, but that's a secondary effect.
+  \item Since $\mathbf{B}$ is zero, we can also ignore the effect of cosmic-ray diffusion.
+\end{enumerate}
+\end{enumerate}
 We simulate 3D special relativistic hydrodynamics with passive CR injections from the GC using \
-the GPU code \textsc{gamer-sr} \citep{tseng2021}.
+the special hydrodynamics GPU code \textsc{gamer-sr} \citep{tseng2021}.
+
+\textsc{gamer-sr} solves mass and energy-momentum conservation laws of a special relativistic ideal fluid\
+with CR
+
+The CRs are advected with the thermal gas, and inreturn the gas can react to the gradients of the CR pressure.\
+In this approach, the CRs are treated as a single species without distinction between electrons and protons.\
+We did not model the CR energy spectrum, and we neglected the cooling and heating processes of CRs,\
+such as energy losses due to synchrotron and inverse Compton emission, and reacceleration in shocks.\
 
@@
 
-\subsection{Assumptions and Numerical Techniques}
 \subsection{The Galactic Model}

### 2021-10-21 paper.tex
update

@@
 \usepackage{graphicx}
+\usepackage{url}
 \usepackage{subfigure}
@@
 \usepackage{empheq}
-%\usepackage{siunitx}
 \usepackage{booktabs}
@@
 \begin{enumerate}
+  \item \textsc{gamer-sr}
+    \begin{enumerate}
+      \item GPU acceleration.
+      \item Using a new algorithm dedicated to the conversion between primitive and conserved variable,\
+            significantly reducing numerical error in the non-relativistic limit.
+    \end{enumerate}
   \item Cosmic-ray
@@
 
-The CRs are advected with the thermal gas, and inreturn the gas can react to the gradients of the CR pressure.\
+The CRs are advected with the thermal gas, but the gas cannot react to the CR pressure.\
 In this approach, the CRs are treated as a single species without distinction between electrons and protons.\
@@
 \subsection{The Galactic Model}
+
+\begin{enumerate}
+\item Gravity
+  \begin{enumerate}
+    \item
+    \item
+  \end{enumerate}
+
+\item Cold disk
+  \begin{enumerate}
+    \item The fractal density is created using the publicly\
+          available pyFC code\footnote{\url{https://pypi.python.org/pypi/pyFC}}.
+    \item
+  \end{enumerate}
+\end{enumerate}
+
 \subsection{Jet injection}

### 2021-10-21 paper.tex
update

@@
       \item Using a new algorithm dedicated to the conversion between primitive and conserved variable,\
-            significantly reducing numerical error in the non-relativistic limit.
+            significantly reducing numerical error caused by the non-relativistic cold disk.
     \end{enumerate}

### 2021-10-21 paper.tex
update

@@
     \end{enumerate}
+  \item Gravity
+    \begin{enumerate}
+      \item Since , we have assumed the 
+    \end{enumerate}
 \end{enumerate}
@@
 \textsc{gamer-sr} solves mass and energy-momentum conservation laws of a special relativistic ideal fluid\
-with CR
+with CR.
 
@@
    &\partial_{t} D+\partial_{j} \left(DU^{j}/\gamma\right)=0,\label{D evolution}\\
-   &\partial_{t} M^{i}+\partial_{j} \left(M^{i}U^{j}/\gamma+p_{\text{gas}}\delta^{ij}\right)=0,\label{M evolution}\\
+   &\partial_{t} M^{i}+\partial_{j} \left(M^{i}U^{j}/\gamma+p_{\text{gas}}\delta^{ij}\right)=\
+   -\rho\partial_{i}\Phi,\label{M evolution}\\
    &\partial_{t} \tilde{E}+\partial_j \left[\left(\tilde{E}+p_{\text{gas}}\right)U^{j}/\gamma\right]=0, \label{E evoltion}\\
@@
 $\gamma$ and $U^{j}$ are the temporal and spatial component of four-velocity of gas.\
+$\rho$ is the gas density in the local rest frame defined by $D/\gamma$.\
 $p_{\text{gas}}$ is the gas pressure.\
 $p_{\text{cr}}$ and $e_{\text{cr}}$ are the CR pressure and CR energy density measured in the local rest frame.\
+$\Phi$ is the gravitation potential.\
 $c$ is the speed of light, and $\delta^{ij}$ is the Kronecker delta notation.\
@@
 \begin{enumerate}
-\item Gravity
+\item Gravitational potential
   \begin{enumerate}
-    \item
-    \item
+    \item Isothermal slab
+    \item NFW potential
   \end{enumerate}
@@
 \subsection{Jet injection}
+
+\subsection{X-ray and Gamma-ray emission}
+  \begin{enumerate}
+    \item X-ray
+       \begin{enumerate}
+         \item
+       \end{enumerate}
+    \item Gamma-ray
+       \begin{enumerate}
+         \item
+       \end{enumerate}
+  \end{enumerate}
 

### 2021-10-23 paper.tex
update

@@
 \begin{enumerate}
-  \item \textsc{gamer-sr}
+  \item Numerical features:
     \begin{enumerate}
-      \item GPU acceleration.
+      \item GPU acceleration with the \textsc{gamer-sr} code.
+      \item Special relativistic hydrodynamics.
       \item Using a new algorithm dedicated to the conversion between primitive and conserved variable,\
@@
     \end{enumerate}
-  \item Cosmic-ray
+  \item Assumptions on cosmic-ray:
     \begin{enumerate}
@@
     \end{enumerate}
-  \item Gravity
+  \item Assumptions on gravity:
     \begin{enumerate}
-      \item Since , we have assumed the 
+      \item The ISM disk and atmosphere are subjected to the fixed external potential of bulge.
+      \item In addition to the gravitational interaction, we ignore other interactions between stars and gases.
+      \item We also ignore the self-gravity of the ISM disk and of the atmosphere.
+      \item We ignore the Milky Way rotation.
+      \item We use the potential of isothermal slab to mimic the fixed gravitational potential of the stellar bulge.
+      \item The interface between cold ISM disk and atmosphere is parallel to galactic plane and is pressure balanced.
     \end{enumerate}
@@
 \begin{enumerate}
-\item Gravitational potential
+\item Fixed externel gravitational potential:
   \begin{enumerate}
-    \item Isothermal slab
-    \item NFW potential
+    \item Bulge:
+      \begin{enumerate}
+       \item Peak density: $\rho_{\text{bulge}}^{\text{peak}}=4\times 10^{-24}$ g/cm$^3$.
+       \item Potential (isothermal slab):
+         \begin{equation}
+           \Phi_{\text{bulge}}=\
+           2\sigma^2_{\text{bulge}}\
+           \ln\cosh\left(z\sqrt{\frac{2\pi G\rho_{\text{bulge}}^{\text{peak}}}{\sigma^2_{\text{bulge}}}}\right),
+         \end{equation}
+          where $\displaystyle \sigma_{\text{bulge}}=\
+                \sqrt{\frac{k_{B}T_{\text{bulge}}}{m}}=100$ km/s \citep{velocity-dispersion-MW}.
       \end{enumerate}
 
-\item Cold disk
+    \item Dark logarithmic halo:
+         \begin{equation}
+           \Phi_{\text{halo}}=v^2_{\text{halo}}\ln\left(z^2+d^2_{\text{h}}\right),
+         \end{equation}
+         where $v_{\text{halo}}=131.5$ km/s, $d_{\text{h}}=12$ kpc.
+
+  \end{enumerate}
+
+\item Clummpy cold disk:
   \begin{enumerate}
+    \item Scale height: $z_{0}=100$ pc. \citep{paek-ism-density}
+    \item Peak density: $\rho_{\text{disk}}^{\text{peak}}=10^{-23}$ g/cm$^3$. \citep{paek-ism-density}
+    \item $T_{\text{disk}}=10^{3}$ K. \citep{paek-ism-density}
+    \item Density:
+          \begin{equation}
+             \rho_{\text{disk}}=\rho_{\text{disk}}^{\text{peak}}
+             \exp\left[-\frac{\Phi_{\text{bulge}}}{k_{B}T_{\text{disk}}/m}\right].
+             \label{disk-density}
+          \end{equation}
+
     \item The fractal density is created using the publicly\
           available pyFC code\footnote{\url{https://pypi.python.org/pypi/pyFC}}.
-    \item
-  \end{enumerate}
   \end{enumerate}
 
+\item Isothermal atmosphere:
+  \begin{enumerate}
+     \item $T_{\text{atmp}}=10^{6}$ K. \citep{temperature-MW}
+     \item Density:
+          \begin{equation}
+             \rho_{\text{atmp}}=\rho_{\text{atmp}}^{\text{peak}}
+             \exp\left[-\frac{\Phi_{\text{bulge}}}{k_{B}T_{\text{atmp}}/m}\right],
+             \label{atmosphere-density}
+          \end{equation}
+          where $\rho_{\text{atmp}}^{\text{peak}}$ can be obtained by assuming that pressure\
+          and gravitational potential are continuous at the interface between disk and atmosphere (i.e. $z=\pm z_{0}$).
+  \end{enumerate}
+
+\end{enumerate}
 \subsection{Jet injection}
@@
   \begin{enumerate}
-    \item X-ray
+    \item X-ray:
        \begin{enumerate}
-         \item
+         \item Thermal bremsstrahlung:
        \end{enumerate}
-    \item Gamma-ray
+    \item Gamma-ray:
        \begin{enumerate}
-         \item
+         \item Hadronic process:
        \end{enumerate}

### 2021-10-23 paper.tex
update

@@
           where $\rho_{\text{atmp}}^{\text{peak}}$ can be obtained by assuming that pressure\
-          and gravitational potential are continuous at the interface between disk and atmosphere (i.e. $z=\pm z_{0}$).
+          and gravitational potential are continuous at the interface ($z=\pm z_{0}$) between disk and atmosphere.
   \end{enumerate}

### 2021-10-26 paper.tex
update

@@
       \item We have assumed cosmic-ray is passive. (i.e. $p_{\text{cr}}\ll p_{\text{gas}}$)
-      \item We have assumed $\mathbf{B}$ is zero within the simulation box as the field inside\
+      \item We have ignored the $\mathbf{B}$ field within\
+            the simulation box as the field inside\
             the bubbles should be weak due to adiabatic expansion, and thus the magnetic fields has\
             little effect on the overall dynamics.\
-            It might somewhat affect the instabilities near the bubble's surface, but that's a secondary effect.
-      \item Since $\mathbf{B}$ is zero, we can also ignore the effect of cosmic-ray diffusion.
+            We also assumed the magnetic field is highly entangled in small-scale (how small?), resulting in\
+            the negligible cosmic-ray diffusion.
     \end{enumerate}
@@
     \begin{enumerate}
-      \item The ISM disk and atmosphere are subjected to the fixed external potential of bulge.
+      \item We have assumed relativistic gravity is insignificant.
+      \item The ISM disk and atmosphere are subjected to the fixed external potential\
+            contributed by disk bulge and dark matter halo.
       \item In addition to the gravitational interaction, we ignore other interactions between stars and gases.
@@
 \begin{enumerate}
-\item Fixed externel gravitational potential:
+\item Fixed external gravitational potential:
   \begin{enumerate}
-    \item Bulge:
+    \item Bulge potential:
       \begin{enumerate}
@@
 
-    \item Dark logarithmic halo:
+    \item Dark logarithmic halo potential:
          \begin{equation}
@@
          \end{equation}
-         where $v_{\text{halo}}=131.5$ km/s, $d_{\text{h}}=12$ kpc.
+         where $v_{\text{halo}}=131.5$ km/s, $d_{\text{h}}=12$ kpc \citep{Yang2013}.
 
+    \item Total potential: $\Phi_{\text{total}}=\Phi_{\text{bulge}}+\Phi_{\text{halo}}$.
   \end{enumerate}
 
-\item Clummpy cold disk:
+\item Clumpy cold disk:
   \begin{enumerate}
-    \item Scale height: $z_{0}=100$ pc. \citep{paek-ism-density}
-    \item Peak density: $\rho_{\text{disk}}^{\text{peak}}=10^{-23}$ g/cm$^3$. \citep{paek-ism-density}
-    \item $T_{\text{disk}}=10^{3}$ K. \citep{paek-ism-density}
-    \item Density:
+    \item Dimension: $14\times14\times0.2$ kpc. i.e. Scale heght $=z_{0}=100$ pc. \citep{paek-ism-density}
+    \item Peak mass density: $\rho_{\text{disk}}^{\text{peak}}=10^{-23}$ g/cm$^3$. \citep{paek-ism-density}
+    \item Temperature: $T_{\text{disk}}=10^{3}$ K. \citep{paek-ism-density}
+    \item Average mass density:
           \begin{equation}
              \rho_{\text{disk}}=\rho_{\text{disk}}^{\text{peak}}
-             \exp\left[-\frac{\Phi_{\text{bulge}}}{k_{B}T_{\text{disk}}/m}\right].
+             \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{disk}}/m}\right].
              \label{disk-density}
@@
 
-    \item The fractal density is created using the publicly\
-          available pyFC code\footnote{\url{https://pypi.python.org/pypi/pyFC}}.
+    \item Pressure: $\displaystyle p_{\text{disk}}=\rho_{\text{disk}}T_{\text{disk}}$.
+
+    \item The clumpy cuboid, using the publicly\
+          available pyFC code\footnote{\url{https://pypi.python.org/pypi/pyFC}},\
+          are described by a log-normal distribution with mean 1.0 and variance 5.0.\
+          Also, the power spectrum of the clumpy cuboid is characterized by $k_{\text{min}}$ and $\beta$,\
+          where $k_{\text{min}}$ sets the maximum cloud size within the clumpy cuboid,\
+          and $\beta$ is the slope of power spectrum in Fourier space.
+          In this paper, we set $\beta=-5/3$ and $k_{\text{min}}=375$ to follow the Kolmogorov spectrum\
+          and to limits the maximum size of an individual cloud to approximately 25 pc.
+
+    \item The clumpy disk is constructed by multiplying a fractal cuboid with \Cref{disk-density}.
+
+    \item The clouds and voids within clumpy disk are pressure balanced.
   \end{enumerate}
@@
              \rho_{\text{atmp}}=\rho_{\text{atmp}}^{\text{peak}}
-             \exp\left[-\frac{\Phi_{\text{bulge}}}{k_{B}T_{\text{atmp}}/m}\right],
+             \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{atmp}}/m}\right],
              \label{atmosphere-density}

### 2021-10-26 paper.tex
update

@@
     \begin{enumerate}
-      \item GPU acceleration with the \textsc{gamer-sr} code.
+      \item GPU acceleration with \textsc{gamer-sr} code.
       \item Special relativistic hydrodynamics.
-      \item Using a new algorithm dedicated to the conversion between primitive and conserved variable,\
-            significantly reducing numerical error caused by the non-relativistic cold disk.
+      \item Using a new algorithm \citep{tseng2021} dedicated to the conversion between primitive and conserved variable,\
+            significantly reducing numerical error caused by catastrophic cancellation occurs\
+            within the non-relativistically cold disk.
     \end{enumerate}
@@
   \begin{enumerate}
-    \item Dimension: $14\times14\times0.2$ kpc. i.e. Scale heght $=z_{0}=100$ pc. \citep{paek-ism-density}
+    \item Dimension: $14\times14\times0.2$ kpc. i.e. Scale height $(z_{0})=100$ pc. \citep{paek-ism-density}
     \item Peak mass density: $\rho_{\text{disk}}^{\text{peak}}=10^{-23}$ g/cm$^3$. \citep{paek-ism-density}
@@
 
-    \item The clumpy disk is constructed by multiplying a fractal cuboid with \Cref{disk-density}.
+    \item The clumpy disk is then constructed by multiplying a fractal cuboid with \Cref{disk-density}.
 
@@
   \begin{enumerate}
+     \item The region outside the clumpy cold disk is atmosphere.
      \item $T_{\text{atmp}}=10^{6}$ K. \citep{temperature-MW}

### 2021-10-26 paper.tex
update

@@
       \item Special relativistic hydrodynamics.
-      \item Using a new algorithm \citep{tseng2021} dedicated to the conversion between primitive and conserved variable,\
-            significantly reducing numerical error caused by catastrophic cancellation occurs\
-            within the non-relativistically cold disk.
+      \item Using a new algorithm \citep{tseng2021} dedicated to the conversion between\
+            primitive and conserved variable, significantly reducing\
+            numerical error caused by catastrophic cancellation occurs frequently\
+            within the jet-ISM interaction zones.
     \end{enumerate}
@@
 \end{enumerate}
-We simulate 3D special relativistic hydrodynamics with passive CR injections from the GC using \
+We simulate 3D special relativistic hydrodynamics with passive CR injections from the GC using\
 the special hydrodynamics GPU code \textsc{gamer-sr} \citep{tseng2021}.
@@
        \begin{enumerate}
-         \item Thermal bremsstrahlung:
+         \item Thermal bremsstrahlung: The X-ray emissivity in an energy range 1.4–1.6 keV is calculated\
+               using the MEKAL model (\citealt{Xray-1}; \citealt{Xray-2}; \citealt{Xray-3})\
+               implemented in the utility XSPEC\citep{XSPEC}, assuming solar metallicity.
        \end{enumerate}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 %%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
-
-% The best way to enter references is to use BibTeX:
-
 \bibliographystyle{mnras}
 \bibliography{paper} % if your bibtex file is called example.bib
-
-% Alternatively you could enter them by hand, like this:
-% This method is tedious and prone to error if you have lots of references
-%\begin{thebibliography}{99}
-%\bibitem[\protect\citeauthoryear{Munz, Claus-Dieter and Núñez-de la Rosa, Jonatan}{2016}]{XTROEM}
-%Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
-%\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
-%Others S., 2012, Journal of Interesting Stuff, 17, 198
-%\end{thebibliography}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2021-10-27 paper.tex
update

@@
       \item Special relativistic hydrodynamics.
-      \item Using a new algorithm \citep{tseng2021} dedicated to the conversion between\
-            primitive and conserved variable, significantly reducing\
-            numerical error caused by catastrophic cancellation occurs frequently\
+      \item We use a new algorithm \citep{tseng2021}, dedicated to the conversion between\
+            primitive and conserved variables, to significantly reduce\
+            numerical error caused by catastrophic cancellations that commonly occur\
             within the jet-ISM interaction zones.
@@
       \item The ISM disk and atmosphere are subjected to the fixed external potential\
-            contributed by disk bulge and dark matter halo.
+            due to a disk bulge and dark matter halo.
       \item In addition to the gravitational interaction, we ignore other interactions between stars and gases.
       \item We also ignore the self-gravity of the ISM disk and of the atmosphere.
-      \item We ignore the Milky Way rotation.
-      \item We use the potential of isothermal slab to mimic the fixed gravitational potential of the stellar bulge.
+      \item We ignore the centrifugal force due to the rotation of Milky Way.
+      \item We use the potential of isothermal slab to mimic the gravitational potential due to the stellar bulge.
       \item The interface between cold ISM disk and atmosphere is parallel to galactic plane and is pressure balanced.

### 2021-10-28 paper.tex
update

@@
     \end{enumerate}
+  \item Assumptions on hydrodynamics:
+    \begin{enumerate}
+      \item Ideal fluid with TM EoS.
+    \end{enumerate}
   \item Assumptions on cosmic-ray:
@@
             little effect on the overall dynamics.\
-            We also assumed the magnetic field is highly entangled in small-scale (how small?), resulting in\
+            We also assumed the magnetic field is highly entangled on small-scale (how small?), resulting in\
             the negligible cosmic-ray diffusion.
@@
     \begin{enumerate}
-      \item We have assumed relativistic gravity is insignificant.
+      \item We use the potential of isothermal slab, symmetric about $z=0$ and\
+            supported by gas pressure and under its own self-gravity,\
+            to mimic the realistic potential of Galactic bulge.
+      \item We still use Newtonian gravity as relativistic fluid ejected by the jet source\
+            is quickly slowed down by heavy disk in a short time, and the relativistic fluid\
+            accounts for a little minority of total mass inside the simulation box.
       \item The ISM disk and atmosphere are subjected to the fixed external potential\
@@
       \item We also ignore the self-gravity of the ISM disk and of the atmosphere.
-      \item We ignore the centrifugal force due to the rotation of Milky Way.
+      \item We ignore the centrifugal force of Milky Way rotation acting on the bubbles.
       \item We use the potential of isothermal slab to mimic the gravitational potential due to the stellar bulge.

### 2021-11-04 paper.tex
update

@@
             numerical error caused by catastrophic cancellations that commonly occur\
-            within the jet-ISM interaction zones.
+            within the regions with high Mach number. i.e. jet-ISM interaction zones.
+      \item To further alleviate the numerical error due to high Mach number,\
+            \textsc{gamer-sr} also adaptively reduce the min-mod coefficient \citep{tseng2021}\
+            inside the failed patch.\
+            Doing so provides an elegant way to avoid the use of pressure/density floor,\
+            which is unnatural but widely used in almost publicly available code.
+      \item Accuracy analysis and show why it is a numerical challenge.
     \end{enumerate}

### 2021-11-05 paper.tex
update

@@
       \item Special relativistic hydrodynamics.
-      \item We use a new algorithm \citep{tseng2021}, dedicated to the conversion between\
-            primitive and conserved variables, to significantly reduce\
+      \item We use a new algorithm \citep{tseng2021} to convert between\
+            primitive and conserved variables, significantly reducing\
             numerical error caused by catastrophic cancellations that commonly occur\
@@
             which is unnatural but widely used in almost publicly available code.
-      \item Accuracy analysis and show why it is a numerical challenge.
     \end{enumerate}
@@
     \begin{enumerate}
-      \item Ideal fluid with TM EoS.
+      \item Ideal fluid with TM EoS (\citealt{Taub}; \citealt{TM_EOS}).
     \end{enumerate}
@@
       \item We have assumed cosmic-ray is passive. (i.e. $p_{\text{cr}}\ll p_{\text{gas}}$)
-      \item We have ignored the $\mathbf{B}$ field within\
+      \item \textcolor{red}{We have ignored the $\mathbf{B}$ field within\
             the simulation box as the field inside\
@@
             We also assumed the magnetic field is highly entangled on small-scale (how small?), resulting in\
-            the negligible cosmic-ray diffusion.
+            the negligible cosmic-ray diffusion.}
     \end{enumerate}
@@
       \item We use the potential of isothermal slab, symmetric about $z=0$ and\
-            supported by gas pressure and under its own self-gravity,\
+            supported by gas pressure and by under its own self-gravity,\
             to mimic the realistic potential of Galactic bulge.
-      \item We still use Newtonian gravity as relativistic fluid ejected by the jet source\
+      \item We still use Newtonian gravity, as the relativistic fluid ejected by the jet source\
             is quickly slowed down by heavy disk in a short time, and the relativistic fluid\
@@
       \item We use the potential of isothermal slab to mimic the gravitational potential due to the stellar bulge.
-      \item The interface between cold ISM disk and atmosphere is parallel to galactic plane and is pressure balanced.
+      \item The interface between cold ISM disk and atmosphere is parallel to the Galactic plane and is pressure balanced.
     \end{enumerate}
@@
   \begin{enumerate}
-    \item Dimension: $14\times14\times0.2$ kpc. i.e. Scale height $(z_{0})=100$ pc. \citep{paek-ism-density}
+    \item Dimension: $14\times14\times0.2$ kpc. i.e. Scale height, $z_{0}=100$ pc. \citep{paek-ism-density}
     \item Peak mass density: $\rho_{\text{disk}}^{\text{peak}}=10^{-23}$ g/cm$^3$. \citep{paek-ism-density}
-    \item Temperature: $T_{\text{disk}}=10^{3}$ K. \citep{paek-ism-density}
+    \item Average temperature: $T_{\text{disk}}=10^{3}$ K. \citep{paek-ism-density}
     \item Average mass density:
@@
        \begin{enumerate}
-         \item Hadronic process:
+         \item Hadronic process:pion decay
+          In the hadronic model, CRp undergo hadronic collisions with thermal gas protons\
+          and produce $\gamma$-ray via pion decay. The volume emissivity of the emission can be writen as
+          \begin{equation}
+             \epsilon \propto U_{\text{CRp}}n_{p}\sigma_{p}\kappa_{pp}.
+          \end{equation}
        \end{enumerate}

### 2021-11-05 paper.tex
update

@@
        \begin{enumerate}
-         \item Hadronic process:pion decay
+         \item Leptonic process:\\
+          The gamma-ray emission is produced by inverse Comptom scattering of the ISRF by CRe.
+         \item Hadronic process:\\
           In the hadronic model, CRp undergo hadronic collisions with thermal gas protons\

### 2021-11-08 paper.tex
update

@@
           In the hadronic model, CRp undergo hadronic collisions with thermal gas protons\
-          and produce $\gamma$-ray via pion decay. The volume emissivity of the emission can be writen as
+          and produce $\gamma$-ray via pion decay. The volume emissivity of the emission can be written as
           \begin{equation}
@@
   \end{enumerate}
+
+Note that the observed X-ray emission is contributed by all the gas in the Milky Way halo,\
+which likely extends to a radius of $\sim$250 kpc (\citealt{halo-radius-1}; \citealt{halo-radius-2}),\
+much bigger than our simulation box. Therefore, we first compute the X-ray emissivity\
+from the simulated gas within a radius of 25 kpc away from the GC.
+Then, beyond 25 kpc the gas is assumed to be isothermal with $T=10^6$ K and\
+follows out to a radius of 250 kpc the observed density profile of \citep{temperature-MW}.
 

### 2021-12-09 paper.tex
update

@@
 \subsection{Assumptions and Numerical Techniques}
+  We used the GPU-accelerated special relativistic hydrodynamics AMR code (\textsc{gamer-sr}) developed at the\
+  National Taiwan University\
+  (Schive et al. \citeyear{gamer-1}, \citeyear{gamer-2}; \citeauthor{tseng2021} \citeyear{tseng2021}) to carry out\
+  the simulations of Fermi and eROSITA bubbles. \textsc{gamer-sr} adopts a new algorithm \citep{tseng2021} to convert between\
+  primitive and conserved variables, significantly reducing numerical error caused by catastrophic cancellations\
+  that commonly occur within the regions with high Mach number. i.e. jet-ISM interaction zones.
+
+  \textsc{gamer-sr} also adaptively and locally reduce the min-mod coefficient \citep{tseng2021} within the failed patch group.\
+  Doing so provides an elegant way to avoid the use of pressure/density floor,\
+  being unnatural but widely used in almost publicly available code.
+  %to further alleviate the numerical error due to extremely high Mach number,\
+
+  The simulation box is $14\times14\times28$ kpc, slightly larger than the size of eROISTA bubbles,\
+  with a root grid $N=16\times16\times32$. We resolve the jet source located at the center of the simulation domain,\
+  cells are refined to level 11, leading to a finest spatial resolution of 0.4 pc.\
+
+  To save computational costs further, we restrict the refinement level is 7 within the cold disk so that\
+  a molecular colud can be adequately resolved by approximately 30 cells along their diameter, 100 pc.
+
+  We treat CRs as a second fluid and solve directly for the evolution of CR pressure $p_{\text{cr}}$\
+  as a function of $\mathbf{r}$ and $t$.\
+  We did not model the CR energy spectrum and neglect the cooling and heating processes of CRs,\
+  such as energy losses due to synchrotron and inverse Compton emission, and reacceleration in shocks.
+
+  We have assumed cosmic-ray is passive. (i.e. $p_{\text{cr}}\ll p_{\text{gas}}$)
+
+  We have ignored the $\mathbf{B}$ field within\
+  the simulation box as the field inside\
+  the bubbles should be weak due to adiabatic expansion, and thus the magnetic fields has\
+  little effect on the overall dynamics.\
+
+  We also assumed the magnetic field is highly entangled on small-scale (how small?), resulting in\
+  the negligible cosmic-ray diffusion.
+
+  \textsc{gamer-sr} solves the mass and energy-momentum conservation laws of special relativistic ideal fluid\
+  including CR advection, and dynamical coupling between the thermal gas and CRs. The governing equations\
+  can be written as
+
 \begin{enumerate}
-  \item Numerical features:
-    \begin{enumerate}
-      \item GPU acceleration with \textsc{gamer-sr} code.
-      \item Special relativistic hydrodynamics.
-      \item We use a new algorithm \citep{tseng2021} to convert between\
-            primitive and conserved variables, significantly reducing\
-            numerical error caused by catastrophic cancellations that commonly occur\
-            within the regions with high Mach number. i.e. jet-ISM interaction zones.
-      \item To further alleviate the numerical error due to high Mach number,\
-            \textsc{gamer-sr} also adaptively reduce the min-mod coefficient \citep{tseng2021}\
-            inside the failed patch.\
-            Doing so provides an elegant way to avoid the use of pressure/density floor,\
-            which is unnatural but widely used in almost publicly available code.
-    \end{enumerate}
   \item Assumptions on hydrodynamics:
@@
     \end{enumerate}
-  \item Assumptions on cosmic-ray:
-    \begin{enumerate}
-      \item We treat CRs as a second fluid and solve directly for the evolution of CR pressure $p_{\text{cr}}$\
-            as a function of $\mathbf{r}$ and $t$.
-      \item We did not model the CR energy spectrum.
-      \item We neglected the cooling and heating processes of CRs, such as energy losses due to synchrotron\
-            and inverse Compton emission, and reacceleration in shocks.
-      \item We have assumed cosmic-ray is passive. (i.e. $p_{\text{cr}}\ll p_{\text{gas}}$)
-      \item \textcolor{red}{We have ignored the $\mathbf{B}$ field within\
-            the simulation box as the field inside\
-            the bubbles should be weak due to adiabatic expansion, and thus the magnetic fields has\
-            little effect on the overall dynamics.\
-            We also assumed the magnetic field is highly entangled on small-scale (how small?), resulting in\
-            the negligible cosmic-ray diffusion.}
-    \end{enumerate}
+%  \item Assumptions on cosmic-ray:
+%    \begin{enumerate}
+%      \item We treat CRs as a second fluid and solve directly for the evolution of CR pressure $p_{\text{cr}}$\
+%            as a function of $\mathbf{r}$ and $t$.
+%      \item We did not model the CR energy spectrum.
+%      \item We neglected the cooling and heating processes of CRs, such as energy losses due to synchrotron\
+%            and inverse Compton emission, and reacceleration in shocks.
+%      \item We have assumed cosmic-ray is passive. (i.e. $p_{\text{cr}}\ll p_{\text{gas}}$)
+%      \item \textcolor{red}{We have ignored the $\mathbf{B}$ field within\
+%            the simulation box as the field inside\
+%            the bubbles should be weak due to adiabatic expansion, and thus the magnetic fields has\
+%            little effect on the overall dynamics.\
+%            We also assumed the magnetic field is highly entangled on small-scale (how small?), resulting in\
+%            the negligible cosmic-ray diffusion.}
+%    \end{enumerate}
   \item Assumptions on gravity:
@@
 \subsection{Jet injection}
+ \begin{enumerate}
+    \item Why the overall structure is insensitive to jet direction?
+      \begin{enumerate}
+        \item Jet source size.
+        \item Cold disk.
+        \item Large pressure gradient along z-dircetion.
+      \end{enumerate}
+ \end{enumerate}
 
 \subsection{X-ray and Gamma-ray emission}
+
   \begin{enumerate}
@@
 
+Inverse Compton scattering
+\begin{equation}
+  \frac{dE}{dtd\epsilon_{1}dV} = \frac{3}{4}\sigma_{T}c\textit{C}\int^{\epsilon_{\text{max}}}_{\epsilon_{\text{min}}}
+               \epsilon_{1}\frac{n(\epsilon)}{\epsilon}d\epsilon\int^{\gamma_{\text{max}}}_{\gamma_{\text{min}}}
+               \gamma^{-(p+2)}f(q, \Gamma)d\gamma.
+\end{equation}
+
+\begin{equation}
+f(q, \Gamma) = 2q\ln q+(1+2q)(1-q)+0.5(1-q)\frac{\left(\Gamma q\right)^2}{1+\Gamma q},
+\end{equation}
+
+\begin{equation}
+\Gamma=\frac{4\epsilon \gamma_{\text{e}}}{m_{\text{e}}c^2}
+\end{equation}
+
+\begin{equation}
+q=\frac{\epsilon_{1}/\gamma_{\text{e}}m_{\text{e}}c^{2}}{\Gamma\left(1-\epsilon_{1}/\gamma_{\text{e}}m_{\text{e}}c^{2}\right)}.
+\end{equation}
+
+Hadronic process
+\begin{equation}
+  \frac{dE}{dtd\epsilon_{1}dV} = cn_{H}pC\left(\frac{\epsilon_{1}}{m_{\text{p}}c^2}\right)^{-p}\int_{0}^{1}\sigma(\epsilon_{\text{p}}) F(x,\epsilon_{\text{p}}) x^{p}dx.
+\end{equation}
+
+\begin{equation}
+\sigma(\epsilon_{\text{p}})=34.3+1.88L+0.25L^{2} \text{ mb}.
+\end{equation}
+
+\begin{equation}
+F(x,\epsilon_{\text{p}})=B\frac{d}{dx}\left[\ln(x)\left(\frac{1-x^{\beta}}{1+kx^{\beta}\left(1-x^{\beta}\right)}\right)^4\right],
+\end{equation}
+
+where $B=1.30+0.14L+0.011L^2$, $\beta=\left(1.79+0.11L+0.008L^{2}\right)^{-1}$,\
+$\left(0.801+0.049L+0.014L^{2}\right)^{-1}$, $L=\ln(\epsilon_{\text{p}}/1 \text{ TeV})$.
+
+\section{to-do-list}
+\begin{enumerate}
+  \item Predict cold inner bubbles, emitting OIII or OII spectrum.
+\end{enumerate}
+
 \section{conclusions}

### 2021-12-13 paper.tex
update

@@
 \begin{abstract}
+\begin{enumerate}
+  \item Release the caveat of jet direction.
+  \item Rule out the hadronic process.
+  \item Predict the small inner bubbles.
+  \item How to explain why we assume e_CR << e_gas
+  \item How to explain the lifespan of bubbles is too long.
+  \item How to explain the jet power.
+  \item How to explain the inconsistant of gamma-ray map.
+\end{enumerate}
 \end{abstract}
@@
 \section{Methodology}
-\subsection{Assumptions and Numerical Techniques}
+
   We used the GPU-accelerated special relativistic hydrodynamics AMR code (\textsc{gamer-sr}) developed at the\
   National Taiwan University\
-  (Schive et al. \citeyear{gamer-1}, \citeyear{gamer-2}; \citeauthor{tseng2021} \citeyear{tseng2021}) to carry out\
-  the simulations of Fermi and eROSITA bubbles. \textsc{gamer-sr} adopts a new algorithm \citep{tseng2021} to convert between\
-  primitive and conserved variables, significantly reducing numerical error caused by catastrophic cancellations\
-  that commonly occur within the regions with high Mach number. i.e. jet-ISM interaction zones.
+  (Schive et al. \citeyear{gamer-1}, \citeyear{gamer-2}; \citeauthor{tseng2021} \citeyear{tseng2021})\
+  to carry out the simulations of the Fermi and eROSITA bubbles by CR and relativistic fluid injections from the GC.
 
-  \textsc{gamer-sr} also adaptively and locally reduce the min-mod coefficient \citep{tseng2021} within the failed patch group.\
-  Doing so provides an elegant way to avoid the use of pressure/density floor,\
-  being unnatural but widely used in almost publicly available code.
-  %to further alleviate the numerical error due to extremely high Mach number,\
+  The CRs are advected with the thermal gas, and in return the velocities of gas\
+  can react to the gradients of the CR pressure\
+  via the presence of a source (or coupling) term containing spatial derivatives of fluid velocities.
 
-  The simulation box is $14\times14\times28$ kpc, slightly larger than the size of eROISTA bubbles,\
-  with a root grid $N=16\times16\times32$. We resolve the jet source located at the center of the simulation domain,\
-  cells are refined to level 11, leading to a finest spatial resolution of 0.4 pc.\
+  Since CR diuusion insignificantly affect on the overall mophology of the Fermi bubbles\
+  but only sharpen the edges of the simulated bubbles by the interplay between anisotropic CR diffusion\
+  and magnetic fields
+with suppressed perpendicular diffusion across the bubble surface.
 
-  To save computational costs further, we restrict the refinement level is 7 within the cold disk so that\
-  a molecular colud can be adequately resolved by approximately 30 cells along their diameter, 100 pc.
+  Since the sharpness of bubble edges requires suppression of CR diffusion across the bubble surface
+ has a insignificant effect on the overall mophology of the Fermi bubbles
 
-  We treat CRs as a second fluid and solve directly for the evolution of CR pressure $p_{\text{cr}}$\
+  In this approach, the CRs are treated as a single species without distinction between electrons and protons.\
+  We do not simulate the spectral evolution of the CR, and we neglected the cooling and heating processes of CRs,\
+  such as energy losses due to synchrotron and inverse Compton emission, and reacceleration in shocks.\
+
+  We treat CRs as a second fluid with a initially fixed energy\
+  and solve directly for the evolution of CR pressure $p_{\text{cr}}$\
   as a function of $\mathbf{r}$ and $t$.\
-  We did not model the CR energy spectrum and neglect the cooling and heating processes of CRs,\
-  such as energy losses due to synchrotron and inverse Compton emission, and reacceleration in shocks.
 
@@
 
+  We still use Newtonian gravity, as the relativistic fluid ejected by the jet source\
+  is quickly slowed down by heavy disk in a short time, and the relativistic fluid\
+  accounts for a little minority of total mass inside the simulation box.
+
   \textsc{gamer-sr} solves the mass and energy-momentum conservation laws of special relativistic ideal fluid\
-  including CR advection, and dynamical coupling between the thermal gas and CRs. The governing equations\
-  can be written as
+  including CR advection, and dynamical coupling between the thermal gas and CRs without diffusion.\
+  The governing equations can be written as
+
+  \begin{subequations}
+    \label{conservative-form}
+    \begin{align}
+     &\partial_{t} D+\partial_{j} \left(DU^{j}/\gamma\right)=0,\label{D evolution}\\
+     &\partial_{t} M^{i}+\partial_{j} \left(M^{i}U^{j}/\gamma+p_{\text{gas}}\delta^{ij}\right)=\
+     -\rho\partial_{i}\Phi,\label{M evolution}\\
+     &\partial_{t} \tilde{E}+\partial_j \left[\left(\tilde{E}+p_{\text{gas}}\right)U^{j}/\gamma\right]=0, \label{E evoltion}\\
+     &\partial_{t} \left(\gamma e_{\text{cr}}\right) + \partial_{j} \left(e_{\text{cr}}U^{j}\right)=\
+     -p_{\text{cr}} \partial_{j} U^{j},\label{D evolution}
+    \end{align}
+  \end{subequations}
+
+  where the five conserved quantities of gas $D$, $M^{i}$, and $\tilde{E}$ are the mass density,\
+  the momentum densities, and the reduced energy density, respectively.\
+  The reduced energy density is defined by subtracting the rest mass energy density of gas\
+  from the total energy density of gas.\
+  $\gamma$ and $U^{j}$ are the temporal and spatial component of four-velocity of gas.\
+  $\rho$ is the gas density in the local rest frame defined by $D/\gamma$.\
+  $p_{\text{gas}}$ is the gas pressure.\
+  $p_{\text{cr}}$ and $e_{\text{cr}}$ are the CR pressure and CR energy density measured in the local rest frame.\
+  $\Phi$ is the gravitation potential.\
+  $c$ is the speed of light, and $\delta^{ij}$ is the Kronecker delta notation.\
+  Throughout this paper, Latin indices run from 1 to 3, except when stated otherwise.
+
+  \textsc{gamer-sr} adopts a new algorithm \citep{tseng2021} to convert between\
+  primitive ($p$, $\rho$, $U^{j}$) and conserved variables, significantly reducing numerical error\
+  caused by catastrophic cancellations\
+  that commonly occur within the regions with high Mach number. e.g., jet-ISM interaction zones.
+
+  \textsc{gamer-sr} also adaptively and locally reduce the min-mod coefficient \citep{tseng2021} within the failed patch group.\
+  Doing so provides an elegant way to avoid the use of pressure/density floor,\
+  being unnatural but widely used in almost publicly available code.
+  %to further alleviate the numerical error due to extremely high Mach number,\
+
+\subsection{Initial conditions for the Fermi and eROSITA bubbles}
+  The simulation box is $14\times14\times28$ kpc, slightly larger than the size of eROISTA bubbles,\
+  with a root grid $N=16\times16\times32$. We resolve the jet source located at the center of the simulation domain,\
+  cells are refined to level 11, leading to a finest spatial resolution of 0.4 pc.\
+
+  To save computational costs further, we restrict the refinement level is 7 within the cold disk so that\
+  a molecular colud can be adequately resolved by approximately 30 cells along their diameter, 100 pc.
 
@@
             to mimic the realistic potential of Galactic bulge.
-      \item We still use Newtonian gravity, as the relativistic fluid ejected by the jet source\
-            is quickly slowed down by heavy disk in a short time, and the relativistic fluid\
-            accounts for a little minority of total mass inside the simulation box.
+%      \item We still use Newtonian gravity, as the relativistic fluid ejected by the jet source\
+%            is quickly slowed down by heavy disk in a short time, and the relativistic fluid\
+%            accounts for a little minority of total mass inside the simulation box.
       \item The ISM disk and atmosphere are subjected to the fixed external potential\
@@
 with CR.
-
-The CRs are advected with the thermal gas, but the gas cannot react to the CR pressure.\
-In this approach, the CRs are treated as a single species without distinction between electrons and protons.\
-We did not model the CR energy spectrum, and we neglected the cooling and heating processes of CRs,\
-such as energy losses due to synchrotron and inverse Compton emission, and reacceleration in shocks.\
-
-\begin{subequations}
-  \label{conservative-form}
-  \begin{align}
-   &\partial_{t} D+\partial_{j} \left(DU^{j}/\gamma\right)=0,\label{D evolution}\\
-   &\partial_{t} M^{i}+\partial_{j} \left(M^{i}U^{j}/\gamma+p_{\text{gas}}\delta^{ij}\right)=\
-   -\rho\partial_{i}\Phi,\label{M evolution}\\
-   &\partial_{t} \tilde{E}+\partial_j \left[\left(\tilde{E}+p_{\text{gas}}\right)U^{j}/\gamma\right]=0, \label{E evoltion}\\
-   &\partial_{t} \left(\gamma e_{\text{cr}}\right) + \partial_{j} \left(e_{\text{cr}}U^{j}\right)=-p_{\text{cr}} \partial_{j} U^{j},\label{D evolution}
-  \end{align}
-\end{subequations}
-where the five conserved quantities of gas $D$, $M^{i}$, and $\tilde{E}$ are the mass density,\
-the momentum densities, and the reduced energy density, respectively.\
-The reduced energy density is defined by subtracting the rest mass energy density of gas\
-from the total energy density of gas.\
-$\gamma$ and $U^{j}$ are the temporal and spatial component of four-velocity of gas.\
-$\rho$ is the gas density in the local rest frame defined by $D/\gamma$.\
-$p_{\text{gas}}$ is the gas pressure.\
-$p_{\text{cr}}$ and $e_{\text{cr}}$ are the CR pressure and CR energy density measured in the local rest frame.\
-$\Phi$ is the gravitation potential.\
-$c$ is the speed of light, and $\delta^{ij}$ is the Kronecker delta notation.\
-Throughout this paper, Latin indices run from 1 to 3, except when stated otherwise.
 
@@
 \begin{equation}
-  \frac{dE}{dtd\epsilon_{1}dV} = \frac{3}{4}\sigma_{T}c\textit{C}\int^{\epsilon_{\text{max}}}_{\epsilon_{\text{min}}}
-               \epsilon_{1}\frac{n(\epsilon)}{\epsilon}d\epsilon\int^{\gamma_{\text{max}}}_{\gamma_{\text{min}}}
+  \frac{dE}{dtd\epsilon_{1}dV} = \frac{3}{4}\sigma_{T}c\textit{C}\epsilon_{1}\int^{\epsilon_{\text{max}}}_{\epsilon_{\text{min}}}
+               \frac{n(\epsilon)}{\epsilon}d\epsilon\int^{\gamma_{\text{max}}}_{\gamma_{\text{min}}\left(\epsilon\right)}
                \gamma^{-(p+2)}f(q, \Gamma)d\gamma.
@@
 \begin{equation}
-f(q, \Gamma) = 2q\ln q+(1+2q)(1-q)+0.5(1-q)\frac{\left(\Gamma q\right)^2}{1+\Gamma q},
+f(\gamma_{\text{e}}, \epsilon) = 2q\ln q+(1+2q)(1-q)+0.5(1-q)\frac{\left(\Gamma q\right)^2}{1+\Gamma q},
 \end{equation}
@@
 \end{equation}
+
+$\gamma_{\text{min}}\left(\epsilon\right)$ is the root of $f(\gamma_{\text{e}}, \epsilon)=0$ at a specific incident photon energy.
 
@@
 \begin{equation}
-\sigma(\epsilon_{\text{p}})=34.3+1.88L+0.25L^{2} \text{ mb}.
+\sigma(\epsilon_{\text{p}})=34.3+1.88L+0.25L^{2}\left[1-\frac{E_{\text{threshold}}}{E_{\text{p}}}\right]^{4} \text{ mb}.
 \end{equation}
@@
 
-where $B=1.30+0.14L+0.011L^2$, $\beta=\left(1.79+0.11L+0.008L^{2}\right)^{-1}$,\
+where
+$x=\epsilon_{1}/\epsilon_{\text{p}}$, $B=1.30+0.14L+0.011L^2$, $\beta=\left(1.79+0.11L+0.008L^{2}\right)^{-1}$,\
 $\left(0.801+0.049L+0.014L^{2}\right)^{-1}$, $L=\ln(\epsilon_{\text{p}}/1 \text{ TeV})$.

### 2021-12-14 paper.tex
update

@@
   \item Predict the small inner bubbles.
-  \item How to explain why we assume e_CR << e_gas
+  \item How to explain why we assume e\_CR << e\_gas
   \item How to explain the lifespan of bubbles is too long.
@@
   The CRs are advected with the thermal gas, and in return the velocities of gas\
-  can react to the gradients of the CR pressure\
-  via the presence of a source (or coupling) term containing spatial derivatives of fluid velocities.
+  can react to the gradients of the CR pressure via the source term\
+  containing spatial divergence of fluid velocities.\
 
-  Since CR diuusion insignificantly affect on the overall mophology of the Fermi bubbles\
-  but only sharpen the edges of the simulated bubbles by the interplay between anisotropic CR diffusion\
-  and magnetic fields
-with suppressed perpendicular diffusion across the bubble surface.
+  Although the high-energy CRe ($10$ --- $100$ GeV) plays a crucial role in reproducing the $\gamma$-ray map\
+  within the range of $1$ --- $100$ GeV, we assume the pressure of CRe is much less than that of gas\
+  thoughout the simulation so that we , and the Fermi bubbles can be outlined against the eROSITA bubbles.
 
-  Since the sharpness of bubble edges requires suppression of CR diffusion across the bubble surface
- has a insignificant effect on the overall mophology of the Fermi bubbles
+  As stressed by \citet{Yang2012}, CR diffusion has insignificant effect on the overall mophology of the Fermi bubbles,\
+  but only sharpens the edges of the simulated bubbles by the interplay between anisotropic CR diffusion\
+  and magnetic fields with suppressed perpendicular diffusion across the bubble surface. Morever,\
+  the bubbles should be weak due to adiabatic expansion, and thus the magnetic fields has\
+  little effect on the overall dynamics. For these two reasons,\
+  we have ignored the CR diffusion and the magnetic field throughout\
+  the simulation.
 
-  In this approach, the CRs are treated as a single species without distinction between electrons and protons.\
   We do not simulate the spectral evolution of the CR, and we neglected the cooling and heating processes of CRs,\
@@
 
-  We treat CRs as a second fluid with a initially fixed energy\
-  and solve directly for the evolution of CR pressure $p_{\text{cr}}$\
+  In this approach, we treat CRs as a single species without distinction between electrons and protons,\
+  that cannot react to the gas via the application of CRe pressure,\
+  and solve directly for the evolution of CR energy density $e_{\text{cr}}$\
   as a function of $\mathbf{r}$ and $t$.\
 
-  We have assumed cosmic-ray is passive. (i.e. $p_{\text{cr}}\ll p_{\text{gas}}$)
+  Since the relativistic fluid ejected by the jet source\
+  is quickly stalled off and slowed down by a dense ISM disk in a short time,\
+  and the relativistic fluid\
+  accounts for a little minority of total mass inside the simulation box,\
+  we still use the Newtonian gravity to attack this problem.
 
-  We have ignored the $\mathbf{B}$ field within\
-  the simulation box as the field inside\
-  the bubbles should be weak due to adiabatic expansion, and thus the magnetic fields has\
-  little effect on the overall dynamics.\
-
-  We also assumed the magnetic field is highly entangled on small-scale (how small?), resulting in\
-  the negligible cosmic-ray diffusion.
-
-  We still use Newtonian gravity, as the relativistic fluid ejected by the jet source\
-  is quickly slowed down by heavy disk in a short time, and the relativistic fluid\
-  accounts for a little minority of total mass inside the simulation box.
-
-  \textsc{gamer-sr} solves the mass and energy-momentum conservation laws of special relativistic ideal fluid\
-  including CR advection, and dynamical coupling between the thermal gas and CRs without diffusion.\
-  The governing equations can be written as
+  The governing equations solving the special relativistic ideal fluid\
+  including CR advection, and dynamical coupling between the thermal gas and CRs without diffusion\
+  turn out to be
 
@@
   \textsc{gamer-sr} adopts a new algorithm \citep{tseng2021} to convert between\
-  primitive ($p$, $\rho$, $U^{j}$) and conserved variables, significantly reducing numerical error\
-  caused by catastrophic cancellations\
+  primitive ($p$, $\rho$, $U^{j}$) and conserved variables, ($D$, $M^{j}$, $\tilde{E}$)\
+  significantly reducing numerical error caused by catastrophic cancellations\
   that commonly occur within the regions with high Mach number. e.g., jet-ISM interaction zones.
 
-  \textsc{gamer-sr} also adaptively and locally reduce the min-mod coefficient \citep{tseng2021} within the failed patch group.\
+  \textsc{gamer-sr} also adaptively and locally reduce the min-mod coefficient\
+  \citep{tseng2021} within the failed patch group.\
   Doing so provides an elegant way to avoid the use of pressure/density floor,\
   being unnatural but widely used in almost publicly available code.
-  %to further alleviate the numerical error due to extremely high Mach number,\
 

### 2021-12-14 paper.tex
update

@@
   within the range of $1$ --- $100$ GeV, we assume the pressure of CRe is much less than that of gas\
-  thoughout the simulation so that we , and the Fermi bubbles can be outlined against the eROSITA bubbles.
+  throughout the simulation so that we , and the Fermi bubbles can be outlined against the eROSITA bubbles.
 
-  As stressed by \citet{Yang2012}, CR diffusion has insignificant effect on the overall mophology of the Fermi bubbles,\
+  As stressed by \citet{Yang2012}, CR diffusion has insignificant effect on the overall morphology of the Fermi bubbles,\
   but only sharpens the edges of the simulated bubbles by the interplay between anisotropic CR diffusion\
-  and magnetic fields with suppressed perpendicular diffusion across the bubble surface. Morever,\
+  and magnetic fields with suppressed perpendicular diffusion across the bubble surface. Moreover,\
   the bubbles should be weak due to adiabatic expansion, and thus the magnetic fields has\
@@
   Doing so provides an elegant way to avoid the use of pressure/density floor,\
-  being unnatural but widely used in almost publicly available code.
+  being unnatural but widely used in almost publicly available codes.
 
@@
   To save computational costs further, we restrict the refinement level is 7 within the cold disk so that\
-  a molecular colud can be adequately resolved by approximately 30 cells along their diameter, 100 pc.
+  a molecular cloud can be adequately resolved by approximately 30 cells along their diameter, 100 pc.
 
@@
     \end{enumerate}
-%  \item Assumptions on cosmic-ray:
-%    \begin{enumerate}
-%      \item We treat CRs as a second fluid and solve directly for the evolution of CR pressure $p_{\text{cr}}$\
-%            as a function of $\mathbf{r}$ and $t$.
-%      \item We did not model the CR energy spectrum.
-%      \item We neglected the cooling and heating processes of CRs, such as energy losses due to synchrotron\
-%            and inverse Compton emission, and reacceleration in shocks.
-%      \item We have assumed cosmic-ray is passive. (i.e. $p_{\text{cr}}\ll p_{\text{gas}}$)
-%      \item \textcolor{red}{We have ignored the $\mathbf{B}$ field within\
-%            the simulation box as the field inside\
-%            the bubbles should be weak due to adiabatic expansion, and thus the magnetic fields has\
-%            little effect on the overall dynamics.\
-%            We also assumed the magnetic field is highly entangled on small-scale (how small?), resulting in\
-%            the negligible cosmic-ray diffusion.}
-%    \end{enumerate}
+
   \item Assumptions on gravity:

### 2021-12-16 paper.tex
update

@@
   The governing equations solving the special relativistic ideal fluid\
-  including CR advection, and dynamical coupling between the thermal gas and CRs without diffusion\
+  including CR advection, and dynamical coupling between the thermal gas and CRs without CR diffusion\
   turn out to be
@@
   $c$ is the speed of light, and $\delta^{ij}$ is the Kronecker delta notation.\
-  Throughout this paper, Latin indices run from 1 to 3, except when stated otherwise.
+  Throughout this paper, Latin indices run from 1 to 3, except when stated otherwise.\
+
+  The set of equations is closed by using the Taub-Mathews equation of state (\citealt{Taub}; \citealt{TM_EOS})\
+  that approximates the exact EoS \citep{Synge} for ultra-relativistically\
+  hot gases coexisting with non-relativistically cold gases.
 
@@
 
-  To save computational costs further, we restrict the refinement level is 7 within the cold disk so that\
+  To save computational costs, we restrict the refinement level is 7 within the cold disk so that\
   a molecular cloud can be adequately resolved by approximately 30 cells along their diameter, 100 pc.
@@
   \item Assumptions on hydrodynamics:
-    \begin{enumerate}
-      \item Ideal fluid with TM EoS (\citealt{Taub}; \citealt{TM_EOS}).
-    \end{enumerate}
 

### 2021-12-16 paper.tex
update

@@
   \textsc{gamer-sr} adopts a new algorithm \citep{tseng2021} to convert between\
-  primitive ($p$, $\rho$, $U^{j}$) and conserved variables, ($D$, $M^{j}$, $\tilde{E}$)\
+  primitive ($\rho$, $U^{j}$, $p$) and conserved variables ($D$, $M^{j}$, $\tilde{E}$),\
   significantly reducing numerical error caused by catastrophic cancellations\
@@
   Doing so provides an elegant way to avoid the use of pressure/density floor,\
-  being unnatural but widely used in almost publicly available codes.
+  being unnatural but widely used in almost publicly available codes.\
 
-\subsection{Initial conditions for the Fermi and eROSITA bubbles}
-  The simulation box is $14\times14\times28$ kpc, slightly larger than the size of eROISTA bubbles,\
-  with a root grid $N=16\times16\times32$. We resolve the jet source located at the center of the simulation domain,\
-  cells are refined to level 11, leading to a finest spatial resolution of 0.4 pc.\
+  \subsection{The Galactic Model}
 
-  To save computational costs, we restrict the refinement level is 7 within the cold disk so that\
-  a molecular cloud can be adequately resolved by approximately 30 cells along their diameter, 100 pc.
+  We model the external and fixed gravity of the Milky Way by prescribing a\
+  plane parallel self-gravitating isothermal slab, symmetry about the mid-plane $z=0$,\
+  in a simulation box size of\
+  $14\times14\times28$ kpc, slightly larger than the size of eROISTA bubbles.
+
+  In our 3D simulation, the Galactic potential can be written as
+
+  \begin{equation}
+    \Phi_{\text{total}} = \Phi_{\text{disk}} + \Phi_{\text{halo}},
+  \end{equation}
+
+  where $\Phi_{\text{halo}}=v^2_{\text{halo}}\ln\left(z^2+d^2_{\text{h}}\right)$\
+
+  is dark logarithmic halo potential,
+
+  \begin{equation}
+    \Phi_{\text{disk}}=\
+    2\sigma^2_{\text{disk}}\
+    \ln\cosh\left(z\sqrt{\frac{2\pi G\rho_{\text{disk}}^{\text{peak}}}{\sigma^2_{\text{disk}}}}\right),
+  \end{equation}
+
+  is the potential of a plane-parallel isothermal slab.
+
+  The slab is used to mimic the gravity contributed by the stars within the Galactic plane,\
+  the  thus
+
+  We mimic the galactic potential by using
+
+  The potential of slab is mainly contributed by the stars within the Galactic center.
+
+  The AMR base level is covered by $16\times16\times32$ root grids, refined progressively on the plane $z=0$\
+  , with the outflow boundary condition.
+
+  confined by an external dark halo potential.
+
+  We use three components (1) cold ISM disk (2) hot gas ambient (3) stellar disk\
+  to locally mimic the environment near the GC (i.e. no galactic rotation).\
+
+  The density distributions of ISM disk and hot gas ambient are derived from\
+  hydrostatic equilibrium within the fixed external potential.
+
+  We use the potential of isothermal slab, symmetric about $z=0$, and\
+  supported by gas pressure and by its own self-gravity,\
+  to mimic the realistic potential of Galactic bulge.
 
 \begin{enumerate}
-  \item Assumptions on hydrodynamics:
-
   \item Assumptions on gravity:
@@
             to mimic the realistic potential of Galactic bulge.
-%      \item We still use Newtonian gravity, as the relativistic fluid ejected by the jet source\
-%            is quickly slowed down by heavy disk in a short time, and the relativistic fluid\
-%            accounts for a little minority of total mass inside the simulation box.
       \item The ISM disk and atmosphere are subjected to the fixed external potential\
@@
 \end{enumerate}
-We simulate 3D special relativistic hydrodynamics with passive CR injections from the GC using\
-the special hydrodynamics GPU code \textsc{gamer-sr} \citep{tseng2021}.
-
-\textsc{gamer-sr} solves mass and energy-momentum conservation laws of a special relativistic ideal fluid\
-with CR.
-
-\subsection{The Galactic Model}
 
@@
 \end{enumerate}
+
+\subsection{Cold disk}
+  We restrict the refinement level is 7 within the cold disk so that\
+  a molecular cloud can be adequately resolved by approximately 30 cells along their diameter, 100 pc.\
+
 \subsection{Jet injection}
+  We resolve the jet source located at the center of the simulation domain,\
+  cells are refined to level 11, leading to a finest spatial resolution of 0.4 pc.\
+
  \begin{enumerate}

### 2021-12-16 paper.tex
update

@@
 
-  We model the external and fixed gravity of the Milky Way by prescribing a\
+  We model the external gravity of the Milky Way by prescribing a\
   plane parallel self-gravitating isothermal slab, symmetry about the mid-plane $z=0$,\
@@
   where $\Phi_{\text{halo}}=v^2_{\text{halo}}\ln\left(z^2+d^2_{\text{h}}\right)$\
-
   is dark logarithmic halo potential,
@@
 
-  is the potential of a plane-parallel isothermal slab.
+  is the potential of a plane-parallel isothermal slab contributed by stars within the Galactic plane.
 
-  The slab is used to mimic the gravity contributed by the stars within the Galactic plane,\
-  the  thus
+  The steady-state density distribution in a total potential, $\Phi_{\text{total}}$,\
+  for the atmosphere gas can be derived from the isothermal and hydrostatic equilibrium condition,\
+  given by
 
-  We mimic the galactic potential by using
+  \begin{equation}
+     \rho(z)=
+     \begin{cases}
+     \displaystyle\rho_{\text{atmp}}^{\text{peak}}
+     \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{atmp}}/m}\right] & \text{if z > $z_{0}$}\\
+     \displaystyle\rho_{\text{disk}}^{\text{peak}}
+     \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{disk}}/m}\right] & \text{if z > $z_{0}$}
+     \end{cases}
+  \end{equation}
 
-  The potential of slab is mainly contributed by the stars within the Galactic center.
+  where $\rho_{\text{atmp}}^{\text{peak}}$ can be obtained by assuming that pressure\
+  and gravitational potential are continuous at the interface ($z=\pm z_{0}$) between disk and atmosphere.
 
@@
 
-  We use three components (1) cold ISM disk (2) hot gas ambient (3) stellar disk\
-  to locally mimic the environment near the GC (i.e. no galactic rotation).\
+  The adopted parameters for are
 
-  The density distributions of ISM disk and hot gas ambient are derived from\
-  hydrostatic equilibrium within the fixed external potential.
+  %We use three components (1) cold ISM disk (2) hot gas ambient (3) stellar disk\
+  %to locally mimic the environment near the GC (i.e. no galactic rotation).\
 
-  We use the potential of isothermal slab, symmetric about $z=0$, and\
-  supported by gas pressure and by its own self-gravity,\
-  to mimic the realistic potential of Galactic bulge.
+  %The density distributions of ISM disk and hot gas ambient are derived from\
+  %hydrostatic equilibrium within the fixed external potential.
+
+  %We use the potential of isothermal slab, symmetric about $z=0$, and\
+  %supported by gas pressure and by its own self-gravity,\
+  %to mimic the realistic potential of Galactic bulge.
 

### 2021-12-17 paper.tex
update

@@
   \begin{equation}
-    \Phi_{\text{total}} = \Phi_{\text{disk}} + \Phi_{\text{halo}},
+    \Phi_{\text{total}} = \Phi_{\text{bulge}} + \Phi_{\text{halo}},
   \end{equation}
@@
   \begin{equation}
-    \Phi_{\text{disk}}=\
-    2\sigma^2_{\text{disk}}\
-    \ln\cosh\left(z\sqrt{\frac{2\pi G\rho_{\text{disk}}^{\text{peak}}}{\sigma^2_{\text{disk}}}}\right),
+    \Phi_{\text{bulge}}=\
+    2\sigma^2_{\text{bulge}}\
+    \ln\cosh\left(z\sqrt{\frac{2\pi G\rho_{\text{bulge}}^{\text{peak}}}{\sigma^2_{\text{bulge}}}}\right)
   \end{equation}
 
-  is the potential of a plane-parallel isothermal slab contributed by stars within the Galactic plane.
+  is the potential of a plane-parallel isothermal slab mainly contributed by stars within the Galactic plane.
 
   The steady-state density distribution in a total potential, $\Phi_{\text{total}}$,\
-  for the atmosphere gas can be derived from the isothermal and hydrostatic equilibrium condition,\
+  for the gas can be derived from the isothermal and hydrostatic equilibrium condition,\
   given by
@@
      \begin{cases}
+     \displaystyle\rho_{\text{bulge}}^{\text{peak}}
+     \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{bulge}}/m}\right] & \text{, if $|z| < z_{0}$,}\\
      \displaystyle\rho_{\text{atmp}}^{\text{peak}}
-     \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{atmp}}/m}\right] & \text{if z > $z_{0}$}\\
-     \displaystyle\rho_{\text{disk}}^{\text{peak}}
-     \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{disk}}/m}\right] & \text{if z > $z_{0}$}
+     \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{atmp}}/m}\right] & \text{, otherwise.}
      \end{cases}
   \end{equation}
+
+  where $\rho_{\text{bulge}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the mass density\
+  of the bulge and the atmosphere at the $z=0$ plane.
 
@@
   %to mimic the realistic potential of Galactic bulge.
+
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+\begin{table*}[t]
+\begin{tabular}{@{}llc@{}}
+\toprule
+Parameter                           & Description                   & Value                         \\ \midrule
+Potential \& halo                   &                               &                               \\
+$\sigma_{\text{bulge}}$             & Velocity dispersion of bulge  & 100 km/s                      \\
+$\rho_{\text{bulge}}^{\text{peak}}$ & Peak average density of bulge & $4\times 10^{-24}$ g/cm$^{3}$ \\
+$v_{\text{halo}}$                   &                               & 131.5 km/s                    \\
+$d_{\text{h}}$                      &                               & 12 kpc                        \\
+Atmosphere                          &                               &                               \\
+$T_{\text{\text{atmp}}}$            &                               & $10^{6}$ K                    \\
+Disk                                &                               &                               \\
+$z_{0}$                             & Scale height of disk          & 100 pc                        \\
+$\rho_{\text{disk}}^{\text{peak}}$  & Peak number density of disk   & $6\text{ c.c.}^{-1}$          \\
+$T_{\text{\text{disk}}}$            & Temperature of disk           & $10^{3}$ K                    \\ \bottomrule
+\end{tabular}
+\end{table*}
 

### 2021-12-17 paper.tex
update

@@
 \usepackage{ae,aecompl}
+\usepackage{xcolor,colortbl}
 \usepackage{tikz}
@@
 }
+
+\definecolor{Gray}{gray}{0.85}
 
@@
 \begin{table*}[t]
-\begin{tabular}{@{}llc@{}}
-\toprule
-Parameter                           & Description                   & Value                         \\ \midrule
-Potential \& halo                   &                               &                               \\
-$\sigma_{\text{bulge}}$             & Velocity dispersion of bulge  & 100 km/s                      \\
-$\rho_{\text{bulge}}^{\text{peak}}$ & Peak average density of bulge & $4\times 10^{-24}$ g/cm$^{3}$ \\
-$v_{\text{halo}}$                   &                               & 131.5 km/s                    \\
-$d_{\text{h}}$                      &                               & 12 kpc                        \\
-Atmosphere                          &                               &                               \\
-$T_{\text{\text{atmp}}}$            &                               & $10^{6}$ K                    \\
-Disk                                &                               &                               \\
-$z_{0}$                             & Scale height of disk          & 100 pc                        \\
-$\rho_{\text{disk}}^{\text{peak}}$  & Peak number density of disk   & $6\text{ c.c.}^{-1}$          \\
-$T_{\text{\text{disk}}}$            & Temperature of disk           & $10^{3}$ K                    \\ \bottomrule
+\centering
+\caption{Parameters of the disk, atmosphere, and gravitational potential in the simulation.}
+\label{table-parameters}
+\begin{tabular}{@{}llrr@{}}
+\toprule[1pt]\midrule[0.3pt]
+Parameter                           & Description                   & Value                                & Reference                         \\ \midrule
+{\bf Potential \& halo}             &                               &                                      &                                   \\ \cmidrule(r){1-1}
+$\sigma_{\text{bulge}}$             & Velocity dispersion of bulge  & 100 km/s                             & \citep{velocity-dispersion-MW}    \\
+$\rho_{\text{bulge}}^{\text{peak}}$ & Peak average density of bulge & $4\times 10^{-24}$ g/cm$^{3}$        &                                   \\
+$v_{\text{halo}}$                   &                               & 131.5 km/s                           & \citep{Johnston1995}              \\
+$d_{\text{h}}$                      &                               & 12 kpc                               & \citep{Johnston1995}              \\
+{\bf Atmosphere}                    &                               &                                      &                                   \\ \cmidrule(r){1-1}
+$T_{\text{\text{atmp}}}$            &                               & $10^{6}$ K                           & \citep{temperature-MW}            \\
+{\bf Disk}                          &                               &                                      &                                   \\ \cmidrule(r){1-1}
+$z_{0}$                             & Scale height of disk          & 100 pc                               &                                   \\
+		$\rho_{\text{disk}}^{\text{peak}}$  & Peak number density of disk   & $6\text{ c.c.}^{-1}$ & \citep{peak-ism-density}          \\
+$T_{\text{\text{disk}}}$            & Temperature of disk           & $10^{3}$ K                           &                                   \\ \midrule
 \end{tabular}
@@
   \begin{enumerate}
-    \item Dimension: $14\times14\times0.2$ kpc. i.e. Scale height, $z_{0}=100$ pc. \citep{paek-ism-density}
-    \item Peak mass density: $\rho_{\text{disk}}^{\text{peak}}=10^{-23}$ g/cm$^3$. \citep{paek-ism-density}
-    \item Average temperature: $T_{\text{disk}}=10^{3}$ K. \citep{paek-ism-density}
+    \item Dimension: $14\times14\times0.2$ kpc. i.e. Scale height, $z_{0}=100$ pc. \citep{peak-ism-density}
+    \item Peak mass density: $\rho_{\text{disk}}^{\text{peak}}=10^{-23}$ g/cm$^3$. \citep{peak-ism-density}
+    \item Average temperature: $T_{\text{disk}}=10^{3}$ K. \citep{peak-ism-density}
     \item Average mass density:

### 2021-12-17 paper.tex
update

@@
      \begin{cases}
-     \displaystyle\rho_{\text{bulge}}^{\text{peak}}
-     \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{bulge}}/m}\right] & \text{, if $|z| < z_{0}$,}\\
+     \displaystyle\rho_{\text{disk}}^{\text{peak}}
+     \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{disk}}/m}\right] & \text{, if $|z| < z_{0}$,}\\\\
      \displaystyle\rho_{\text{atmp}}^{\text{peak}}
@@
 
-  where $\rho_{\text{bulge}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the mass density\
+  where $\rho_{\text{disk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the mass density\
   of the bulge and the atmosphere at the $z=0$ plane.
@@
 {\bf Atmosphere}                    &                                   &                                      &                                   \\ \cmidrule(r){1-1}
-$T_{\text{\text{atmp}}}$            &                               & $10^{6}$ K                           & \citep{temperature-MW}            \\
+$T_{\text{\text{atmp}}}$            & Temperature of atmosphere         & $10^{6}$ K                           & \citep{temperature-MW}            \\
 {\bf Disk}                          &                                   &                                      &                                   \\ \cmidrule(r){1-1}
-$z_{0}$                             & Scale height of disk          & 100 pc                               &                                   \\
-		$\rho_{\text{disk}}^{\text{peak}}$  & Peak number density of disk   & $6\text{ c.c.}^{-1}$ & \citep{peak-ism-density}          \\
-$T_{\text{\text{disk}}}$            & Temperature of disk           & $10^{3}$ K                           &                                   \\ \midrule
+$z_{0}$                             & Scale height of disk              & 100 pc                               & \citep{peak-ism-density}          \\
+$T_{\text{\text{disk}}}$            & Temperature of disk               & $10^{3}$ K                           & \citep{peak-ism-density}          \\
+$\rho_{\text{disk}}^{\text{peak}}$  & Peak number density of disk       & $6\text{ c.c.}^{-1}$                 & \citep{peak-ism-density}          \\ \midrule
 \end{tabular}

### 2021-12-17 paper.tex
update

@@
 Parameter                           & Description                       & Value                                & Reference                         \\ \midrule
-{\bf Potential \& halo}             &                                   &                                      &                                   \\ \cmidrule(r){1-1}
+{\bf Potential \& halo}             &                                   &                                      &                                   \\
 $\sigma_{\text{bulge}}$             & Velocity dispersion of bulge      & 100 km/s                             & \citep{velocity-dispersion-MW}    \\
@@
 $v_{\text{halo}}$                   &                                   & 131.5 km/s                           & \citep{Johnston1995}              \\
-$d_{\text{h}}$                      &                                   & 12 kpc                               & \citep{Johnston1995}              \\
-{\bf Atmosphere}                    &                                   &                                      &                                   \\ \cmidrule(r){1-1}
-$T_{\text{\text{atmp}}}$            & Temperature of atmosphere         & $10^{6}$ K                           & \citep{temperature-MW}            \\
-{\bf Disk}                          &                                   &                                      &                                   \\ \cmidrule(r){1-1}
+$d_{\text{h}}$                      &                                   & 12 kpc                               & \citep{Johnston1995}              \\ \hline
+{\bf Atmosphere}                    &                                   &                                      &                                   \\
+$T_{\text{\text{atmp}}}$            & Temperature of atmosphere         & $10^{6}$ K                           & \citep{temperature-MW}            \\ \hline
+{\bf Disk}                          &                                   &                                      &                                   \\
 $z_{0}$                             & Scale height of disk              & 100 pc                               & \citep{peak-ism-density}          \\

### 2021-12-17 paper.tex
update

@@
   given by
-
   \begin{equation}
@@
      \displaystyle\rho_{\text{disk}}^{\text{peak}}
-     \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{disk}}/m}\right] & \text{, if $|z| < z_{0}$,}\\\\
+     \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{disk}}/m}\right] & \text{, if $|z| < z_{0}$}\\
+     \\
      \displaystyle\rho_{\text{atmp}}^{\text{peak}}
@@
   where $\rho_{\text{disk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the mass density\
-  of the bulge and the atmosphere at the $z=0$ plane.
+  of the bulge and atmosphere on the $z=0$ plane.
 
@@
 $v_{\text{halo}}$                   &                                   & 131.5 km/s                           & \citep{Johnston1995}              \\
-$d_{\text{h}}$                      &                                   & 12 kpc                               & \citep{Johnston1995}              \\ \hline
+$d_{\text{h}}$                      & Core radius                       & 12 kpc                               & \citep{Johnston1995}              \\ \hline
 {\bf Atmosphere}                    &                                   &                                      &                                   \\
@@
 $T_{\text{\text{disk}}}$            & Temperature of disk               & $10^{3}$ K                           & \citep{peak-ism-density}          \\
-$\rho_{\text{disk}}^{\text{peak}}$  & Peak number density of disk       & $6\text{ c.c.}^{-1}$                 & \citep{peak-ism-density}          \\ \midrule
+$\rho_{\text{disk}}^{\text{peak}}$  & Peak mass density of disk         & $10^{-23}$ g/cm$^{3}$                & \citep{peak-ism-density}          \\ \midrule
 \end{tabular}

### 2021-12-18 paper.tex
update

@@
 \begin{document}
-\title{Fermi and eROSITA bubbles}
+\title{Fermi and eROSITA bubbles: a proof of concept study}
 
@@
 
-  We model the external gravity of the Milky Way by prescribing a\
-  plane parallel self-gravitating isothermal slab, symmetry about the mid-plane $z=0$,\
+  As a proof-of-concept study, we approximate conventionally axisymmetric potential of Milky Way\
+  by a plane-parallel potential that is symmetric about the mid-plane $z=0$\
   in a simulation box size of\
@@
 
-  In our 3D simulation, the Galactic potential can be written as
+  The plane-parallel potential is fixed throughout our simulations and given by
 
@@
 
-  where $\Phi_{\text{halo}}=v^2_{\text{halo}}\ln\left(z^2+d^2_{\text{h}}\right)$\
-  is dark logarithmic halo potential,
+  where
 
@@
 
-  is the potential of a plane-parallel isothermal slab mainly contributed by stars within the Galactic plane.
+  is the potential of a isothermal slab mainly contributed by stars within the Galactic plane.
 
-  The steady-state density distribution in a total potential, $\Phi_{\text{total}}$,\
-  for the gas can be derived from the isothermal and hydrostatic equilibrium condition,\
-  given by
+  $\Phi_{\text{halo}}=v^2_{\text{halo}}\ln\left(z^2+d^2_{\text{h}}\right)$\
+  is a plane-parallel dark logarithmic halo potential.
+
+  With the help of the isothermal and hydrostatic equilibrium conditions,\
+  the steady-state gaseous density distribution in a total potential, $\Phi_{\text{total}}$,\
+  can be written as
   \begin{equation}
@@
 
-  where $\rho_{\text{atmp}}^{\text{peak}}$ can be obtained by assuming that pressure\
-  and gravitational potential are continuous at the interface ($z=\pm z_{0}$) between disk and atmosphere.
+  All parameters are listed in \Cref{table-parameters}, excpet for $\rho_{\text{atmp}}^{\text{peak}}$ that\
+  can be derived from the pressure equilibrium on the interfaces ($|z|=z_{0}$) between disk and atmosphere.
 
@@
 Parameter                           & Description                       & Value                                & Reference                         \\ \midrule
+{\bf Disk}                          &                                   &                                      &                                   \\
+$z_{0}$                             & Scale height of disk              & 100 pc                               & \citep{peak-ism-density}          \\
+$T_{\text{\text{disk}}}$            & Temperature of disk               & $10^{3}$ K                           & \citep{peak-ism-density}          \\
+$\rho_{\text{disk}}^{\text{peak}}$  & Peak mass density of disk         & $10^{-23}$ g/cm$^{3}$                & \citep{peak-ism-density}          \\ \hline
+{\bf Atmosphere}                    &                                   &                                      &                                   \\
+$T_{\text{\text{atmp}}}$            & Temperature of atmosphere         & $10^{6}$ K                           & \citep{temperature-MW}            \\ \hline
 {\bf Potential \& halo}             &                                   &                                      &                                   \\
@@
 $v_{\text{halo}}$                   &                                   & 131.5 km/s                           & \citep{Johnston1995}              \\
-$d_{\text{h}}$                      & Core radius                       & 12 kpc                               & \citep{Johnston1995}              \\ \hline
-{\bf Atmosphere}                    &                                   &                                      &                                   \\
-$T_{\text{\text{atmp}}}$            & Temperature of atmosphere         & $10^{6}$ K                           & \citep{temperature-MW}            \\ \hline
-{\bf Disk}                          &                                   &                                      &                                   \\
-$z_{0}$                             & Scale height of disk              & 100 pc                               & \citep{peak-ism-density}          \\
-$T_{\text{\text{disk}}}$            & Temperature of disk               & $10^{3}$ K                           & \citep{peak-ism-density}          \\
-$\rho_{\text{disk}}^{\text{peak}}$  & Peak mass density of disk         & $10^{-23}$ g/cm$^{3}$                & \citep{peak-ism-density}          \\ \midrule
+$d_{\text{h}}$                      & Core radius                       & 12 kpc                               & \citep{Johnston1995}              \\ \midrule
 \end{tabular}

### 2021-12-19 paper.tex
update

@@
   \begin{subequations}
-    \label{conservative-form}
+    \label{governing-eq}
     \begin{align}
@@
 
-  The set of equations is closed by using the Taub-Mathews equation of state (\citealt{Taub}; \citealt{TM_EOS})\
+  The set of \Cref{governing-eq} is closed by using the Taub-Mathews equation of state (\citealt{Taub}; \citealt{TM_EOS})\
   that approximates the exact EoS \citep{Synge} for ultra-relativistically\
@@
   \subsection{The Galactic Model}
-
-  As a proof-of-concept study, we approximate conventionally axisymmetric potential of Milky Way\
-  by a plane-parallel potential that is symmetric about the mid-plane $z=0$\
+  As a proof-of-concept study, we approximate conventionally axisymmetric stellar potential of Milky Way\
+  by an external plane-parallel potential that is symmetric about the mid-plane $z=0$\
   in a simulation box size of\
@@
   The plane-parallel potential is fixed throughout our simulations and given by
-
   \begin{equation}
-    \Phi_{\text{total}} = \Phi_{\text{bulge}} + \Phi_{\text{halo}},
+    \Phi_{\text{total}}(z) = \Phi_{\text{bulge}}(z) + \Phi_{\text{halo}}(z),
   \end{equation}
-
   where
-
   \begin{equation}
-    \Phi_{\text{bulge}}=\
+    \Phi_{\text{bulge}}(z)=\
     2\sigma^2_{\text{bulge}}\
@@
   \end{equation}
-
-  is the potential of a isothermal slab mainly contributed by stars within the Galactic plane.
-
-  $\Phi_{\text{halo}}=v^2_{\text{halo}}\ln\left(z^2+d^2_{\text{h}}\right)$\
+  is the potential of an isothermal slab mainly contributed by stars around the Galactic plane, and\
+  $\Phi_{\text{halo}}(z)=v^2_{\text{halo}}\ln\left(z^2+d^2_{\text{h}}\right)$\
   is a plane-parallel dark logarithmic halo potential.
@@
   With the help of the isothermal and hydrostatic equilibrium conditions,\
-  the steady-state gaseous density distribution in a total potential, $\Phi_{\text{total}}$,\
+  the steady-state gaseous density distribution of disk and atmosphere\
+  confined in the total potential, $\Phi_{\text{total}}$,\
   can be written as
@@
      \displaystyle\rho_{\text{disk}}^{\text{peak}}
-     \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{disk}}/m}\right] & \text{, if $|z| < z_{0}$}\\
+     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{disk}}/m_{\text{p}}}\right] & \text{, if $|z| < z_{0}$}\\
      \\
      \displaystyle\rho_{\text{atmp}}^{\text{peak}}
-     \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{atmp}}/m}\right] & \text{, otherwise.}
+     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{atmp}}/m_{\text{p}}}\right] & \text{, otherwise,}
      \end{cases}
   \end{equation}
-
-  where $\rho_{\text{disk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the mass density\
-  of the bulge and atmosphere on the $z=0$ plane.
+  where $m_{\text{p}}$ is a proton mass,\
+  $T_{\text{disk}}$ and $T_{\text{atmp}}$ is the temperature of the disk and the atmosphere,\
+  $\rho_{\text{disk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the peak mass density\
+  of the bulge and atmosphere on the mid-plane $z=0$.
 
   All parameters are listed in \Cref{table-parameters}, excpet for $\rho_{\text{atmp}}^{\text{peak}}$ that\
-  can be derived from the pressure equilibrium on the interfaces ($|z|=z_{0}$) between disk and atmosphere.
+  can be derived from the known parameters and pressure equilibrium\
+  on the interfaces $(z=\pm z_{0})$ between disk and atmosphere.
 
@@
 Parameter                                             & Description                   & Value                          & Reference                       \\ \midrule
-{\bf Disk}                          &                                   &                                      &                                   \\
-$z_{0}$                             & Scale height of disk              & 100 pc                               & \citep{peak-ism-density}          \\
-$T_{\text{\text{disk}}}$            & Temperature of disk               & $10^{3}$ K                           & \citep{peak-ism-density}          \\
-$\rho_{\text{disk}}^{\text{peak}}$  & Peak mass density of disk         & $10^{-23}$ g/cm$^{3}$                & \citep{peak-ism-density}          \\ \hline
-{\bf Atmosphere}                    &                                   &                                      &                                   \\
-$T_{\text{\text{atmp}}}$            & Temperature of atmosphere         & $10^{6}$ K                           & \citep{temperature-MW}            \\ \hline
-{\bf Potential \& halo}             &                                   &                                      &                                   \\
+{\bf Disk }\citep{peak-ism-density}                   &                               &                                &                                 \\
+$z_{0}$                                               & Scale height of disk          & 100 pc                         &                                 \\
+$T_{\text{\text{disk}}}$                              & Temperature of disk           & $10^{3}$ K                     &                                 \\
+$\rho_{\text{disk}}^{\text{peak}}$                    & Peak mass density of disk     & $10^{-23}$ g/cm$^{3}$          &                                 \\ \hline
+{\bf Atmosphere }\citep{temperature-MW}               &                               &                                &                                 \\
+$T_{\text{\text{atmp}}}$                              & Temperature of atmosphere     & $10^{6}$ K                     &                                 \\ \hline
+{\bf Static stellar potential }                       &                               &                                &                                 \\
 $\sigma_{\text{bulge}}$                               & Velocity dispersion of bulge  & 100 km/s                       & \citep{velocity-dispersion-MW}  \\
-$\rho_{\text{bulge}}^{\text{peak}}$ & Peak average density of bulge     & $4\times 10^{-24}$ g/cm$^{3}$        &                                   \\
-$v_{\text{halo}}$                   &                                   & 131.5 km/s                           & \citep{Johnston1995}              \\
-$d_{\text{h}}$                      & Core radius                       & 12 kpc                               & \citep{Johnston1995}              \\ \midrule
+$\rho_{\text{bulge}}^{\text{peak}}$                   & Peak average density of bulge & $4\times 10^{-24}$ g/cm$^{3}$  &                                 \\ \hline
+{\bf Static dark halo potential }\citep{Johnston1995} &                               &                                &                                 \\
+$v_{\text{halo}}$                                     &                               & 131.5 km/s                     &                                 \\
+$d_{\text{h}}$                                        & Core radius                   & 12 kpc                         &                                 \\ \midrule
 \end{tabular}

### 2021-12-19 paper.tex
update

@@
 \begin{document}
-\title{Fermi and eROSITA bubbles: a proof of concept study}
+\title{Fermi and eROSITA bubbles: A proof-of-concept study}
 
@@
   With the help of the isothermal and hydrostatic equilibrium conditions,\
-  the steady-state gaseous density distribution of disk and atmosphere\
-  confined in the total potential, $\Phi_{\text{total}}$,\
-  can be written as
+  we can write the steady-state gaseous density distributions of disk and atmosphere\
+  that are in pressure equilibrium and\
+  confined in the total potential, $\Phi_{\text{total}}$, as\
   \begin{equation}
@@
   $\rho_{\text{disk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the peak mass density\
-  of the bulge and atmosphere on the mid-plane $z=0$.
+  of the disk and atmosphere on the mid-plane $z=0$.
 
-  All parameters are listed in \Cref{table-parameters}, excpet for $\rho_{\text{atmp}}^{\text{peak}}$ that\
-  can be derived from the known parameters and pressure equilibrium\
+  All parameters are listed in \Cref{table-parameters}, except for $\rho_{\text{atmp}}^{\text{peak}}$ that\
+  can be derived from the known parameters and pressure equilibrium condition\
   on the interfaces $(z=\pm z_{0})$ between disk and atmosphere.

### 2021-12-19 paper.tex
update

@@
 
-  \subsection{The Galactic Model}
+  \subsection{The Galactic and Disk Models}
   As a proof-of-concept study, we approximate conventionally axisymmetric stellar potential of Milky Way\
@@
   With the help of the isothermal and hydrostatic equilibrium conditions,\
-  we can write the steady-state gaseous density distributions of disk and atmosphere\
+  we can write the steady-state gaseous density distributions of disk and the Galactic atmosphere\
   that are in pressure equilibrium and\
@@
 
+  \Cref{density-profile} shows the initial density profile of hot halo for the simulation presented here.\
+
+  \begin{figure*}[h]
+    \subfigure[The initial gaseous density profile along z-axis] % caption
+    {
+      \includegraphics[width=0.4\linewidth]{figures/fig__density-profile.png}
+      \label{density-profile}
+    }
+  \caption{Captions}
+  \end{figure*}
+
   The AMR base level is covered by $16\times16\times32$ root grids, refined progressively on the plane $z=0$\
@@
 
-  confined by an external dark halo potential.
+  \subsubsection{The clumpy, and warm/cold ISM disk}
 
-  The adopted parameters for are
-
-  %We use three components (1) cold ISM disk (2) hot gas ambient (3) stellar disk\
-  %to locally mimic the environment near the GC (i.e. no galactic rotation).\
-
-  %The density distributions of ISM disk and hot gas ambient are derived from\
-  %hydrostatic equilibrium within the fixed external potential.
-
-  %We use the potential of isothermal slab, symmetric about $z=0$, and\
-  %supported by gas pressure and by its own self-gravity,\
-  %to mimic the realistic potential of Galactic bulge.
+  A crucial ingredient in the simulations is the clumpy ISM disk,\
+  in which the temperature ranging from
 

### 2021-12-19 paper.tex
update

@@
   \end{equation}
-  is the potential of an isothermal slab mainly contributed by stars around the Galactic plane, and\
+  is the potential of an isothermal slab mainly contributed by stars around the Galactic bulge, and\
   $\Phi_{\text{halo}}(z)=v^2_{\text{halo}}\ln\left(z^2+d^2_{\text{h}}\right)$\
@@
   With the help of the isothermal and hydrostatic equilibrium conditions,\
+  and assuming the disk and atmosphere is in pressure equilibrium,\
   we can write the steady-state gaseous density distributions of disk and the Galactic atmosphere\
-  that are in pressure equilibrium and\
   confined in the total potential, $\Phi_{\text{total}}$, as\
@@
 
-  All parameters are listed in \Cref{table-parameters}, except for $\rho_{\text{atmp}}^{\text{peak}}$ that\
+  We tabulate all parameters in \Cref{table-parameters}, except for $\rho_{\text{atmp}}^{\text{peak}}$ that\
   can be derived from the known parameters and pressure equilibrium condition\
-  on the interfaces $(z=\pm z_{0})$ between disk and atmosphere.
+  on the interfaces $(z=\pm z_{0})$ between disk and atmosphere.\
 
-  \Cref{density-profile} shows the initial density profile of hot halo for the simulation presented here.\
+  The initial density profile based on the above construction is shown in \Cref{density-profile}\
+  and compared to the observed result beyond 1 kpc \citep{Miller_2013}.\
+
+  Note that there is an difficulty in disentangling the contribution\
+  of the Local Bubble, a supernova remnant in which the Solar System is embedded \citep{Snowden1990},\
+  and the contribution from solar wind charge-exchange processes, which produce soft\
+  X-ray emission throughout the Solar System. As a result, the density profile of the Galactic halo remains unclear\
+  \citep{BlandHawthorn2016}.
 
@@
 Parameter                                             & Description                   & Value                          & Reference                       \\ \midrule
-{\bf Disk }\citep{peak-ism-density}                   &                               &                                &                                 \\
+{\bf ISM Disk }\citep{peak-ism-density}                   &                               &                                &                                 \\
 $z_{0}$                                               & Scale height of disk          & 100 pc                         &                                 \\

### 2021-12-19 paper.tex
update

@@
 \begin{document}
-\title{Fermi and eROSITA bubbles: A proof-of-concept study}
+\title{The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study}
 
@@
   and assuming the disk and atmosphere is in pressure equilibrium,\
-  we can write the steady-state gaseous density distributions of disk and the Galactic atmosphere\
-  confined in the total potential, $\Phi_{\text{total}}$, as\
+  we can write the steady-state gaseous density distributions,\
+  confined in the total potential, of disk and the Galactic atmosphere as\
   \begin{equation}

### 2021-12-19 paper.tex
update

@@
   $\rho_{\text{disk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the peak mass density\
-  of the disk and atmosphere on the mid-plane $z=0$.
+  of the disk and the atmosphere on the mid-plane $z=0$.
 

### 2021-12-19 paper.tex
update

@@
 
-  A crucial ingredient in the simulations is the clumpy ISM disk,\
-  in which the temperature ranging from
+  A crucial ingredient in our work is the clumpy ISM disk initialized by\
+  the publicly available pyFC code
+  \footnote{\url{https://pypi.python.org/pypi/pyFC}}.
+  The spatial density distribution $\rho(\bold{x})$ of clumpy ISM obeys\
+  the log-normal probability distribution in real space,\
+  and the Kolmogorov power spectrum in the Fourier space.
+  \begin{equation}
+    D(k)=\int k^{2} \hat{\rho}(k)\hat{\rho}^{*}(k)dk \propto k^{-5/3},
+  \end{equation}
+  where $\hat{\rho}(k)$ is the Fourier transform of $\rho(\bold{r})$.
+
+  \citet{LA2002} and \citet{Wagner2012} have outlined a detailed procedure\
+   for constructing clumpy structure, and we do not repeat here.
 

### 2021-12-19 paper.tex
update

@@
   significantly reducing numerical error caused by catastrophic cancellations\
-  that commonly occur within the regions with high Mach number. e.g., jet-ISM interaction zones.
+  that commonly occur within the regions with high Mach number flows. e.g., jet-ISM interaction zones.
 
@@
   The initial density profile based on the above construction is shown in \Cref{density-profile}\
-  and compared to the observed result beyond 1 kpc \citep{Miller_2013}.\
+  and compared to the observed result \citep{Miller_2013} beyond 1 kpc.\
 
@@
   \end{equation}
-  where $\hat{\rho}(k)$ is the Fourier transform of $\rho(\bold{r})$.
+  where $\hat{\rho}(k)$ is the Fourier transform of $\rho(\bold{x})$.
 

### 2021-12-21 paper.tex
update

@@
   \end{equation}
-  where $m_{\text{p}}$ is a proton mass,\
+  where $m_{\text{p}}$ is the proton mass,\
   $T_{\text{disk}}$ and $T_{\text{atmp}}$ is the temperature of the disk and the atmosphere,\
@@
   The spatial density distribution $\rho(\bold{x})$ of clumpy ISM obeys\
-  the log-normal probability distribution in real space,\
-  and the Kolmogorov power spectrum in the Fourier space.
+  the log-normal probability distribution \citep{Berkhuijsen2008} with mean $\mu=1.3$ and dispersion $\sigma=0.13$ in real space,\
+  and the power-law Kolmogorov spectrum
   \begin{equation}
@@
   \end{equation}
-  where $\hat{\rho}(k)$ is the Fourier transform of $\rho(\bold{x})$.
+  where $\hat{\rho}(k)$ is the Fourier transform of $\rho(\bold{x})$.\
+  The spectrum $D(k)$ with index $-5/3$ in the Fourier space has the cutoff wave number $k_{\text{min}}=375.0$,\
+  corresponding to the average clump sizes of $\sim 20$ pc.
 

### 2021-12-21 paper.tex
update

@@
 
-  A crucial ingredient in our work is the clumpy ISM disk initialized by\
+  A crucial component in our work is the clumpy ISM disk initialized by\
   the publicly available pyFC code
@@
   The spatial density distribution $\rho(\bold{x})$ of clumpy ISM obeys\
-  the log-normal probability distribution \citep{Berkhuijsen2008} with mean $\mu=1.3$ and dispersion $\sigma=0.13$ in real space,\
+  the log-normal probability distribution \citep{Berkhuijsen2008} with mean $\mu=1.3$ and dispersion $\sigma=0.13$,\
   and the power-law Kolmogorov spectrum
@@
   where $\hat{\rho}(k)$ is the Fourier transform of $\rho(\bold{x})$.\
-  The spectrum $D(k)$ with index $-5/3$ in the Fourier space has the cutoff wave number $k_{\text{min}}=375.0$,\
+  The spectrum $D(k)$ with index $-5/3$ in the Fourier space has a cutoff wave number $k_{\text{min}}=375.0$,\
   corresponding to the average clump sizes of $\sim 20$ pc.

### 2021-12-22 paper.tex
update

@@
 
-  \citet{LA2002} and \citet{Wagner2012} have outlined a detailed procedure\
-   for constructing clumpy structure, and we do not repeat here.
+  The reader is referred to \citet{LA2002} and \citet{Wagner2012} for further details of this method.
+
+  The temperature in each cell of the warm gas distribution is determined by pressure equilibrium with hot gas.\
+  When the warm gas temperature exceeds $T_{\text{crit}}=$ K, it is deemed to be thermally unstable and is replaced\
+  by hot gas. This makes the gas porous.
 
@@
 \label{table-parameters}
-\begin{tabular}{@{}llrr@{}}
+\begin{tabular}{@{}llrc@{}}
 \toprule[1pt]\midrule[0.3pt]
 Parameter                                             & Description                               & Value                                & Reference                       \\ \midrule
-{\bf ISM Disk }\citep{peak-ism-density}               &                               &                                &                                 \\
-$z_{0}$                                               & Scale height of disk          & 100 pc                         &                                 \\
-$T_{\text{\text{disk}}}$                              & Temperature of disk           & $10^{3}$ K                     &                                 \\
-$\rho_{\text{disk}}^{\text{peak}}$                    & Peak mass density of disk     & $10^{-23}$ g/cm$^{3}$          &                                 \\ \hline
-{\bf Atmosphere }\citep{temperature-MW}               &                               &                                &                                 \\
-$T_{\text{\text{atmp}}}$                              & Temperature of atmosphere     & $10^{6}$ K                     &                                 \\ \hline
+{\bf ISM Disk }                                       &                                           &                                      &                                 \\
+$z_{0}$                                               & Scale height of disk                      & 100 pc                               & \citet{peak-ism-density}        \\
+$T_{\text{\text{disk}}}$                              & Temperature of disk                       & $10^{3}$ K                           & \multicolumn{1}{c}{''}          \\
+$\rho_{\text{disk}}^{\text{peak}}$                    & Peak mass density of disk                 & $10^{-23}$ g$\cdot$cm$^{-3}$         & \multicolumn{1}{c}{''}          \\
+$T_{\text{\text{c}}}$                                 & Critical temperature of warm atomic phase & $3\times 10^{4}$ K                   & \multicolumn{1}{c}{''}          \\
+$k_{\text{min}}$                                      & Cutoff wave number                        & 375.0                                & \multicolumn{1}{c}{''}          \\
+$\mu$                                                 & Mean of number density                    & 1.3 $\text{cm}^{-3}$                 & \citet{Wagner2012}              \\
+$\sigma^2$                                            & Variance of number density                & 5.0 $\text{cm}^{-6}$                 & \multicolumn{1}{c}{''}          \\
+$\beta$                                               & Power law index                           & -5/3                                 & \multicolumn{1}{c}{''}          \\ \hline
+{\bf Atmosphere }                                     &                                           &                                      &                                 \\
+$T_{\text{\text{atmp}}}$                              & Temperature of atmosphere                 & $10^{6}$ K                           & \citet{temperature-MW}          \\ \hline
 {\bf Static stellar potential }                       &                                           &                                      &                                 \\
-$\sigma_{\text{bulge}}$                               & Velocity dispersion of bulge  & 100 km/s                       & \citep{velocity-dispersion-MW}  \\
-$\rho_{\text{bulge}}^{\text{peak}}$                   & Peak average density of bulge & $4\times 10^{-24}$ g/cm$^{3}$  &                                 \\ \hline
-{\bf Static dark halo potential }\citep{Johnston1995} &                               &                                &                                 \\
-$v_{\text{halo}}$                                     &                               & 131.5 km/s                     &                                 \\
-$d_{\text{h}}$                                        & Core radius                   & 12 kpc                         &                                 \\ \midrule
+$\sigma_{\text{bulge}}$                               & Velocity dispersion of bulge              & 100 km$\cdot$s$^{-1}$                & \citet{velocity-dispersion-MW}  \\
+$\rho_{\text{bulge}}^{\text{peak}}$                   & Peak average density of bulge             & $4\times 10^{-24}$ g$\cdot$cm$^{-3}$ &                                 \\ \hline
+{\bf Static dark halo potential }                     &                                           &                                      &                                 \\
+$v_{\text{halo}}$                                     &                                           & 131.5 km$\cdot$s$^{-1}$              & \citet{Johnston1995}            \\
+$d_{\text{h}}$                                        & Core radius                               & 12 kpc                               & \multicolumn{1}{c}{''}          \\ \midrule
 \end{tabular}

### 2021-12-22 paper.tex
update

@@
 $\mu$                                                 & Mean of number density                    & 1.3 $\text{cm}^{-3}$                 & \citet{Wagner2012}              \\
-$\sigma^2$                                            & Variance of number density                & 5.0 $\text{cm}^{-6}$                 & \multicolumn{1}{c}{''}          \\
+$\sigma$                                              & Dispersion of number density              & 1.7 $\text{cm}^{-3}$                 & \multicolumn{1}{c}{''}          \\
 $\beta$                                               & Power law index                           & -5/3                                 & \multicolumn{1}{c}{''}          \\ \hline

### 2021-12-22 paper.tex
update

@@
   The spatial density distribution $\rho(\bold{x})$ of clumpy ISM obeys\
-  the log-normal probability distribution \citep{Berkhuijsen2008} with mean $\mu=1.3$ and dispersion $\sigma=0.13$,\
+  the log-normal probability distribution \citep{Berkhuijsen2008} with mean $\mu$ and dispersion $\sigma$,\
   and the power-law Kolmogorov spectrum
   \begin{equation}
-    D(k)=\int k^{2} \hat{\rho}(k)\hat{\rho}^{*}(k)dk \propto k^{-5/3},
+    D(k)=\int k^{2} \hat{\rho}(k)\hat{\rho}^{*}(k)dk \propto k^{-\beta},
   \end{equation}
   where $\hat{\rho}(k)$ is the Fourier transform of $\rho(\bold{x})$.\
-  The spectrum $D(k)$ with index $-5/3$ in the Fourier space has a cutoff wave number $k_{\text{min}}=375.0$,\
-  corresponding to the average clump sizes of $\sim 20$ pc.
+  The spectrum $D(k)$ with a power law index $\beta$ in the Fourier space has a cutoff wave number $k_{\text{min}}=375.0$,\
+  corresponding to the average clump sizes of $\sim 20$ pc.\
+  \Cref{table-parameters} presents the parameters of clumpy disk.
 

### 2021-12-22 paper.tex
update

@@
   The spatial density distribution $\rho(\bold{x})$ of clumpy ISM obeys\
-  the log-normal probability distribution \citep{Berkhuijsen2008} with mean $\mu$ and dispersion $\sigma$,\
+  the log-normal probability distribution with mean $\mu$ and dispersion $\sigma$,\
+  %the log-normal probability distribution \citep{Berkhuijsen2008} with mean $\mu$ and dispersion $\sigma$,\
   and the power-law Kolmogorov spectrum
@@
   corresponding to the average clump sizes of $\sim 20$ pc.\
-  \Cref{table-parameters} presents the parameters of clumpy disk.
+  \Cref{table-parameters} presents the parameters of clumpy disk and their references.
 
-  The reader is referred to \citet{LA2002} and \citet{Wagner2012} for further details of this method.
+  %The reader is referred to \citet{LA2002} and \citet{Wagner2012} for further details of this method.
+  \citet{LA2002} and \citet{Wagner2012} have outlined a detailed procedure\
+  for constructing clumpy structure, and we do not repeat here.
 

### 2021-12-22 paper.tex
update

@@
 $k_{\text{min}}$                                      & Cutoff wave number                        & 375.0                                & \multicolumn{1}{c}{''}          \\
-$\mu$                                                 & Mean of number density                    & 1.3 $\text{cm}^{-3}$                 & \citet{Wagner2012}              \\
+$\mu$                                                 & Mean of number density                    & 1.0 $\text{cm}^{-3}$                 & \citet{Wagner2012}              \\
 $\sigma$                                              & Dispersion of number density              & 1.7 $\text{cm}^{-3}$                 & \multicolumn{1}{c}{''}          \\

### 2021-12-22 paper.tex
update

@@
   where $\hat{\rho}(k)$ is the Fourier transform of $\rho(\bold{x})$.\
-  The spectrum $D(k)$ with a power law index $\beta$ in the Fourier space has a cutoff wave number $k_{\text{min}}=375.0$,\
-  corresponding to the average clump sizes of $\sim 20$ pc.\
+  The spectrum $D(k)$ in the Fourier space is characterized by the power law index $\beta$,\
+  the Nyquist limit $k_{\text{max}}$, and the lower cutoff wave number $k_{\text{min}}$.
+  $k_{\text{max}}$ is one-half of the cell numbers along the edge of the simulation box,\
+  and $k_{\text{min}}$ is set to 375.0, corresponding to the maximum size of an individual cloud $\sim 20$ pc.\
   \Cref{table-parameters} presents the parameters of clumpy disk and their references.

### 2021-12-23 paper.tex
update

--- 2021-12-22 paper.tex
@@
   With the help of the isothermal and hydrostatic equilibrium conditions,\
-  and assuming the disk and atmosphere is in pressure equilibrium,\
+  and assuming the isothermal disk and atmosphere is in pressure equilibrium,\
   we can write the steady-state gaseous density distributions,\
-  confined in the total potential, of disk and the Galactic atmosphere as\
-  \begin{equation}
-     \rho(z)=
-     \begin{cases}
-     \displaystyle\rho_{\text{disk}}^{\text{peak}}
-     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{disk}}/m_{\text{p}}}\right] & \text{, if $|z| < z_{0}$}\\
-     \\
-     \displaystyle\rho_{\text{atmp}}^{\text{peak}}
-     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{atmp}}/m_{\text{p}}}\right] & \text{, otherwise,}
-     \end{cases}
-  \end{equation}
+  confined in the total potential, of the disk and the Galactic atmosphere as\
+  \begin{subequations}
+  \begin{align}
+     \displaystyle \rho_{\text{isoDisk}}(z) = \rho_{\text{isoDisk}}^{\text{peak}}
+     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{isoDisk}}/m_{\text{p}}}\right]&\label{isothermal-disk-density}\\
+     \text{, if $|z| < z_{0}$}& \nonumber \\
+     \nonumber\\
+     \displaystyle \rho_{\text{atmp}}(z) = \rho_{\text{atmp}}^{\text{peak}}
+     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{atmp}}/m_{\text{p}}}\right]&\label{isothermal-atmp-density}\\
+     \text{, otherwise,}& \nonumber
+  \end{align}
+  \label{disk-atm-sys}
+  \end{subequations}
   where $m_{\text{p}}$ is the proton mass,\
-  $T_{\text{disk}}$ and $T_{\text{atmp}}$ is the temperature of the disk and the atmosphere,\
-  $\rho_{\text{disk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the peak mass density\
-  of the disk and the atmosphere on the mid-plane $z=0$.
+  $T_{\text{isoDisk}}$ and $T_{\text{atmp}}$ is the temperature of the isothermal disk and atmosphere,\
+  $\rho_{\text{isoDisk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the peak mass density\
+  of the disk and atmosphere on the mid-plane $z=0$.
 
-  We tabulate all parameters in \Cref{table-parameters}, except for $\rho_{\text{atmp}}^{\text{peak}}$ that\
+  We tabulate parameters in the \textbf{Isothermal disk} and \textbf{Atmosphere}\
+  categories in \Cref{table-parameters},\
+  except for $\rho_{\text{atmp}}^{\text{peak}}$ that\
   can be derived from the known parameters and pressure equilibrium condition\
-  on the interfaces $(z=\pm z_{0})$ between disk and atmosphere.\
+  on the interfaces $(z=\pm z_{0})$ between the disk and atmosphere.\
 
-  The initial density profile based on the above construction is shown in \Cref{density-profile}\
+  The initial density profile of \Cref{disk-atm-sys} is shown in \Cref{density-profile}\
   and compared to the observed result \citep{Miller_2013} beyond 1 kpc.\
@@
   \footnote{\url{https://pypi.python.org/pypi/pyFC}}.
-  The spatial density distribution $\rho(\bold{x})$ of clumpy ISM obeys\
-  the log-normal probability distribution with mean $\mu$ and dispersion $\sigma$,\
-  %the log-normal probability distribution \citep{Berkhuijsen2008} with mean $\mu$ and dispersion $\sigma$,\
+  The spatial density distribution $\rho_{\text{clumpy}}(\bold{x})$ of clumpy disk obeys\
+  the log-normal probability distribution\
+  %the log-normal probability distribution \citep{Berkhuijsen2008}\
+  with mean $\mu_{\text{clumpy}}$ and dispersion $\sigma_{\text{clumpy}}$,\
   and the power-law Kolmogorov spectrum
@@
     D(k)=\int k^{2} \hat{\rho}(k)\hat{\rho}^{*}(k)dk \propto k^{-\beta},
+    \label{Kolmogorov-spectrum}
   \end{equation}
-  where $\hat{\rho}(k)$ is the Fourier transform of $\rho(\bold{x})$.\
-  The spectrum $D(k)$ with a power law index $\beta$ in the Fourier space has a cutoff wave number $k_{\text{min}}=375.0$,\
-  corresponding to the average clump sizes of $\sim 20$ pc.\
-  \Cref{table-parameters} presents the parameters of clumpy disk and their references.
+  where $\hat{\rho}(k)$ is the Fourier transform of $\rho_{\text{clumpy}}(\bold{x})$.\
+  The spectrum $D(k)$ in the Fourier space is characterized by the power law index $\beta$,\
+  the Nyquist limit $k_{\text{max}}$, and the lower cutoff wave number $k_{\text{min}}$.
+  $k_{\text{max}}$ is one-half of the spatial resolution within disk,\
+  and $k_{\text{min}}$ is 375.0, corresponding to the maximum size of an individual cloud $\sim 20$ pc.\
+
+  The temperature in each cell of the clumpy disk is determined by $p_{\text{disk}}$
+
+  We summarize the parameters of clumpy disk and their references in \Cref{table-parameters}.
 
@@
   by hot gas. This makes the gas porous.
+
+  \begin{enumerate}
+     \item Constructing the isothermal disk $\rho_{\text{isoDisk}}(\bold{x})$ by \Cref{isothermal-disk-density}.
+     \item Using PyFC code to obtain the clumpy cuboid $\rho_{\text{clumpy}}$ obeying\
+           lognormal distribution and the power-law spectrum, \Cref{Kolmogorov-spectrum}.
+     \item $\rho_{\text{ismDisk}}(\bf{x}) = \rho_{\text{clumpy}}(\bf{x}) \times \rho_{\text{isoDisk}}(\bf{x})$.
+     \item
+  \end{enumerate}
 
@@
 Parameter                                             & Description                               & Value                                & Reference                       \\ \midrule
-{\bf ISM Disk }                                       &                                           &                                      &                                 \\
+{\bf Isothermal disk }                                &                                           &                                      &                                 \\
 $z_{0}$                                               & Scale height of disk                      & 100 pc                               & \citet{peak-ism-density}        \\
-$T_{\text{\text{disk}}}$                              & Temperature of disk                       & $10^{3}$ K                           & \multicolumn{1}{c}{''}          \\
-$\rho_{\text{disk}}^{\text{peak}}$                    & Peak mass density of disk                 & $10^{-23}$ g$\cdot$cm$^{-3}$         & \multicolumn{1}{c}{''}          \\
+$T_{\text{\text{isoDisk}}}$                           & Temperature of disk                       & $10^{3}$ K                           & \multicolumn{1}{c}{''}          \\
+$\rho_{\text{isoDisk}}^{\text{peak}}$                 & Peak mass density of disk                 & $10^{-23}$ g$\cdot$cm$^{-3}$         & \multicolumn{1}{c}{''}          \\ \hline
+{\bf Atmosphere }                                     &                                           &                                      &                                 \\
+$T_{\text{\text{atmp}}}$                              & Temperature of atmosphere                 & $10^{6}$ K                           & \citet{temperature-MW}          \\ \hline
+{\bf Clumpy disk }                                    &                                           &                                      &                                 \\
 $T_{\text{\text{c}}}$                                 & Critical temperature of warm atomic phase & $3\times 10^{4}$ K                   & \multicolumn{1}{c}{''}          \\
 $k_{\text{min}}$                                      & Cutoff wave number                        & 375.0                                & \multicolumn{1}{c}{''}          \\
-$\mu$                                                 & Mean of number density                    & 1.0 $\text{cm}^{-3}$                 & \citet{Wagner2012}              \\
-$\sigma$                                              & Dispersion of number density              & 1.7 $\text{cm}^{-3}$                 & \multicolumn{1}{c}{''}          \\
+$\mu_{\text{clumpy}}$                                 & Mean of number density                    & 1.0 $\text{cm}^{-3}$                 & \citet{Wagner2012}              \\
+$\sigma_{\text{clumpy}}$                              & Dispersion of number density              & 1.7 $\text{cm}^{-3}$                 & \multicolumn{1}{c}{''}          \\
 $\beta$                                               & Power law index                           & -5/3                                 & \multicolumn{1}{c}{''}          \\ \hline
-{\bf Atmosphere }                                     &                                           &                                      &                                 \\
-$T_{\text{\text{atmp}}}$                              & Temperature of atmosphere                 & $10^{6}$ K                           & \citet{temperature-MW}          \\ \hline
 {\bf Static stellar potential }                       &                                           &                                      &                                 \\

### 2021-12-23 paper.tex
update

@@
 \toprule[1pt]\midrule[0.3pt]
-Parameter                                             & Description                               & Value                                & Reference                       \\ \midrule
-{\bf Isothermal disk }                                &                                           &                                      &                                 \\
-$z_{0}$                                               & Scale height of disk                      & 100 pc                               & \citet{peak-ism-density}        \\
-$T_{\text{\text{isoDisk}}}$                           & Temperature of disk                       & $10^{3}$ K                           & \multicolumn{1}{c}{''}          \\
-$\rho_{\text{isoDisk}}^{\text{peak}}$                 & Peak mass density of disk                 & $10^{-23}$ g$\cdot$cm$^{-3}$         & \multicolumn{1}{c}{''}          \\ \hline
-{\bf Atmosphere }                                     &                                           &                                      &                                 \\
-$T_{\text{\text{atmp}}}$                              & Temperature of atmosphere                 & $10^{6}$ K                           & \citet{temperature-MW}          \\ \hline
-{\bf Clumpy disk }                                    &                                           &                                      &                                 \\
-$T_{\text{\text{c}}}$                                 & Critical temperature of warm atomic phase & $3\times 10^{4}$ K                   & \multicolumn{1}{c}{''}          \\
-$k_{\text{min}}$                                      & Cutoff wave number                        & 375.0                                & \multicolumn{1}{c}{''}          \\
-$\mu_{\text{clumpy}}$                                 & Mean of number density                    & 1.0 $\text{cm}^{-3}$                 & \citet{Wagner2012}              \\
-$\sigma_{\text{clumpy}}$                              & Dispersion of number density              & 1.7 $\text{cm}^{-3}$                 & \multicolumn{1}{c}{''}          \\
-$\beta$                                               & Power law index                           & -5/3                                 & \multicolumn{1}{c}{''}          \\ \hline
-{\bf Static stellar potential }                       &                                           &                                      &                                 \\
-$\sigma_{\text{bulge}}$                               & Velocity dispersion of bulge              & 100 km$\cdot$s$^{-1}$                & \citet{velocity-dispersion-MW}  \\
-$\rho_{\text{bulge}}^{\text{peak}}$                   & Peak average density of bulge             & $4\times 10^{-24}$ g$\cdot$cm$^{-3}$ &                                 \\ \hline
-{\bf Static dark halo potential }                     &                                           &                                      &                                 \\
-$v_{\text{halo}}$                                     &                                           & 131.5 km$\cdot$s$^{-1}$              & \citet{Johnston1995}            \\
-$d_{\text{h}}$                                        & Core radius                               & 12 kpc                               & \multicolumn{1}{c}{''}          \\ \midrule
+Parameter                                                    & Description                               & Value                                \\ \midrule
+{\bf Isothermal disk }\citep{peak-ism-density}               &                                           &                                      \\
+$z_{0}$                                                      & Scale height of disk                      & 100 pc                               \\
+$T_{\text{\text{isoDisk}}}$                                  & Temperature of disk                       & $10^{3}$ K                           \\
+$\rho_{\text{isoDisk}}^{\text{peak}}$                        & Peak mass density of disk                 & $10^{-23}$ g$\cdot$cm$^{-3}$         \\ \hline
+{\bf Atmosphere }\citep{temperature-MW}                      &                                           &                                      \\
+$T_{\text{\text{atmp}}}$                                     & Temperature of atmosphere                 & $10^{6}$ K                           \\
+{\bf Clumpy disk }\citep{Wagner2012}                         &                                           &                                      \\
+$T_{\text{\text{c}}}$                                        & Critical temperature of warm atomic phase & $3\times 10^{4}$ K                   \\
+$k_{\text{min}}$                                             & Cutoff wave number                        & 375.0                                \\
+$\mu_{\text{clumpy}}$                                        & Mean of number density                    & 1.0 $\text{cm}^{-3}$                 \\
+$\sigma_{\text{clumpy}}$                                     & Dispersion of number density              & 1.7 $\text{cm}^{-3}$                 \\
+$\beta$                                                      & Power law index                           & -5/3                                 \\ \hline
+{\bf Static stellar potential }\citep{velocity-dispersion-MW}&                                           &                                      \\
+$\sigma_{\text{bulge}}$                                      & Velocity dispersion of bulge              & 100 km$\cdot$s$^{-1}$                \\
+$\rho_{\text{bulge}}^{\text{peak}}$                          & Peak average density of bulge             & $4\times 10^{-24}$ g$\cdot$cm$^{-3}$ \\ \hline
+{\bf Static dark halo potential }\citep{Johnston1995}        &                                           &                                      \\
+$v_{\text{halo}}$                                            &                                           & 131.5 km$\cdot$s$^{-1}$              \\
+$d_{\text{h}}$                                               & Core radius                               & 12 kpc                               \\ \midrule
 \end{tabular}

### 2021-12-23 paper.tex
update

@@
 {\bf Atmosphere }\citep{temperature-MW}                      &                                           &                                      \\
-$T_{\text{\text{atmp}}}$                                     & Temperature of atmosphere                 & $10^{6}$ K                           \\
+$T_{\text{\text{atmp}}}$                                     & Temperature of atmosphere                 & $10^{6}$ K                           \\ \hline
 {\bf Clumpy disk }\citep{Wagner2012}                         &                                           &                                      \\

### 2021-12-23 paper.tex
update

--- 2021-12-23 paper.tex
@@
 Parameter                                                    & Description                               & Value                                \\ \midrule
+{\bf Static stellar potential }\citep{velocity-dispersion-MW}&                                           &                                      \\
+$\sigma_{\text{bulge}}$                                      & Velocity dispersion of bulge              & 100 km$\cdot$s$^{-1}$                \\
+$\rho_{\text{bulge}}^{\text{peak}}$                          & Peak average density of bulge             & $4\times 10^{-24}$ g$\cdot$cm$^{-3}$ \\ \hline
+{\bf Static dark halo potential }\citep{Johnston1995}        &                                           &                                      \\
+$v_{\text{halo}}$                                            &                                           & 131.5 km$\cdot$s$^{-1}$              \\
+$d_{\text{h}}$                                               & Core radius                               & 12 kpc                               \\ \hline
 {\bf Isothermal disk }\citep{peak-ism-density}               &                                           &                                      \\
@@
 $\sigma_{\text{clumpy}}$                                     & Dispersion of number density              & 1.7 $\text{cm}^{-3}$                 \\
-$\beta$                                                      & Power law index                           & -5/3                                 \\ \hline
-{\bf Static stellar potential }\citep{velocity-dispersion-MW}&                                           &                                      \\
-$\sigma_{\text{bulge}}$                                      & Velocity dispersion of bulge              & 100 km$\cdot$s$^{-1}$                \\
-$\rho_{\text{bulge}}^{\text{peak}}$                          & Peak average density of bulge             & $4\times 10^{-24}$ g$\cdot$cm$^{-3}$ \\ \hline
-{\bf Static dark halo potential }\citep{Johnston1995}        &                                           &                                      \\
-$v_{\text{halo}}$                                            &                                           & 131.5 km$\cdot$s$^{-1}$              \\
-$d_{\text{h}}$                                               & Core radius                               & 12 kpc                               \\ \midrule
+$\beta$                                                      & Power law index                           & -5/3                                 \\ \midrule
 \end{tabular}

### 2021-12-23 paper.tex
update

@@
 
-  We tabulate parameters in the \textbf{Isothermal disk} and \textbf{Atmosphere}\
+  We tabulate parameters in the first four\
   categories in \Cref{table-parameters},\
@@
            lognormal distribution and the power-law spectrum, \Cref{Kolmogorov-spectrum}.
-     \item $\rho_{\text{ismDisk}}(\bf{x}) = \rho_{\text{clumpy}}(\bf{x}) \times \rho_{\text{isoDisk}}(\bf{x})$.
+     \item $\rho_{\text{ismDisk}}(\bf{x}) = \rho_{\text{clumpy}}(\bf{x}) \rho_{\text{isoDisk}}(\bf{x})$.
      \item

### 2021-12-23 paper.tex
update

@@
   We tabulate parameters in the first four\
-  categories in \Cref{table-parameters},\
+  categories of \Cref{table-parameters},\
   except for $\rho_{\text{atmp}}^{\text{peak}}$ that\

### 2021-12-23 paper.tex
update

@@
   With the help of the isothermal and hydrostatic equilibrium conditions,\
-  and assuming the isothermal disk and atmosphere is in pressure equilibrium,\
+  and assuming the interface between isothermal disk and atmosphere is in pressure equilibrium,\
   we can write the steady-state gaseous density distributions,\
@@
   \footnote{\url{https://pypi.python.org/pypi/pyFC}}.
-  The spatial density distribution $\rho_{\text{clumpy}}(\bold{x})$ of clumpy disk obeys\
+  First, pyFC create a dimensionless 3D scalar field $f_{\text{clumpy}}(\bold{x})$ that is clumpy but obeys\
   the log-normal probability distribution\
@@
   with mean $\mu_{\text{clumpy}}$ and dispersion $\sigma_{\text{clumpy}}$,\
-  and the power-law Kolmogorov spectrum
+  and follows the power-law Kolmogorov spectrum
   \begin{equation}
-    D(k)=\int k^{2} \hat{\rho}(k)\hat{\rho}^{*}(k)dk \propto k^{-\beta},
+    D(\bold{k})=\int k^{2} \hat{f}(\bold{k})\hat{f}^{*}(\bold{k})d\Omega \propto k^{-\beta},
     \label{Kolmogorov-spectrum}
   \end{equation}
-  where $\hat{\rho}(k)$ is the Fourier transform of $\rho_{\text{clumpy}}(\bold{x})$.\
-  The spectrum $D(k)$ in the Fourier space is characterized by the power law index $\beta$,\
+  where $\hat{f}(\bold{k})$ is the Fourier transform of $f_{\text{clumpy}}(\bold{x})$.\
+  The spectrum $D(\bold{k})$ in the Fourier space is characterized by the power law index $\beta$,\
   the Nyquist limit $k_{\text{max}}$, and the lower cutoff wave number $k_{\text{min}}$.
   $k_{\text{max}}$ is one-half of the spatial resolution within disk,\
-  and $k_{\text{min}}$ is 375.0, corresponding to the maximum size of an individual cloud $\sim 20$ pc.\
+  and $k_{\text{min}}$ is 375.0, corresponding to the maximum size of an individual clump $\sim 20$ pc.\
 
@@
      \item Constructing the isothermal disk $\rho_{\text{isoDisk}}(\bold{x})$ by \Cref{isothermal-disk-density}.
-     \item Using PyFC code to obtain the clumpy cuboid $\rho_{\text{clumpy}}$ obeying\
+     \item Using PyFC code to obtain a dimensionless clumpy distribution $f_{\text{clumpy}}$ obeying\
            lognormal distribution and the power-law spectrum, \Cref{Kolmogorov-spectrum}.
-     \item $\rho_{\text{ismDisk}}(\bf{x}) = \rho_{\text{clumpy}}(\bf{x}) \rho_{\text{isoDisk}}(\bf{x})$.
+     \item $\rho_{\text{ismDisk}}(\bf{x}) = f_{\text{clumpy}}(\bf{x}) \rho_{\text{isoDisk}}(\bf{x})$.
      \item
@@
 $\mu_{\text{clumpy}}$                                        & Mean of number density                    & 1.0 $\text{cm}^{-3}$                 \\
-$\sigma_{\text{clumpy}}$                                     & Dispersion of number density              & 1.7 $\text{cm}^{-3}$                 \\
+$\sigma_{\text{clumpy}}$                                     & Dispersion of number density              & 1.7 $\text{cm}^{-3}$                 \\ % RELATIVISTIC JET FEEDBACK IN EVOLVING GALAXIES Wagner (2011)
 $\beta$                                                      & Power law index                           & -5/3                                 \\ \midrule

### 2021-12-23 paper.tex
update

@@
   \footnote{\url{https://pypi.python.org/pypi/pyFC}}.
-  First, pyFC create a dimensionless 3D scalar field $f_{\text{clumpy}}(\bold{x})$ that is clumpy but obeys\
-  the log-normal probability distribution\
+  The pyFC randomly generates dimensionless 3D scalar field $f_{\text{clumpy}}(\bold{x})$ that is clumpy and porous.
+  The random scalar field obeys the log-normal probability distribution\
   %the log-normal probability distribution \citep{Berkhuijsen2008}\
@@
   where $\hat{f}(\bold{k})$ is the Fourier transform of $f_{\text{clumpy}}(\bold{x})$.\
-  The spectrum $D(\bold{k})$ in the Fourier space is characterized by the power law index $\beta$,\
+  The spectrum $D(\bold{k})$ in the Fourier space is characterized by the power law index $\beta=5/3$,\
   the Nyquist limit $k_{\text{max}}$, and the lower cutoff wave number $k_{\text{min}}$.
@@
 
-  The temperature in each cell of the clumpy disk is determined by $p_{\text{disk}}$
-
   We summarize the parameters of clumpy disk and their references in \Cref{table-parameters}.
-
-  %The reader is referred to \citet{LA2002} and \citet{Wagner2012} for further details of this method.
   \citet{LA2002} and \citet{Wagner2012} have outlined a detailed procedure\
@@
 
-  The temperature in each cell of the warm gas distribution is determined by pressure equilibrium with hot gas.\
+  Finally, we multiply $f_{\text{clumpy}}(\bold{x})$ and $\rho_{\text{isoDisk}}(z)$\
+  to obtain the density of ISM disk $\rho_{\text{ismDisk}}(\bold{x})$. i.e.\
+  $\displaystyle\rho_{\text{ismDisk}}(\bold{x}) =\
+  f_{\text{clumpy}}(\bold{x}) \rho_{\text{isoDisk}}(z)$.
+
+  The temperature in each cell of the disk is determined by pressure equilibrium with hot gas.\
+
   When the warm gas temperature exceeds $T_{\text{crit}}=$ K, it is deemed to be thermally unstable and is replaced\
@@
 
-  \begin{enumerate}
-     \item Constructing the isothermal disk $\rho_{\text{isoDisk}}(\bold{x})$ by \Cref{isothermal-disk-density}.
-     \item Using PyFC code to obtain a dimensionless clumpy distribution $f_{\text{clumpy}}$ obeying\
-           lognormal distribution and the power-law spectrum, \Cref{Kolmogorov-spectrum}.
-     \item $\rho_{\text{ismDisk}}(\bf{x}) = f_{\text{clumpy}}(\bf{x}) \rho_{\text{isoDisk}}(\bf{x})$.
-     \item
-  \end{enumerate}
+%  \begin{enumerate}
+%     \item Constructing the isothermal disk $\rho_{\text{isoDisk}}(z)$ by \Cref{isothermal-disk-density}.
+%     \item Using PyFC code to obtain a dimensionless clumpy distribution $f_{\text{clumpy}}$ obeying\
+%           lognormal distribution and the power-law spectrum, \Cref{Kolmogorov-spectrum}.
+%     \item \Cref{density-ism-disk}.
+%     \item
+%  \end{enumerate}
 
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
 \begin{table*}[t]
@@
 $k_{\text{min}}$                                             & Cutoff wave number                        & 375.0                                \\
-$\mu_{\text{clumpy}}$                                        & Mean of number density                    & 1.0 $\text{cm}^{-3}$                 \\
-$\sigma_{\text{clumpy}}$                                     & Dispersion of number density              & 1.7 $\text{cm}^{-3}$                 \\ % RELATIVISTIC JET FEEDBACK IN EVOLVING GALAXIES Wagner (2011)
+$\mu_{\text{clumpy}}$                                        & Mean of scalar field                      & 1.0                                  \\
+$\sigma_{\text{clumpy}}$                                     & Dispersion of scalar field                & 1.7                                  \\ % RELATIVISTIC JET FEEDBACK IN EVOLVING GALAXIES Wagner (2011)
 $\beta$                                                      & Power law index                           & -5/3                                 \\ \midrule

### 2021-12-24 paper.tex
update

@@
 
+   % The dispersion:
+   %   2010-Comparing the statistics of interstellar turbulence in simulations and observations
+   %   2011-RELATIVISTIC JET FEEDBACK IN EVOLVING GALAXIES
+
   A crucial component in our work is the clumpy ISM disk initialized by\
   the publicly available pyFC code
-  \footnote{\url{https://pypi.python.org/pypi/pyFC}}.
-  The pyFC randomly generates dimensionless 3D scalar field $f_{\text{clumpy}}(\bold{x})$ that is clumpy and porous.
-  The random scalar field obeys the log-normal probability distribution\
-  %the log-normal probability distribution \citep{Berkhuijsen2008}\
+  \footnote{\url{https://pypi.python.org/pypi/pyFC}}.\
+
+  The pyFC randomly generates dimensionless 3D scalar field $f_{\text{clumpy}}(\bold{x})$\ % that is clumpy and porous.
+  that obeys the log-normal probability distribution\
   with mean $\mu_{\text{clumpy}}$ and dispersion $\sigma_{\text{clumpy}}$,\
@@
 
-  We summarize the parameters of clumpy disk and their references in \Cref{table-parameters}.
-  \citet{LA2002} and \citet{Wagner2012} have outlined a detailed procedure\
-  for constructing clumpy structure, and we do not repeat here.
-
   Finally, we multiply $f_{\text{clumpy}}(\bold{x})$ and $\rho_{\text{isoDisk}}(z)$\
@@
   The temperature in each cell of the disk is determined by pressure equilibrium with hot gas.\
+
+  The porosity of the warm phase arises by imposing an upper temperature cutoff for the\
+  existence of clouds at $T_{\text{crit}} = 10^{4}$ K, beyond which clouds
+  are deemed thermally unstable.
+
+  We summarize the parameters of clumpy disk and their references in \Cref{table-parameters}.
+  \citet{LA2002} and \citet{Wagner2012} have outlined a detailed procedure\
+  for constructing clumpy structure, and we do not repeat here.
 
@@
 \begin{table*}[t]
-\centering
+\raggedright
 \caption{Parameters of the disk, atmosphere, and gravitational potential in the simulation.}
@@
 $d_{\text{h}}$                                               & Core radius                               & 12 kpc                               \\ \hline
+{\bf Atmosphere }\citep{temperature-MW}                      &                                           &                                      \\
+$T_{\text{\text{atmp}}}$                                     & Temperature of atmosphere                 & $10^{6}$ K                           \\ \hline
 {\bf Isothermal disk }\citep{peak-ism-density}               &                                           &                                      \\
@@
 $\rho_{\text{isoDisk}}^{\text{peak}}$                        & Peak mass density of disk                 & $10^{-23}$ g$\cdot$cm$^{-3}$         \\ \hline
-{\bf Atmosphere }\citep{temperature-MW}                      &                                           &                                      \\
-$T_{\text{\text{atmp}}}$                                     & Temperature of atmosphere                 & $10^{6}$ K                           \\ \hline
 {\bf Clumpy disk }\citep{Wagner2012}                         &                                           &                                      \\
 $T_{\text{\text{c}}}$                                        & Critical temperature of warm atomic phase & $3\times 10^{4}$ K                   \\
-$k_{\text{min}}$                                             & Cutoff wave number                        & 375.0                                \\
+$\dagger k_{\text{min}}$                                             & Cutoff wave number                        & 375.0                                \\
 $\mu_{\text{clumpy}}$                                        & Mean of scalar field                      & 1.0                                  \\
@@
 \end{tabular}
+\begin{tablenotes}
+      \raggedright
+      \small
+      \item  $\dagger k_{\text{min}}=375.0$ leads to the size of an individual clump $\sim 100$ pc.
+    \end{tablenotes}
 \end{table*}

### 2021-12-25 paper.tex
update

@@
 \toprule[1pt]\midrule[0.3pt]
-Parameter                                                    & Description                               & Value                                \\ \midrule
-{\bf Static stellar potential }\citep{velocity-dispersion-MW}&                                           &                                      \\
-$\sigma_{\text{bulge}}$                                      & Velocity dispersion of bulge              & 100 km$\cdot$s$^{-1}$                \\
-$\rho_{\text{bulge}}^{\text{peak}}$                          & Peak average density of bulge             & $4\times 10^{-24}$ g$\cdot$cm$^{-3}$ \\ \hline
-{\bf Static dark halo potential }\citep{Johnston1995}        &                                           &                                      \\
-$v_{\text{halo}}$                                            &                                           & 131.5 km$\cdot$s$^{-1}$              \\
-$d_{\text{h}}$                                               & Core radius                               & 12 kpc                               \\ \hline
-{\bf Atmosphere }\citep{temperature-MW}                      &                                           &                                      \\
-$T_{\text{\text{atmp}}}$                                     & Temperature of atmosphere                 & $10^{6}$ K                           \\ \hline
-{\bf Isothermal disk }\citep{peak-ism-density}               &                                           &                                      \\
-$z_{0}$                                                      & Scale height of disk                      & 100 pc                               \\
-$T_{\text{\text{isoDisk}}}$                                  & Temperature of disk                       & $10^{3}$ K                           \\
-$\rho_{\text{isoDisk}}^{\text{peak}}$                        & Peak mass density of disk                 & $10^{-23}$ g$\cdot$cm$^{-3}$         \\ \hline
-{\bf Clumpy disk }\citep{Wagner2012}                         &                                           &                                      \\
-$T_{\text{\text{c}}}$                                        & Critical temperature of warm atomic phase & $3\times 10^{4}$ K                   \\
-$\dagger k_{\text{min}}$                                             & Cutoff wave number                        & 375.0                                \\
-$\mu_{\text{clumpy}}$                                        & Mean of scalar field                      & 1.0                                  \\
-$\sigma_{\text{clumpy}}$                                     & Dispersion of scalar field                & 1.7                                  \\ % RELATIVISTIC JET FEEDBACK IN EVOLVING GALAXIES Wagner (2011)
-$\beta$                                                      & Power law index                           & -5/3                                 \\ \midrule
+Parameter                             & Description                               & Value                                &  Reference                     \\ \midrule
+{\bf Static stellar potential }       &                                           &                                      &                                \\
+$\sigma_{\text{bulge}}$               & Velocity dispersion of bulge              & 100 km$\cdot$s$^{-1}$                & \citep{velocity-dispersion-MW} \\
+$\rho_{\text{bulge}}^{\text{peak}}$   & Peak average density of bulge             & $4\times 10^{-24}$ g$\cdot$cm$^{-3}$ &   N/A                          \\ \hline
+{\bf Static dark halo potential }     &                                           &                                      &                                \\
+$v_{\text{halo}}$                     &                                           & 131.5 km$\cdot$s$^{-1}$              & \citep{Johnston1995}           \\
+$d_{\text{h}}$                        & Core radius                               & 12 kpc                               & \multicolumn{1}{c}{''}         \\ \hline
+{\bf Atmosphere }                     &                                           &                                      &                                \\
+$T_{\text{\text{atmp}}}$              & Temperature of atmosphere                 & $10^{6}$ K                           & \citep{temperature-MW}         \\ \hline
+{\bf Isothermal disk }                &                                           &                                      &                                \\
+$z_{0}$                               & Scale height of disk                      & 100 pc                               & \citep{peak-ism-density}       \\
+$T_{\text{\text{isoDisk}}}$           & Temperature of disk                       & $10^{3}$ K                           & \multicolumn{1}{c}{''}         \\
+$\rho_{\text{isoDisk}}^{\text{peak}}$ & Peak mass density of disk                 & $10^{-23}$ g$\cdot$cm$^{-3}$         & \multicolumn{1}{c}{''}         \\ \hline
+{\bf Clumpy disk }                    &                                           &                                      &                                \\
+$T_{\text{\text{c}}}$                 & Critical temperature of warm atomic phase & $10^{4}$ K                           & \citep{peak-ism-density}       \\
+$\dagger$  $k_{\text{min}}$           & Cutoff wave number                        & 375.0                                &   N/A                          \\
+$\mu_{\text{clumpy}}$                 & Mean of scalar field                      & 1.0                                  &   N/A                          \\
+$\ddag$  $\sigma_{\text{clumpy}}$     & Dispersion of scalar field                & 2.2                                  & \citep{Federrath2010}          \\
+$\beta$                               & Power law index                           & -5/3                                 &   N/A                          \\ \midrule
 \end{tabular}
@@
       \raggedright
-      \small
-      \item  $\dagger k_{\text{min}}=375.0$ leads to the size of an individual clump $\sim 100$ pc.
+      \item  $\dagger$  $k_{\text{min}}=375.0$ leads to the size of an individual clump $\sim 100$ pc.
+      \item    $\ddag$  $\sigma_{\text{clumpy}}=$ ....
     \end{tablenotes}

### 2021-12-26 paper.tex
update

@@
   As a proof-of-concept study, we approximate conventionally axisymmetric stellar potential of Milky Way\
-  by an external plane-parallel potential that is symmetric about the mid-plane $z=0$\
+  by an plane-parallel potential that is symmetric about the mid-plane $z=0$\
   in a simulation box size of\
@@
 
-  The pyFC randomly generates dimensionless 3D scalar field $f_{\text{clumpy}}(\bold{x})$\ % that is clumpy and porous.
+  pyFC randomly generates dimensionless 3D scalar field $f(\bold{x})$\ % that is clumpy and porous.
   that obeys the log-normal probability distribution\
-  with mean $\mu_{\text{clumpy}}$ and dispersion $\sigma_{\text{clumpy}}$,\
+  with mean $\mu$ and dispersion $\sigma$,\
   and follows the power-law Kolmogorov spectrum
@@
   \end{equation}
-  where $\hat{f}(\bold{k})$ is the Fourier transform of $f_{\text{clumpy}}(\bold{x})$.\
+  where $\hat{f}(\bold{k})$ is the Fourier transform of $f(\bold{x})$.\
   The spectrum $D(\bold{k})$ in the Fourier space is characterized by the power law index $\beta=5/3$,\
@@
 
-  Finally, we multiply $f_{\text{clumpy}}(\bold{x})$ and $\rho_{\text{isoDisk}}(z)$\
-  to obtain the density of ISM disk $\rho_{\text{ismDisk}}(\bold{x})$. i.e.\
-  $\displaystyle\rho_{\text{ismDisk}}(\bold{x}) =\
-  f_{\text{clumpy}}(\bold{x}) \rho_{\text{isoDisk}}(z)$.
+  \begin{enumerate}
+     \item  We multiply $f(\bold{x})$ and $\rho_{\text{isoDisk}}(z)$\
+            to obtain the density of disk $\tilde{\rho}_{\text{ismDisk}}(\bold{x})$. i.e.\
+            $\displaystyle\tilde{\rho}_{\text{ismDisk}}(\bold{x}) =\
+            f(\bold{x}) \rho_{\text{isoDisk}}(z)$.\
+            The temperature is determined by
+            $\displaystyle \tilde{T}_{\text{ismDisk}} = T_{\text{isoDisk}}\rho_{\text{isoDisk}}/\tilde{\rho}_{\text{ismDisk}}$.
+     \item  If $\tilde{T}_{\text{ismDisk}}$ larger than $T_{\text{crit}}$,
+  \end{enumerate}
 
-  The temperature in each cell of the disk is determined by pressure equilibrium with hot gas.\
+  The porosity of the disk arises by imposing an upper temperature cutoff for the\
+  existence of clouds at $T_{\text{crit}} = 10^{4}$ K, beyond which clouds
+  are deemed thermally unstable and replaced by temperature of atmosphere.
 
-  The porosity of the warm phase arises by imposing an upper temperature cutoff for the\
-  existence of clouds at $T_{\text{crit}} = 10^{4}$ K, beyond which clouds
-  are deemed thermally unstable.
+  The temperature in each cell within the disk is determined by pressure equilibrium with hot gas.\
+  The clouds within the disk are in pressure equilibrium with the surrounding hot voids, thus\
+  $\displaystyle T_{\text{ismDisk}} = T_{\text{isoDisk}}\rho_{\text{isoDisk}}/\rho_{\text{ismDisk}}$.
 
@@
 %     \item Constructing the isothermal disk $\rho_{\text{isoDisk}}(z)$ by \Cref{isothermal-disk-density}.
-%     \item Using PyFC code to obtain a dimensionless clumpy distribution $f_{\text{clumpy}}$ obeying\
+%     \item Using PyFC code to obtain a dimensionless clumpy distribution $f$ obeying\
 %           lognormal distribution and the power-law spectrum, \Cref{Kolmogorov-spectrum}.
@@
 $\dagger$  $k_{\text{min}}$           & Cutoff wave number                        & 375.0                                &   N/A                          \\
-$\mu_{\text{clumpy}}$                 & Mean of scalar field                      & 1.0                                  &   N/A                          \\
-$\ddag$  $\sigma_{\text{clumpy}}$     & Dispersion of scalar field                & 2.2                                  & \citep{Federrath2010}          \\
+$\mu$                                 & Mean of scalar field                      & 1.0                                  &   N/A                          \\
+$\ddag$  $\sigma$                     & Dispersion of scalar field                & 2.2                                  & \citep{Federrath2010}          \\
 $\beta$                               & Power law index                           & -5/3                                 &   N/A                          \\ \midrule
@@
       \item  $\dagger$  $k_{\text{min}}=375.0$ leads to the size of an individual clump $\sim 100$ pc.
-      \item    $\ddag$  $\sigma_{\text{clumpy}}=$ ....
+      \item    $\ddag$  $\sigma=$ ....
     \end{tablenotes}

### 2021-12-27 paper.tex
update

@@
 \section{Introduction}
+Early attempts to model the Fermi bubbles assumed that the jet is vertial to the Galactic plane...
 
@@
   including CR advection, and dynamical coupling between the thermal gas and CRs without CR diffusion\
-  turn out to be
+  can be written a succinct form as
 
@@
 
-  \begin{enumerate}
-     \item  We multiply $f(\bold{x})$ and $\rho_{\text{isoDisk}}(z)$\
-            to obtain the density of disk $\tilde{\rho}_{\text{ismDisk}}(\bold{x})$. i.e.\
-            $\displaystyle\tilde{\rho}_{\text{ismDisk}}(\bold{x}) =\
+  \citet{LA2002} and \citet{Wagner2012} have outlined a detailed procedure\
+  for constructing a clumpy scalar field, and we do not repeat here.
+
+  The density of clumpy disk can thus be obtained by taking the scalar products of\
+  $f(\bold{x})$ with $\rho_{\text{isoDisk}}(z)$ over all cells within the disk:\
+  $\displaystyle\rho_{\text{ismDisk}}(\bold{x}) =\
   f(\bold{x}) \rho_{\text{isoDisk}}(z)$.\
-            The temperature is determined by
-            $\displaystyle \tilde{T}_{\text{ismDisk}} = T_{\text{isoDisk}}\rho_{\text{isoDisk}}/\tilde{\rho}_{\text{ismDisk}}$.
-     \item  If $\tilde{T}_{\text{ismDisk}}$ larger than $T_{\text{crit}}$,
-  \end{enumerate}
+  Also, the pressure equilibrium condition implies that the temperature of disk is
+  $\displaystyle T_{\text{ismDisk}}(\bold{x}) =\
+  T_{\text{isoDisk}}(z)\rho_{\text{isoDisk}}(z)/\rho_{\text{ismDisk}}(\bold{x})$.
 
-  The porosity of the disk arises by imposing an upper temperature cutoff for the\
-  existence of clouds at $T_{\text{crit}} = 10^{4}$ K, beyond which clouds
-  are deemed thermally unstable and replaced by temperature of atmosphere.
+  Moreover, as the clouds are considered to be thermally unstable\
+  when the cloud temperature beyond\
+  the critical temperature of the warm atomic phase.\
+  We replace the cell density with\
+  $\rho_{\text{ismDisk}}T_{\text{ismDisk}}/T_{\text{atmp}}$\
+  for a cell temperature greater than the critical value $T_{\text{crit}}$.
 
-  The temperature in each cell within the disk is determined by pressure equilibrium with hot gas.\
-  The clouds within the disk are in pressure equilibrium with the surrounding hot voids, thus\
-  $\displaystyle T_{\text{ismDisk}} = T_{\text{isoDisk}}\rho_{\text{isoDisk}}/\rho_{\text{ismDisk}}$.
+  %Doing so, the porosity of the disk can arises,\
 
   We summarize the parameters of clumpy disk and their references in \Cref{table-parameters}.
-  \citet{LA2002} and \citet{Wagner2012} have outlined a detailed procedure\
-  for constructing clumpy structure, and we do not repeat here.
-
-  When the warm gas temperature exceeds $T_{\text{crit}}=$ K, it is deemed to be thermally unstable and is replaced\
-  by hot gas. This makes the gas porous.
-
-%  \begin{enumerate}
-%     \item Constructing the isothermal disk $\rho_{\text{isoDisk}}(z)$ by \Cref{isothermal-disk-density}.
-%     \item Using PyFC code to obtain a dimensionless clumpy distribution $f$ obeying\
-%           lognormal distribution and the power-law spectrum, \Cref{Kolmogorov-spectrum}.
-%     \item \Cref{density-ism-disk}.
-%     \item
-%  \end{enumerate}
 

### 2021-12-27 paper.tex
update

@@
 
-  The AMR base level is covered by $16\times16\times32$ root grids, refined progressively on the plane $z=0$\
-  , with the outflow boundary condition.
-
-  \subsubsection{The clumpy, and warm/cold ISM disk}
-
    % The dispersion:
@@
    %   2011-RELATIVISTIC JET FEEDBACK IN EVOLVING GALAXIES
+
+  \subsection{The Clumpy Multiphase Interstellar Medium}
 
@@
 
-  Moreover, as the clouds are considered to be thermally unstable\
-  when the cloud temperature beyond\
-  the critical temperature of the warm atomic phase.\
-  We replace the cell density with\
-  $\rho_{\text{ismDisk}}T_{\text{ismDisk}}/T_{\text{atmp}}$\
-  for a cell temperature greater than the critical value $T_{\text{crit}}$.
-
-  %Doing so, the porosity of the disk can arises,\
+%  Moreover, since the clouds are considered to be thermally unstable\
+%  when the cloud temperature beyond\
+%  the critical temperature of the warm atomic phase,\
+%  we replace the cell density as\
+%  $\rho_{\text{ismDisk}}T_{\text{ismDisk}}/T_{\text{atmp}}$\
+%  when the cell temperature beyond the critical value $T_{\text{crit}}$.
 
   We summarize the parameters of clumpy disk and their references in \Cref{table-parameters}.
+
+  The AMR base level is covered by $16\times16\times32$ root cells, refined progressively on the mid-plane $z=0$\
+  based on the gradient of mass desnity.\
+  The highest refinement level is 7 so that the clumps within the disk can be adequately\
+  resolved by approximately 30 cells along their diameter, 20 pc.
 
@@
 $T_{\text{\text{c}}}$                 & Critical temperature of warm atomic phase & $10^{4}$ K                           & \citep{peak-ism-density}       \\
-$\dagger$  $k_{\text{min}}$           & Cutoff wave number                        & 375.0                                &   N/A                          \\
+$\dagger$  $k_{\text{min}}$           & Cutoff wave number                        & 375.0                                & \multicolumn{1}{c}{''}         \\
 $\mu$                                 & Mean of scalar field                      & 1.0                                  &   N/A                          \\
-$\ddag$  $\sigma$                     & Dispersion of scalar field                & 2.2                                  & \citep{Federrath2010}          \\
+$\ddag$  $\sigma$                     & Dispersion of scalar field                & 5.0                                  & \citep{Federrath2010}          \\
 $\beta$                               & Power law index                           & -5/3                                 &   N/A                          \\ \midrule
@@
       \raggedright
-      \item  $\dagger$  $k_{\text{min}}=375.0$ leads to the size of an individual clump $\sim 100$ pc.
-      \item    $\ddag$  $\sigma=$ ....
+      \item  $\dagger$  $k_{\text{min}}=375.0$ leads to the size of an individual molecular cloud $\sim 100$ pc.
+      \item  $\ddag$ In numerical simulations of turbulence,\
+             \citet{Federrath2010} find $\sigma\sim 3.6$ and 35 for solenoidal (divergence-free) and compressive (curl-free) forcing,\
+             respectively, so that our adopted value of 5 is closer to their solenoidal result.
     \end{tablenotes}
@@
 \subsection{Cold disk}
-  We restrict the refinement level is 7 within the cold disk so that\
-  a molecular cloud can be adequately resolved by approximately 30 cells along their diameter, 100 pc.\
 

### 2021-12-27 paper.tex
update

@@
   As a proof-of-concept study, we approximate conventionally axisymmetric stellar potential of Milky Way\
-  by an plane-parallel potential that is symmetric about the mid-plane $z=0$\
+  by a plane-parallel potential that is symmetric about the mid-plane $z=0$\
   in a simulation box size of\
@@
   except for $\rho_{\text{atmp}}^{\text{peak}}$ that\
-  can be derived from the known parameters and pressure equilibrium condition\
+  can be derived from the other known parameters and pressure equilibrium condition\
   on the interfaces $(z=\pm z_{0})$ between the disk and atmosphere.\
@@
   and $k_{\text{min}}$ is 375.0, corresponding to the maximum size of an individual clump $\sim 20$ pc.\
-
   \citet{LA2002} and \citet{Wagner2012} have outlined a detailed procedure\
@@
 
-  We summarize the parameters of clumpy disk and their references in \Cref{table-parameters}.
+  \Cref{table-parameters} summarize the parameters of the clumpy disk and their references.
 
-  The AMR base level is covered by $16\times16\times32$ root cells, refined progressively on the mid-plane $z=0$\
-  based on the gradient of mass desnity.\
-  The highest refinement level is 7 so that the clumps within the disk can be adequately\
-  resolved by approximately 30 cells along their diameter, 20 pc.
+  On the basis of this setup, we cover the AMR base level with\
+  $16\times16\times32$ root cells, refined progressively on the mid-plane $z=0$\
+  based on the gradient of mass density.\
+  We also restrict the refinement level is 7 within the cold disk so that\
+  a molecular cloud can be adequately resolved by approximately 30 cells along their diameter, 20 pc.
 
@@
 
-\begin{enumerate}
-  \item Assumptions on gravity:
-    \begin{enumerate}
-      \item We use the potential of isothermal slab, symmetric about $z=0$ and\
-            supported by gas pressure and by under its own self-gravity,\
-            to mimic the realistic potential of Galactic bulge.
-      \item The ISM disk and atmosphere are subjected to the fixed external potential\
-            due to a disk bulge and dark matter halo.
-      \item In addition to the gravitational interaction, we ignore other interactions between stars and gases.
-      \item We also ignore the self-gravity of the ISM disk and of the atmosphere.
-      \item We ignore the centrifugal force of Milky Way rotation acting on the bubbles.
-      \item We use the potential of isothermal slab to mimic the gravitational potential due to the stellar bulge.
-      \item The interface between cold ISM disk and atmosphere is parallel to the Galactic plane and is pressure balanced.
-    \end{enumerate}
-\end{enumerate}
-
-\begin{enumerate}
-\item Fixed external gravitational potential:
-  \begin{enumerate}
-    \item Bulge potential:
-      \begin{enumerate}
-       \item Peak density: $\rho_{\text{bulge}}^{\text{peak}}=4\times 10^{-24}$ g/cm$^3$.
-       \item Potential (isothermal slab):
-         \begin{equation}
-           \Phi_{\text{bulge}}=\
-           2\sigma^2_{\text{bulge}}\
-           \ln\cosh\left(z\sqrt{\frac{2\pi G\rho_{\text{bulge}}^{\text{peak}}}{\sigma^2_{\text{bulge}}}}\right),
-         \end{equation}
-          where $\displaystyle \sigma_{\text{bulge}}=\
-                \sqrt{\frac{k_{B}T_{\text{bulge}}}{m}}=100$ km/s \citep{velocity-dispersion-MW}.
-      \end{enumerate}
-
-    \item Dark logarithmic halo potential:
-         \begin{equation}
-           \Phi_{\text{halo}}=v^2_{\text{halo}}\ln\left(z^2+d^2_{\text{h}}\right),
-         \end{equation}
-         where $v_{\text{halo}}=131.5$ km/s, $d_{\text{h}}=12$ kpc \citep{Yang2013}.
-
-    \item Total potential: $\Phi_{\text{total}}=\Phi_{\text{bulge}}+\Phi_{\text{halo}}$.
-  \end{enumerate}
-
-\item Clumpy cold disk:
-  \begin{enumerate}
-    \item Dimension: $14\times14\times0.2$ kpc. i.e. Scale height, $z_{0}=100$ pc. \citep{peak-ism-density}
-    \item Peak mass density: $\rho_{\text{disk}}^{\text{peak}}=10^{-23}$ g/cm$^3$. \citep{peak-ism-density}
-    \item Average temperature: $T_{\text{disk}}=10^{3}$ K. \citep{peak-ism-density}
-    \item Average mass density:
-          \begin{equation}
-             \rho_{\text{disk}}=\rho_{\text{disk}}^{\text{peak}}
-             \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{disk}}/m}\right].
-             \label{disk-density}
-          \end{equation}
-
-    \item Pressure: $\displaystyle p_{\text{disk}}=\rho_{\text{disk}}T_{\text{disk}}$.
-
-    \item The clumpy cuboid, using the publicly\
-          available pyFC code\footnote{\url{https://pypi.python.org/pypi/pyFC}},\
-          are described by a log-normal distribution with mean 1.0 and variance 5.0.\
-          Also, the power spectrum of the clumpy cuboid is characterized by $k_{\text{min}}$ and $\beta$,\
-          where $k_{\text{min}}$ sets the maximum cloud size within the clumpy cuboid,\
-          and $\beta$ is the slope of power spectrum in Fourier space.
-          In this paper, we set $\beta=-5/3$ and $k_{\text{min}}=375$ to follow the Kolmogorov spectrum\
-          and to limits the maximum size of an individual cloud to approximately 25 pc.
-
-    \item The clumpy disk is then constructed by multiplying a fractal cuboid with \Cref{disk-density}.
-
-    \item The clouds and voids within clumpy disk are pressure balanced.
-  \end{enumerate}
-
-\item Isothermal atmosphere:
-  \begin{enumerate}
-     \item The region outside the clumpy cold disk is atmosphere.
-     \item $T_{\text{atmp}}=10^{6}$ K. \citep{temperature-MW}
-     \item Density:
-          \begin{equation}
-             \rho_{\text{atmp}}=\rho_{\text{atmp}}^{\text{peak}}
-             \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{atmp}}/m}\right],
-             \label{atmosphere-density}
-          \end{equation}
-          where $\rho_{\text{atmp}}^{\text{peak}}$ can be obtained by assuming that pressure\
-          and gravitational potential are continuous at the interface ($z=\pm z_{0}$) between disk and atmosphere.
-  \end{enumerate}
-
-\end{enumerate}
-
-\subsection{Cold disk}
+%\begin{enumerate}
+%  \item Assumptions on gravity:
+%    \begin{enumerate}
+%      \item We use the potential of isothermal slab, symmetric about $z=0$ and\
+%            supported by gas pressure and by under its own self-gravity,\
+%            to mimic the realistic potential of Galactic bulge.
+%      \item The ISM disk and atmosphere are subjected to the fixed external potential\
+%            due to a disk bulge and dark matter halo.
+%      \item In addition to the gravitational interaction, we ignore other interactions between stars and gases.
+%      \item We also ignore the self-gravity of the ISM disk and of the atmosphere.
+%      \item We ignore the centrifugal force of Milky Way rotation acting on the bubbles.
+%      \item We use the potential of isothermal slab to mimic the gravitational potential due to the stellar bulge.
+%      \item The interface between cold ISM disk and atmosphere is parallel to the Galactic plane and is pressure balanced.
+%    \end{enumerate}
+%\end{enumerate}
+%
+%
+%
+%\begin{enumerate}
+%\item Fixed external gravitational potential:
+%  \begin{enumerate}
+%    \item Bulge potential:
+%      \begin{enumerate}
+%       \item Peak density: $\rho_{\text{bulge}}^{\text{peak}}=4\times 10^{-24}$ g/cm$^3$.
+%       \item Potential (isothermal slab):
+%         \begin{equation}
+%           \Phi_{\text{bulge}}=\
+%           2\sigma^2_{\text{bulge}}\
+%           \ln\cosh\left(z\sqrt{\frac{2\pi G\rho_{\text{bulge}}^{\text{peak}}}{\sigma^2_{\text{bulge}}}}\right),
+%         \end{equation}
+%          where $\displaystyle \sigma_{\text{bulge}}=\
+%                \sqrt{\frac{k_{B}T_{\text{bulge}}}{m}}=100$ km/s \citep{velocity-dispersion-MW}.
+%      \end{enumerate}
+%
+%    \item Dark logarithmic halo potential:
+%         \begin{equation}
+%           \Phi_{\text{halo}}=v^2_{\text{halo}}\ln\left(z^2+d^2_{\text{h}}\right),
+%         \end{equation}
+%         where $v_{\text{halo}}=131.5$ km/s, $d_{\text{h}}=12$ kpc \citep{Yang2013}.
+%
+%    \item Total potential: $\Phi_{\text{total}}=\Phi_{\text{bulge}}+\Phi_{\text{halo}}$.
+%  \end{enumerate}
+%
+%
+%\item Clumpy cold disk:
+%  \begin{enumerate}
+%    \item Dimension: $14\times14\times0.2$ kpc. i.e. Scale height, $z_{0}=100$ pc. \citep{peak-ism-density}
+%    \item Peak mass density: $\rho_{\text{disk}}^{\text{peak}}=10^{-23}$ g/cm$^3$. \citep{peak-ism-density}
+%    \item Average temperature: $T_{\text{disk}}=10^{3}$ K. \citep{peak-ism-density}
+%    \item Average mass density:
+%          \begin{equation}
+%             \rho_{\text{disk}}=\rho_{\text{disk}}^{\text{peak}}
+%             \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{disk}}/m}\right].
+%             \label{disk-density}
+%          \end{equation}
+%
+%    \item Pressure: $\displaystyle p_{\text{disk}}=\rho_{\text{disk}}T_{\text{disk}}$.
+%
+%    \item The clumpy cuboid, using the publicly\
+%          available pyFC code\footnote{\url{https://pypi.python.org/pypi/pyFC}},\
+%          are described by a log-normal distribution with mean 1.0 and variance 5.0.\
+%          Also, the power spectrum of the clumpy cuboid is characterized by $k_{\text{min}}$ and $\beta$,\
+%          where $k_{\text{min}}$ sets the maximum cloud size within the clumpy cuboid,\
+%          and $\beta$ is the slope of power spectrum in Fourier space.
+%          In this paper, we set $\beta=-5/3$ and $k_{\text{min}}=375$ to follow the Kolmogorov spectrum\
+%          and to limits the maximum size of an individual cloud to approximately 25 pc.
+%
+%    \item The clumpy disk is then constructed by multiplying a fractal cuboid with \Cref{disk-density}.
+%
+%    \item The clouds and voids within clumpy disk are pressure balanced.
+%  \end{enumerate}
+%
+%
+%\item Isothermal atmosphere:
+%  \begin{enumerate}
+%     \item The region outside the clumpy cold disk is atmosphere.
+%     \item $T_{\text{atmp}}=10^{6}$ K. \citep{temperature-MW}
+%     \item Density:
+%          \begin{equation}
+%             \rho_{\text{atmp}}=\rho_{\text{atmp}}^{\text{peak}}
+%             \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{atmp}}/m}\right],
+%             \label{atmosphere-density}
+%          \end{equation}
+%          where $\rho_{\text{atmp}}^{\text{peak}}$ can be obtained by assuming that pressure\
+%          and gravitational potential are continuous at the interface ($z=\pm z_{0}$) between disk and atmosphere.
+%  \end{enumerate}
+%
+%
+%
+%\end{enumerate}
+%
 

### 2021-12-27 paper.tex
update

@@
 
-%\begin{enumerate}
-%  \item Assumptions on gravity:
-%    \begin{enumerate}
-%      \item We use the potential of isothermal slab, symmetric about $z=0$ and\
-%            supported by gas pressure and by under its own self-gravity,\
-%            to mimic the realistic potential of Galactic bulge.
-%      \item The ISM disk and atmosphere are subjected to the fixed external potential\
-%            due to a disk bulge and dark matter halo.
-%      \item In addition to the gravitational interaction, we ignore other interactions between stars and gases.
-%      \item We also ignore the self-gravity of the ISM disk and of the atmosphere.
-%      \item We ignore the centrifugal force of Milky Way rotation acting on the bubbles.
-%      \item We use the potential of isothermal slab to mimic the gravitational potential due to the stellar bulge.
-%      \item The interface between cold ISM disk and atmosphere is parallel to the Galactic plane and is pressure balanced.
-%    \end{enumerate}
-%\end{enumerate}
-%
-%
-%
-%\begin{enumerate}
-%\item Fixed external gravitational potential:
-%  \begin{enumerate}
-%    \item Bulge potential:
-%      \begin{enumerate}
-%       \item Peak density: $\rho_{\text{bulge}}^{\text{peak}}=4\times 10^{-24}$ g/cm$^3$.
-%       \item Potential (isothermal slab):
-%         \begin{equation}
-%           \Phi_{\text{bulge}}=\
-%           2\sigma^2_{\text{bulge}}\
-%           \ln\cosh\left(z\sqrt{\frac{2\pi G\rho_{\text{bulge}}^{\text{peak}}}{\sigma^2_{\text{bulge}}}}\right),
-%         \end{equation}
-%          where $\displaystyle \sigma_{\text{bulge}}=\
-%                \sqrt{\frac{k_{B}T_{\text{bulge}}}{m}}=100$ km/s \citep{velocity-dispersion-MW}.
-%      \end{enumerate}
-%
-%    \item Dark logarithmic halo potential:
-%         \begin{equation}
-%           \Phi_{\text{halo}}=v^2_{\text{halo}}\ln\left(z^2+d^2_{\text{h}}\right),
-%         \end{equation}
-%         where $v_{\text{halo}}=131.5$ km/s, $d_{\text{h}}=12$ kpc \citep{Yang2013}.
-%
-%    \item Total potential: $\Phi_{\text{total}}=\Phi_{\text{bulge}}+\Phi_{\text{halo}}$.
-%  \end{enumerate}
-%
-%
-%\item Clumpy cold disk:
-%  \begin{enumerate}
-%    \item Dimension: $14\times14\times0.2$ kpc. i.e. Scale height, $z_{0}=100$ pc. \citep{peak-ism-density}
-%    \item Peak mass density: $\rho_{\text{disk}}^{\text{peak}}=10^{-23}$ g/cm$^3$. \citep{peak-ism-density}
-%    \item Average temperature: $T_{\text{disk}}=10^{3}$ K. \citep{peak-ism-density}
-%    \item Average mass density:
-%          \begin{equation}
-%             \rho_{\text{disk}}=\rho_{\text{disk}}^{\text{peak}}
-%             \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{disk}}/m}\right].
-%             \label{disk-density}
-%          \end{equation}
-%
-%    \item Pressure: $\displaystyle p_{\text{disk}}=\rho_{\text{disk}}T_{\text{disk}}$.
-%
-%    \item The clumpy cuboid, using the publicly\
-%          available pyFC code\footnote{\url{https://pypi.python.org/pypi/pyFC}},\
-%          are described by a log-normal distribution with mean 1.0 and variance 5.0.\
-%          Also, the power spectrum of the clumpy cuboid is characterized by $k_{\text{min}}$ and $\beta$,\
-%          where $k_{\text{min}}$ sets the maximum cloud size within the clumpy cuboid,\
-%          and $\beta$ is the slope of power spectrum in Fourier space.
-%          In this paper, we set $\beta=-5/3$ and $k_{\text{min}}=375$ to follow the Kolmogorov spectrum\
-%          and to limits the maximum size of an individual cloud to approximately 25 pc.
-%
-%    \item The clumpy disk is then constructed by multiplying a fractal cuboid with \Cref{disk-density}.
-%
-%    \item The clouds and voids within clumpy disk are pressure balanced.
-%  \end{enumerate}
-%
-%
-%\item Isothermal atmosphere:
-%  \begin{enumerate}
-%     \item The region outside the clumpy cold disk is atmosphere.
-%     \item $T_{\text{atmp}}=10^{6}$ K. \citep{temperature-MW}
-%     \item Density:
-%          \begin{equation}
-%             \rho_{\text{atmp}}=\rho_{\text{atmp}}^{\text{peak}}
-%             \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{atmp}}/m}\right],
-%             \label{atmosphere-density}
-%          \end{equation}
-%          where $\rho_{\text{atmp}}^{\text{peak}}$ can be obtained by assuming that pressure\
-%          and gravitational potential are continuous at the interface ($z=\pm z_{0}$) between disk and atmosphere.
-%  \end{enumerate}
-%
-%
-%
-%\end{enumerate}
+% In addition to the gravitational interaction, we ignore other interactions between stars and gases.
+% We also ignore the self-gravity of the ISM disk and of the atmosphere.
+% We ignore the centrifugal force of Milky Way rotation acting on the bubbles.
 %
@@
 \subsection{Jet injection}
-  We resolve the jet source located at the center of the simulation domain,\
+  The core of this work is to release the caveat that the jet direction must be perpendicular to the Galactic plane.\
+  We resolve the jet source at the center of the simulation domain,\
   cells are refined to level 11, leading to a finest spatial resolution of 0.4 pc.\
@@
         \item Cold disk.
-        \item Large pressure gradient along z-dircetion.
+        \item Large pressure gradient along z-direction.
       \end{enumerate}

### 2021-12-28 paper.tex
update

@@
   based on the gradient of mass density.\
-  We also restrict the refinement level is 7 within the cold disk so that\
+  We also restrict the refinement level at 7 within the cold disk so that\
   a molecular cloud can be adequately resolved by approximately 30 cells along their diameter, 20 pc.
@@
 
-\subsection{Jet injection}
-  The core of this work is to release the caveat that the jet direction must be perpendicular to the Galactic plane.\
+\subsection{Inclined jet injection}
+  Recent paper \citep{Gallimore2006} has proposed that\
+  there is a lack of preferred orientation of jets with respect to the plane of the disc.\
+  There are a number of galaxies in which the jets are inclined to the disc normal\
+  (e.g. NGC 3079, \citealt{Cecil2001}; NGC 1052, \citealt{Dopita2015}),\
+  including galaxies in which the jets lie in the plane of the disc (e.g. IC 5063, \citealt{Morganti2015}).
+
+  Motivated by these observations, we simulate three different inclined angles
+  $10^{\circ}$, $45^{\circ}$, and $80^{\circ}$ with respect to the Galactic plane to\
+  release the caveat that\
+  the jet direction must be perpendicular to the Galactic plane, and in particular to\
+  investigate the effect of inclined angle on the shape of bubbles.
+
+  The jet is constantly ejected from a cylindrical source with
+  four-velocity
+
+  the density contrast between the thermal gas contained in the jets
+  and the ambient gas
+
   We resolve the jet source at the center of the simulation domain,\
@@
 
-\subsection{X-ray and Gamma-ray emission}
+\section{Results}
+
+\subsection{X-ray emission}
 
@@
 
-Inverse Compton scattering
+\subsection{Gamma-ray emission}
+
+\subsubsection{Leptonic process}
+
 \begin{equation}
@@
 
-Hadronic process
+\subsubsection{Hadronic process}
+
 \begin{equation}

### 2021-12-28 paper.tex
update

@@
 \subsection{Inclined jet injection}
-  Recent paper \citep{Gallimore2006} has proposed that\
+  Early observation \citep{Gallimore2006} has proposed that\
   there is a lack of preferred orientation of jets with respect to the plane of the disc.\
@@
 
-  Motivated by these observations, we simulate three different inclined angles
-  $10^{\circ}$, $45^{\circ}$, and $80^{\circ}$ with respect to the Galactic plane to\
-  release the caveat that\
+  Motivated by these observations, we simulate three different inclined angles,\
+  $10^{\circ}$, $45^{\circ}$, and $80^{\circ}$ with respect to the Galactic plane\
+  in order to release the caveat that\
   the jet direction must be perpendicular to the Galactic plane, and in particular to\
-  investigate the effect of inclined angle on the shape of bubbles.
+  investigate the effect of the jet-disk misalignment on the symmetry of bubbles.
 
-  The jet is constantly ejected from a cylindrical source with
-  four-velocity
+  All three cases with different inclined angles share the same injection parameters:\
+  the density contrast between the thermal gas contained in the jet source and the ambient gas,\
+  $\rho_{\text{jet}}/\rho_{\text{amb}}=10^{-3}$,\
+  the temperature contrast, $T_{\text{jet}}/T_{\text{amb}}=2\times10^{4}$,\
+  the CR energy density $e_{\text{CR}}=??$,\
+  and the flow 4-velocity inside the jet source $\beta\gamma = 0.6$\
+  along the symmetric axis of cylinder.
 
-  the density contrast between the thermal gas contained in the jets
-  and the ambient gas
+  Note that as we inject the jets within the clumpy disk,\
+  we define the ambient gas density by the peak density of\
+  the isothermal disk on the mid-plane $z=0$ (i.e. $\rho^{\text{peak}}_{\text{isoDisk}}$),\
+  as opposed to the \textit{clumpy} density around the jet source, to avoid ambiguous definition.
+
+  Jet power Eddington luminosity
+
+  The bipolar jets are constantly and bidirectionally ejected from a cylindrical source\
+  with diameter and height of 4 pc, leading to the volume $\sim 50 \text{pc}^{3}$,\
+  much smaller than that of individual clump by a factor of 83.\
+  By intentionally reducing the ratio of the volume of jet source and of clump,\
+  we
 
@@
   cells are refined to level 11, leading to a finest spatial resolution of 0.4 pc.\
+
+  Source size is much smaller than clump
 

### 2021-12-28 paper.tex
update

@@
 
-  Note that as we inject the jets within the clumpy disk,\
+  Note that as we inject the jets at the center of the clumpy disk,\
   we define the ambient gas density by the peak density of\
@@
   The bipolar jets are constantly and bidirectionally ejected from a cylindrical source\
-  with diameter and height of 4 pc, leading to the volume $\sim 50 \text{pc}^{3}$,\
+  with diameter and height of 4 pc, leading to the source volume $\sim 50 \text{pc}^{3}$ is\
   much smaller than that of individual clump by a factor of 83.\
-  By intentionally reducing the ratio of the volume of jet source and of clump,\
-  we
+  By intentionally reducing the volume ratio of the jet source to an individual clump,\
+  we can diminish the effect of the randomness of the clumps on the bubbles.
 
-  We resolve the jet source at the center of the simulation domain,\
-  cells are refined to level 11, leading to a finest spatial resolution of 0.4 pc.\
-
-  Source size is much smaller than clump
+  We resolve the jet source with the highest refinement level 11,\
+  bringing the finest spatial resolution up to 0.4 pc.\
 

### 2021-12-28 paper.tex
update

@@
   The bipolar jets are constantly and bidirectionally ejected from a cylindrical source\
-  with diameter and height of 4 pc, leading to the source volume $\sim 50 \text{pc}^{3}$ is\
+  with diameter and height of 4 pc, leading to the source volume $\sim 50 \text{ pc}^{3}$ is\
   much smaller than that of individual clump by a factor of 83.\

### 2021-12-30 paper.tex
update

--- 2021-12-28 paper.tex
@@
   The density of clumpy disk can thus be obtained by taking the scalar products of\
-  $f(\bold{x})$ with $\rho_{\text{isoDisk}}(z)$ over all cells within the disk:\
+  $f(\bold{x})$ with $\rho_{\text{isoDisk}}(z)$ over all cells within the disk, i.e.,\
   $\displaystyle\rho_{\text{ismDisk}}(\bold{x}) =\
   f(\bold{x}) \rho_{\text{isoDisk}}(z)$.\
-  Also, the pressure equilibrium condition implies that the temperature of disk is
+  Also, the pressure equilibrium within the clumpy disk implies that the temperature of disk is
   $\displaystyle T_{\text{ismDisk}}(\bold{x}) =\
@@
 
-  Motivated by these observations, we simulate three different inclined angles,\
+  Motivated by these observations, we simulate three cases with different inclined angles,\
   $10^{\circ}$, $45^{\circ}$, and $80^{\circ}$ with respect to the Galactic plane\
@@
   and the flow 4-velocity inside the jet source $\beta\gamma = 0.6$\
-  along the symmetric axis of cylinder.
+  along the symmetric axis of cylinder.\
+  The jet power is thus $3.2\times 10^{42}$ erg/s, resulting in the Eddington ratio 0.008.
 
@@
 
-  Jet power Eddington luminosity
-
-  The bipolar jets are constantly and bidirectionally ejected from a cylindrical source\
-  with diameter and height of 4 pc, leading to the source volume $\sim 50 \text{pc}^{3}$ is\
+  The bipolar jets are constantly ejected from a cylindrical source\
+  with diameter and height of 4 pc, leading to the source volume $\sim 50 \text{ pc}^{3}$ is\
   much smaller than that of individual clump by a factor of 83.\

### 2021-12-30 paper.tex
update

@@
 
-\begin{equation}
-  \frac{dE}{dtd\epsilon_{1}dV} = \frac{3}{4}\sigma_{T}c\textit{C}\epsilon_{1}\int^{\epsilon_{\text{max}}}_{\epsilon_{\text{min}}}
+In the leptonic scenario, the gamma-rays originate from IC scattering of the ISRF by CRe.\
+The emissivity of the upscattered photons at the energy $\epsilon_{1}$ is given by\
+\citet{Jones1968,BLUMENTHAL1970}.
+
+\begin{subequations}
+  \begin{align}
+  &\frac{dE}{dtd\epsilon_{1}dV} =\nonumber\\
+               &\frac{3}{4}\sigma_{T}c\textit{C}\epsilon_{1}\int^{\epsilon_{\text{max}}}_{\epsilon_{\text{min}}}
                \frac{n(\epsilon)}{\epsilon}d\epsilon\int^{\gamma_{\text{max}}}_{\gamma_{\text{min}}\left(\epsilon\right)}
-               \gamma^{-(p+2)}f(q, \Gamma)d\gamma.
-\end{equation}
+               \gamma^{-(p+2)}f(q, \Gamma)d\gamma,\\
+  \nonumber\\
+  &f(q, \Gamma) =\nonumber\\
+               &2q\ln q+(1+2q)(1-q)+0.5(1-q)\frac{\left(\Gamma q\right)^2}{1+\Gamma q},\\
+  &q=\frac{\epsilon_{1}/\gamma_{\text{e}}\
+               m_{\text{e}}c^{2}}{\Gamma\left(1-\epsilon_{1}/\gamma_{\text{e}}m_{\text{e}}c^{2}\right)},\\
+  &\Gamma=\frac{4\epsilon \gamma_{\text{e}}}{m_{\text{e}}c^2},
+  \end{align}
+\end{subequations}
 
-\begin{equation}
-f(\gamma_{\text{e}}, \epsilon) = 2q\ln q+(1+2q)(1-q)+0.5(1-q)\frac{\left(\Gamma q\right)^2}{1+\Gamma q},
-\end{equation}
+where $\gamma_{\text{min}}(\epsilon)$ and $\gamma_{\text{max}}=10^{6}$\
+are the minimum and maximum Lorentz factor of CRe,\
+$n(\epsilon)$ is the photon number density of ISRF per energy,
 
-\begin{equation}
-\Gamma=\frac{4\epsilon \gamma_{\text{e}}}{m_{\text{e}}c^2}
-\end{equation}
+We set $\gamma_{\text{max}}$ to be $10^{6}$, corresponding to the cutoff CRe energy $0.5$ GeV,\
+$\gamma_{\text{min}}(\epsilon)$ is the minimum Lorentz factor of CRe such that CRe is energetic enough to\
+produce scattered photon at the energy $\epsilon_{1}$ from an incident photon energy $\epsilon$.
 
@@
 \begin{equation}
-q=\frac{\epsilon_{1}/\gamma_{\text{e}}m_{\text{e}}c^{2}}{\Gamma\left(1-\epsilon_{1}/\gamma_{\text{e}}m_{\text{e}}c^{2}\right)}.
+\gamma_{\text{min}}=\
+ 0.5\left(\frac{\epsilon_{1}}{mc^2}+\sqrt{\left(\frac{\epsilon_{1}}{mc^2}\right)^2+\
+ \frac{\epsilon_{1}}{\epsilon}}\right).
 \end{equation}

### 2021-12-30 paper.tex
update

--- 2021-12-30 paper.tex
@@
 
-\begin{equation}
-  \frac{dE}{dtd\epsilon_{1}dV} = \frac{3}{4}\sigma_{T}c\textit{C}\epsilon_{1}\int^{\epsilon_{\text{max}}}_{\epsilon_{\text{min}}}
+In the leptonic scenario, the gamma-rays originate from IC scattering of the ISRF by CRe.\
+
+The emissivity of the upscattered photons at the energy $\epsilon_{1}$ is given by\
+the double integrals \citep{BLUMENTHAL1970}\
+over the range of incident photon energy and the CRe Lorentz factor:
+
+\begin{subequations}
+  \begin{align}
+  &\frac{dE}{dtd\epsilon_{1}dV} =\nonumber\\
+               &\frac{3}{4}\sigma_{T}c\mathbb{C}\epsilon_{1}\int^{\epsilon_{\text{max}}}_{\epsilon_{\text{min}}}
                \frac{n(\epsilon)}{\epsilon}d\epsilon\int^{\gamma_{\text{max}}}_{\gamma_{\text{min}}\left(\epsilon\right)}
-               \gamma^{-(p+2)}f(q, \Gamma)d\gamma.
-\end{equation}
+               \gamma^{-(p+2)}f(q, \Gamma)d\gamma,\\
+  \nonumber\\
+  &f(q, \Gamma) =\nonumber\\
+               &2q\ln q+(1+2q)(1-q)+0.5(1-q)\frac{\left(\Gamma q\right)^2}{1+\Gamma q},\\
+  &q=\frac{\epsilon_{1}/\gamma\
+               m_{\text{e}}c^{2}}{\Gamma\left(1-\epsilon_{1}/\gamma m_{\text{e}}c^{2}\right)},\\
+  &\Gamma=\frac{4\epsilon \gamma}{m_{\text{e}}c^2},\\
+  &\gamma_{\text{min}}(\epsilon)=\
+   0.5\left(\frac{\epsilon_{1}}{mc^2}+\sqrt{\left(\frac{\epsilon_{1}}{mc^2}\right)^2+\
+   \frac{\epsilon_{1}}{\epsilon}}\right),
+  \end{align}
+\end{subequations}
 
-\begin{equation}
-f(\gamma_{\text{e}}, \epsilon) = 2q\ln q+(1+2q)(1-q)+0.5(1-q)\frac{\left(\Gamma q\right)^2}{1+\Gamma q},
-\end{equation}
+where $\sigma_{T}$ is the Thomson cross section, $c$ speed of light, $m_{\text{e}}$ electron mass,\
+$n(\epsilon)$ the photon number density of ISRF per energy, $\gamma$ the Lorentz factor of CRe,\
+$\mathbb{C}$ and $p$ are the normalization constant and spectral index of CRe power-law spectrum,\
+$\gamma_{\text{min}}(\epsilon)$ is the minimum Lorentz factor of CRe such that CRe is energetic enough to\
+produce scattered photon at the energy $\epsilon_{1}$ from an incident photon energy $\epsilon$.\
+We set $\gamma_{\text{max}}$ to be $10^{6}$, corresponding to the cutoff CRe energy $0.5$ GeV.
 
-\begin{equation}
-\Gamma=\frac{4\epsilon \gamma_{\text{e}}}{m_{\text{e}}c^2}
-\end{equation}
+To  we integrate the incident photon energy from\
+$\epsilon_{\text{min}}=1.13\times10^{-4}$ eV (CMB radiation) to\
+$\epsilon_{\text{max}}=13.59$ eV (starlight).
 
-$\gamma_{\text{min}}\left(\epsilon\right)$ is the root of $f(\gamma_{\text{e}}, \epsilon)=0$ at a specific incident photon energy.
-
-\begin{equation}
-q=\frac{\epsilon_{1}/\gamma_{\text{e}}m_{\text{e}}c^{2}}{\Gamma\left(1-\epsilon_{1}/\gamma_{\text{e}}m_{\text{e}}c^{2}\right)}.
-\end{equation}
+The gamma-ray emissivity\
+is computed for each computational volume element in our simulations\
+using the Klein–Nishina IC cross-section \citep{Jones1968} based\
+on the simulated CR number density and the ISRF model given by \citep{Porter2017}.
 

### 2021-12-30 paper.tex
update

@@
 using the Klein–Nishina IC cross-section \citep{Jones1968} based\
-on the simulated CR number density and the ISRF model given by \citep{Porter2017}.
+on the simulated CR number density and the ISRF model given by \citet{Porter2017}.
 

### 2021-12-30 paper.tex
update

@@
   With the help of the isothermal and hydrostatic equilibrium conditions,\
-  and assuming the interface between isothermal disk and atmosphere is in pressure equilibrium,\
+  and assuming the interfaces between isothermal disk and atmosphere are in pressure equilibrium,\
   we can write the steady-state gaseous density distributions,\

### 2021-12-30 paper.tex
update

@@
 $\mathbb{C}$ and $p$ are the normalization constant and spectral index of CRe power-law spectrum,\
-$\gamma_{\text{min}}(\epsilon)$ is the minimum Lorentz factor of CRe such that CRe is energetic enough to\
+$\gamma_{\text{min}}(\epsilon)$ is the minimum required Lorentz factor of CRe such that CRe is energetic enough to\
 produce scattered photon at the energy $\epsilon_{1}$ from an incident photon energy $\epsilon$.\
@@
 on the simulated CR number density and the ISRF model given by \citet{Porter2017}.
+
+% After projection the photon flux at energy $$ is computed ..
 

### 2021-12-30 paper.tex
update

@@
       \item  $\ddag$ In numerical simulations of turbulence,\
-             \citet{Federrath2010} find $\sigma\sim 3.6$ and 35 for solenoidal (divergence-free) and compressive (curl-free) forcing,\
+             \citet{Federrath2010} find $\sigma\sim 3.6$ and 35 for solenoidal (divergence-free)\
+             and compressive (curl-free) driving force,\
              respectively, so that our adopted value of 5 is closer to their solenoidal result.
@@
   &\gamma_{\text{min}}(\epsilon)=\
-   0.5\left(\frac{\epsilon_{1}}{mc^2}+\sqrt{\left(\frac{\epsilon_{1}}{mc^2}\right)^2+\
+   0.5\left(\frac{\epsilon_{1}}{m_{\text{e}}c^2}+\sqrt{\left(\frac{\epsilon_{1}}{m_{\text{e}}c^2}\right)^2+\
    \frac{\epsilon_{1}}{\epsilon}}\right),

### 2021-12-31 paper.tex
update

@@
 In the leptonic scenario, the gamma-rays originate from IC scattering of the ISRF by CRe.\
+The CRe spectrum follows a power law distribution with a spectral index 2 and ranges from\
+$m_{\text{e}}c^2$ ($0.5$ MeV) to $10^{6}m_{\text{e}}c^2$ ($0.5$ TeV).\
 
@@
 $\mathbb{C}$ and $p$ are the normalization constant and spectral index of CRe power-law spectrum,\
-$\gamma_{\text{min}}(\epsilon)$ is the minimum required Lorentz factor of CRe such that CRe is energetic enough to\
-produce scattered photon at the energy $\epsilon_{1}$ from an incident photon energy $\epsilon$.\
-We set $\gamma_{\text{max}}$ to be $10^{6}$, corresponding to the cutoff CRe energy $0.5$ GeV.
+$\gamma_{\text{min}}(\epsilon)$ is the minimum required Lorentz factor of CRe such that CRe is energetic sufficient for\
+producing scattered photon at the energy $\epsilon_{1}$ from an incident photon energy $\epsilon$.\
+$\gamma_{\text{max}}$ is the maximum CRe Lorentz factor in the spectrum, i.e. $\gamma_{\text{max}}=10^{6}$.
 
-To  we integrate the incident photon energy from\
+Since the ISRF is dominated by the cosmic microwave background (CMB)\
+at high latitudes and optical starlight at low latitudes,\
+
+we integrate the incident photon energy from\
 $\epsilon_{\text{min}}=1.13\times10^{-4}$ eV (CMB radiation) to\
@@
 The gamma-ray emissivity\
-is computed for each computational volume element in our simulations\
+is computed for each computational cell in our simulations\
 using the Klein–Nishina IC cross-section \citep{Jones1968} based\
@@
 % After projection the photon flux at energy $$ is computed ..
+
+\begin{equation}
+I = \frac{1}{\epsilon_{1}}\int \frac{dE}{dtd\epsilon_{1}dV} dl,
+\end{equation}
 

### 2021-12-31 paper.tex
update

@@
 
-% After projection the photon flux at energy $$ is computed ..
-
+To evaluate the photon flux at the energy $\epsilon_{1}$ and\
+take into account the perspective projection effect,
+we integrate the emissivity along line-of-sights from the solar position:
 \begin{equation}
@@
 \subsubsection{Hadronic process}
-
 \begin{equation}
-  \frac{dE}{dtd\epsilon_{1}dV} = cn_{H}pC\left(\frac{\epsilon_{1}}{m_{\text{p}}c^2}\right)^{-p}\int_{0}^{1}\sigma(\epsilon_{\text{p}}) F(x,\epsilon_{\text{p}}) x^{p}dx.
+  \frac{dE}{dtd\epsilon_{1}dV} =\
+   cn_{H}pC\left(\frac{\epsilon_{1}}{m_{\text{p}}c^2}\right)^{-p}\
+   \int_{0}^{1}\sigma(\epsilon_{\text{p}}) F(x,\epsilon_{\text{p}}) x^{p}dx.
 \end{equation}

### 2021-12-31 paper.tex
update

@@
 
-To evaluate the photon flux at the energy $\epsilon_{1}$ and\
+To evaluate the simulated photon flux at the energy $\epsilon_{1}$ and\
 take into account the perspective projection effect,

### 2022-01-01 paper.tex
update

--- 2021-12-31 paper.tex
@@
 
-  The set of \Cref{governing-eq} is closed by using the Taub-Mathews equation of state (\citealt{Taub}; \citealt{TM_EOS})\
+  The set of \Cref{governing-eq} is closed by using the Taub-Mathews equation of state \citep{Taub,TM_EOS}\
   that approximates the exact EoS \citep{Synge} for ultra-relativistically\
@@
          \item Thermal bremsstrahlung: The X-ray emissivity in an energy range 1.4–1.6 keV is calculated\
-               using the MEKAL model (\citealt{Xray-1}; \citealt{Xray-2}; \citealt{Xray-3})\
-               implemented in the utility XSPEC\citep{XSPEC}, assuming solar metallicity.
+               using the MEKAL model \citep{Xray-1,Xray-2,Xray-3}\
+               implemented in the utility XSPEC \citep{XSPEC}, assuming solar metallicity.
        \end{enumerate}
@@
 Note that the observed X-ray emission is contributed by all the gas in the Milky Way halo,\
-which likely extends to a radius of $\sim$250 kpc (\citealt{halo-radius-1}; \citealt{halo-radius-2}),\
+which likely extends to a radius of $\sim$250 kpc \citep{halo-radius-1,halo-radius-2},\
 much bigger than our simulation box. Therefore, we first compute the X-ray emissivity\
@@
 
-Since the ISRF is dominated by the cosmic microwave background (CMB)\
-at high latitudes and optical starlight at low latitudes,\
-
-we integrate the incident photon energy from\
+We integrate the incident photon energy from\
 $\epsilon_{\text{min}}=1.13\times10^{-4}$ eV (CMB radiation) to\
-$\epsilon_{\text{max}}=13.59$ eV (starlight).
+$\epsilon_{\text{max}}=13.59$ eV (starlight) in order to\
+facilitate a reliable interpretation.
 
@@
 
-To evaluate the photon flux at the energy $\epsilon_{1}$ and\
+To evaluate the simulated photon flux $I$ at the energy $\epsilon_{1}$ and\
 take into account the perspective projection effect,
-we integrate the emissivity along line-of-sights from the solar position:
+we integrate the emissivity over line-of-sights from the solar position:
 \begin{equation}
-I = \frac{1}{\epsilon_{1}}\int \frac{dE}{dtd\epsilon_{1}dV} dl,
+I = \frac{1}{\epsilon_{1}}\int \frac{dE}{dtd\epsilon_{1}dV} dl.
 \end{equation}

### 2022-01-01 paper.tex
update

@@
 
-  \begin{enumerate}
-    \item X-ray:
-       \begin{enumerate}
-         \item Thermal bremsstrahlung: The X-ray emissivity in an energy range 1.4–1.6 keV is calculated\
+Thermal bremsstrahlung: The X-ray emissivity in an energy range 1.4–1.6 keV is calculated\
 using the MEKAL model \citep{Xray-1,Xray-2,Xray-3}\
-               implemented in the utility XSPEC \citep{XSPEC}, assuming solar metallicity.
-       \end{enumerate}
-    \item Gamma-ray:
-       \begin{enumerate}
-         \item Leptonic process:\\
-          The gamma-ray emission is produced by inverse Comptom scattering of the ISRF by CRe.
-         \item Hadronic process:\\
-          In the hadronic model, CRp undergo hadronic collisions with thermal gas protons\
-          and produce $\gamma$-ray via pion decay. The volume emissivity of the emission can be written as
-          \begin{equation}
-             \epsilon \propto U_{\text{CRp}}n_{p}\sigma_{p}\kappa_{pp}.
-          \end{equation}
-       \end{enumerate}
-  \end{enumerate}
+implemented in the utility XSPEC \citep{XSPEC}, assuming solar metallicity.\
 
@@
 \subsubsection{Leptonic process}
-
 In the leptonic scenario, the gamma-rays originate from IC scattering of the ISRF by CRe.\
@@
 \subsubsection{Hadronic process}
+In the hadronic model, CRp undergo hadronic collisions with thermal gas protons\
+and produce $\gamma$-ray via pion decay. The volume emissivity of the emission can be written as
+\begin{equation}
+   \epsilon \propto U_{\text{CRp}}n_{p}\sigma_{p}\kappa_{pp}.
+\end{equation}
+
 \begin{equation}

### 2022-01-03 paper.tex
update

@@
 In the leptonic scenario, the gamma-rays originate from IC scattering of the ISRF by CRe.\
-The CRe spectrum follows a power law distribution with a spectral index 2 and ranges from\
+The CRe spectrum follows a power law distribution\
+with a spectral index $p=2$ and ranges from\
 $m_{\text{e}}c^2$ ($0.5$ MeV) to $10^{6}m_{\text{e}}c^2$ ($0.5$ TeV).\

### 2022-01-04 figures/combine_gammaRay.sh
update

@@ -1,0 +1,4 @@
+convert  \
+fig__gammaRay_2e9_1e6_angle_000.png \
+fig__gammaRay_10e9_1e6_angle_000.png \
+fig__gammaRay_100e9_1e6_angle_000.png  -smush 20 fig__gammaRay.png

### 2022-01-04 paper.tex
update

@@
 
-  The initial density profile of \Cref{disk-atm-sys} is shown in \Cref{density-profile}\
+  The density profile of \Cref{disk-atm-sys} is shown in \Cref{fig__initial-density-profile}\
   and compared to the observed result \citep{Miller_2013} beyond 1 kpc.\
@@
 
-  \begin{figure*}[h]
-    \subfigure[The initial gaseous density profile along z-axis] % caption
-    {
-      \includegraphics[width=0.4\linewidth]{figures/fig__density-profile.png}
-      \label{density-profile}
-    }
-  \caption{Captions}
-  \end{figure*}
+  \begin{figure}
+    \includegraphics[width=1.0\linewidth]{figures/fig__initial-density-profile.png}
+    \caption{The profile of $\rho_{\text{isoDisk}}(z)$ along z-axis.}
+    \label{fig__initial-density-profile}
+  \end{figure}
+
+  \begin{figure}
+      \includegraphics[width=1.0\linewidth]{figures/fig__numberDensityHistogram.png}
+      \caption{The initial density distribution of the number density\
+               for a settling ISM without jet source.} % caption
+      \label{fig__numberDensityHistogram}
+  \end{figure}
 

### 2022-01-04 paper.tex
update

@@
   \begin{figure}
-    \includegraphics[width=1.0\linewidth]{figures/fig__initial-density-profile.png}
+    \includegraphics[width=\columnwidth]{figures/fig__initial-density-profile.png}
     \caption{The profile of $\rho_{\text{isoDisk}}(z)$ along z-axis.}
@@
   \begin{figure}
-      \includegraphics[width=1.0\linewidth]{figures/fig__numberDensityHistogram.png}
+      \includegraphics[width=\columnwidth]{figures/fig__numberDensityHistogram.png}
       \caption{The initial density distribution of the number density\
@@
       \label{fig__numberDensityHistogram}
+  \end{figure}
+
+  \begin{figure}
+    \includegraphics[width=\columnwidth]{figures/fig__zoom-in-disk.png}
+    \caption{The slice of pressure (top), temperature (middle), and number density (bottom)\
+             in the y-z plane passing through the center of the disk.}
+    \label{fig__zoom-in-disk}
   \end{figure}
@@
 
+  \begin{figure*}
+    \includegraphics[width=\linewidth]{figures/fig__xRay.png}
+    \caption{One-dimensional surface-brightness\
+             profiles in the same energy band\
+             , cut at various galactic latitudes (as labelled).\
+             For comparison, we also show ...}
+    \label{fig__xRay.png}
+  \end{figure*}
+
 \subsection{Gamma-ray emission}
@@
 
+\begin{figure*}
+  \includegraphics[width=\linewidth]{figures/fig__gammaRay.png}
+  \caption{The simulated photon flux at  2 GeV (top), 10 GeV (middle), and 100 GeV (bottom).}
+  \label{fig__gammaRay}
+\end{figure*}
+
 \subsubsection{Hadronic process}

### 2022-01-04 figures/combine_xRay.sh

@@ -1,0 +1,6 @@
+convert fig__x-ray-profile-0.8keV-000.png -resize 1334x fig__x-ray-profile-0.8keV-000-resize.png
+
+convert -trim fig__xray_0.8keV_angle_000.png fig__x-ray-profile-0.8keV-000-resize.png -smush 10 fig__xRay.png
+
+
+rm fig__x-ray-profile-0.8keV-000-resize.png

### 2022-01-04 figures/combine_xRay.sh
update

@@ -2,5 +2,4 @@ convert fig__x-ray-profile-0.8keV-000.png -resize 1334x fig__x-ray-profile-0.8ke
 
 convert -trim fig__xray_0.8keV_angle_000.png fig__x-ray-profile-0.8keV-000-resize.png -smush 10 fig__xRay.png
 
-
 rm fig__x-ray-profile-0.8keV-000-resize.png

### 2022-01-05 paper.tex
update

@@
 
-%  Moreover, since the clouds are considered to be thermally unstable\
-%  when the cloud temperature beyond\
-%  the critical temperature of the warm atomic phase,\
-%  we replace the cell density as\
-%  $\rho_{\text{ismDisk}}T_{\text{ismDisk}}/T_{\text{atmp}}$\
-%  when the cell temperature beyond the critical value $T_{\text{crit}}$.
-
   \Cref{table-parameters} summarize the parameters of the clumpy disk and their references.
@@
 {\bf Clumpy disk }                    &                                           &                                      &                                \\
-$T_{\text{\text{c}}}$                 & Critical temperature of warm atomic phase & $10^{4}$ K                           & \citep{peak-ism-density}       \\
-$\dagger$  $k_{\text{min}}$           & Cutoff wave number                        & 375.0                                & \multicolumn{1}{c}{''}         \\
+$\dagger$  $k_{\text{min}}$           & Cutoff wave number                        & 375.0                                & \citep{peak-ism-density}       \\
 $\mu$                                 & Mean of scalar field                      & 1.0                                  &   N/A                          \\
@@
 
+  \begin{figure}
+    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp.png}
+    \caption{The slice of ...}
+    \label{fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp}
+  \end{figure}
+
 \subsection{X-ray emission}
@@
 \subsection{Gamma-ray emission}
+
+  \begin{figure}
+    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg-CR.png}
+    \caption{The slice of CR...}
+    \label{fig__jetI5+ismSeed3-45deg-CR}
+  \end{figure}
 
@@
 $\epsilon_{\text{max}}=13.59$ eV (starlight) in order to\
-facilitate a reliable interpretation.
+facilitate a reliable interpretation of simulated gamma-ray map.
 

### 2022-01-05 paper.tex
update

@@
 \begin{abstract}
-\begin{enumerate}
-  \item Release the caveat of jet direction.
-  \item Rule out the hadronic process.
-  \item Predict the small inner bubbles.
-  \item How to explain why we assume e\_CR << e\_gas
-  \item How to explain the lifespan of bubbles is too long.
-  \item How to explain the jet power.
-  \item How to explain the inconsistant of gamma-ray map.
-\end{enumerate}
 \end{abstract}
@@
 
-\section{to-do-list}
-\begin{enumerate}
-  \item Predict cold inner bubbles, emitting OIII or OII spectrum.
-\end{enumerate}
-
 \section{conclusions}

### 2022-01-06 paper.tex
update

@@
   With the help of the isothermal and hydrostatic equilibrium conditions,\
-  and assuming the interfaces between isothermal disk and atmosphere are in pressure equilibrium,\
+  and assuming the interfaces between isothermal disk and atmosphere are in thermal pressure equilibrium,\
   we can write the steady-state gaseous density distributions,\
@@
   except for $\rho_{\text{atmp}}^{\text{peak}}$ that\
-  can be derived from the other known parameters and pressure equilibrium condition\
+  can be derived from the other known parameters and thermal pressure equilibrium condition\
   on the interfaces $(z=\pm z_{0})$ between the disk and atmosphere.\
 
-  The density profile of \Cref{disk-atm-sys} is shown in \Cref{fig__initial-density-profile}\
-  and compared to the observed result \citep{Miller_2013} beyond 1 kpc.\
+  The density profile of \Cref{disk-atm-sys} is shown in \Cref{fig__initial-density-profile}.\
+  Beyond the core radius ($\sim 2 \text{ kpc}$) the gaseous density decreases rapidly as a power-law.
 
-  Note that there is an difficulty in disentangling the contribution\
-  of the Local Bubble, a supernova remnant in which the Solar System is embedded \citep{Snowden1990},\
-  and the contribution from solar wind charge-exchange processes, which produce soft\
-  X-ray emission throughout the Solar System. As a result, the density profile of the Galactic halo remains unclear\
-  \citep{BlandHawthorn2016}.
+%  The density profile of \Cref{disk-atm-sys} is shown in \Cref{fig__initial-density-profile}\
+%  and compared to the observed result \citep{Miller_2013} beyond 1 kpc.\
+%
+%  Note that there is an difficulty in disentangling the contribution\
+%  of the Local Bubble, a supernova remnant in which the Solar System is embedded \citep{Snowden1990},\
+%  and the contribution from solar wind charge-exchange processes, which produce soft\
+%  X-ray emission throughout the Solar System. As a result, the density profile of the Galactic halo remains unclear\
+%  \citep{BlandHawthorn2016}.
 
@@
     \includegraphics[width=\columnwidth]{figures/fig__initial-density-profile.png}
-    \caption{The profile of $\rho_{\text{isoDisk}}(z)$ along z-axis.}
+    \caption{The density profile of the isothermal disk (red pluses) and\
+             atmosphere (blue crosses) along the positive z-axis.\
+             The density distribution is derived from hydrostatic equilibrium,\
+             the interface ($z=0.1$) between the isothermal disk\
+             and the atmosphere is pressure balanced.}
     \label{fig__initial-density-profile}
-  \end{figure}
-
-  \begin{figure}
-      \includegraphics[width=\columnwidth]{figures/fig__numberDensityHistogram.png}
-      \caption{The initial density distribution of the number density\
-               for a settling ISM without jet source.} % caption
-      \label{fig__numberDensityHistogram}
-  \end{figure}
-
-  \begin{figure}
-    \includegraphics[width=\columnwidth]{figures/fig__zoom-in-disk.png}
-    \caption{The slice of pressure (top), temperature (middle), and number density (bottom)\
-             in the y-z plane passing through the center of the disk.}
-    \label{fig__zoom-in-disk}
   \end{figure}
@@
   f(\bold{x}) \rho_{\text{isoDisk}}(z)$.\
-  Also, the pressure equilibrium within the clumpy disk implies that the temperature of disk is
+  Also, the thermal pressure equilibrium within the clumpy disk implies that the temperature of disk is
   $\displaystyle T_{\text{ismDisk}}(\bold{x}) =\
@@
   a molecular cloud can be adequately resolved by approximately 30 cells along their diameter, 20 pc.
+
+  \Cref{fig__zoom-in-disk} shows a close-up view of the\
+  pressure, temperature, and number density slices
+  in the y-z plane through the center of the disk.
+
+  \Cref{fig__numberDensityHistogram} plots the volume filling factor as a function of\
+  initial number density within the disk without jet source.\
+
+  \begin{figure}
+      \includegraphics[width=\columnwidth]{figures/fig__numberDensityHistogram.png}
+    \caption{The volume filling factor as a function of\
+             initial number density within the disk without jet source.\
+             The regions covered by vertical bands represent the allowable number densities \citep{peak-ism-density} for\
+             hot ionized, warm neutral (WNM), warm ionized (WIM), cold nuetral mediums (CNM), and molecular clouds.}
+      \label{fig__numberDensityHistogram}
+  \end{figure}
+
+  \begin{figure}
+    \includegraphics[width=\columnwidth]{figures/fig__zoom-in-disk.png}
+    \caption{Close-up view of the\
+             pressure (top), temperature (middle), and number density (bottom) slices\
+             in the y-z plane through the center of the disk.
+             }
+    \label{fig__zoom-in-disk}
+  \end{figure}
 
@@
   there is a lack of preferred orientation of jets with respect to the plane of the disc.\
-  There are a number of galaxies in which the jets are inclined to the disc normal\
+  A number of galaxies in which the jets are inclined to the disc normal\
   (e.g. NGC 3079, \citealt{Cecil2001}; NGC 1052, \citealt{Dopita2015}),\

### 2022-01-06 paper.tex
update

@@
   the temperature contrast, $T_{\text{jet}}/T_{\text{amb}}=2\times10^{4}$,\
-  the CR energy density $e_{\text{CR}}=??$,\
+  the pressure ratio of CR to gas is 0.18,\
   and the flow 4-velocity inside the jet source $\beta\gamma = 0.6$\

### 2022-01-06 paper.tex
update

@@
 
-  Motivated by these observations, we simulate three cases with different inclined angles,\
-  $10^{\circ}$, $45^{\circ}$, and $80^{\circ}$ with respect to the Galactic plane\
+  Motivated by these observations, we simulate the jet with an inclination angle\
+  $45^{\circ}$ with respect to the Galactic plane\
   in order to release the caveat that\
@@
 
-  The bipolar jets are constantly ejected from a cylindrical source\
-  with diameter and height of 4 pc, leading to the source volume $\sim 50 \text{ pc}^{3}$ is\
-  much smaller than that of individual clump by a factor of 83.\
+  The bipolar jets are constantly ejected from a cylindrical source within a jet duration time 1.2 Myr,\
+  allowing the total ejected energy $1.2\times10^{56}$ erg is between\
+  $8\times10^{55}$ erg and $1.3\times10^{56}$ erg, estimated by \citet{Predehl2020}.\
+
+  The diameter and height of cylindrical source are 4 pc, leading to the source volume $\sim 50 \text{ pc}^{3}$ is\
+  much smaller than that of an individual clump by a factor of about 83.\
   By intentionally reducing the volume ratio of the jet source to an individual clump,\
-  we can diminish the effect of the randomness of the clumps on the bubbles.
-
-  We resolve the jet source with the highest refinement level 11,\
+  we can diminish the effect of the randomness of the clumps on the bubbles.\
+  Moreover, we resolve the jet source with the highest refinement level 11,\
   bringing the finest spatial resolution up to 0.4 pc.\
-
- \begin{enumerate}
-    \item Why the overall structure is insensitive to jet direction?
-      \begin{enumerate}
-        \item Jet source size.
-        \item Cold disk.
-        \item Large pressure gradient along z-direction.
-      \end{enumerate}
- \end{enumerate}
 

### 2022-01-06 paper.tex
update

@@
 
-  All three cases with different inclined angles share the same injection parameters:\
+  A few additional quantities are used to characterize the jets:
   the density contrast between the thermal gas contained in the jet source and the ambient gas,\

### 2022-01-06 paper.tex
update

@@
   By intentionally reducing the volume ratio of the jet source to an individual clump,\
-  we can diminish the effect of the randomness of the clumps on the bubbles.\
+  we can mitigate the effect of the randomness of the clumps on the bubbles.\
   Moreover, we resolve the jet source with the highest refinement level 11,\

### 2022-01-06 paper.tex
update

@@
 \begin{document}
-\title{The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study}
+\title{Title: A proof-of-concept study}
 
@@
   there is a lack of preferred orientation of jets with respect to the plane of the disc.\
-  A number of galaxies in which the jets are inclined to the disc normal\
+  A number of galaxies in which the jets are tilted to the disc normal\
   (e.g. NGC 3079, \citealt{Cecil2001}; NGC 1052, \citealt{Dopita2015}),\
@@
     \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp.png}
-    \caption{The slice of ...}
+    \caption{Comparison of the cases with (left) and without (right) the dense disk.\
+             In the both cases, the bipolar jets are injected at the origin along the $z=-y$ direction\
+             with a constant 4-velocity of 0.6 for a duration of 1.2 Myr.
+             The pressure (top), temperature (middle), and number density (bottom) slices\
+             through the jet source show that the dense disk not only helps the bubbles to align the disk normal\
+             but also create an under pressure, cold, and dense bubble in the most inner region.
+             }
     \label{fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp}

### 2022-01-06 paper.tex
update

@@
 \usepackage{url}
+\usepackage{floatrow}
+%\usepackage[FIGTOPCAP]{subfigure}
 \usepackage{subfigure}
@@
              The pressure (top), temperature (middle), and number density (bottom) slices\
-             through the jet source show that the dense disk not only helps the bubbles to align the disk normal\
-             but also create an under pressure, cold, and dense bubble in the most inner region.
+             through the jet sources show that the dense disk not only helps the bubbles to align the disk normal\
+             but also creates an under pressure, cold, and dense bubble in the most inner region.
              }
@@
 
+  %\begin{figure*}[ht]
   \begin{figure*}
-    \includegraphics[width=\linewidth]{figures/fig__xRay.png}
-    \caption{One-dimensional surface-brightness\
-             profiles in the same energy band\
-             , cut at various galactic latitudes (as labelled).\
-             For comparison, we also show ...}
-    \label{fig__xRay.png}
+    \subfigure[Simulated count rate (photons s$^{-1}$ deg$^{-2}$) map in the 0.6-1.0 keV range,\
+               using a Hammer-Aitoff projection.]
+     {
+      \includegraphics[width=\linewidth]{figures/fig__xray_0.8keV_angle_000.png}
+      \label{fig__xray_0.8keV_angle_000}
+     }
+    \subfigure[Comparison of observed (black; \citealt{Predehl2020}) and simulated (red) one-dimensional\
+               count rate profiles in the same energy band as \Cref{fig__xray_0.8keV_angle_000},\
+               cut at various galactic latitudes (as labelled).]
+     {
+      \includegraphics[width=\linewidth]{figures/fig__x-ray-profile-0.8keV-000.png}
+      \label{fig__x-ray-profile-0.8keV-000}
+     }
+    \caption{dddd}
+    \label{fig_xray}
   \end{figure*}

### 2022-01-06 paper.tex
update

@@
 take into account the perspective projection effect,
-we integrate the emissivity over line-of-sights from the solar position:
+we integrate the emissivity over line-of-sights from the solar position at $(x,y,z)=(8,0,0)$ kpc:
 \begin{equation}

### 2022-01-07 paper.tex
update

@@
   \begin{figure*}
-    \subfigure[Simulated count rate (photons s$^{-1}$ deg$^{-2}$) map in the 0.6-1.0 keV range,\
-               using a Hammer-Aitoff projection.]
+    \subfigure[Synthetic count rate (photons s$^{-1}$ deg$^{-2}$) in the 0.6-1.0 keV range,\
+               using a Hammer-Aitoff projection. Throughout this paper we show sky maps in\
+               Galactic coordinates centered on the Galactic center.]
      {
@@
      }
-    \caption{dddd}
+    \caption{}
     \label{fig_xray}

### 2022-01-07 figures/combine_xRay.sh

@@ -1,5 +1,8 @@
-convert fig__x-ray-profile-0.8keV-000.png -resize 1334x fig__x-ray-profile-0.8keV-000-resize.png
+convert fig__xray_0.8keV_observed.png -resize 1100x fig__xray_0.8keV_observed-resize.png
 
-convert -trim fig__xray_0.8keV_angle_000.png fig__x-ray-profile-0.8keV-000-resize.png -smush 10 fig__xRay.png
+convert -size 1320x1200 \
+        -page 0x0 fig__xray_0.8keV_observed-resize.png  \
+        -page 50x50 fig__xray_0.8keV_angle_000.png  \
+        -layers flatten  fig__xRayMap.png
 
-rm fig__x-ray-profile-0.8keV-000-resize.png
+rm fig__xray_0.8keV_observed-resize.png

### 2022-01-07 paper.tex
update

@@
 
-  \begin{figure}
-    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp.png}
-    \caption{Comparison of the cases with (left) and without (right) the dense disk.\
-             In the both cases, the bipolar jets are injected at the origin along the $z=-y$ direction\
+  \begin{figure*}
+    \includegraphics[width=\linewidth]{figures/fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp.png}
+    \caption{
+             Comparison between the case with the clumpy (the first column from the left)\
+             and smooth disk (the second) in the stratified atmosphere\
+             shows that the density distribution of the dense disk has insignificant effect\
+             on the overall dynamics of the bubbles. However, the bubbles with the smooth disk (the third)\
+             in a uniform atmosphere is spherical-shape,\
+             suggesting the stratified ambient helps to elongate bubbles notably.\
+             Moreover, the rightmost column shows that the bubbles without the disk is tilted even\
+             in the stratified atmosphere, indicating the dense disk is a crucial component\
+             for the formation of axis-symmetric bubbles.\
+             In all the cases, the bipolar jets are injected at the origin along the $z=-y$ direction\
              with a constant 4-velocity of 0.6 for a duration of 1.2 Myr.
@@
              but also creates an under pressure, cold, and dense bubble in the most inner region.
+             % , undetected by any telescopes (frame the inner bubble)
              }
     \label{fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp}
-  \end{figure}
+  \end{figure*}
 

### 2022-01-08 paper.tex
update

--- 2022-01-07 paper.tex
@@
     \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp.png}
-    \caption{Comparison of the cases with (left) and without (right) the dense disk.\
-             In the both cases, the bipolar jets are injected at the origin along the $z=-y$ direction\
-             with a constant 4-velocity of 0.6 for a duration of 1.2 Myr.
+    \caption{
+             Comparison between the case with a clumpy (first column from left)\
+             and a smooth disk (second) in a stratified atmosphere\
+             shows that the density distribution of the dense disk has insignificant effect\
+             on the overall dynamics of the bubbles. However, the bubbles with the smooth disk (third)\
+             in an uniform atmosphere is spherical-shape,\
+             suggesting the stratification facilitate bubbles elongation.\
+             The rightmost column shows that the bubbles without disk is tilted even\
+             in the stratified atmosphere, indicating dense disk is a crucial component\
+             for axis-symmetric bubbles formation.\
+             In all cases, bipolar jets are injected at the origin along $z=-y$ direction\
+             for a duration of 1.2 Myr.
              The pressure (top), temperature (middle), and number density (bottom) slices\
-             through the jet sources show that the dense disk not only helps the bubbles to align the disk normal\
-             but also creates an under pressure, cold, and dense bubble in the most inner region.
+             through jet sources show that the under pressure, cold, and dense bubbles (dashed box)\
+             only appear if disk is present.
              }

### 2022-01-08 paper.tex
update

--- 2022-01-07 paper.tex
@@
 \affiliation{Physics Division, National Center for Theoretical Sciences, Taipei 10617, Taiwan}
+
+\author{Chun-Yen Chen}
+\affiliation{Institute of physics, National Taiwan University, Taipei 10617, Taiwan}
 
@@
     \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp.png}
-    \caption{Comparison of the cases with (left) and without (right) the dense disk.\
-             In the both cases, the bipolar jets are injected at the origin along the $z=-y$ direction\
-             with a constant 4-velocity of 0.6 for a duration of 1.2 Myr.
+    \caption{
              The pressure (top), temperature (middle), and number density (bottom) slices\
-             through the jet sources show that the dense disk not only helps the bubbles to align the disk normal\
-             but also creates an under pressure, cold, and dense bubble in the most inner region.
+             through a bipolar jet sources injecting along $z=-y$ direction from\
+             the origin for a duration of 1.2 Myr under four different circumstances.\
+             Comparison between the cases with a clumpy (first column from left)\
+             and a smooth disk (second) in a stratified atmosphere\
+             shows that the density distribution of the dense disk has insignificant effect\
+             on the overall dynamics of the bubbles. However, the bubbles with the smooth disk (third)\
+             in an uniform atmosphere is spherical-shape,\
+             suggesting the stratification facilitates bubbles elongation significantly.\
+
+             The first three and the rightmost columns shows that the under pressure, cold, and dense bubbles
+             the bubbles without disk is tilted even\
+             in the stratified atmosphere, and
+
+             and the under pressure, cold, and dense bubbles (dashed box)\
+             is also evident in the first three columns,
+
+             indicating dense disk is a crucial component for axis-symmetric bubbles formation.\
+
+             Comparing all cases show that the under pressure, cold, and dense bubbles (dashed box)\
+             ionly appear if disk is present.
+
+             The first three diagrams and the rightmost diagram show that the air bubbles can only be generated\
+             with the disk and without the disk, the air bubbles will be skewed.
              }

### 2022-01-08 paper.tex
update

--- 2022-01-08 paper.tex
@@
     \caption{
-             Comparison between the case with a clumpy (first column from left)\
-             and a smooth disk (second) in a stratified atmosphere\
+             The pressure (top), temperature (middle), and number density (bottom) slices\
+             through a bipolar jet sources injecting along $z=-y$ direction from\
+             the origin for a duration of 1.2 Myr under four different circumstances from left column to right.\
+             Comparison between the cases with a clumpy (first column from left)\
+             and with a smooth disk (second) in a stratified atmosphere\
              shows that the density distribution of the dense disk has insignificant effect\
-             on the overall dynamics of the bubbles. However, the bubbles with the smooth disk (third)\
+             on the overall dynamics of the bubbles. However, the outer bubbles with the smooth disk (third)\
              in an uniform atmosphere is spherical-shape,\
-             suggesting the stratification facilitate bubbles elongation.\
-             The rightmost column shows that the bubbles without disk is tilted even\
-             in the stratified atmosphere, indicating dense disk is a crucial component\
-             for axis-symmetric bubbles formation.\
-             In all cases, bipolar jets are injected at the origin along $z=-y$ direction\
-             for a duration of 1.2 Myr.
-             The pressure (top), temperature (middle), and number density (bottom) slices\
-             through jet sources show that the under pressure, cold, and dense bubbles (dashed box)\
-             only appear if disk is present.
+             suggesting the stratification facilitates the outer bubbles elongation significantly.\
+             Also, the first three and the rightmost columns show that the most inner bubbles (dashed box)\
+             can only appear with the disk, and without the disk, the outer bubbles will be tilted,
+             indicating the dense disk is a crucial component for\
+             the formation of the axis-symmetrically outer bubbles and of the most inner bubbles.
              }

### 2022-01-09 paper.tex
update

--- 2022-01-08 paper.tex
@@
     \caption{
-             Comparison between the case with a clumpy (first column from left)\
-             and a smooth disk (second) in a stratified atmosphere\
+             The pressure (top), temperature (middle), and number density (bottom) slices\
+             through a bipolar jet sources injecting along $z=-y$ direction from\
+             the origin for a duration of 1.2 Myr under four different cases from left to right.\
+             Comparison between the cases with a clumpy (first column from left)\
+             and with a smooth disk (second) in a stratified atmosphere\
              shows that the density distribution of the dense disk has insignificant effect\
-             on the overall dynamics of the bubbles. However, the bubbles with the smooth disk (third)\
-             in an uniform atmosphere is spherical-shape,\
-             suggesting the stratification facilitate bubbles elongation.\
-             The rightmost column shows that the bubbles without disk is tilted even\
-             in the stratified atmosphere, indicating dense disk is a crucial component\
-             for axis-symmetric bubbles formation.\
-             In all cases, bipolar jets are injected at the origin along $z=-y$ direction\
-             for a duration of 1.2 Myr.
-             The pressure (top), temperature (middle), and number density (bottom) slices\
-             through jet sources show that the under pressure, cold, and dense bubbles (dashed box)\
-             only appear if disk is present.
+             on the overall dynamics of the bubbles. However, the outer bubbles with the smooth disk\
+             in an uniform atmosphere (third) is spherical-shape,\
+             suggesting the stratification facilitates the outer bubbles elongation significantly.\
+             Also, the first three and the rightmost columns show that the most inner bubbles (dashed box)\
+             can only appear with the disk, and without the disk, the outer bubbles will be tilted,
+             indicating the dense disk is a crucial component for\
+             the axis-symmetrically outer bubbles and of the most inner bubbles formation.
              }

### 2022-01-09 paper.tex
update

@@
              can only appear with the disk, and without the disk, the outer bubbles will be tilted,
-             indicating the dense disk is a crucial component for\
+             indicating the dense disk is crucial for\
              the axis-symmetrically outer bubbles and of the most inner bubbles formation.

### 2022-01-09 paper.tex
update

@@
              and with a smooth disk (second) in a stratified atmosphere\
-             shows that the density distribution of the dense disk has insignificant effect\
-             on the overall dynamics of the bubbles. However, the outer bubbles with the smooth disk\
+             shows that the initial density distribution of the dense disk has insignificant effect\
+             on the overall dynamics of bubbles. However, the outer bubbles with the smooth disk\
              in an uniform atmosphere (third) is spherical-shape,\

### 2022-01-11 figures/combine_xRay.sh
update

@@ -1,8 +1,1 @@
-convert fig__xray_0.8keV_observed.png -resize 1100x fig__xray_0.8keV_observed-resize.png
-
-convert -size 1320x1200 \
-        -page 0x0 fig__xray_0.8keV_observed-resize.png  \
-        -page 50x50 fig__xray_0.8keV_angle_000.png  \
-        -layers flatten  fig__xRayMap.png
-
-rm fig__xray_0.8keV_observed-resize.png
+convert fig__xray_0.8keV_observed.png -resize x570 fig__xray_0.8keV_observed-resize.png

### 2022-01-11 figures/combine_xRay.sh
update

@@ -1,1 +1,1 @@
-convert fig__xray_0.8keV_observed.png -resize x570 fig__xray_0.8keV_observed-resize.png
+convert fig__xray_0.8keV_observed.png -resize x463 fig__xray_0.8keV_observed-resize.png

### 2022-01-12 figures/combine_xRay.sh
update

@@ -1,1 +1,4 @@
-convert fig__xray_0.8keV_observed.png -resize x463 fig__xray_0.8keV_observed-resize.png
+convert fig__xray_0.8keV_observed.png -resize 945x470! fig__xray_0.8keV_observed-resize.png
+
+
+composite -geometry +120+512  fig__xray_0.8keV_observed-resize.png  fig__xray_0.8keV_angle_000.png fig__xraymap.png

### 2022-01-12 paper.tex
update

@@
   \begin{figure*}
-    \subfigure[Synthetic count rate (photons s$^{-1}$ deg$^{-2}$) in the 0.6-1.0 keV range,\
+    \subfigure[(Reproduced with permission from R. Blatt, Rev. Mod. Phys. 87, 1419 (2015).\
+               Copyright 2015 American Physical Society.)\
+               Synthetic count rate (photons s$^{-1}$ deg$^{-2}$) in the 0.6-1.0 keV range,\
                using a Hammer-Aitoff projection. Throughout this paper we show sky maps in\
-               Galactic coordinates centered on the Galactic center.]
+               Galactic coordinates centered on the Galactic center, and the view point .]
      {
-      \includegraphics[width=\linewidth]{figures/fig__xray_0.8keV_angle_000.png}
+      \includegraphics[width=0.8\linewidth]{figures/fig__xraymap.png}
       \label{fig__xray_0.8keV_angle_000}
@@
 The CRe spectrum follows a power law distribution\
-with a spectral index $p=2$ and ranges from\
+with a spectral index $p=2.4$ \citep{Selig2015} and ranges from\
 $m_{\text{e}}c^2$ ($0.5$ MeV) to $10^{6}m_{\text{e}}c^2$ ($0.5$ TeV).\
@@
 \begin{figure*}
-  \includegraphics[width=\linewidth]{figures/fig__gammaRay.png}
-  \caption{The simulated photon flux at  2 GeV (top), 10 GeV (middle), and 100 GeV (bottom).}
+  \includegraphics[width=\linewidth]{figures/fig__GammaRay.png}
+  \caption{The observed (left) and simulated (right) photon flux at 1.7 GeV (top), 13.6 GeV (middle), and 108.6 GeV (bottom).\
+           Note that the panels on left side are diffuse (i.e. no point-like component)\
+           photon flux reconstructed by the D$^3$PO algorithm \citep{Selig2015} that analyze\
+           the photon data from the \textit{Fermi} Large Area Telescope \citep{Atwood2009}.
+  }
   \label{fig__gammaRay}

### 2022-01-20 paper.tex
update

@@
 \author[0000-0003-3269-4660]{H.-Y. Karen Yang}
-\affiliation{Institute of Astronomy and Department of Physics, National Tsing Hua University, Hsinchu 30013, Taiwan}
+\affiliation{Institute of Astronomy, National Tsing Hua University, Hsinchu 30013, Taiwan}
+\affiliation{Center for Informatics and Computation in Astronomy, National Tsing Hua University, Hsinchu 30013, Taiwan}
+\affiliation{Physics Division, National Center for Theoretical Sciences, Taipei 10617, Taiwan}
 
@@
      {
-      \includegraphics[width=\linewidth]{figures/fig__x-ray-profile-0.8keV-000.png}
+      \includegraphics[width=\linewidth]{figures/fig__xray-profile-0.8keV-000.png}
       \label{fig__x-ray-profile-0.8keV-000}
@@
 \begin{figure*}
-  \includegraphics[width=\linewidth]{figures/fig__GammaRay.png}
+  \includegraphics[width=\linewidth]{figures/fig__GammaRay_100e9_1e6_angle_000.png}
   \caption{The observed (left) and simulated (right) photon flux at 1.7 GeV (top), 13.6 GeV (middle), and 108.6 GeV (bottom).\
@@
 \end{figure*}
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{figures/fig__spectrum.png}
+  \caption{The observed (left) and simulated (right) photon flux at 1.7 GeV (top), 13.6 GeV (middle), and 108.6 GeV (bottom).\
+           Note that the panels on left side are diffuse (i.e. no point-like component)\
+           photon flux reconstructed by the D$^3$PO algorithm \citep{Selig2015} that analyze\
+           the photon data from the \textit{Fermi} Large Area Telescope \citep{Atwood2009}.
+  }
+  \label{fig__gammaRay}
+\end{figure}
 

### 2022-01-25 paper.tex
update

@@
 
-  As stressed by \citet{Yang2012}, CR diffusion has insignificant effect on the overall morphology of the Fermi bubbles,\
+  As stressed by \citet{Yang2012}, CR diffusion has an insignificant effect on the overall morphology of the Fermi bubbles,\
   but only sharpens the edges of the simulated bubbles by the interplay between anisotropic CR diffusion\
@@
   the bubbles should be weak due to adiabatic expansion, and thus the magnetic fields has\
-  little effect on the overall dynamics. For these two reasons,\
+  a little effect on the overall dynamics. For these two reasons,\
   we have ignored the CR diffusion and the magnetic field throughout\
@@
              and with a smooth disk (second) in a stratified atmosphere\
-             shows that the initial density distribution of the dense disk has insignificant effect\
+             shows that the initial density distribution of the dense disk has an insignificant effect\
              on the overall dynamics of bubbles. However, the outer bubbles with the smooth disk\
@@
              Also, the first three and the rightmost columns show that the most inner bubbles (dashed box)\
-             can only appear with the disk, and without the disk, the outer bubbles will be tilted,
+             can only appear associated with the disk, and without the disk, the outer bubbles will be tilted,
              indicating the dense disk is crucial for\
@@
 
-  %\begin{figure*}[ht]
   \begin{figure*}
-    \subfigure[(Reproduced with permission from R. Blatt, Rev. Mod. Phys. 87, 1419 (2015).\
-               Copyright 2015 American Physical Society.)\
-               Synthetic count rate (photons s$^{-1}$ deg$^{-2}$) in the 0.6-1.0 keV range,\
-               using a Hammer-Aitoff projection. Throughout this paper we show sky maps in\
-               Galactic coordinates centered on the Galactic center, and the view point .]
+    \subfigure[Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
+               (photons s$^{-1}$ deg$^{-2}$) in the 0.6-1.0 keV range,\
+               using a Hammer-Aitoff projection. Throughout this paper we show sky maps\
+               in Galactic coordinates centered on the Galactic center and observed by the poistion of the Sun.\
+               The red arrow at the center of the\
+               top panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
+               to the disk normal in 1.2 Myr.]
      {
@@
   \includegraphics[width=\linewidth]{figures/fig__GammaRay_100e9_1e6_angle_000.png}
-  \caption{The observed (left) and simulated (right) photon flux at 1.7 GeV (top), 13.6 GeV (middle), and 108.6 GeV (bottom).\
-           Note that the panels on left side are diffuse (i.e. no point-like component)\
+  \caption{The observed (left) and simulated (right) photon flux at 108.6 GeV.\
+           Note that the panel on left side is diffuse (i.e. no point-like component)\
            photon flux reconstructed by the D$^3$PO algorithm \citep{Selig2015} that analyze\
@@
   \includegraphics[width=\linewidth]{figures/fig__spectrum.png}
-  \caption{The observed (left) and simulated (right) photon flux at 1.7 GeV (top), 13.6 GeV (middle), and 108.6 GeV (bottom).\
-           Note that the panels on left side are diffuse (i.e. no point-like component)\
-           photon flux reconstructed by the D$^3$PO algorithm \citep{Selig2015} that analyze\
-           the photon data from the \textit{Fermi} Large Area Telescope \citep{Atwood2009}.
+  \caption{
+      Simulated spectra of the Fermi bubbles calculated for a longitude range of\
+      $l=[-10^{\circ},10^{\circ}]$ for different latitude bins.\
+      The gray band represents the observational data of \citet{Ackermann2014}.
   }

### 2022-01-25 paper.tex
update

@@
 \section{Introduction}
+The \textit{Fermi} bubbles, two giant bubbles extending about 50 degrees above and below the Galactic center (GC),\
+are among the most important findings of the Fermi Gamma-ray Space Telescope\
+
 Early attempts to model the Fermi bubbles assumed that the jet is vertial to the Galactic plane...
@@
                using a Hammer-Aitoff projection. Throughout this paper we show sky maps\
-               in Galactic coordinates centered on the Galactic center and observed by the poistion of the Sun.\
+               in Galactic coordinates centered on the Galactic center and observed by the solar position.\
                The red arrow at the center of the\
@@
 The CRe spectrum follows a power law distribution\
-with a spectral index $p=2.4$ \citep{Selig2015} and ranges from\
-$m_{\text{e}}c^2$ ($0.5$ MeV) to $10^{6}m_{\text{e}}c^2$ ($0.5$ TeV).\
+with a spectral index $p=2.4$ and ranges from\
+$m_{\text{e}}c^2$ ($0.5$ MeV) to $1.1\times10^{6}m_{\text{e}}c^2$ ($0.55$ TeV).\
 
@@
   \caption{The observed (left) and simulated (right) photon flux at 108.6 GeV.\
-           Note that the panel on left side is diffuse (i.e. no point-like component)\
-           photon flux reconstructed by the D$^3$PO algorithm \citep{Selig2015} that analyze\
-           the photon data from the \textit{Fermi} Large Area Telescope \citep{Atwood2009}.
+           Note that the left panel is the\
+           photon flux of the diffuse component reconstructed by the D$^3$PO algorithm \citep{Selig2015} that analyzes\
+           the photon data from the \textit{Fermi} Large Area Telescope \citep{Atwood2009}\
+           and removes the contribution from point-like component.
   }
@@
 
-\appendix
+%\appendix
 

### 2022-01-25 paper.tex
update

@@
 \section{Introduction}
-The \textit{Fermi} bubbles, two giant bubbles extending about 50 degrees above and below the Galactic center (GC),\
+A decade after the discovery of the \textit{Fermi} bubbles \citep{Su2012,Ackermann2014,Narayanan2017},\
+the high resolution X-ray map \citep{Predehl2020} from eROSITA \citep{Predehl2021} also shows\
+similar X-ray bubbles above and below the Galaxy,\
+but about twice as large as the Fermi bubbles, each having a diameter of about 45,000 lightyears.\
+
+The \textit{Fermi} and eROSITA bubbles, two couple giant bubbles extending about 50 degrees\
+above and below the Galactic center (GC),\
 are among the most important findings of the Fermi Gamma-ray Space Telescope\
+
+The Fermi bubbles and large-scale X-ray emission revealed by eROSITA\
+show remarkable morphological similarity.
 
@@
            Note that the left panel is the\
-           photon flux of the diffuse component reconstructed by the D$^3$PO algorithm \citep{Selig2015} that analyzes\
+           photon flux of the diffuse component reconstructed by the D$^3$PO\
+           algorithm \citep{Selig2015} that analyzes\
            the photon data from the \textit{Fermi} Large Area Telescope \citep{Atwood2009}\
@@
 %\appendix
+% https://heasarc.gsfc.nasa.gov/docs/objects/heapow/archive/normal_galaxies/fermibubbles_erosita.html
+
+%Jet_SrcVel 0.6
+%Jet_SrcDens 1e-26
+%Jet_SrcTemp 2e10
+%Jet_SrcPres => 1.6e-8
 

### 2022-01-25 paper.tex
update

@@
      }
-    \subfigure[Comparison of observed (black; \citealt{Predehl2020}) and simulated (red) one-dimensional\
+    \subfigure[Comparison of simulated (red) and observed (black; \citealt{Predehl2020}) one-dimensional\
                count rate profiles in the same energy band as \Cref{fig__xray_0.8keV_angle_000},\
@@
      {
-      \includegraphics[width=\linewidth]{figures/fig__xray-profile-0.8keV-000.png}
+      \includegraphics[width=0.8\linewidth]{figures/fig__xray-profile-0.8keV-000.png}
       \label{fig__x-ray-profile-0.8keV-000}

### 2022-01-26 paper.tex
update

@@
 \begin{document}
-\title{Title: A proof-of-concept study}
+\title{The symmetric \textit{Fermi} and eROSITA bubbles problem: A proof-of-concept study}
 
@@
 \section{Introduction}
-A decade after the discovery of the \textit{Fermi} bubbles \citep{Su2012,Ackermann2014,Narayanan2017},\
+Over the last decade the discovery of the \textit{Fermi} bubbles \citep{Su2012,Ackermann2014,Narayanan2017},\
 the high resolution X-ray map \citep{Predehl2020} from eROSITA \citep{Predehl2021} also shows\
@@
 
-\subsubsection{Hadronic process}
-In the hadronic model, CRp undergo hadronic collisions with thermal gas protons\
-and produce $\gamma$-ray via pion decay. The volume emissivity of the emission can be written as
-\begin{equation}
-   \epsilon \propto U_{\text{CRp}}n_{p}\sigma_{p}\kappa_{pp}.
-\end{equation}
-
-\begin{equation}
-  \frac{dE}{dtd\epsilon_{1}dV} =\
-   cn_{H}pC\left(\frac{\epsilon_{1}}{m_{\text{p}}c^2}\right)^{-p}\
-   \int_{0}^{1}\sigma(\epsilon_{\text{p}}) F(x,\epsilon_{\text{p}}) x^{p}dx.
-\end{equation}
-
-\begin{equation}
-\sigma(\epsilon_{\text{p}})=34.3+1.88L+0.25L^{2}\left[1-\frac{E_{\text{threshold}}}{E_{\text{p}}}\right]^{4} \text{ mb}.
-\end{equation}
-
-\begin{equation}
-F(x,\epsilon_{\text{p}})=B\frac{d}{dx}\left[\ln(x)\left(\frac{1-x^{\beta}}{1+kx^{\beta}\left(1-x^{\beta}\right)}\right)^4\right],
-\end{equation}
-
-where
-$x=\epsilon_{1}/\epsilon_{\text{p}}$, $B=1.30+0.14L+0.011L^2$, $\beta=\left(1.79+0.11L+0.008L^{2}\right)^{-1}$,\
-$\left(0.801+0.049L+0.014L^{2}\right)^{-1}$, $L=\ln(\epsilon_{\text{p}}/1 \text{ TeV})$.
+%\subsubsection{Hadronic process}
+%In the hadronic model, CRp undergo hadronic collisions with thermal gas protons\
+%and produce $\gamma$-ray via pion decay. The volume emissivity of the emission can be written as
+%\begin{equation}
+%   \epsilon \propto U_{\text{CRp}}n_{p}\sigma_{p}\kappa_{pp}.
+%\end{equation}
+%
+%\begin{equation}
+%  \frac{dE}{dtd\epsilon_{1}dV} =\
+%   cn_{H}pC\left(\frac{\epsilon_{1}}{m_{\text{p}}c^2}\right)^{-p}\
+%   \int_{0}^{1}\sigma(\epsilon_{\text{p}}) F(x,\epsilon_{\text{p}}) x^{p}dx.
+%\end{equation}
+%
+%\begin{equation}
+%\sigma(\epsilon_{\text{p}})=34.3+1.88L+0.25L^{2}\left[1-\frac{E_{\text{threshold}}}{E_{\text{p}}}\right]^{4} \text{ mb}.
+%\end{equation}
+%
+%\begin{equation}
+%F(x,\epsilon_{\text{p}})=B\frac{d}{dx}\left[\ln(x)\left(\frac{1-x^{\beta}}{1+kx^{\beta}\left(1-x^{\beta}\right)}\right)^4\right],
+%\end{equation}
+%
+%
+%where
+%$x=\epsilon_{1}/\epsilon_{\text{p}}$, $B=1.30+0.14L+0.011L^2$, $\beta=\left(1.79+0.11L+0.008L^{2}\right)^{-1}$,\
+%$\left(0.801+0.049L+0.014L^{2}\right)^{-1}$, $L=\ln(\epsilon_{\text{p}}/1 \text{ TeV})$.
 

### 2022-01-28 paper.tex
update

@@
              initial number density within the disk without jet source.\
-             The regions covered by vertical bands represent the allowable number densities \citep{peak-ism-density} for\
+             The vertical bands represent the allowable number densities \citep{peak-ism-density} for\
              hot ionized, warm neutral (WNM), warm ionized (WIM), cold nuetral mediums (CNM), and molecular clouds.}
@@
   \caption{
-      Simulated spectra of the Fermi bubbles calculated for a longitude range of\
-      $l=[-10^{\circ},10^{\circ}]$ for different latitude bins.\
-      The gray band represents the observational data of \citet{Ackermann2014}.
+      Simulated gamma-ray spectra (top) of the Fermi bubbles calculated for a longitude range of\
+      $|l|<10^{\circ}$ for different latitude bins.\
+      The gray band represents the observational data of \citet{Ackermann2014}.\
+      Microwave spectra (bottom) averaged over $|l|<10^{\circ}$, $20^{\circ}<|b|<30^{\circ}$.\
+      The data point represents the \textit{WMAP} data in the 23 GHz K band and the shaded area indicates the range\
+      of synchrotron spectral indices allowed for the \textit{WMAP} haze \citep{Dobler_2008}.
   }

### 2022-01-28 paper.tex
update

@@
              initial number density within the disk without jet source.\
-             The vertical bands represent the allowable number densities \citep{peak-ism-density} for\
+             The vertical bands represent from left to right: the allowable number densities \citep{peak-ism-density} for\
              hot ionized, warm neutral (WNM), warm ionized (WIM), cold nuetral mediums (CNM), and molecular clouds.}

### 2022-01-28 paper.tex
update

@@
 
+  To quantify the synchrotron radiation as a function of position, it\
+  is essential to start the simulation with a more realistic magnetic\
+  field distribution. To this end, for our fixed magnetic field we adopt\
+  the default exponential model in \textsc{galprop} \citep{Strong2007}
+  which has the following spatial dependence:\
+
+  \begin{equation}
+     |\mathbf{B}(R, z)|=B_{0}\exp{-z/z_{0}}\exp{-R/R_{0}},
+  \end{equation}
+
+  where $R=\sqrt{x^{2}+y^{2}}$, $B_{0}$ is the average field strength at the GC\
+  and $z_{0}$ and $R_{0}$ are the characteristic scales in the vertical and radial\
+  directions, respectively. We adopt $z_{0} = 2$ kpc and $R_{0} = 10$ kpc, which\
+  are best-fitting values in the \textsc{galprop} model to reproduce the\
+  observed large-scale 408 MHz synchrotron radiation in the Galaxy.\
+  We choose $B_{0} = 50$ $\mu$G based on the observed field strength at the\
+  GC \citep{Crocker2010}.
+
    % The dispersion:
@@
 with a spectral index $p=2.4$ and ranges from\
-$m_{\text{e}}c^2$ ($0.5$ MeV) to $1.1\times10^{6}m_{\text{e}}c^2$ ($0.55$ TeV).\
+$m_{\text{e}}c^2$ ($0.5$ MeV) to $1.1\times10^{6}m_{\text{e}}c^2$ ($550$ GeV).\
 
@@
   \caption{
-      Simulated gamma-ray spectra (top) of the Fermi bubbles calculated for a longitude range of\
+      Simulated gamma-ray spectra (colored lines in top panel) of the Fermi bubbles calculated for a longitude range of\
       $|l|<10^{\circ}$ for different latitude bins.\
       The gray band represents the observational data of \citet{Ackermann2014}.\
-      Microwave spectra (bottom) averaged over $|l|<10^{\circ}$, $20^{\circ}<|b|<30^{\circ}$.\
+      Simulated microwave spectra (colored lines in bottom) averaged over $|l|<10^{\circ}$, $20^{\circ}<|b|<30^{\circ}$.\
       The data point represents the \textit{WMAP} data in the 23 GHz K band and the shaded area indicates the range\

### 2022-01-28 paper.tex
update

@@
     \includegraphics[width=\columnwidth]{figures/fig__zoom-in-disk.png}
-    \caption{Close-up view of the\
+    \caption{Close-up view of the initial\
              pressure (top), temperature (middle), and number density (bottom) slices\

### 2022-01-29 paper.tex
update

@@
 
-\begin{figure}
+\begin{figure*}
   \includegraphics[width=\linewidth]{figures/fig__spectrum.png}
   \caption{
-      Simulated gamma-ray spectra (colored lines in top panel) of the Fermi bubbles calculated for a longitude range of\
+      Simulated gamma-ray spectra (colored lines in right column) of the Fermi bubbles calculated for a longitude range of\
       $|l|<10^{\circ}$ for different latitude bins.\
       The gray band represents the observational data of \citet{Ackermann2014}.\
-      Simulated microwave spectra (colored lines in bottom) averaged over $|l|<10^{\circ}$, $20^{\circ}<|b|<30^{\circ}$.\
+      Simulated microwave spectra (colored lines in left) averaged over $|l|<10^{\circ}$, $20^{\circ}<|b|<30^{\circ}$.\
       The data point represents the \textit{WMAP} data in the 23 GHz K band and the shaded area indicates the range\
@@
   \label{fig__gammaRay}
-\end{figure}
+\end{figure*}
 

### 2022-02-02 paper.tex
update

@@
 \section{Introduction}
-Over the last decade the discovery of the \textit{Fermi} bubbles \citep{Su2012,Ackermann2014,Narayanan2017},\
-the high resolution X-ray map \citep{Predehl2020} from eROSITA \citep{Predehl2021} also shows\
-similar X-ray bubbles above and below the Galaxy,\
-but about twice as large as the Fermi bubbles, each having a diameter of about 45,000 lightyears.\
+The detection of the \textit{Fermi} bubbles \citep{Su2012,Ackermann2014,Narayanan2017},\
+two giant bubbles symmetrically extending about 50 degrees above and below the Galactic center,
+is one of the great discoveries made with \textit{Fermi} Large Area Telescope \citep{Atwood2009}.
 
-The \textit{Fermi} and eROSITA bubbles, two couple giant bubbles extending about 50 degrees\
-above and below the Galactic center (GC),\
-are among the most important findings of the Fermi Gamma-ray Space Telescope\
+The gamma-ray emission of the Fermi bubbles is observed in the energy range\
+of $1\lesssim E_{\gamma} \lesssim 100$ GeV and has an almost spatially uniform hard\
+spectrum, sharp edges and an approximately flat brightness distribution.\
 
-The Fermi bubbles and large-scale X-ray emission revealed by eROSITA\
-show remarkable morphological similarity.
+Over the course of a decade,\
+the first all-sky survey X-ray data with high-spatial resolution \citep{Predehl2021}\
+from eROSITA \citep{Predehl2020} also reveals\
+a large hourglass-shaped structure (eROSITA bubbles, hereafter) at the GC,\
+symmetrically extending about 80 degress above and below GC.
+
+The large-scale X-ray structure\
+shows that the intrinsic size of the bubbles is 14 kiloparsecs across \citep{Predehl2021},
+and has remarkable morphological similarities to the Fermi bubbles.
+
+The Fermi and eROSITA bubbles (collectiely we called the Galactic bubbles)
 

### 2022-02-02 paper.tex
update

@@
 The detection of the \textit{Fermi} bubbles \citep{Su2012,Ackermann2014,Narayanan2017},\
-two giant bubbles symmetrically extending about 50 degrees above and below the Galactic center,
+two large bubbles symmetrically extending about 50 degrees above and below the Galactic center,
 is one of the great discoveries made with \textit{Fermi} Large Area Telescope \citep{Atwood2009}.
@@
 from eROSITA \citep{Predehl2020} also reveals\
-a large hourglass-shaped structure (eROSITA bubbles, hereafter) at the GC,\
+a giant hourglass-shaped structure (eROSITA bubbles, hereafter) at the GC,\
 symmetrically extending about 80 degress above and below GC.
@@
 shows that the intrinsic size of the bubbles is 14 kiloparsecs across \citep{Predehl2021},
-and has remarkable morphological similarities to the Fermi bubbles.
+and has remarkable morphological symmetry about the Galactic plane as the Fermi bubbles.
 
-The Fermi and eROSITA bubbles (collectiely we called the Galactic bubbles)
+Their symmetry about the GC suggests that they originate\
+from powerful energy injections from the GC, possibly related to nuclear star formation\
+\citep{PhysRevLett.106.101102,Carretti2013}
+or past active galactic nucleus (AGN) activity \citep{Guo2012,Yang2017}.
 
-Early attempts to model the Fermi bubbles assumed that the jet is vertial to the Galactic plane...
+Early attempts to model the Fermi and eROSITA bubbles (collectiely we called the Galactic bubbles)\
+assumed that the jet is vertial to the Galactic plane...
 

### 2022-02-03 paper.tex
update

@@
 \begin{document}
-\title{The symmetric \textit{Fermi} and eROSITA bubbles problem: A proof-of-concept study}
+\title{The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study}
 
@@
 The detection of the \textit{Fermi} bubbles \citep{Su2012,Ackermann2014,Narayanan2017},\
-two large bubbles symmetrically extending about 50 degrees above and below the Galactic center,
+two large bubbles symmetrically extending about 50 degrees above and below the Galactic plane,
 is one of the great discoveries made with \textit{Fermi} Large Area Telescope \citep{Atwood2009}.
@@
 from eROSITA \citep{Predehl2020} also reveals\
-a giant hourglass-shaped structure (eROSITA bubbles, hereafter) at the GC,\
-symmetrically extending about 80 degress above and below GC.
+a giant hourglass-shaped structure (eROSITA bubbles hereafter) at the GC,\
+but extending about twice as large as the Fermi bubbles.
 
@@
 shows that the intrinsic size of the bubbles is 14 kiloparsecs across \citep{Predehl2021},
-and has remarkable morphological symmetry about the Galactic plane as the Fermi bubbles.
+and displays morphological symmetry about the Galactic plane as the Fermi bubbles.
 
@@
 
-Early attempts to model the Fermi and eROSITA bubbles (collectiely we called the Galactic bubbles)\
-assumed that the jet is vertial to the Galactic plane...
+Early attempts to model the Fermi and eROSITA bubbles (collectiely we call the Galactic bubbles)\
+assumed that the jet is vertial to the Galactic plane. However,\
+observation \citep{Gallimore2006} has proposed that\
+there is a lack of preferred orientation of jets with respect to the plane of the disc.\
+A number of galaxies in which the jets are tilted to the disc normal\
+(e.g. NGC 3079, \citealt{Cecil2001}; NGC 1052, \citealt{Dopita2015}),\
+including galaxies in which the jets lie in the plane of the disc (e.g. IC 5063, \citealt{Morganti2015}).
+
+To this end, this work consider a dense thin disk of interstellar medium\
+around a jet source, in an attempt to remedy the symmetry problem of the Galactic bubbles.\
+
+We perform three-dimensional special relativistic hydrodynamics simulations\
+of the formation of the Galactic bubbles by CR jet injections\
+from the central SMBH in the Galaxy.
+
+This paper is organized as follows. We introduce
 
@@
 \subsection{Inclined jet injection}
-  Early observation \citep{Gallimore2006} has proposed that\
-  there is a lack of preferred orientation of jets with respect to the plane of the disc.\
-  A number of galaxies in which the jets are tilted to the disc normal\
-  (e.g. NGC 3079, \citealt{Cecil2001}; NGC 1052, \citealt{Dopita2015}),\
-  including galaxies in which the jets lie in the plane of the disc (e.g. IC 5063, \citealt{Morganti2015}).
 

### 2022-02-03 paper.tex
update

@@
 
-To this end, this work consider a dense thin disk of interstellar medium\
+To this end, this work introduces a dense thin disk of interstellar medium\
 around a jet source, in an attempt to remedy the symmetry problem of the Galactic bubbles.\
+The thin disk contains a reservoir of dense molecular/atomic gas, resulting in\
 
@@
 
-This paper is organized as follows. We introduce
+This paper is organized as follows.\
+In Section \ref{Methodology}, we describe the numerical techniques and initial conditions employed.\
+We directly compare the morphology of the Galactic bubbles with observation,\
+and also show the simulated gamma-ray and microwave spectra compared with observations\
+in Section \ref{Results}.
+Finally, we summarize our findings in Section \ref{Conclusions}.
 
 \section{Methodology}
-
+\label{Methodology}
   We used the GPU-accelerated special relativistic hydrodynamics AMR code (\textsc{gamer-sr}) developed at the\
@@
 \section{Results}
-
+\label{Results}
   \begin{figure}
@@
 
-\section{conclusions}
+\section{Conclusions}
+\label{Conclusions}
 

### 2022-02-03 paper.tex
update

@@
 Over the course of a decade,\
-the first all-sky survey X-ray data with high-spatial resolution \citep{Predehl2021}\
+the first all-sky X-ray survey with high-spatial resolution \citep{Predehl2021}\
 from eROSITA \citep{Predehl2020} also reveals\
 a giant hourglass-shaped structure (eROSITA bubbles hereafter) at the GC,\
-but extending about twice as large as the Fermi bubbles.
-
+but extending about twice as large as the Fermi bubbles.\
 The large-scale X-ray structure\

### 2022-02-03 paper.tex
update

@@
 
-Early attempts to model the Fermi and eROSITA bubbles (collectiely we call the Galactic bubbles)\
+Early attempts \citep{Sarkar2015,Yang2017,Zhang2020}\
+to model the Fermi and eROSITA bubbles (collectiely we call the Galactic bubbles)\
 assumed that the jet is vertial to the Galactic plane. However,\
@@
 To this end, this work introduces a dense thin disk of interstellar medium\
-around a jet source, in an attempt to remedy the symmetry problem of the Galactic bubbles.\
-The thin disk contains a reservoir of dense molecular/atomic gas, resulting in\
+around a jet source to deflects and decelerates the jets,\
+in an attempt to remedy the symmetry problem of the Galactic bubbles.\
 
@@
 \label{Conclusions}
+We have found qualitative similarities between the results our simulations\
+and the observed spectrum and morphological structure of the Galactic bubbles.
+
+Since the jets encounter a larger column depth of cloudsalong their path,\
+they interact more strongly with the dense ISM.\
+The jets do not immediately clear a channel along the inclined axis of launch.\
+Rather, the dense clouds deflect the jets, which then decelerate\
+and launch a sub-relativistic outflow along the minor axis following the path of least resistance.
 

### 2022-02-03 paper.tex
update

@@
 
-We perform three-dimensional special relativistic hydrodynamics simulations\
-of the formation of the Galactic bubbles by CR jet injections\
-from the central SMBH in the Galaxy.
+The main purpose of this study is to use three-dimensional\
+special relativistic hydrodynamics simulations\
+involving CR jet injections from the central SMBH in the Galaxy to investigate\
+whether the jet scenario is able to produce symmetric Galactic bubbles that are\
+consistent with the observed features, including the shape, the\
+flat surface brightness, and the sharp edges.\
 

### 2022-02-04 paper.tex
update

@@
 Early attempts \citep{Sarkar2015,Yang2017,Zhang2020}\
-to model the Fermi and eROSITA bubbles (collectiely we call the Galactic bubbles)\
-assumed that the jet is vertial to the Galactic plane. However,\
+to model the symmetric Fermi and eROSITA bubbles (collectively we call the Galactic bubbles)\
+assumed that the jet is vertical to the Galactic plane. However,\
 observation \citep{Gallimore2006} has proposed that\

### 2022-02-04 paper.tex
update

@@
 observation \citep{Gallimore2006} has proposed that\
-there is a lack of preferred orientation of jets with respect to the plane of the disc.\
+there is a lack of preferred orientation of jets with respect to a disc normal.\
 A number of galaxies in which the jets are tilted to the disc normal\
@@
 
-To this end, this work introduces a dense thin disk of interstellar medium\
+To this end, this work introduces a dense thin disc of interstellar medium\
 around a jet source to deflects and decelerates the jets,\
@@
   Since the relativistic fluid ejected by the jet source\
-  is quickly stalled off and slowed down by a dense ISM disk in a short time,\
+  is quickly stalled off and slowed down by a dense ISM disc in a short time,\
   and the relativistic fluid\
@@
   With the help of the isothermal and hydrostatic equilibrium conditions,\
-  and assuming the interfaces between isothermal disk and atmosphere are in thermal pressure equilibrium,\
+  and assuming the interfaces between isothermal disc and atmosphere are in thermal pressure equilibrium,\
   we can write the steady-state gaseous density distributions,\
-  confined in the total potential, of the disk and the Galactic atmosphere as\
+  confined in the total potential, of the disc and the Galactic atmosphere as\
   \begin{subequations}
@@
      \displaystyle \rho_{\text{isoDisk}}(z) = \rho_{\text{isoDisk}}^{\text{peak}}
-     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{isoDisk}}/m_{\text{p}}}\right]&\label{isothermal-disk-density}\\
+     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{isoDisk}}/m_{\text{p}}}\right]&\label{isothermal-disc-density}\\
      \text{, if $|z| < z_{0}$}& \nonumber \\
@@
   \end{align}
-  \label{disk-atm-sys}
+  \label{disc-atm-sys}
   \end{subequations}
   where $m_{\text{p}}$ is the proton mass,\
-  $T_{\text{isoDisk}}$ and $T_{\text{atmp}}$ is the temperature of the isothermal disk and atmosphere,\
+  $T_{\text{isoDisk}}$ and $T_{\text{atmp}}$ is the temperature of the isothermal disc and atmosphere,\
   $\rho_{\text{isoDisk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the peak mass density\
-  of the disk and atmosphere on the mid-plane $z=0$.
+  of the disc and atmosphere on the mid-plane $z=0$.
 
@@
   can be derived from the other known parameters and thermal pressure equilibrium condition\
-  on the interfaces $(z=\pm z_{0})$ between the disk and atmosphere.\
+  on the interfaces $(z=\pm z_{0})$ between the disc and atmosphere.\
 
-  The density profile of \Cref{disk-atm-sys} is shown in \Cref{fig__initial-density-profile}.\
+  The density profile of \Cref{disc-atm-sys} is shown in \Cref{fig__initial-density-profile}.\
   Beyond the core radius ($\sim 2 \text{ kpc}$) the gaseous density decreases rapidly as a power-law.
 
-%  The density profile of \Cref{disk-atm-sys} is shown in \Cref{fig__initial-density-profile}\
+%  The density profile of \Cref{disc-atm-sys} is shown in \Cref{fig__initial-density-profile}\
 %  and compared to the observed result \citep{Miller_2013} beyond 1 kpc.\
@@
     \includegraphics[width=\columnwidth]{figures/fig__initial-density-profile.png}
-    \caption{The density profile of the isothermal disk (red pluses) and\
+    \caption{The density profile of the isothermal disc (red pluses) and\
              atmosphere (blue crosses) along the positive z-axis.\
              The density distribution is derived from hydrostatic equilibrium,\
-             the interface ($z=0.1$) between the isothermal disk\
+             the interface ($z=0.1$) between the isothermal disc\
              and the atmosphere is pressure balanced.}
@@
 
-  A crucial component in our work is the clumpy ISM disk initialized by\
+  A crucial component in our work is the clumpy ISM disc initialized by\
   the publicly available pyFC code
@@
   the Nyquist limit $k_{\text{max}}$, and the lower cutoff wave number $k_{\text{min}}$.
-  $k_{\text{max}}$ is one-half of the spatial resolution within disk,\
+  $k_{\text{max}}$ is one-half of the spatial resolution within disc,\
   and $k_{\text{min}}$ is 375.0, corresponding to the maximum size of an individual clump $\sim 20$ pc.\
@@
 
-  The density of clumpy disk can thus be obtained by taking the scalar products of\
-  $f(\bold{x})$ with $\rho_{\text{isoDisk}}(z)$ over all cells within the disk, i.e.,\
+  The density of clumpy disc can thus be obtained by taking the scalar products of\
+  $f(\bold{x})$ with $\rho_{\text{isoDisk}}(z)$ over all cells within the disc, i.e.,\
   $\displaystyle\rho_{\text{ismDisk}}(\bold{x}) =\
   f(\bold{x}) \rho_{\text{isoDisk}}(z)$.\
-  Also, the thermal pressure equilibrium within the clumpy disk implies that the temperature of disk is
+  Also, the thermal pressure equilibrium within the clumpy disc implies that the temperature of disc is
   $\displaystyle T_{\text{ismDisk}}(\bold{x}) =\
@@
 
-  \Cref{table-parameters} summarize the parameters of the clumpy disk and their references.
+  \Cref{table-parameters} summarize the parameters of the clumpy disc and their references.
 
@@
   based on the gradient of mass density.\
-  We also restrict the refinement level at 7 within the cold disk so that\
+  We also restrict the refinement level at 7 within the cold disc so that\
   a molecular cloud can be adequately resolved by approximately 30 cells along their diameter, 20 pc.
 
-  \Cref{fig__zoom-in-disk} shows a close-up view of the\
+  \Cref{fig__zoom-in-disc} shows a close-up view of the\
   pressure, temperature, and number density slices
-  in the y-z plane through the center of the disk.
+  in the y-z plane through the center of the disc.
 
   \Cref{fig__numberDensityHistogram} plots the volume filling factor as a function of\
-  initial number density within the disk without jet source.\
+  initial number density within the disc without jet source.\
 
@@
     \caption{The volume filling factor as a function of\
-             initial number density within the disk without jet source.\
+             initial number density within the disc without jet source.\
              The vertical bands represent from left to right: the allowable number densities \citep{peak-ism-density} for\
@@
   \begin{figure}
-    \includegraphics[width=\columnwidth]{figures/fig__zoom-in-disk.png}
+    \includegraphics[width=\columnwidth]{figures/fig__zoom-in-disc.png}
     \caption{Close-up view of the initial\
              pressure (top), temperature (middle), and number density (bottom) slices\
-             in the y-z plane through the center of the disk.
+             in the y-z plane through the center of the disc.
              }
-    \label{fig__zoom-in-disk}
+    \label{fig__zoom-in-disc}
   \end{figure}
@@
 \raggedright
-\caption{Parameters of the disk, atmosphere, and gravitational potential in the simulation.}
+\caption{Parameters of the disc, atmosphere, and gravitational potential in the simulation.}
 \label{table-parameters}
@@
 $T_{\text{\text{atmp}}}$              & Temperature of atmosphere                 & $10^{6}$ K                           & \citep{temperature-MW}         \\ \hline
-{\bf Isothermal disk }                &                                           &                                      &                                \\
-$z_{0}$                               & Scale height of disk                      & 100 pc                               & \citep{peak-ism-density}       \\
-$T_{\text{\text{isoDisk}}}$           & Temperature of disk                       & $10^{3}$ K                           & \multicolumn{1}{c}{''}         \\
-$\rho_{\text{isoDisk}}^{\text{peak}}$ & Peak mass density of disk                 & $10^{-23}$ g$\cdot$cm$^{-3}$         & \multicolumn{1}{c}{''}         \\ \hline
-{\bf Clumpy disk }                    &                                           &                                      &                                \\
+{\bf Isothermal disc }                &                                           &                                      &                                \\
+$z_{0}$                               & Scale height of disc                      & 100 pc                               & \citep{peak-ism-density}       \\
+$T_{\text{\text{isoDisk}}}$           & Temperature of disc                       & $10^{3}$ K                           & \multicolumn{1}{c}{''}         \\
+$\rho_{\text{isoDisk}}^{\text{peak}}$ & Peak mass density of disc                 & $10^{-23}$ g$\cdot$cm$^{-3}$         & \multicolumn{1}{c}{''}         \\ \hline
+{\bf Clumpy disc }                    &                                           &                                      &                                \\
 $\dagger$  $k_{\text{min}}$           & Cutoff wave number                        & 375.0                                & \citep{peak-ism-density}       \\
@@
 % In addition to the gravitational interaction, we ignore other interactions between stars and gases.
-% We also ignore the self-gravity of the ISM disk and of the atmosphere.
+% We also ignore the self-gravity of the ISM disc and of the atmosphere.
 % We ignore the centrifugal force of Milky Way rotation acting on the bubbles.
@@
   the jet direction must be perpendicular to the Galactic plane, and in particular to\
-  investigate the effect of the jet-disk misalignment on the symmetry of bubbles.
+  investigate the effect of the jet-disc misalignment on the symmetry of bubbles.
 
@@
 
-  Note that as we inject the jets at the center of the clumpy disk,\
+  Note that as we inject the jets at the center of the clumpy disc,\
   we define the ambient gas density by the peak density of\
-  the isothermal disk on the mid-plane $z=0$ (i.e. $\rho^{\text{peak}}_{\text{isoDisk}}$),\
+  the isothermal disc on the mid-plane $z=0$ (i.e. $\rho^{\text{peak}}_{\text{isoDisk}}$),\
   as opposed to the \textit{clumpy} density around the jet source, to avoid ambiguous definition.
@@
   \begin{figure}
-    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp.png}
+    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp.png}
     \caption{
@@
              Comparison between the cases with a clumpy (first column from left)\
-             and with a smooth disk (second) in a stratified atmosphere\
-             shows that the initial density distribution of the dense disk has an insignificant effect\
-             on the overall dynamics of bubbles. However, the outer bubbles with the smooth disk\
+             and with a smooth disc (second) in a stratified atmosphere\
+             shows that the initial density distribution of the dense disc has an insignificant effect\
+             on the overall dynamics of bubbles. However, the outer bubbles with the smooth disc\
              in an uniform atmosphere (third) is spherical-shape,\
@@
              Also, the first three and the rightmost columns show that the most inner bubbles (dashed box)\
-             can only appear associated with the disk, and without the disk, the outer bubbles will be tilted,
-             indicating the dense disk is crucial for\
+             can only appear associated with the disc, and without the disc, the outer bubbles will be tilted,
+             indicating the dense disc is crucial for\
              the axis-symmetrically outer bubbles and of the most inner bubbles formation.
              }
-    \label{fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp}
+    \label{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp}
   \end{figure}
@@
                top panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
-               to the disk normal in 1.2 Myr.]
+               to the disc normal in 1.2 Myr.]
      {

### 2022-02-04 paper.tex
update

@@
 there is a lack of preferred orientation of jets with respect to a disc normal.\
-A number of galaxies in which the jets are tilted to the disc normal\
+In contrast, a number of galaxies in which the jets are tilted to the disc normal\
 (e.g. NGC 3079, \citealt{Cecil2001}; NGC 1052, \citealt{Dopita2015}),\
@@
 involving CR jet injections from the central SMBH in the Galaxy to investigate\
-whether the jet scenario is able to produce symmetric Galactic bubbles that are\
+whether the \textit{inclined} jet scenario is able to produce the \textit{symmetric} Galactic bubbles that are\
 consistent with the observed features, including the shape, the\
-flat surface brightness, and the sharp edges.\
+surface brightness (for eROSITA bubbles), and the spectra (for \textit{Fermi} bubbles).\
 

### 2022-02-04 paper.tex
update

@@
 involving CR jet injections from the central SMBH in the Galaxy to investigate\
-whether the \textit{inclined} jet scenario is able to produce the \textit{symmetric} Galactic bubbles that are\
+whether the \textit{inclined} jet scenario is able to produce\
+the \textit{symmetric} Galactic bubbles that are\
 consistent with the observed features, including the shape, the\
@@
   \caption{
+      Simulated microwave spectra (colored lines in left) averaged over $|l|<10^{\circ}$, $20^{\circ}<|b|<30^{\circ}$.\
+      The data point represents the \textit{WMAP} data in the 23 GHz K band and the shaded area indicates the range\
+      of synchrotron spectral indices allowed for the \textit{WMAP} haze \citep{Dobler_2008}.\
       Simulated gamma-ray spectra (colored lines in right column) of the Fermi bubbles calculated for a longitude range of\
@@
       The gray band represents the observational data of \citet{Ackermann2014}.\
-      Simulated microwave spectra (colored lines in left) averaged over $|l|<10^{\circ}$, $20^{\circ}<|b|<30^{\circ}$.\
-      The data point represents the \textit{WMAP} data in the 23 GHz K band and the shaded area indicates the range\
-      of synchrotron spectral indices allowed for the \textit{WMAP} haze \citep{Dobler_2008}.
+      The rows from top to bottom show the microwave (left) and gamma-ray (left) spectra\
+      with CRe spectra index $p=2.0, 2.2$ and $2.4$.
+      %At larger $p$, the microwave spectrum was found to be steeper as $I_{\nu}\propto \nu^{-(p-1)/2}$.
   }

### 2022-02-04 paper.tex
update

@@
       Simulated microwave spectra (colored lines in left) averaged over $|l|<10^{\circ}$, $20^{\circ}<|b|<30^{\circ}$.\
-      The data point represents the \textit{WMAP} data in the 23 GHz K band and the shaded area indicates the range\
+      The data point represents the \textit{WMAP} data in the 23 GHz K band and\
+      the shaded bow-tie area indicates the range\
       of synchrotron spectral indices allowed for the \textit{WMAP} haze \citep{Dobler_2008}.\

### 2022-02-04 paper.tex
update

--- 2022-02-04 paper.tex
@@
       The rows from top to bottom show the microwave (left) and gamma-ray (left) spectra\
-      with CRe spectra index $p=2.0, 2.2$ and $2.4$.
+      with CRe spectra index $p=2.0, 2.2$ and $2.4$.\
+      The CRe cutoff energy is $1.1\times10^{6}m_{\text{e}}c^{2}$ in all cases.
       %At larger $p$, the microwave spectrum was found to be steeper as $I_{\nu}\propto \nu^{-(p-1)/2}$.

### 2022-02-04 paper.tex
update

--- 2022-02-04 paper.tex
@@
       The gray band represents the observational data of \citet{Ackermann2014}.\
-      The rows from top to bottom show the microwave (left) and gamma-ray (left) spectra\
-      with CRe spectra index $p=2.0, 2.2$ and $2.4$.
+      The rows from top to bottom show the microwave (left) and gamma-ray (right) spectra\
+      with CRe spectra index $p=2.2, 2.4$ and $2.6$.\
+      The CRe cutoff energy is $1.1\times10^{6}m_{\text{e}}c^{2}$ in all cases.
       %At larger $p$, the microwave spectrum was found to be steeper as $I_{\nu}\propto \nu^{-(p-1)/2}$.

### 2022-02-04 paper.tex
update

--- 2022-02-04 paper.tex
@@
 
-The gamma-ray emission of the Fermi bubbles is observed in the energy range\
+The gamma-ray emission of the \textit{Fermi} bubbles is observed in the energy range\
 of $1\lesssim E_{\gamma} \lesssim 100$ GeV and has an almost spatially uniform hard\
@@
 a giant hourglass-shaped structure (eROSITA bubbles hereafter) at the GC,\
-but extending about twice as large as the Fermi bubbles.\
+but extending about twice as large as the \textit{Fermi} bubbles.\
 The large-scale X-ray structure\
 shows that the intrinsic size of the bubbles is 14 kiloparsecs across \citep{Predehl2021},
-and displays morphological symmetry about the Galactic plane as the Fermi bubbles.
+and displays morphological symmetry about the Galactic plane as the \textit{Fermi} bubbles.
 
@@
 Early attempts \citep{Sarkar2015,Yang2017,Zhang2020}\
-to model the symmetric Fermi and eROSITA bubbles (collectively we call the Galactic bubbles)\
+to model the symmetric \textit{Fermi} and eROSITA bubbles (collectively we call the Galactic bubbles)\
 assumed that the jet is vertical to the Galactic plane. However,\
@@
   (Schive et al. \citeyear{gamer-1}, \citeyear{gamer-2}; \citeauthor{tseng2021} \citeyear{tseng2021})\
-  to carry out the simulations of the Fermi and eROSITA bubbles by CR and relativistic fluid injections from the GC.
+  to carry out the simulations of the \textit{Fermi} and eROSITA bubbles by CR and relativistic fluid injections from the GC.
 
@@
   within the range of $1$ --- $100$ GeV, we assume the pressure of CRe is much less than that of gas\
-  throughout the simulation so that we , and the Fermi bubbles can be outlined against the eROSITA bubbles.
+  throughout the simulation so that we , and the \textit{Fermi} bubbles can be outlined against the eROSITA bubbles.
 
-  As stressed by \citet{Yang2012}, CR diffusion has an insignificant effect on the overall morphology of the Fermi bubbles,\
+  As stressed by \citet{Yang2012}, CR diffusion has an insignificant effect\
+  on the overall morphology of the \textit{Fermi} bubbles,\
   but only sharpens the edges of the simulated bubbles by the interplay between anisotropic CR diffusion\
@@
       of synchrotron spectral indices allowed for the \textit{WMAP} haze \citep{Dobler_2008}.\
-      Simulated gamma-ray spectra (colored lines in right column) of the Fermi bubbles calculated for a longitude range of\
+      Simulated gamma-ray spectra (colored lines in right column)\
+      of the \textit{Fermi} bubbles calculated for a longitude range of\
       $|l|<10^{\circ}$ for different latitude bins.\
       The gray band represents the observational data of \citet{Ackermann2014}.\
-      The rows from top to bottom show the microwave (left) and gamma-ray (left) spectra\
-      with CRe spectra index $p=2.0, 2.2$ and $2.4$.
+      The rows from top to bottom show the microwave (left) and gamma-ray (right) spectra\
+      with CRe spectra index $p=2.2, 2.4$ and $2.6$.\
+      The CRe cutoff energy is $1.1\times10^{6}m_{\text{e}}c^{2}$ in all cases.
       %At larger $p$, the microwave spectrum was found to be steeper as $I_{\nu}\propto \nu^{-(p-1)/2}$.

### 2022-02-04 paper.tex
update

@@
 To this end, this work introduces a dense thin disc of interstellar medium\
-around a jet source to deflects and decelerates the jets,\
+around a jet source to deflects and decelerates the inclined jets,\
 in an attempt to remedy the symmetry problem of the Galactic bubbles.\
@@
   \includegraphics[width=\linewidth]{figures/fig__GammaRay_100e9_1e6_angle_000.png}
-  \caption{The observed (left) and simulated (right) photon flux at 108.6 GeV.\
+  \caption{The observed (left) and simulated (right) photon flux\
+           in the energy bin $76.8-153.6$ GeV.\
            Note that the left panel is the\
@@
            and removes the contribution from point-like component.
+           The red arrow at the center of the\
+           top panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
+           to the disc normal in 1.2 Myr.]
   }

### 2022-02-04 paper.tex
update

@@
            and removes the contribution from point-like component.
-           The red arrow at the center of the\
-           top panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
+           The red arrow at the center
+           panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
            to the disc normal in 1.2 Myr.]

### 2022-02-04 paper.tex
update

@@
            panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
-           to the disc normal in 1.2 Myr.]
+           to the disc normal in 1.2 Myr.
   }

### 2022-02-04 paper.tex
update

@@
            and removes the contribution from point-like component.
-           The red arrow at the center
+           The red arrow at the center of left\
            panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\

### 2022-02-04 paper.tex
update

--- 2022-02-04 paper.tex
@@
            and removes the contribution from point-like component.
-           The red arrow at the center
+           The red arrow at the center of the right\
            panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\

### 2022-02-04 paper.tex
update

@@
   \caption{
-      Simulated microwave spectra (colored lines in left) averaged over $|l|<10^{\circ}$, $20^{\circ}<|b|<30^{\circ}$.\
+      Simulated microwave spectra (colored lines in left) averaged over $20^{\circ}<|b|<30^{\circ}$, $|l|<10^{\circ}$.\
       The data point represents the \textit{WMAP} data in the 23 GHz K band and\

### 2022-02-04 paper.tex
update

@@
       The rows from top to bottom show the microwave (left) and gamma-ray (right) spectra\
-      with CRe spectra index $p=2.2, 2.4$ and $2.6$.\
+      with CRe spectra index $2.2, 2.4$ and $2.6$.\
       The CRe cutoff energy is $1.1\times10^{6}m_{\text{e}}c^{2}$ in all cases.

### 2022-02-04 paper.tex
update

@@
 $\epsilon_{\text{max}}=13.59$ eV (starlight) in order to\
-facilitate a reliable interpretation of simulated gamma-ray map.
+facilitate a reliable interpretation of simulated gamma-ray spectrum.
 

### 2022-02-04 paper.tex
update

--- 2022-02-04 paper.tex
@@
     \subfigure[Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
-               (photons s$^{-1}$ deg$^{-2}$) in the 0.6-1.0 keV range,\
-               using a Hammer-Aitoff projection. Throughout this paper we show sky maps\
-               in Galactic coordinates centered on the Galactic center and observed by the solar position.\
+               (photons s$^{-1}$ deg$^{-2}$) in the 0.6-1.0 keV range.\
+               Throughout this paper we show sky maps\
+               in Galactic coordinates centered on the Galactic center using a Hammer-Aitoff projection,\
+               and observed from the solar system.\
                The red arrow at the center of the\
@@
 $\epsilon_{\text{min}}=1.13\times10^{-4}$ eV (CMB radiation) to\
-$\epsilon_{\text{max}}=13.59$ eV (starlight) in order to\
-facilitate a reliable interpretation of simulated gamma-ray map.
+$\epsilon_{\text{max}}=13.59$ eV (optical starlight) in order to\
+facilitate a reliable interpretation of simulated gamma-ray spectrum.
 

### 2022-02-04 paper.tex
update

@@
              initial number density within the disc without jet source.\
-             The vertical bands represent from left to right: the allowable number densities \citep{peak-ism-density} for\
+             The vertical bands from left to right depict the allowable number densities \citep{peak-ism-density} for\
              hot ionized, warm neutral (WNM), warm ionized (WIM), cold nuetral mediums (CNM), and molecular clouds.}

### 2022-02-04 paper.tex
update

@@
              indicating the dense disc is crucial for\
-             the axis-symmetrically outer bubbles and of the most inner bubbles formation.
+             the axis-symmetrical outer bubbles and of the most inner bubbles formation.
              }

### 2022-02-05 paper.tex
update

@@
 
-\subsection{X-ray emission}
+\subsection{X-ray}
 
@@
 
-\subsection{Gamma-ray emission}
+\subsection{Microwave haze}
+
+  \begin{subequations}
+     \begin{align}
+        &I_{\nu} = \frac{4\pi\mathbb{C}e^{3}B^{0.5(p+1)}}{m_{\text{e}}c^{2}}\
+        \left(\frac{3e}{4\pi m_{\text{e}}c}\right)^{0.5(p-1)}\
+        a(p)\nu^{-0.5(p-1)}.\\
+        &a(p)=\nonumber\\
+             &\frac{2^{0.5(p-1)}\sqrt{3}\Gamma\left[\left(3p-1\right)/12\right]\
+                                        \Gamma\left[\left(3p+9\right)/12\right]\
+                                        \Gamma\left[\left(p+5\right)/4\right]}
+        {8\sqrt{\pi}(p+1)\Gamma\left[\left(p+7\right)/4\right]}
+     \end{align}
+  \end{subequations}
+
+\subsection{Gamma-ray}
 
@@
 
-\subsubsection{Leptonic process}
 In the leptonic scenario, the gamma-rays originate from IC scattering of the ISRF by CRe.\

### 2022-02-05 paper.tex
update

@@
 \subsection{X-ray}
-
-Thermal bremsstrahlung: The X-ray emissivity in an energy range 1.4–1.6 keV is calculated\
+The X-ray emissivity in an energy range 1.4–1.6 keV is calculated\
 using the MEKAL model \citep{Xray-1,Xray-2,Xray-3}\
@@
      \begin{align}
-        &I_{\nu} = \frac{4\pi\mathbb{C}e^{3}B^{0.5(p+1)}}{m_{\text{e}}c^{2}}\
+        &\frac{dE}{dtd\nu dV} =\nonumber\\
+        &\frac{4\pi\mathbb{C}e^{3}B^{0.5(p+1)}}{m_{\text{e}}c^{2}}\
         \left(\frac{3e}{4\pi m_{\text{e}}c}\right)^{0.5(p-1)}\

### 2022-02-05 paper.tex
update

@@
      |\mathbf{B}(R, z)|=B_{0}\exp{-z/z_{0}}\exp{-R/R_{0}},
+     \label{magnetic-field}
   \end{equation}
@@
 \section{Results}
+
+ \Cref{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp} shows\
+ the pressure (top), temperature (middile), number density (bottom) of slices on $x=0$ plane\
+ passing through a bipolar jet sources injecting along $z=-y$ direction from\
+ the origin for a duration of 1.2 Myr under four different cases from left to right.\
+ Comparison between the cases with a clumpy (first column from left)\
+ and with a smooth disc (second) in a stratified atmosphere\
+ shows that the initial density distribution of the dense disc has an insignificant effect\
+ on the overall dynamics of bubbles. However, the outer bubbles with the smooth disc\
+ in an uniform atmosphere (third) is spherical-shape,\
+ suggesting the stratification facilitates the outer bubbles elongation significantly.\
+ Also, the first three and the rightmost columns show that the most inner bubbles (dashed box)\
+ can only appear associated with the disc, and without the disc, the outer bubbles will be tilted,
+ indicating the dense disc is crucial for\
+ the axis-symmetrical outer bubbles and of the most inner bubbles formation.
+
 \label{Results}
@@
              The pressure (top), temperature (middle), and number density (bottom) slices\
-             through a bipolar jet sources injecting along $z=-y$ direction from\
+             passing through a bipolar jet sources injecting along $z=-y$ direction from\
              the origin for a duration of 1.2 Myr under four different cases from left to right.\
@@
   \subsection{X-ray}
-The X-ray emissivity in an energy range 1.4–1.6 keV is calculated\
+  The X-ray emissivity in an energy range 0.6 --- 1.0 keV is calculated\
   using the MEKAL model \citep{Xray-1,Xray-2,Xray-3}\
@@
 
-\subsection{Microwave haze}
-
-  \begin{subequations}
-     \begin{align}
-        &\frac{dE}{dtd\nu dV} =\nonumber\\
-        &\frac{4\pi\mathbb{C}e^{3}B^{0.5(p+1)}}{m_{\text{e}}c^{2}}\
-        \left(\frac{3e}{4\pi m_{\text{e}}c}\right)^{0.5(p-1)}\
-        a(p)\nu^{-0.5(p-1)}.\\
-        &a(p)=\nonumber\\
-             &\frac{2^{0.5(p-1)}\sqrt{3}\Gamma\left[\left(3p-1\right)/12\right]\
-                                        \Gamma\left[\left(3p+9\right)/12\right]\
-                                        \Gamma\left[\left(p+5\right)/4\right]}
-        {8\sqrt{\pi}(p+1)\Gamma\left[\left(p+7\right)/4\right]}
-     \end{align}
-  \end{subequations}
-
-\subsection{Gamma-ray}
+\subsection{Gamma-ray and microwave emission}
+  In this section, we compare the simulated gamma-ray and microwave\
+  spectra based on the leptonic AGN jet model with the\
+  observed spectra of the Fermi bubbles and the microwave haze.
 
@@
 
-where $\sigma_{T}$ is the Thomson cross section, $c$ speed of light, $m_{\text{e}}$ electron mass,\
+where $\sigma_{T}$ is the Thomson cross section, $c$ speed of light,\
 $n(\epsilon)$ the photon number density of ISRF per energy, $\gamma$ the Lorentz factor of CRe,\
-$\mathbb{C}$ and $p$ are the normalization constant and spectral index of CRe power-law spectrum,\
+$\mathbb{C}$ and $p$ are the normalization constant and spectral index of CRe power-law spectrum.
 $\gamma_{\text{min}}(\epsilon)$ is the minimum required Lorentz factor of CRe such that CRe is energetic sufficient for\
@@
   }
-  \label{fig__gammaRay}
+  \label{fig__gammaRay-map}
 \end{figure*}
+
+One can see that the general morphological characteristics of the \textit{Fermi} bubbles can be reproduced.\
+
+% assuming a uniform CR spectrum with energy cutoff of ~500 GeV\
+% and spectral index of 2.4, one could also reproduce the gamma-ray spectrum quite well.\
+% Note that the simulation time at this point is 12.39 Myr,\
+% much longer than the CR electron cooling time, so their Emax should\
+% have cooled to below 500 GeV by this time (we should think about how to estimate this).\
+% Therefore, the CRe generating the gamma-ray emission would need to be re-accelerated\
+% by some in-situ acceleration mechanisms such as shocks or turbulence.\
+% The forward shock is pretty far away from the gamma-ray bubbles,\
+% so it's more likely associated with turbulence.
+
+  Having successfully reproduced the morphology\
+  and spectrum of the \textit{Fermi} bubbles,\
+  we now ask whether CRe could also explain\
+  the Galactic microwave haze.
+
+  The microwave haze at 23 GHz was first detected by the \textit{WMAP} \citep{Dobler_2008}\
+  within the region $|b|<30^{\circ}$ above and below the Galactic plane,\
+  and later confirmed by the Planck Collaboration IX \citep{PlanckCollaborationIX2013}.
+
+  The synchrotron emissivity with an isotropic electron pitch angle distribution\
+  is given by \citet{BLUMENTHAL1970}:
+
+  \begin{subequations}
+     \begin{align}
+        &\frac{dE}{dtd\nu dV} =\nonumber\\
+        &\frac{4\pi\mathbb{C}e^{3}B^{0.5(p+1)}}{m_{\text{e}}c^{2}}\
+        \left(\frac{3e}{4\pi m_{\text{e}}c}\right)^{0.5(p-1)}\
+        a(p)\nu^{-0.5(p-1)},\\
+        &a(p)=\nonumber\\
+             &\frac{2^{0.5(p-1)}\sqrt{3}\Gamma\left[\left(3p-1\right)/12\right]\
+                                        \Gamma\left[\left(3p+9\right)/12\right]\
+                                        \Gamma\left[\left(p+5\right)/4\right]}
+        {8\sqrt{\pi}(p+1)\Gamma\left[\left(p+7\right)/4\right]},
+     \end{align}
+     \label{synchrotron-emissivity}
+  \end{subequations}
+
+  where $\Gamma$ is gamma function, $B$ is the magnetic field strength defined in\
+  \Cref{magnetic-field}.
+
+  \Cref{fig__gammaRaySynchtronSpectrum} shows the simulated microwave (left)\
+  and gamma-ray (right) spectra averaged over the different patches (shown in the legends) of the sky.
+
+  For a given longitude and latitude range, the simulated spectra are\
+  computed by projecting the gamma-ray/microwave emissivities as a\
+  function of energy along finely sampled lines of sight\
+  (with resolutions of 0.5 degrees), and then we average the spectra\
+  over all the sight lines within the region.
+
+  Indeed, we find that the simulated gamma-ray\
+  spectra for all latitudes exhibit a spectral cutoff at\
+  similar energies 400---500 GeV, consistent with\
+  the observed cutoff energy.
+
+  %The enhanced emission at the lower latitude would likely be due to
+  %similar to the bottom right panel in Fig. 5 of YR17, which is dominated by\
+  %the optical starlight. That's also why in your plot above,\
+  %the high-latitude spectrum tends to be dimmer because of the decay of the ISRF intensity in optical.
 
@@
   }
-  \label{fig__gammaRay}
+  \label{fig__gammaRaySynchtronSpectrum}
 \end{figure*}
+
+The correlation between the multi-wavelength simulation suggest that\
+the \textit{Fermi} bubbles are produced by high-energy electrons\
+via an inverse Compton scattering process, as the same electrons can\
+also simultaneously produce synchrotron radiations in the\
+presence of magnetic fields.
 
@@
 
-Since the jets encounter a larger column depth of cloudsalong their path,\
+Since the jets encounter a larger column depth of clouds along their path,\
 they interact more strongly with the dense ISM.\
@@
 and launch a sub-relativistic outflow along the minor axis following the path of least resistance.
+
+Assuming that a relativistic electron population of spectral
+index x = 2.2 gives rise to the microwave haze via synchrotron
+emission.
 

### 2022-02-06 paper.tex
update

@@
 
-  Although the high-energy CRe ($10$ --- $100$ GeV) plays a crucial role in reproducing the $\gamma$-ray map\
-  within the range of $1$ --- $100$ GeV, we assume the pressure of CRe is much less than that of gas\
+  Although the high-energy CRe ($10$ -- $100$ GeV) plays a crucial role in reproducing the $\gamma$-ray map\
+  within the range of $1$ -- $100$ GeV, we assume the pressure of CRe is much less than that of gas\
   throughout the simulation so that we , and the \textit{Fermi} bubbles can be outlined against the eROSITA bubbles.
@@
 
-  The bipolar jets are constantly ejected from a cylindrical source within a jet duration time 1.2 Myr,\
+  The bipolar jets are constantly ejected from a cylindrical source within a jet duration time $t=0--1.2$ Myr,\
   allowing the total ejected energy $1.2\times10^{56}$ erg is between\
@@
  \Cref{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp} shows\
- the pressure (top), temperature (middile), number density (bottom) of slices on $x=0$ plane\
- passing through a bipolar jet sources injecting along $z=-y$ direction from\
- the origin for a duration of 1.2 Myr under four different cases from left to right.\
- Comparison between the cases with a clumpy (first column from left)\
- and with a smooth disc (second) in a stratified atmosphere\
+ the pressure (top), temperature (middile), number density (bottom) of the $x=0$ slices\
+ passing through the bipolar jet source injecting along $z=-y$ direction\
+ at the end of simulation $t=12.39$ Myr.\
+ Comparison between the clumpy (first column from left)\
+ and the smooth disc (second) in a stratified atmosphere\
  shows that the initial density distribution of the dense disc has an insignificant effect\
- on the overall dynamics of bubbles. However, the outer bubbles with the smooth disc\
+ on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
  in an uniform atmosphere (third) is spherical-shape,\
- suggesting the stratification facilitates the outer bubbles elongation significantly.\
- Also, the first three and the rightmost columns show that the most inner bubbles (dashed box)\
- can only appear associated with the disc, and without the disc, the outer bubbles will be tilted,
+ suggesting the stratification facilitates the outermost bubbles elongation significantly.\
+ Also, the two rightmost columns indicate that the development of the innermost bubbles (dashed box)\
+ is always associated with the disc, and without the disc,\
+ the outermost bubbles and the turbulent region will be tilted,
  indicating the dense disc is crucial for\
- the axis-symmetrical outer bubbles and of the most inner bubbles formation.
+ the axis-symmetry of bubbles and for the innermost bubbles formation.
 
@@
              The pressure (top), temperature (middle), and number density (bottom) slices\
-             passing through a bipolar jet sources injecting along $z=-y$ direction from\
-             the origin for a duration of 1.2 Myr under four different cases from left to right.\
-             Comparison between the cases with a clumpy (first column from left)\
-             and with a smooth disc (second) in a stratified atmosphere\
+             at the end of simulation $t=12.39$ Myr.\
+             The slices pass through a bipolar jet source injecting along $z=-y$ direction\
+             for a duration $t=0$--$1.2$ Myr.\
+             Comparison between the clumpy (first column from left)\
+             and the smooth disc (second) in a stratified atmosphere\
              shows that the initial density distribution of the dense disc has an insignificant effect\
-             on the overall dynamics of bubbles. However, the outer bubbles with the smooth disc\
+             on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
              in an uniform atmosphere (third) is spherical-shape,\
-             suggesting the stratification facilitates the outer bubbles elongation significantly.\
-             Also, the first three and the rightmost columns show that the most inner bubbles (dashed box)\
-             can only appear associated with the disc, and without the disc, the outer bubbles will be tilted,
+             suggesting the stratification facilitates the outermost bubbles elongation significantly.\
+             Also, the two rightmost columns indicate that the development of the innermost bubbles (dashed box)\
+             is always associated with the disc, and without the disc,\
+             the outermost bubbles and the turbulent region will be tilted,
              indicating the dense disc is crucial for\
-             the axis-symmetrical outer bubbles and of the most inner bubbles formation.
+             the axis-symmetry of bubbles and for the innermost bubbles formation.
              }
@@
   \subsection{X-ray}
-  The X-ray emissivity in an energy range 0.6 --- 1.0 keV is calculated\
+  The X-ray emissivity in an energy range 0.6 -- 1.0 keV is calculated\
   using the MEKAL model \citep{Xray-1,Xray-2,Xray-3}\
@@
   spectra for all latitudes exhibit a spectral cutoff at\
-  similar energies 400---500 GeV, consistent with\
+  similar energies 400--500 GeV, consistent with\
   the observed cutoff energy.

### 2022-02-06 paper.tex
update

@@
  suggesting the stratification facilitates the outermost bubbles elongation significantly.\
- Also, the two rightmost columns indicate that the development of the innermost bubbles (dashed box)\
+ Also, the two rightmost columns reveal that the development of the innermost bubbles (dashed box)\
  is always associated with the disc, and without the disc,\
@@
  indicating the dense disc is crucial for\
- the axis-symmetry of bubbles and for the innermost bubbles formation.
+ the axis-symmetry of the Galactic bubbles and for the innermost bubbles formation.
 
@@
              suggesting the stratification facilitates the outermost bubbles elongation significantly.\
-             Also, the two rightmost columns indicate that the development of the innermost bubbles (dashed box)\
+             Also, the two rightmost columns reveal that the development of the innermost bubbles (dashed box)\
              is always associated with the disc, and without the disc,\
@@
              indicating the dense disc is crucial for\
-             the axis-symmetry of bubbles and for the innermost bubbles formation.
+             the axis-symmetry of the Galactic bubbles and for the innermost bubbles formation.
              }

### 2022-02-06 paper.tex
update

--- 2022-02-06 paper.tex
@@
  indicating the dense disc is crucial for\
- the axis-symmetry of bubbles and for the innermost bubbles formation.
+ the symmetry of the Galactic bubbles and for the innermost bubbles formation.
 
@@
              indicating the dense disc is crucial for\
-             the axis-symmetry of bubbles and for the innermost bubbles formation.
+             the symmetry of the Galactic bubbles and for the innermost bubbles formation.
              }

### 2022-02-06 paper.tex
update

@@
  \Cref{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp} shows\
- the pressure (top), temperature (middile), number density (bottom) of the $x=0$ slices\
+ the pressure (top), temperature (middile), number density (bottom) slices\
  passing through the bipolar jet source injecting along $z=-y$ direction\

### 2022-02-06 paper.tex
update

@@
  \Cref{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp} shows\
- the pressure (top), temperature (middile), number density (bottom) slices\
+ the slices of pressure (top), temperature (middile), number density (bottom)\
  passing through the bipolar jet source injecting along $z=-y$ direction\
@@
     \caption{
-             The pressure (top), temperature (middle), and number density (bottom) slices\
+             The slices of pressure (top), temperature (middle), and number density (bottom)\
              at the end of simulation $t=12.39$ Myr.\

### 2022-02-06 paper.tex
update

@@
  the slices of pressure (top), temperature (middile), number density (bottom)\
- passing through the bipolar jet source injecting along $z=-y$ direction\
  at the end of simulation $t=12.39$ Myr.\
+ The slices pass through the bipolar jet source injecting along $z=-y$ direction\
+ for a duration $t=0$--$1.2$ Myr.\
  Comparison between the clumpy (first column from left)\

### 2022-02-06 paper.tex
update

@@
   \subsection{X-ray}
-  The X-ray emissivity in an energy range 0.6 -- 1.0 keV is calculated\
+  The X-ray emissivity in an energy range 0.6 -- 1.0 keV is computed\
+  for each computational volume cell
   using the MEKAL model \citep{Xray-1,Xray-2,Xray-3}\
   implemented in the utility XSPEC \citep{XSPEC}, assuming solar metallicity.\
+  the X-ray intensity map are then generated by projecting the emissivities\
+  along lines of sight across the sky.
 
@@
   follows out to a radius of 250 kpc the observed density profile of \citep{temperature-MW}.
+
+  \Cref{fig__xray_0.8keV_angle_000} shows the projected X-ray emissivity from simulation,\
+  overlaid with the red arrow representing the direction of the bipolar jet,\
+  constantly ejecting at an angle of $45^{\circ}$\
+  to the disc normal.
 
@@
     \caption{}
-    \label{fig_xray}
+    \label{fig_xray-map}
   \end{figure*}

### 2022-02-06 paper.tex
update

--- 2022-02-06 paper.tex
@@
 \section{Results}
+\label{Results}
+
+\subsection{Morphology}
 
@@
 
-\label{Results}
   \begin{figure}
@@
   \subsection{X-ray}
-  The X-ray emissivity in an energy range 0.6 -- 1.0 keV is calculated\
+  The X-ray emissivity in an energy range 0.6 -- 1.0 keV is computed\
+  for each computational volume cell
   using the MEKAL model \citep{Xray-1,Xray-2,Xray-3}\
   implemented in the utility XSPEC \citep{XSPEC}, assuming solar metallicity.\
+  The X-ray intensity map are then generated by projecting the emissivities\
+  along lines of sight across the sky.
 
-  Note that the observed X-ray emission is contributed by all the gas in the Milky Way halo,\
+  We point out that the projections employed throughout this paper is \lq perspective\rq,\
+  which has the effect of making distant object appear smaller than the same object in the near distance,\
+  and also that the observed X-ray emission is contributed by all the gas in the Milky Way halo,\
   which likely extends to a radius of $\sim$250 kpc \citep{halo-radius-1,halo-radius-2},\
@@
   follows out to a radius of 250 kpc the observed density profile of \citep{temperature-MW}.
+
+  \Cref{fig__xray_0.8keV_angle_000} shows the projected X-ray emissivity from simulation,\
+  overlaid with the red arrow representing the direction of the bipolar jet,\
+  constantly ejecting during 0--1.2 Myr at an angle of $45^{\circ}$\
+  to the disc normal.
 

### 2022-02-06 paper.tex
update

@@
 
-  We point out that the projections employed throughout this paper is \lq perspective\rq,\
+  We point out that the projections throughout this paper is \lq perspective\rq,\
   which has the effect of making distant object appear smaller than the same object in the near distance,\
@@
 
-  \Cref{fig__xray_0.8keV_angle_000} shows the projected X-ray emissivity from simulation,\
+  \Cref{fig__xray_0.8keV_angle_000} shows\
+  the simulated photon count rate (top)\
+  in the 0.6--1.0 keV range at the present time,\
   overlaid with the red arrow representing the direction of the bipolar jet,\
-  constantly ejecting during 0--1.2 Myr at an angle of $45^{\circ}$\
-  to the disc normal.
+  compared with the observed count rate (bottom) in the same energy bin.
 

### 2022-02-06 paper.tex
update

@@
 \usepackage{floatrow}
-%\usepackage[FIGTOPCAP]{subfigure}
 \usepackage{subfigure}
@@
 \newcommand{\MyDiamond}[1][fill=black]{
-\begin{tikzpicture}[x=1.2ex,y=1.2ex,line width=.1ex,line join=round, yshift=0.0ex] \draw  [#1]  (0,.5) -- (.5,1) -- (1,.5) -- (.5,0);
+\begin{tikzpicture}[x=1.2ex,y=1.2ex,line width=.1ex,line join=round, yshift=0.0ex]\
+\draw  [#1]  (0,.5) -- (.5,1) -- (1,.5) -- (.5,0);
 \end{tikzpicture}
@@
   (Schive et al. \citeyear{gamer-1}, \citeyear{gamer-2}; \citeauthor{tseng2021} \citeyear{tseng2021})\
-  to carry out the simulations of the \textit{Fermi} and eROSITA bubbles by CR and relativistic fluid injections from the GC.
+  to carry out the simulations of the Galactic bubbles by CR and relativistic fluid injections from the GC.
 

### 2022-02-06 paper.tex
update

@@
 
-In the leptonic scenario, the gamma-rays originate from IC scattering of the ISRF by CRe.\
+In the leptonic scenario, the gamma-rays originate from IC scattering of the interstellar radiation field by CRe.\
 The CRe spectrum follows a power law distribution\
@@
 where $\sigma_{T}$ is the Thomson cross section, $c$ speed of light,\
-$n(\epsilon)$ the photon number density of ISRF per energy, $\gamma$ the Lorentz factor of CRe,\
+$n(\epsilon)$ the photon number density of interstellar radiation field per energy, $\gamma$ the Lorentz factor of CRe,\
 $\mathbb{C}$ and $p$ are the normalization constant and spectral index of CRe power-law spectrum.
@@
 using the Klein–Nishina IC cross-section \citep{Jones1968} based\
-on the simulated CR number density and the ISRF model given by \citet{Porter2017}.
+on the simulated CR number density and the interstellar radiation field model given by \citet{Porter2017}.
 
@@
   %the optical starlight. That's also why in your plot above,\
-  %the high-latitude spectrum tends to be dimmer because of the decay of the ISRF intensity in optical.
+  %the high-latitude spectrum tends to be dimmer because of the decay of the interstellar radiation field intensity in optical.
 

### 2022-02-06 paper.tex
update

--- 2022-02-06 paper.tex
@@
   where $\hat{f}(\bold{k})$ is the Fourier transform of $f(\bold{x})$.\
-  The spectrum $D(\bold{k})$ in the Fourier space is characterized by the power law index $\beta=5/3$,\
+  The spectrum $D(\bold{k})$ in the Fourier space is characterized by the power-law index $\beta=5/3$,\
   the Nyquist limit $k_{\text{max}}$, and the lower cutoff wave number $k_{\text{min}}$.
@@
 \subsection{Gamma-ray and microwave emission}
+
   In this section, we compare the simulated gamma-ray and microwave\
   spectra based on the leptonic AGN jet model with the\
-  observed spectra of the Fermi bubbles and the microwave haze.
+  observed spectra of the Fermi bubbles and the microwave haze.\
+  The gamma-rays originate from the inverse Compton scattering of ISRF by CRe.\
+  The CRe spectrum follows a power-law distribution\
+  with a spectral index $p=2.4$ and ranges from\
+  $m_{\text{e}}c^2$ ($0.5$ MeV) to $1.1\times10^{6}m_{\text{e}}c^2$ ($550$ GeV),\
+  where $m_{\text{e}}c^2$ is the rest mass energy of an electron.
 
@@
 
-In the leptonic scenario, the gamma-rays originate from IC scattering of the ISRF by CRe.\
-The CRe spectrum follows a power law distribution\
-with a spectral index $p=2.4$ and ranges from\
-$m_{\text{e}}c^2$ ($0.5$ MeV) to $1.1\times10^{6}m_{\text{e}}c^2$ ($550$ GeV).\
-
-The emissivity of the upscattered photons at the energy $\epsilon_{1}$ is given by\
-the double integrals \citep{BLUMENTHAL1970}\
-over the range of incident photon energy and the CRe Lorentz factor:
+  The emissivity of the upscattered photons at the energy $\epsilon_{1}$ is computed for\
+  each computational cell in our simulations\
+  using the Klein-Nishina IC cross-section \citep{Jones1968,BLUMENTHAL1970}\
+  to handle the ultra-relativistic CRe:
 
@@
 where $\sigma_{T}$ is the Thomson cross section, $c$ speed of light,\
-$n(\epsilon)$ the photon number density of ISRF per energy, $\gamma$ the Lorentz factor of CRe,\
+$n(\epsilon)$ the energy distribution of the photon number density in ISRF given by \citet{Porter2017},\
+$\gamma$ the Lorentz factor of CRe,\
 $\mathbb{C}$ and $p$ are the normalization constant and spectral index of CRe power-law spectrum.
-$\gamma_{\text{min}}(\epsilon)$ is the minimum required Lorentz factor of CRe such that CRe is energetic sufficient for\
-producing scattered photon at the energy $\epsilon_{1}$ from an incident photon energy $\epsilon$.\
-$\gamma_{\text{max}}$ is the maximum CRe Lorentz factor in the spectrum, i.e. $\gamma_{\text{max}}=10^{6}$.
+$\gamma_{\text{min}}(\epsilon)$ is the minimum Lorentz factor of CRe\
+that allows incident photons to scatter from energy $\epsilon$ to $\epsilon_{1}$.
+$\gamma_{\text{max}}$ is the maximum CRe Lorentz factor in the spectrum.
 
 We integrate the incident photon energy from\
-$\epsilon_{\text{min}}=1.13\times10^{-4}$ eV (CMB radiation) to\
+$\epsilon_{\text{min}}=1.13\times10^{-4}$ eV (cosmic microwave background radiation) to\
 $\epsilon_{\text{max}}=13.59$ eV (optical starlight) in order to\

### 2022-02-06 paper.tex
update

@@
   The X-ray intensity map are then generated by projecting the emissivities\
-  along lines of sight across the sky.
+  along lines of sight from the solar position at $(x,y,z)=(8,0,0)$ kpc across the sky.
 
@@
   which has the effect of making distant object appear smaller than the same object in the near distance,\
+  in order to facilitate a reliable interpretation of simulated all-sky map,\
   and also that the observed X-ray emission is contributed by all the gas in the Milky Way halo,\
@@
   \end{align}
+\label{gammaray-emissivity}
 \end{subequations}
@@
 
-We integrate the incident photon energy from\
-$\epsilon_{\text{min}}=1.13\times10^{-4}$ eV (cosmic microwave background radiation) to\
-$\epsilon_{\text{max}}=13.59$ eV (optical starlight) in order to\
-facilitate a reliable interpretation of simulated gamma-ray spectrum.
+We perform the integration in \Cref{gammaray-emissivity} on each cell over the range of incident photon energy between\
+$\epsilon_{\text{min}}=1.13\times10^{-4}$ eV (cosmic microwave background radiation) and\
+$\epsilon_{\text{max}}=13.59$ eV (optical starlight)\
+and over the range of CRe Lorentz factor\
+to obtain the simulated IC emissivities.
 
-The gamma-ray emissivity\
-is computed for each computational cell in our simulations\
-using the Klein–Nishina IC cross-section \citep{Jones1968} based\
-on the simulated CR number density and the ISRF model given by \citet{Porter2017}.
+\Cref{fig__gammaRay-map} shows the simulated gamma-ray photon flux compared with the observed one\
+in the energy bin $76.8-153.6$ GeV.\
 
-To evaluate the simulated photon flux $I$ at the energy $\epsilon_{1}$ and\
-take into account the perspective projection effect,
-we integrate the emissivity over line-of-sights from the solar position at $(x,y,z)=(8,0,0)$ kpc:
-\begin{equation}
-I = \frac{1}{\epsilon_{1}}\int \frac{dE}{dtd\epsilon_{1}dV} dl.
-\end{equation}
+One can see that the symmetric of the \textit{Fermi} bubbles can also be reproduced by tilted jets.\
 
@@
 \end{figure*}
-
-One can see that the general morphological characteristics of the \textit{Fermi} bubbles can be reproduced.\
 

### 2022-02-06 paper.tex
update

@@
 
-We perform the integration in \Cref{gammaray-emissivity} on each cell over the range of incident photon energy between\
+We perform the integration in \Cref{gammaray-emissivity} on each cell\
+over the range of CRe Lorentz factor, and\
+the range of incident photon energy between\
 $\epsilon_{\text{min}}=1.13\times10^{-4}$ eV (cosmic microwave background radiation) and\
 $\epsilon_{\text{max}}=13.59$ eV (optical starlight)\
-and over the range of CRe Lorentz factor\
 to obtain the simulated IC emissivities.

### 2022-02-06 paper.tex
update

@@
       The gray band represents the observational data of \citet{Ackermann2014}.\
-      The rows from top to bottom show the microwave (left) and gamma-ray (right) spectra\
-      with CRe spectra index $2.2, 2.4$ and $2.6$.\
+      The row from top to bottom shows the microwave (left) and gamma-ray (right) spectra\
+      with CRe spectral index $2.2, 2.4$ and $2.6$, respectively.\
       The CRe cutoff energy is $1.1\times10^{6}m_{\text{e}}c^{2}$ in all cases.

### 2022-02-06 paper.tex
update

@@
 
-We perform the integration in \Cref{gammaray-emissivity} on each cell\
+We perform the double integration in \Cref{gammaray-emissivity} on each cell\
 over the range of CRe Lorentz factor, and\

### 2022-02-07 paper.tex
update

@@
   \subsection{X-ray}
+  \label{X-ray}
   The X-ray emissivity in an energy range 0.6 -- 1.0 keV is computed\
@@
   The X-ray intensity map are then generated by projecting the emissivities\
-  along lines of sight from the solar position at $(x,y,z)=(8,0,0)$ kpc across the sky.
+  along lines of sight with resolutions of 0.5 degrees\
+  from the solar position at $(x,y,z)=(8,0,0)$ kpc across the sky.
 
@@
 
-\subsection{Gamma-ray and microwave emission}
+\subsection{Gamma-ray and microwave spectra: constraint on the CRe spectral index}
 
-  In this section, we compare the simulated gamma-ray and microwave\
-  spectra based on the leptonic AGN jet model with the\
-  observed spectra of the Fermi bubbles and the microwave haze.\
-  The gamma-rays originate from the inverse Compton scattering of ISRF by CRe.\
-  The CRe spectrum follows a power-law distribution\
-  with a spectral index $p=2.4$ and ranges from\
+In this section, we give the constraint on the CRe spectral index by\
+comparing the simulated gamma-ray and microwave spectra\
+with the observed spectra of the Fermi bubbles \citet{Ackermann2014}\
+and the microwave haze \citep{Dobler_2008}, respectively.\
+
+The simulated gamma-ray and microwave spectra is based on the\
+IC scattering and synchrotron from CRe, in which\
+the CRe spectrum follows a power-law distribution ranging from\
 $m_{\text{e}}c^2$ ($0.5$ MeV) to $1.1\times10^{6}m_{\text{e}}c^2$ ($550$ GeV),\
@@
 
-  \begin{figure}
-    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg-CR.png}
-    \caption{The slice of CR...}
-    \label{fig__jetI5+ismSeed3-45deg-CR}
-  \end{figure}
+%The microwave haze at 23 GHz was first detected by the \textit{WMAP} \citep{Dobler_2008}\
+%within the region $|b|<30^{\circ}$ above and below the Galactic plane,\
+%and later confirmed by the Planck Collaboration IX \citep{PlanckCollaborationIX2013}.
 
-  The emissivity of the upscattered photons at the energy $\epsilon_{1}$ is computed for\
+The IC emissivity of the upscattered photons at the energy $\epsilon_{1}$ is computed for\
 each computational cell in our simulations\
 using the Klein-Nishina IC cross-section \citep{Jones1968,BLUMENTHAL1970}\
-  to handle the ultra-relativistic CRe:
+to handle the scattering between ultra-relativistic CRe and ISRF:
 
@@
 
-\Cref{fig__gammaRay-map} shows the simulated gamma-ray photon flux compared with the observed one\
-in the energy bin $76.8-153.6$ GeV.\
-
-One can see that the symmetric of the \textit{Fermi} bubbles can also be reproduced by tilted jets.\
-
-\begin{figure*}
-  \includegraphics[width=\linewidth]{figures/fig__GammaRay_100e9_1e6_angle_000.png}
-  \caption{The observed (left) and simulated (right) photon flux\
-           in the energy bin $76.8-153.6$ GeV.\
-           Note that the left panel is the\
-           photon flux of the diffuse component reconstructed by the D$^3$PO\
-           algorithm \citep{Selig2015} that analyzes\
-           the photon data from the \textit{Fermi} Large Area Telescope \citep{Atwood2009}\
-           and removes the contribution from point-like component.
-           The red arrow at the center of the right\
-           panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
-           to the disc normal in 1.2 Myr.
-  }
-  \label{fig__gammaRay-map}
-\end{figure*}
-
-% assuming a uniform CR spectrum with energy cutoff of ~500 GeV\
-% and spectral index of 2.4, one could also reproduce the gamma-ray spectrum quite well.\
-% Note that the simulation time at this point is 12.39 Myr,\
-% much longer than the CR electron cooling time, so their Emax should\
-% have cooled to below 500 GeV by this time (we should think about how to estimate this).\
-% Therefore, the CRe generating the gamma-ray emission would need to be re-accelerated\
-% by some in-situ acceleration mechanisms such as shocks or turbulence.\
-% The forward shock is pretty far away from the gamma-ray bubbles,\
-% so it's more likely associated with turbulence.
-
-  Having successfully reproduced the morphology\
-  and spectrum of the \textit{Fermi} bubbles,\
-  we now ask whether CRe could also explain\
-  the Galactic microwave haze.
-
-  The microwave haze at 23 GHz was first detected by the \textit{WMAP} \citep{Dobler_2008}\
-  within the region $|b|<30^{\circ}$ above and below the Galactic plane,\
-  and later confirmed by the Planck Collaboration IX \citep{PlanckCollaborationIX2013}.
-
 The synchrotron emissivity with an isotropic electron pitch angle distribution\
@@
 
+For a given longitude and latitude range, the simulated spectra are\
+computed by projecting emissivities\
+as we project X-ray emissivities in Section \ref{X-ray},\
+and then we average the spectra over all the sight lines within the region on sky.
+
 \Cref{fig__gammaRaySynchtronSpectrum} shows the simulated microwave (left)\
 and gamma-ray (right) spectra averaged over the different patches (shown in the legends) of the sky.
+The row from top to bottom shows the microwave (left) and gamma-ray (right) spectra\
+with CRe spectral index $2.2, 2.4$ and $2.6$, respectively.\
 
-  For a given longitude and latitude range, the simulated spectra are\
-  computed by projecting the gamma-ray/microwave emissivities as a\
-  function of energy along finely sampled lines of sight\
-  (with resolutions of 0.5 degrees), and then we average the spectra\
-  over all the sight lines within the region.
-
-  Indeed, we find that the simulated gamma-ray\
+We find that the simulated gamma-ray\
 spectra for all latitudes exhibit a spectral cutoff at\
@@
 the observed cutoff energy.
-
-  %The enhanced emission at the lower latitude would likely be due to
-  %similar to the bottom right panel in Fig. 5 of YR17, which is dominated by\
-  %the optical starlight. That's also why in your plot above,\
-  %the high-latitude spectrum tends to be dimmer because of the decay of the ISRF intensity in optical.
 
@@
 \end{figure*}
+
+% assuming a uniform CR spectrum with energy cutoff of ~500 GeV\
+% and spectral index of 2.4, one could also reproduce the gamma-ray spectrum quite well.\
+% Note that the simulation time at this point is 12.39 Myr,\
+% much longer than the CR electron cooling time, so their Emax should\
+% have cooled to below 500 GeV by this time (we should think about how to estimate this).\
+% Therefore, the CRe generating the gamma-ray emission would need to be re-accelerated\
+% by some in-situ acceleration mechanisms such as shocks or turbulence.\
+% The forward shock is pretty far away from the gamma-ray bubbles,\
+% so it's more likely associated with turbulence.
+
+  Having successfully reproduced the morphology\
+  and spectrum of the \textit{Fermi} bubbles,\
+  we now ask whether CRe could also explain\
+  the Galactic microwave haze.
+
+  %The enhanced emission at the lower latitude would likely be due to
+  %similar to the bottom right panel in Fig. 5 of YR17, which is dominated by\
+  %the optical starlight. That's also why in your plot above,\
+  %the high-latitude spectrum tends to be dimmer because of the decay of the ISRF intensity in optical.
+
+\begin{figure*}
+  \includegraphics[width=\linewidth]{figures/fig__GammaRay_100e9_1e6_angle_000.png}
+  \caption{The observed (left) and simulated (right) photon flux\
+           in the energy bin $76.8-153.6$ GeV.\
+           Note that the left panel is the\
+           photon flux of the diffuse component reconstructed by the D$^3$PO\
+           algorithm \citep{Selig2015} that analyzes\
+           the photon data from the \textit{Fermi} Large Area Telescope \citep{Atwood2009}\
+           and removes the contribution from point-like component.
+           The red arrow at the center of the right\
+           panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
+           to the disc normal in 1.2 Myr.
+  }
+  \label{fig__gammaRay-map}
+\end{figure*}
+
+  We display the morphology of the \textit{Fermi} bubbles\
+  that emit gamma-rays from the inverse Compton scattering of ISRF by CRe.
+
+  \begin{figure}
+    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg-CR.png}
+    \caption{The slice of CR...}
+    \label{fig__jetI5+ismSeed3-45deg-CR}
+  \end{figure}
+
+\Cref{fig__gammaRay-map} shows the simulated gamma-ray photon flux compared with the observed one\
+in the energy bin $76.8-153.6$ GeV. One can see that the symmetric of the \textit{Fermi} bubbles\
+can also be realized by tilted jets as the eROSITA bubbles.\
 

### 2022-02-07 paper.tex
update

@@
 the CRe spectrum follows a power-law distribution ranging from\
-$m_{\text{e}}c^2$ ($0.5$ MeV) to $1.1\times10^{6}m_{\text{e}}c^2$ ($550$ GeV),\
+$m_{\text{e}}c^2$ ($0.5$ MeV) to $1.1\times10^{6}m_{\text{e}}c^2$ ($562.1$ GeV),\
 where $m_{\text{e}}c^2$ is the rest mass energy of an electron.
@@
    0.5\left(\frac{\epsilon_{1}}{m_{\text{e}}c^2}+\sqrt{\left(\frac{\epsilon_{1}}{m_{\text{e}}c^2}\right)^2+\
-   \frac{\epsilon_{1}}{\epsilon}}\right),
+   \frac{\epsilon_{1}}{\epsilon}}\right) \label{gamma-min},
   \end{align}
@@
 We find that the simulated gamma-ray\
-spectra for all latitudes exhibit a spectral cutoff at\
-similar energies 400--500 GeV, consistent with\
-the observed cutoff energy.
+spectra for all latitudes exhibit a spectral cutoff around energies 400--500 GeV,\
+consistent with the observed cutoff energy.\
+This is expected since
+the upscattered high-energy photons ($\epsilon_{1}\sim450$ GeV) is mainly from\
+the scatterings between the high-energy CRe ($\gamma\gtrapprox0.8\times10^{6}$) and optical starlight ($\epsilon \sim 10$ eV),\
+and therefore \Cref{gamma-min} can be reduced to $\epsilon_{1}\sim\gamma m_{\text{e}}c^2$\
+in the Klein--Nishina limit $\left(\text{i.e. }\epsilon_{1}\epsilon \gg \left(m_{\text{e}}c^2\right)^2\right)$,\
+implying most of the CRe energy (562.1 GeV) is carried away by the upscattered photons ( $\sim$ 450 GeV ).
 

### 2022-02-07 tets.py

@@ -1,0 +1,29 @@
+from parrot import Parrot
+import torch
+import warnings
+warnings.filterwarnings("ignore")
+
+'''
+uncomment to get reproducable paraphrase generations
+def random_state(seed):
+  torch.manual_seed(seed)
+  if torch.cuda.is_available():
+    torch.cuda.manual_seed_all(seed)
+
+random_state(1234)
+'''
+
+#Init models (make sure you init ONLY once if you integrate this to your code)
+parrot = Parrot(model_tag="prithivida/parrot_paraphraser_on_T5")
+
+phrases = ["Can you recommed some upscale restaurants in Newyork?",
+           "What are the famous places we should not miss in Russia?"
+]
+
+for phrase in phrases:
+  print("-"*100)
+  print("Input_phrase: ", phrase)
+  print("-"*100)
+  para_phrases = parrot.augment(input_phrase=phrase, use_gpu=False)
+  for para_phrase in para_phrases:
+   print(para_phrase)

### 2022-02-07 paper.tex
update

@@
 \Cref{fig__gammaRaySynchtronSpectrum} shows the simulated microwave (left)\
-and gamma-ray (right) spectra averaged over the different patches (shown in the legends) of the sky.
+and gamma-ray (right) spectra averaged over the different patches (shown in the legends) of the sky.\
 The row from top to bottom shows the microwave (left) and gamma-ray (right) spectra\
@@
 
-We find that the simulated gamma-ray\
-spectra for all latitudes exhibit a spectral cutoff around energies 400--500 GeV,\
+We find that the simulated gamma-ray spectra are well fitted by\
+the CRe spectral index 2.4 (the middle row),\
+and display several similar features as observed.
+
+First, the simulated and observed spectra of the \textit{Fermi} bubbles is\
+nearly latitude independent, and characterized by a broad bump that roughly peaks around $\sim10$ GeV.\
+However, the high-latitude spectrum tends to be slightly dimmer than low-latitude\
+probably because the optical intensity in ISRF decays with increasing latitude.
+
+Second, the gamma-ray spectra for all latitudes exhibit a spectral cutoff around energies 400--500 GeV,\
 consistent with the observed cutoff energy.\
 This is expected since
-the upscattered high-energy photons ($\epsilon_{1}\sim450$ GeV) is mainly from\
-the scatterings between the high-energy CRe ($\gamma\gtrapprox0.8\times10^{6}$) and optical starlight ($\epsilon \sim 10$ eV),\
+the upscattered high-energy photons ($\epsilon_{1}\sim450$ GeV) mainly arise from\
+the relativistic scatterings between the high-energy CRe ($\gtrapprox 408$ GeV)\
+and optical starlight ($\epsilon \sim 10$ eV),\
 and therefore \Cref{gamma-min} can be reduced to $\epsilon_{1}\sim\gamma m_{\text{e}}c^2$\
-in the Klein--Nishina limit $\left(\text{i.e. }\epsilon_{1}\epsilon \gg \left(m_{\text{e}}c^2\right)^2\right)$,\
-implying most of the CRe energy (562.1 GeV) is carried away by the upscattered photons ( $\sim$ 450 GeV ).
+in the Klein--Nishina limit\
+$\left(\text{i.e. }\epsilon_{1}\epsilon \gg \left(m_{\text{e}}c^2\right)^2\right)$,\
+implying most of the CRe energy is carried away by the upscattered photons.
 
@@
 
-  Having successfully reproduced the morphology\
-  and spectrum of the \textit{Fermi} bubbles,\
-  we now ask whether CRe could also explain\
-  the Galactic microwave haze.
+%  Having successfully reproduced the morphology\
+%  and spectrum of the \textit{Fermi} bubbles,\
+%  we now ask whether CRe could also explain\
+%  the Galactic microwave haze.
 

### 2022-02-07 paper.tex
update

@@
 with CRe spectral index $2.2, 2.4$ and $2.6$, respectively.\
+Several points are worth specific comment.\
 
-We find that the simulated gamma-ray spectra are well fitted by\
+First, we find that the simulated gamma-ray spectra are well fitted by\
 the CRe spectral index 2.4 (the middle row),\
-and display several similar features as observed.
+even simulated microwave spectra are marginally consistent with the observed.
 
-First, the simulated and observed spectra of the \textit{Fermi} bubbles is\
+Second, the simulated and observed gamma-ray spectra is\
 nearly latitude independent, and characterized by a broad bump that roughly peaks around $\sim10$ GeV.\
@@
 
-Second, the gamma-ray spectra for all latitudes exhibit a spectral cutoff around energies 400--500 GeV,\
+Third, the gamma-ray spectra for all latitudes indicate a spectral cutoff around energies 400--500 GeV,\
 consistent with the observed cutoff energy.\
@@
 the upscattered high-energy photons ($\epsilon_{1}\sim450$ GeV) mainly arise from\
-the relativistic scatterings between the high-energy CRe ($\gtrapprox 408$ GeV)\
+the scatterings between the relativistic CRe ($\gtrapprox 408$ GeV)\
 and optical starlight ($\epsilon \sim 10$ eV),\
@@
 implying most of the CRe energy is carried away by the upscattered photons.
+
+Fourth, the good agreement between the simulated and observed gamma-ray/microwave spectra\
+imply that the emission of the Fermi bubbles and\
+the microwave haze can be produced by the same high-energy electrons\
+via inverse Compton scatterings and synchrotron radiations\
+in the presence of ISRF and magnetic fields, respectively,\
+as previously suggested \citep{Su2010,Dobler2012}.
 
@@
 \end{figure*}
+
+ Finally, we display the morphology of the \textit{Fermi} bubbles\
+ that emit gamma-rays from the inverse Compton scattering of ISRF by CRe\
+ with the best-fit CRe sptral index 2.4
 
@@
 \end{figure*}
-
-  We display the morphology of the \textit{Fermi} bubbles\
-  that emit gamma-rays from the inverse Compton scattering of ISRF by CRe.
 

### 2022-02-07 paper.tex
update

@@
 consistent with the observed features, including the shape, the\
-surface brightness (for eROSITA bubbles), and the spectra (for \textit{Fermi} bubbles).\
+surface brightness, and the spectra of \textit{Fermi} and microwave haze \citep{Dobler_2008,PlanckCollaborationIX2013}.
 
@@
 
-The correlation between the multi-wavelength simulation suggest that\
-the \textit{Fermi} bubbles are produced by high-energy electrons\
-via an inverse Compton scattering process, as the same electrons can\
-also simultaneously produce synchrotron radiations in the\
-presence of magnetic fields.
-
 %\subsubsection{Hadronic process}

### 2022-02-07 paper.tex
update

@@
 a giant hourglass-shaped structure (eROSITA bubbles hereafter) at the GC,\
-but extending about twice as large as the \textit{Fermi} bubbles.\
+extending about twice as large as the \textit{Fermi} bubbles.\
 The large-scale X-ray structure\
@@
 consistent with the observed features, including the shape, the\
-surface brightness, and the spectra of \textit{Fermi} and microwave haze \citep{Dobler_2008,PlanckCollaborationIX2013}.
+surface brightness, and the spectra of \textit{Fermi} bubbles \citep{Ackermann2014}\
+and microwave haze \citep{Dobler_2008,PlanckCollaborationIX2013}.
 
@@
   The X-ray intensity map are then generated by projecting the emissivities\
-  along lines of sight with resolutions of 0.5 degrees\
+  along lines of sight with angular resolutions of 0.5 degrees\
   from the solar position at $(x,y,z)=(8,0,0)$ kpc across the sky.

### 2022-02-07 paper.tex
update

@@
   along lines of sight with angular resolutions of 0.5 degrees\
-  from the solar position at $(x,y,z)=(8,0,0)$ kpc across the sky.
+  pointing away from the solar position at $(x,y,z)=(8,0,0)$ kpc.
 

### 2022-02-07 paper.tex
update

@@
   The X-ray intensity map are then generated by projecting the emissivities\
-  along lines of sight with angular resolutions of 0.5 degrees\
-  pointing away from the solar position at $(x,y,z)=(8,0,0)$ kpc.
+  along lines of sight\
+  pointing away from the solar position at $(x,y,z)=(8,0,0)$ kpc\
+  with angular resolutions of 0.5 degrees\
 

### 2022-02-07 paper.tex
update

@@
 
-\keywords{keywords}
+\keywords{\textit{Fermi} bubbles, eROSITA bubbles, cosmic rays}
 
@@
 using the Klein-Nishina IC cross-section \citep{Jones1968,BLUMENTHAL1970}\
-to handle the scattering between ultra-relativistic CRe and ISRF:
+to handle the scattering between ultra-relativistic CRe and photons in the ISRF:
 

### 2022-02-09 paper.tex
update

@@
   \label{X-ray}
-  The X-ray emissivity in an energy range 0.6 -- 1.0 keV is computed\
+  The X-ray emissivity is computed\
   for each computational volume cell
@@
   \Cref{fig__xray_0.8keV_angle_000} shows\
-  the simulated photon count rate (top)\
-  in the 0.6--1.0 keV range at the present time,\
-  overlaid with the red arrow representing the direction of the bipolar jet,\
-  compared with the observed count rate (bottom) in the same energy bin.
+  the comparison between simulated (top) and observed (bottom) all-sky map\
+  in the range 0.6 -- 1.0 keV at the present time.\
+  In the simulated map, the red arrow at the center of map represents the direction of the bipolar jet,\
+  constantly ejecting at an angle of $45\circ$ to the disc normal in 1.2 Myr.
+
+% 1. The boundary of eROSITA bubbles is a shock
+% 2. North Polar Spur is not shown as it is a supernova remanent near us.
+% 3. Why the innermost bubbles does not appear?
+  The innermost bubbles, even though high density, is invisible in the simulated X-ray map as\
+  the temperature of innermost bubbles is around $1$ -- $10$ eV\
+  (see the temperature slice in \Cref{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp}).\
+  Consequently, the X-ray emission within the innermost bubbles
+  is severely suppressed by the cutoff $\exp\left[-h\nu/k_{B}T\right]$ in thermal Bremsstrahlung emissivity.
 
@@
 
-Third, the gamma-ray spectra for all latitudes indicate a spectral cutoff around energies 400--500 GeV,\
+Third, the gamma-ray spectra for all latitudes indicate a spectral cutoff around energies 400 -- 500 GeV,\
 consistent with the observed cutoff energy.\
@@
     \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg-CR.png}
-    \caption{The slice of CR...}
+    \caption{The slice of CR... $p_{CR}$ is much less than $p_{\text{gas}}$...}
     \label{fig__jetI5+ismSeed3-45deg-CR}

### 2022-02-09 paper.tex
update

@@
   We do not simulate the spectral evolution of the CR, and we neglected the cooling and heating processes of CRs,\
-  such as energy losses due to synchrotron and inverse Compton emission, and reacceleration in shocks.\
+  such as energy losses due to synchrotron and inverse Compton emission, and reacceleration in shocks/turbulences.\
 
@@
 
+ % the innermost bubbles is a reverse shock
+ % the forward shock
+
   \begin{figure}
@@
   along lines of sight\
-  pointing away from the solar position at $(x,y,z)=(8,0,0)$ kpc\
+  pointing away from the solar position at $(R_{\odot},0,0)=(8,0,0)$ kpc\
   with angular resolutions of 0.5 degrees\
@@
   In the simulated map, the red arrow at the center of map represents the direction of the bipolar jet,\
-  constantly ejecting at an angle of $45\circ$ to the disc normal in 1.2 Myr.
+  constantly ejecting at an angle of $45^{\circ}$ to the disc normal in 1.2 Myr.
 
-% 1. The boundary of eROSITA bubbles is a shock
+  \Cref{fig__x-ray-profile-0.8keV-000} displays the simulated count rate profiles (red)\
+  in the same energy band as \Cref{fig__xray_0.8keV_angle_000}\
+  cut at various galactic latitudes (as labelled), compared with the observation (black).\
+
+  \Cref{fig_xray-map} is quite revealing in several ways.\
+  First, the symmetric eROSITA bubbles can be formed by an inclined jet within a thin disk\
+  of dense interstellar medium.\
+
+  Second, as shown in \Cref{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp},\
+  the half-width of the outermost bubbles is around 7 kpc,\
+  corresponding to an half angular width $\sin^{-1}(7 \text{ kpc}/R_{\odot})\sim122^{\circ}$,\
+  which is as wide as the eROSITA bubbles in the simulated X-ray map (top panel in \Cref{fig__xray_0.8keV_angle_000}).\
+  We therefore suggest that the nature of eROSITA bubbles is indeed a forward shock\
+  propagating through the halo gas, as previously proposed by \citet{Predehl2020}.
+
 % 2. North Polar Spur is not shown as it is a supernova remanent near us.
-% 3. Why the innermost bubbles does not appear?
-  The innermost bubbles, even though high density, is invisible in the simulated X-ray map as\
+  Third, the innermost bubbles, even though with high column density, is invisible in the simulated X-ray map as\
   the temperature of innermost bubbles is around $1$ -- $10$ eV\
@@
   Consequently, the X-ray emission within the innermost bubbles
-  is severely suppressed by the cutoff $\exp\left[-h\nu/k_{B}T\right]$ in thermal Bremsstrahlung emissivity.
+  is severely suppressed by the cutoff $\exp\left[-h\nu/k_{B}T\right]$ in thermal Bremsstrahlung emissivity.\
+  This is the reason why the innermost bubbles is unseen in the observation.
 
@@
 
+ We close on a speculative note that predicts an existence of a third bubbles for
+ future observations.
+
 % assuming a uniform CR spectrum with energy cutoff of ~500 GeV\
@@
 
+We therefore suggest that the Fermi bubbles and the eROSITA structure are physically related,\
+as suggested by \citet{Predehl2020}.
+
+Our discovery confirms the previously suggested common origin of the two objects \citep{Sofue2000,Kataoka2018}
+
 \section*{Data Availability}

### 2022-02-09 tets.py

@@ -16,8 +16,8 @@ random_state(1234)
 #Init models (make sure you init ONLY once if you integrate this to your code)
 parrot = Parrot(model_tag="prithivida/parrot_paraphraser_on_T5")
 
-phrases = ["Can you recommed some upscale restaurants in Newyork?",
-           "What are the famous places we should not miss in Russia?"
+phrases = [
+"as previously suggested by him"
 ]
 
 for phrase in phrases:

### 2022-02-09 paper.tex
update

@@
     \subfigure[Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
-               (photons s$^{-1}$ deg$^{-2}$) in the 0.6-1.0 keV range.\
+               (photons s$^{-1}$ deg$^{-2}$) in the 0.6 -- 1.0 keV range.\
                Throughout this paper we show sky maps\

### 2022-02-09 paper.tex
update

@@
   Consequently, the X-ray emission within the innermost bubbles
-  is severely suppressed by the cutoff $\exp\left[-h\nu/k_{B}T\right]$ in thermal Bremsstrahlung emissivity.\
+  is severely suppressed by the cutoff $\exp\left[-h\nu/k_{B}T\right]$ in the thermal Bremsstrahlung emissivity.\
   This is the reason why the innermost bubbles is unseen in the observation.

### 2022-02-09 paper.tex
update

@@
   \begin{equation}
-     |\mathbf{B}(R, z)|=B_{0}\exp{-z/z_{0}}\exp{-R/R_{0}},
+     |\mathbf{B}(R, z)|=B_{0}\exp\left[-\frac{z}{z_{0}}\right]\exp\left[-\frac{R}{R_{0}}\right],
      \label{magnetic-field}
@@
   \Cref{fig_xray-map} is quite revealing in several ways.\
-  First, the symmetric eROSITA bubbles can be formed by an inclined jet within a thin disk\
+
+  First, the broad agreement between simulated and observed X-ray map hint that\
+  the symmetric eROSITA bubbles can be properly formed by an inclined jet within a thin disk\
   of dense interstellar medium.\
@@
 
+The broad agreement between simulated and observed X-ray map provides supporting\
+evidence for the inclined jet scenario,
 \section*{Data Availability}

### 2022-02-09 paper.tex
update

@@
 
-  The bipolar jets are constantly ejected from a cylindrical source within a jet duration time $t=0--1.2$ Myr,\
+  The bipolar jets are constantly ejected from a cylindrical source within a jet duration time $t=0$ -- $1.2$ Myr,\
   allowing the total ejected energy $1.2\times10^{56}$ erg is between\
-  $8\times10^{55}$ erg and $1.3\times10^{56}$ erg, estimated by \citet{Predehl2020}.\
+  $8\times10^{55}$ -- $1.3\times10^{56}$ erg, estimated by \citet{Predehl2020}.\
 
@@
   cut at various galactic latitudes (as labelled), compared with the observation (black).\
-
   \Cref{fig_xray-map} is quite revealing in several ways.\

### 2022-02-09 paper.tex
update

@@
   First, the broad agreement between simulated and observed X-ray map hint that\
-  the symmetric eROSITA bubbles can be properly formed by an inclined jet within a thin disk\
+  the full vertical extent of the eROSITA bubbles can be properly formed by an inclined jet within a thin disk\
   of dense interstellar medium.\

### 2022-02-09 paper.tex
update

--- 2022-02-09 paper.tex
@@
 
-  First, the broad agreement between simulated and observed X-ray map hint that\
-  the symmetric eROSITA bubbles can be properly formed by an inclined jet within a thin disk\
+  First, the broad agreement between simulated and observed X-ray maps hint that\
+  the full vertical extent of the eROSITA bubbles can be properly formed by an inclined jet within a thin disk\
   of dense interstellar medium.\

### 2022-02-09 paper.tex
update

@@
 % 2. North Polar Spur is not shown as it is a supernova remanent near us.
-  Third, the innermost bubbles, even though with high column density, is invisible in the simulated X-ray map as\
+  Third, the innermost bubbles\
+  shown in \Cref{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp},\
+  even though with high column density, is invisible in the simulated X-ray map as\
   the temperature of innermost bubbles is around $1$ -- $10$ eV\

### 2022-02-13 paper.tex
update

--- 2022-02-09 paper.tex
@@
 observation \citep{Gallimore2006} has proposed that\
-there is a lack of preferred orientation of jets with respect to a disc normal.\
+there is a lack of preferred orientation of jets with respect to\
+the rotation axis of a galatic plane (disc normal, hereafter).\
 In contrast, a number of galaxies in which the jets are tilted to the disc normal\
@@
 around a jet source to deflects and decelerates the inclined jets,\
-in an attempt to remedy the symmetry problem of the Galactic bubbles.\
+in an attempt to resolve the symmetry problem of the Galactic bubbles.\
 
@@
 
+  %, and prevent the disk from destruction by .
+  % ablate
+
   The diameter and height of cylindrical source are 4 pc, leading to the source volume $\sim 50 \text{ pc}^{3}$ is\
@@
 
- \Cref{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp} shows\
+ \Cref{fig__jetI5+ismSeed3-45deg} shows\
  the slices of pressure (top), temperature (middile), number density (bottom)\
@@
   \begin{figure}
-    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp.png}
+    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg.png}
     \caption{
@@
              }
-    \label{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp}
+    \label{fig__jetI5+ismSeed3-45deg}
   \end{figure}
@@
 
-  First, the broad agreement between simulated and observed X-ray map hint that\
+  First, the broad agreement between simulated and observed X-ray maps hints that\
   the full vertical extent of the eROSITA bubbles can be properly formed by an inclined jet within a thin disk\
@@
 
-  Second, as shown in \Cref{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp},\
+  Second, as shown in \Cref{fig__jetI5+ismSeed3-45deg},\
   the half-width of the outermost bubbles is around 7 kpc,\
@@
   which is as wide as the eROSITA bubbles in the simulated X-ray map (top panel in \Cref{fig__xray_0.8keV_angle_000}).\
-  We therefore suggest that the nature of eROSITA bubbles is indeed a forward shock\
-  propagating through the halo gas, as previously proposed by \citet{Predehl2020}.
+  We therefore suggest that the nature of eROSITA bubbles is indeed a forward shocks\
+  that have been driven into the northern and the southern Galactic halo,
+  as previously proposed by \citet{Predehl2020}.
 
 % 2. North Polar Spur is not shown as it is a supernova remanent near us.
-  Third, the innermost bubbles, even though with high column density, is invisible in the simulated X-ray map as\
+  Third, the innermost bubbles\
+  shown in \Cref{fig__jetI5+ismSeed3-45deg},\
+  even though with high column density, is invisible in the simulated X-ray map as\
   the temperature of innermost bubbles is around $1$ -- $10$ eV\
-  (see the temperature slice in \Cref{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp}).\
+  (see the temperature slice in \Cref{fig__jetI5+ismSeed3-45deg}).\
   Consequently, the X-ray emission within the innermost bubbles
@@
 \label{Conclusions}
+The symmetry of the Galactic bubbles is worth exploring since observations\
+show that there is no preference for the orientation of AGN jets relative to\
+the rotation axis of a galactic plane.
+
+In this work, we introduce a thin, dense disk composed of interstellar medium\
+to divert the inclined jet at an angle $45^{\circ}$\
+to the disk normal in the past energetic event of the central SMBH.
+
+The jet
+
+Also, We investigate the properties of the Galactic bubbles and the microwave\
+haze using 3D special relativistic hydrodynamic simulations of CR injection from\
+the SMBH assuming the leptonic model.
+
+Our findings are as follows.
+
+\begin{itemize}
+
+\item The Galactic bubbles are nearly symmetric about the Galactic plane even the jet is at an angle $45^{\circ}$\
+      with respect to the disc normal.
+\item The randomness of clumpy disk has a insignificant impact on the overall dynamic of the Galactic bubbles.\
+      The ambient stratification facilitates the eROSITA bubbles elongation significantly.
+      The development of the inverse shocks are always associated with the dense disc.
+\item The edge of the eROSITA bubbles is a forward shock,\
+      originally driven by an inclined bipolar jets that emanated from the GC 12.39 million years ago,\
+      and stretched by stratified ambient subsequently.
+\item The nature of the \textit{Fermi} bubbles are essentially a turbulent flows\
+      that can stochastically accelerate CRe. Associated with
+      contact discontinuity\
+\item
+
+\end{itemize}
+
+Over the past few years, there have been numerous efforts,\
+both observational and theoretical, to uncover the nature of the Galactic bubbles.
+
+Spektr-RG \citep{Sunyaev2021} and eROSITA \citep{Predehl2021}
+
 We have found qualitative similarities between the results our simulations\

### 2022-02-13 tets.py

@@ -17,7 +17,7 @@ random_state(1234)
 parrot = Parrot(model_tag="prithivida/parrot_paraphraser_on_T5")
 
 phrases = [
-"as previously suggested by him"
+"To this end, this work introduces a thin disk of dense interstellar medium around the jet source to deflect and decelerate the tilted jet in an attempt to resolve the galactic bubble's symmetry."
 ]
 
 for phrase in phrases:

### 2022-02-13 paper.tex
update

@@
  is always associated with the disc, and without the disc,\
- the outermost bubbles and the turbulent region will be tilted,
+ the outermost bubbles and the turbulent region will be tilted,\
  indicating the dense disc is crucial for\
  the symmetry of the Galactic bubbles and for the innermost bubbles formation.
+
+ % shock wave, followed by a contact discontinuity, moves to the right.
 
@@
       originally driven by an inclined bipolar jets that emanated from the GC 12.39 million years ago,\
-      and stretched by stratified ambient subsequently.
-\item The nature of the \textit{Fermi} bubbles are essentially a turbulent flows\
-      that can stochastically accelerate CRe. Associated with
-      contact discontinuity\
-\item
-
+      and significantly stretched by stratified ambient afterwards.
+\item The nature of the \textit{Fermi} bubbles are essentially a turbulent and high-temperature ($\sim1$ keV)\
+      plasma in pressure balance with the external medium. Associated with the Galactic magnetic filed may\
+      lead to stochastic acceleration of CRe, and balanced with radiative cooling.\
+      We will investigate the competition between CRe acceleration and radiative cooling in a future work.
 \end{itemize}

### 2022-02-13 paper.tex
update

@@
 \item The edge of the eROSITA bubbles is a forward shock,\
-      originally driven by an inclined bipolar jets that emanated from the GC 12.39 million years ago,\
-      and significantly stretched by stratified ambient afterwards.
+      originally driven by a oblique bipolar jets emanating from the GC 12.39 million years ago,\
+      and significantly stretched by the stratified ambient afterwards.
 \item The nature of the \textit{Fermi} bubbles are essentially a turbulent and high-temperature ($\sim1$ keV)\

### 2022-02-13 paper.tex
update

@@
       and significantly stretched by the stratified ambient afterwards.
-\item The nature of the \textit{Fermi} bubbles are essentially a turbulent and high-temperature ($\sim1$ keV)\
+\item Followed by the forward shock is a contact discontinuity,\
+      which we interpret as the edge of the \textit{Fermi} bubbles\
+      The nature of the \textit{Fermi} bubbles are essentially a turbulent and high-temperature ($\sim1$ keV)\
       plasma in pressure balance with the external medium. Associated with the Galactic magnetic filed may\

### 2022-02-13 paper.tex
update

--- 2022-02-13 paper.tex
@@
       originally driven by a oblique bipolar jets emanating from the GC 12.39 million years ago,\
-      and significantly stretched by the stratified ambient afterwards.
-\item The nature of the \textit{Fermi} bubbles are essentially a turbulent and high-temperature ($\sim1$ keV)\
+      and significantly stretched by the stratified atmosphere afterwards.
+\item Followed by the forward shock is a contact discontinuity,\
+      which we interpret as the edge of the \textit{Fermi} bubbles.\
+      The nature of the \textit{Fermi} bubbles are essentially a turbulent and high-temperature ($\sim1$ keV)\
       plasma in pressure balance with the external medium. Associated with the Galactic magnetic filed may\

### 2022-02-13 paper.tex
update

@@
 
-  The bipolar jets are constantly ejected from a cylindrical source within a jet duration time $t=0$ -- $1.2$ Myr,\
-  allowing the total ejected energy $1.2\times10^{56}$ erg is between\
-  $8\times10^{55}$ -- $1.3\times10^{56}$ erg, estimated by \citet{Predehl2020}.\
-
-  %, and prevent the disk from destruction by .
-  % ablate
+  The bipolar jets are constantly ejected from a cylindrical source at the beginning of simulation ($t=0$)\
+  and suddenly quenched at $t=1.2$ Myr before fully breaking out the disc.\
+  Without quenching, the Galactic bubbles at the present time will be asymmetric about the Galactic plane.
+  The jet duration (1.2 Myr) allows the total ejected energy to be $1.2\times10^{56}$ erg, bracketed by\
+  $8\times10^{55}$ and $1.3\times10^{56}$ erg, estimated by \citet{Predehl2020}.\
 
@@
 
-The jet
-
 Also, We investigate the properties of the Galactic bubbles and the microwave\
@@
       The nature of the \textit{Fermi} bubbles are essentially a turbulent and high-temperature ($\sim1$ keV)\
-      plasma in pressure balance with the external medium. Associated with the Galactic magnetic filed may\
-      lead to stochastic acceleration of CRe, and balanced with radiative cooling.\
+      plasma in pressure balance with the external medium. Associated with the Galactic magnetic filed\
+      will leads to stochastic acceleration of CRe, and probably balanced with radiative cooling.\
       We will investigate the competition between CRe acceleration and radiative cooling in a future work.

### 2022-02-13 paper.tex
update

@@
       plasma in pressure balance with the external medium. Associated with the Galactic magnetic filed\
-      will leads to stochastic acceleration of CRe, and probably balanced with radiative cooling.\
+      will leads to stochastic acceleration of CRe, and probably balanced with IC and synchrotron cooling.\
       We will investigate the competition between CRe acceleration and radiative cooling in a future work.

### 2022-02-13 paper.tex
update

--- 2022-02-13 paper.tex
@@
 
+  \Cref{fig__numberDensityHistogram} plots the volume filling factor as a function of\
+  initial number density within the disc without jet source.\
+
   \Cref{fig__zoom-in-disc} shows a close-up view of the\
@@
   in the y-z plane through the center of the disc.
-
-  \Cref{fig__numberDensityHistogram} plots the volume filling factor as a function of\
-  initial number density within the disc without jet source.\
 
@@
       The nature of the \textit{Fermi} bubbles are essentially a turbulent and high-temperature ($\sim1$ keV)\
-      plasma in pressure balance with the external medium. Associated with the Galactic magnetic filed\
-      will leads to stochastic acceleration of CRe, and probably balanced with radiative cooling.\
+      plasma in pressure balance with the external medium. Associated with the Galactic magnetic field\
+      will lead to the stochastic acceleration of CRe, and probably balanced with the IC and synchrotron cooling.\
       We will investigate the competition between CRe acceleration and radiative cooling in a future work.

### 2022-02-14 paper.tex
update

@@
 the CRe spectral index 2.4 (the middle row),\
-even simulated microwave spectra are marginally consistent with the observed.
+despite the simulated microwave spectra are marginally consistent with the observed.
 
@@
 
-\item The Galactic bubbles are nearly symmetric about the Galactic plane even the jet is at an angle $45^{\circ}$\
+\item The Galactic bubbles are nearly symmetric about the Galactic plane albeit the jet is at an angle $45^{\circ}$\
       with respect to the disc normal.
@@
       We will investigate the competition between CRe acceleration and radiative cooling in a future work.
+\item The same leptotonic CRe can simultaneously\
+      account for the \textit{Fermi} bubbles and haze emission suggested that\
+      they have their origin around the GC,\
+      and that the magnetic fields within the bubbles are close to the exponentially distributed\
+      Galactic magnetic field.
 \end{itemize}

### 2022-02-14 tets.py

@@ -17,7 +17,7 @@ random_state(1234)
 parrot = Parrot(model_tag="prithivida/parrot_paraphraser_on_T5")
 
 phrases = [
-"To this end, this work introduces a thin disk of dense interstellar medium around the jet source to deflect and decelerate the tilted jet in an attempt to resolve the galactic bubble's symmetry."
+"The same leptotonic CRe can simultaneously account for the Fermi bubbles and haze emission suggested that the magnetic fields within the bubbles are close to the exponentially distributed Galactic magnetic field. Moreover, the fact that the bubbles are symmetric across the Galactic plane and also centered on the GC endorsing the assumption that the bubbles, and the associated gamma-ray emissions, have their origin at the GC."
 ]
 
 for phrase in phrases:

### 2022-02-14 paper.tex
update

@@
 \item The Galactic bubbles are nearly symmetric about the Galactic plane albeit the jet is at an angle $45^{\circ}$\
-      with respect to the disc normal.
+      with respect to the disc normal.\
+      The broad agreement between simulated and observed mutiwavelength features\
+      provides supporting evidence for the inclined jet scenario, and also\
+      releases the caveat given by earlier simulation-based studies:\
+      the jets shall be vertical to the disc normal.
 \item The randomness of clumpy disk has a insignificant impact on the overall dynamic of the Galactic bubbles.\
@@
       account for the \textit{Fermi} bubbles and haze emission suggested that\
-      they have their origin around the GC,\
+      they are physically related around the GC,\
       and that the magnetic fields within the bubbles are close to the exponentially distributed\
@@
 
-Over the past few years, there have been numerous efforts,\
-both observational and theoretical, to uncover the nature of the Galactic bubbles.
-
-Spektr-RG \citep{Sunyaev2021} and eROSITA \citep{Predehl2021}
+%Over the past few years, there have been numerous efforts,\
+%both observational and theoretical, to uncover the nature of the Galactic bubbles.
+%
+%
+%Spektr-RG \citep{Sunyaev2021} and eROSITA \citep{Predehl2021}
 
@@
 
-We therefore suggest that the Fermi bubbles and the eROSITA structure are physically related,\
-as suggested by \citet{Predehl2020}.
+%We therefore suggest that the Fermi bubbles and the eROSITA structure are physically related,\
+%as suggested by \citet{Predehl2020}.
 
-Our discovery confirms the previously suggested common origin of the two objects \citep{Sofue2000,Kataoka2018}
+%Our discovery confirms the previously suggested common origin of the two objects \citep{Sofue2000,Kataoka2018}
 
-The broad agreement between simulated and observed X-ray map provides supporting\
-evidence for the inclined jet scenario,
 \section*{Data Availability}

### 2022-02-14 paper.tex
update

@@
       which we interpret as the edge of the \textit{Fermi} bubbles.\
-      The nature of the \textit{Fermi} bubbles are essentially a turbulent and high-temperature ($\sim1$ keV)\
+      The nature of the \textit{Fermi} bubbles is essentially a turbulent and high-temperature ($\sim1$ keV)\
       plasma in pressure balance with the external medium. Associated with the Galactic magnetic field\

### 2022-02-15 paper.tex
update

@@
 the rotation axis of a galatic plane (disc normal, hereafter).\
-In contrast, a number of galaxies in which the jets are tilted to the disc normal\
+In contrast, a number of galaxies in which the jets are oblique to the disc normal\
 (e.g. NGC 3079, \citealt{Cecil2001}; NGC 1052, \citealt{Dopita2015}),\
@@
 
-  With the help of the isothermal and hydrostatic equilibrium conditions,\
+  With the recourse to the isothermal and hydrostatic equilibrium conditions,\
   and assuming the interfaces between isothermal disc and atmosphere are in thermal pressure equilibrium,\
@@
 
-\subsection{Morphology}
+\subsection{Morphology and properties of Galactic bubbles}
 
@@
  at the end of simulation $t=12.39$ Myr.\
- The slices pass through the bipolar jet source injecting along $z=-y$ direction\
- for a duration $t=0$--$1.2$ Myr.\
+ The slices pass through the bipolar jet source injecting along $z=-y$ direction.
+
+ The fiducial run (leftmost column) specified in Section \ref{Methodology}\
+ shows that the edge of the outermost bubbles is indeed a forward shock,\
+ expanding roughly 14 kpc above and below the Galactic plane,\
+ and with a radius of about 7 kpc along the plane, as suggested by \citet{Predehl2020}.
+
+ \Cref{} shows the temperature profile cut at the dashed-dotted line in temperature slice.\
+ The temperature profile indicates that most of the volume between the forward shock and the turbulent region\
+ is around 0.3 keV \citep{Miller2016,Kataoka2018}
+
+ originally driven by an oblique bipolar jets emanating from the GC 12.39 million years ago,\
+ and significantly stretched by the stratified atmosphere afterwards.
+
  Comparison between the clumpy (first column from left)\
@@
  is always associated with the disc, and without the disc,\
- the outermost bubbles and the turbulent region will be tilted,\
+ the outermost bubbles and the turbulent region will be oblique,\
  indicating the dense disc is crucial for\
@@
 
- % the innermost bubbles is a reverse shock
+ % the innermost bubbles is an expanding reverse shock
  % the forward shock
@@
              is always associated with the disc, and without the disc,\
-             the outermost bubbles and the turbulent region will be tilted,
+             the outermost bubbles and the turbulent region will be oblique,
              indicating the dense disc is crucial for\
@@
 in the energy bin $76.8-153.6$ GeV. One can see that the symmetric of the \textit{Fermi} bubbles\
-can also be realized by tilted jets as the eROSITA bubbles.\
+can also be realized by oblique jets as the eROSITA bubbles.\
 
@@
 \label{Conclusions}
-The symmetry of the Galactic bubbles is worth exploring since observations\
-show that there is no preference for the orientation of AGN jets relative to\
-the rotation axis of a galactic plane.
+%The symmetry of the Galactic bubbles is worth exploring since observations\
+%show that there is no preference for the orientation of AGN jets relative to\
+%the rotation axis of a galactic plane.
 
@@
 \item The edge of the eROSITA bubbles is a forward shock,\
-      originally driven by a oblique bipolar jets emanating from the GC 12.39 million years ago,\
+      originally driven by an oblique bipolar jets emanating from the GC 12.39 million years ago,\
       and significantly stretched by the stratified atmosphere afterwards.
@@
       We will investigate the competition between CRe acceleration and radiative cooling in a future work.
+\item According to the microwave and leptonic gamma-ray spectra, the best-fitting\
+      CRe power-law index is found to be -2.4.
 \item The same leptotonic CRe can simultaneously\

### 2022-02-15 paper.tex
update

@@
  shows that the edge of the outermost bubbles is indeed a forward shock,\
- expanding roughly 14 kpc above and below the Galactic plane,\
- and with a radius of about 7 kpc along the plane, as suggested by \citet{Predehl2020}.
+ expanding roughly 12.5 kpc above and below the Galactic plane,\
+ and with a radius of about 6.8 kpc along the plane.\
 
- \Cref{} shows the temperature profile cut at the dashed-dotted line in temperature slice.\
- The temperature profile indicates that most of the volume between the forward shock and the turbulent region\
- is around 0.3 keV \citep{Miller2016,Kataoka2018}
+ \Cref{fig__profile} shows the profiles cut at the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.\
+ The temperature profile indicates that most of the region between the forward shock and the turbulent region\
+ is around 0.3-0.4 keV \citep{Miller2016,Kataoka2018}
 
@@
     \label{fig__jetI5+ismSeed3-45deg}
+  \end{figure}
+
+  \begin{figure}
+    \includegraphics[width=\columnwidth]{figures/fig__profile.png}
+    \caption{
+             The profile along the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.
+     }
+    \label{fig__profile}
   \end{figure}

### 2022-02-15 paper.tex
update

@@
 
- The fiducial run (leftmost column) specified in Section \ref{Methodology}\
+ The fiducial run (leftmost column) with the initial condition specified in Section \ref{Methodology}\
  shows that the edge of the outermost bubbles is indeed a forward shock,\
- expanding roughly 12.5 kpc above and below the Galactic plane,\
+ expanding 12.5 kpc above and below the Galactic plane,\
  and with a radius of about 6.8 kpc along the plane.\
+ We note that the overall extent of the outermost bubbles is comparable to\
+ the two spherical objects of a radius 6-7 kpc proposed by \citet{Predehl2020} for modeling the eROSITA bubbles.
 
- \Cref{fig__profile} shows the profiles cut at the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.\
+ \Cref{fig__profile} shows the profiles) cut at the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.\
  The temperature profile indicates that most of the region between the forward shock and the turbulent region\

### 2022-02-15 paper.tex
update

@@
 
- \Cref{fig__profile} shows the profiles) cut at the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.\
- The temperature profile indicates that most of the region between the forward shock and the turbulent region\
- is around 0.3-0.4 keV \citep{Miller2016,Kataoka2018}
+ The left column of \Cref{fig__profile} shows the profiles cut at\
+ the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.\
+ The temperature profile in the left column indicates that\
+ most of the region between the forward shock and the turbulent region\
+ is around 0.3-0.4 keV \citep{Miller2016,Kataoka2018}.
 
- originally driven by an oblique bipolar jets emanating from the GC 12.39 million years ago,\
- and significantly stretched by the stratified atmosphere afterwards.
+ Followed by the forward shock is a turbulent and high temperature ($\sim2$ keV) plasma.\
+ By observing X-ray absorption lines through the hot\
+ gaseous halo along many different sight lines in the sky, Miller& Bregman (2012)\
+ found that the ratio between O viii and O vii\
+ column densities is enhanced for sight lines that pass through\
+ the Fermi bubbles, indicating gas temperature of a few times keV\
+ inside the bubbles.
+
+ % Reverse shock
 
@@
  the symmetry of the Galactic bubbles and for the innermost bubbles formation.
+
+ %originally driven by an oblique bipolar jets emanating from the GC 12.39 million years ago,\
+ %and significantly stretched by the stratified atmosphere afterwards.
 

### 2022-02-15 paper.tex
update

@@
  By observing X-ray absorption lines through the hot\
- gaseous halo along many different sight lines in the sky, Miller& Bregman (2012)\
+ gaseous halo along many different sight lines in the sky, Miller\& Bregman (2012)\
  found that the ratio between O viii and O vii\

### 2022-02-15 paper.tex
update

@@
  expanding 12.5 kpc above and below the Galactic plane,\
- and with a radius of about 6.8 kpc along the plane.\
+ and with a semiminor axis about 6.8 kpc on the plane.\
  We note that the overall extent of the outermost bubbles is comparable to\

### 2022-02-16 paper.tex
update

--- 2022-02-15 paper.tex
@@
 \begin{abstract}
+% out of the Galactic center on either side of the Galactic disk
 \end{abstract}
@@
  expanding 12.5 kpc above and below the Galactic plane,\
- and with a radius of about 6.8 kpc along the plane.\
+ and with a semiminor axis about 6.8 kpc on the plane.\
  We note that the overall extent of the outermost bubbles is comparable to\
- the two spherical objects of a radius 6-7 kpc proposed by \citet{Predehl2020} for modeling the eROSITA bubbles.
+ the two spherical objects of a radius 6-7 kpc proposed by \citet{Predehl2020} for modeling the eROSITA bubbles\
+ based on X-ray emissions.
 
@@
  The temperature profile in the left column indicates that\
- most of the region between the forward shock and the turbulent region\
- is around 0.3-0.4 keV \citep{Miller2016,Kataoka2018}.
+ most of the region between the forward shock and the turbulent zone\
+ is around 0.3-0.4 keV, similar to that observed by \citet{Miller2016} and \citet{Kataoka2018}.
 
- Followed by the forward shock is a turbulent and high temperature ($\sim2$ keV) plasma.\
- By observing X-ray absorption lines through the hot\
- gaseous halo along many different sight lines in the sky, Miller& Bregman (2012)\
- found that the ratio between O viii and O vii\
- column densities is enhanced for sight lines that pass through\
- the Fermi bubbles, indicating gas temperature of a few times keV\
- inside the bubbles.
+ Followed by the forward shock is a turbulent and hot plasma.\
+ The full extent of the hot plasma is approximately agree with the observation \citep{Su2010}.
+ Moreover, the temperature of the plasma is high as 2 keV, comparable to that of the \textit{Fermi} bubbles\
+ by observing X-ray absorption lines through the hot\
+ gaseous halo along many different sight lines in the sky \citep{Miller_2013}.\
+
+ % which we will interpret as the \textit{Fermi} bubbles.\
 

### 2022-02-16 paper.tex
update

@@
  The full extent of the hot plasma is approximately agree with the observation \citep{Su2010}.
- Moreover, the temperature of the plasma is high as 2 keV, comparable to that of the \textit{Fermi} bubbles\
+ Also, the temperature of the plasma is high as 2 keV, comparable to that of the \textit{Fermi} bubbles\
  by observing X-ray absorption lines through the hot\
  gaseous halo along many different sight lines in the sky \citep{Miller_2013}.\
+
+ % pressure balance, contact discontinuity
 

### 2022-02-16 paper.tex
update

--- 2022-02-16 paper.tex
@@
 
- The left column of \Cref{fig__profile} shows the profiles cut at\
- the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.\
- The temperature profile in the left column indicates that\
+ The temperature profile (left column of \Cref{fig__profile}) along the positive z-axis in\
+ \Cref{fig__jetI5+ismSeed3-45deg} indicates that\
  most of the region between the forward shock and the turbulent zone\
@@
  Followed by the forward shock is a turbulent and hot plasma.\
- The full extent of the hot plasma is approximately agree with the observation \citep{Su2010}.
- Moreover, the temperature of the plasma is high as 2 keV, comparable to that of the \textit{Fermi} bubbles\
+ As shown in the temperature or density slices of the fiducial run,\
+ the full extent of the turbulent plasma is approximately agree with\
+ that of the \textit{Fermi} bubbles \citep{Su2010}.
+ Also, the temperature of the plasma is as high as 2 keV, comparable to that inside the \textit{Fermi} bubbles\
  by observing X-ray absorption lines through the hot\
  gaseous halo along many different sight lines in the sky \citep{Miller_2013}.\
+ We also note that the turbulence within the hot plasma is in pressure balance with the external medium,\
+ suggesting that the outer edge of the \textit{Fermi} bubbles\
+ is a tangling contact discontinuity rather than a shock.
 
- % which we will interpret as the \textit{Fermi} bubbles.\
+ The most interesting finding is that there is a innermost bubbles\
+ (dashed box in top left panel of \Cref{fig__jetI5+ismSeed3-45deg})\
+ also extending out from the Galactic center on either side of the thin disk.\
+ The innermost bubbles are cold (1-10 eV), dense ($10^{-4}$ -- $10^{-2}$ cm$^{-3}$),\
+ and underpressured with respect to the turbulent plasma.
 

### 2022-02-16 paper.tex
update

@@
  The innermost bubbles are cold (1-10 eV), dense ($10^{-4}$ -- $10^{-2}$ cm$^{-3}$),\
- and underpressured with respect to the turbulent plasma.
-
- % Reverse shock
+ and underpressured with respect to the turbulent plasma.\
+ Moreover, the close-up view of profiles around $z=3.7$ kpc (right column of \Cref{fig__profile})
+ demonstrates that there is a sharp pressure jump and dense shell at $z=3.61$ kpc
+ indicating that the innermost bubbles are an expanding reverse shock.
 
@@
   pointing away from the solar position at $(R_{\odot},0,0)=(8,0,0)$ kpc\
-  with angular resolutions of 0.5 degrees\
+  with angular resolutions of 0.5 degrees, where $R_{\odot}$ is the Sun-GC distance.
 

### 2022-02-16 paper.tex
update

@@
  (dashed box in top left panel of \Cref{fig__jetI5+ismSeed3-45deg})\
- also extending out from the Galactic center on either side of the thin disk.\
+ extending out from the Galactic center on either side of the thin disk.\
  The innermost bubbles are cold (1-10 eV), dense ($10^{-4}$ -- $10^{-2}$ cm$^{-3}$),\
@@
  Moreover, the close-up view of profiles around $z=3.7$ kpc (right column of \Cref{fig__profile})
- demonstrates that there is a sharp pressure jump and dense shell at $z=3.61$ kpc
- indicating that the innermost bubbles are an expanding reverse shock.
+ demonstrates that there is a sharp pressure jump and dense shell at $z=3.61$ kpc,\
+ indicating that the innermost bubbles are an expanding reverse shock.\
+ We also find that the turbulent plasma is bracketed between the downstream of reverse shock\
+ and of the outermost forward shock, thus heating the turbulent plasma up considerably.
 
- Comparison between the clumpy (first column from left)\
- and the smooth disc (second) in a stratified atmosphere\
- shows that the initial density distribution of the dense disc has an insignificant effect\
+ We stressed that either the outermost, turbulent plasma, or innermost bubbles\
+ are symmetric about the Galactic plane despite the jet is tilted to the disk normal\
+ at an angle $45^{\circ}$.
+
+ To explore how the disk affect the formation of the Galactic bubbles,\
+ we compare the fiducial run (first column from left)\
+ with the case with the smooth disc (second) in a stratified atmosphere.\
+ The results show that the initial density distribution of the dense disc has an insignificant effect\
  on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\

### 2022-02-16 paper.tex
update

@@
  To explore how the disk affect the formation of the Galactic bubbles,\
- we compare the fiducial run (first column from left)\
- with the case with the smooth disc (second) in a stratified atmosphere.\
+ we compare the fiducial run (leftmost column of \Cref{fig__jetI5+ismSeed3-45deg})\
+ with the case adopting the smooth disc\
+ (second column; \Cref{fig__initial-density-profile} shows the density profile) in a stratified atmosphere.\
  The results show that the initial density distribution of the dense disc has an insignificant effect\
  on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
- in an uniform atmosphere (third) is spherical-shape,\
+ in an uniform atmosphere (third column) is spherical-shape,\
  suggesting the stratification facilitates the outermost bubbles elongation significantly.\
- Also, the two rightmost columns reveal that the development of the innermost bubbles (dashed box)\
+ Also, the two rightmost columns reveal that the development of the innermost bubbles\
  is always associated with the disc, and without the disc,\
- the outermost bubbles and the turbulent region will be oblique,\
+ the outermost bubbles and the turbulent plasma will be oblique,\
  indicating the dense disc is crucial for\
@@
              is always associated with the disc, and without the disc,\
-             the outermost bubbles and the turbulent region will be oblique,
+             the outermost bubbles and the turbulent plasma will be oblique,
              indicating the dense disc is crucial for\

### 2022-02-16 paper.tex
update

@@
     \caption{
-             The profile along the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.
+             Left: the profiles of pressure (top), temperature (middle),\
+             and number density (bottom)\
+             along the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.
+             Right: the close-up view of profiles around $z=3.7$ kpc.\
+             The sharp pressure jump and dense shell at $z=3.61$ kpc\
+             indicate that the innermost bubbles are an expanding reverse shock.\
      }

### 2022-02-16 paper.tex
update

@@
  We also note that the turbulence within the hot plasma is in pressure balance with the external medium,\
- suggesting that the outer edge of the \textit{Fermi} bubbles\
+ suggesting the outer edge of the \textit{Fermi} bubbles\
  is a tangling contact discontinuity rather than a shock.
@@
              suggesting the stratification facilitates the outermost bubbles elongation significantly.\
-             Also, the two rightmost columns reveal that the development of the innermost bubbles (dashed box)\
+             Also, the two rightmost columns reveal that the development of the innermost bubbles\
+             (dashed box in top left panel)\
              is always associated with the disc, and without the disc,\
@@
              The sharp pressure jump and dense shell at $z=3.61$ kpc\
-             indicate that the innermost bubbles are an expanding reverse shock.\
+             indicate that the innermost bubbles\
+             (dashed box in top left panel of \Cref{fig__jetI5+ismSeed3-45deg})\
+             are an expanding reverse shock.\
      }

### 2022-02-16 paper.tex
update

@@
   \includegraphics[width=\linewidth]{figures/fig__GammaRay_100e9_1e6_angle_000.png}
-  \caption{The observed (left) and simulated (right) photon flux\
+  \caption{The observed (left; \citep{Selig2015}) and simulated (right) photon flux\
            in the energy bin $76.8-153.6$ GeV.\

### 2022-02-16 paper.tex
update

--- 2022-02-16 paper.tex
@@
   \includegraphics[width=\linewidth]{figures/fig__GammaRay_100e9_1e6_angle_000.png}
-  \caption{The observed (left) and simulated (right) photon flux\
+  \caption{The observed (left; \citealt{Selig2015}) and simulated (right) photon flux\
            in the energy bin $76.8-153.6$ GeV.\

### 2022-02-16 paper.tex
update

@@
  Also, the two rightmost columns reveal that the development of the innermost bubbles\
- is always associated with the disc, and without the disc,\
+ is always associated with the disc, without the disc,\
  the outermost bubbles and the turbulent plasma will be oblique,\
@@
              (dashed box in top left panel)\
-             is always associated with the disc, and without the disc,\
+             is always associated with the disc, without the disc,\
              the outermost bubbles and the turbulent plasma will be oblique,

### 2022-02-16 paper.tex
update

@@
 the range of incident photon energy between\
-$\epsilon_{\text{min}}=1.13\times10^{-4}$ eV (cosmic microwave background radiation) and\
+$\epsilon_{\text{min}}=1.13\times10^{-4}$ eV (cosmic microwave background) and\
 $\epsilon_{\text{max}}=13.59$ eV (optical starlight)\

### 2022-02-16 paper.tex
update

@@
       The ambient stratification facilitates the eROSITA bubbles elongation significantly.
-      The development of the inverse shocks are always associated with the dense disc.
+      The development of the reverse shocks (the innermost bubbles) are always associated with the dense disc.
 \item The edge of the eROSITA bubbles is a forward shock,\
@@
       and significantly stretched by the stratified atmosphere afterwards.
-\item Followed by the forward shock is a contact discontinuity,\
+\item Followed by the forward shock is a tangling contact discontinuity,\
       which we interpret as the edge of the \textit{Fermi} bubbles.\
-      The nature of the \textit{Fermi} bubbles is essentially a turbulent and high-temperature ($\sim1$ keV)\
+      The nature of the \textit{Fermi} bubbles is essentially a turbulent and high-temperature ($\sim2$ keV)\
       plasma in pressure balance with the external medium. Associated with the Galactic magnetic field\

### 2022-02-16 paper.tex
update

@@
   \textsc{gamer-sr} also adaptively and locally reduce the min-mod coefficient\
-  \citep{tseng2021} within the failed patch group.\
-  Doing so provides an elegant way to avoid the use of pressure/density floor,\
+  \citep{tseng2021} within the failed patch group when performing full-step update\
+  and ghost-zone interpolations.\
+  In this way, we provide an elegant way to avoid the use of pressure/density floor,\
   being unnatural but widely used in almost publicly available codes.\

### 2022-02-16 paper.tex
update

--- 2022-02-16 paper.tex
@@
   \textsc{gamer-sr} also adaptively and locally reduce the min-mod coefficient\
-  \citep{tseng2021} within the failed patch group.\
-  Doing so provides an elegant way to avoid the use of pressure/density floor,\
+  \citep{tseng2021} within the failed patch group when performing full-step updates,\
+  new patches allocations, and ghost-zone interpolations.\
+  In this way, we provide an elegant way to avoid the use of pressure/density floor,\
   being unnatural but widely used in almost publicly available codes.\

### 2022-02-16 paper.tex
update

@@
  expanding 12.5 kpc above and below the Galactic plane,\
- and with a semiminor axis about 6.8 kpc on the plane.\
+ with a semiminor axis about 6.8 kpc on the plane.\
  We note that the overall extent of the outermost bubbles is comparable to\
@@
 
- The temperature profile (left column of \Cref{fig__profile}) along the positive z-axis in\
+ The temperature profile (left middle panel in \Cref{fig__profile}) along the positive z-axis in\
  \Cref{fig__jetI5+ismSeed3-45deg} indicates that\
@@
  The most interesting finding is that there is a innermost bubbles\
- (dashed box in top left panel of \Cref{fig__jetI5+ismSeed3-45deg})\
+ (dashed box in left top panel of \Cref{fig__jetI5+ismSeed3-45deg})\
  extending out from the Galactic center on either side of the thin disk.\
@@
  and underpressured with respect to the turbulent plasma.\
- Moreover, the close-up view of profiles around $z=3.7$ kpc (right column of \Cref{fig__profile})
+ Moreover, the close-up view of profiles around $z=3.7$ kpc (right column in \Cref{fig__profile})
  demonstrates that there is a sharp pressure jump and dense shell at $z=3.61$ kpc,\
@@
  To explore how the disk affect the formation of the Galactic bubbles,\
- we compare the fiducial run (leftmost column of \Cref{fig__jetI5+ismSeed3-45deg})\
+ we compare the fiducial run (first column from left in \Cref{fig__jetI5+ismSeed3-45deg})\
  with the case adopting the smooth disc\

### 2022-02-16 paper.tex
update

@@
   which likely extends to a radius of $\sim$250 kpc \citep{halo-radius-1,halo-radius-2},\
-  much bigger than our simulation box. Therefore, we first compute the X-ray emissivity\
+  much bigger than our simulation box.
+
+  We first compute the X-ray emissivity\
   from the simulated gas within a radius of 25 kpc away from the GC.
@@
   the comparison between simulated (top) and observed (bottom) all-sky map\
-  in the range 0.6 -- 1.0 keV at the present time.\
+  in the range 0.6 -- 1.0 keV at 12.39 Myr and the present time, respectively.\
   In the simulated map, the red arrow at the center of map represents the direction of the bipolar jet,\
-  constantly ejecting at an angle of $45^{\circ}$ to the disc normal in 1.2 Myr.
+  constantly ejecting at an angle of $45^{\circ}$ to the disc normal between 0 -- 1.2 Myr.
 
@@
   the temperature of innermost bubbles is around $1$ -- $10$ eV\
-  (see the temperature slice in \Cref{fig__jetI5+ismSeed3-45deg}).\
+  (see the temperature profile in \Cref{fig__profile}).\
   Consequently, the X-ray emission within the innermost bubbles
@@
 comparing the simulated gamma-ray and microwave spectra\
-with the observed spectra of the Fermi bubbles \citet{Ackermann2014}\
+with the observed spectra of the Fermi bubbles \citep{Ackermann2014}\
 and the microwave haze \citep{Dobler_2008}, respectively.\
@@
 The simulated gamma-ray and microwave spectra is based on the\
-IC scattering and synchrotron from CRe, in which\
+IC scattering and synchrotron from CRe, respectively, in which\
 the CRe spectrum follows a power-law distribution ranging from\
-$m_{\text{e}}c^2$ ($0.5$ MeV) to $1.1\times10^{6}m_{\text{e}}c^2$ ($562.1$ GeV),\
-where $m_{\text{e}}c^2$ is the rest mass energy of an electron.
+$0.5$ MeV to $562.1$ GeV.
 
@@
 where $\sigma_{T}$ is the Thomson cross section, $c$ speed of light,\
+$m_{\text{e}}$ electron mass,\
 $n(\epsilon)$ the energy distribution of the photon number density in ISRF given by \citet{Porter2017},\
@@
 and gamma-ray (right) spectra averaged over the different patches (shown in the legends) of the sky.\
-The row from top to bottom shows the microwave (left) and gamma-ray (right) spectra\
-with CRe spectral index $2.2, 2.4$ and $2.6$, respectively.\
+The row from top to bottom shows the spectra with different CRe spectral index $2.2, 2.4$ and $2.6$.\
 Several points are worth specific comment.\

### 2022-02-16 paper.tex
update

@@
 
-  Although the high-energy CRe ($10$ -- $100$ GeV) plays a crucial role in reproducing the $\gamma$-ray map\
-  within the range of $1$ -- $100$ GeV, we assume the pressure of CRe is much less than that of gas\
+  Although the high-energy CRe ($10$--$100$ GeV) plays a crucial role in reproducing the $\gamma$-ray map\
+  within the range of $1$--$100$ GeV, we assume the pressure of CRe is much less than that of gas\
   throughout the simulation so that we , and the \textit{Fermi} bubbles can be outlined against the eROSITA bubbles.
@@
  extending out from the Galactic center on either side of the thin disk.\
- The innermost bubbles are cold (1-10 eV), dense ($10^{-4}$ -- $10^{-2}$ cm$^{-3}$),\
+ The innermost bubbles are cold (1-10 eV), dense ($10^{-4}$--$10^{-2}$ cm$^{-3}$),\
  and underpressured with respect to the turbulent plasma.\
@@
   the comparison between simulated (top) and observed (bottom) all-sky map\
-  in the range 0.6 -- 1.0 keV at 12.39 Myr and the present time, respectively.\
+  in the range 0.6--1.0 keV at 12.39 Myr and the present time, respectively.\
   In the simulated map, the red arrow at the center of map represents the direction of the bipolar jet,\
-  constantly ejecting at an angle of $45^{\circ}$ to the disc normal between 0 -- 1.2 Myr.
+  constantly ejecting at an angle of $45^{\circ}$ to the disc normal between 0--1.2 Myr.
 
@@
   even though with high column density, is invisible in the simulated X-ray map as\
-  the temperature of innermost bubbles is around $1$ -- $10$ eV\
+  the temperature of innermost bubbles is around $1$--$10$ eV\
   (see the temperature profile in \Cref{fig__profile}).\
@@
     \subfigure[Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
-               (photons s$^{-1}$ deg$^{-2}$) in the 0.6 -- 1.0 keV range.\
+               (photons s$^{-1}$ deg$^{-2}$) in the 0.6--1.0 keV range.\
                Throughout this paper we show sky maps\
@@
 
-Third, the gamma-ray spectra for all latitudes indicate a spectral cutoff around energies 400 -- 500 GeV,\
+Third, the gamma-ray spectra for all latitudes indicate a spectral cutoff around energies 400--500 GeV,\
 consistent with the observed cutoff energy.\

### 2022-02-16 paper.tex
update

@@
 Third, the gamma-ray spectra for all latitudes indicate a spectral cutoff around energies 400--500 GeV,\
-consistent with the observed cutoff energy.\
-This is expected since
+remarkably consistent with the observed cutoff energy.\
+This is expected since\
 the upscattered high-energy photons ($\epsilon_{1}\sim450$ GeV) mainly arise from\

### 2022-02-16 paper.tex
update

--- 2022-02-16 paper.tex
@@
 Third, the gamma-ray spectra for all latitudes indicate a spectral cutoff around energies 400--500 GeV,\
-consistent with the observed cutoff energy.\
-This is expected since
+remarkably consistent with the observed cutoff energy.\
+This is expected since\
 the upscattered high-energy photons ($\epsilon_{1}\sim450$ GeV) mainly arise from\
 the scatterings between the relativistic CRe ($\gtrapprox 408$ GeV)\
-and optical starlight ($\epsilon \sim 10$ eV),\
-and therefore \Cref{gamma-min} can be reduced to $\epsilon_{1}\sim\gamma m_{\text{e}}c^2$\
+and optical starlight ($\epsilon \sim 10$ eV).\
+Thus, \Cref{gamma-min} can be reduced to $\epsilon_{1}\sim\gamma m_{\text{e}}c^2$\
 in the Klein--Nishina limit\
@@
 Fourth, the good agreement between the simulated and observed gamma-ray/microwave spectra\
-imply that the emission of the Fermi bubbles and\
+imply that, in the presence of ISRF and magnetic fields, the emission of the Fermi bubbles and\
 the microwave haze can be produced by the same high-energy electrons\
-via inverse Compton scatterings and synchrotron radiations\
-in the presence of ISRF and magnetic fields, respectively,\
+via inverse Compton scatterings and synchrotron radiations, respectively,\
 as previously suggested \citep{Su2010,Dobler2012}.

### 2022-02-16 paper.tex
update

@@
 
- Finally, we display the morphology of the \textit{Fermi} bubbles\
- that emit gamma-rays from the inverse Compton scattering of ISRF by CRe\
- with the best-fit CRe sptral index 2.4
+ Finally, \Cref{fig__gammaRay-map} shows the simulated gamma-ray photon flux compared with the observed one\
+ in the energy bin $76.8-153.6$ GeV. One can see that the symmetric of the \textit{Fermi} bubbles\
+ can also be realized by oblique jets as the eROSITA bubbles.\
 
- We close on a speculative note that predicts an existence of a third bubbles for
- future observations.
+ %We close on a speculative note that predicts an existence of a third bubbles for
+ %future observations.
 
@@
 % so it's more likely associated with turbulence.
-
-%  Having successfully reproduced the morphology\
-%  and spectrum of the \textit{Fermi} bubbles,\
-%  we now ask whether CRe could also explain\
-%  the Galactic microwave haze.
 
@@
   \end{figure}
-
-\Cref{fig__gammaRay-map} shows the simulated gamma-ray photon flux compared with the observed one\
-in the energy bin $76.8-153.6$ GeV. One can see that the symmetric of the \textit{Fermi} bubbles\
-can also be realized by oblique jets as the eROSITA bubbles.\
 

### 2022-02-16 paper.tex
update

@@
 
- Finally, \Cref{fig__gammaRay-map} shows the simulated gamma-ray photon flux compared with the observed one\
+ Finally, \Cref{fig__gammaRay-map} shows the simulated gamma-ray photon flux with a CRe power-law index 2.4\
+ compared with the observed one\
  in the energy bin $76.8-153.6$ GeV. One can see that the symmetric of the \textit{Fermi} bubbles\

### 2022-02-16 paper.tex
update

--- 2022-02-16 paper.tex
@@
 
- Finally, \Cref{fig__gammaRay-map} shows the simulated gamma-ray photon flux compared with the observed one\
- in the energy bin $76.8-153.6$ GeV. One can see that the symmetric of the \textit{Fermi} bubbles\
- can also be realized by oblique jets as the eROSITA bubbles.\
+ \Cref{fig__gammaRay-map} shows the simulated gamma-ray photon flux with a CRe power-law index 2.4\
+ compared with the observed one\
+ in the energy bin $76.8-153.6$ GeV.\
+ As the eROSITA bubbles,\
+ one can see that the symmetric of the \textit{Fermi} bubbles\
+ can also be realized by oblique jets.\
+
+ Finally, the comparison between \Cref{fig__jetI5+ismSeed3-45deg-CR} and\
+ \Cref{fig__jetI5+ismSeed3-45deg} shows that the CR pressure\
+ is around 5$\times10^{-15}$--8$\times10^{-15}$ erg/cm$^{3}$, less than the gas pressure by a factor 10--20.\
+ We thefore stress that in \Cref{governing-eq},\
+ assuming $p_{CR}\ll p_{\text{gas}}$ is resonable.
 

### 2022-02-16 paper.tex
update

@@
  is around 5$\times10^{-15}$--8$\times10^{-15}$ erg/cm$^{3}$, less than the gas pressure by a factor 10--20.\
- We thefore stress that in \Cref{governing-eq},\
- assuming $p_{CR}\ll p_{\text{gas}}$ is resonable.
+ We thefore stress that\
+ assuming $p_{CR}\ll p_{\text{gas}}$ in \Cref{governing-eq} is resonable.
 

### 2022-02-16 paper.tex
update

@@
  We thefore stress that\
- assuming $p_{CR}\ll p_{\text{gas}}$ in \Cref{governing-eq} is resonable.
+ ignoring the contribution of CR pressure gradient to the momentum of the gas\
+ in \Cref{governing-eq} is resonable.
 

### 2022-02-16 paper.tex
update

--- 2022-02-16 paper.tex
@@
 
- Finally, the comparison between \Cref{fig__jetI5+ismSeed3-45deg-CR} and\
- \Cref{fig__jetI5+ismSeed3-45deg} shows that the CR pressure\
+ Finally, the comparison between\
+ \Cref{fig__jetI5+ismSeed3-45deg}\
+ and\
+ \Cref{fig__jetI5+ismSeed3-45deg-CR}\
+ shows that the CR pressure\
  is around 5$\times10^{-15}$--8$\times10^{-15}$ erg/cm$^{3}$, less than the gas pressure by a factor 10--20.\
  We thefore stress that\
- assuming $p_{CR}\ll p_{\text{gas}}$ in \Cref{governing-eq} is resonable.
+ ignoring the contribution of CR pressure gradient to the momentum of the gas\
+ in \Cref{governing-eq} is resonable.
 

### 2022-02-16 paper.tex
update

@@
  shows that the CR pressure\
- is around 5$\times10^{-15}$--8$\times10^{-15}$ erg/cm$^{3}$, less than the gas pressure by a factor 10--20.\
+ is around 5$\times10^{-15}$--8$\times10^{-15}$ erg/cm$^{3}$, less than the gas pressure\
+ by a factor of 10--20.\
  We thefore stress that\

### 2022-02-16 paper.tex
update

@@
     \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg-CR.png}
-    \caption{The slice of CR... $p_{CR}$ is much less than $p_{\text{gas}}$...}
+    \caption{
+     The CR pressure slice passing through the jet source at 12.39 Myr.\
+     Comparison between\
+     gas pressure (\Cref{fig__jetI5+ismSeed3-45deg}) and cosmic ray pressure\
+     shows that
+     the CR pressure\
+     is around 5$\times10^{-15}$--8$\times10^{-15}$ erg/cm$^{3}$,\
+     less than the gas pressure\
+     by a factor of 10--20.\
+     We thefore stress that\
+     ignoring the contribution of CR pressure gradient to the momentum of the gas\
+     in \Cref{governing-eq} is resonable.
+     }
     \label{fig__jetI5+ismSeed3-45deg-CR}

### 2022-02-16 paper.tex
update

@@
  shows that the CR pressure\
- is around 5$\times10^{-15}$--8$\times10^{-15}$ erg/cm$^{3}$, less than the gas pressure\
- by a factor of 10--20.\
+ is around 5$\times10^{-15}$--8$\times10^{-15}$ erg/cm$^{3}$,\
+ bringing the the pressure ratio of CR to gas is 0.1--0.2,
+ similar to that (0.18) at the begining of the simulation.
  We thefore stress that\

### 2022-02-16 paper.tex
update

@@
  bringing the the pressure ratio of CR to gas is 0.1--0.2,
- similar to that (0.18) at the begining of the simulation.
+ similar to 0.18 at the begining of the simulation.
  We thefore stress that\

### 2022-02-16 paper.tex
update

@@
      is around 5$\times10^{-15}$--8$\times10^{-15}$ erg/cm$^{3}$,\
-     less than the gas pressure\
-     by a factor of 10--20.\
+     bringing the the pressure ratio of CR to gas is 0.1--0.2,
+     similar to 0.18 at the begining of the simulation.
      We thefore stress that\

### 2022-02-16 paper.tex
update

@@
 The large-scale X-ray structure\
-shows that the intrinsic size of the bubbles is 14 kiloparsecs across \citep{Predehl2021},
+shows that the intrinsic size of the bubbles is 14 kpc across \citep{Predehl2021},
 and displays morphological symmetry about the Galactic plane as the \textit{Fermi} bubbles.
@@
 there is a lack of preferred orientation of jets with respect to\
-the rotation axis of a galatic plane (disc normal, hereafter).\
+the rotation axis of a galactic plane (disc normal, hereafter).\
 In contrast, a number of galaxies in which the jets are oblique to the disc normal\
@@
              The vertical bands from left to right depict the allowable number densities \citep{peak-ism-density} for\
-             hot ionized, warm neutral (WNM), warm ionized (WIM), cold nuetral mediums (CNM), and molecular clouds.}
+             hot ionized, warm neutral (WNM), warm ionized (WIM), cold neutral mediums (CNM), and molecular clouds.}
       \label{fig__numberDensityHistogram}
@@
  \Cref{fig__jetI5+ismSeed3-45deg} shows\
- the slices of pressure (top), temperature (middile), number density (bottom)\
+ the slices of pressure (top), temperature (middle), number density (bottom)\
  at the end of simulation $t=12.39$ Myr.\
@@
  is around 5$\times10^{-15}$--8$\times10^{-15}$ erg/cm$^{3}$,\
- bringing the the pressure ratio of CR to gas is 0.1--0.2,
- similar to 0.18 at the begining of the simulation.
- We thefore stress that\
+ bringing the pressure ratio of CR to gas is 0.1--0.2,
+ similar to 0.18 at the beginning of the simulation.
+ We therefore stress that\
  ignoring the contribution of CR pressure gradient to the momentum of the gas\
- in \Cref{governing-eq} is resonable.
+ in \Cref{governing-eq} is reasonable.
 
@@
      is around 5$\times10^{-15}$--8$\times10^{-15}$ erg/cm$^{3}$,\
-     bringing the the pressure ratio of CR to gas is 0.1--0.2,
-     similar to 0.18 at the begining of the simulation.
-     We thefore stress that\
+     bringing the pressure ratio of CR to gas is 0.1--0.2,
+     similar to 0.18 at the beginning of the simulation.
+     We therefore stress that\
      ignoring the contribution of CR pressure gradient to the momentum of the gas\
-     in \Cref{governing-eq} is resonable.
+     in \Cref{governing-eq} is reasonable.
      }

### 2022-02-16 paper.tex
update

@@
       with CRe spectral index $2.2, 2.4$ and $2.6$, respectively.\
-      The CRe cutoff energy is $1.1\times10^{6}m_{\text{e}}c^{2}$ in all cases.
+      The CRe cutoff energy is 562.1 GeV in all cases.
       %At larger $p$, the microwave spectrum was found to be steeper as $I_{\nu}\propto \nu^{-(p-1)/2}$.

### 2022-02-16 paper.tex
update

@@
  suggesting the outer edge of the \textit{Fermi} bubbles\
- is a tangling contact discontinuity rather than a shock.
+ is a tangling contact discontinuity rather than a smooth shock.
 

### 2022-02-16 paper.tex
update

--- 2022-02-16 paper.tex
@@
  suggesting the outer edge of the \textit{Fermi} bubbles\
- is a tangling contact discontinuity rather than a shock.
+ is a tangling contact discontinuity rather than a smooth shock \citep{Zhang2020}.
 

### 2022-02-17 paper.tex
update

@@
 
+\section{Acknowledgements}
+The authors thank Mateusz Ruszkowski and Ellen G. Zweibel for insightful comments.\
+We thank Peter Predehl for providing the colorbar limits of \Cref{fig__xray_0.8keV_angle_000}.\
+The simulations are partly performed and analyzed using computing facilities\
+operated by the national center for High Performance Computing.
+HYKY acknowledge support from\
+Yushan Scholar Program of the Ministry of Education of Taiwan\
+and\
+Ministry of Science and Technology of Taiwan (MOST 109-2112-M-007-037-MY3).
+HS acknowledges\
+funding support from the Jade Mountain Young Scholar Award No. NTU-109V0201,\
+sponsored by the Ministry of Education, Taiwan.\
+This research is partially supported by the Ministry of Science and\
+Technology of Taiwan (MOST) under grants MOST 107-2119-M-002-036-MY3\
+and MOST 108-2112-M-002-023-MY3, and the NTU\
+Core Consortium project under grants NTU-CC-108L893401 and\
+NTU-CC-108L893402.
+
 \section*{Data Availability}

### 2022-02-17 paper.tex
update

@@
 We thank Peter Predehl for providing the colorbar limits of \Cref{fig__xray_0.8keV_angle_000}.\
-The simulations are partly performed and analyzed using computing facilities\
+A part of the simulations are performed and analyzed using computing facilities\
 operated by the national center for High Performance Computing.

### 2022-02-17 paper.tex
update

@@
 In Section \ref{Methodology}, we describe the numerical techniques and initial conditions employed.\
-We directly compare the morphology of the Galactic bubbles with observation,\
-and also show the simulated gamma-ray and microwave spectra compared with observations\
-in Section \ref{Results}.
-Finally, we summarize our findings in Section \ref{Conclusions}.
+In Section \ref{Results}, we first present characteristics of our simulated Galactic bubbles,\
+and then discuss how the disk affect the formation of the bubbles.\
+We directly compare the morphology and profile of simulated eROSITA bubbles with\
+observred X-ray map in Section \ref{X-ray},\
+and also present the simulated and observed multiwavelength spectra of\
+the \textit{Fermi} bubbles in Section \ref{sec:gamma-ray-microwave}.\
+Finally, the summary and implications of our findings are given in Section \ref{Conclusions}.
+
+% \ref{X-ray} \ref{sec:gamma-ray-microwave}
 
@@
 \subsection{Gamma-ray and microwave spectra: constraint on the CRe spectral index}
-
+\label{sec:gamma-ray-microwave}
 In this section, we give the constraint on the CRe spectral index by\
@@
       with respect to the disc normal.\
-      The broad agreement between simulated and observed mutiwavelength features\
+      The broad agreement between simulated and observed multiwavelength features\
       provides supporting evidence for the inclined jet scenario, and also\

### 2022-02-17 paper.tex
update

@@
 
-% \ref{X-ray} \ref{sec:gamma-ray-microwave}
-
 \section{Methodology}
@@
 
+  As stressed by \citet{Yang2012}, CR diffusion has an insignificant effect\
+  on the overall morphology of the \textit{Fermi} bubbles,\
+  but only sharpens the edges of the simulated bubbles by the interplay between magnetic fields\
+  and anisotropic CR diffusion with suppressed perpendicular diffusion across the bubble surface. Moreover,\
+  the magnetic fields within the \textit{Fermi} bubbles should be weak due to\
+  adiabatic expansion, and thus the fields has\
+  a little effect on the overall dynamics.
+
+  For these two reasons,\
+  we have ignored the CR diffusion and the magnetic field throughout\
+  the simulation.\
+  Also, we do not simulate the spectral evolution of the CR\
+  and assume the CR pressure is much less than the gas pressure over the bubbles formation so that\
+  the contribution of CR pressure gradient to the momentum of the gas can be ignored.
+  In addition, we neglect the cooling and heating processes of CRs,\
+  such as energy losses due to synchrotron and inverse Compton emission,\
+  and CR reacceleration in shocks/turbulences.
+
+  In this approach, we treat CRs as a single species without distinction between electrons and protons,\
+  and directly evolve the CR energy density $e_{\text{cr}}$\
+  as a function of $\mathbf{r}$ and $t$.\
   The CRs are advected with the thermal gas, and in return the velocities of gas\
   can react to the gradients of the CR pressure via the source term\
-  containing spatial divergence of fluid velocities.\
-
-  Although the high-energy CRe ($10$--$100$ GeV) plays a crucial role in reproducing the $\gamma$-ray map\
-  within the range of $1$--$100$ GeV, we assume the pressure of CRe is much less than that of gas\
-  throughout the simulation so that we , and the \textit{Fermi} bubbles can be outlined against the eROSITA bubbles.
-
-  As stressed by \citet{Yang2012}, CR diffusion has an insignificant effect\
-  on the overall morphology of the \textit{Fermi} bubbles,\
-  but only sharpens the edges of the simulated bubbles by the interplay between anisotropic CR diffusion\
-  and magnetic fields with suppressed perpendicular diffusion across the bubble surface. Moreover,\
-  the bubbles should be weak due to adiabatic expansion, and thus the magnetic fields has\
-  a little effect on the overall dynamics. For these two reasons,\
-  we have ignored the CR diffusion and the magnetic field throughout\
-  the simulation.
-
-  We do not simulate the spectral evolution of the CR, and we neglected the cooling and heating processes of CRs,\
-  such as energy losses due to synchrotron and inverse Compton emission, and reacceleration in shocks/turbulences.\
-
-  In this approach, we treat CRs as a single species without distinction between electrons and protons,\
-  that cannot react to the gas via the application of CRe pressure,\
-  and solve directly for the evolution of CR energy density $e_{\text{cr}}$\
-  as a function of $\mathbf{r}$ and $t$.\
+  containing spatial divergence of fluid velocities.
 
@@
 The authors thank Mateusz Ruszkowski and Ellen G. Zweibel for insightful comments.\
-We thank Peter Predehl for providing the colorbar limits of \Cref{fig__xray_0.8keV_angle_000}.\
+We thank Peter Predehl for providing the range of observed X-ray intensity in \Cref{fig__xray_0.8keV_angle_000}.\
 A part of the simulations are performed and analyzed using computing facilities\

### 2022-02-17 paper.tex
update

@@
   new patches allocations, and ghost-zone interpolations.\
-  In this way, we provide an elegant way to avoid the use of pressure/density floor,\
+  In this way, we provide an elegant approach to avoid the use of pressure/density floor,\
   being unnatural but widely used in almost publicly available codes.\

### 2022-02-17 paper.tex
update

@@
   Also, we do not simulate the spectral evolution of the CR\
-  and assume the CR pressure is much less than the gas pressure over the bubbles formation so that\
-  the contribution of CR pressure gradient to the momentum of the gas can be ignored.
+  and assume the pressure ratio of CR to gas is much less than 1 over the bubbles formation so that\
+  the contribution of CR pressure gradient to the momentum of the gas can be ignored.\
+  (We will see that the pressure ratio is around 0.1--0.2 throughtout the bubbles formation)\
   In addition, we neglect the cooling and heating processes of CRs,\

### 2022-02-17 paper.tex
update

--- 2022-02-17 paper.tex
@@
   Also, we do not simulate the spectral evolution of the CR\
-  and assume the CR pressure is much less than the gas pressure over the bubbles formation so that\
-  the contribution of CR pressure gradient to the momentum of the gas can be ignored.
+  and assume the pressure ratio of CR to gas is much less than 1 over the bubbles formation so that\
+  the contribution of CR pressure gradient to the momentum of the gas can be ignored.\
+  (we will see that the pressure ratio is around 0.1--0.2 throughtout the bubbles formation)\
   In addition, we neglect the cooling and heating processes of CRs,\

### 2022-02-17 paper.tex
update

--- 2022-02-17 paper.tex
@@
   Also, we do not simulate the spectral evolution of the CR\
-  and assume the CR pressure is much less than the gas pressure over the bubbles formation so that\
-  the contribution of CR pressure gradient to the momentum of the gas can be ignored.
+  and assume the pressure ratio of CR to gas is much less than 1 so that\
+  the contribution of CR pressure gradient to the momentum of the gas can be ignored.\
+  (we will see that the pressure ratio is around 0.1--0.2 throughtout the bubbles formation)\
   In addition, we neglect the cooling and heating processes of CRs,\

### 2022-02-17 paper.tex
update

@@
   but only sharpens the edges of the simulated bubbles by the interplay between magnetic fields\
-  and anisotropic CR diffusion with suppressed perpendicular diffusion across the bubble surface. Moreover,\
-  the magnetic fields within the \textit{Fermi} bubbles should be weak due to\
+  and anisotropic CR diffusion with suppressed perpendicular diffusion across the bubble surface.
+
+  Moreover, the magnetic fields within the \textit{Fermi} bubbles should be weak due to\
   adiabatic expansion, and thus the fields has\
@@
 We thank Peter Predehl for providing the range of observed X-ray intensity in \Cref{fig__xray_0.8keV_angle_000}.\
-A part of the simulations are performed and analyzed using computing facilities\
+A part of the simulations are performed and analyzed using computing resources\
 operated by the national center for High Performance Computing.

### 2022-02-17 paper.tex
update

@@
 A part of the simulations are performed and analyzed using computing resources\
-operated by the national center for High Performance Computing.
+operated by the National Center for High Performance Computing (NCHC).
 HYKY acknowledge support from\

### 2022-02-17 paper.tex
update

--- 2022-02-17 paper.tex
@@
 A part of the simulations are performed and analyzed using computing resources\
-operated by the national center for High Performance Computing.
+operated by the National Center for High-Performance Computing (NCHC).
 HYKY acknowledge support from\

### 2022-02-18 paper.tex
update

@@
      &\partial_{t} D+\partial_{j} \left(DU^{j}/\gamma\right)=0,\label{D evolution}\\
-     &\partial_{t} M^{i}+\partial_{j} \left(M^{i}U^{j}/\gamma+p_{\text{gas}}\delta^{ij}\right)=\
+     &\partial_{t} M^{i}+\partial_{j} \left(M^{i}U^{j}/\gamma+p_{\text{total}}\delta^{ij}\right)=\
      -\rho\partial_{i}\Phi,\label{M evolution}\\
@@
   $p_{\text{cr}}$ and $e_{\text{cr}}$ are the CR pressure and CR energy density measured in the local rest frame.\
+  $p_{\text{total}}$ is the sum of $p_{\text{gas}}$ and $p_{\text{cr}}$.\
+  Note that we simply replace $p_{\text{total}}$ by $p_{\text{gas}}$ in this paper\
+  as we have assumed $p_{\text{cr}}\ll p_{\text{gas}}$ in this paper.\
   $\Phi$ is the gravitation potential.\

### 2022-02-18 paper.tex
update

@@
 operated by the National Center for High-Performance Computing (NCHC).
-HYKY acknowledge support from\
+HYKY acknowledges support from\
 Yushan Scholar Program of the Ministry of Education of Taiwan\

### 2022-02-21 paper.tex
update

@@
 \begin{abstract}
-% out of the Galactic center on either side of the Galactic disk
+A decade ago, the \textit{Fermi Gamma-Ray Space Telescope} reveals two large bubbles in the Galaxy,\
+which extend nearly symmetrically $\sim50^{\circ}$ on either side of the Galactic disk.\
+
 \end{abstract}
@@
   (we will see that the pressure ratio is around 0.1--0.2 throughtout the bubbles formation)\
-  In addition, we neglect the cooling and heating processes of CRs,\
+  Over and above, we neglect the cooling and heating processes of CRs,\
   such as energy losses due to synchrotron and inverse Compton emission,\
@@
 
-In this work, we introduce a thin, dense disk composed of interstellar medium\
+In this work, we introduce a thin, dense disk composed of clumpy interstellar medium\
 to divert the inclined jet at an angle $45^{\circ}$\
@@
 \item The edge of the eROSITA bubbles is a forward shock,\
-      originally driven by an oblique bipolar jets emanating from the GC 12.39 million years ago,\
+      originally driven by oblique bipolar jets emanating from the GC 12.39 million years ago,\
       and significantly stretched by the stratified atmosphere afterwards.
@@
 \item According to the microwave and leptonic gamma-ray spectra, the best-fitting\
-      CRe power-law index is found to be -2.4.
+      CRe power-law index is found to be 2.4.
 \item The same leptotonic CRe can simultaneously\
@@
 \end{itemize}
-
-%Over the past few years, there have been numerous efforts,\
-%both observational and theoretical, to uncover the nature of the Galactic bubbles.
-%
-%
-%Spektr-RG \citep{Sunyaev2021} and eROSITA \citep{Predehl2021}
-
-We have found qualitative similarities between the results our simulations\
-and the observed spectrum and morphological structure of the Galactic bubbles.
-
-Since the jets encounter a larger column depth of clouds along their path,\
-they interact more strongly with the dense ISM.\
-The jets do not immediately clear a channel along the inclined axis of launch.\
-Rather, the dense clouds deflect the jets, which then decelerate\
-and launch a sub-relativistic outflow along the minor axis following the path of least resistance.
-
-Assuming that a relativistic electron population of spectral
-index x = 2.2 gives rise to the microwave haze via synchrotron
-emission.
-
-%We therefore suggest that the Fermi bubbles and the eROSITA structure are physically related,\
-%as suggested by \citet{Predehl2020}.
-
-%Our discovery confirms the previously suggested common origin of the two objects \citep{Sofue2000,Kataoka2018}
 

### 2022-02-21 paper.tex
update

@@
 \begin{abstract}
-A decade ago, the \textit{Fermi Gamma-Ray Space Telescope} reveals two large bubbles in the Galaxy,\
+A decade ago, the \textit{Fermi Gamma-Ray Space Telescope} reveals two large gamma-ray bubbles in the Galaxy,\
 which extend nearly symmetrically $\sim50^{\circ}$ on either side of the Galactic disk.\
+The recent discovery of eROSITA bubbles also shows a symmetrically enhanced X-ray\
+emission from the shells around the eROSITA bubbles.\
+To this end, previous simulation-based works assumed that the jets are vertical to the Galactic disk;\
+however, there is a lack of preferred orientation of jets with respect to the Galactic disk.\
+Using three-dimensional (3D) special relativistic hydrodynamic simulations that\
+include cosmic rays (CRs) and thermal gas, we show that a thin interstellar medium disk is an essential\
+component for the formation of the symmetrical Galactic bubbles.\
+We also produce simulated gamma-ray and\
+microwave spectra from the inverse Compton scattering and synchrotron,\
+and compare them with the observed counterparts in order to verify\
+the oblique jets model.
+We find that (1)
 
@@
 \label{Conclusions}
-%The symmetry of the Galactic bubbles is worth exploring since observations\
-%show that there is no preference for the orientation of AGN jets relative to\
-%the rotation axis of a galactic plane.
-
 In this work, we introduce a thin, dense disk composed of clumpy interstellar medium\

### 2022-02-21 paper.tex
update

--- 2022-02-21 paper.tex
@@
 \begin{abstract}
-A decade ago, the \textit{Fermi Gamma-Ray Space Telescope} reveals two large bubbles in the Galaxy,\
+A decade ago, the \textit{Fermi Gamma-Ray Space Telescope} reveals two large gamma-ray bubbles in the Galaxy,\
 which extend nearly symmetrically $\sim50^{\circ}$ on either side of the Galactic disk.\
+The recent discovery of eROSITA bubbles also shows a symmetrically enhanced X-ray\
+emission from the shells around the eROSITA bubbles.\
+To this end, previous simulation-based works assumed that the jets are vertical to the Galactic disk;\
+however, there is a lack of preferred orientation of jets with respect to the Galactic disk.\
+Using three-dimensional (3D) special relativistic hydrodynamic simulations that\
+include cosmic rays (CRs) and thermal gas, we show that a thin interstellar medium disk is an essential\
+component for the symmetry Galactic bubbles.\
+We also produce simulated gamma-ray and\
+microwave spectra from the inverse Compton scattering and synchrotron,\
+and compare them with the observed counterparts in order to verify\
+the oblique jets model. We find that\
+(1) The Galactic bubbles are nearly symmetric about the Galactic plane albeit\
+the jet is at an angle $45^{\circ}$ with respect to the disc normal.\
+(2) The randomness of clumpy disk has a insignificant impact on the overall dynamic of the Galactic bubbles.\
+The ambient stratification facilitates the eROSITA bubbles elongation significantly.
+The development of the reverse shocks (the innermost bubbles) are always associated with the dense disc.
 
@@
 \item The randomness of clumpy disk has a insignificant impact on the overall dynamic of the Galactic bubbles.\
-      The ambient stratification facilitates the eROSITA bubbles elongation significantly.
-      The development of the reverse shocks (the innermost bubbles) are always associated with the dense disc.
+      The development of the reverse shocks (the innermost bubbles) are always associated with the dense disc,\
+      without the disc, the outermost bubbles and the turbulent plasma will be oblique,\
+      indicating the dense disc is crucial for\
+      the symmetry of the Galactic bubbles and for the innermost bubbles formation.
 \item The edge of the eROSITA bubbles is a forward shock,\
       originally driven by oblique bipolar jets emanating from the GC 12.39 million years ago,\
-      and significantly stretched by the stratified atmosphere afterwards.
+      and significantly stretched by the stratified atmosphere afterwards.\
+      The simulated eROSITA bubbles are not as limb-brightened as the observed one.\
+      A possibility to enhance the X-ray emission is to include shock-accelerated CRs near the shock,\
+      in which CRs could increase the compressibility of the fluid.
 \item Followed by the forward shock is a tangling contact discontinuity,\

### 2022-02-21 paper.tex
update

@@
       A possibility to enhance the X-ray emission is to include shock-accelerated CRs near the shock,\
-      in which CRs could increase the compressibility of the fluid.
+      in which CRs could increase the compressibility of the fluid.\
+      We will leave shock-accelerated CRs as a future study.
 \item Followed by the forward shock is a tangling contact discontinuity,\
@@
       will lead to the stochastic acceleration of CRe, and probably balanced with the IC and synchrotron cooling.\
-      We will investigate the competition between CRe acceleration and radiative cooling in a future work.
+      We will investigate the competition between stochastic acceleration and radiative cooling in a future work.
 \item According to the microwave and leptonic gamma-ray spectra, the best-fitting\

### 2022-02-21 paper.tex
update

@@
       in which CRs could increase the compressibility of the fluid.\
-      We will leave shock-accelerated CRs as a future study.
 \item Followed by the forward shock is a tangling contact discontinuity,\

### 2022-02-21 paper.tex
update

@@
 the oblique jets model. We find that\
-(1) The Galactic bubbles are nearly symmetric about the Galactic plane albeit\
+(1) The simulated Galactic bubbles are nearly symmetric about the Galactic plane albeit\
 the jet is at an angle $45^{\circ}$ with respect to the disc normal.\
-(2) The randomness of clumpy disk has a insignificant impact on the overall dynamic of the Galactic bubbles.\
-The ambient stratification facilitates the eROSITA bubbles elongation significantly.
-The development of the reverse shocks (the innermost bubbles) are always associated with the dense disc.
-
+(2) The edge of the eROSITA bubbles is a forward shock,\
+originally driven by oblique bipolar jets emanating from the GC 12.39 million years ago,\
+and significantly stretched by the stratified atmosphere afterwards.\
+(3) Followed by the forward shock is a tangling contact discontinuity,\
+which we interpret as the edge of the \textit{Fermi} bubbles.\
+The nature of the \textit{Fermi} bubbles is essentially a turbulent and high-temperature ($\sim2$ keV)\
+plasma in pressure balance with the external medium.
+(4) According to the microwave and leptonic gamma-ray spectra, the best-fitting\
+CRe power-law index is found to be 2.4.\
+The broad agreement between simulated and observed multiwavelength features\
+releases the caveat given by earlier simulation-based studies:\
+the jets shall be vertical to the disc normal.
 \end{abstract}

### 2022-02-21 paper.tex
update

@@
   Note that we simply replace $p_{\text{total}}$ by $p_{\text{gas}}$ in this paper\
-  as we have assumed $p_{\text{cr}}\ll p_{\text{gas}}$ in this paper.\
+  as we have assumed $p_{\text{cr}}\ll p_{\text{gas}}$.\
   $\Phi$ is the gravitation potential.\

### 2022-02-21 paper.tex
update

@@
 \begin{abstract}
-A decade ago, the \textit{Fermi Gamma-Ray Space Telescope} reveals two large gamma-ray bubbles in the Galaxy,\
-which extend nearly symmetrically $\sim50^{\circ}$ on either side of the Galactic disk.\
+A decade ago, the \textit{Fermi Gamma-Ray Space Telescope} reveals two large bubbles in the Galaxy,\
+which extend nearly symmetrically $\sim50^{\circ}$ on either side of the Galactic center (GC).\
 The recent discovery of eROSITA bubbles also shows a symmetrically enhanced X-ray\
@@
 include cosmic rays (CRs) and thermal gas, we show that a thin interstellar medium disk is an essential\
-component for the symmetry Galactic bubbles.\
+component for the symmetry \textit{Fermi} and eROSITA bubbles (collectively, Galactic bubbles).\
 We also produce simulated gamma-ray and\
@@
 the oblique jets model. We find that\
-(1) The simulated Galactic bubbles are nearly symmetric about the Galactic plane albeit\
-the jet is at an angle $45^{\circ}$ with respect to the disc normal.\
+(1) The simulated Galactic bubbles are nearly symmetric about the GC albeit\
+the bipolar jets are at an angle $45^{\circ}$ with respect to the disc normal.\
 (2) The edge of the eROSITA bubbles is a forward shock,\
@@
 to model the symmetric \textit{Fermi} and eROSITA bubbles (collectively we call the Galactic bubbles)\
-assumed that the jet is vertical to the Galactic plane. However,\
+assumed that the jets are vertical to the Galactic plane. However,\
 observation \citep{Gallimore2006} has proposed that\
@@
 To this end, this work introduces a dense thin disc of interstellar medium\
-around a jet source to deflects and decelerates the inclined jets,\
+around a jet source to deflects and decelerates the oblique jets,\
 in an attempt to resolve the symmetry problem of the Galactic bubbles.\
@@
 involving CR jet injections from the central SMBH in the Galaxy to investigate\
-whether the \textit{inclined} jet scenario is able to produce\
+whether the \textit{oblique} jet scenario is able to produce\
 the \textit{symmetric} Galactic bubbles that are\
@@
  (dashed box in left top panel of \Cref{fig__jetI5+ismSeed3-45deg})\
- extending out from the Galactic center on either side of the thin disk.\
+ extending out from the GC on either side of the thin disk.\
  The innermost bubbles are cold (1-10 eV), dense ($10^{-4}$--$10^{-2}$ cm$^{-3}$),\
@@
   First, the broad agreement between simulated and observed X-ray maps hints that\
-  the full vertical extent of the eROSITA bubbles can be properly formed by an inclined jet within a thin disk\
+  the full vertical extent of the eROSITA bubbles can be properly formed by an oblique jet within a thin disk\
   of dense interstellar medium.\
@@
 In this work, we introduce a thin, dense disk composed of clumpy interstellar medium\
-to divert the inclined jet at an angle $45^{\circ}$\
+to divert the oblique jets at an angle $45^{\circ}$\
 to the disk normal in the past energetic event of the central SMBH.
@@
 
-\item The Galactic bubbles are nearly symmetric about the Galactic plane albeit the jet is at an angle $45^{\circ}$\
+\item The Galactic bubbles are nearly symmetric about the Galactic plane albeit\
+      the bipolar jets are at an angle $45^{\circ}$\
       with respect to the disc normal.\
       The broad agreement between simulated and observed multiwavelength features\
-      provides supporting evidence for the inclined jet scenario, and also\
+      provides supporting evidence for the oblique jet scenario, and also\
       releases the caveat given by earlier simulation-based studies:\

### 2022-02-21 paper.tex
update

@@
 which extend nearly symmetrically $\sim50^{\circ}$ on either side of the Galactic center (GC).\
-The recent discovery of eROSITA bubbles also shows a symmetrically enhanced X-ray\
+The recent discovery of giant eROSITA bubbles also shows a symmetrically enhanced X-ray\
 emission from the shells around the eROSITA bubbles.\
@@
 Early attempts \citep{Sarkar2015,Yang2017,Zhang2020}\
-to model the symmetric \textit{Fermi} and eROSITA bubbles (collectively we call the Galactic bubbles)\
+to model the symmetric Galactic bubbles\
 assumed that the jets are vertical to the Galactic plane. However,\

### 2022-02-21 paper.tex
update

@@
 
-The main purpose of this study is to use three-dimensional\
+The main purpose of this study is to use 3D\
 special relativistic hydrodynamics simulations\

### 2022-02-21 paper.tex
update

@@
 The broad agreement between simulated and observed multiwavelength features\
-releases the caveat given by earlier simulation-based studies:\
+have thus released the caveat:\
 the jets shall be vertical to the disc normal.

### 2022-02-21 paper.tex
update

@@
 (1) The simulated Galactic bubbles are nearly symmetric about the GC albeit\
-the bipolar jets are at an angle $45^{\circ}$ with respect to the disc normal.\
+the bipolar jets are at an angle $45^{\circ}$ with respect to\
+the rotation axis of the Galatic plane (disc normal hereafter).\
 (2) The edge of the eROSITA bubbles is a forward shock,\
@@
 observation \citep{Gallimore2006} has proposed that\
-there is a lack of preferred orientation of jets with respect to\
-the rotation axis of a galactic plane (disc normal, hereafter).\
+there is a lack of preferred orientation of jets with respect to the disc normal.\
 In contrast, a number of galaxies in which the jets are oblique to the disc normal\

### 2022-02-21 paper.tex
update

@@
   A few additional quantities are used to characterize the jets:
-  the density contrast between the thermal gas contained in the jet source and the ambient gas,\
+  the density contrast between the thermal gas contained in the jet source and the atmosphere gas,\
   $\rho_{\text{jet}}/\rho_{\text{amb}}=10^{-3}$,\
@@
   Note that as we inject the jets at the center of the clumpy disc,\
-  we define the ambient gas density by the peak density of\
+  we define the atmosphere gas density by the peak density of\
   the isothermal disc on the mid-plane $z=0$ (i.e. $\rho^{\text{peak}}_{\text{isoDisk}}$),\

### 2022-02-21 paper.tex
update

@@
 (3) Followed by the forward shock is a tangling contact discontinuity,\
-which we interpret as the edge of the \textit{Fermi} bubbles.\
-The nature of the \textit{Fermi} bubbles is essentially a turbulent and high-temperature ($\sim2$ keV)\
+which we interpret as the edge of the \textit{Fermi} bubbles,\
+composed of turbulent and high-temperature ($\sim2$ keV)\
 plasma in pressure balance with the external medium.

### 2022-02-21 paper.tex
update

@@
 The broad agreement between simulated and observed multiwavelength features\
-have thus released the caveat:\
+has thus released the caveat:\
 the jets shall be vertical to the disc normal.

### 2022-02-21 paper.tex
update

@@
 emission from the shells around the eROSITA bubbles.\
-To this end, previous simulation-based works assumed that the jets are vertical to the Galactic disk;\
+To this end, previous simulation-based works based on AGN jets model\
+assumed that the jets are vertical to the Galactic disk;\
 however, there is a lack of preferred orientation of jets with respect to the Galactic disk.\
@@
 and compare them with the observed counterparts in order to verify\
-the oblique jets model. We find that\
+an oblique AGN jets model. We find that\
 (1) The simulated Galactic bubbles are nearly symmetric about the GC albeit\
@@
 (3) Followed by the forward shock is a tangling contact discontinuity,\
-which we interpret as the edge of the \textit{Fermi} bubbles,\
+which we interpret as the edge of the \textit{Fermi} bubbles\
 composed of turbulent and high-temperature ($\sim2$ keV)\
@@
 The broad agreement between simulated and observed multiwavelength features\
-has thus released the caveat:\
+has thus released a caveat:\
 the jets shall be vertical to the disc normal.

### 2022-02-21 paper.tex
update

@@
 emission from the shells around the eROSITA bubbles.\
-To this end, previous simulation-based works based on AGN jets model\
+To this end, previous simulation-based works based on active galactic nucleus (AGN) jets model\
 assumed that the jets are vertical to the Galactic disk;\
@@
 \citep{PhysRevLett.106.101102,Carretti2013}
-or past active galactic nucleus (AGN) activity \citep{Guo2012,Yang2017}.
+or past AGN activity \citep{Guo2012,Yang2017}.
 

### 2022-02-21 paper.tex
update

@@
 The gamma-ray emission of the \textit{Fermi} bubbles is observed in the energy range\
-of $1\lesssim E_{\gamma} \lesssim 100$ GeV and has an almost spatially uniform hard\
+of 1--100 GeV and has an almost spatially uniform hard\
 spectrum, sharp edges and an approximately flat brightness distribution.\

### 2022-02-21 paper.tex
update

@@
 surface brightness, and the spectra of \textit{Fermi} bubbles \citep{Ackermann2014}\
-and microwave haze \citep{Dobler_2008,PlanckCollaborationIX2013}.
+and of microwave haze \citep{Dobler_2008,PlanckCollaborationIX2013}.
 

### 2022-02-21 paper.tex
update

@@
 Using three-dimensional (3D) special relativistic hydrodynamic simulations that\
-include cosmic rays (CRs) and thermal gas, we show that a thin interstellar medium disk is an essential\
+include cosmic rays (CRs) and thermal gas, we show that a thin interstellar medium (ISM) disk is an essential\
 component for the symmetry \textit{Fermi} and eROSITA bubbles (collectively, Galactic bubbles).\
@@
 
-To this end, this work introduces a dense thin disc of interstellar medium\
+To this end, this work introduces a dense thin disc of ISM\
 around a jet source to deflects and decelerates the oblique jets,\
@@
   Since the relativistic fluid ejected by the jet source\
-  is quickly stalled off and slowed down by a dense ISM disc in a short time,\
+  is quickly stalled off and slowed down by the dense ISM disc in a short time,\
   and the relativistic fluid\
@@
   the full vertical extent of the eROSITA bubbles can be properly formed by an oblique jet within a thin disk\
-  of dense interstellar medium.\
+  of dense ISM.\
 
@@
 \label{Conclusions}
-In this work, we introduce a thin, dense disk composed of clumpy interstellar medium\
+In this work, we introduce a thin, dense disk composed of clumpy ISM\
 to divert the oblique jets at an angle $45^{\circ}$\

### 2022-02-21 paper.tex
update

@@
   Since the relativistic fluid ejected by the jet source\
-  is quickly stalled off and slowed down by the dense ISM disc in a short time,\
+  is quickly stalled off and slowed down by the dense ISM in a short time,\
   and the relativistic fluid\

### 2022-02-21 paper.tex
update

@@
   as we have assumed $p_{\text{cr}}\ll p_{\text{gas}}$.\
-  $\Phi$ is the gravitation potential.\
+  $\Phi$ is the gravitational potential.\
   $c$ is the speed of light, and $\delta^{ij}$ is the Kronecker delta notation.\

### 2022-02-21 paper.tex
update

@@
 however, there is a lack of preferred orientation of jets with respect to the Galactic disk.\
-Using three-dimensional (3D) special relativistic hydrodynamic simulations that\
+Using three-dimensional (3D) special relativistic hydrodynamic (SRHD) simulations that\
 include cosmic rays (CRs) and thermal gas, we show that a thin interstellar medium (ISM) disk is an essential\
@@
   \textsc{gamer-sr} also adaptively and locally reduce the min-mod coefficient\
-  \citep{tseng2021} within the failed patch group when performing full-step updates,\
+  \citep{tseng2021} within the failed patch group rarely occurring in the SRHD solver,\
   new patches allocations, and ghost-zone interpolations.\
-  In this way, we provide an elegant approach to avoid the use of pressure/density floor,\
+  In this manner, we provide an elegant approach to avoid the use of pressure/density floor,\
   being unnatural but widely used in almost publicly available codes.\

### 2022-02-21 paper.tex
update

@@
   as we have assumed $p_{\text{cr}}\ll p_{\text{gas}}$.\
-  $\Phi$ is the gravitational potential.\
+  $\Phi$ is a gravitational potential.\
   $c$ is the speed of light, and $\delta^{ij}$ is the Kronecker delta notation.\

### 2022-02-21 paper.tex
update

@@
   and assuming the interfaces between isothermal disc and atmosphere are in thermal pressure equilibrium,\
-  we can write the steady-state gaseous density distributions,\
+  we can write the steady-state gaseous density distribution,\
   confined in the total potential, of the disc and the Galactic atmosphere as\

### 2022-02-21 paper.tex
update

@@
 
-  To quantify the synchrotron radiation as a function of position, it\
-  is essential to start the simulation with a more realistic magnetic\
-  field distribution. To this end, for our fixed magnetic field we adopt\
+  To quantify the synchrotron radiation as a function of position,\
+  we adopt\
   the default exponential model in \textsc{galprop} \citep{Strong2007}

### 2022-02-21 paper.tex
update

@@
 \begin{abstract}
-A decade ago, the \textit{Fermi Gamma-Ray Space Telescope} reveals two large bubbles in the Galaxy,\
+The \textit{Fermi Gamma-Ray Space Telescope} reveals two large bubbles in the Galaxy,\
 which extend nearly symmetrically $\sim50^{\circ}$ on either side of the Galactic center (GC).\
@@
 
- %originally driven by an oblique bipolar jets emanating from the GC 12.39 million years ago,\
- %and significantly stretched by the stratified atmosphere afterwards.
-
- % shock wave, followed by a contact discontinuity, moves to the right.
-
- % the innermost bubbles is an expanding reverse shock
- % the forward shock
-
   \begin{figure}
@@
   which is as wide as the eROSITA bubbles in the simulated X-ray map (top panel in \Cref{fig__xray_0.8keV_angle_000}).\
-  We therefore suggest that the nature of eROSITA bubbles is indeed a forward shocks\
+  We therefore suggest that the eROSITA bubble shells are a signature of compressed forward shocks\
   that have been driven into the northern and the southern Galactic halo,
@@
  in \Cref{governing-eq} is reasonable.
-
- %We close on a speculative note that predicts an existence of a third bubbles for
- %future observations.
 

### 2022-02-21 paper.tex
update

@@
 
-To this end, this work introduces a dense thin disc of ISM\
+To this end, this work introduces a dense, thin disc of ISM\
 around a jet source to deflects and decelerates the oblique jets,\
@@
 
-  With the recourse to the isothermal and hydrostatic equilibrium conditions,\
-  and assuming the interfaces between isothermal disc and atmosphere are in thermal pressure equilibrium,\
+  With the help of the isothermal and hydrostatic equilibrium conditions,\
+  and assuming the interfaces between the disc and atmosphere are in thermal pressure equilibrium,\
   we can write the steady-state gaseous density distribution,\
-  confined in the total potential, of the disc and the Galactic atmosphere as\
+  confined in the total potential, of the disc and  Galactic atmosphere as\
   \begin{subequations}
@@
      \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{isoDisk}}/m_{\text{p}}}\right]&\label{isothermal-disc-density}\\
-     \text{, if $|z| < z_{0}$}& \nonumber \\
+     \text{, if $|z| < z_{0}$,}& \nonumber \\
      \nonumber\\
@@
   where $m_{\text{p}}$ is the proton mass,\
-  $T_{\text{isoDisk}}$ and $T_{\text{atmp}}$ is the temperature of the isothermal disc and atmosphere,\
+  $T_{\text{isoDisk}}$ and $T_{\text{atmp}}$ is the temperature of the disc and atmosphere,\
   $\rho_{\text{isoDisk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the peak mass density\
@@
     \includegraphics[width=\columnwidth]{figures/fig__initial-density-profile.png}
-    \caption{The density profile of the isothermal disc (red pluses) and\
+    \caption{The density profile of the disc (red pluses) and\
              atmosphere (blue crosses) along the positive z-axis.\
@@
   the Nyquist limit $k_{\text{max}}$, and the lower cutoff wave number $k_{\text{min}}$.
-  $k_{\text{max}}$ is one-half of the spatial resolution within disc,\
+  $k_{\text{max}}$ is one-half of the spatial resolution within the disc,\
   and $k_{\text{min}}$ is 375.0, corresponding to the maximum size of an individual clump $\sim 20$ pc.\
@@
 
-  The density of clumpy disc can thus be obtained by taking the scalar products of\
+  The density of the clumpy disc can thus be obtained by taking the scalar products of\
   $f(\bold{x})$ with $\rho_{\text{isoDisk}}(z)$ over all cells within the disc, i.e.,\
@@
   f(\bold{x}) \rho_{\text{isoDisk}}(z)$.\
-  Also, the thermal pressure equilibrium within the clumpy disc implies that the temperature of disc is
+  Also, the thermal pressure equilibrium within the clumpy disc implies that the temperature of the disc is
   $\displaystyle T_{\text{ismDisk}}(\bold{x}) =\
@@
   based on the gradient of mass density.\
-  We also restrict the refinement level at 7 within the cold disc so that\
+  We also restrict the refinement level at 7 within the disc so that\
   a molecular cloud can be adequately resolved by approximately 30 cells along their diameter, 20 pc.
@@
   we define the atmosphere gas density by the peak density of\
-  the isothermal disc on the mid-plane $z=0$ (i.e. $\rho^{\text{peak}}_{\text{isoDisk}}$),\
+  the smooth disc on the mid-plane $z=0$ (i.e. $\rho^{\text{peak}}_{\text{isoDisk}}$),\
   as opposed to the \textit{clumpy} density around the jet source, to avoid ambiguous definition.

### 2022-02-21 paper.tex
update

@@
   As a proof-of-concept study, we approximate conventionally axisymmetric stellar potential of Milky Way\
-  by a plane-parallel potential that is symmetric about the mid-plane $z=0$\
+  by a plane-parallel potential that is symmetric about the mid-plane, or the Galactic plane, $z=0$\
   in a simulation box size of\
@@
   With the help of the isothermal and hydrostatic equilibrium conditions,\
-  and assuming the interfaces between the disc and atmosphere are in thermal pressure equilibrium,\
+  and assuming the interfaces between the isothermal disc and atmosphere are in thermal pressure equilibrium,\
   we can write the steady-state gaseous density distribution,\
@@
   where $m_{\text{p}}$ is the proton mass,\
-  $T_{\text{isoDisk}}$ and $T_{\text{atmp}}$ is the temperature of the disc and atmosphere,\
+  $T_{\text{isoDisk}}$ and $T_{\text{atmp}}$ is the temperature of the isothermal disc and atmosphere,\
   $\rho_{\text{isoDisk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the peak mass density\
@@
     \includegraphics[width=\columnwidth]{figures/fig__initial-density-profile.png}
-    \caption{The density profile of the disc (red pluses) and\
+    \caption{The density profile of the isothermal disc (red pluses) and\
              atmosphere (blue crosses) along the positive z-axis.\
@@
   we define the atmosphere gas density by the peak density of\
-  the smooth disc on the mid-plane $z=0$ (i.e. $\rho^{\text{peak}}_{\text{isoDisk}}$),\
+  the isothermal disc on the mid-plane $z=0$ (i.e. $\rho^{\text{peak}}_{\text{isoDisk}}$),\
   as opposed to the \textit{clumpy} density around the jet source, to avoid ambiguous definition.

### 2022-02-21 paper.tex
update

@@
   To quantify the synchrotron radiation as a function of position,\
-  we adopt\
-  the default exponential model in \textsc{galprop} \citep{Strong2007}
+  we adopt the default exponential magnetic field model in \textsc{galprop} \citep{Strong2007}
   which has the following spatial dependence:\

### 2022-02-21 paper.tex
update

--- 2022-02-21 paper.tex
@@
   To quantify the synchrotron radiation as a function of position,\
-  we adopt\
-  the default exponential model in \textsc{galprop} \citep{Strong2007}
-  which has the following spatial dependence:\
+  we adopt the default exponential magnetic field in \textsc{galprop} \citep{Strong2007}
+  which obeys the following spatial dependence:\
 

### 2022-02-21 paper.tex
update

--- 2022-02-21 paper.tex
@@
   To quantify the synchrotron radiation as a function of position,\
-  we adopt\
-  the default exponential model in \textsc{galprop} \citep{Strong2007}
-  which has the following spatial dependence:\
+  we adopt the default exponential magnetic field in \textsc{galprop} \citep{Strong2007}
+  that obeys the following spatial dependence:\
 
@@
 
-  where $R=\sqrt{x^{2}+y^{2}}$, $B_{0}$ is the average field strength at the GC\
+  where $R=\sqrt{x^{2}+y^{2}}$, $B_{0}$ is the average field strength at the GC,\
   and $z_{0}$ and $R_{0}$ are the characteristic scales in the vertical and radial\
@@
   where $\hat{f}(\bold{k})$ is the Fourier transform of $f(\bold{x})$.\
-  The spectrum $D(\bold{k})$ in the Fourier space is characterized by the power-law index $\beta=5/3$,\
-  the Nyquist limit $k_{\text{max}}$, and the lower cutoff wave number $k_{\text{min}}$.
+  The spectrum $D(\bold{k})$ in the Fourier space is characterized by a power-law index $\beta=5/3$,\
+  a Nyquist limit $k_{\text{max}}$, and a lower cutoff wave number $k_{\text{min}}$.
   $k_{\text{max}}$ is one-half of the spatial resolution within the disc,\
@@
 
-  \Cref{table-parameters} summarize the parameters of the clumpy disc and their references.
+  The last category in \Cref{table-parameters} summarize the parameters of the clumpy disc and their references.
 

### 2022-02-21 paper.tex
update

@@
 
-  \Cref{fig__numberDensityHistogram} plots the volume filling factor as a function of\
-  initial number density within the disc without jet source.\
-
-  \Cref{fig__zoom-in-disc} shows a close-up view of the\
+  In this way, we plot the volume filling factor as a function of\
+  initial number density within the disc without the jet source in \Cref{fig__numberDensityHistogram},\
+  and show a close-up view of the\
   pressure, temperature, and number density slices
-  in the y-z plane through the center of the disc.
+  in the y-z plane through the center of the disc in \Cref{fig__zoom-in-disc} .
 

### 2022-02-21 paper.tex
update

@@
   the jet direction must be perpendicular to the Galactic plane, and in particular to\
-  investigate the effect of the jet-disc misalignment on the symmetry of bubbles.
+  investigate how the dense disc affect the bubbles formation.
 

### 2022-02-21 paper.tex
update

@@
 
-  Motivated by these observations, we simulate the jet with an inclination angle\
+  We simulate the jet with an inclination angle\
   $45^{\circ}$ with respect to the Galactic plane\

### 2022-02-21 paper.tex
update

@@
   Without quenching, the Galactic bubbles at the present time will be asymmetric about the Galactic plane.
-  The jet duration (1.2 Myr) allows the total ejected energy to be $1.2\times10^{56}$ erg, bracketed by\
+  The jet duration allows the total ejected energy to be $1.2\times10^{56}$ erg, bracketed by\
   $8\times10^{55}$ and $1.3\times10^{56}$ erg, estimated by \citet{Predehl2020}.\

### 2022-02-21 paper.tex
update

@@
   Without quenching, the Galactic bubbles at the present time will be asymmetric about the Galactic plane.
-  The jet duration allows the total ejected energy to be $1.2\times10^{56}$ erg, bracketed by\
+  The jet duration allows the total ejected energy to be $1.2\times10^{56}$ erg between\
   $8\times10^{55}$ and $1.3\times10^{56}$ erg, estimated by \citet{Predehl2020}.\

### 2022-02-21 paper.tex
update

@@
   The jet duration allows the total ejected energy to be $1.2\times10^{56}$ erg between\
-  $8\times10^{55}$ and $1.3\times10^{56}$ erg, estimated by \citet{Predehl2020}.\
-
-  The diameter and height of cylindrical source are 4 pc, leading to the source volume $\sim 50 \text{ pc}^{3}$ is\
+  $8\times10^{55}$ erg and $1.3\times10^{56}$ erg, estimated by \citet{Predehl2020}.\
+
+  The diameter and height of cylindrical source are 4 pc,\
+  leading to the source volume ($\sim 50 \text{ pc}^{3}$) is\
   much smaller than that of an individual clump by a factor of about 83.\

### 2022-02-21 paper.tex
update

@@
  \Cref{fig__jetI5+ismSeed3-45deg} indicates that\
- most of the region between the forward shock and the turbulent zone\
+ the smooth region (red band) emitting X-ray\
  is around 0.3-0.4 keV, similar to that observed by \citet{Miller2016} and \citet{Kataoka2018}.

### 2022-02-21 paper.tex
update

@@
  \Cref{fig__jetI5+ismSeed3-45deg} indicates that\
- the smooth region (red band) emitting X-ray\
- is around 0.3-0.4 keV, similar to that observed by \citet{Miller2016} and \citet{Kataoka2018}.
+ the smooth region (purple band) emitting X-ray\
+ is around 0.3-0.5 keV, similar to that observed by \citet{Miller2016} and \citet{Kataoka2018}.
 
@@
  and underpressured with respect to the turbulent plasma.\
- Moreover, the close-up view of profiles around $z=3.7$ kpc (right column in \Cref{fig__profile})
+ Moreover, the close-up view (right column in \Cref{fig__profile}) of profiles in yellow band
  demonstrates that there is a sharp pressure jump and dense shell at $z=3.61$ kpc,\
@@
              along the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.
-             Right: the close-up view of profiles around $z=3.7$ kpc.\
+             Right: the close-up view of profiles in the yellow band.\
              The sharp pressure jump and dense shell at $z=3.61$ kpc\

### 2022-02-21 paper.tex
update

@@
  that of the \textit{Fermi} bubbles \citep{Su2010}.
- Also, the temperature of the plasma is as high as 2 keV, comparable to that inside the \textit{Fermi} bubbles\
- by observing X-ray absorption lines through the hot\
+ Also, the temperature of the plasma is as high as 2 keV, comparable to few keV inside the \textit{Fermi} bubbles\
+ obtained by observing X-ray absorption lines through the hot\
  gaseous halo along many different sight lines in the sky \citep{Miller_2013}.\

### 2022-02-21 paper.tex
update

@@
  and underpressured with respect to the turbulent plasma.\
- Moreover, the close-up view (right column in \Cref{fig__profile}) of profiles in yellow band
+ Moreover, the close-up view (right column in \Cref{fig__profile}) of profiles\
  demonstrates that there is a sharp pressure jump and dense shell at $z=3.61$ kpc,\

### 2022-02-22 paper.tex
update

@@
 {\bf Static dark halo potential }     &                                           &                                      &                                \\
-$v_{\text{halo}}$                     &                                           & 131.5 km$\cdot$s$^{-1}$              & \citep{Johnston1995}           \\
+$v_{\text{halo}}$                     & Characteristic velocity                   & 131.5 km$\cdot$s$^{-1}$              & \citep{Johnston1995}           \\
 $d_{\text{h}}$                        & Core radius                               & 12 kpc                               & \multicolumn{1}{c}{''}         \\ \hline
@@
 
-  First, the broad agreement between simulated and observed X-ray maps hints that\
+  First, we observe that\
+  The simulated eROSITA bubbles are not as limb-brightened as the observation.\
+  A possibility to enhance the X-ray emission is to include shock-accelerated CRs near the shock,\
+  in which CRs could increase the compressibility of the fluid,\
+  resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density.
+  The broad agreement between simulated and observed X-ray maps hints that\
   the full vertical extent of the eROSITA bubbles can be properly formed by an oblique jet within a thin disk\
-  of dense ISM.\
+  of dense ISM.
 
@@
       and significantly stretched by the stratified atmosphere afterwards.\
-      The simulated eROSITA bubbles are not as limb-brightened as the observed one.\
+      The simulated eROSITA bubbles are not as limb-brightened as the observation.\
       A possibility to enhance the X-ray emission is to include shock-accelerated CRs near the shock,\
-      in which CRs could increase the compressibility of the fluid.\
+      in which CRs could increase the compressibility of the fluid,\
+      resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density.
 \item Followed by the forward shock is a tangling contact discontinuity,\

### 2022-02-22 paper.tex
update

@@
 \raggedright
-\caption{Parameters of the disc, atmosphere, and gravitational potential in the simulation.}
+\caption{Parameters of the disc, atmosphere, and gravitational potential in the simulations.}
 \label{table-parameters}
@@
   in which CRs could increase the compressibility of the fluid,\
-  resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density.
+  resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density squared.
   The broad agreement between simulated and observed X-ray maps hints that\
@@
       in which CRs could increase the compressibility of the fluid,\
-      resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density.
+      resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density squared.
 \item Followed by the forward shock is a tangling contact discontinuity,\

### 2022-02-22 paper.tex
update

@@
  \Cref{fig__jetI5+ismSeed3-45deg} indicates that\
- the smooth region (purple band) emitting X-ray\
+ the smooth region (purple band in \Cref{fig__profile}) emitting X-ray\
  is around 0.3-0.5 keV, similar to that observed by \citet{Miller2016} and \citet{Kataoka2018}.

### 2022-02-22 paper.tex
update

@@
 to divert the oblique jets at an angle $45^{\circ}$\
-to the disk normal in the past energetic event of the central SMBH.
-
-Also, We investigate the properties of the Galactic bubbles and the microwave\
+to the disk normal in the past energetic event of the central SMBH.\
+We investigate the properties of the Galactic bubbles and the microwave\
 haze using 3D special relativistic hydrodynamic simulations of CR injection from\
@@
 \item The randomness of clumpy disk has a insignificant impact on the overall dynamic of the Galactic bubbles.\
-      The development of the reverse shocks (the innermost bubbles) are always associated with the dense disc,\
+      The development of the reverse shocks (the innermost bubbles) is always associated with the dense disc,\
       without the disc, the outermost bubbles and the turbulent plasma will be oblique,\
@@
       plasma in pressure balance with the external medium. Associated with the Galactic magnetic field\
-      will lead to the stochastic acceleration of CRe, and probably balanced with the IC and synchrotron cooling.\
+      will lead to the stochastic acceleration of CRe, possibly in balance with the IC and synchrotron cooling.\
       We will investigate the competition between stochastic acceleration and radiative cooling in a future work.

### 2022-02-22 paper.tex
update

@@
 Fourth, the good agreement between the simulated and observed gamma-ray/microwave spectra\
-imply that, in the presence of ISRF and magnetic fields, the emission of the Fermi bubbles and\
+implies that, in the presence of ISRF and magnetic fields, the emission of the Fermi bubbles and\
 the microwave haze can be produced by the same high-energy electrons\

### 2022-02-22 paper.tex
update

@@
  As the eROSITA bubbles,\
- one can see that the symmetric of the \textit{Fermi} bubbles\
+ one can see that the symmetric \textit{Fermi} bubbles\
  can also be realized by oblique jets.\

### 2022-02-22 paper.tex
update

@@
 The simulated gamma-ray and microwave spectra is based on the\
-IC scattering and synchrotron from CRe, respectively, in which\
-the CRe spectrum follows a power-law distribution ranging from\
+IC scattering and synchrotron, respectively, from CRe.\
+The CRe spectrum follows a power-law distribution ranging from\
 $0.5$ MeV to $562.1$ GeV.
@@
 
-where $\Gamma$ is gamma function, $B$ is the magnetic field strength defined in\
+where $\Gamma$ is the gamma function, $B$ is the magnetic field strength defined in\
 \Cref{magnetic-field}.

### 2022-02-22 paper.tex
update

@@
 We also produce simulated gamma-ray and\
-microwave spectra from the inverse Compton scattering and synchrotron,\
+microwave spectra from the inverse Compton (IC) scattering and synchrotron,\
 and compare them with the observed counterparts in order to verify\

### 2022-02-22 paper.tex
update

@@
      &\partial_{t} \left(\gamma e_{\text{cr}}\right) + \partial_{j} \left(e_{\text{cr}}U^{j}\right)=\
-     -p_{\text{cr}} \partial_{j} U^{j},\label{D evolution}
+     -p_{\text{cr}} \partial_{j} U^{j},\label{E evolution}
     \end{align}

### 2022-02-22 paper.tex
update

@@
 include cosmic rays (CRs) and thermal gas, we show that a thin interstellar medium (ISM) disk is an essential\
-component for the symmetry \textit{Fermi} and eROSITA bubbles (collectively, Galactic bubbles).\
+component for the symmetric \textit{Fermi} and eROSITA bubbles (collectively, Galactic bubbles).\
 We also produce simulated gamma-ray and\

### 2022-02-22 paper.tex
update

@@
              along the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.
-             Right: the close-up view of profiles in the yellow band.\
+             Right: the close-up view of the profiles in the yellow band.\
              The sharp pressure jump and dense shell at $z=3.61$ kpc\

### 2022-02-24 paper.tex
update

@@
 
-\subsection{Inclined jet injection}
+\subsection{Oblique jets injection}
 
@@
 
- The most interesting finding is that there is a innermost bubbles\
+ The most interesting finding is that there are innermost bubbles\
  (dashed box in left top panel of \Cref{fig__jetI5+ismSeed3-45deg})\
@@
  and underpressured with respect to the turbulent plasma.\
+
  Moreover, the close-up view (right column in \Cref{fig__profile}) of profiles\
- demonstrates that there is a sharp pressure jump and dense shell at $z=3.61$ kpc,\
- indicating that the innermost bubbles are an expanding reverse shock.\
+ demonstrates that there is a sharp pressure jump at $z=3.62$ kpc,\
+ indicating that the pressure jump is an expanding reverse shock.\
+ The high density upstream of the reverse shock requires\
+ an even higher density downstream, i.e. a dense shell formation.\
+ Continuing outward, the higher density must match with low density further downstream;\
+ thus there exists a contact discontinuity ($z=3.75$ kpc).
+
  We also find that the turbulent plasma is bracketed between the downstream of reverse shock\
  and of the outermost forward shock, thus heating the turbulent plasma up considerably.
+
+ The small contact discontinuity, CD, is interesting in its own way\
+ but not a major event to alter the overall large scale structure of the flow.\
 

### 2022-02-24 paper.tex
update

@@
  The high density upstream of the reverse shock requires\
- an even higher density downstream, i.e. a dense shell formation.\
+ an even higher density downstream.\
  Continuing outward, the higher density must match with low density further downstream;\
- thus there exists a contact discontinuity ($z=3.75$ kpc).
+ thus there exists a dense shell (3.62--3.75 kpc) associated with a contact discontinuity ($z=3.75$ kpc).
 
@@
              Right: the close-up view of the profiles in the yellow band.\
-             The sharp pressure jump and dense shell at $z=3.61$ kpc\
+             The sharp pressure jump at $z=3.62$ kpc\
              indicate that the innermost bubbles\
@@
              are an expanding reverse shock.\
+             The high density upstream of the reverse shock requires\
+             an even higher density downstream.\
+             Continuing outward, the higher density must match with low density further downstream;\
+             thus there exists a dense shell (3.62--3.75 kpc) associated with a contact discontinuity ($z=3.75$ kpc).
      }

### 2022-02-24 paper.tex
update

@@
 
- We also find that the turbulent plasma is bracketed between the downstream of reverse shock\
+ The turbulent plasma is therefore bracketed between the downstream of reverse shock\
  and of the outermost forward shock, thus heating the turbulent plasma up considerably.
-
- The small contact discontinuity, CD, is interesting in its own way\
- but not a major event to alter the overall large scale structure of the flow.\
 

### 2022-02-24 paper.tex
update

@@
              The sharp pressure jump at $z=3.62$ kpc\
-             indicate that the innermost bubbles\
+             indicates that the innermost bubbles\
              (dashed box in top left panel of \Cref{fig__jetI5+ismSeed3-45deg})\

### 2022-02-24 paper.tex
update

@@
  Moreover, the close-up view (right column in \Cref{fig__profile}) of profiles\
- demonstrates that there is a sharp pressure jump at $z=3.62$ kpc,\
- indicating that the pressure jump is an expanding reverse shock.\
+ demonstrates that there is a sharp pressure jump on the edge of the innermost bubbles ($z=3.62$ kpc),\
+ indicating that the innermost bubbles are an expanding reverse shock.\
  The high density upstream of the reverse shock requires\
@@
  thus there exists a dense shell (3.62--3.75 kpc) associated with a contact discontinuity ($z=3.75$ kpc).
-
  The turbulent plasma is therefore bracketed between the downstream of reverse shock\

### 2022-02-24 paper.tex
update

@@
   is severely suppressed by the cutoff $\exp\left[-h\nu/k_{B}T\right]$ in the thermal Bremsstrahlung emissivity.\
-  This is the reason why the innermost bubbles is unseen in the observation.
+  This is the reason why the innermost bubbles is unseen in the X-ray observation.
 

### 2022-02-24 paper.tex
update

--- 2022-02-24 paper.tex
@@
   is severely suppressed by the cutoff $\exp\left[-h\nu/k_{B}T\right]$ in the thermal Bremsstrahlung emissivity.\
-  This is the reason why the innermost bubbles is unseen in the observation.
+  This is the reason why the innermost bubbles are unseen in the X-ray observation.
 

### 2022-02-24 paper.tex
update

--- 2022-02-24 paper.tex
@@
   even though with high column density, is invisible in the simulated X-ray map as\
-  the temperature of innermost bubbles is around $1$--$10$ eV\
+  the temperature of the innermost bubbles is around $1$--$10$ eV\
   (see the temperature profile in \Cref{fig__profile}).\

### 2022-02-24 paper.tex
update

--- 2022-02-24 paper.tex
@@
   shown in \Cref{fig__jetI5+ismSeed3-45deg},\
-  even though with high column density, is invisible in the simulated X-ray map as\
-  the temperature of innermost bubbles is around $1$--$10$ eV\
+  even though with high column density, are invisible in the simulated X-ray map as\
+  the temperature of the innermost bubbles is around $1$--$10$ eV\
   (see the temperature profile in \Cref{fig__profile}).\
@@
   is severely suppressed by the cutoff $\exp\left[-h\nu/k_{B}T\right]$ in the thermal Bremsstrahlung emissivity.\
-  This is the reason why the innermost bubbles is unseen in the X-ray observation.
+  This is the reason why the innermost bubbles are unseen in the X-ray observation.
 

### 2022-02-24 paper.tex
update

@@
 
- To explore how the disk affect the formation of the Galactic bubbles,\
+ To explore how the disk affects the formation of the Galactic bubbles,\
  we compare the fiducial run (first column from left in \Cref{fig__jetI5+ismSeed3-45deg})\

### 2022-03-03 overleaf.tex
update

--- 2022-02-24 paper.tex
@@
 In Section \ref{Results}, we first present characteristics of our simulated Galactic bubbles,\
-and then discuss how the disk affect the formation of the bubbles.\
+and then discuss how the disk affects the formation of the bubbles.\
 We directly compare the morphology and profile of simulated eROSITA bubbles with\

### 2022-03-03 paper.tex
update

@@
 
+  \begin{figure}
+    \includegraphics[width=\columnwidth]{figures/fig__innerbubbles.png}
+    \caption{
+       Zoom-in image of the innermost bubbles
+     }
+    \label{fig__innerbubbles}
+  \end{figure}
+
   \subsection{X-ray}

### 2022-03-03 paper.tex
update

@@
 and significantly stretched by the stratified atmosphere afterwards.\
-(3) Followed by the forward shock is a tangling contact discontinuity,\
-which we interpret as the edge of the \textit{Fermi} bubbles\
-composed of turbulent and high-temperature ($\sim2$ keV)\
+(3) Followed by the forward shock is a tangling turbulence,\
+which we interpret as the \textit{Fermi} bubbles\
+composed of high-temperature ($\sim2$ keV)\
 plasma in pressure balance with the external medium.
@@
 
- Followed by the forward shock is a turbulent and hot plasma.\
+ Followed by the forward shock is a turbulent and hot plasma\
+ in pressure balance with the external medium.\
  As shown in the temperature or density slices of the fiducial run,\
- the full extent of the turbulent plasma is approximately agree with\
- that of the \textit{Fermi} bubbles \citep{Su2010}.
- Also, the temperature of the plasma is as high as 2 keV, comparable to few keV inside the \textit{Fermi} bubbles\
- obtained by observing X-ray absorption lines through the hot\
+ the full extent of the turbulent plasma is 9 kpc, fairly close to\
+ that of the observed \textit{Fermi} bubbles \citep{Su2010}.
+ Also, the temperature of the plasma is as high as 2 keV,\
+ comparable to few keV inside the \textit{Fermi} bubbles\
+ by observing X-ray absorption lines through the hot\
  gaseous halo along many different sight lines in the sky \citep{Miller_2013}.\
- We also note that the turbulence within the hot plasma is in pressure balance with the external medium,\
- suggesting the outer edge of the \textit{Fermi} bubbles\
- is a tangling contact discontinuity rather than a smooth shock \citep{Zhang2020}.
+ The general agreement of extent and temperature\
+ suggests that the \textit{Fermi} bubbles\
+ is essentially a turbulence rather than a smooth shock \citep{Zhang2020}.
 
@@
     \caption{
-       Zoom-in image of the innermost bubbles
+       Zoom-in image of the innermost bubbles.
      }

### 2022-03-03 paper.tex
update

@@
  Continuing outward, the higher density must match with low density further downstream;\
- thus there exists a dense shell (3.62--3.75 kpc) associated with a contact discontinuity ($z=3.75$ kpc).
+ thus there exists a dense shell (3.62--3.75 kpc).
+
  The turbulent plasma is therefore bracketed between the downstream of reverse shock\
@@
              Continuing outward, the higher density must match with low density further downstream;\
-             thus there exists a dense shell (3.62--3.75 kpc) associated with a contact discontinuity ($z=3.75$ kpc).
+             thus there exists a dense shell (3.62--3.75 kpc).
      }
@@
       resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density squared.
-\item Followed by the forward shock is a tangling contact discontinuity,\
-      which we interpret as the edge of the \textit{Fermi} bubbles.\
-      The nature of the \textit{Fermi} bubbles is essentially a turbulent and high-temperature ($\sim2$ keV)\
-      plasma in pressure balance with the external medium. Associated with the Galactic magnetic field\
+\item Followed by the forward shock is a turbulent and hot plasma ($\sim2$ keV),\
+      which we interpret as the \textit{Fermi} bubbles.\
+      The similarity of the morphology, temperature, and gamma-ray spectrum between\
+      simulated and observed \textit{Fermi} bubbles suggests that\
+      the \textit{Fermi} bubbles are essentially a turbulent\
+      high temperature plasma in pressure balance with external medium.
+      Associated with the Galactic magnetic field\
       will lead to the stochastic acceleration of CRe, possibly in balance with the IC and synchrotron cooling.\

### 2022-03-03 paper.tex
update

@@
       simulated and observed \textit{Fermi} bubbles suggests that\
-      the \textit{Fermi} bubbles are essentially a turbulent\
+      the \textit{Fermi} bubbles are essentially a turbulent and\
       high temperature plasma in pressure balance with external medium.

### 2022-03-03 paper.tex
update

@@
 Using three-dimensional (3D) special relativistic hydrodynamic (SRHD) simulations that\
-include cosmic rays (CRs) and thermal gas, we show that a thin interstellar medium (ISM) disk is an essential\
+include cosmic rays (CRs) and thermal gas, we show that a thin interstellar medium (ISM) disk is a substantial\
 component for the symmetric \textit{Fermi} and eROSITA bubbles (collectively, Galactic bubbles).\
@@
 and significantly stretched by the stratified atmosphere afterwards.\
-(3) Followed by the forward shock is a tangling turbulence,\
-which we interpret as the \textit{Fermi} bubbles\
-composed of high-temperature ($\sim2$ keV)\
-plasma in pressure balance with the external medium.
+(3) Followed by the forward shock is a\
+hot ($\sim2$ keV), turbulent, and pressure-balanced plasma,\
+which we interpret as the \textit{Fermi} bubbles.\
+Inside the simulated \textit{Fermi} bubbles,\
+there are two innermost bubbles we have not detected yet.\
+The innermost bubbles are essentially a reverse shock.
 (4) According to the microwave and leptonic gamma-ray spectra, the best-fitting\
 CRe power-law index is found to be 2.4.\
-The broad agreement between simulated and observed multiwavelength features\
+The broad agreement between the simulations and observations\
+, either from the point of view of their morphology or multiwavelength features,\
 has thus released a caveat:\

### 2022-03-03 paper.tex
update

@@
 Inside the simulated \textit{Fermi} bubbles,\
-there are two innermost bubbles we have not detected yet.\
-The innermost bubbles are essentially a reverse shock.
+there are two additional innermost bubbles we have not detected yet.\
+The innermost bubbles are essentially a reverse shock permanently associated with the disk.\
 (4) According to the microwave and leptonic gamma-ray spectra, the best-fitting\

### 2022-03-03 paper.tex
update

@@
 
- Moreover, the close-up view (right column in \Cref{fig__profile}) of profiles\
- demonstrates that there is a sharp pressure jump on the edge of the innermost bubbles ($z=3.62$ kpc),\
+ Moreover, the close-up view (right column in \Cref{fig__profile})\
+ of profiles and slices (\Cref{fig__innerbubbles})\
+ demonstrates that the pressure rises dramatically outward across\
+ the edge of the innermost bubbles,\
  indicating that the innermost bubbles are an expanding reverse shock.\
@@
  Continuing outward, the higher density must match with low density further downstream;\
- thus there exists a dense shell (3.62--3.75 kpc).
+ thus there exists a dense shell.
 
@@
              (dashed box in top left panel of \Cref{fig__jetI5+ismSeed3-45deg})\
-             are an expanding reverse shock.\
+             are an expanding reverse shock.
+     }
+    \label{fig__profile}
+  \end{figure}
+
+  \begin{figure}
+    \includegraphics[width=\columnwidth]{figures/fig__innerbubbles.png}
+    \caption{
+       Zoom-in images of the density (left) and pressure (right) slices of the innermost bubbles.\
        The high density upstream of the reverse shock requires\
@@
        Continuing outward, the higher density must match with low density further downstream;\
-             thus there exists a dense shell (3.62--3.75 kpc).
-     }
-    \label{fig__profile}
-  \end{figure}
-
-  \begin{figure}
-    \includegraphics[width=\columnwidth]{figures/fig__innerbubbles.png}
-    \caption{
-       Zoom-in image of the innermost bubbles.
+       thus there exists a dense shell\
+       (the turbulent region outside the black dashed line on density slice).
      }

### 2022-03-08 paper.tex
update

@@
 
- The fiducial run (leftmost column) with the initial condition specified in Section \ref{Methodology}\
+ The fiducial run (a1-a3) with the initial condition specified in Section \ref{Methodology}\
  shows that the edge of the outermost bubbles is indeed a forward shock,\
@@
  To explore how the disk affects the formation of the Galactic bubbles,\
- we compare the fiducial run (first column from left in \Cref{fig__jetI5+ismSeed3-45deg})\
+ we compare the fiducial run (panels a1-a3 in \Cref{fig__jetI5+ismSeed3-45deg})\
  with the case adopting the smooth disc\
- (second column; \Cref{fig__initial-density-profile} shows the density profile) in a stratified atmosphere.\
+ (panels b1-b3; \Cref{fig__initial-density-profile} shows the density profile) in a stratified atmosphere.\
  The results show that the initial density distribution of the dense disc has an insignificant effect\
  on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
- in an uniform atmosphere (third column) is spherical-shape,\
+ in an uniform atmosphere (panels c1-c3) is spherical-shape,\
  suggesting the stratification facilitates the outermost bubbles elongation significantly.\
@@
              for a duration $t=0$--$1.2$ Myr.\
-             Comparison between the clumpy (first column from left)\
-             and the smooth disc (second) in a stratified atmosphere\
+             Comparison between the clumpy (a1-a3)\
+             and the smooth disc (b1-b3) in a stratified atmosphere\
              shows that the initial density distribution of the dense disc has an insignificant effect\
              on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
-             in an uniform atmosphere (third) is spherical-shape,\
+             in an uniform atmosphere (c1-c3) is spherical-shape,\
              suggesting the stratification facilitates the outermost bubbles elongation significantly.\
              Also, the two rightmost columns reveal that the development of the innermost bubbles\
-             (dashed box in top left panel)\
+             (a1)\
              is always associated with the disc, without the disc,\

### 2022-03-08 paper.tex
update

@@
 \usepackage{mathtools}
+%\usepackage{caption}
+%\usepackage{subcaption}
 \usepackage{natbib}
@@
 \usepackage{floatrow}
-\usepackage{subfigure}
+\usepackage[]{subfigure}
 \usepackage{float}
@@
 
- To explore how the disk affects the formation of the Galactic bubbles,\
- we compare the fiducial run (panels a1-a3 in \Cref{fig__jetI5+ismSeed3-45deg})\
+ \Cref{fig__jetI5+ismSeed3-45deg} shows the slices of various gas properties at $t=12.39$ Myr,
+ including pressure (top), temperature (middle), density (bottom) with the same jet source as the fiducial run\
+ but in different Galactic environments.
+
+ %To explore how the disk affects the formation of the Galactic bubbles,\
+ We compare the fiducial run (a1-a3)\
  with the case adopting the smooth disc\
- (panels b1-b3; \Cref{fig__initial-density-profile} shows the density profile) in a stratified atmosphere.\
+ (b1-b3), specified by the initial density profile shown in
+ \Cref{fig__initial-density-profile}, in a stratified atmosphere.\
  The results show that the initial density distribution of the dense disc has an insignificant effect\
  on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
- in an uniform atmosphere (panels c1-c3) is spherical-shape,\
+ in an uniform atmosphere (c1-c3) is spherical-shape,\
  suggesting the stratification facilitates the outermost bubbles elongation significantly.\
@@
              Also, the two rightmost columns reveal that the development of the innermost bubbles\
-             (a1)\
-             is always associated with the disc, without the disc,\
+             is always associated with the disc, without the disc (d1-d3),\
              the outermost bubbles and the turbulent plasma will be oblique,
@@
   \end{figure}
+
+\begin{figure}%
+  \centering%
+  \subfigure[][]%
+    {%
+      \includegraphics[height=10.1cm]{figures/fig__jetI5+ismSeed3-45deg-a}%
+      \label{fig__jetI5+ismSeed3-45deg-a}% A
+    }%
+  \hspace{2pt}%
+  \subfigure[][]%
+    {%
+      \includegraphics[height=10.1cm]{figures/fig__jetI5+ismSeed3-45deg-b}%
+      \label{fig__jetI5+ismSeed3-45deg-b}%
+    }%
+  \hspace{2pt}%
+  \subfigure[][]%
+    {%
+      \includegraphics[height=10.1cm]{figures/fig__jetI5+ismSeed3-45deg-c}%
+      \label{fig__jetI5+ismSeed3-45deg-c}%
+    }%
+  \hspace{2pt}%
+  \subfigure[][]%
+    {%
+      \includegraphics[height=10.1cm]{figures/fig__jetI5+ismSeed3-45deg-d}
+      \label{fig__jetI5+ismSeed3-45deg-d} %D
+    }%
+  \caption{}%
+  \label{fig__jetI5+ismSeed3-45deg}%
+\end{figure}%
 

### 2022-03-11 paper.tex
update

@@
 \usepackage{mathtools}
-%\usepackage{caption}
-%\usepackage{subcaption}
 \usepackage{natbib}
@@
 \pdfminorversion=5
+
+\renewcommand*{\thesubfigure}{\Alph{subfigure}}
 
@@
 \label{Methodology}
-  We used the GPU-accelerated special relativistic hydrodynamics AMR code (\textsc{gamer-sr}) developed at the\
+  We used the GPU-accelerated special relativistic\
+  hydrodynamics AMR code (\textsc{gamer-sr}) developed at the\
   National Taiwan University\
@@
 
- The fiducial run (a1-a3) with the initial condition specified in Section \ref{Methodology}\
+ The fiducial run (\Cref{fig__jetI5+ismSeed3-45deg-a})\
+ with the initial condition specified in Section \ref{Methodology}\
  shows that the edge of the outermost bubbles is indeed a forward shock,\
@@
  We note that the overall extent of the outermost bubbles is comparable to\
- the two spherical objects of a radius 6-7 kpc proposed by \citet{Predehl2020} for modeling the eROSITA bubbles\
+ the two spherical objects of a radius 6-7 kpc proposed by \citet{Predehl2020}\
+ for modeling the eROSITA bubbles\
  based on X-ray emissions.
@@
  The most interesting finding is that there are innermost bubbles\
- (dashed box in left top panel of \Cref{fig__jetI5+ismSeed3-45deg})\
+ (dashed box in the top panel of \Cref{fig__jetI5+ismSeed3-45deg-a})\
  extending out from the GC on either side of the thin disk.\
@@
 
- \Cref{fig__jetI5+ismSeed3-45deg} shows the slices of various gas properties at $t=12.39$ Myr,
- including pressure (top), temperature (middle), density (bottom) with the same jet source as the fiducial run\
+ \Cref{fig__jetI5+ismSeed3-45deg} shows the slices of various gas properties at $t=12.39$ Myr,\
+ including pressure (top), temperature (middle),\
+ density (bottom) with the same jet source as the fiducial run\
  but in different Galactic environments.
@@
  %To explore how the disk affects the formation of the Galactic bubbles,\
- We compare the fiducial run (a1-a3)\
- with the case adopting the smooth disc\
- (b1-b3), specified by the initial density profile shown in
- \Cref{fig__initial-density-profile}, in a stratified atmosphere.\
- The results show that the initial density distribution of the dense disc has an insignificant effect\
+ We compare the clumpy disk (\Cref{fig__jetI5+ismSeed3-45deg-a})\
+ with the smooth disc (\Cref{fig__jetI5+ismSeed3-45deg-b}),\
+ specified by the initial density profile shown in \Cref{fig__initial-density-profile},\
+ in a stratified atmosphere.\
+ The results show that the initial density distribution of\
+ the dense disc has an insignificant effect\
  on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
- in an uniform atmosphere (c1-c3) is spherical-shape,\
+ in an uniform atmosphere (\Cref{fig__jetI5+ismSeed3-45deg-c}) is spherical-shape,\
  suggesting the stratification facilitates the outermost bubbles elongation significantly.\
- Also, the two rightmost columns reveal that the development of the innermost bubbles\
+ Also, \Cref{fig__jetI5+ismSeed3-45deg-c,fig__jetI5+ismSeed3-45deg-d}\
+ reveal that the development of the innermost bubbles\
  is always associated with the disc, without the disc,\
@@
  the symmetry of the Galactic bubbles and for the innermost bubbles formation.
-
-  \begin{figure}
-    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg.png}
-    \caption{
-             The slices of pressure (top), temperature (middle), and number density (bottom)\
-             at the end of simulation $t=12.39$ Myr.\
-             The slices pass through a bipolar jet source injecting along $z=-y$ direction\
-             for a duration $t=0$--$1.2$ Myr.\
-             Comparison between the clumpy (a1-a3)\
-             and the smooth disc (b1-b3) in a stratified atmosphere\
-             shows that the initial density distribution of the dense disc has an insignificant effect\
-             on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
-             in an uniform atmosphere (c1-c3) is spherical-shape,\
-             suggesting the stratification facilitates the outermost bubbles elongation significantly.\
-             Also, the two rightmost columns reveal that the development of the innermost bubbles\
-             is always associated with the disc, without the disc (d1-d3),\
-             the outermost bubbles and the turbulent plasma will be oblique,
-             indicating the dense disc is crucial for\
-             the symmetry of the Galactic bubbles and for the innermost bubbles formation.
-             }
-    \label{fig__jetI5+ismSeed3-45deg}
-  \end{figure}
 
@@
       \includegraphics[height=10.1cm]{figures/fig__jetI5+ismSeed3-45deg-a}%
-      \label{fig__jetI5+ismSeed3-45deg-a}% A
+      \label{fig__jetI5+ismSeed3-45deg-a}%
     }%
@@
     {%
-      \includegraphics[height=10.1cm]{figures/fig__jetI5+ismSeed3-45deg-d}
-      \label{fig__jetI5+ismSeed3-45deg-d} %D
+      \includegraphics[height=10.1cm]{figures/fig__jetI5+ismSeed3-45deg-d}%
+      \label{fig__jetI5+ismSeed3-45deg-d}%
     }%
-  \caption{}%
+  \caption{
+             The slices of pressure (top), temperature (middle), and number density (bottom)\
+             at the end of simulation $t=12.39$ Myr.\
+             The slices pass through a bipolar jet source injecting along $z=-y$ direction\
+             for a duration $t=0$--$1.2$ Myr.\
+             Comparison between the clumpy (column a)\
+             and the smooth disc (column b) in a stratified atmosphere\
+             shows that the initial density distribution of the dense disc has an insignificant effect\
+             on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
+             in an uniform atmosphere (column c) is spherical-shape,\
+             suggesting the stratification facilitates the outermost bubbles elongation significantly.\
+             Also, the two rightmost columns reveal that the development of the innermost bubbles\
+             is always associated with the disc, without the disc (column d),\
+             the outermost bubbles and the turbulent plasma will be oblique,
+             indicating the dense disc is crucial for\
+             the symmetry of the Galactic bubbles and for the innermost bubbles formation.
+  }%
   \label{fig__jetI5+ismSeed3-45deg}%
@@
 
-  \begin{figure}
-    \includegraphics[width=\columnwidth]{figures/fig__profile.png}
+\begin{figure}%
+  \centering%
+  \subfigure[][]%
+    {%
+      \includegraphics[height=7cm]{figures/fig__profile-1.png}%
+      \label{fig__profile-1}%
+    }%
+  \hspace{2pt}%
+  \subfigure[][]%
+    {%
+      \includegraphics[height=7cm]{figures/fig__profile-2.png}%
+      \label{fig__profile-2}%
+    }%
     \caption{
@@
              indicates that the innermost bubbles\
-             (dashed box in top left panel of \Cref{fig__jetI5+ismSeed3-45deg})\
+             (dashed box in the top panel in \Cref{fig__jetI5+ismSeed3-45deg-a})\
              are an expanding reverse shock.
@@
 
-  \begin{figure*}
-    \subfigure[Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
+  \begin{figure*}[]
+    \subfigure[(A) Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
                (photons s$^{-1}$ deg$^{-2}$) in the 0.6--1.0 keV range.\
@@
      }
-    \subfigure[Comparison of simulated (red) and observed (black; \citealt{Predehl2020}) one-dimensional\
+    \subfigure[(B) Comparison of simulated (red) and observed (black; \citealt{Predehl2020}) one-dimensional\
                count rate profiles in the same energy band as \Cref{fig__xray_0.8keV_angle_000},\

### 2022-03-13 mnras_guide.tex
update

% mnras_guide.tex
%
% MNRAS LaTeX user guide
%
% v3.1 released 11 June 2020
%
% v3.0 released 22 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0   September 2013 - May 2015
%    First version: complete rewrite of the user guide
%    Basic structure taken from mnras_template.tex by the same author

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[fleqn,usenatbib,useAMS]{mnras}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
\usepackage{pdflscape}	% Landscape pages
\usepackage{orcidlink}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
\newcommand{\kms}{\,km\,s$^{-1}$} % kilometres per second
\newcommand{\bibtex}{\textsc{Bib}\!\TeX} % bibtex. Not quite the correct typesetting, but close enough
%\newcommand{\orcid}[1]{\href{https://orcid.org/#1}{\textcolor[HTML]{A6CE39}{\aiOrcid}}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[]{The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[P. H. Tseng et al.]{\large
Po-Hsun Tseng$^{1}$%
\thanks{\href{mailto:zengbs@gmail.com}{zengbs@gmail.com}}%
\orcidlink{https://orcid.org/0000-0002-1868-0660}%
\quad H.-Y. Karen Yang$^{2,3,4}$%
\thanks{\href{mailto:hyang@phys.nthu.edu.tw}{hyang@phys.nthu.edu.tw}}%
\orcidlink{https://orcid.org/0000-0003-3269-4660}%
\quad Hsi-Yu Schive$^{1,5,6,4}$%
\thanks{\href{mailto:hyschive@phys.ntu.edu.tw}{hyschive@phys.ntu.edu.tw}}%
\orcidlink{https://orcid.org/0000-0002-1249-279X}%
\quad Chun-Yen Chen$^{7}$
\quad Tzihong Chiueh$^{1,5,6}$%
\thanks{\href{mailto:chiuehth@phys.ntu.edu.tw}{chiuehth@phys.ntu.edu.tw}}%
\orcidlink{https://orcid.org/0000-0003-2654-8763}%
\\\\%
$^{1}$Institute of Astrophysics, National Taiwan University, Taipei 10617, Taiwan\\
$^{2}$Institute of Astronomy, National Tsing Hua University, Hsinchu 30013, Taiwan\\
$^{3}$Center for Informatics and Computation in Astronomy, National Tsing Hua University, Hsinchu 30013, Taiwan\\
$^{4}$Physics Division, National Center for Theoretical Sciences, Taipei 10617, Taiwan\\
$^{5}$Department of Physics, National Taiwan University, Taipei 10617, Taiwan\\
$^{6}$Center for Theoretical Physics, National Taiwan University, Taipei 10617, Taiwan\\
$^{7}$Institute of physics, National Taiwan University, Taipei 10617, Taiwan\\
}

% These dates will be filled out by the publisher
\date{Last updated 2020 June 10; in original form 2013 September 5}

% Enter the current year, for the copyright statements etc.
\pubyear{2020}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
This is a guide for preparing papers for \textit{Monthly Notices of the Royal Astronomical Society} using the \verb'mnras' \LaTeX\ package.
It provides instructions for using the additional features in the document class.
This is not a general guide on how to use \LaTeX, and nor does it replace the journal's instructions to authors.
See \texttt{mnras\_template.tex} for a simple template.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
editorials, notices -- miscellaneous
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

% The MNRAS class isn't designed to include a table of contents, but for this document one is useful.
% I therefore have to do some kludging to make it work without masses of blank space.
\begingroup
\let\clearpage\relax
\tableofcontents
\endgroup
\newpage

\section{Introduction}

The journal \textit{Monthly Notices of the Royal Astronomical Society} (MNRAS) encourages authors to prepare their papers using \LaTeX.
The style file \verb'mnras.cls' can be used to approximate the final appearance of the journal, and provides numerous features to simplify the preparation of papers.
This document, \verb'mnras_guide.tex', provides guidance on using that style file and the features it enables.

This is not a general guide on how to use \LaTeX, of which many excellent examples already exist.
We particularly recommend \textit{Wikibooks \LaTeX}\footnote{\url{https://en.wikibooks.org/wiki/LaTeX}}, a collaborative online textbook which is of use to both beginners and experts.
Alternatively there are several other online resources, and most academic libraries also hold suitable beginner's guides.

For guidance on the contents of papers, journal style, and how to submit a paper, see the MNRAS Instructions to Authors\footnote{\label{foot:itas}\url{http://www.oxfordjournals.org/our_journals/mnras/for_authors/}}.
Only technical issues with the \LaTeX\ class are considered here.

\section{Obtaining and installing the MNRAS package}
Some \LaTeX\ distributions come with the MNRAS package by default.
If yours does not, you can either install it using your distribution's package manager, or download it from the Comprehensive \TeX\ Archive Network\footnote{\url{http://www.ctan.org/tex-archive/macros/latex/contrib/mnras}} (CTAN).

The files can either be installed permanently by placing them in the appropriate directory (consult the documentation for your \LaTeX\ distribution), or used temporarily by placing them in the working directory for your paper.

To use the MNRAS package, simply specify \verb'mnras' as the document class at the start of a \verb'.tex' file:

\begin{verbatim}
\documentclass{mnras}
\end{verbatim}
Then compile \LaTeX\ (and if necessary \bibtex) in the usual way.

\section{Preparing and submitting a paper}
We recommend that you start with a copy of the \texttt{mnras\_template.tex} file.
Rename the file, update the information on the title page, and then work on the text of your paper.
Guidelines for content, style etc. are given in the instructions to authors on the journal's website$^{\ref{foot:itas}}$.
Note that this document does not follow all the aspects of MNRAS journal style (e.g. it has a table of contents).

If a paper is accepted, it is professionally typeset and copyedited by the publishers.
It is therefore likely that minor changes to presentation will occur.
For this reason, we ask authors to ignore minor details such as slightly long lines, extra blank spaces, or misplaced figures, because these details will be dealt with during the production process.

Papers must be submitted electronically via the online submission system; paper submissions are not permitted.
For full guidance on how to submit a paper, see the instructions to authors.

\section{Class options}
\label{sec:options}
There are several options which can be added to the document class line like this:

\begin{verbatim}
\documentclass[option1,option2]{mnras}
\end{verbatim}
The available options are:
\begin{itemize}
\item \verb'letters' -- used for papers in the journal's Letters section.
\item \verb'onecolumn' -- single column, instead of the default two columns. This should be used {\it only} if necessary for the display of numerous very long equations.
\item \verb'doublespacing' -- text has double line spacing. Please don't submit papers in this format.
\item \verb'referee' -- \textit{(deprecated)} single column, double spaced, larger text, bigger margins. Please don't submit papers in this format.
\item \verb'galley' -- \textit{(deprecated)} no running headers, no attempt to align the bottom of columns.
\item \verb'landscape' -- \textit{(deprecated)} sets the whole document on landscape paper.
\item \verb"usenatbib" -- \textit{(all papers should use this)} this uses Patrick Daly's \verb"natbib.sty" package for citations.
\item \verb"usegraphicx" -- \textit{(most papers will need this)} includes the \verb'graphicx' package, for inclusion of figures and images.
\item \verb'useAMS' -- adds support for upright Greek characters \verb'\upi', \verb'\umu' and \verb'\upartial' ($\upi$, $\umu$ and $\upartial$). Only these three are included, if you require other symbols you will need to include the \verb'amsmath' or \verb'amsymb' packages (see section~\ref{sec:packages}).
\item \verb"usedcolumn" -- includes the package \verb"dcolumn", which includes two new types of column alignment for use in tables.
\end{itemize}

Some of these options are deprecated and retained for backwards compatibility only.
Others are used in almost all papers, but again are retained as options to ensure that papers written decades ago will continue to compile without problems.
If you want to include any other packages, see section~\ref{sec:packages}.

\section{Title page}

If you are using \texttt{mnras\_template.tex} the necessary code for generating the title page, headers and footers is already present.
Simply edit the title, author list, institutions, abstract and keywords as described below.

\subsection{Title}
There are two forms of the title: the full version used on the first page, and a short version which is used in the header of other odd-numbered pages (the `running head').
Enter them with \verb'\title[]{}' like this:
\begin{verbatim}
\title[Running head]{Full title of the paper}
\end{verbatim}
The full title can be multiple lines (use \verb'\\' to start a new line) and may be as long as necessary, although we encourage authors to use concise titles. The running head must be $\le~45$ characters on a single line.

See appendix~\ref{sec:advanced} for more complicated examples.

\subsection{Authors and institutions}

Like the title, there are two forms of author list: the full version which appears on the title page, and a short form which appears in the header of the even-numbered pages. Enter them using the \verb'\author[]{}' command.

If the author list is more than one line long, start a new line using \verb'\newauthor'. Use \verb'\\' to start the institution list. Affiliations for each author should be indicated with a superscript number, and correspond to the list of institutions below the author list.

For example, if I were to write a paper with two coauthors at another institution, one of whom also works at a third location:
\begin{verbatim}
\author[K. T. Smith et al.]{
Keith T. Smith,$^{1}$
A. N. Other,$^{2}$
and Third Author$^{2,3}$
\\
$^{1}$Affiliation 1\\
$^{2}$Affiliation 2\\
$^{3}$Affiliation 3}
\end{verbatim}
Affiliations should be in the format `Department, Institution, Street Address, City and Postal Code, Country'.

Email addresses can be inserted with the \verb'\thanks{}' command which adds a title page footnote.
If you want to list more than one email, put them all in the same \verb'\thanks' and use \verb'\footnotemark[]' to refer to the same footnote multiple times.
Present addresses (if different to those where the work was performed) can also be added with a \verb'\thanks' command.

\subsection{Abstract and keywords}

The abstract is entered in an \verb'abstract' environment:
\begin{verbatim}
\begin{abstract}
The abstract of the paper.
\end{abstract}
\end{verbatim}
\noindent Note that there is a word limit on the length of abstracts.
For the current word limit, see the journal instructions to authors$^{\ref{foot:itas}}$.

Immediately following the abstract, a set of keywords is entered in a \verb'keywords' environment:
\begin{verbatim}
\begin{keywords}
keyword 1 -- keyword 2 -- keyword 3
\end{keywords}
\end{verbatim}
\noindent There is a list of permitted keywords, which is agreed between all the major astronomy journals and revised every few years.
Do \emph{not} make up new keywords!
For the current list of allowed keywords, see the journal's instructions to authors$^{\ref{foot:itas}}$.

\section{Sections and lists}

Sections and lists are generally the same as in the standard \LaTeX\ classes.

\subsection{Sections}
\label{sec:sections}
Sections are entered in the usual way, using \verb'\section{}' and its variants. It is possible to nest up to four section levels:
\begin{verbatim}
\section{Main section}
 \subsection{Subsection}
  \subsubsection{Subsubsection}
   \paragraph{Lowest level section}
\end{verbatim}
\noindent The other \LaTeX\ sectioning commands \verb'\part', \verb'\chapter' and \verb'\subparagraph{}' are deprecated and should not be used.

Some sections are not numbered as part of journal style (e.g. the Acknowledgements).
To insert an unnumbered section use the `starred' version of the command: \verb'\section*{}'.

See appendix~\ref{sec:advanced} for more complicated examples.

\subsection{Lists}

Two forms of lists can be used in MNRAS -- numbered and unnumbered.

For a numbered list, use the \verb'enumerate' environment:
\begin{verbatim}
\begin{enumerate}
 \item First item
 \item Second item
 \item etc.
\end{enumerate}
\end{verbatim}
\noindent which produces
\begin{enumerate}
 \item First item
 \item Second item
 \item etc.
\end{enumerate}
Note that the list uses lowercase Roman numerals, rather than the \LaTeX\ default Arabic numerals.

For an unnumbered list, use the \verb'description' environment without the optional argument:
\begin{verbatim}
\begin{description}
 \item First item
 \item Second item
 \item etc.
\end{description}
\end{verbatim}
\noindent which produces
\begin{description}
 \item First item
 \item Second item
 \item etc.
\end{description}

Bulleted lists using the \verb'itemize' environment should not be used in MNRAS; it is retained for backwards compatibility only.

\section{Mathematics and symbols}

The MNRAS class mostly adopts standard \LaTeX\ handling of mathematics, which is briefly summarised here.
See also section~\ref{sec:packages} for packages that support more advanced mathematics.

Mathematics can be inserted into the running text using the syntax \verb'$1+1=2$', which produces $1+1=2$.
Use this only for short expressions or when referring to mathematical quantities; equations should be entered as described below.

\subsection{Equations}
Equations should be entered using the \verb'equation' environment, which automatically numbers them:

\begin{verbatim}
\begin{equation}
 a^2=b^2+c^2
\end{equation}
\end{verbatim}
\noindent which produces
\begin{equation}
 a^2=b^2+c^2
\end{equation}

By default, the equations are numbered sequentially throughout the whole paper. If a paper has a large number of equations, it may be better to number them by section (2.1, 2.2 etc.). To do this, add the command \verb'\numberwithin{equation}{section}' to the preamble.

It is also possible to produce un-numbered equations by using the \LaTeX\ built-in \verb'\['\textellipsis\verb'\]' and \verb'$$'\textellipsis\verb'$$' commands; however MNRAS requires that all equations are numbered, so these commands should be avoided.

\subsection{Special symbols}

\begin{table}
 \caption{Additional commands for special symbols commonly used in astronomy. These can be used anywhere.}
 \label{tab:anysymbols}
 \begin{tabular*}{\columnwidth}{@{}l@{\hspace*{50pt}}l@{\hspace*{50pt}}l@{}}
  \hline
  Command & Output & Meaning\\
  \hline
  \verb'\sun' & \sun & Sun, solar\\[2pt] % additional height spacing for enhanced symbol legibility
  \verb'\earth' & \earth & Earth, terrestrial\\[2pt]
  \verb'\micron' & \micron & microns\\[2pt]
  \verb'\degr' & \degr & degrees\\[2pt]
  \verb'\arcmin' & \arcmin & arcminutes\\[2pt]
  \verb'\arcsec' & \arcsec & arcseconds\\[2pt]
  \verb'\fdg' & \fdg & fraction of a degree\\[2pt]
  \verb'\farcm' & \farcm & fraction of an arcminute\\[2pt]
  \verb'\farcs' & \farcs & fraction of an arcsecond\\[2pt]
  \verb'\fd' & \fd & fraction of a day\\[2pt]
  \verb'\fh' & \fh & fraction of an hour\\[2pt]
  \verb'\fm' & \fm & fraction of a minute\\[2pt]
  \verb'\fs' & \fs & fraction of a second\\[2pt]
  \verb'\fp' & \fp & fraction of a period\\[2pt]
  \verb'\diameter' & \diameter & diameter\\[2pt]
  \verb'\sq' & \sq & square, Q.E.D.\\[2pt]
  \hline
 \end{tabular*}
\end{table}

\begin{table}
 \caption{Additional commands for mathematical symbols. These can only be used in maths mode.}
 \label{tab:mathssymbols}
 \begin{tabular*}{\columnwidth}{l@{\hspace*{40pt}}l@{\hspace*{40pt}}l}
  \hline
  Command & Output & Meaning\\
  \hline
  \verb'\upi' & $\upi$ & upright pi\\[2pt] % additional height spacing for enhanced symbol legibility
  \verb'\umu' & $\umu$ & upright mu\\[2pt]
  \verb'\upartial' & $\upartial$ & upright partial derivative\\[2pt]
  \verb'\lid' & $\lid$ & less than or equal to\\[2pt]
  \verb'\gid' & $\gid$ & greater than or equal to\\[2pt]
  \verb'\la' & $\la$ & less than of order\\[2pt]
  \verb'\ga' & $\ga$ & greater than of order\\[2pt]
  \verb'\loa' & $\loa$ & less than approximately\\[2pt]
  \verb'\goa' & $\goa$ & greater than approximately\\[2pt]
  \verb'\cor' & $\cor$ & corresponds to\\[2pt]
  \verb'\sol' & $\sol$ & similar to or less than\\[2pt]
  \verb'\sog' & $\sog$ & similar to or greater than\\[2pt]
  \verb'\lse' & $\lse$ & less than or homotopic to \\[2pt]
  \verb'\gse' & $\gse$ & greater than or homotopic to\\[2pt]
  \verb'\getsto' & $\getsto$ & from over to\\[2pt]
  \verb'\grole' & $\grole$ & greater over less\\[2pt]
  \verb'\leogr' & $\leogr$ & less over greater\\
  \hline
 \end{tabular*}
\end{table}

Some additional symbols of common use in astronomy have been added in the MNRAS class. These are shown in tables~\ref{tab:anysymbols}--\ref{tab:mathssymbols}. The command names are -- as far as possible -- the same as those used in other major astronomy journals.

Many other mathematical symbols are also available, either built into \LaTeX\ or via additional packages. If you want to insert a specific symbol but don't know the \LaTeX\ command, we recommend using the Detexify website\footnote{\url{http://detexify.kirelabs.org}}.

Sometimes font or coding limitations mean a symbol may not get smaller when used in sub- or superscripts, and will therefore be displayed at the wrong size. There is no need to worry about this as it will be corrected by the typesetter during production.

To produce bold symbols in mathematics, use \verb'\bmath' for simple variables, and the \verb'bm' package for more complex symbols (see section~\ref{sec:packages}). Vectors are set in bold italic, using \verb'\mathbfit{}'.

For matrices, use \verb'\mathbfss{}' to produce a bold sans-serif font e.g. \mathbfss{H}; this works even outside maths mode, but not all symbols are available (e.g. Greek). For $\nabla$ (del, used in gradients, divergence etc.) use \verb'$\nabla$'.

\subsection{Ions}

A new \verb'\ion{}{}' command has been added to the class file, for the correct typesetting of ionisation states.
For example, to typeset singly ionised calcium use \verb'\ion{Ca}{ii}', which produces \ion{Ca}{ii}.

\section{Figures and tables}
\label{sec:fig_table}
Figures and tables (collectively called `floats') are mostly the same as built into \LaTeX.

\subsection{Basic examples}
%\begin{figure}
% \includegraphics[width=\columnwidth]{example}
% \caption{An example figure.}
% \label{fig:example}
%\end{figure}
Figures are inserted in the usual way using a \verb'figure' environment and \verb'\includegraphics'. The example Figure~\ref{fig:example} was generated using the code:
\begin{verbatim}
\begin{figure}
 \includegraphics[width=\columnwidth]{example}
 \caption{An example figure.}
 \label{fig:example}
\end{figure}
\end{verbatim}

\begin{table}
 \caption{An example table.}
 \label{tab:example}
 \begin{tabular}{lcc}
  \hline
  Star & Mass & Luminosity\\
   & $M_{\sun}$ & $L_{\sun}$\\
  \hline
  Sun & 1.00 & 1.00\\
  $\alpha$~Cen~A & 1.10 & 1.52\\
  $\epsilon$~Eri & 0.82 & 0.34\\
  \hline
 \end{tabular}
\end{table}
The example Table~\ref{tab:example} was generated using the code:
\begin{verbatim}
\begin{table}
 \caption{An example table.}
 \label{tab:example}
 \begin{tabular}{lcc}
  \hline
  Star & Mass & Luminosity\\
   & $M_{\sun}$ & $L_{\sun}$\\
  \hline
  Sun & 1.00 & 1.00\\
  $\alpha$~Cen~A & 1.10 & 1.52\\
  $\epsilon$~Eri & 0.82 & 0.34\\
  \hline
 \end{tabular}
\end{table}
\end{verbatim}

\subsection{Captions and placement}
Captions go \emph{above} tables but \emph{below} figures, as in the examples above.

The \LaTeX\ float placement commands \verb'[htbp]' are intentionally disabled.
Layout of figures and tables will be adjusted by the publisher during the production process, so authors should not concern themselves with placement to avoid disappointment and wasted effort.
Simply place the \LaTeX\ code close to where the figure or table is first mentioned in the text and leave exact placement to the publishers.

By default a figure or table will occupy one column of the page.
To produce a wider version which covers both columns, use the \verb'figure*' or \verb'table*'  environment.

If a figure or table is too long to fit on a single page it can be split it into several parts.
Create an additional figure or table which uses \verb'\contcaption{}' instead of \verb'\caption{}'.
This will automatically correct the numbering and add `\emph{continued}' at the start of the caption.
\begin{table}
 \contcaption{A table continued from the previous one.}
 \label{tab:continued}
 \begin{tabular}{lcc}
  \hline
  Star & Mass & Luminosity\\
   & $M_{\sun}$ & $L_{\sun}$\\
  \hline
  $\tau$~Cet & 0.78 & 0.52\\
  $\delta$~Pav & 0.99 & 1.22\\
  $\sigma$~Dra & 0.87 & 0.43\\
  \hline
 \end{tabular}
\end{table}
Table~\ref{tab:continued} was generated using the code:

\begin{verbatim}
\begin{table}
 \contcaption{A table continued from the previous one.}
 \label{tab:continued}
 \begin{tabular}{lcc}
  \hline
  Star & Mass & Luminosity\\
   & $M_{\sun}$ & $L_{\sun}$\\
  \hline
  $\tau$~Cet & 0.78 & 0.52\\
  $\delta$~Pav & 0.99 & 1.22\\
  $\sigma$~Dra & 0.87 & 0.43\\
  \hline
 \end{tabular}
\end{table}
\end{verbatim}

To produce a landscape figure or table, use the \verb'pdflscape' package and the \verb'landscape' environment.
The landscape Table~\ref{tab:landscape} was produced using the code:
\begin{verbatim}
\begin{landscape}
 \begin{table}
  \caption{An example landscape table.}
  \label{tab:landscape}
  \begin{tabular}{cccccccccc}
    \hline
    Header & Header & ...\\
    Unit & Unit & ...\\
    \hline
    Data & Data & ...\\
    Data & Data & ...\\
    ...\\
    \hline
  \end{tabular}
 \end{table}
\end{landscape}
\end{verbatim}
Unfortunately this method will force a page break before the table appears.
More complicated solutions are possible, but authors shouldn't worry about this.

\begin{landscape}
 \begin{table}
  \caption{An example landscape table.}
  \label{tab:landscape}
  \begin{tabular}{cccccccccc}
    \hline
    Header & Header & Header & Header & Header & Header & Header & Header & Header & Header\\
    Unit & Unit & Unit & Unit & Unit & Unit & Unit & Unit & Unit & Unit \\
    \hline
    Data & Data & Data & Data & Data & Data & Data & Data & Data & Data\\
    Data & Data & Data & Data & Data & Data & Data & Data & Data & Data\\
    Data & Data & Data & Data & Data & Data & Data & Data & Data & Data\\
    Data & Data & Data & Data & Data & Data & Data & Data & Data & Data\\
    Data & Data & Data & Data & Data & Data & Data & Data & Data & Data\\
    Data & Data & Data & Data & Data & Data & Data & Data & Data & Data\\
    Data & Data & Data & Data & Data & Data & Data & Data & Data & Data\\
    Data & Data & Data & Data & Data & Data & Data & Data & Data & Data\\
    \hline
  \end{tabular}
 \end{table}
\end{landscape}

\section{References and citations}

\subsection{Cross-referencing}

The usual \LaTeX\ commands \verb'\label{}' and \verb'\ref{}' can be used for cross-referencing within the same paper.
We recommend that you use these whenever relevant, rather than writing out the section or figure numbers explicitly.
This ensures that cross-references are updated whenever the numbering changes (e.g. during revision) and provides clickable links (if available in your compiler).

It is best to give each section, figure and table a logical label.
For example, Table~\ref{tab:mathssymbols} has the label \verb'tab:mathssymbols', whilst section~\ref{sec:packages} has the label \verb'sec:packages'.
Add the label \emph{after} the section or caption command, as in the examples in sections~\ref{sec:sections} and \ref{sec:fig_table}.
Enter the cross-reference with a non-breaking space between the type of object and the number, like this: \verb'see Figure~\ref{fig:example}'.

The \verb'\autoref{}' command can be used to automatically fill out the type of object, saving on typing.
It also causes the link to cover the whole phrase rather than just the number, but for that reason is only suitable for single cross-references rather than ranges.
For example, \verb'\autoref{tab:journal_abbr}' produces \autoref{tab:journal_abbr}.

\subsection{Citations}
\label{sec:cite}

MNRAS uses the Harvard -- author (year) -- citation style, e.g. \citet{author2013}.
This is implemented in \LaTeX\ via the \verb'natbib' package, which in turn is included via the \verb'usenatbib' package option (see section~\ref{sec:options}), which should be used in all papers.

Each entry in the reference list has a `key' (see section~\ref{sec:ref_list}) which is used to generate citations.
There are two basic \verb'natbib' commands:
\begin{description}
 \item \verb'\citet{key}' produces an in-text citation: \citet{author2013}
 \item \verb'\citep{key}' produces a bracketed (parenthetical) citation: \citep{author2013}
\end{description}
Citations will include clickable links to the relevant entry in the reference list, if supported by your \LaTeX\ compiler.

\defcitealias{smith2014}{Paper~I}
\begin{table*}
 \caption{Common citation commands, provided by the \texttt{natbib} package.}
 \label{tab:natbib}
 \begin{tabular}{lll}
  \hline
  Command & Ouput & Note\\
  \hline
  \verb'\citet{key}' & \citet{smith2014} & \\
  \verb'\citep{key}' & \citep{smith2014} & \\
  \verb'\citep{key,key2}' & \citep{smith2014,jones2015} & Multiple papers\\
  \verb'\citet[table 4]{key}' & \citet[table 4]{smith2014} & \\
  \verb'\citep[see][figure 7]{key}' & \citep[see][figure 7]{smith2014} & \\
  \verb'\citealt{key}' & \citealt{smith2014} & For use with manual brackets\\
  \verb'\citeauthor{key}' & \citeauthor{smith2014} & If already cited in close proximity\\
  \verb'\defcitealias{key}{Paper~I}' &  & Define an alias (doesn't work in floats)\\
  \verb'\citetalias{key}' & \citetalias{smith2014} & \\
  \verb'\citepalias{key}' & \citepalias{smith2014} & \\
  \hline
 \end{tabular}
\end{table*}

There are a number of other \verb'natbib' commands which can be used for more complicated citations.
The most commonly used ones are listed in Table~\ref{tab:natbib}.
For full guidance on their use, consult the \verb'natbib' documentation\footnote{\url{http://www.ctan.org/pkg/natbib}}.

If a reference has several authors, \verb'natbib' will automatically use `et al.' if there are more than two authors. However, if a paper has exactly three authors, MNRAS style is to list all three on the first citation and use `et al.' thereafter. If you are using \bibtex\ (see section~\ref{sec:ref_list}) then this is handled automatically. If not, the \verb'\citet*{}' and \verb'\citep*{}' commands can be used at the first citation to include all of the authors.

\subsection{The list of references}
\label{sec:ref_list}

It is possible to enter references manually using the usual \LaTeX\ commands, but we strongly encourage authors to use \bibtex\ instead.
\bibtex\ ensures that the reference list is updated automatically as references are added or removed from the paper, puts them in the correct format, saves on typing, and the same reference file can be used for many different papers -- saving time hunting down reference details.
An MNRAS \bibtex\ style file, \verb'mnras.bst', is distributed as part of this package.
The rest of this section will assume you are using \bibtex.

References are entered into a separate \verb'.bib' file in standard \bibtex\ formatting.
This can be done manually, or there are several software packages which make editing the \verb'.bib' file much easier.
We particularly recommend \textsc{JabRef}\footnote{\url{http://jabref.sourceforge.net/}}, which works on all major operating systems.
\bibtex\ entries can be obtained from the NASA Astrophysics Data System\footnote{\label{foot:ads}\url{http://adsabs.harvard.edu}} (ADS) by clicking on `Bibtex entry for this abstract' on any entry.
Simply copy this into your \verb'.bib' file or into the `BibTeX source' tab in \textsc{JabRef}.

Each entry in the \verb'.bib' file must specify a unique `key' to identify the paper, the format of which is up to the author.
Simply cite it in the usual way, as described in section~\ref{sec:cite}, using the specified key.
Compile the paper as usual, but add an extra step to run the \texttt{bibtex} command.
Consult the documentation for your compiler or latex distribution.

Correct formatting of the reference list will be handled by \bibtex\ in almost all cases, provided that the correct information was entered into the \verb'.bib' file.
Note that ADS entries are not always correct, particularly for older papers and conference proceedings, so may need to be edited.
If in doubt, or if you are producing the reference list manually, see the MNRAS instructions to authors$^{\ref{foot:itas}}$ for the current guidelines on how to format the list of references.

\section{Appendices and online material}

To start an appendix, simply place the \verb'\appendix' command before the next \verb'\section{}'.
This will automatically adjust the section headings, figures, tables, and equations to reflect the fact that they are part of an appendix.
It is only necessary to enter the \verb'\appendix' command once -- everything after that command is in an appendix.
Remember that appendices should be placed \textit{after} the list of references.

Unlike other astronomy class files, there are no special commands for online material.
If your paper has any online material, it should be placed in a separate file.
See our instructions to authors$^{\ref{foot:itas}}$ for guidance.

\section{Packages and custom commands}
\label{sec:packages}
\subsection{Additional packages}

Sometimes authors need to include additional \LaTeX\ packages, which provide extra features.
For example, the \verb'bm' package provides extra bold maths symbols, whilst the \verb'pdflscape' package adds support for landscape pages.
Packages can be included by adding the \verb'\usepackage{}' command to the preamble of the document (not the main body).

Please \emph{only include packages which are actually used in the paper}, and include a comment to explain what each one does.
This will assist the typesetters.
If you are using \texttt{mnras\_template.tex}, it includes a specific section for this purpose, near the start of the file with the header 'authors - place your own packages here'.

For example, to include \verb'pdflscape', use:
\begin{verbatim}
\usepackage{pdflscape}	% Landscape pages
\end{verbatim}
Consult the documentation for that package for instructions on how to use the additional features.

\subsection{Custom commands}

Authors should avoid duplicating or redefining commands which are already available in \LaTeX\ or \verb'mnras.cls'.
However it may sometimes be necessary to introduce a custom command e.g. as a shortcut while writing the paper.

Please \emph{only include commands which are actually used in the paper}, and include a comment to explain what each one does.
This will assist the typesetters.
Use \verb'\newcommand', \emph{not} \verb'\def', as this will avoid accidentally overwriting existing commands.
Place custom commands in the preamble of the document (not the main body).
If you are using \texttt{mnras\_template.tex}, it includes a specific section for this purpose, near the start of the file with the header 'authors - place your own commands here'.

As an example, a shortcut for the unit \kms can be defined like this:
\begin{verbatim}
\newcommand{\kms}{\,km\,s$^{-1}$}	% kilometres per second
\end{verbatim}
Velocities can then be written as e.g. \verb'2.3\kms' which produces 2.3\kms.
Similar shortcuts can be used for frequently quoted object designations.

\section*{Acknowledgements}
% Entry for the table of contents, for this guide only
\addcontentsline{toc}{section}{Acknowledgements}

This guide replaces an earlier one originally prepared by Cambridge University Press (CUP) in 1994, and last updated in 2002 by Blackwell Publishing.
Some code segments are reproduced from, and some examples are based upon, that guide.
The authors were: A.~Woollatt, M.~Reed, R.~Mulvey, K.~Matthews, D.~Starling, Y.~Yu, A.~Richardson (all CUP), and Penny~Smith, N.~Thompson and Gregor~Hutton (all Blackwell), whose work is gratefully acknowledged.

The accompanying \bibtex\ style file was written by John Sleath, Tim Jenness and Norman Gray, without whom \bibtex\ support would not have been possible.

Some special symbols in tables~\ref{tab:anysymbols}--\ref{tab:mathssymbols} were taken from the Springer Verlag \textit{Astronomy \& Astrophysics} \LaTeX\ class, with their permission.

KTS thanks Nelson Beebe (University of Utah) for helpful advice regarding CTAN.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Data Availability}

The inclusion of a Data Availability Statement is a requirement for articles published in MNRAS. Data Availability Statements provide a standardised format for readers to understand the availability of data underlying the research results described in the article. The statement may refer to original data generated in the course of the study or to third-party data analysed in the article. The statement should describe and provide means of access, where possible, by linking to the data or providing the required accession numbers for the relevant databases or DOIs.

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:

%\bibliographystyle{mnras}
%\bibliography{example} % if your bibtex file is called example.bib

% Alternatively you could enter them by hand, like this:
\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Author}{2013}]{author2013}
Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
\bibitem[\protect\citeauthoryear{Jones}{2015}]{jones2015}
Jones C.~D., 2015, Journal of Interesting Stuff, 17, 198
\bibitem[\protect\citeauthoryear{Smith}{2014}]{smith2014}
Smith A.~B., 2014, The Example Journal, 12, 345 (Paper I)
\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

\appendix
\section{Journal abbreviations}
\label{sec:abbreviations}
Abbreviations for cited journals can be accessed using the commands listed in table~\ref{tab:journal_abbr}.
Although some of these may appear to be outdated or rarely cited, they have been selected to be compatible with the \bibtex\ output by the NASA Astrophysics Data System$^{\ref{foot:ads}}$, commands used by other astronomy journals, and with additional entries for journals with non-standard abbreviations in MNRAS.
For journals which are not on this list, see our instructions to authors$^{\ref{foot:itas}}$ for guidance on how to abbreviate titles.

\begin{table*}
\caption{Commands for abbreviated journal names, see appendix~\ref{sec:abbreviations}.}
\label{tab:journal_abbr}
\begin{tabular}{@{}l@{\:}l@{\:}l@{}} % manual @ spacing to prevent this being too wide for a page
\hline
Command & Output & Journal name\\
\hline
\verb'\aap' or \verb'\astap' & \aap & Astronomy and Astrophysics$^a$\\
\verb'\aapr' & \aapr & The Astronomy and Astrophysics Review\\
\verb'\aaps' & \aaps  & Astronomy and Astrophysics Supplement Series\\
\verb'\actaa' & \actaa & Acta Astronomica\\
\verb'\afz' & \afz & Astrofizika\\
\verb'\aj' & \aj & The Astronomical Journal\\
\verb'\ao' or \verb'\applopt' & \ao & Applied Optics\\
\verb'\aplett' & \aplett & Astrophysics Letters\\
\verb'\apj' & \apj & The Astrophysical Journal\\
\verb'\apjl' or \verb'\apjlett' & \apjl & The Astrophysical Journal Letters$^a$\\
\verb'\apjs' or \verb'\apjsupp' & \apjs & The Astrophysical Journal Supplement Series\\
\verb'\apss' & \apss & Astrophysics and Space Science\\
\verb'\araa' & \araa & Annual Review of Astronomy and Astrophysics\\
\verb'\arep' & \arep & Astronomy Reports$^b$\\
\verb'\aspc' & \aspc & Astronomical Society of the Pacific Conference Series\\
\verb'\azh' & \azh & Astronomicheskii Zhurnal$^c$\\
\verb'\baas' & \baas & Bulletin of the American Astronomical Society\\
\verb'\bac' & \bac & Bulletin of the Astronomical Institutes of Czechoslovakia\\
\verb'\bain' & \bain & Bull. Astron. Inst. Netherlands\\
\verb'\caa' & \caa & Chinese Astronomy and Astrophysics\\
\verb'\cjaa' & \cjaa & Chinese Journal of Astronomy and Astrophysics\\
\verb'\fcp' & \fcp & Fundamentals of Cosmic Physics\\
\verb'\gca' & \gca & Geochimica Cosmochimica Acta\\
\verb'\grl' & \grl & Geophysics Research Letters\\
\verb'\iaucirc' & \iaucirc & International Astronomical Union Circulars\\
\verb'\icarus' & \icarus & Icarus\\
\verb'\japa' & \japa & Journal of Astrophysics and Astronomy\\
\verb'\jcap' & \jcap & Journal of Cosmology and Astroparticle Physics\\
\verb'\jcp' & \jcp & Journal of Chemical Physics\\
\verb'\jgr' & \jgr & Journal of Geophysics Research\\
\verb'\jqsrt' & \jqsrt & Journal of Quantitiative Spectroscopy and Radiative Transfer\\
\verb'\jrasc' & \jrasc & Journal of the Royal Astronomical Society of Canada\\
\verb'\memras' & \memras & Memoirs of the Royal Astronomical Society\\
\verb'\memsai' & \memsai & Memoire della Societa Astronomica Italiana\\
\verb'\mnassa' & \mnassa & Monthly Notes of the Astronomical Society of Southern Africa\\
\verb'\mnras' & \mnras & Monthly Notices of the Royal Astronomical Society$^a$\\
\verb'\na' & \na & New Astronomy\\
\verb'\nar' & \nar & New Astronomy Review\\
\verb'\nat' & \nat & Nature\\
\verb'\nphysa' & \nphysa & Nuclear Physics A\\
\verb'\pra' & \pra & Physical Review A: Atomic, molecular, and optical physics\\
\verb'\prb' & \prb & Physical Review B: Condensed matter and materials physics\\
\verb'\prc' & \prc & Physical Review C: Nuclear physics\\
\verb'\prd' & \prd & Physical Review D: Particles, fields, gravitation, and cosmology\\
\verb'\pre' & \pre & Physical Review E: Statistical, nonlinear, and soft matter physics\\
\verb'\prl' & \prl & Physical Review Letters\\
\verb'\pasa' & \pasa & Publications of the Astronomical Society of Australia\\
\verb'\pasp' & \pasp & Publications of the Astronomical Society of the Pacific\\
\verb'\pasj' & \pasj & Publications of the Astronomical Society of Japan\\
\verb'\physrep' & \physrep & Physics Reports\\
\verb'\physscr' & \physscr & Physica Scripta\\
\verb'\planss' & \planss & Planetary and Space Science\\
\verb'\procspie' & \procspie & Proceedings of the Society of Photo-Optical Instrumentation Engineers\\
\verb'\rmxaa' & \rmxaa & Revista Mexicana de Astronomia y Astrofisica\\
\verb'\qjras' & \qjras & Quarterly Journal of the Royal Astronomical Society\\
\verb'\sci' & \sci & Science\\
\verb'\skytel' & \skytel & Sky and Telescope\\
\verb'\solphys' & \solphys & Solar Physics\\
\verb'\sovast' & \sovast & Soviet Astronomy$^b$\\
\verb'\ssr' & \ssr & Space Science Reviews\\
\verb'\zap' & \zap & Zeitschrift fuer Astrophysik\\
\hline
\multicolumn{3}{l}{$^a$ Letters are designated by an L at the start of the page number, not in the journal name}\\
\multicolumn{3}{l}{\footnotesize$^b$ In 1992 the English translation of this journal changed its name from Soviet Astronomy to Astronomy Reports}\\
\multicolumn{3}{l}{\footnotesize$^c$ Including the English translation Astronomy Letters}\\
\end{tabular}
\end{table*}

\clearpage % to avoid the long table breaking up the formatting examples
\section{Advanced formatting examples}
\label{sec:advanced}

Sometimes formatting doesn't behave exactly as expected when used in titles or section headings, and must be modified to obtain the correct appearance.
Generally the publishers can fix these problems during the typesetting process after a paper is accepted, but authors may wish to adjust these themselves to minimise the possibility of errors and/or for the benefit of the refereeing process.
Below are some examples of output, followed by the \LaTeX\ code which produces them.

Most mathematics and text formatting works as expected, but some commands might not be the correct size, bold or italic.
If so they can be finessed by hand, as in the bold mathematics here:
\boxit{\huge\bf \textit{Herschel} observations of galaxies at $\bm{\delta > 60\degr}$}
\begin{verbatim}
\title{\textit{Herschel} observations of galaxies at
 $\bm{\delta > 60\degr}$}
\end{verbatim}

Most fonts do not provide bold and italic versions of small capitals, so the \verb'\ion{}{}' command doesn't produce the expected output in headings.
The effect has to be `faked' using font size commands, remembering that the running head is a different style:
\boxit{\huge\bf Abundances in H\,{\Large \textbf{II}} regions}
\begin{verbatim}
\title
[Abundances in H\,{\normalsize \textit{II}} regions]
{Abundances in H\,{\Large \textbf{II}} regions}
\end{verbatim}

Complex mathematics can cause problems with links, so might require adding a less formatted short version of the heading:
\boxit{\bf 2\quad FINDING Mg\,{\sevensize II} ABSORBERS AT $\bm{z > 2}$}
\begin{verbatim}
\section
[Finding Mg II absorbers at z > 2]
{Finding M\lowercase{g}\,{\sevensize II} absorbers
 at $\lowercase{\bm{z > 2}}$}
\end{verbatim}

Using square brackets in headings can cause additional linking problems, which are solved by wrapping them in \{\textellipsis\}:
\boxit{\bf 2.1\quad [C\,{\sevensize II}] 158$\bmath{\umu}$m emission}
\begin{verbatim}
\subsection
[{[C II] 158$\umu$m emission}]
{[C\,{\sevensize II}] 158$\bmath{\umu}$m
 emission}
\end{verbatim}

Use \verb'\text{}' (not \verb'\rm') for non-variables in mathematics, which preserves the formatting of the surrounding text.
For the same reasons, use \verb'\textit{}' for italics (not \verb'\it').
\boxit{\bf 3.1\quad Measuring $\bm{T}_\text{eff}$ from \textit{Gaia} photometry}
\begin{verbatim}
\subsection{Measuring $\bm{T}_\text{eff}$ from
 \textit{Gaia} photometry}
\end{verbatim}

\section{Additional commands for editors only}
The following commands are available for the use of editors and production staff only.
They should not be used (or modified in the template) by authors.

\begin{description}
 \item \verb'\maketitle' inserts the title, authors and institution list in the correct formatting.
 \item \verb'\nokeywords' tidies up the spacing if there are no keywords, but authors should always enter at least one.
 \item \verb'\volume{}' sets the volume number (default is 000)
 \item \verb'\pagerange{}' sets the page range. The standard template generates this automatically, starting from 1.
 \item \verb'\bsp' adds the `This paper has been typeset\textellipsis' comment at the end of the paper.
The command name refers to Blackwell Science Publishing, who were the publishers at the time when MNRAS began accepting \LaTeX\ submissions in 1993.
 \item \verb'\mniiiauth{}' used by the \bibtex\ style to handle MNRAS style for citing papers with three authors. It should not be used manually.
 \item \verb'\eprint{}' used by the \bibtex\ style for citing arXiv eprints.
 \item \verb'\doi{}' used by the \bibtex\ style for citing Digital Object Identifiers.
\end{description}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

% End of mnras_guide.tex

### 2022-03-13 mnras_guide.tex
update

@@
-% mnras_guide.tex
-%
-% MNRAS LaTeX user guide
-%
-% v3.1 released 11 June 2020
-%
-% v3.0 released 22 May 2015
-% (version numbers match those of mnras.cls)
-%
-% Copyright (C) Royal Astronomical Society 2015
-% Authors:
-% Keith T. Smith (Royal Astronomical Society)
-
-% Change log
-%
-% v3.0   September 2013 - May 2015
-%    First version: complete rewrite of the user guide
-%    Basic structure taken from mnras_template.tex by the same author
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Basic setup. Most papers should leave these options alone.
 \documentclass[fleqn,usenatbib,useAMS]{mnras}
-
-%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
-
-% Only include extra packages if you really need them. Common packages are:
+\usepackage{mathtools}
+\usepackage{natbib}
+\bibliographystyle{abbrvnat}
+\setcitestyle{authoryear,open={(},close={)}}
 \usepackage{graphicx}	% Including figure files
@@
 \usepackage{orcidlink}
+\usepackage{cleveref}
+\usepackage{booktabs}
+\usepackage[flushleft]{threeparttable}
+\usepackage{caption}
+\usepackage{subcaption}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%%
-
-% Please keep new commands to a minimum, and use \newcommand not \def to avoid
-% overwriting existing commands. Example:
-%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
 \newcommand{\kms}{\,km\,s$^{-1}$} % kilometres per second
 \newcommand{\bibtex}{\textsc{Bib}\!\TeX} % bibtex. Not quite the correct typesetting, but close enough
-%\newcommand{\orcid}[1]{\href{https://orcid.org/#1}{\textcolor[HTML]{A6CE39}{\aiOrcid}}}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Use vector fonts, so it zooms properly in on-screen viewing software
-% Don't change these lines unless you know what you are doing
-\usepackage[T1]{fontenc}
-\usepackage{ae,aecompl}
-
-% MNRAS is set in Times font. If you don't have this installed (most LaTeX
-% installations will be fine) or prefer the old Computer Modern fonts, comment
-% out the following line
-\usepackage{newtxtext,newtxmath}
-% Depending on your LaTeX fonts installation, you might get better results with one of these:
-%\usepackage{mathptmx}
-%\usepackage{txfonts}
-
+%
+%
 %%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
@@
 % These dates will be filled out by the publisher
-\date{Last updated 2020 June 10; in original form 2013 September 5}
+\date{\today}
 
 % Enter the current year, for the copyright statements etc.
-\pubyear{2020}
+\pubyear{2022}
 
@@
 \begin{abstract}
-This is a guide for preparing papers for \textit{Monthly Notices of the Royal Astronomical Society} using the \verb'mnras' \LaTeX\ package.
-It provides instructions for using the additional features in the document class.
-This is not a general guide on how to use \LaTeX, and nor does it replace the journal's instructions to authors.
-See \texttt{mnras\_template.tex} for a simple template.
+The \textit{Fermi Gamma-Ray Space Telescope} reveals two large bubbles in the Galaxy,\
+which extend nearly symmetrically $\sim50^{\circ}$ on either side of the Galactic center (GC).\
+The recent discovery of giant eROSITA bubbles also shows a symmetrically enhanced X-ray\
+emission from the shells around the eROSITA bubbles.\
+To this end, previous simulation-based works based on active galactic nucleus (AGN) jets model\
+assumed that the jets are vertical to the Galactic disk;\
+however, there is a lack of preferred orientation of jets with respect to the Galactic disk.\
+Using three-dimensional (3D) special relativistic hydrodynamic (SRHD) simulations that\
+include cosmic rays (CRs) and thermal gas, we show that a thin interstellar medium (ISM) disk is a substantial\
+component for the symmetric \textit{Fermi} and eROSITA bubbles (collectively, Galactic bubbles).\
+We also produce simulated gamma-ray and\
+microwave spectra from the inverse Compton (IC) scattering and synchrotron,\
+and compare them with the observed counterparts in order to verify\
+an oblique AGN jets model. We find that\
+(1) The simulated Galactic bubbles are nearly symmetric about the GC albeit\
+the bipolar jets are at an angle $45^{\circ}$ with respect to\
+the rotation axis of the Galatic plane (disc normal hereafter).\
+(2) The edge of the eROSITA bubbles is a forward shock,\
+originally driven by oblique bipolar jets emanating from the GC 12.39 million years ago,\
+and significantly stretched by the stratified atmosphere afterwards.\
+(3) Followed by the forward shock is a\
+hot ($\sim2$ keV), turbulent, and pressure-balanced plasma,\
+which we interpret as the \textit{Fermi} bubbles.\
+Inside the simulated \textit{Fermi} bubbles,\
+there are two additional innermost bubbles we have not detected yet.\
+The innermost bubbles are essentially a reverse shock permanently associated with the disk.\
+(4) According to the microwave and leptonic gamma-ray spectra, the best-fitting\
+CRe power-law index is found to be 2.4.\
+The broad agreement between the simulations and observations\
+, either from the point of view of their morphology or multiwavelength features,\
+has thus released a caveat:\
+the jets shall be vertical to the disc normal.
 \end{abstract}
@@
 \let\clearpage\relax
-\tableofcontents
+%\tableofcontents
 \endgroup
@@
 \section{Introduction}
+The detection of the \textit{Fermi} bubbles \citep{Su2012,Ackermann2014,Narayanan2017},\
+two large bubbles symmetrically extending about 50 degrees above and below the Galactic plane,
+is one of the great discoveries made with \textit{Fermi} Large Area Telescope \citep{Atwood2009}.
 
-The journal \textit{Monthly Notices of the Royal Astronomical Society} (MNRAS) encourages authors to prepare their papers using \LaTeX.
-The style file \verb'mnras.cls' can be used to approximate the final appearance of the journal, and provides numerous features to simplify the preparation of papers.
-This document, \verb'mnras_guide.tex', provides guidance on using that style file and the features it enables.
+The gamma-ray emission of the \textit{Fermi} bubbles is observed in the energy range\
+of 1--100 GeV and has an almost spatially uniform hard\
+spectrum, sharp edges and an approximately flat brightness distribution.\
 
-This is not a general guide on how to use \LaTeX, of which many excellent examples already exist.
-We particularly recommend \textit{Wikibooks \LaTeX}\footnote{\url{https://en.wikibooks.org/wiki/LaTeX}}, a collaborative online textbook which is of use to both beginners and experts.
-Alternatively there are several other online resources, and most academic libraries also hold suitable beginner's guides.
+Over the course of a decade,\
+the first all-sky X-ray survey with high-spatial resolution \citep{Predehl2021}\
+from eROSITA \citep{Predehl2020} also reveals\
+a giant hourglass-shaped structure (eROSITA bubbles hereafter) at the GC,\
+extending about twice as large as the \textit{Fermi} bubbles.\
+The large-scale X-ray structure\
+shows that the intrinsic size of the bubbles is 14 kpc across \citep{Predehl2021},
+and displays morphological symmetry about the Galactic plane as the \textit{Fermi} bubbles.
 
-For guidance on the contents of papers, journal style, and how to submit a paper, see the MNRAS Instructions to Authors\footnote{\label{foot:itas}\url{http://www.oxfordjournals.org/our_journals/mnras/for_authors/}}.
-Only technical issues with the \LaTeX\ class are considered here.
+Their symmetry about the GC suggests that they originate\
+from powerful energy injections from the GC, possibly related to nuclear star formation\
+\citep{PhysRevLett.106.101102,Carretti2013}
+or past AGN activity \citep{Guo2012,Yang2017}.
 
-\section{Obtaining and installing the MNRAS package}
-Some \LaTeX\ distributions come with the MNRAS package by default.
-If yours does not, you can either install it using your distribution's package manager, or download it from the Comprehensive \TeX\ Archive Network\footnote{\url{http://www.ctan.org/tex-archive/macros/latex/contrib/mnras}} (CTAN).
+Early attempts \citep{Sarkar2015,Yang2017,Zhang2020}\
+to model the symmetric Galactic bubbles\
+assumed that the jets are vertical to the Galactic plane. However,\
+observation \citep{Gallimore2006} has proposed that\
+there is a lack of preferred orientation of jets with respect to the disc normal.\
+In contrast, a number of galaxies in which the jets are oblique to the disc normal\
+(e.g. NGC 3079, \citealt{Cecil2001}; NGC 1052, \citealt{Dopita2015}),\
+including galaxies in which the jets lie in the plane of the disc (e.g. IC 5063, \citealt{Morganti2015}).
 
-The files can either be installed permanently by placing them in the appropriate directory (consult the documentation for your \LaTeX\ distribution), or used temporarily by placing them in the working directory for your paper.
+To this end, this work introduces a dense, thin disc of ISM\
+around a jet source to deflects and decelerates the oblique jets,\
+in an attempt to resolve the symmetry problem of the Galactic bubbles.\
 
-To use the MNRAS package, simply specify \verb'mnras' as the document class at the start of a \verb'.tex' file:
+The main purpose of this study is to use 3D\
+special relativistic hydrodynamics simulations\
+involving CR jet injections from the central SMBH in the Galaxy to investigate\
+whether the \textit{oblique} jet scenario is able to produce\
+the \textit{symmetric} Galactic bubbles that are\
+consistent with the observed features, including the shape, the\
+surface brightness, and the spectra of \textit{Fermi} bubbles \citep{Ackermann2014}\
+and of microwave haze \citep{Dobler_2008,PlanckCollaborationIX2013}.
 
-\begin{verbatim}
-\documentclass{mnras}
-\end{verbatim}
-Then compile \LaTeX\ (and if necessary \bibtex) in the usual way.
+This paper is organized as follows.\
+In Section \ref{Methodology}, we describe the numerical techniques and initial conditions employed.\
+In Section \ref{Results}, we first present characteristics of our simulated Galactic bubbles,\
+and then discuss how the disk affects the formation of the bubbles.\
+We directly compare the morphology and profile of simulated eROSITA bubbles with\
+observred X-ray map in Section \ref{X-ray},\
+and also present the simulated and observed multiwavelength spectra of\
+the \textit{Fermi} bubbles in Section \ref{sec:gamma-ray-microwave}.\
+Finally, the summary and implications of our findings are given in Section \ref{Conclusions}.
 
-\section{Preparing and submitting a paper}
-We recommend that you start with a copy of the \texttt{mnras\_template.tex} file.
-Rename the file, update the information on the title page, and then work on the text of your paper.
-Guidelines for content, style etc. are given in the instructions to authors on the journal's website$^{\ref{foot:itas}}$.
-Note that this document does not follow all the aspects of MNRAS journal style (e.g. it has a table of contents).
+\section{Methodology}
+\label{Methodology}
+  We used the GPU-accelerated special relativistic\
+  hydrodynamics AMR code (\textsc{gamer-sr}) developed at the\
+  National Taiwan University\
+  (Schive et al. \citeyear{gamer-1}, \citeyear{gamer-2}; \citeauthor{tseng2021} \citeyear{tseng2021})\
+  to carry out the simulations of the Galactic bubbles by CR and relativistic fluid injections from the GC.
 
-If a paper is accepted, it is professionally typeset and copyedited by the publishers.
-It is therefore likely that minor changes to presentation will occur.
-For this reason, we ask authors to ignore minor details such as slightly long lines, extra blank spaces, or misplaced figures, because these details will be dealt with during the production process.
+  As stressed by \citet{Yang2012}, CR diffusion has an insignificant effect\
+  on the overall morphology of the \textit{Fermi} bubbles,\
+  but only sharpens the edges of the simulated bubbles by the interplay between magnetic fields\
+  and anisotropic CR diffusion with suppressed perpendicular diffusion across the bubble surface.
 
-Papers must be submitted electronically via the online submission system; paper submissions are not permitted.
-For full guidance on how to submit a paper, see the instructions to authors.
+  Moreover, the magnetic fields within the \textit{Fermi} bubbles should be weak due to\
+  adiabatic expansion, and thus the fields has\
+  a little effect on the overall dynamics.
 
-\section{Class options}
-\label{sec:options}
-There are several options which can be added to the document class line like this:
+  For these two reasons,\
+  we have ignored the CR diffusion and the magnetic field throughout\
+  the simulation.\
+  Also, we do not simulate the spectral evolution of the CR\
+  and assume the pressure ratio of CR to gas is much less than 1 so that\
+  the contribution of CR pressure gradient to the momentum of the gas can be ignored.\
+  (we will see that the pressure ratio is around 0.1--0.2 throughtout the bubbles formation)\
+  Over and above, we neglect the cooling and heating processes of CRs,\
+  such as energy losses due to synchrotron and inverse Compton emission,\
+  and CR reacceleration in shocks/turbulences.
 
-\begin{verbatim}
-\documentclass[option1,option2]{mnras}
-\end{verbatim}
-The available options are:
+  In this approach, we treat CRs as a single species without distinction between electrons and protons,\
+  and directly evolve the CR energy density $e_{\text{cr}}$\
+  as a function of \textbf{r} and $t$.\
+  The CRs are advected with the thermal gas, and in return the velocities of gas\
+  can react to the gradients of the CR pressure via the source term\
+  containing spatial divergence of fluid velocities.
+
+  Since the relativistic fluid ejected by the jet source\
+  is quickly stalled off and slowed down by the dense ISM in a short time,\
+  and the relativistic fluid\
+  accounts for a little minority of total mass inside the simulation box,\
+  we still use the Newtonian gravity to attack this problem.
+
+  The governing equations solving the special relativistic ideal fluid\
+  including CR advection, and dynamical coupling between the thermal gas and CRs without CR diffusion\
+  can be written a succinct form as
+
+  \begin{subequations}
+    \label{governing-eq}
+    \begin{align}
+     &\partial_{t} D+\partial_{j} \left(DU^{j}/\gamma\right)=0,\label{D evolution}\\
+     &\partial_{t} M^{i}+\partial_{j} \left(M^{i}U^{j}/\gamma+p_{\text{total}}\delta^{ij}\right)=\
+     -\rho\partial_{i}\Phi,\label{M evolution}\\
+     &\partial_{t} \tilde{E}+\partial_j \left[\left(\tilde{E}+p_{\text{gas}}\right)U^{j}/\gamma\right]=0, \label{E evoltion}\\
+     &\partial_{t} \left(\gamma e_{\text{cr}}\right) + \partial_{j} \left(e_{\text{cr}}U^{j}\right)=\
+     -p_{\text{cr}} \partial_{j} U^{j},\label{E evolution}
+    \end{align}
+  \end{subequations}
+
+  where the five conserved quantities of gas $D$, $M^{i}$, and $\tilde{E}$ are the mass density,\
+  the momentum densities, and the reduced energy density, respectively.\
+  The reduced energy density is defined by subtracting the rest mass energy density of gas\
+  from the total energy density of gas.\
+  $\gamma$ and $U^{j}$ are the temporal and spatial component of four-velocity of gas.\
+  $\rho$ is the gas density in the local rest frame defined by $D/\gamma$.\
+  $p_{\text{gas}}$ is the gas pressure.\
+  $p_{\text{cr}}$ and $e_{\text{cr}}$ are the CR pressure and CR energy density measured in the local rest frame.\
+  $p_{\text{total}}$ is the sum of $p_{\text{gas}}$ and $p_{\text{cr}}$.\
+  Note that we simply replace $p_{\text{total}}$ by $p_{\text{gas}}$ in this paper\
+  as we have assumed $p_{\text{cr}}\ll p_{\text{gas}}$.\
+  $\Phi$ is a gravitational potential.\
+  $c$ is the speed of light, and $\delta^{ij}$ is the Kronecker delta notation.\
+  Throughout this paper, Latin indices run from 1 to 3, except when stated otherwise.\
+
+  The set of \Cref{governing-eq} is closed by using the Taub-Mathews equation of state \citep{Taub,TM_EOS}\
+  that approximates the exact EoS \citep{Synge} for ultra-relativistically\
+  hot gases coexisting with non-relativistically cold gases.
+
+  \textsc{gamer-sr} adopts a new algorithm \citep{tseng2021} to convert between\
+  primitive ($\rho$, $U^{j}$, $p$) and conserved variables ($D$, $M^{j}$, $\tilde{E}$),\
+  significantly reducing numerical error caused by catastrophic cancellations\
+  that commonly occur within the regions with high Mach number flows. e.g., jet-ISM interaction zones.
+
+  \textsc{gamer-sr} also adaptively and locally reduce the min-mod coefficient\
+  \citep{tseng2021} within the failed patch group rarely occurring in the SRHD solver,\
+  new patches allocations, and ghost-zone interpolations.\
+  In this manner, we provide an elegant approach to avoid the use of pressure/density floor,\
+  being unnatural but widely used in almost publicly available codes.\
+
+  \subsection{The Galactic and Disk Models}
+  As a proof-of-concept study, we approximate conventionally axisymmetric stellar potential of Milky Way\
+  by a plane-parallel potential that is symmetric about the mid-plane, or the Galactic plane, $z=0$\
+  in a simulation box size of\
+  $14\times14\times28$ kpc, slightly larger than the size of eROISTA bubbles.
+
+  The plane-parallel potential is fixed throughout our simulations and given by
+  \begin{equation}
+    \Phi_{\text{total}}(z) = \Phi_{\text{bulge}}(z) + \Phi_{\text{halo}}(z),
+  \end{equation}
+  where
+  \begin{equation}
+    \Phi_{\text{bulge}}(z)=\
+    2\sigma^2_{\text{bulge}}\
+    \ln\cosh\left(z\sqrt{\frac{2\pi G\rho_{\text{bulge}}^{\text{peak}}}{\sigma^2_{\text{bulge}}}}\right)
+  \end{equation}
+  is the potential of an isothermal slab mainly contributed by stars around the Galactic bulge, and\
+  $\Phi_{\text{halo}}(z)=v^2_{\text{halo}}\ln\left(z^2+d^2_{\text{h}}\right)$\
+  is a plane-parallel dark logarithmic halo potential.
+
+  With the help of the isothermal and hydrostatic equilibrium conditions,\
+  and assuming the interfaces between the isothermal disc and atmosphere are in thermal pressure equilibrium,\
+  we can write the steady-state gaseous density distribution,\
+  confined in the total potential, of the disc and  Galactic atmosphere as\
+  \begin{subequations}
+  \begin{align}
+     \displaystyle \rho_{\text{isoDisk}}(z) = \rho_{\text{isoDisk}}^{\text{peak}}
+     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{isoDisk}}/m_{\text{p}}}\right]&\label{isothermal-disc-density}\\
+     \text{, if $|z| < z_{0}$,}& \nonumber \\
+     \nonumber\\
+     \displaystyle \rho_{\text{atmp}}(z) = \rho_{\text{atmp}}^{\text{peak}}
+     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{atmp}}/m_{\text{p}}}\right]&\label{isothermal-atmp-density}\\
+     \text{, otherwise,}& \nonumber
+  \end{align}
+  \label{disc-atm-sys}
+  \end{subequations}
+  where $m_{\text{p}}$ is the proton mass,\
+  $T_{\text{isoDisk}}$ and $T_{\text{atmp}}$ is the temperature of the isothermal disc and atmosphere,\
+  $\rho_{\text{isoDisk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the peak mass density\
+  of the disc and atmosphere on the mid-plane $z=0$.
+
+  We tabulate parameters in the first four\
+  categories of \Cref{table-parameters},\
+  except for $\rho_{\text{atmp}}^{\text{peak}}$ that\
+  can be derived from the other known parameters and thermal pressure equilibrium condition\
+  on the interfaces $(z=\pm z_{0})$ between the disc and atmosphere.\
+
+  The density profile of \Cref{disc-atm-sys} is shown in \Cref{fig__initial-density-profile}.\
+  Beyond the core radius ($\sim 2 \text{ kpc}$) the gaseous density decreases rapidly as a power-law.
+
+  The density profile of \Cref{disc-atm-sys} is shown in \Cref{fig__initial-density-profile}\
+  and compared to the observed result \citep{Miller_2013} beyond 1 kpc.\
+
+  Note that there is an difficulty in disentangling the contribution\
+  of the Local Bubble, a supernova remnant in which the Solar System is embedded \citep{Snowden1990},\
+  and the contribution from solar wind charge-exchange processes, which produce soft\
+  X-ray emission throughout the Solar System. As a result, the density profile of the Galactic halo remains unclear\
+  \citep{BlandHawthorn2016}.
+
+  \begin{figure}
+    \includegraphics[width=\columnwidth]{figures/fig__initial-density-profile.png}
+    \caption{The density profile of the isothermal disc (red pluses) and\
+             atmosphere (blue crosses) along the positive z-axis.\
+             The density distribution is derived from hydrostatic equilibrium,\
+             the interface ($z=0.1$) between the isothermal disc\
+             and the atmosphere is pressure balanced.}
+    \label{fig__initial-density-profile}
+  \end{figure}
+
+  To quantify the synchrotron radiation as a function of position,\
+  we adopt the default exponential magnetic field in \textsc{galprop} \citep{Strong2007}
+  that obeys the following spatial dependence:\
+
+  \begin{equation}
+     |\mathbf{B}(R, z)|=B_{0}\exp\left[-\frac{z}{z_{0}}\right]\exp\left[-\frac{R}{R_{0}}\right],
+     \label{magnetic-field}
+  \end{equation}
+
+  where $R=\sqrt{x^{2}+y^{2}}$, $B_{0}$ is the average field strength at the GC,\
+  and $z_{0}$ and $R_{0}$ are the characteristic scales in the vertical and radial\
+  directions, respectively. We adopt $z_{0} = 2$ kpc and $R_{0} = 10$ kpc, which\
+  are best-fitting values in the \textsc{galprop} model to reproduce the\
+  observed large-scale 408 MHz synchrotron radiation in the Galaxy.\
+  We choose $B_{0} = 50$ $\mu$G based on the observed field strength at the\
+  GC \citep{Crocker2010}.
+
+  % The dispersion:
+  %   2010-Comparing the statistics of interstellar turbulence in simulations and observations
+  %   2011-RELATIVISTIC JET FEEDBACK IN EVOLVING GALAXIES
+
+  \subsection{The Clumpy Multiphase Interstellar Medium}
+
+  A crucial component in our work is the clumpy ISM disc initialized by\
+  the publicly available pyFC code
+  \footnote{\url{https://pypi.python.org/pypi/pyFC}}.\
+
+  pyFC randomly generates dimensionless 3D scalar field $f(\bold{x})$\ % that is clumpy and porous.
+  that obeys the log-normal probability distribution\
+  with mean $\mu$ and dispersion $\sigma$,\
+  and follows the power-law Kolmogorov spectrum
+  \begin{equation}
+    D(\bold{k})=\int k^{2} \hat{f}(\bold{k})\hat{f}^{*}(\bold{k})d\Omega \propto k^{-\beta},
+    \label{Kolmogorov-spectrum}
+  \end{equation}
+  where $\hat{f}(\bold{k})$ is the Fourier transform of $f(\bold{x})$.\
+  The spectrum $D(\bold{k})$ in the Fourier space is characterized by a power-law index $\beta=5/3$,\
+  a Nyquist limit $k_{\text{max}}$, and a lower cutoff wave number $k_{\text{min}}$.
+  $k_{\text{max}}$ is one-half of the spatial resolution within the disc,\
+  and $k_{\text{min}}$ is 375.0, corresponding to the maximum size of an individual clump $\sim 20$ pc.\
+  \citet{LA2002} and \citet{Wagner2012} have outlined a detailed procedure\
+  for constructing a clumpy scalar field, and we do not repeat here.
+
+  The density of the clumpy disc can thus be obtained by taking the scalar products of\
+  $f(\bold{x})$ with $\rho_{\text{isoDisk}}(z)$ over all cells within the disc, i.e.,\
+  $\displaystyle\rho_{\text{ismDisk}}(\bold{x}) =\
+  f(\bold{x}) \rho_{\text{isoDisk}}(z)$.\
+  Also, the thermal pressure equilibrium within the clumpy disc implies that the temperature of the disc is
+  $\displaystyle T_{\text{ismDisk}}(\bold{x}) =\
+  T_{\text{isoDisk}}(z)\rho_{\text{isoDisk}}(z)/\rho_{\text{ismDisk}}(\bold{x})$.
+
+  The last category in \Cref{table-parameters} summarize the parameters of the clumpy disc and their references.
+
+  On the basis of this setup, we cover the AMR base level with\
+  $16\times16\times32$ root cells, refined progressively on the mid-plane $z=0$\
+  based on the gradient of mass density.\
+  We also restrict the refinement level at 7 within the disc so that\
+  a molecular cloud can be adequately resolved by approximately 30 cells along their diameter, 20 pc.
+
+  In this way, we plot the volume filling factor as a function of\
+  initial number density within the disc without the jet source in \Cref{fig__numberDensityHistogram},\
+  and show a close-up view of the\
+  pressure, temperature, and number density slices
+  in the y-z plane through the center of the disc in \Cref{fig__zoom-in-disc} .
+
+  \begin{figure}
+      \includegraphics[width=\columnwidth]{figures/fig__numberDensityHistogram.png}
+    \caption{The volume filling factor as a function of\
+             initial number density within the disc without jet source.\
+             The vertical bands from left to right depict the allowable number densities \citep{peak-ism-density} for\
+             hot ionized, warm neutral (WNM), warm ionized (WIM), cold neutral mediums (CNM), and molecular clouds.}
+      \label{fig__numberDensityHistogram}
+  \end{figure}
+
+  \begin{figure}
+    \includegraphics[width=\columnwidth]{figures/fig__zoom-in-disc.png}
+    \caption{Close-up view of the initial\
+             pressure (top), temperature (middle), and number density (bottom) slices\
+             in the y-z plane through the center of the disc.
+             }
+    \label{fig__zoom-in-disc}
+  \end{figure}
+
+\begin{table*}[t]
+\raggedright
+\caption{Parameters of the disc, atmosphere, and gravitational potential in the simulations.}
+\label{table-parameters}
+\begin{tabular}{@{}llrc@{}}
+\toprule[1pt]\midrule[0.3pt]
+Parameter                             & Description                               & Value                                &  Reference                     \\ \midrule
+{\bf Static stellar potential }       &                                           &                                      &                                \\
+$\sigma_{\text{bulge}}$               & Velocity dispersion of bulge              & 100 km$\cdot$s$^{-1}$                & \citep{velocity-dispersion-MW} \\
+$\rho_{\text{bulge}}^{\text{peak}}$   & Peak average density of bulge             & $4\times 10^{-24}$ g$\cdot$cm$^{-3}$ &   N/A                          \\ \hline
+{\bf Static dark halo potential }     &                                           &                                      &                                \\
+$v_{\text{halo}}$                     & Characteristic velocity                   & 131.5 km$\cdot$s$^{-1}$              & \citep{Johnston1995}           \\
+$d_{\text{h}}$                        & Core radius                               & 12 kpc                               & \multicolumn{1}{c}{''}         \\ \hline
+{\bf Atmosphere }                     &                                           &                                      &                                \\
+$T_{\text{\text{atmp}}}$              & Temperature of atmosphere                 & $10^{6}$ K                           & \citep{temperature-MW}         \\ \hline
+{\bf Isothermal disc }                &                                           &                                      &                                \\
+$z_{0}$                               & Scale height of disc                      & 100 pc                               & \citep{peak-ism-density}       \\
+$T_{\text{\text{isoDisk}}}$           & Temperature of disc                       & $10^{3}$ K                           & \multicolumn{1}{c}{''}         \\
+$\rho_{\text{isoDisk}}^{\text{peak}}$ & Peak mass density of disc                 & $10^{-23}$ g$\cdot$cm$^{-3}$         & \multicolumn{1}{c}{''}         \\ \hline
+{\bf Clumpy disc }                    &                                           &                                      &                                \\
+$\dagger$  $k_{\text{min}}$           & Cutoff wave number                        & 375.0                                & \citep{peak-ism-density}       \\
+$\mu$                                 & Mean of scalar field                      & 1.0                                  &   N/A                          \\
+$\ddag$  $\sigma$                     & Dispersion of scalar field                & 5.0                                  & \citep{Federrath2010}          \\
+$\beta$                               & Power law index                           & -5/3                                 &   N/A                          \\ \midrule
+\end{tabular}
+\begin{tablenotes}
+      \raggedright
+      \item  $\dagger$  $k_{\text{min}}=375.0$ leads to the size of an individual molecular cloud $\sim 100$ pc.
+      \item  $\ddag$ In numerical simulations of turbulence,\
+             \citet{Federrath2010} find $\sigma\sim 3.6$ and 35 for solenoidal (divergence-free)\
+             and compressive (curl-free) driving force,\
+             respectively, so that our adopted value of 5 is closer to their solenoidal result.
+    \end{tablenotes}
+\end{table*}
+
+% In addition to the gravitational interaction, we ignore other interactions between stars and gases.
+% We also ignore the self-gravity of the ISM disc and of the atmosphere.
+% We ignore the centrifugal force of Milky Way rotation acting on the bubbles.
+%
+
+\subsection{Oblique jets injection}
+
+  We simulate the jet with an inclination angle\
+  $45^{\circ}$ with respect to the Galactic plane\
+  in order to release the caveat that\
+  the jet direction must be perpendicular to the Galactic plane, and in particular to\
+  investigate how the dense disc affect the bubbles formation.
+
+  A few additional quantities are used to characterize the jets:
+  the density contrast between the thermal gas contained in the jet source and the atmosphere gas,\
+  $\rho_{\text{jet}}/\rho_{\text{amb}}=10^{-3}$,\
+  the temperature contrast, $T_{\text{jet}}/T_{\text{amb}}=2\times10^{4}$,\
+  the pressure ratio of CR to gas is 0.18,\
+  and the flow 4-velocity inside the jet source $\beta\gamma = 0.6$\
+  along the symmetric axis of cylinder.\
+  The jet power is thus $3.2\times 10^{42}$ erg/s, resulting in the Eddington ratio 0.008.
+
+  Note that as we inject the jets at the center of the clumpy disc,\
+  we define the atmosphere gas density by the peak density of\
+  the isothermal disc on the mid-plane $z=0$ (i.e. $\rho^{\text{peak}}_{\text{isoDisk}}$),\
+  as opposed to the \textit{clumpy} density around the jet source, to avoid ambiguous definition.
+
+  The bipolar jets are constantly ejected from a cylindrical source at the beginning of simulation ($t=0$)\
+  and suddenly quenched at $t=1.2$ Myr before fully breaking out the disc.\
+  Without quenching, the Galactic bubbles at the present time will be asymmetric about the Galactic plane.
+  The jet duration allows the total ejected energy to be $1.2\times10^{56}$ erg between\
+  $8\times10^{55}$ erg and $1.3\times10^{56}$ erg, estimated by \citet{Predehl2020}.\
+
+  The diameter and height of cylindrical source are 4 pc,\
+  leading to the source volume ($\sim 50 \text{ pc}^{3}$) is\
+  much smaller than that of an individual clump by a factor of about 83.\
+  By intentionally reducing the volume ratio of the jet source to an individual clump,\
+  we can mitigate the effect of the randomness of the clumps on the bubbles.\
+  Moreover, we resolve the jet source with the highest refinement level 11,\
+  bringing the finest spatial resolution up to 0.4 pc.\
+
+\section{Results}
+\label{Results}
+
+\subsection{Morphology and properties of Galactic bubbles}
+
+ \Cref{fig__jetI5+ismSeed3-45deg} shows\
+ the slices of pressure (top), temperature (middle), number density (bottom)\
+ at the end of simulation $t=12.39$ Myr.\
+ The slices pass through the bipolar jet source injecting along $z=-y$ direction.
+
+ The fiducial run (\Cref{fig__jetI5+ismSeed3-45deg-a})\
+ with the initial condition specified in Section \ref{Methodology}\
+ shows that the edge of the outermost bubbles is indeed a forward shock,\
+ expanding 12.5 kpc above and below the Galactic plane,\
+ with a semiminor axis about 6.8 kpc on the plane.\
+ We note that the overall extent of the outermost bubbles is comparable to\
+ the two spherical objects of a radius 6-7 kpc proposed by \citet{Predehl2020}\
+ for modeling the eROSITA bubbles\
+ based on X-ray emissions.
+
+ The temperature profile (left middle panel in \Cref{fig__profile}) along the positive z-axis in\
+ \Cref{fig__jetI5+ismSeed3-45deg} indicates that\
+ the smooth region (purple band in \Cref{fig__profile}) emitting X-ray\
+ is around 0.3-0.5 keV, similar to that observed by \citet{Miller2016} and \citet{Kataoka2018}.
+
+ Followed by the forward shock is a turbulent and hot plasma\
+ in pressure balance with the external medium.\
+ As shown in the temperature or density slices of the fiducial run,\
+ the full extent of the turbulent plasma is 9 kpc, fairly close to\
+ that of the observed \textit{Fermi} bubbles \citep{Su2010}.
+ Also, the temperature of the plasma is as high as 2 keV,\
+ comparable to few keV inside the \textit{Fermi} bubbles\
+ by observing X-ray absorption lines through the hot\
+ gaseous halo along many different sight lines in the sky \citep{Miller_2013}.\
+ The general agreement of extent and temperature\
+ suggests that the \textit{Fermi} bubbles\
+ is essentially a turbulence rather than a smooth shock \citep{Zhang2020}.
+
+ The most interesting finding is that there are innermost bubbles\
+ (dashed box in the top panel of \Cref{fig__jetI5+ismSeed3-45deg-a})\
+ extending out from the GC on either side of the thin disk.\
+ The innermost bubbles are cold (1-10 eV), dense ($10^{-4}$--$10^{-2}$ cm$^{-3}$),\
+ and underpressured with respect to the turbulent plasma.\
+
+ Moreover, the close-up view (right column in \Cref{fig__profile})\
+ of profiles and slices (\Cref{fig__innerbubbles})\
+ demonstrates that the pressure rises dramatically outward across\
+ the edge of the innermost bubbles,\
+ indicating that the innermost bubbles are an expanding reverse shock.\
+ The high density upstream of the reverse shock requires\
+ an even higher density downstream.\
+ Continuing outward, the higher density must match with low density further downstream;\
+ thus there exists a dense shell.
+
+ The turbulent plasma is therefore bracketed between the downstream of reverse shock\
+ and of the outermost forward shock, thus heating the turbulent plasma up considerably.
+
+ We stressed that either the outermost, turbulent plasma, or innermost bubbles\
+ are symmetric about the Galactic plane despite the jet is tilted to the disk normal\
+ at an angle $45^{\circ}$.
+
+ \Cref{fig__jetI5+ismSeed3-45deg} shows the slices of various gas properties at $t=12.39$ Myr,\
+ including pressure (top), temperature (middle),\
+ density (bottom) with the same jet source as the fiducial run\
+ but in different Galactic environments.
+
+ %To explore how the disk affects the formation of the Galactic bubbles,\
+ We compare the clumpy disk (\Cref{fig__jetI5+ismSeed3-45deg-a})\
+ with the smooth disc (\Cref{fig__jetI5+ismSeed3-45deg-b}),\
+ specified by the initial density profile shown in \Cref{fig__initial-density-profile},\
+ in a stratified atmosphere.\
+ The results show that the initial density distribution of\
+ the dense disc has an insignificant effect\
+ on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
+ in an uniform atmosphere (\Cref{fig__jetI5+ismSeed3-45deg-c}) is spherical-shape,\
+ suggesting the stratification facilitates the outermost bubbles elongation significantly.\
+ Also, \Cref{fig__jetI5+ismSeed3-45deg-c,fig__jetI5+ismSeed3-45deg-d}\
+ reveal that the development of the innermost bubbles\
+ is always associated with the disc, without the disc,\
+ the outermost bubbles and the turbulent plasma will be oblique,\
+ indicating the dense disc is crucial for\
+ the symmetry of the Galactic bubbles and for the innermost bubbles formation.
+
+ \begin{figure}
+      \begin{subfigure}[b]{0.2\linewidth}%
+         \centering%
+         \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-a}%
+         \label{fig__jetI5+ismSeed3-45deg-a}%
+         \hspace{2pt}%
+      \end{subfigure}%
+      \begin{subfigure}[b]{0.2\linewidth}%
+         \centering%
+         \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-b}%
+         \label{fig__jetI5+ismSeed3-45deg-b}%
+         \hspace{2pt}%
+      \end{subfigure}%
+      \begin{subfigure}[b]{0.2\linewidth}%
+         \centering%
+         \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-c}%
+         \label{fig__jetI5+ismSeed3-45deg-c}%
+         \hspace{2pt}%
+      \end{subfigure}%
+      \begin{subfigure}[b]{0.2\linewidth}%
+         \centering%
+         \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-d}%
+         \label{fig__jetI5+ismSeed3-45deg-d}%
+     \end{subfigure}%
+ \end{figure}
+
+%\begin{figure}%
+%  \centering%
+%  \subfigure[][]%
+%    {%
+%      \includegraphics[height=10.1cm]{figures/fig__jetI5+ismSeed3-45deg-a}%
+%      \label{fig__jetI5+ismSeed3-45deg-a}%
+%    }%
+%  \hspace{2pt}%
+%  \subfigure[][]%
+%    {%
+%      \includegraphics[height=10.1cm]{figures/fig__jetI5+ismSeed3-45deg-b}%
+%      \label{fig__jetI5+ismSeed3-45deg-b}%
+%    }%
+%  \hspace{2pt}%
+%  \subfigure[][]%
+%    {%
+%      \includegraphics[height=10.1cm]{figures/fig__jetI5+ismSeed3-45deg-c}%
+%      \label{fig__jetI5+ismSeed3-45deg-c}%
+%    }%
+%  \hspace{2pt}%
+%  \subfigure[][]%
+%    {%
+%      \includegraphics[height=10.1cm]{figures/fig__jetI5+ismSeed3-45deg-d}%
+%      \label{fig__jetI5+ismSeed3-45deg-d}%
+%    }%
+%  \caption{
+%             The slices of pressure (top), temperature (middle), and number density (bottom)\
+%             at the end of simulation $t=12.39$ Myr.\
+%             The slices pass through a bipolar jet source injecting along $z=-y$ direction\
+%             for a duration $t=0$--$1.2$ Myr.\
+%             Comparison between the clumpy (column a)\
+%             and the smooth disc (column b) in a stratified atmosphere\
+%             shows that the initial density distribution of the dense disc has an insignificant effect\
+%             on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
+%             in an uniform atmosphere (column c) is spherical-shape,\
+%             suggesting the stratification facilitates the outermost bubbles elongation significantly.\
+%             Also, the two rightmost columns reveal that the development of the innermost bubbles\
+%             is always associated with the disc, without the disc (column d),\
+%             the outermost bubbles and the turbulent plasma will be oblique,
+%             indicating the dense disc is crucial for\
+%             the symmetry of the Galactic bubbles and for the innermost bubbles formation.
+%  }%
+%  \label{fig__jetI5+ismSeed3-45deg}%
+%\end{figure}%
+
+%\begin{figure}%
+%  \centering%
+%  \subfigure[][]%
+%    {%
+%      \includegraphics[height=7cm]{figures/fig__profile-1.png}%
+%      \label{fig__profile-1}%
+%    }%
+%  \hspace{2pt}%
+%  \subfigure[][]%
+%    {%
+%      \includegraphics[height=7cm]{figures/fig__profile-2.png}%
+%      \label{fig__profile-2}%
+%    }%
+%    \caption{
+%             Left: the profiles of pressure (top), temperature (middle),\
+%             and number density (bottom)\
+%             along the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.
+%             Right: the close-up view of the profiles in the yellow band.\
+%             The sharp pressure jump at $z=3.62$ kpc\
+%             indicates that the innermost bubbles\
+%             (dashed box in the top panel in \Cref{fig__jetI5+ismSeed3-45deg-a})\
+%             are an expanding reverse shock.
+%     }
+%    \label{fig__profile}
+%  \end{figure}
+
+  \begin{figure}
+    \includegraphics[width=\columnwidth]{figures/fig__innerbubbles.png}
+    \caption{
+       Zoom-in images of the density (left) and pressure (right) slices of the innermost bubbles.\
+       The high density upstream of the reverse shock requires\
+       an even higher density downstream.\
+       Continuing outward, the higher density must match with low density further downstream;\
+       thus there exists a dense shell\
+       (the turbulent region outside the black dashed line on density slice).
+     }
+    \label{fig__innerbubbles}
+  \end{figure}
+
+  \subsection{X-ray}
+  \label{X-ray}
+  The X-ray emissivity is computed\
+  for each computational volume cell
+  using the MEKAL model \citep{Xray-1,Xray-2,Xray-3}\
+  implemented in the utility XSPEC \citep{XSPEC}, assuming solar metallicity.\
+  The X-ray intensity map are then generated by projecting the emissivities\
+  along lines of sight\
+  pointing away from the solar position at $(R_{\odot},0,0)=(8,0,0)$ kpc\
+  with angular resolutions of 0.5 degrees, where $R_{\odot}$ is the Sun-GC distance.
+
+  We point out that the projections throughout this paper is \lq perspective\rq,\
+  which has the effect of making distant object appear smaller than the same object in the near distance,\
+  in order to facilitate a reliable interpretation of simulated all-sky map,\
+  and also that the observed X-ray emission is contributed by all the gas in the Milky Way halo,\
+  which likely extends to a radius of $\sim$250 kpc \citep{halo-radius-1,halo-radius-2},\
+  much bigger than our simulation box.
+
+  We first compute the X-ray emissivity\
+  from the simulated gas within a radius of 25 kpc away from the GC.
+  Then, beyond 25 kpc the gas is assumed to be isothermal with $T=10^6$ K and\
+  follows out to a radius of 250 kpc the observed density profile of \citep{temperature-MW}.
+
+  \Cref{fig__xray_0.8keV_angle_000} shows\
+  the comparison between simulated (top) and observed (bottom) all-sky map\
+  in the range 0.6--1.0 keV at 12.39 Myr and the present time, respectively.\
+  In the simulated map, the red arrow at the center of map represents the direction of the bipolar jet,\
+  constantly ejecting at an angle of $45^{\circ}$ to the disc normal between 0--1.2 Myr.
+
+  \Cref{fig__x-ray-profile-0.8keV-000} displays the simulated count rate profiles (red)\
+  in the same energy band as \Cref{fig__xray_0.8keV_angle_000}\
+  cut at various galactic latitudes (as labelled), compared with the observation (black).\
+  \Cref{fig_xray-map} is quite revealing in several ways.\
+
+  First, we observe that\
+  The simulated eROSITA bubbles are not as limb-brightened as the observation.\
+  A possibility to enhance the X-ray emission is to include shock-accelerated CRs near the shock,\
+  in which CRs could increase the compressibility of the fluid,\
+  resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density squared.
+  The broad agreement between simulated and observed X-ray maps hints that\
+  the full vertical extent of the eROSITA bubbles can be properly formed by an oblique jet within a thin disk\
+  of dense ISM.
+
+  Second, as shown in \Cref{fig__jetI5+ismSeed3-45deg},\
+  the half-width of the outermost bubbles is around 7 kpc,\
+  corresponding to an half angular width $\sin^{-1}(7 \text{ kpc}/R_{\odot})\sim122^{\circ}$,\
+  which is as wide as the eROSITA bubbles in the simulated X-ray map (top panel in \Cref{fig__xray_0.8keV_angle_000}).\
+  We therefore suggest that the eROSITA bubble shells are a signature of compressed forward shocks\
+  that have been driven into the northern and the southern Galactic halo,
+  as previously proposed by \citet{Predehl2020}.
+
+% 2. North Polar Spur is not shown as it is a supernova remanent near us.
+  Third, the innermost bubbles\
+  shown in \Cref{fig__jetI5+ismSeed3-45deg},\
+  even though with high column density, are invisible in the simulated X-ray map as\
+  the temperature of the innermost bubbles is around $1$--$10$ eV\
+  (see the temperature profile in \Cref{fig__profile}).\
+  Consequently, the X-ray emission within the innermost bubbles
+  is severely suppressed by the cutoff $\exp\left[-h\nu/k_{B}T\right]$ in the thermal Bremsstrahlung emissivity.\
+  This is the reason why the innermost bubbles are unseen in the X-ray observation.
+
+%  \begin{figure*}[]
+%    \subfigure[(A) Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
+%               (photons s$^{-1}$ deg$^{-2}$) in the 0.6--1.0 keV range.\
+%               Throughout this paper we show sky maps\
+%               in Galactic coordinates centered on the Galactic center using a Hammer-Aitoff projection,\
+%               and observed from the solar system.\
+%               The red arrow at the center of the\
+%               top panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
+%               to the disc normal in 1.2 Myr.]
+%     {
+%      \includegraphics[width=0.8\linewidth]{figures/fig__xraymap.png}
+%      \label{fig__xray_0.8keV_angle_000}
+%     }
+%    \subfigure[(B) Comparison of simulated (red) and observed (black; \citealt{Predehl2020}) one-dimensional\
+%               count rate profiles in the same energy band as \Cref{fig__xray_0.8keV_angle_000},\
+%               cut at various galactic latitudes (as labelled).]
+%     {
+%      \includegraphics[width=0.8\linewidth]{figures/fig__xray-profile-0.8keV-000.png}
+%      \label{fig__x-ray-profile-0.8keV-000}
+%     }
+%    \caption{}
+%    \label{fig_xray-map}
+%  \end{figure*}
+
+\subsection{Gamma-ray and microwave spectra: constraint on the CRe spectral index}
+\label{sec:gamma-ray-microwave}
+In this section, we give the constraint on the CRe spectral index by\
+comparing the simulated gamma-ray and microwave spectra\
+with the observed spectra of the Fermi bubbles \citep{Ackermann2014}\
+and the microwave haze \citep{Dobler_2008}, respectively.\
+
+The simulated gamma-ray and microwave spectra is based on the\
+IC scattering and synchrotron, respectively, from CRe.\
+The CRe spectrum follows a power-law distribution ranging from\
+$0.5$ MeV to $562.1$ GeV.
+
+%The microwave haze at 23 GHz was first detected by the \textit{WMAP} \citep{Dobler_2008}\
+%within the region $|b|<30^{\circ}$ above and below the Galactic plane,\
+%and later confirmed by the Planck Collaboration IX \citep{PlanckCollaborationIX2013}.
+
+The IC emissivity of the upscattered photons at the energy $\epsilon_{1}$ is computed for\
+each computational cell in our simulations\
+using the Klein-Nishina IC cross-section \citep{Jones1968,BLUMENTHAL1970}\
+to handle the scattering between ultra-relativistic CRe and photons in the ISRF:
+
+\begin{subequations}
+  \begin{align}
+  &\frac{dE}{dtd\epsilon_{1}dV} =\nonumber\\
+               &\frac{3}{4}\sigma_{T}c\mathbb{C}\epsilon_{1}\int^{\epsilon_{\text{max}}}_{\epsilon_{\text{min}}}
+               \frac{n(\epsilon)}{\epsilon}d\epsilon\int^{\gamma_{\text{max}}}_{\gamma_{\text{min}}\left(\epsilon\right)}
+               \gamma^{-(p+2)}f(q, \Gamma)d\gamma,\\
+  \nonumber\\
+  &f(q, \Gamma) =\nonumber\\
+               &2q\ln q+(1+2q)(1-q)+0.5(1-q)\frac{\left(\Gamma q\right)^2}{1+\Gamma q},\\
+  &q=\frac{\epsilon_{1}/\gamma\
+               m_{\text{e}}c^{2}}{\Gamma\left(1-\epsilon_{1}/\gamma m_{\text{e}}c^{2}\right)},\\
+  &\Gamma=\frac{4\epsilon \gamma}{m_{\text{e}}c^2},\\
+  &\gamma_{\text{min}}(\epsilon)=\
+   0.5\left(\frac{\epsilon_{1}}{m_{\text{e}}c^2}+\sqrt{\left(\frac{\epsilon_{1}}{m_{\text{e}}c^2}\right)^2+\
+   \frac{\epsilon_{1}}{\epsilon}}\right) \label{gamma-min},
+  \end{align}
+\label{gammaray-emissivity}
+\end{subequations}
+
+where $\sigma_{T}$ is the Thomson cross section, $c$ speed of light,\
+$m_{\text{e}}$ electron mass,\
+$n(\epsilon)$ the energy distribution of the photon number density in ISRF given by \citet{Porter2017},\
+$\gamma$ the Lorentz factor of CRe,\
+$\mathbb{C}$ and $p$ are the normalization constant and spectral index of CRe power-law spectrum.
+$\gamma_{\text{min}}(\epsilon)$ is the minimum Lorentz factor of CRe\
+that allows incident photons to scatter from energy $\epsilon$ to $\epsilon_{1}$.
+$\gamma_{\text{max}}$ is the maximum CRe Lorentz factor in the spectrum.
+
+We perform the double integration in \Cref{gammaray-emissivity} on each cell\
+over the range of CRe Lorentz factor, and\
+the range of incident photon energy between\
+$\epsilon_{\text{min}}=1.13\times10^{-4}$ eV (cosmic microwave background) and\
+$\epsilon_{\text{max}}=13.59$ eV (optical starlight)\
+to obtain the simulated IC emissivities.
+
+The synchrotron emissivity with an isotropic electron pitch angle distribution\
+is given by \citet{BLUMENTHAL1970}:
+
+\begin{subequations}
+   \begin{align}
+      &\frac{dE}{dtd\nu dV} =\nonumber\\
+      &\frac{4\pi\mathbb{C}e^{3}B^{0.5(p+1)}}{m_{\text{e}}c^{2}}\
+      \left(\frac{3e}{4\pi m_{\text{e}}c}\right)^{0.5(p-1)}\
+      a(p)\nu^{-0.5(p-1)},\\
+      &a(p)=\nonumber\\
+           &\frac{2^{0.5(p-1)}\sqrt{3}\Gamma\left[\left(3p-1\right)/12\right]\
+                                      \Gamma\left[\left(3p+9\right)/12\right]\
+                                      \Gamma\left[\left(p+5\right)/4\right]}
+      {8\sqrt{\pi}(p+1)\Gamma\left[\left(p+7\right)/4\right]},
+   \end{align}
+   \label{synchrotron-emissivity}
+\end{subequations}
+
+where $\Gamma$ is the gamma function, $B$ is the magnetic field strength defined in\
+\Cref{magnetic-field}.
+
+For a given longitude and latitude range, the simulated spectra are\
+computed by projecting emissivities\
+as we project X-ray emissivities in Section \ref{X-ray},\
+and then we average the spectra over all the sight lines within the region on sky.
+
+\Cref{fig__gammaRaySynchtronSpectrum} shows the simulated microwave (left)\
+and gamma-ray (right) spectra averaged over the different patches (shown in the legends) of the sky.\
+The row from top to bottom shows the spectra with different CRe spectral index $2.2, 2.4$ and $2.6$.\
+Several points are worth specific comment.\
+
+First, we find that the simulated gamma-ray spectra are well fitted by\
+the CRe spectral index 2.4 (the middle row),\
+despite the simulated microwave spectra are marginally consistent with the observed.
+
+Second, the simulated and observed gamma-ray spectra is\
+nearly latitude independent, and characterized by a broad bump that roughly peaks around $\sim10$ GeV.\
+However, the high-latitude spectrum tends to be slightly dimmer than low-latitude\
+probably because the optical intensity in ISRF decays with increasing latitude.
+
+Third, the gamma-ray spectra for all latitudes indicate a spectral cutoff around energies 400--500 GeV,\
+remarkably consistent with the observed cutoff energy.\
+This is expected since\
+the upscattered high-energy photons ($\epsilon_{1}\sim450$ GeV) mainly arise from\
+the scatterings between the relativistic CRe ($\gtrapprox 408$ GeV)\
+and optical starlight ($\epsilon \sim 10$ eV).\
+Thus, \Cref{gamma-min} can be reduced to $\epsilon_{1}\sim\gamma m_{\text{e}}c^2$\
+in the Klein--Nishina limit\
+$\left(\text{i.e. }\epsilon_{1}\epsilon \gg \left(m_{\text{e}}c^2\right)^2\right)$,\
+implying most of the CRe energy is carried away by the upscattered photons.
+
+Fourth, the good agreement between the simulated and observed gamma-ray/microwave spectra\
+implies that, in the presence of ISRF and magnetic fields, the emission of the Fermi bubbles and\
+the microwave haze can be produced by the same high-energy electrons\
+via inverse Compton scatterings and synchrotron radiations, respectively,\
+as previously suggested \citep{Su2010,Dobler2012}.
+
+\begin{figure*}
+  \includegraphics[width=\linewidth]{figures/fig__spectrum.png}
+  \caption{
+      Simulated microwave spectra (colored lines in left) averaged over $20^{\circ}<|b|<30^{\circ}$, $|l|<10^{\circ}$.\
+      The data point represents the \textit{WMAP} data in the 23 GHz K band and\
+      the shaded bow-tie area indicates the range\
+      of synchrotron spectral indices allowed for the \textit{WMAP} haze \citep{Dobler_2008}.\
+      Simulated gamma-ray spectra (colored lines in right column)\
+      of the \textit{Fermi} bubbles calculated for a longitude range of\
+      $|l|<10^{\circ}$ for different latitude bins.\
+      The gray band represents the observational data of \citet{Ackermann2014}.\
+      The row from top to bottom shows the microwave (left) and gamma-ray (right) spectra\
+      with CRe spectral index $2.2, 2.4$ and $2.6$, respectively.\
+      The CRe cutoff energy is 562.1 GeV in all cases.
+      %At larger $p$, the microwave spectrum was found to be steeper as $I_{\nu}\propto \nu^{-(p-1)/2}$.
+  }
+  \label{fig__gammaRaySynchtronSpectrum}
+\end{figure*}
+
+ \Cref{fig__gammaRay-map} shows the simulated gamma-ray photon flux with a CRe power-law index 2.4\
+ compared with the observed one\
+ in the energy bin $76.8-153.6$ GeV.\
+ As the eROSITA bubbles,\
+ one can see that the symmetric \textit{Fermi} bubbles\
+ can also be realized by oblique jets.\
+
+ Finally, the comparison between\
+ \Cref{fig__jetI5+ismSeed3-45deg}\
+ and\
+ \Cref{fig__jetI5+ismSeed3-45deg-CR}\
+ shows that the CR pressure\
+ is around 5$\times10^{-15}$--8$\times10^{-15}$ erg/cm$^{3}$,\
+ bringing the pressure ratio of CR to gas is 0.1--0.2,
+ similar to 0.18 at the beginning of the simulation.
+ We therefore stress that\
+ ignoring the contribution of CR pressure gradient to the momentum of the gas\
+ in \Cref{governing-eq} is reasonable.
+
+% assuming a uniform CR spectrum with energy cutoff of ~500 GeV\
+% and spectral index of 2.4, one could also reproduce the gamma-ray spectrum quite well.\
+% Note that the simulation time at this point is 12.39 Myr,\
+% much longer than the CR electron cooling time, so their Emax should\
+% have cooled to below 500 GeV by this time (we should think about how to estimate this).\
+% Therefore, the CRe generating the gamma-ray emission would need to be re-accelerated\
+% by some in-situ acceleration mechanisms such as shocks or turbulence.\
+% The forward shock is pretty far away from the gamma-ray bubbles,\
+% so it's more likely associated with turbulence.
+
+  %The enhanced emission at the lower latitude would likely be due to
+  %similar to the bottom right panel in Fig. 5 of YR17, which is dominated by\
+  %the optical starlight. That's also why in your plot above,\
+  %the high-latitude spectrum tends to be dimmer because of the decay of the ISRF intensity in optical.
+
+\begin{figure*}
+  \includegraphics[width=\linewidth]{figures/fig__GammaRay_100e9_1e6_angle_000.png}
+  \caption{The observed (left; \citealt{Selig2015}) and simulated (right) photon flux\
+           in the energy bin $76.8-153.6$ GeV.\
+           Note that the left panel is the\
+           photon flux of the diffuse component reconstructed by the D$^3$PO\
+           algorithm \citep{Selig2015} that analyzes\
+           the photon data from the \textit{Fermi} Large Area Telescope \citep{Atwood2009}\
+           and removes the contribution from point-like component.
+           The red arrow at the center of the right\
+           panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
+           to the disc normal in 1.2 Myr.
+  }
+  \label{fig__gammaRay-map}
+\end{figure*}
+
+  \begin{figure}
+    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg-CR.png}
+    \caption{
+     The CR pressure slice passing through the jet source at 12.39 Myr.\
+     Comparison between\
+     gas pressure (\Cref{fig__jetI5+ismSeed3-45deg}) and cosmic ray pressure\
+     shows that
+     the CR pressure\
+     is around 5$\times10^{-15}$--8$\times10^{-15}$ erg/cm$^{3}$,\
+     bringing the pressure ratio of CR to gas is 0.1--0.2,
+     similar to 0.18 at the beginning of the simulation.
+     We therefore stress that\
+     ignoring the contribution of CR pressure gradient to the momentum of the gas\
+     in \Cref{governing-eq} is reasonable.
+     }
+    \label{fig__jetI5+ismSeed3-45deg-CR}
+  \end{figure}
+
+%\subsubsection{Hadronic process}
+%In the hadronic model, CRp undergo hadronic collisions with thermal gas protons\
+%and produce $\gamma$-ray via pion decay. The volume emissivity of the emission can be written as
+%\begin{equation}
+%   \epsilon \propto U_{\text{CRp}}n_{p}\sigma_{p}\kappa_{pp}.
+%\end{equation}
+%
+%\begin{equation}
+%  \frac{dE}{dtd\epsilon_{1}dV} =\
+%   cn_{H}pC\left(\frac{\epsilon_{1}}{m_{\text{p}}c^2}\right)^{-p}\
+%   \int_{0}^{1}\sigma(\epsilon_{\text{p}}) F(x,\epsilon_{\text{p}}) x^{p}dx.
+%\end{equation}
+%
+%\begin{equation}
+%\sigma(\epsilon_{\text{p}})=34.3+1.88L+0.25L^{2}\left[1-\frac{E_{\text{threshold}}}{E_{\text{p}}}\right]^{4} \text{ mb}.
+%\end{equation}
+%
+%\begin{equation}
+%F(x,\epsilon_{\text{p}})=B\frac{d}{dx}\left[\ln(x)\left(\frac{1-x^{\beta}}{1+kx^{\beta}\left(1-x^{\beta}\right)}\right)^4\right],
+%\end{equation}
+%
+%
+%where
+%$x=\epsilon_{1}/\epsilon_{\text{p}}$, $B=1.30+0.14L+0.011L^2$, $\beta=\left(1.79+0.11L+0.008L^{2}\right)^{-1}$,\
+%$\left(0.801+0.049L+0.014L^{2}\right)^{-1}$, $L=\ln(\epsilon_{\text{p}}/1 \text{ TeV})$.
+
+\section{Conclusions}
+\label{Conclusions}
+In this work, we introduce a thin, dense disk composed of clumpy ISM\
+to divert the oblique jets at an angle $45^{\circ}$\
+to the disk normal in the past energetic event of the central SMBH.\
+We investigate the properties of the Galactic bubbles and the microwave\
+haze using 3D special relativistic hydrodynamic simulations of CR injection from\
+the SMBH assuming the leptonic model.
+
+Our findings are as follows.
+
 \begin{itemize}
-\item \verb'letters' -- used for papers in the journal's Letters section.
-\item \verb'onecolumn' -- single column, instead of the default two columns. This should be used {\it only} if necessary for the display of numerous very long equations.
-\item \verb'doublespacing' -- text has double line spacing. Please don't submit papers in this format.
-\item \verb'referee' -- \textit{(deprecated)} single column, double spaced, larger text, bigger margins. Please don't submit papers in this format.
-\item \verb'galley' -- \textit{(deprecated)} no running headers, no attempt to align the bottom of columns.
-\item \verb'landscape' -- \textit{(deprecated)} sets the whole document on landscape paper.
-\item \verb"usenatbib" -- \textit{(all papers should use this)} this uses Patrick Daly's \verb"natbib.sty" package for citations.
-\item \verb"usegraphicx" -- \textit{(most papers will need this)} includes the \verb'graphicx' package, for inclusion of figures and images.
-\item \verb'useAMS' -- adds support for upright Greek characters \verb'\upi', \verb'\umu' and \verb'\upartial' ($\upi$, $\umu$ and $\upartial$).
-Only these three are included, if you require other symbols you will need to include the \verb'amsmath' or \verb'amsymb' packages (see section~\ref{sec:packages}).
-\item \verb"usedcolumn" -- includes the package \verb"dcolumn", which includes two new types of column alignment for use in tables.
+
+\item The Galactic bubbles are nearly symmetric about the Galactic plane albeit\
+      the bipolar jets are at an angle $45^{\circ}$\
+      with respect to the disc normal.\
+      The broad agreement between simulated and observed multiwavelength features\
+      provides supporting evidence for the oblique jet scenario, and also\
+      releases the caveat given by earlier simulation-based studies:\
+      the jets shall be vertical to the disc normal.
+\item The randomness of clumpy disk has a insignificant impact on the overall dynamic of the Galactic bubbles.\
+      The development of the reverse shocks (the innermost bubbles) is always associated with the dense disc,\
+      without the disc, the outermost bubbles and the turbulent plasma will be oblique,\
+      indicating the dense disc is crucial for\
+      the symmetry of the Galactic bubbles and for the innermost bubbles formation.
+\item The edge of the eROSITA bubbles is a forward shock,\
+      originally driven by oblique bipolar jets emanating from the GC 12.39 million years ago,\
+      and significantly stretched by the stratified atmosphere afterwards.\
+      The simulated eROSITA bubbles are not as limb-brightened as the observation.\
+      A possibility to enhance the X-ray emission is to include shock-accelerated CRs near the shock,\
+      in which CRs could increase the compressibility of the fluid,\
+      resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density squared.
+\item Followed by the forward shock is a turbulent and hot plasma ($\sim2$ keV),\
+      which we interpret as the \textit{Fermi} bubbles.\
+      The similarity of the morphology, temperature, and gamma-ray spectrum between\
+      simulated and observed \textit{Fermi} bubbles suggests that\
+      the \textit{Fermi} bubbles are essentially a turbulent and\
+      high temperature plasma in pressure balance with external medium.
+      Associated with the Galactic magnetic field\
+      will lead to the stochastic acceleration of CRe, possibly in balance with the IC and synchrotron cooling.\
+      We will investigate the competition between stochastic acceleration and radiative cooling in a future work.
+\item According to the microwave and leptonic gamma-ray spectra, the best-fitting\
+      CRe power-law index is found to be 2.4.
+\item The same leptotonic CRe can simultaneously\
+      account for the \textit{Fermi} bubbles and haze emission suggested that\
+      they are physically related around the GC,\
+      and that the magnetic fields within the bubbles are close to the exponentially distributed\
+      Galactic magnetic field.
 \end{itemize}
 
-Some of these options are deprecated and retained for backwards compatibility only.
-Others are used in almost all papers, but again are retained as options to ensure that papers written decades ago will continue to compile without problems.
-If you want to include any other packages, see section~\ref{sec:packages}.
-
-\section{Title page}
-
-If you are using \texttt{mnras\_template.tex} the necessary code for generating the title page, headers and footers is already present.
-Simply edit the title, author list, institutions, abstract and keywords as described below.
-
-\subsection{Title}
-There are two forms of the title: the full version used on the first page, and a short version which is used in the header of other odd-numbered pages (the `running head').
-Enter them with \verb'\title[]{}' like this:
-\begin{verbatim}
-\title[Running head]{Full title of the paper}
-\end{verbatim}
-The full title can be multiple lines (use \verb'\\' to start a new line) and may be as long as necessary, although we encourage authors to use concise titles.
-The running head must be $\le~45$ characters on a single line.
-
-See appendix~\ref{sec:advanced} for more complicated examples.
-
-\subsection{Authors and institutions}
-
-Like the title, there are two forms of author list: the full version which appears on the title page, and a short form which appears in the header of the even-numbered pages.
-Enter them using the \verb'\author[]{}' command.
-
-If the author list is more than one line long, start a new line using \verb'\newauthor'.
-Use \verb'\\' to start the institution list.
-Affiliations for each author should be indicated with a superscript number, and correspond to the list of institutions below the author list.
-
-For example, if I were to write a paper with two coauthors at another institution, one of whom also works at a third location:
-\begin{verbatim}
-\author[K. T. Smith et al.]{
-Keith T. Smith,$^{1}$
-A. N. Other,$^{2}$
-and Third Author$^{2,3}$
-\\
-$^{1}$Affiliation 1\\
-$^{2}$Affiliation 2\\
-$^{3}$Affiliation 3}
-\end{verbatim}
-Affiliations should be in the format `Department, Institution, Street Address, City and Postal Code, Country'.
-
-Email addresses can be inserted with the \verb'\thanks{}' command which adds a title page footnote.
-If you want to list more than one email, put them all in the same \verb'\thanks' and use \verb'\footnotemark[]' to refer to the same footnote multiple times.
-Present addresses (if different to those where the work was performed) can also be added with a \verb'\thanks' command.
-
-\subsection{Abstract and keywords}
-
-The abstract is entered in an \verb'abstract' environment:
-\begin{verbatim}
-\begin{abstract}
-The abstract of the paper.
-\end{abstract}
-\end{verbatim}
-\noindent Note that there is a word limit on the length of abstracts.
-For the current word limit, see the journal instructions to authors$^{\ref{foot:itas}}$.
-
-Immediately following the abstract, a set of keywords is entered in a \verb'keywords' environment:
-\begin{verbatim}
-\begin{keywords}
-keyword 1 -- keyword 2 -- keyword 3
-\end{keywords}
-\end{verbatim}
-\noindent There is a list of permitted keywords, which is agreed between all the major astronomy journals and revised every few years.
-Do \emph{not} make up new keywords!
-For the current list of allowed keywords, see the journal's instructions to authors$^{\ref{foot:itas}}$.
-
-\section{Sections and lists}
-
-Sections and lists are generally the same as in the standard \LaTeX\ classes.
-
-\subsection{Sections}
-\label{sec:sections}
-Sections are entered in the usual way, using \verb'\section{}' and its variants. It is possible to nest up to four section levels:
-\begin{verbatim}
-\section{Main section}
- \subsection{Subsection}
-  \subsubsection{Subsubsection}
-   \paragraph{Lowest level section}
-\end{verbatim}
-\noindent The other \LaTeX\ sectioning commands \verb'\part', \verb'\chapter' and \verb'\subparagraph{}' are deprecated and should not be used.
-
-Some sections are not numbered as part of journal style (e.g. the Acknowledgements).
-To insert an unnumbered section use the `starred' version of the command: \verb'\section*{}'.
-
-See appendix~\ref{sec:advanced} for more complicated examples.
-
-\subsection{Lists}
-
-Two forms of lists can be used in MNRAS -- numbered and unnumbered.
-
-For a numbered list, use the \verb'enumerate' environment:
-\begin{verbatim}
-\begin{enumerate}
- \item First item
- \item Second item
- \item etc.
-\end{enumerate}
-\end{verbatim}
-\noindent which produces
-\begin{enumerate}
- \item First item
- \item Second item
- \item etc.
-\end{enumerate}
-Note that the list uses lowercase Roman numerals, rather than the \LaTeX\ default Arabic numerals.
-
-For an unnumbered list, use the \verb'description' environment without the optional argument:
-\begin{verbatim}
-\begin{description}
- \item First item
- \item Second item
- \item etc.
-\end{description}
-\end{verbatim}
-\noindent which produces
-\begin{description}
- \item First item
- \item Second item
- \item etc.
-\end{description}
-
-Bulleted lists using the \verb'itemize' environment should not be used in MNRAS; it is retained for backwards compatibility only.
-
-\section{Mathematics and symbols}
-
-The MNRAS class mostly adopts standard \LaTeX\ handling of mathematics, which is briefly summarised here.
-See also section~\ref{sec:packages} for packages that support more advanced mathematics.
-
-Mathematics can be inserted into the running text using the syntax \verb'$1+1=2$', which produces $1+1=2$.
-Use this only for short expressions or when referring to mathematical quantities; equations should be entered as described below.
-
-\subsection{Equations}
-Equations should be entered using the \verb'equation' environment, which automatically numbers them:
-
-\begin{verbatim}
-\begin{equation}
- a^2=b^2+c^2
-\end{equation}
-\end{verbatim}
-\noindent which produces
-\begin{equation}
- a^2=b^2+c^2
-\end{equation}
-
-By default, the equations are numbered sequentially throughout the whole paper.
-If a paper has a large number of equations, it may be better to number them by section (2.1, 2.2 etc.).
-To do this, add the command \verb'\numberwithin{equation}{section}' to the preamble.
-
-It is also possible to produce un-numbered equations by using the \LaTeX\ built-in \verb'\['\textellipsis\verb'\]' and \verb'$$'\textellipsis\verb'$$' commands; however MNRAS requires that all equations are numbered, so these commands should be avoided.
-
-\subsection{Special symbols}
-
-\begin{table}
- \caption{Additional commands for special symbols commonly used in astronomy. These can be used anywhere.}
- \label{tab:anysymbols}
- \begin{tabular*}{\columnwidth}{@{}l@{\hspace*{50pt}}l@{\hspace*{50pt}}l@{}}
-  \hline
-  Command & Output & Meaning\\
-  \hline
-  \verb'\sun' & \sun & Sun, solar\\[2pt] % additional height spacing for enhanced symbol legibility
-  \verb'\earth' & \earth & Earth, terrestrial\\[2pt]
-  \verb'\micron' & \micron & microns\\[2pt]
-  \verb'\degr' & \degr & degrees\\[2pt]
-  \verb'\arcmin' & \arcmin & arcminutes\\[2pt]
-  \verb'\arcsec' & \arcsec & arcseconds\\[2pt]
-  \verb'\fdg' & \fdg & fraction of a degree\\[2pt]
-  \verb'\farcm' & \farcm & fraction of an arcminute\\[2pt]
-  \verb'\farcs' & \farcs & fraction of an arcsecond\\[2pt]
-  \verb'\fd' & \fd & fraction of a day\\[2pt]
-  \verb'\fh' & \fh & fraction of an hour\\[2pt]
-  \verb'\fm' & \fm & fraction of a minute\\[2pt]
-  \verb'\fs' & \fs & fraction of a second\\[2pt]
-  \verb'\fp' & \fp & fraction of a period\\[2pt]
-  \verb'\diameter' & \diameter & diameter\\[2pt]
-  \verb'\sq' & \sq & square, Q.E.D.\\[2pt]
-  \hline
- \end{tabular*}
-\end{table}
-
-\begin{table}
- \caption{Additional commands for mathematical symbols. These can only be used in maths mode.}
- \label{tab:mathssymbols}
- \begin{tabular*}{\columnwidth}{l@{\hspace*{40pt}}l@{\hspace*{40pt}}l}
-  \hline
-  Command & Output & Meaning\\
-  \hline
-  \verb'\upi' & $\upi$ & upright pi\\[2pt] % additional height spacing for enhanced symbol legibility
-  \verb'\umu' & $\umu$ & upright mu\\[2pt]
-  \verb'\upartial' & $\upartial$ & upright partial derivative\\[2pt]
-  \verb'\lid' & $\lid$ & less than or equal to\\[2pt]
-  \verb'\gid' & $\gid$ & greater than or equal to\\[2pt]
-  \verb'\la' & $\la$ & less than of order\\[2pt]
-  \verb'\ga' & $\ga$ & greater than of order\\[2pt]
-  \verb'\loa' & $\loa$ & less than approximately\\[2pt]
-  \verb'\goa' & $\goa$ & greater than approximately\\[2pt]
-  \verb'\cor' & $\cor$ & corresponds to\\[2pt]
-  \verb'\sol' & $\sol$ & similar to or less than\\[2pt]
-  \verb'\sog' & $\sog$ & similar to or greater than\\[2pt]
-  \verb'\lse' & $\lse$ & less than or homotopic to \\[2pt]
-  \verb'\gse' & $\gse$ & greater than or homotopic to\\[2pt]
-  \verb'\getsto' & $\getsto$ & from over to\\[2pt]
-  \verb'\grole' & $\grole$ & greater over less\\[2pt]
-  \verb'\leogr' & $\leogr$ & less over greater\\
-  \hline
- \end{tabular*}
-\end{table}
-
-Some additional symbols of common use in astronomy have been added in the MNRAS class.
-These are shown in tables~\ref{tab:anysymbols}--\ref{tab:mathssymbols}.
-The command names are -- as far as possible -- the same as those used in other major astronomy journals.
-
-Many other mathematical symbols are also available, either built into \LaTeX\ or via additional packages.
-If you want to insert a specific symbol but don't know the \LaTeX\ command, we recommend using the Detexify website\footnote{\url{http://detexify.kirelabs.org}}.
-
-Sometimes font or coding limitations mean a symbol may not get smaller when used in sub- or superscripts, and will therefore be displayed at the wrong size.
-There is no need to worry about this as it will be corrected by the typesetter during production.
-
-To produce bold symbols in mathematics, use \verb'\bmath' for simple variables, and the \verb'bm' package for more complex symbols (see section~\ref{sec:packages}).
-Vectors are set in bold italic, using \verb'\mathbfit{}'.
-
-For matrices, use \verb'\mathbfss{}' to produce a bold sans-serif font e.g.
-\mathbfss{H}; this works even outside maths mode, but not all symbols are available (e.g.
-Greek).
-For $\nabla$ (del, used in gradients, divergence etc.) use \verb'$\nabla$'.
-
-\subsection{Ions}
-
-A new \verb'\ion{}{}' command has been added to the class file, for the correct typesetting of ionisation states.
-For example, to typeset singly ionised calcium use \verb'\ion{Ca}{ii}', which produces \ion{Ca}{ii}.
-
-\section{Figures and tables}
-\label{sec:fig_table}
-Figures and tables (collectively called `floats') are mostly the same as built into \LaTeX.
-
-\subsection{Basic examples}
-%\begin{figure}
-% \includegraphics[width=\columnwidth]{example}
-% \caption{An example figure.}
-% \label{fig:example}
-%\end{figure}
-Figures are inserted in the usual way using a \verb'figure' environment and \verb'\includegraphics'. The example Figure~\ref{fig:example} was generated using the code:
-\begin{verbatim}
-\begin{figure}
- \includegraphics[width=\columnwidth]{example}
- \caption{An example figure.}
- \label{fig:example}
-\end{figure}
-\end{verbatim}
-
-\begin{table}
- \caption{An example table.}
- \label{tab:example}
- \begin{tabular}{lcc}
-  \hline
-  Star & Mass & Luminosity\\
-   & $M_{\sun}$ & $L_{\sun}$\\
-  \hline
-  Sun & 1.00 & 1.00\\
-  $\alpha$~Cen~A & 1.10 & 1.52\\
-  $\epsilon$~Eri & 0.82 & 0.34\\
-  \hline
- \end{tabular}
-\end{table}
-The example Table~\ref{tab:example} was generated using the code:
-\begin{verbatim}
-\begin{table}
- \caption{An example table.}
- \label{tab:example}
- \begin{tabular}{lcc}
-  \hline
-  Star & Mass & Luminosity\\
-   & $M_{\sun}$ & $L_{\sun}$\\
-  \hline
-  Sun & 1.00 & 1.00\\
-  $\alpha$~Cen~A & 1.10 & 1.52\\
-  $\epsilon$~Eri & 0.82 & 0.34\\
-  \hline
- \end{tabular}
-\end{table}
-\end{verbatim}
-
-\subsection{Captions and placement}
-Captions go \emph{above} tables but \emph{below} figures, as in the examples above.
-
-The \LaTeX\ float placement commands \verb'[htbp]' are intentionally disabled.
-Layout of figures and tables will be adjusted by the publisher during the production process, so authors should not concern themselves with placement to avoid disappointment and wasted effort.
-Simply place the \LaTeX\ code close to where the figure or table is first mentioned in the text and leave exact placement to the publishers.
-
-By default a figure or table will occupy one column of the page.
-To produce a wider version which covers both columns, use the \verb'figure*' or \verb'table*'  environment.
-
-If a figure or table is too long to fit on a single page it can be split it into several parts.
-Create an additional figure or table which uses \verb'\contcaption{}' instead of \verb'\caption{}'.
-This will automatically correct the numbering and add `\emph{continued}' at the start of the caption.
-\begin{table}
- \contcaption{A table continued from the previous one.}
- \label{tab:continued}
- \begin{tabular}{lcc}
-  \hline
-  Star & Mass & Luminosity\\
-   & $M_{\sun}$ & $L_{\sun}$\\
-  \hline
-  $\tau$~Cet & 0.78 & 0.52\\
-  $\delta$~Pav & 0.99 & 1.22\\
-  $\sigma$~Dra & 0.87 & 0.43\\
-  \hline
- \end{tabular}
-\end{table}
-Table~\ref{tab:continued} was generated using the code:
-
-\begin{verbatim}
-\begin{table}
- \contcaption{A table continued from the previous one.}
- \label{tab:continued}
- \begin{tabular}{lcc}
-  \hline
-  Star & Mass & Luminosity\\
-   & $M_{\sun}$ & $L_{\sun}$\\
-  \hline
-  $\tau$~Cet & 0.78 & 0.52\\
-  $\delta$~Pav & 0.99 & 1.22\\
-  $\sigma$~Dra & 0.87 & 0.43\\
-  \hline
- \end{tabular}
-\end{table}
-\end{verbatim}
-
-To produce a landscape figure or table, use the \verb'pdflscape' package and the \verb'landscape' environment.
-The landscape Table~\ref{tab:landscape} was produced using the code:
-\begin{verbatim}
-\begin{landscape}
- \begin{table}
-  \caption{An example landscape table.}
-  \label{tab:landscape}
-  \begin{tabular}{cccccccccc}
-    \hline
-    Header & Header & ...\\
-    Unit & Unit & ...\\
-    \hline
-    Data & Data & ...\\
-    Data & Data & ...\\
-    ...\\
-    \hline
-  \end{tabular}
- \end{table}
-\end{landscape}
-\end{verbatim}
-Unfortunately this method will force a page break before the table appears.
-More complicated solutions are possible, but authors shouldn't worry about this.
-
-\begin{landscape}
- \begin{table}
-  \caption{An example landscape table.}
-  \label{tab:landscape}
-  \begin{tabular}{cccccccccc}
-    \hline
-    Header & Header & Header & Header & Header & Header & Header & Header & Header & Header\\
-    Unit & Unit & Unit & Unit & Unit & Unit & Unit & Unit & Unit & Unit \\
-    \hline
-    Data & Data & Data & Data & Data & Data & Data & Data & Data & Data\\
-    Data & Data & Data & Data & Data & Data & Data & Data & Data & Data\\
-    Data & Data & Data & Data & Data & Data & Data & Data & Data & Data\\
-    Data & Data & Data & Data & Data & Data & Data & Data & Data & Data\\
-    Data & Data & Data & Data & Data & Data & Data & Data & Data & Data\\
-    Data & Data & Data & Data & Data & Data & Data & Data & Data & Data\\
-    Data & Data & Data & Data & Data & Data & Data & Data & Data & Data\\
-    Data & Data & Data & Data & Data & Data & Data & Data & Data & Data\\
-    \hline
-  \end{tabular}
- \end{table}
-\end{landscape}
-
-\section{References and citations}
-
-\subsection{Cross-referencing}
-
-The usual \LaTeX\ commands \verb'\label{}' and \verb'\ref{}' can be used for cross-referencing within the same paper.
-We recommend that you use these whenever relevant, rather than writing out the section or figure numbers explicitly.
-This ensures that cross-references are updated whenever the numbering changes (e.g. during revision) and provides clickable links (if available in your compiler).
-
-It is best to give each section, figure and table a logical label.
-For example, Table~\ref{tab:mathssymbols} has the label \verb'tab:mathssymbols', whilst section~\ref{sec:packages} has the label \verb'sec:packages'.
-Add the label \emph{after} the section or caption command, as in the examples in sections~\ref{sec:sections} and \ref{sec:fig_table}.
-Enter the cross-reference with a non-breaking space between the type of object and the number, like this: \verb'see Figure~\ref{fig:example}'.
-
-The \verb'\autoref{}' command can be used to automatically fill out the type of object, saving on typing.
-It also causes the link to cover the whole phrase rather than just the number, but for that reason is only suitable for single cross-references rather than ranges.
-For example, \verb'\autoref{tab:journal_abbr}' produces \autoref{tab:journal_abbr}.
-
-\subsection{Citations}
-\label{sec:cite}
-
-MNRAS uses the Harvard -- author (year) -- citation style, e.g. \citet{author2013}.
-This is implemented in \LaTeX\ via the \verb'natbib' package, which in turn is included via the \verb'usenatbib' package option (see section~\ref{sec:options}), which should be used in all papers.
-
-Each entry in the reference list has a `key' (see section~\ref{sec:ref_list}) which is used to generate citations.
-There are two basic \verb'natbib' commands:
-\begin{description}
- \item \verb'\citet{key}' produces an in-text citation: \citet{author2013}
- \item \verb'\citep{key}' produces a bracketed (parenthetical) citation: \citep{author2013}
-\end{description}
-Citations will include clickable links to the relevant entry in the reference list, if supported by your \LaTeX\ compiler.
-
-\defcitealias{smith2014}{Paper~I}
-\begin{table*}
- \caption{Common citation commands, provided by the \texttt{natbib} package.}
- \label{tab:natbib}
- \begin{tabular}{lll}
-  \hline
-  Command & Ouput & Note\\
-  \hline
-  \verb'\citet{key}' & \citet{smith2014} & \\
-  \verb'\citep{key}' & \citep{smith2014} & \\
-  \verb'\citep{key,key2}' & \citep{smith2014,jones2015} & Multiple papers\\
-  \verb'\citet[table 4]{key}' & \citet[table 4]{smith2014} & \\
-  \verb'\citep[see][figure 7]{key}' & \citep[see][figure 7]{smith2014} & \\
-  \verb'\citealt{key}' & \citealt{smith2014} & For use with manual brackets\\
-  \verb'\citeauthor{key}' & \citeauthor{smith2014} & If already cited in close proximity\\
-  \verb'\defcitealias{key}{Paper~I}' &  & Define an alias (doesn't work in floats)\\
-  \verb'\citetalias{key}' & \citetalias{smith2014} & \\
-  \verb'\citepalias{key}' & \citepalias{smith2014} & \\
-  \hline
- \end{tabular}
-\end{table*}
-
-There are a number of other \verb'natbib' commands which can be used for more complicated citations.
-The most commonly used ones are listed in Table~\ref{tab:natbib}.
-For full guidance on their use, consult the \verb'natbib' documentation\footnote{\url{http://www.ctan.org/pkg/natbib}}.
-
-If a reference has several authors, \verb'natbib' will automatically use `et al.' if there are more than two authors.
-However, if a paper has exactly three authors, MNRAS style is to list all three on the first citation and use `et al.' thereafter.
-If you are using \bibtex\ (see section~\ref{sec:ref_list}) then this is handled automatically.
-If not, the \verb'\citet*{}' and \verb'\citep*{}' commands can be used at the first citation to include all of the authors.
-
-\subsection{The list of references}
-\label{sec:ref_list}
-
-It is possible to enter references manually using the usual \LaTeX\ commands, but we strongly encourage authors to use \bibtex\ instead.
-\bibtex\ ensures that the reference list is updated automatically as references are added or removed from the paper, puts them in the correct format, saves on typing, and the same reference file can be used for many different papers -- saving time hunting down reference details.
-An MNRAS \bibtex\ style file, \verb'mnras.bst', is distributed as part of this package.
-The rest of this section will assume you are using \bibtex.
-
-References are entered into a separate \verb'.bib' file in standard \bibtex\ formatting.
-This can be done manually, or there are several software packages which make editing the \verb'.bib' file much easier.
-We particularly recommend \textsc{JabRef}\footnote{\url{http://jabref.sourceforge.net/}}, which works on all major operating systems.
-\bibtex\ entries can be obtained from the NASA Astrophysics Data System\footnote{\label{foot:ads}\url{http://adsabs.harvard.edu}} (ADS) by clicking on `Bibtex entry for this abstract' on any entry.
-Simply copy this into your \verb'.bib' file or into the `BibTeX source' tab in \textsc{JabRef}.
-
-Each entry in the \verb'.bib' file must specify a unique `key' to identify the paper, the format of which is up to the author.
-Simply cite it in the usual way, as described in section~\ref{sec:cite}, using the specified key.
-Compile the paper as usual, but add an extra step to run the \texttt{bibtex} command.
-Consult the documentation for your compiler or latex distribution.
-
-Correct formatting of the reference list will be handled by \bibtex\ in almost all cases, provided that the correct information was entered into the \verb'.bib' file.
-Note that ADS entries are not always correct, particularly for older papers and conference proceedings, so may need to be edited.
-If in doubt, or if you are producing the reference list manually, see the MNRAS instructions to authors$^{\ref{foot:itas}}$ for the current guidelines on how to format the list of references.
-
-\section{Appendices and online material}
-
-To start an appendix, simply place the \verb'\appendix' command before the next \verb'\section{}'.
-This will automatically adjust the section headings, figures, tables, and equations to reflect the fact that they are part of an appendix.
-It is only necessary to enter the \verb'\appendix' command once -- everything after that command is in an appendix.
-Remember that appendices should be placed \textit{after} the list of references.
-
-Unlike other astronomy class files, there are no special commands for online material.
-If your paper has any online material, it should be placed in a separate file.
-See our instructions to authors$^{\ref{foot:itas}}$ for guidance.
-
-\section{Packages and custom commands}
-\label{sec:packages}
-\subsection{Additional packages}
-
-Sometimes authors need to include additional \LaTeX\ packages, which provide extra features.
-For example, the \verb'bm' package provides extra bold maths symbols, whilst the \verb'pdflscape' package adds support for landscape pages.
-Packages can be included by adding the \verb'\usepackage{}' command to the preamble of the document (not the main body).
-
-Please \emph{only include packages which are actually used in the paper}, and include a comment to explain what each one does.
-This will assist the typesetters.
-If you are using \texttt{mnras\_template.tex}, it includes a specific section for this purpose, near the start of the file with the header 'authors - place your own packages here'.
-
-For example, to include \verb'pdflscape', use:
-\begin{verbatim}
-\usepackage{pdflscape}	% Landscape pages
-\end{verbatim}
-Consult the documentation for that package for instructions on how to use the additional features.
-
-\subsection{Custom commands}
-
-Authors should avoid duplicating or redefining commands which are already available in \LaTeX\ or \verb'mnras.cls'.
-However it may sometimes be necessary to introduce a custom command e.g. as a shortcut while writing the paper.
-
-Please \emph{only include commands which are actually used in the paper}, and include a comment to explain what each one does.
-This will assist the typesetters.
-Use \verb'\newcommand', \emph{not} \verb'\def', as this will avoid accidentally overwriting existing commands.
-Place custom commands in the preamble of the document (not the main body).
-If you are using \texttt{mnras\_template.tex}, it includes a specific section for this purpose, near the start of the file with the header 'authors - place your own commands here'.
-
-As an example, a shortcut for the unit \kms can be defined like this:
-\begin{verbatim}
-\newcommand{\kms}{\,km\,s$^{-1}$}	% kilometres per second
-\end{verbatim}
-Velocities can then be written as e.g. \verb'2.3\kms' which produces 2.3\kms.
-Similar shortcuts can be used for frequently quoted object designations.
-
-\section*{Acknowledgements}
-% Entry for the table of contents, for this guide only
-\addcontentsline{toc}{section}{Acknowledgements}
-
-This guide replaces an earlier one originally prepared by Cambridge University Press (CUP) in 1994, and last updated in 2002 by Blackwell Publishing.
-Some code segments are reproduced from, and some examples are based upon, that guide.
-The authors were: A.~Woollatt, M.~Reed, R.~Mulvey, K.~Matthews, D.~Starling, Y.~Yu, A.~Richardson (all CUP), and Penny~Smith, N.~Thompson and Gregor~Hutton (all Blackwell), whose work is gratefully acknowledged.
-
-The accompanying \bibtex\ style file was written by John Sleath, Tim Jenness and Norman Gray, without whom \bibtex\ support would not have been possible.
-
-Some special symbols in tables~\ref{tab:anysymbols}--\ref{tab:mathssymbols} were taken from the Springer Verlag \textit{Astronomy \& Astrophysics} \LaTeX\ class, with their permission.
-
-KTS thanks Nelson Beebe (University of Utah) for helpful advice regarding CTAN.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Acknowledgements}
+The authors thank Mateusz Ruszkowski and Ellen G. Zweibel for insightful comments.\
+We thank Peter Predehl for providing the range of observed X-ray intensity in \Cref{fig__xray_0.8keV_angle_000}.\
+A part of the simulations are performed and analyzed using computing resources\
+operated by the National Center for High-Performance Computing (NCHC).
+HYKY acknowledges support from\
+Yushan Scholar Program of the Ministry of Education of Taiwan\
+and\
+Ministry of Science and Technology of Taiwan (MOST 109-2112-M-007-037-MY3).
+HS acknowledges\
+funding support from the Jade Mountain Young Scholar Award No. NTU-109V0201,\
+sponsored by the Ministry of Education, Taiwan.\
+This research is partially supported by the Ministry of Science and\
+Technology of Taiwan (MOST) under grants MOST 107-2119-M-002-036-MY3\
+and MOST 108-2112-M-002-023-MY3, and the NTU\
+Core Consortium project under grants NTU-CC-108L893401 and\
+NTU-CC-108L893402.
 
 \section*{Data Availability}
-
-The inclusion of a Data Availability Statement is a requirement for articles published in MNRAS.
-Data Availability Statements provide a standardised format for readers to understand the availability of data underlying the research results described in the article.
-The statement may refer to original data generated in the course of the study or to third-party data analysed in the article.
-The statement should describe and provide means of access, where possible, by linking to the data or providing the required accession numbers for the relevant databases or DOIs.
+The data underlying this article are available in the article and in its online supplementary material.
 
@@
 
-%\bibliographystyle{mnras}
-%\bibliography{example} % if your bibtex file is called example.bib
-
-% Alternatively you could enter them by hand, like this:
-\begin{thebibliography}{99}
-\bibitem[\protect\citeauthoryear{Author}{2013}]{author2013}
-Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
-\bibitem[\protect\citeauthoryear{Jones}{2015}]{jones2015}
-Jones C.~D., 2015, Journal of Interesting Stuff, 17, 198
-\bibitem[\protect\citeauthoryear{Smith}{2014}]{smith2014}
-Smith A.~B., 2014, The Example Journal, 12, 345 (Paper I)
-\end{thebibliography}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\bibliographystyle{mnras}
+\bibliography{paper} % if your bibtex file is called example.bib
 
@@
 
-\appendix
-\section{Journal abbreviations}
-\label{sec:abbreviations}
-Abbreviations for cited journals can be accessed using the commands listed in table~\ref{tab:journal_abbr}.
-Although some of these may appear to be outdated or rarely cited, they have been selected to be compatible with the \bibtex\ output by the NASA Astrophysics Data System$^{\ref{foot:ads}}$, commands used by other astronomy journals, and with additional entries for journals with non-standard abbreviations in MNRAS.
-For journals which are not on this list, see our instructions to authors$^{\ref{foot:itas}}$ for guidance on how to abbreviate titles.
-
-\begin{table*}
-\caption{Commands for abbreviated journal names, see appendix~\ref{sec:abbreviations}.}
-\label{tab:journal_abbr}
-\begin{tabular}{@{}l@{\:}l@{\:}l@{}} % manual @ spacing to prevent this being too wide for a page
-\hline
-Command & Output & Journal name\\
-\hline
-\verb'\aap' or \verb'\astap' & \aap & Astronomy and Astrophysics$^a$\\
-\verb'\aapr' & \aapr & The Astronomy and Astrophysics Review\\
-\verb'\aaps' & \aaps  & Astronomy and Astrophysics Supplement Series\\
-\verb'\actaa' & \actaa & Acta Astronomica\\
-\verb'\afz' & \afz & Astrofizika\\
-\verb'\aj' & \aj & The Astronomical Journal\\
-\verb'\ao' or \verb'\applopt' & \ao & Applied Optics\\
-\verb'\aplett' & \aplett & Astrophysics Letters\\
-\verb'\apj' & \apj & The Astrophysical Journal\\
-\verb'\apjl' or \verb'\apjlett' & \apjl & The Astrophysical Journal Letters$^a$\\
-\verb'\apjs' or \verb'\apjsupp' & \apjs & The Astrophysical Journal Supplement Series\\
-\verb'\apss' & \apss & Astrophysics and Space Science\\
-\verb'\araa' & \araa & Annual Review of Astronomy and Astrophysics\\
-\verb'\arep' & \arep & Astronomy Reports$^b$\\
-\verb'\aspc' & \aspc & Astronomical Society of the Pacific Conference Series\\
-\verb'\azh' & \azh & Astronomicheskii Zhurnal$^c$\\
-\verb'\baas' & \baas & Bulletin of the American Astronomical Society\\
-\verb'\bac' & \bac & Bulletin of the Astronomical Institutes of Czechoslovakia\\
-\verb'\bain' & \bain & Bull. Astron. Inst. Netherlands\\
-\verb'\caa' & \caa & Chinese Astronomy and Astrophysics\\
-\verb'\cjaa' & \cjaa & Chinese Journal of Astronomy and Astrophysics\\
-\verb'\fcp' & \fcp & Fundamentals of Cosmic Physics\\
-\verb'\gca' & \gca & Geochimica Cosmochimica Acta\\
-\verb'\grl' & \grl & Geophysics Research Letters\\
-\verb'\iaucirc' & \iaucirc & International Astronomical Union Circulars\\
-\verb'\icarus' & \icarus & Icarus\\
-\verb'\japa' & \japa & Journal of Astrophysics and Astronomy\\
-\verb'\jcap' & \jcap & Journal of Cosmology and Astroparticle Physics\\
-\verb'\jcp' & \jcp & Journal of Chemical Physics\\
-\verb'\jgr' & \jgr & Journal of Geophysics Research\\
-\verb'\jqsrt' & \jqsrt & Journal of Quantitiative Spectroscopy and Radiative Transfer\\
-\verb'\jrasc' & \jrasc & Journal of the Royal Astronomical Society of Canada\\
-\verb'\memras' & \memras & Memoirs of the Royal Astronomical Society\\
-\verb'\memsai' & \memsai & Memoire della Societa Astronomica Italiana\\
-\verb'\mnassa' & \mnassa & Monthly Notes of the Astronomical Society of Southern Africa\\
-\verb'\mnras' & \mnras & Monthly Notices of the Royal Astronomical Society$^a$\\
-\verb'\na' & \na & New Astronomy\\
-\verb'\nar' & \nar & New Astronomy Review\\
-\verb'\nat' & \nat & Nature\\
-\verb'\nphysa' & \nphysa & Nuclear Physics A\\
-\verb'\pra' & \pra & Physical Review A: Atomic, molecular, and optical physics\\
-\verb'\prb' & \prb & Physical Review B: Condensed matter and materials physics\\
-\verb'\prc' & \prc & Physical Review C: Nuclear physics\\
-\verb'\prd' & \prd & Physical Review D: Particles, fields, gravitation, and cosmology\\
-\verb'\pre' & \pre & Physical Review E: Statistical, nonlinear, and soft matter physics\\
-\verb'\prl' & \prl & Physical Review Letters\\
-\verb'\pasa' & \pasa & Publications of the Astronomical Society of Australia\\
-\verb'\pasp' & \pasp & Publications of the Astronomical Society of the Pacific\\
-\verb'\pasj' & \pasj & Publications of the Astronomical Society of Japan\\
-\verb'\physrep' & \physrep & Physics Reports\\
-\verb'\physscr' & \physscr & Physica Scripta\\
-\verb'\planss' & \planss & Planetary and Space Science\\
-\verb'\procspie' & \procspie & Proceedings of the Society of Photo-Optical Instrumentation Engineers\\
-\verb'\rmxaa' & \rmxaa & Revista Mexicana de Astronomia y Astrofisica\\
-\verb'\qjras' & \qjras & Quarterly Journal of the Royal Astronomical Society\\
-\verb'\sci' & \sci & Science\\
-\verb'\skytel' & \skytel & Sky and Telescope\\
-\verb'\solphys' & \solphys & Solar Physics\\
-\verb'\sovast' & \sovast & Soviet Astronomy$^b$\\
-\verb'\ssr' & \ssr & Space Science Reviews\\
-\verb'\zap' & \zap & Zeitschrift fuer Astrophysik\\
-\hline
-\multicolumn{3}{l}{$^a$ Letters are designated by an L at the start of the page number, not in the journal name}\\
-\multicolumn{3}{l}{\footnotesize$^b$ In 1992 the English translation of this journal changed its name from Soviet Astronomy to Astronomy Reports}\\
-\multicolumn{3}{l}{\footnotesize$^c$ Including the English translation Astronomy Letters}\\
-\end{tabular}
-\end{table*}
-
-\clearpage % to avoid the long table breaking up the formatting examples
-\section{Advanced formatting examples}
-\label{sec:advanced}
-
-Sometimes formatting doesn't behave exactly as expected when used in titles or section headings, and must be modified to obtain the correct appearance.
-Generally the publishers can fix these problems during the typesetting process after a paper is accepted, but authors may wish to adjust these themselves to minimise the possibility of errors and/or for the benefit of the refereeing process.
-Below are some examples of output, followed by the \LaTeX\ code which produces them.
-
-Most mathematics and text formatting works as expected, but some commands might not be the correct size, bold or italic.
-If so they can be finessed by hand, as in the bold mathematics here:
-\boxit{\huge\bf \textit{Herschel} observations of galaxies at $\bm{\delta > 60\degr}$}
-\begin{verbatim}
-\title{\textit{Herschel} observations of galaxies at
- $\bm{\delta > 60\degr}$}
-\end{verbatim}
-
-Most fonts do not provide bold and italic versions of small capitals, so the \verb'\ion{}{}' command doesn't produce the expected output in headings.
-The effect has to be `faked' using font size commands, remembering that the running head is a different style:
-\boxit{\huge\bf Abundances in H\,{\Large \textbf{II}} regions}
-\begin{verbatim}
-\title
-[Abundances in H\,{\normalsize \textit{II}} regions]
-{Abundances in H\,{\Large \textbf{II}} regions}
-\end{verbatim}
-
-Complex mathematics can cause problems with links, so might require adding a less formatted short version of the heading:
-\boxit{\bf 2\quad FINDING Mg\,{\sevensize II} ABSORBERS AT $\bm{z > 2}$}
-\begin{verbatim}
-\section
-[Finding Mg II absorbers at z > 2]
-{Finding M\lowercase{g}\,{\sevensize II} absorbers
- at $\lowercase{\bm{z > 2}}$}
-\end{verbatim}
-
-Using square brackets in headings can cause additional linking problems, which are solved by wrapping them in \{\textellipsis\}:
-\boxit{\bf 2.1\quad [C\,{\sevensize II}] 158$\bmath{\umu}$m emission}
-\begin{verbatim}
-\subsection
-[{[C II] 158$\umu$m emission}]
-{[C\,{\sevensize II}] 158$\bmath{\umu}$m
- emission}
-\end{verbatim}
-
-Use \verb'\text{}' (not \verb'\rm') for non-variables in mathematics, which preserves the formatting of the surrounding text.
-For the same reasons, use \verb'\textit{}' for italics (not \verb'\it').
-\boxit{\bf 3.1\quad Measuring $\bm{T}_\text{eff}$ from \textit{Gaia} photometry}
-\begin{verbatim}
-\subsection{Measuring $\bm{T}_\text{eff}$ from
- \textit{Gaia} photometry}
-\end{verbatim}
-
-\section{Additional commands for editors only}
-The following commands are available for the use of editors and production staff only.
-They should not be used (or modified in the template) by authors.
-
-\begin{description}
- \item \verb'\maketitle' inserts the title, authors and institution list in the correct formatting.
- \item \verb'\nokeywords' tidies up the spacing if there are no keywords, but authors should always enter at least one.
- \item \verb'\volume{}' sets the volume number (default is 000)
- \item \verb'\pagerange{}' sets the page range. The standard template generates this automatically, starting from 1.
- \item \verb'\bsp' adds the `This paper has been typeset\textellipsis' comment at the end of the paper.
-The command name refers to Blackwell Science Publishing, who were the publishers at the time when MNRAS began accepting \LaTeX\ submissions in 1993.
- \item \verb'\mniiiauth{}' used by the \bibtex\ style to handle MNRAS style for citing papers with three authors. It should not be used manually.
- \item \verb'\eprint{}' used by the \bibtex\ style for citing arXiv eprints.
- \item \verb'\doi{}' used by the \bibtex\ style for citing Digital Object Identifiers.
-\end{description}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Don't change these lines
-\bsp	% typesetting comment
-\label{lastpage}
 \end{document}

### 2022-03-14 mnras_guide.tex
update

@@
 \usepackage{orcidlink}
+\usepackage{url}
 \usepackage{cleveref}
@@
 
-  The density profile of \Cref{disc-atm-sys} is shown in \Cref{fig__initial-density-profile}.\
+  The density profile of \Cref{disc-atm-sys} is shown in Fig. \ref{fig__initial-density-profile}.\
   Beyond the core radius ($\sim 2 \text{ kpc}$) the gaseous density decreases rapidly as a power-law.
 
-  The density profile of \Cref{disc-atm-sys} is shown in \Cref{fig__initial-density-profile}\
+  The density profile of \Cref{disc-atm-sys} is shown in Fig. \ref{fig__initial-density-profile}\
   and compared to the observed result \citep{Miller_2013} beyond 1 kpc.\
@@
   In this way, we plot the volume filling factor as a function of\
-  initial number density within the disc without the jet source in \Cref{fig__numberDensityHistogram},\
+  initial number density within the disc without the jet source in Fig. \ref{fig__numberDensityHistogram},\
   and show a close-up view of the\
   pressure, temperature, and number density slices
-  in the y-z plane through the center of the disc in \Cref{fig__zoom-in-disc} .
+  in the y-z plane through the center of the disc in Fig. \ref{fig__zoom-in-disc} .
 
@@
 
- \Cref{fig__jetI5+ismSeed3-45deg} shows\
+ Fig. \ref{fig__jetI5+ismSeed3-45deg} shows\
  the slices of pressure (top), temperature (middle), number density (bottom)\
@@
 
- The fiducial run (\Cref{fig__jetI5+ismSeed3-45deg-a})\
+ The fiducial run (Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
  with the initial condition specified in Section \ref{Methodology}\
@@
 
- The temperature profile (left middle panel in \Cref{fig__profile}) along the positive z-axis in\
- \Cref{fig__jetI5+ismSeed3-45deg} indicates that\
- the smooth region (purple band in \Cref{fig__profile}) emitting X-ray\
+ The temperature profile (left middle panel in Fig. \ref{fig__profile}) along the positive z-axis in\
+ Fig. \ref{fig__jetI5+ismSeed3-45deg} indicates that\
+ the smooth region (purple band in Fig. \ref{fig__profile}) emitting X-ray\
  is around 0.3-0.5 keV, similar to that observed by \citet{Miller2016} and \citet{Kataoka2018}.
@@
  The most interesting finding is that there are innermost bubbles\
- (dashed box in the top panel of \Cref{fig__jetI5+ismSeed3-45deg-a})\
+ (dashed box in the top panel of Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
  extending out from the GC on either side of the thin disk.\
@@
 
- Moreover, the close-up view (right column in \Cref{fig__profile})\
- of profiles and slices (\Cref{fig__innerbubbles})\
+ Moreover, the close-up view (right column in Fig. \ref{fig__profile})\
+ of profiles and slices (Fig. \ref{fig__innerbubbles})\
  demonstrates that the pressure rises dramatically outward across\
@@
 
- \Cref{fig__jetI5+ismSeed3-45deg} shows the slices of various gas properties at $t=12.39$ Myr,\
+ Fig. \ref{fig__jetI5+ismSeed3-45deg} shows the slices of various gas properties at $t=12.39$ Myr,\
  including pressure (top), temperature (middle),\
@@
  %To explore how the disk affects the formation of the Galactic bubbles,\
- We compare the clumpy disk (\Cref{fig__jetI5+ismSeed3-45deg-a})\
- with the smooth disc (\Cref{fig__jetI5+ismSeed3-45deg-b}),\
- specified by the initial density profile shown in \Cref{fig__initial-density-profile},\
+ We compare the clumpy disk (Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
+ with the smooth disc (Fig. \ref{fig__jetI5+ismSeed3-45deg-b}),\
+ specified by the initial density profile shown in Fig. \ref{fig__initial-density-profile},\
  in a stratified atmosphere.\
@@
  on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
- in an uniform atmosphere (\Cref{fig__jetI5+ismSeed3-45deg-c}) is spherical-shape,\
+ in an uniform atmosphere (Fig. \ref{fig__jetI5+ismSeed3-45deg-c}) is spherical-shape,\
  suggesting the stratification facilitates the outermost bubbles elongation significantly.\
- Also, \Cref{fig__jetI5+ismSeed3-45deg-c,fig__jetI5+ismSeed3-45deg-d}\
+ Also, Fig. \ref{fig__jetI5+ismSeed3-45deg-c,fig__jetI5+ismSeed3-45deg-d}\
  reveal that the development of the innermost bubbles\
@@
 
- \begin{figure}
+ \begin{figure}%
+      \captionsetup[subfigure]{labelformat=simple}
       \begin{subfigure}[b]{0.2\linewidth}%
-         \centering%
          \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-a}%
+         \caption{}%
          \label{fig__jetI5+ismSeed3-45deg-a}%
-         \hspace{2pt}%
       \end{subfigure}%
+      \hspace{10pt}%
       \begin{subfigure}[b]{0.2\linewidth}%
-         \centering%
          \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-b}%
+         \caption{}%
          \label{fig__jetI5+ismSeed3-45deg-b}%
-         \hspace{2pt}%
       \end{subfigure}%
+      \hspace{-2pt}%
       \begin{subfigure}[b]{0.2\linewidth}%
-         \centering%
          \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-c}%
+         \caption{}%
          \label{fig__jetI5+ismSeed3-45deg-c}%
-         \hspace{2pt}%
       \end{subfigure}%
+      \hspace{-2pt}%
       \begin{subfigure}[b]{0.2\linewidth}%
-         \centering%
          \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-d}%
+         \caption{}%
          \label{fig__jetI5+ismSeed3-45deg-d}%
      \end{subfigure}%
- \end{figure}
-
-%\begin{figure}%
-%  \centering%
-%  \subfigure[][]%
-%    {%
-%      \includegraphics[height=10.1cm]{figures/fig__jetI5+ismSeed3-45deg-a}%
-%      \label{fig__jetI5+ismSeed3-45deg-a}%
-%    }%
-%  \hspace{2pt}%
-%  \subfigure[][]%
-%    {%
-%      \includegraphics[height=10.1cm]{figures/fig__jetI5+ismSeed3-45deg-b}%
-%      \label{fig__jetI5+ismSeed3-45deg-b}%
-%    }%
-%  \hspace{2pt}%
-%  \subfigure[][]%
-%    {%
-%      \includegraphics[height=10.1cm]{figures/fig__jetI5+ismSeed3-45deg-c}%
-%      \label{fig__jetI5+ismSeed3-45deg-c}%
-%    }%
-%  \hspace{2pt}%
-%  \subfigure[][]%
-%    {%
-%      \includegraphics[height=10.1cm]{figures/fig__jetI5+ismSeed3-45deg-d}%
-%      \label{fig__jetI5+ismSeed3-45deg-d}%
-%    }%
-%  \caption{
-%             The slices of pressure (top), temperature (middle), and number density (bottom)\
-%             at the end of simulation $t=12.39$ Myr.\
-%             The slices pass through a bipolar jet source injecting along $z=-y$ direction\
-%             for a duration $t=0$--$1.2$ Myr.\
-%             Comparison between the clumpy (column a)\
-%             and the smooth disc (column b) in a stratified atmosphere\
-%             shows that the initial density distribution of the dense disc has an insignificant effect\
-%             on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
-%             in an uniform atmosphere (column c) is spherical-shape,\
-%             suggesting the stratification facilitates the outermost bubbles elongation significantly.\
-%             Also, the two rightmost columns reveal that the development of the innermost bubbles\
-%             is always associated with the disc, without the disc (column d),\
-%             the outermost bubbles and the turbulent plasma will be oblique,
-%             indicating the dense disc is crucial for\
-%             the symmetry of the Galactic bubbles and for the innermost bubbles formation.
-%  }%
-%  \label{fig__jetI5+ismSeed3-45deg}%
-%\end{figure}%
-
-%\begin{figure}%
-%  \centering%
-%  \subfigure[][]%
-%    {%
-%      \includegraphics[height=7cm]{figures/fig__profile-1.png}%
-%      \label{fig__profile-1}%
-%    }%
-%  \hspace{2pt}%
-%  \subfigure[][]%
-%    {%
-%      \includegraphics[height=7cm]{figures/fig__profile-2.png}%
-%      \label{fig__profile-2}%
-%    }%
-%    \caption{
-%             Left: the profiles of pressure (top), temperature (middle),\
-%             and number density (bottom)\
-%             along the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.
-%             Right: the close-up view of the profiles in the yellow band.\
-%             The sharp pressure jump at $z=3.62$ kpc\
-%             indicates that the innermost bubbles\
-%             (dashed box in the top panel in \Cref{fig__jetI5+ismSeed3-45deg-a})\
-%             are an expanding reverse shock.
-%     }
-%    \label{fig__profile}
-%  \end{figure}
+      \caption{
+             The slices of pressure (top), temperature (middle), and number density (bottom)\
+             at the end of simulation $t=12.39$ Myr.\
+             The slices pass through a bipolar jet source injecting along $z=-y$ direction\
+             for a duration $t=0$--$1.2$ Myr.\
+             Comparison between the clumpy (column a)\
+             and the smooth disc (column b) in a stratified atmosphere\
+             shows that the initial density distribution of the dense disc has an insignificant effect\
+             on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
+             in an uniform atmosphere (column c) is spherical-shape,\
+             suggesting the stratification facilitates the outermost bubbles elongation significantly.\
+             Also, the two rightmost columns reveal that the development of the innermost bubbles\
+             is always associated with the disc, without the disc (column d),\
+             the outermost bubbles and the turbulent plasma will be oblique,
+             indicating the dense disc is crucial for\
+             the symmetry of the Galactic bubbles and for the innermost bubbles formation.
+      }
+      \label{fig__jetI5+ismSeed3-45deg}
+ \end{figure}%
+
+ \begin{figure}%
+      \begin{subfigure}[t]{0.5\linewidth}%
+         \includegraphics[height=8cm]{figures/fig__profile-1.png}%
+         \label{fig__profile-1}%
+      \end{subfigure}%
+      \hspace{4pt}
+      \begin{subfigure}[t]{0.5\linewidth}%
+         \includegraphics[height=8cm]{figures/fig__profile-2.png}%
+         \label{fig__profile-2}%
+      \end{subfigure}%
+      \caption{
+             Left: the profiles of pressure (top), temperature (middle),\
+             and number density (bottom)\
+             along the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.
+             Right: the close-up view of the profiles in the yellow band.\
+             The sharp pressure jump at $z=3.62$ kpc\
+             indicates that the innermost bubbles\
+             (dashed box in the top panel in \Cref{fig__jetI5+ismSeed3-45deg-a})\
+             are an expanding reverse shock.
+      }%
+      \label{fig__profile}%
+ \end{figure}%
 
@@
 
-  \Cref{fig__xray_0.8keV_angle_000} shows\
+  Fig. \ref{fig__xray_0.8keV_angle_000} shows\
   the comparison between simulated (top) and observed (bottom) all-sky map\
@@
 
-  \Cref{fig__x-ray-profile-0.8keV-000} displays the simulated count rate profiles (red)\
-  in the same energy band as \Cref{fig__xray_0.8keV_angle_000}\
+  Fig. \ref{fig__x-ray-profile-0.8keV-000} displays the simulated count rate profiles (red)\
+  in the same energy band as Fig. \ref{fig__xray_0.8keV_angle_000}\
   cut at various galactic latitudes (as labelled), compared with the observation (black).\
-  \Cref{fig_xray-map} is quite revealing in several ways.\
+  Fig. \ref{fig_xray-map} is quite revealing in several ways.\
 
@@
 
-  Second, as shown in \Cref{fig__jetI5+ismSeed3-45deg},\
+  Second, as shown in Fig. \ref{fig__jetI5+ismSeed3-45deg},\
   the half-width of the outermost bubbles is around 7 kpc,\
   corresponding to an half angular width $\sin^{-1}(7 \text{ kpc}/R_{\odot})\sim122^{\circ}$,\
-  which is as wide as the eROSITA bubbles in the simulated X-ray map (top panel in \Cref{fig__xray_0.8keV_angle_000}).\
+  which is as wide as the eROSITA bubbles in the simulated X-ray map\
+  (top panel in Fig. \ref{fig__xray_0.8keV_angle_000}).\
   We therefore suggest that the eROSITA bubble shells are a signature of compressed forward shocks\
@@
   Third, the innermost bubbles\
-  shown in \Cref{fig__jetI5+ismSeed3-45deg},\
+  shown in Fig. \ref{fig__jetI5+ismSeed3-45deg},\
   even though with high column density, are invisible in the simulated X-ray map as\
   the temperature of the innermost bubbles is around $1$--$10$ eV\
-  (see the temperature profile in \Cref{fig__profile}).\
+  (see the temperature profile in Fig. \ref{fig__profile}).\
   Consequently, the X-ray emission within the innermost bubbles
@@
 
+ \begin{figure*}%
+      \begin{subfigure}[t]{\textwidth}%
+         \centering%
+         \includegraphics[width=0.9\textwidth]{figures/fig__xraymap.png}%
+         \caption{
+               (A) Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
+               (photons s$^{-1}$ deg$^{-2}$) in the 0.6--1.0 keV range.\
+               Throughout this paper we show sky maps\
+               in Galactic coordinates centered on the Galactic center using a Hammer-Aitoff projection,\
+               and observed from the solar system.\
+               The red arrow at the center of the\
+               top panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
+               to the disc normal in 1.2 Myr.
+         }%
+         \label{fig__xray_0.8keV_angle_000}%
+         \end{subfigure}%
+         \hspace{4pt}%
+      \begin{subfigure}[t]{\textwidth}%
+         \centering%
+         \includegraphics[width=0.9\textwidth]{figures/fig__xray-profile-0.8keV-000.png}%
+         \caption{
+               (B) Comparison of simulated (red) and observed (black; \citealt{Predehl2020}) one-dimensional\
+               count rate profiles in the same energy band as Fig. \ref{fig__xray_0.8keV_angle_000},\
+               cut at various galactic latitudes (as labelled).]
+         }%
+         \label{fig__x-ray-profile-0.8keV-000}%
+      \end{subfigure}%
+      \caption{}%
+      \label{fig_xray-map}
+ \end{figure*}%
+
 \subsection{Gamma-ray and microwave spectra: constraint on the CRe spectral index}
@@
 
-\Cref{fig__gammaRaySynchtronSpectrum} shows the simulated microwave (left)\
+Fig. \ref{fig__gammaRaySynchtronSpectrum} shows the simulated microwave (left)\
 and gamma-ray (right) spectra averaged over the different patches (shown in the legends) of the sky.\
@@
 
- \Cref{fig__gammaRay-map} shows the simulated gamma-ray photon flux with a CRe power-law index 2.4\
+ Fig. \ref{fig__gammaRay-map} shows the simulated gamma-ray photon flux with a CRe power-law index 2.4\
  compared with the observed one\
@@
  Finally, the comparison between\
- \Cref{fig__jetI5+ismSeed3-45deg}\
+ Fig. \ref{fig__jetI5+ismSeed3-45deg}\
  and\
- \Cref{fig__jetI5+ismSeed3-45deg-CR}\
+ Fig. \ref{fig__jetI5+ismSeed3-45deg-CR}\
  shows that the CR pressure\
@@
      Comparison between\
-     gas pressure (\Cref{fig__jetI5+ismSeed3-45deg}) and cosmic ray pressure\
+     gas pressure (Fig. \ref{fig__jetI5+ismSeed3-45deg}) and cosmic ray pressure\
      shows that
@@
 The authors thank Mateusz Ruszkowski and Ellen G. Zweibel for insightful comments.\
-We thank Peter Predehl for providing the range of observed X-ray intensity in \Cref{fig__xray_0.8keV_angle_000}.\
+We thank Peter Predehl for providing the range of observed X-ray intensity in Fig. \ref{fig__xray_0.8keV_angle_000}.\
 A part of the simulations are performed and analyzed using computing resources\

### 2022-03-14 mnras_guide.tex
update

@@
 \usepackage{natbib}
-\bibliographystyle{abbrvnat}
+\bibliographystyle{mnras}
 \setcitestyle{authoryear,open={(},close={)}}
@@
 \orcidlink{https://orcid.org/0000-0003-2654-8763}%
-\\\\%
+\\\\
 $^{1}$Institute of Astrophysics, National Taiwan University, Taipei 10617, Taiwan\\
@@
 
-%  \begin{figure*}[]
-%    \subfigure[(A) Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
-%               (photons s$^{-1}$ deg$^{-2}$) in the 0.6--1.0 keV range.\
-%               Throughout this paper we show sky maps\
-%               in Galactic coordinates centered on the Galactic center using a Hammer-Aitoff projection,\
-%               and observed from the solar system.\
-%               The red arrow at the center of the\
-%               top panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
-%               to the disc normal in 1.2 Myr.]
-%     {
-%      \includegraphics[width=0.8\linewidth]{figures/fig__xraymap.png}
-%      \label{fig__xray_0.8keV_angle_000}
-%     }
-%    \subfigure[(B) Comparison of simulated (red) and observed (black; \citealt{Predehl2020}) one-dimensional\
-%               count rate profiles in the same energy band as \Cref{fig__xray_0.8keV_angle_000},\
-%               cut at various galactic latitudes (as labelled).]
-%     {
-%      \includegraphics[width=0.8\linewidth]{figures/fig__xray-profile-0.8keV-000.png}
-%      \label{fig__x-ray-profile-0.8keV-000}
-%     }
-%    \caption{}
-%    \label{fig_xray-map}
-%  \end{figure*}
-
  \begin{figure*}%
@@
          \centering%
-         \includegraphics[width=0.9\textwidth]{figures/fig__xraymap.png}%
+         \includegraphics[width=0.85\textwidth]{figures/fig__xraymap.png}%
          \caption{
-               (A) Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
+               Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
                (photons s$^{-1}$ deg$^{-2}$) in the 0.6--1.0 keV range.\
@@
          \centering%
-         \includegraphics[width=0.9\textwidth]{figures/fig__xray-profile-0.8keV-000.png}%
+         \includegraphics[width=0.85\textwidth]{figures/fig__xray-profile-0.8keV-000.png}%
          \caption{
-               (B) Comparison of simulated (red) and observed (black; \citealt{Predehl2020}) one-dimensional\
+               Comparison of simulated (red) and observed (black; \citealt{Predehl2020}) one-dimensional\
                count rate profiles in the same energy band as Fig. \ref{fig__xray_0.8keV_angle_000},\
-               cut at various galactic latitudes (as labelled).]
+               cut at various galactic latitudes (as labelled).
          }%

### 2022-03-14 mnras_guide.tex
update

@@
 
-  The density profile of \Cref{disc-atm-sys} is shown in Fig. \ref{fig__initial-density-profile}\
-  and compared to the observed result \citep{Miller_2013} beyond 1 kpc.\
-
-  Note that there is an difficulty in disentangling the contribution\
-  of the Local Bubble, a supernova remnant in which the Solar System is embedded \citep{Snowden1990},\
-  and the contribution from solar wind charge-exchange processes, which produce soft\
-  X-ray emission throughout the Solar System. As a result, the density profile of the Galactic halo remains unclear\
-  \citep{BlandHawthorn2016}.
+%  The density profile of \Cref{disc-atm-sys} is shown in Fig. \ref{fig__initial-density-profile}\
+%  and compared to the observed result \citep{Miller_2013} beyond 1 kpc.\
+%
+%  Note that there is an difficulty in disentangling the contribution\
+%  of the Local Bubble, a supernova remnant in which the Solar System is embedded \citep{Snowden1990},\
+%  and the contribution from solar wind charge-exchange processes, which produce soft\
+%  X-ray emission throughout the Solar System. As a result, the density profile of the Galactic halo remains unclear\
+%  \citep{BlandHawthorn2016}.
 

### 2022-03-14 mnras_guide.tex
update

@@
   National Taiwan University\
-  (Schive et al. \citeyear{gamer-1}, \citeyear{gamer-2}; \citeauthor{tseng2021} \citeyear{tseng2021})\
+  (\citeauthor{gamer-1} \citeyear{gamer-1}, \citeyear{gamer-2}; \citeauthor{tseng2021} \citeyear{tseng2021})\
   to carry out the simulations of the Galactic bubbles by CR and relativistic fluid injections from the GC.
@@
 
-  The set of \Cref{governing-eq} is closed by using the Taub-Mathews equation of state \citep{Taub,TM_EOS}\
+  The set of Eq. \ref{governing-eq} is closed by using the Taub-Mathews equation of state \citep{Taub,TM_EOS}\
   that approximates the exact EoS \citep{Synge} for ultra-relativistically\
@@
 
-  The density profile of \Cref{disc-atm-sys} is shown in Fig. \ref{fig__initial-density-profile}.\
+  The density profile of Eq. \ref{disc-atm-sys} is shown in Fig. \ref{fig__initial-density-profile}.\
   Beyond the core radius ($\sim 2 \text{ kpc}$) the gaseous density decreases rapidly as a power-law.
@@
 
-\begin{table*}[t]
+\begin{table*}
 \raggedright
@@
  Fig. \ref{fig__jetI5+ismSeed3-45deg} indicates that\
- the smooth region (purple band in Fig. \ref{fig__profile}) emitting X-ray\
+ the temperature of the smooth region (purple band in Fig. \ref{fig__profile}) emitting X-ray\
  is around 0.3-0.5 keV, similar to that observed by \citet{Miller2016} and \citet{Kataoka2018}.
@@
  suggesting the stratification facilitates the outermost bubbles elongation significantly.\
- Also, Fig. \ref{fig__jetI5+ismSeed3-45deg-c,fig__jetI5+ismSeed3-45deg-d}\
+ Also, Fig. \ref{fig__jetI5+ismSeed3-45deg-c} and \ref{fig__jetI5+ismSeed3-45deg-d}\
  reveal that the development of the innermost bubbles\
- is always associated with the disc, without the disc,\
+ is always associated with the disc, without the disc (Fig. \ref{fig__jetI5+ismSeed3-45deg-d}),\
  the outermost bubbles and the turbulent plasma will be oblique,\
@@
              for a duration $t=0$--$1.2$ Myr.\
-             Comparison between the clumpy (column a)\
-             and the smooth disc (column b) in a stratified atmosphere\
+             Comparison between the clumpy (Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
+             and the smooth disc (Fig. \ref{fig__jetI5+ismSeed3-45deg-b}) in a stratified atmosphere\
              shows that the initial density distribution of the dense disc has an insignificant effect\
              on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
-             in an uniform atmosphere (column c) is spherical-shape,\
+             in an uniform atmosphere (Fig. \ref{fig__jetI5+ismSeed3-45deg-c}) is spherical-shape,\
              suggesting the stratification facilitates the outermost bubbles elongation significantly.\
-             Also, the two rightmost columns reveal that the development of the innermost bubbles\
-             is always associated with the disc, without the disc (column d),\
+             Also, Fig. \ref{fig__jetI5+ismSeed3-45deg-c} and \ref{fig__jetI5+ismSeed3-45deg-d}\
+             reveal that the development of the innermost bubbles\
+             is always associated with the disc, without the disc (Fig. \ref{fig__jetI5+ismSeed3-45deg-d}),\
              the outermost bubbles and the turbulent plasma will be oblique,
@@
              and number density (bottom)\
-             along the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.
+             along the positive z-axis in Fig. \ref{fig__jetI5+ismSeed3-45deg}.
              Right: the close-up view of the profiles in the yellow band.\
@@
              indicates that the innermost bubbles\
-             (dashed box in the top panel in \Cref{fig__jetI5+ismSeed3-45deg-a})\
+             (dashed box in the top panel in Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
              are an expanding reverse shock.
@@
   First, we observe that\
-  The simulated eROSITA bubbles are not as limb-brightened as the observation.\
+  the simulated eROSITA bubbles are not as limb-brightened as the observation.\
   A possibility to enhance the X-ray emission is to include shock-accelerated CRs near the shock,\
@@
 
-  Second, as shown in Fig. \ref{fig__jetI5+ismSeed3-45deg},\
+  Second, as shown in Fig. \ref{fig__jetI5+ismSeed3-45deg-a},\
   the half-width of the outermost bubbles is around 7 kpc,\
@@
 
-We perform the double integration in \Cref{gammaray-emissivity} on each cell\
+We perform the double integration in Eq. \ref{gammaray-emissivity} on each cell\
 over the range of CRe Lorentz factor, and\
@@
 where $\Gamma$ is the gamma function, $B$ is the magnetic field strength defined in\
-\Cref{magnetic-field}.
+Eq. \ref{magnetic-field}.
 
@@
 and optical starlight ($\epsilon \sim 10$ eV).\
-Thus, \Cref{gamma-min} can be reduced to $\epsilon_{1}\sim\gamma m_{\text{e}}c^2$\
+Thus, Eq. \ref{gamma-min} can be reduced to $\epsilon_{1}\sim\gamma m_{\text{e}}c^2$\
 in the Klein--Nishina limit\
@@
  ignoring the contribution of CR pressure gradient to the momentum of the gas\
- in \Cref{governing-eq} is reasonable.
+ in Eq. \ref{governing-eq} is reasonable.
 
@@
      ignoring the contribution of CR pressure gradient to the momentum of the gas\
-     in \Cref{governing-eq} is reasonable.
+     in Eq. \ref{governing-eq} is reasonable.
      }

### 2022-03-14 mnras_guide.tex
update

@@
 % Keep the title short and informative.
-\title[]{The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study}
+\title[]{Can the symmetric Fermi and eROSITA bubbles be produced by tilted jets: a proof-of-concept study}
 
@@
 \orcidlink{https://orcid.org/0000-0002-1868-0660}%
-\quad H.-Y. Karen Yang$^{2,3,4}$%
+\quad H.-Y. Karen Yang$^{2,3,4,5}$%
 \thanks{\href{mailto:hyang@phys.nthu.edu.tw}{hyang@phys.nthu.edu.tw}}%
 \orcidlink{https://orcid.org/0000-0003-3269-4660}%
-\quad Hsi-Yu Schive$^{1,5,6,4}$%
+\quad Hsi-Yu Schive$^{1,5,6,7}$%
 \thanks{\href{mailto:hyschive@phys.ntu.edu.tw}{hyschive@phys.ntu.edu.tw}}%
 \orcidlink{https://orcid.org/0000-0002-1249-279X}%
-\quad Chun-Yen Chen$^{7}$
+\quad Chun-Yen Chen$^{8}$
 \quad Tzihong Chiueh$^{1,5,6}$%
@@
 $^{2}$Institute of Astronomy, National Tsing Hua University, Hsinchu 30013, Taiwan\\
-$^{3}$Center for Informatics and Computation in Astronomy, National Tsing Hua University, Hsinchu 30013, Taiwan\\
-$^{4}$Physics Division, National Center for Theoretical Sciences, Taipei 10617, Taiwan\\
-$^{5}$Department of Physics, National Taiwan University, Taipei 10617, Taiwan\\
-$^{6}$Center for Theoretical Physics, National Taiwan University, Taipei 10617, Taiwan\\
-$^{7}$Institute of physics, National Taiwan University, Taipei 10617, Taiwan\\
+$^{3}$Department of Physics, National Tsing Hua University, Hsinchu 30013, Taiwan\\
+$^{4}$Center for Informatics and Computation in Astronomy, National Tsing Hua University, Hsinchu 30013, Taiwan\\
+$^{5}$Physics Division, National Center for Theoretical Sciences, Taipei 10617, Taiwan\\
+$^{6}$Department of Physics, National Taiwan University, Taipei 10617, Taiwan\\
+$^{7}$Center for Theoretical Physics, National Taiwan University, Taipei 10617, Taiwan\\
+$^{8}$Institute of physics, National Taiwan University, Taipei 10617, Taiwan\\
 }

### 2022-03-14 mnras_guide.tex
update

@@
 \orcidlink{https://orcid.org/0000-0002-1249-279X}%
-\quad Chun-Yen Chen$^{8}$
+\quad Chun-Yen Chen$^{8}, $
 \quad Tzihong Chiueh$^{1,5,6}$%
@@
 The \textit{Fermi Gamma-Ray Space Telescope} reveals two large bubbles in the Galaxy,\
-which extend nearly symmetrically $\sim50^{\circ}$ on either side of the Galactic center (GC).\
-The recent discovery of giant eROSITA bubbles also shows a symmetrically enhanced X-ray\
-emission from the shells around the eROSITA bubbles.\
-To this end, previous simulation-based works based on active galactic nucleus (AGN) jets model\
-assumed that the jets are vertical to the Galactic disk;\
-however, there is a lack of preferred orientation of jets with respect to the Galactic disk.\
+which extend nearly symmetrically $\sim50^{\circ}$ above and below the Galactic center (GC).\
+The recent discovery of giant eROSITA bubbles also shows such a symmetry about the GC, suggesting that they may originate from a single GC activity.\
+Previous simulations of bubble formation that invoke active galactic nucleus (AGN) jets\
+have assumed that the jets are vertical to the Galactic plane;\
+however, in general there does not need to be a correlation between the jet orientation and the rotational axis of the Galactic disk.\
 Using three-dimensional (3D) special relativistic hydrodynamic (SRHD) simulations that\
-include cosmic rays (CRs) and thermal gas, we show that a thin interstellar medium (ISM) disk is a substantial\
+include cosmic rays (CRs) and thermal gas, we show that a thin interstellar medium (ISM) disk is an essential\
 component for the symmetric \textit{Fermi} and eROSITA bubbles (collectively, Galactic bubbles).\
@@
 and significantly stretched by the stratified atmosphere afterwards.\
-(3) Followed by the forward shock is a\
-hot ($\sim2$ keV), turbulent, and pressure-balanced plasma,\
-which we interpret as the \textit{Fermi} bubbles.\
-Inside the simulated \textit{Fermi} bubbles,\
-there are two additional innermost bubbles we have not detected yet.\
-The innermost bubbles are essentially a reverse shock permanently associated with the disk.\
+(3) Followed by the forward shock is a tangling contact discontinuity,\
+which we interpret as the edge of the \textit{Fermi} bubbles\
+composed of turbulent and high-temperature ($\sim2$ keV)\
+plasma in pressure balance with the external medium.
 (4) According to the microwave and leptonic gamma-ray spectra, the best-fitting\
 CRe power-law index is found to be 2.4.\
-The broad agreement between the simulations and observations\
-, either from the point of view of their morphology or multiwavelength features,\
+The broad agreement between simulated and observed multiwavelength features\
 has thus released a caveat:\
@@
 \citep{PhysRevLett.106.101102,Carretti2013}
-or past AGN activity \citep{Guo2012,Yang2017}.
+or past AGN activity \citep{Guo2012,Li,Yang2017,Zhu}.
 
@@
 
- Followed by the forward shock is a turbulent and hot plasma\
- in pressure balance with the external medium.\
+ Followed by the forward shock is a turbulent and hot plasma.\
  As shown in the temperature or density slices of the fiducial run,\
- the full extent of the turbulent plasma is 9 kpc, fairly close to\
+ the full extent of the turbulent plasma is approximately agree with\
  that of the observed \textit{Fermi} bubbles \citep{Su2010}.
@@
  comparable to few keV inside the \textit{Fermi} bubbles\
- by observing X-ray absorption lines through the hot\
+ obtained by observing X-ray absorption lines through the hot\
  gaseous halo along many different sight lines in the sky \citep{Miller_2013}.\
- The general agreement of extent and temperature\
- suggests that the \textit{Fermi} bubbles\
- is essentially a turbulence rather than a smooth shock \citep{Zhang2020}.
+ We also note that the turbulence within the hot plasma is in pressure balance with the external medium,\
+ suggesting the outer edge of the \textit{Fermi} bubbles\
+ is a turbulence rather than a smooth shock \citep{Zhang2020}.
 
@@
 
- Moreover, the close-up view (right column in Fig. \ref{fig__profile})\
- of profiles and slices (Fig. \ref{fig__innerbubbles})\
- demonstrates that the pressure rises dramatically outward across\
- the edge of the innermost bubbles,\
+ Moreover, the close-up view (right column in Fig. \ref{fig__profile}) of profiles\
+ and slices (Fig. \ref{fig__innerbubbles})\
+ demonstrate that there is a sharp pressure jump on the edge of the innermost bubbles ($z=3.62$ kpc),\
  indicating that the innermost bubbles are an expanding reverse shock.\

### 2022-03-14 mnras_guide.tex
update

@@
  can also be realized by oblique jets.\
+ However, we find that the simulated surface is not as smooth
+ as the observed one. The instabilities at the bubble
+ surface may be suppressed by the magnetic draping
+ effect \citep{Lyutikov2006,Yang2012} if magnetic fields were
+ included in the simulations.
+
+ The simulated gamma-ray intensity
+ distribution shown in Fig. \ref{fig__gammaRay-map} does not appear to be
+ as uniform as originally found in \citet{Su2012}.
+ As discussed above, the gamma-ray intensity is slightly
+ higher close to the Galactic plane due to the stronger
+ radiation field at lower latitudes. However, this level
+ of brightness variations is consistent with the later
+ observational data of \citet{Ackermann2014} and \citet{Selig2015}.
 

### 2022-03-14 KY-3.14.tex
update

--- 2022-03-03 overleaf.tex
@@
 \begin{document}
-\title{The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study}
+%\title{The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study}
+\title{Can the symmetric \textit{Fermi} and eROSITA bubbles be produced by tilted jets: a proof-of-concept study}
 
@@
 \affiliation{Institute of Astronomy, National Tsing Hua University, Hsinchu 30013, Taiwan}
+\affiliation{Department of Physics, National Tsing Hua University, Hsinchu 30013, Taiwan}
 \affiliation{Center for Informatics and Computation in Astronomy, National Tsing Hua University, Hsinchu 30013, Taiwan}
@@
 \affiliation{Institute of Astrophysics, National Taiwan University, Taipei 10617, Taiwan}
+\affiliation{Physics Division, National Center for Theoretical Sciences, Taipei 10617, Taiwan}
 \affiliation{Department of Physics, National Taiwan University, Taipei 10617, Taiwan}
 \affiliation{Center for Theoretical Physics, National Taiwan University, Taipei 10617, Taiwan}
-\affiliation{Physics Division, National Center for Theoretical Sciences, Taipei 10617, Taiwan}
 
@@
 The \textit{Fermi Gamma-Ray Space Telescope} reveals two large bubbles in the Galaxy,\
-which extend nearly symmetrically $\sim50^{\circ}$ on either side of the Galactic center (GC).\
-The recent discovery of giant eROSITA bubbles also shows a symmetrically enhanced X-ray\
-emission from the shells around the eROSITA bubbles.\
-To this end, previous simulation-based works based on active galactic nucleus (AGN) jets model\
-assumed that the jets are vertical to the Galactic disk;\
-however, there is a lack of preferred orientation of jets with respect to the Galactic disk.\
+which extend nearly symmetrically $\sim50^{\circ}$ above and below the Galactic center (GC).\
+The recent discovery of giant eROSITA bubbles also shows such a symmetry about the GC, suggesting that they may originate from a single GC activity.\
+Previous simulations of bubble formation that invoke active galactic nucleus (AGN) jets\
+have assumed that the jets are vertical to the Galactic plane;\
+however, in general there does not need to be a correlation between the jet orientation and the rotational axis of the Galactic disk.\
 Using three-dimensional (3D) special relativistic hydrodynamic (SRHD) simulations that\
@@
 including galaxies in which the jets lie in the plane of the disc (e.g. IC 5063, \citealt{Morganti2015}).
+
+{\color{red} Cite references for pc-scale jet candidates of Sgr A\*, e.g., \citep{Li, Zhu}.}
 
@@
  one can see that the symmetric \textit{Fermi} bubbles\
- can also be realized by oblique jets.\
+ can also be realized by oblique jets.\ {\color{red} KY: Please add brief discussion about (1) the surface of the bubbles, e.g., the simulated surface is not as smooth as the observed one).
+The instabilities at the bubble surface may be suppressed by the magnetic draping effect (Lyutikov 2006, Y12) if magnetic fields were included in the simulations.
+(2) the uniform gamma-ray intensity: The simulated gamma-ray intensity distribution shown in Figure 8 does not appear to be as uniform as originally found in Su et al.
+(2012).
+As discussed above, the gamma-ray intensity is slightly higher close to the Galactic plane due to the stronger radiation field at lower latitudes.
+However, this level of brightness variations is consistent with the later observational data of Ackermann et al.
+(2014) and Selig et al.
+(2015).}
 
@@
  in \Cref{governing-eq} is reasonable.
+
+{\color{red} KY: Please also add a section (either in the Discussion or Appendix) to discuss about the parameter variations. I think the figures you showed me are very important and informative.}
+
+{\color{red} KY: Please add a Discussion section to discuss the cooling times of CR electrons and the requirement for re-acceleration.
+Emphasize that our modeled gamma-ray and microwave spectra assumed that the underlying CR spectrum is spatially uniform.
+Therefore our results imply that, whatever the true re-acceleration mechanism is, the CR spectrum has to be spatially uniform with a spectral index of 2.4 in order to fit the observed spectra.
+Please also include this in the abstract and the conclusions since this is an important point to make.}
 

### 2022-03-14 paper.tex
update

--- 2022-03-08 paper.tex
@@
-\documentclass[twocolumn]{aastex631}
+\documentclass[fleqn,usenatbib,useAMS]{mnras}
 \usepackage{mathtools}
 \usepackage{natbib}
-\bibliographystyle{abbrvnat}
+\bibliographystyle{mnras}
 \setcitestyle{authoryear,open={(},close={)}}
-\usepackage{txfonts}
-\usepackage{lipsum, babel}
-\usepackage[T1]{fontenc}
-\usepackage{ae,aecompl}
-\usepackage{xcolor,colortbl}
-\usepackage{tikz}
-\usepackage{graphicx}
+\usepackage{graphicx}	% Including figure files
+\usepackage{amsmath}	% Advanced maths commands
+\usepackage{amssymb}	% Extra maths symbols
+\usepackage{multicol}        % Multi-column entries in tables
+\usepackage{bm}		% Bold maths symbols, including upright Greek
+\usepackage{pdflscape}	% Landscape pages
+\usepackage{orcidlink}
 \usepackage{url}
-\usepackage{floatrow}
-\usepackage{subfigure}
-\usepackage{float}
-\usepackage{amsmath}
-\usepackage{amssymb}
 \usepackage{cleveref}
-\usepackage{physics}
-\usepackage{empheq}
 \usepackage{booktabs}
-\usepackage{array}
-\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}
-\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
-\usepackage{multirow}
 \usepackage[flushleft]{threeparttable}
-\usepackage{mathrsfs}
-\usepackage{soul}
-\pdfminorversion=5
-
-\newcommand{\MyDiamond}[1][fill=black]{
-\begin{tikzpicture}[x=1.2ex,y=1.2ex,line width=.1ex,line join=round, yshift=0.0ex]\
-\draw  [#1]  (0,.5) -- (.5,1) -- (1,.5) -- (.5,0);
-\end{tikzpicture}
+\usepackage{caption}
+\usepackage{subcaption}
+
+\newcommand{\kms}{\,km\,s$^{-1}$} % kilometres per second
+\newcommand{\bibtex}{\textsc{Bib}\!\TeX} % bibtex. Not quite the correct typesetting, but close enough
+%
+%
+%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
+
+% Title of the paper, and the short title which is used in the headers.
+% Keep the title short and informative.
+\title[]{Can the symmetric \textit{Fermi} and eROSITA bubbles be produced by tilted jets: a proof-of-concept study}
+
+% The list of authors, and the short list which is used in the headers.
+% If you need two or more lines of authors, add an extra line using \newauthor
+\author[P. H. Tseng et al.]{\large
+Po-Hsun Tseng$^{1}$%
+\thanks{\href{mailto:zengbs@gmail.com}{zengbs@gmail.com}}%
+\orcidlink{https://orcid.org/0000-0002-1868-0660}%
+\quad H.-Y. Karen Yang$^{2,3,4,5}$%
+\thanks{\href{mailto:hyang@phys.nthu.edu.tw}{hyang@phys.nthu.edu.tw}}%
+\orcidlink{https://orcid.org/0000-0003-3269-4660}%
+\quad Hsi-Yu Schive$^{1,5,6,7}$%
+\thanks{\href{mailto:hyschive@phys.ntu.edu.tw}{hyschive@phys.ntu.edu.tw}}%
+\orcidlink{https://orcid.org/0000-0002-1249-279X}%
+\quad Chun-Yen Chen$^{8}, $
+\quad Tzihong Chiueh$^{1,5,6}$%
+\thanks{\href{mailto:chiuehth@phys.ntu.edu.tw}{chiuehth@phys.ntu.edu.tw}}%
+\orcidlink{https://orcid.org/0000-0003-2654-8763}%
+\\\\
+$^{1}$Institute of Astrophysics, National Taiwan University, Taipei 10617, Taiwan\\
+$^{2}$Institute of Astronomy, National Tsing Hua University, Hsinchu 30013, Taiwan\\
+$^{3}$Department of Physics, National Tsing Hua University, Hsinchu 30013, Taiwan\\
+$^{4}$Center for Informatics and Computation in Astronomy, National Tsing Hua University, Hsinchu 30013, Taiwan\\
+$^{5}$Physics Division, National Center for Theoretical Sciences, Taipei 10617, Taiwan\\
+$^{6}$Department of Physics, National Taiwan University, Taipei 10617, Taiwan\\
+$^{7}$Center for Theoretical Physics, National Taiwan University, Taipei 10617, Taiwan\\
+$^{8}$Institute of physics, National Taiwan University, Taipei 10617, Taiwan\\
 }
 
-\newcommand{\MyPlus}[1][fill=black]
-{
-\begin{tikzpicture}[x=1.5ex,y=1.5ex,line width=0.5ex]
-\draw[#1] (0,.5) -- (1,.5);
-\draw[#1] (.5,0) -- (.5,1);
-\end{tikzpicture}
-}
-
-\newcommand{\MyCross}[1][fill=black]
-{
-\begin{tikzpicture}[x=1.ex,y=1.ex,line width=0.5ex]
-\draw[#1] (0,0) -- (1,1);
-\draw[#1] (0,1) -- (1,0);
-\end{tikzpicture}
-}
-
-\newcommand{\MyTriangle}[1][fill=black]
-{
-\begin{tikzpicture}[x=1.ex,y=1.ex,line width=0.2ex]
-\draw[#1] (0,1) -- (1,1);
-\draw[#1] (1,1) -- (.5,0);
-\draw[#1] (.5,0) -- (0,1);
-\fill[#1] (0,1) -- (1,1) -- (.5,0) -- cycle;
-\end{tikzpicture}
-}
-
-\newcommand{\MySolidLine}[1][fill=black]
-{
-\begin{tikzpicture}[x=2.ex,y=1.ex,line width=0.5ex]
-\draw[#1] (0,.5) -- (2.5,.5);
-\end{tikzpicture}
-}
-
-\newcommand{\MyDashedLine}[1][fill=black]
-{
-\begin{tikzpicture}[x=2.ex,y=1.ex,line width=0.5ex]
-\draw [#1,dashed] (0,.5) -- (2.5,.5);
-\end{tikzpicture}
-}
-
-\newcommand{\MyDashedDottedLine}[1][fill=black]
-{
-\begin{tikzpicture}[x=2.ex,y=1.ex,line width=0.5ex]
-\draw [#1,dash dot] (0,.5) -- (2.5,.5);
-\end{tikzpicture}
-}
-
-\newcommand{\MyDottedLine}[1][fill=black]
-{
-\begin{tikzpicture}[x=2.ex,y=1.ex,line width=0.5ex]
-\draw [#1,dotted] (0,.5) -- (2.5,.5);
-\end{tikzpicture}
-}
-
-\definecolor{Gray}{gray}{0.85}
-
+% These dates will be filled out by the publisher
+\date{\today}
+
+% Enter the current year, for the copyright statements etc.
+\pubyear{2022}
+
+% Don't change these lines
 \begin{document}
-\title{The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study}
-
-\author[0000-0002-1868-0660]{Po-Hsun Tseng}
-\affiliation{Institute of Astrophysics, National Taiwan University, Taipei 10617, Taiwan}
-
-\author[0000-0003-3269-4660]{H.-Y. Karen Yang}
-\affiliation{Institute of Astronomy, National Tsing Hua University, Hsinchu 30013, Taiwan}
-\affiliation{Center for Informatics and Computation in Astronomy, National Tsing Hua University, Hsinchu 30013, Taiwan}
-\affiliation{Physics Division, National Center for Theoretical Sciences, Taipei 10617, Taiwan}
-
-\author[0000-0002-1249-279X]{Hsi-Yu Schive}
-\affiliation{Institute of Astrophysics, National Taiwan University, Taipei 10617, Taiwan}
-\affiliation{Department of Physics, National Taiwan University, Taipei 10617, Taiwan}
-\affiliation{Center for Theoretical Physics, National Taiwan University, Taipei 10617, Taiwan}
-\affiliation{Physics Division, National Center for Theoretical Sciences, Taipei 10617, Taiwan}
-
-\author{Chun-Yen Chen}
-\affiliation{Institute of physics, National Taiwan University, Taipei 10617, Taiwan}
-
-\author[0000-0003-2654-8763]{Tzihong Chiueh}
-\affiliation{Institute of Astrophysics, National Taiwan University, Taipei 10617, Taiwan}
-\affiliation{Department of Physics, National Taiwan University, Taipei 10617, Taiwan}
-\affiliation{Center for Theoretical Physics, National Taiwan University, Taipei 10617, Taiwan}
-
-\correspondingauthor{Po-Hsun Tseng}
-\email{zengbs@gmail.com}
-
-\keywords{\textit{Fermi} bubbles, eROSITA bubbles, cosmic rays}
-
+\label{firstpage}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}}
+\maketitle
+
+% Abstract of the paper
 \begin{abstract}
 The \textit{Fermi Gamma-Ray Space Telescope} reveals two large bubbles in the Galaxy,\
-which extend nearly symmetrically $\sim50^{\circ}$ on either side of the Galactic center (GC).\
-The recent discovery of giant eROSITA bubbles also shows a symmetrically enhanced X-ray\
-emission from the shells around the eROSITA bubbles.\
-To this end, previous simulation-based works based on active galactic nucleus (AGN) jets model\
-assumed that the jets are vertical to the Galactic disk;\
-however, there is a lack of preferred orientation of jets with respect to the Galactic disk.\
+which extend nearly symmetrically $\sim50^{\circ}$ above and below the Galactic center (GC).\
+The recent discovery of giant eROSITA bubbles also shows such a symmetry about the GC, suggesting that they may originate from a single GC activity.\
+Previous simulations of bubble formation that invoke active galactic nucleus (AGN) jets\
+have assumed that the jets are vertical to the Galactic plane;\
+however, in general there does not need to be a correlation between the jet orientation and the rotational axis of the Galactic disk.\
 Using three-dimensional (3D) special relativistic hydrodynamic (SRHD) simulations that\
-include cosmic rays (CRs) and thermal gas, we show that a thin interstellar medium (ISM) disk is a substantial\
+include cosmic rays (CRs) and thermal gas, we show that a thin interstellar medium (ISM) disk is an essential\
 component for the symmetric \textit{Fermi} and eROSITA bubbles (collectively, Galactic bubbles).\
@@
 \end{abstract}
+
+% Select between one and six entries from the list of approved keywords.
+% Don't make up new ones.
+\begin{keywords}
+editorials, notices -- miscellaneous
+\end{keywords}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%
+
+% The MNRAS class isn't designed to include a table of contents, but for this document one is useful.
+% I therefore have to do some kludging to make it work without masses of blank space.
+\begingroup
+\let\clearpage\relax
+%\tableofcontents
+\endgroup
+\newpage
 
@@
 is one of the great discoveries made with \textit{Fermi} Large Area Telescope \citep{Atwood2009}.
-
 The gamma-ray emission of the \textit{Fermi} bubbles is observed in the energy range\
@@
 \label{Methodology}
-  We used the GPU-accelerated special relativistic hydrodynamics AMR code (\textsc{gamer-sr}) developed at the\
+  We used the GPU-accelerated special relativistic\
+  hydrodynamics AMR code (\textsc{gamer-sr}) developed at the\
   National Taiwan University\
-  (Schive et al. \citeyear{gamer-1}, \citeyear{gamer-2}; \citeauthor{tseng2021} \citeyear{tseng2021})\
+  (\citeauthor{gamer-1} \citeyear{gamer-1}, \citeyear{gamer-2}; \citeauthor{tseng2021} \citeyear{tseng2021})\
   to carry out the simulations of the Galactic bubbles by CR and relativistic fluid injections from the GC.
@@
   and directly evolve the CR energy density $e_{\text{cr}}$\
-  as a function of $\mathbf{r}$ and $t$.\
+  as a function of \textbf{r} and $t$.\
   The CRs are advected with the thermal gas, and in return the velocities of gas\
@@
 
-  The density profile of \Cref{disc-atm-sys} is shown in \Cref{fig__initial-density-profile}.\
+  The density profile of Eq. \ref{disc-atm-sys} is shown in Fig. \ref{fig__initial-density-profile}.\
   Beyond the core radius ($\sim 2 \text{ kpc}$) the gaseous density decreases rapidly as a power-law.
-
-%  The density profile of \Cref{disc-atm-sys} is shown in \Cref{fig__initial-density-profile}\
-%  and compared to the observed result \citep{Miller_2013} beyond 1 kpc.\
-%
-%  Note that there is an difficulty in disentangling the contribution\
-%  of the Local Bubble, a supernova remnant in which the Solar System is embedded \citep{Snowden1990},\
-%  and the contribution from solar wind charge-exchange processes, which produce soft\
-%  X-ray emission throughout the Solar System. As a result, the density profile of the Galactic halo remains unclear\
-%  \citep{BlandHawthorn2016}.
 
@@
 
-% In addition to the gravitational interaction, we ignore other interactions between stars and gases.
-% We also ignore the self-gravity of the ISM disc and of the atmosphere.
-% We ignore the centrifugal force of Milky Way rotation acting on the bubbles.
 %
@@
 
- The fiducial run (a1-a3) with the initial condition specified in Section \ref{Methodology}\
+ The fiducial run (Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
+ with the initial condition specified in Section \ref{Methodology}\
  shows that the edge of the outermost bubbles is indeed a forward shock,\
@@
  We note that the overall extent of the outermost bubbles is comparable to\
- the two spherical objects of a radius 6-7 kpc proposed by \citet{Predehl2020} for modeling the eROSITA bubbles\
+ the two spherical objects of a radius 6-7 kpc proposed by \citet{Predehl2020}\
+ for modeling the eROSITA bubbles\
  based on X-ray emissions.
 
- The temperature profile (left middle panel in \Cref{fig__profile}) along the positive z-axis in\
- \Cref{fig__jetI5+ismSeed3-45deg} indicates that\
- the smooth region (purple band in \Cref{fig__profile}) emitting X-ray\
+ The temperature profile (left middle panel in Fig. \ref{fig__profile}) along the positive z-axis in\
+ Fig. \ref{fig__jetI5+ismSeed3-45deg} indicates that\
+ the temperature of the smooth region (purple band in Fig. \ref{fig__profile}) emitting X-ray\
  is around 0.3-0.5 keV, similar to that observed by \citet{Miller2016} and \citet{Kataoka2018}.
 
- Followed by the forward shock is a turbulent and hot plasma\
- in pressure balance with the external medium.\
+ Followed by the forward shock is a turbulent and hot plasma.\
  As shown in the temperature or density slices of the fiducial run,\
- the full extent of the turbulent plasma is 9 kpc, fairly close to\
+ the full extent of the turbulent plasma is approximately agree with\
  that of the observed \textit{Fermi} bubbles \citep{Su2010}.
@@
  comparable to few keV inside the \textit{Fermi} bubbles\
- by observing X-ray absorption lines through the hot\
+ obtained by observing X-ray absorption lines through the hot\
  gaseous halo along many different sight lines in the sky \citep{Miller_2013}.\
- The general agreement of extent and temperature\
- suggests that the \textit{Fermi} bubbles\
- is essentially a turbulence rather than a smooth shock \citep{Zhang2020}.
+ We also note that the turbulence within the hot plasma is in pressure balance with the external medium,\
+ suggesting the outer edge of the \textit{Fermi} bubbles\
+ is a turbulence rather than a smooth shock \citep{Zhang2020}.
 
  The most interesting finding is that there are innermost bubbles\
- (dashed box in left top panel of \Cref{fig__jetI5+ismSeed3-45deg})\
+ (dashed box in the top panel of Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
  extending out from the GC on either side of the thin disk.\
@@
 
- Moreover, the close-up view (right column in \Cref{fig__profile})\
- of profiles and slices (\Cref{fig__innerbubbles})\
- demonstrates that the pressure rises dramatically outward across\
- the edge of the innermost bubbles,\
+ Moreover, the close-up view (right column in Fig. \ref{fig__profile}) of profiles\
+ and slices (Fig. \ref{fig__innerbubbles})\
+ demonstrate that there is a sharp pressure jump on the edge of the innermost bubbles ($z=3.62$ kpc),\
  indicating that the innermost bubbles are an expanding reverse shock.\
@@
 
- To explore how the disk affects the formation of the Galactic bubbles,\
- we compare the fiducial run (panels a1-a3 in \Cref{fig__jetI5+ismSeed3-45deg})\
- with the case adopting the smooth disc\
- (panels b1-b3; \Cref{fig__initial-density-profile} shows the density profile) in a stratified atmosphere.\
- The results show that the initial density distribution of the dense disc has an insignificant effect\
+ Fig. \ref{fig__jetI5+ismSeed3-45deg} shows the slices of various gas properties at $t=12.39$ Myr,\
+ including pressure (top), temperature (middle),\
+ density (bottom) with the same jet source as the fiducial run\
+ but in different Galactic environments.
+
+ We compare the clumpy disk (Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
+ with the smooth disc (Fig. \ref{fig__jetI5+ismSeed3-45deg-b}),\
+ specified by the initial density profile shown in Fig. \ref{fig__initial-density-profile},\
+ in a stratified atmosphere.\
+ The results show that the initial density distribution of\
+ the dense disc has an insignificant effect\
  on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
- in an uniform atmosphere (panels c1-c3) is spherical-shape,\
+ in an uniform atmosphere (Fig. \ref{fig__jetI5+ismSeed3-45deg-c}) is spherical-shape,\
  suggesting the stratification facilitates the outermost bubbles elongation significantly.\
- Also, the two rightmost columns reveal that the development of the innermost bubbles\
- is always associated with the disc, without the disc,\
+ Also, Fig. \ref{fig__jetI5+ismSeed3-45deg-c} and \ref{fig__jetI5+ismSeed3-45deg-d}\
+ reveal that the development of the innermost bubbles\
+ is always associated with the disc, without the disc (Fig. \ref{fig__jetI5+ismSeed3-45deg-d}),\
  the outermost bubbles and the turbulent plasma will be oblique,\
@@
 
-  \begin{figure}
-    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg.png}
+ \begin{figure}%
+      \captionsetup[subfigure]{labelformat=simple}
+      \begin{subfigure}[b]{0.2\linewidth}%
+         \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-a}%
+         \caption{}%
+         \label{fig__jetI5+ismSeed3-45deg-a}%
+      \end{subfigure}%
+      \hspace{10pt}%
+      \begin{subfigure}[b]{0.2\linewidth}%
+         \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-b}%
+         \caption{}%
+         \label{fig__jetI5+ismSeed3-45deg-b}%
+      \end{subfigure}%
+      \hspace{-2pt}%
+      \begin{subfigure}[b]{0.2\linewidth}%
+         \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-c}%
+         \caption{}%
+         \label{fig__jetI5+ismSeed3-45deg-c}%
+      \end{subfigure}%
+      \hspace{-2pt}%
+      \begin{subfigure}[b]{0.2\linewidth}%
+         \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-d}%
+         \caption{}%
+         \label{fig__jetI5+ismSeed3-45deg-d}%
+     \end{subfigure}%
       \caption{
@@
              for a duration $t=0$--$1.2$ Myr.\
-             Comparison between the clumpy (a1-a3)\
-             and the smooth disc (b1-b3) in a stratified atmosphere\
+             Comparison between the clumpy (Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
+             and the smooth disc (Fig. \ref{fig__jetI5+ismSeed3-45deg-b}) in a stratified atmosphere\
              shows that the initial density distribution of the dense disc has an insignificant effect\
              on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
-             in an uniform atmosphere (c1-c3) is spherical-shape,\
+             in an uniform atmosphere (Fig. \ref{fig__jetI5+ismSeed3-45deg-c}) is spherical-shape,\
              suggesting the stratification facilitates the outermost bubbles elongation significantly.\
-             Also, the two rightmost columns reveal that the development of the innermost bubbles\
-             (a1)\
-             is always associated with the disc, without the disc,\
+             Also, Fig. \ref{fig__jetI5+ismSeed3-45deg-c} and \ref{fig__jetI5+ismSeed3-45deg-d}\
+             reveal that the development of the innermost bubbles\
+             is always associated with the disc, without the disc (Fig. \ref{fig__jetI5+ismSeed3-45deg-d}),\
              the outermost bubbles and the turbulent plasma will be oblique,
@@
       \label{fig__jetI5+ismSeed3-45deg}
-  \end{figure}
-
-  \begin{figure}
-    \includegraphics[width=\columnwidth]{figures/fig__profile.png}
+ \end{figure}%
+
+ \begin{figure}%
+      \begin{subfigure}[t]{0.5\linewidth}%
+         \includegraphics[height=8cm]{figures/fig__profile-1.png}%
+         \label{fig__profile-1}%
+      \end{subfigure}%
+      \hspace{4pt}
+      \begin{subfigure}[t]{0.5\linewidth}%
+         \includegraphics[height=8cm]{figures/fig__profile-2.png}%
+         \label{fig__profile-2}%
+      \end{subfigure}%
       \caption{
@@
              indicates that the innermost bubbles\
-             (dashed box in top left panel of \Cref{fig__jetI5+ismSeed3-45deg})\
+             (dashed box in the top panel in Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
              are an expanding reverse shock.
-     }
-    \label{fig__profile}
-  \end{figure}
+      }%
+      \label{fig__profile}%
+ \end{figure}%
 
@@
 
-  \Cref{fig__x-ray-profile-0.8keV-000} displays the simulated count rate profiles (red)\
-  in the same energy band as \Cref{fig__xray_0.8keV_angle_000}\
+  Fig. \ref{fig__x-ray-profile-0.8keV-000} displays the simulated count rate profiles (red)\
+  in the same energy band as Fig. \ref{fig__xray_0.8keV_angle_000}\
   cut at various galactic latitudes (as labelled), compared with the observation (black).\
-  \Cref{fig_xray-map} is quite revealing in several ways.\
+  Fig. \ref{fig_xray-map} is quite revealing in several ways.\
 
   First, we observe that\
-  The simulated eROSITA bubbles are not as limb-brightened as the observation.\
+  the simulated eROSITA bubbles are not as limb-brightened as the observation.\
   A possibility to enhance the X-ray emission is to include shock-accelerated CRs near the shock,\
@@
 
-  Second, as shown in \Cref{fig__jetI5+ismSeed3-45deg},\
+  Second, as shown in Fig. \ref{fig__jetI5+ismSeed3-45deg-a},\
   the half-width of the outermost bubbles is around 7 kpc,\
   corresponding to an half angular width $\sin^{-1}(7 \text{ kpc}/R_{\odot})\sim122^{\circ}$,\
-  which is as wide as the eROSITA bubbles in the simulated X-ray map (top panel in \Cref{fig__xray_0.8keV_angle_000}).\
+  which is as wide as the eROSITA bubbles in the simulated X-ray map\
+  (top panel in Fig. \ref{fig__xray_0.8keV_angle_000}).\
   We therefore suggest that the eROSITA bubble shells are a signature of compressed forward shocks\
@@
 
-  \begin{figure*}
-    \subfigure[Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
+ \begin{figure*}%
+      \begin{subfigure}[t]{\textwidth}%
+         \centering%
+         \includegraphics[width=0.85\textwidth]{figures/fig__xraymap.png}%
+         \caption{
+               Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
                (photons s$^{-1}$ deg$^{-2}$) in the 0.6--1.0 keV range.\
@@
                top panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
-               to the disc normal in 1.2 Myr.]
-     {
-      \includegraphics[width=0.8\linewidth]{figures/fig__xraymap.png}
-      \label{fig__xray_0.8keV_angle_000}
-     }
-    \subfigure[Comparison of simulated (red) and observed (black; \citealt{Predehl2020}) one-dimensional\
-               count rate profiles in the same energy band as \Cref{fig__xray_0.8keV_angle_000},\
-               cut at various galactic latitudes (as labelled).]
-     {
-      \includegraphics[width=0.8\linewidth]{figures/fig__xray-profile-0.8keV-000.png}
-      \label{fig__x-ray-profile-0.8keV-000}
-     }
-    \caption{}
+               to the disc normal in 1.2 Myr.
+         }%
+         \label{fig__xray_0.8keV_angle_000}%
+         \end{subfigure}%
+         \hspace{4pt}%
+      \begin{subfigure}[t]{\textwidth}%
+         \centering%
+         \includegraphics[width=0.85\textwidth]{figures/fig__xray-profile-0.8keV-000.png}%
+         \caption{
+               Comparison of simulated (red) and observed (black; \citealt{Predehl2020}) one-dimensional\
+               count rate profiles in the same energy band as Fig. \ref{fig__xray_0.8keV_angle_000},\
+               cut at various galactic latitudes (as labelled).
+         }%
+         \label{fig__x-ray-profile-0.8keV-000}%
+      \end{subfigure}%
+      \caption{}%
       \label{fig_xray-map}
-  \end{figure*}
+ \end{figure*}%
 
@@
 $0.5$ MeV to $562.1$ GeV.
-
-%The microwave haze at 23 GHz was first detected by the \textit{WMAP} \citep{Dobler_2008}\
-%within the region $|b|<30^{\circ}$ above and below the Galactic plane,\
-%and later confirmed by the Planck Collaboration IX \citep{PlanckCollaborationIX2013}.
 
@@
       The CRe cutoff energy is 562.1 GeV in all cases.
-      %At larger $p$, the microwave spectrum was found to be steeper as $I_{\nu}\propto \nu^{-(p-1)/2}$.
   }
@@
  can also be realized by oblique jets.\
+ However, we find that the simulated surface is not as smooth
+ as the observed one. The instabilities at the bubble
+ surface may be suppressed by the magnetic draping
+ effect \citep{Lyutikov2006,Yang2012} if magnetic fields were
+ included in the simulations.
+
+ The simulated gamma-ray intensity
+ distribution shown in Fig. \ref{fig__gammaRay-map} does not appear to be
+ as uniform as originally found in \citet{Su2012}.
+ As discussed above, the gamma-ray intensity is slightly
+ higher close to the Galactic plane due to the stronger
+ radiation field at lower latitudes. However, this level
+ of brightness variations is consistent with the later
+ observational data of \citet{Ackermann2014} and \citet{Selig2015}.
 
  Finally, the comparison between\
- \Cref{fig__jetI5+ismSeed3-45deg}\
+ Fig. \ref{fig__jetI5+ismSeed3-45deg}\
  and\
- \Cref{fig__jetI5+ismSeed3-45deg-CR}\
+ Fig. \ref{fig__jetI5+ismSeed3-45deg-CR}\
  shows that the CR pressure\
@@
  ignoring the contribution of CR pressure gradient to the momentum of the gas\
- in \Cref{governing-eq} is reasonable.
-
-% assuming a uniform CR spectrum with energy cutoff of ~500 GeV\
-% and spectral index of 2.4, one could also reproduce the gamma-ray spectrum quite well.\
-% Note that the simulation time at this point is 12.39 Myr,\
-% much longer than the CR electron cooling time, so their Emax should\
-% have cooled to below 500 GeV by this time (we should think about how to estimate this).\
-% Therefore, the CRe generating the gamma-ray emission would need to be re-accelerated\
-% by some in-situ acceleration mechanisms such as shocks or turbulence.\
-% The forward shock is pretty far away from the gamma-ray bubbles,\
-% so it's more likely associated with turbulence.
-
-  %The enhanced emission at the lower latitude would likely be due to
-  %similar to the bottom right panel in Fig. 5 of YR17, which is dominated by\
-  %the optical starlight. That's also why in your plot above,\
-  %the high-latitude spectrum tends to be dimmer because of the decay of the ISRF intensity in optical.
+ in Eq. \ref{governing-eq} is reasonable.
 
@@
 
-%\subsubsection{Hadronic process}
-%In the hadronic model, CRp undergo hadronic collisions with thermal gas protons\
-%and produce $\gamma$-ray via pion decay. The volume emissivity of the emission can be written as
-%\begin{equation}
-%   \epsilon \propto U_{\text{CRp}}n_{p}\sigma_{p}\kappa_{pp}.
-%\end{equation}
-%
-%\begin{equation}
-%  \frac{dE}{dtd\epsilon_{1}dV} =\
-%   cn_{H}pC\left(\frac{\epsilon_{1}}{m_{\text{p}}c^2}\right)^{-p}\
-%   \int_{0}^{1}\sigma(\epsilon_{\text{p}}) F(x,\epsilon_{\text{p}}) x^{p}dx.
-%\end{equation}
-%
-%\begin{equation}
-%\sigma(\epsilon_{\text{p}})=34.3+1.88L+0.25L^{2}\left[1-\frac{E_{\text{threshold}}}{E_{\text{p}}}\right]^{4} \text{ mb}.
-%\end{equation}
-%
-%\begin{equation}
-%F(x,\epsilon_{\text{p}})=B\frac{d}{dx}\left[\ln(x)\left(\frac{1-x^{\beta}}{1+kx^{\beta}\left(1-x^{\beta}\right)}\right)^4\right],
-%\end{equation}
-%
-%
-%where
-%$x=\epsilon_{1}/\epsilon_{\text{p}}$, $B=1.30+0.14L+0.011L^2$, $\beta=\left(1.79+0.11L+0.008L^{2}\right)^{-1}$,\
-%$\left(0.801+0.049L+0.014L^{2}\right)^{-1}$, $L=\ln(\epsilon_{\text{p}}/1 \text{ TeV})$.
+\section{Discussion}
+Our modeled gamma-ray and microwave spectra assumed that
+the underlying CRe spectrum is spatially uniform.
+Therefore our results imply that, whatever the true re-acceleration and cooling mechanisms are,
+the CRe spectrum at the present time has to be spatially uniform with
+a spectral index of 2.4 in order to fit the observed spectra.
 
@@
 %%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
+
+% The best way to enter references is to use BibTeX:
+
 \bibliographystyle{mnras}
@@
 
+\appendix
+\section{jets parameter variations}
+\textcolor{red}{KY: Please also add a section (either in the Discussion
+or Appendix) to discuss about the parameter variations.
+I think the figures you showed me are very important
+and informative.}
+
 %%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
-
-%\appendix
-% https://heasarc.gsfc.nasa.gov/docs/objects/heapow/archive/normal_galaxies/fermibubbles_erosita.html
-
-%Jet_SrcVel 0.6
-%Jet_SrcDens 1e-26
-%Jet_SrcTemp 2e10
-%Jet_SrcPres => 1.6e-8
-
 \end{document}
+
+% End of mnras_guide.tex

### 2022-03-14 paper.tex
update

@@
 The detection of the \textit{Fermi} bubbles \citep{Su2012,Ackermann2014,Narayanan2017},\
-two large bubbles symmetrically extending about 50 degrees above and below the Galactic plane,
-is one of the great discoveries made with \textit{Fermi} Large Area Telescope \citep{Atwood2009}.
+two large bubbles symmetrically extending about 50 degrees above and below the Galactic plane,\
+is one of the great discoveries made with \textit{Fermi} Large Area Telescope \citep{Atwood2009}.\
 The gamma-ray emission of the \textit{Fermi} bubbles is observed in the energy range\
@@
 shows that the intrinsic size of the bubbles is 14 kpc across \citep{Predehl2021},
-and displays morphological symmetry about the Galactic plane as the \textit{Fermi} bubbles.
-
+and displays morphological symmetry about the Galactic plane as the \textit{Fermi} bubbles.\
 Their symmetry about the GC suggests that they originate\
@@
 (e.g. NGC 3079, \citealt{Cecil2001}; NGC 1052, \citealt{Dopita2015}),\
-including galaxies in which the jets lie in the plane of the disc (e.g. IC 5063, \citealt{Morganti2015}).
-
+including galaxies in which the jets lie in the plane of the disc (e.g. IC 5063, \citealt{Morganti2015}).\
 To this end, this work introduces a dense, thin disc of ISM\
@@
   and anisotropic CR diffusion with suppressed perpendicular diffusion across the bubble surface.
-
   Moreover, the magnetic fields within the \textit{Fermi} bubbles should be weak due to\
@@
   significantly reducing numerical error caused by catastrophic cancellations\
-  that commonly occur within the regions with high Mach number flows. e.g., jet-ISM interaction zones.
-
+  that commonly occur within the regions with high Mach number flows. e.g., jet-ISM interaction zones.\
   \textsc{gamer-sr} also adaptively and locally reduce the min-mod coefficient\
@@
   the publicly available pyFC code
-  \footnote{\url{https://pypi.python.org/pypi/pyFC}}.\
-
+  \footnote{\url{https://pypi.python.org/pypi/pyFC}}.
   pyFC randomly generates dimensionless 3D scalar field $f(\bold{x})$\ % that is clumpy and porous.
@@
  Continuing outward, the higher density must match with low density further downstream;\
- thus there exists a dense shell.
-
+ thus there exists a dense shell.\
  The turbulent plasma is therefore bracketed between the downstream of reverse shock\
@@
 
-Fourth, the good agreement between the simulated and observed gamma-ray/microwave spectra\
+Finally, the good agreement between the simulated and observed gamma-ray/microwave spectra\
 implies that, in the presence of ISRF and magnetic fields, the emission of the Fermi bubbles and\
@@
 
- Finally, the comparison between\
+ The comparison between\
  Fig. \ref{fig__jetI5+ismSeed3-45deg}\

### 2022-03-24 paper.tex
update

--- 2022-03-14 paper.tex
@@
 Using three-dimensional (3D) special relativistic hydrodynamic (SRHD) simulations that\
-include cosmic rays (CRs) and thermal gas, we show that a thin interstellar medium (ISM) disk is an essential\
-component for the symmetric \textit{Fermi} and eROSITA bubbles (collectively, Galactic bubbles).\
-We also produce simulated gamma-ray and\
-microwave spectra from the inverse Compton (IC) scattering and synchrotron,\
-and compare them with the observed counterparts in order to verify\
-an oblique AGN jets model. We find that\
-(1) The simulated Galactic bubbles are nearly symmetric about the GC albeit\
+include cosmic rays (CRs) and thermal gas, we show that the interaction between the AGN jets and the thin interstellar medium (ISM) disk is crucial for producing the symmetric \textit{Fermi} and eROSITA bubbles (collectively, Galactic bubbles).\
+%We also produce simulated gamma-ray and\
+%microwave spectra from the inverse Compton (IC) scattering and synchrotron,\
+%and compare them with the observed counterparts in order to verify\
+%an oblique AGN jets model.
+Specifically, we find that\
+(1) the simulated Galactic bubbles are nearly symmetric about the GC albeit\
 the bipolar jets are at an angle $45^{\circ}$ with respect to\
-the rotation axis of the Galatic plane (disc normal hereafter).\
-(2) The edge of the eROSITA bubbles is a forward shock,\
-originally driven by oblique bipolar jets emanating from the GC 12.39 million years ago,\
-and significantly stretched by the stratified atmosphere afterwards.\
-(3) Followed by the forward shock is a tangling contact discontinuity,\
+the rotational axis of the Galaxy;\
+(2) the edge of the eROSITA bubbles corresponds to a forward shock,\
+originally driven by oblique bipolar jets emanating from the GC 12.39 million years ago; %,\
+%and significantly stretched by the stratified atmosphere afterwards.\
+(3) followed by the forward shock is a tangling contact discontinuity,\
 which we interpret as the edge of the \textit{Fermi} bubbles\
 composed of turbulent and high-temperature ($\sim2$ keV)\
-plasma in pressure balance with the external medium.
-(4) According to the microwave and leptonic gamma-ray spectra, the best-fitting\
-CRe power-law index is found to be 2.4.\
-The broad agreement between simulated and observed multiwavelength features\
-has thus released a caveat:\
-the jets shall be vertical to the disc normal.
+plasma in pressure balance with the external medium;
+(4) assuming a leptonic model with spatially uniform CR electron spectrum, we find that the observed gamma-ray and microwave spectra can be reproduced with a best-fit CR power-law index of 2.4.\
+The broad agreement between simulated and observed multi-wavelength features suggests that forming the Galactic bubbles by oblique AGN jets is a plausible scenario.
+%has thus released a caveat:\
+%the jets shall be vertical to the disc normal.
 \end{abstract}
@@
 The detection of the \textit{Fermi} bubbles \citep{Su2012,Ackermann2014,Narayanan2017},\
-two large bubbles symmetrically extending about 50 degrees above and below the Galactic plane,
-is one of the great discoveries made with \textit{Fermi} Large Area Telescope \citep{Atwood2009}.
+two large bubbles symmetrically extending about 50 degrees above and below the Galactic plane,\
+is one of the great discoveries of the \textit{Fermi} Large Area Telescope \citep{Atwood2009}.\
 The gamma-ray emission of the \textit{Fermi} bubbles is observed in the energy range\
-of 1--100 GeV and has an almost spatially uniform hard\
-spectrum, sharp edges and an approximately flat brightness distribution.\
+of $\sim$1--100 GeV and has an almost spatially uniform hard\
+spectrum, sharp edges and an approximately flat brightness distribution (see \cite{Yang2018} for a review).
+Recently, the newly launched eROSITA \citep{Predehl2021} conducted an all-sky X-ray survey with high-spatial resolution and revealed two gigantic bubbles (eROSITA bubbles hereafter) extending to $\sim 80$ degrees in Galactic latitudes, corresponding to an intrinsic size of 14 kpc across \citep{Predehl2020}.\
+The remarkable resemblance between the eROSITA and \textit{Fermi} bubbles suggest that they likely share the same origin \citep{Yang2022}.
+Their symmetry about the GC further suggests that these Galactic bubbles may be generated by powerful energy injections from the GC, possibly related to nuclear star formation\
+\citep{PhysRevLett.106.101102,Carretti2013,Crocker2015,Sarkar2015}
+or past AGN activity \citep{Guo2012,Guo2012b,Yang2012,Yang2013,Mou2014,Yang2017}. The latter scenario is what we will focus on in this work.
 
-Over the course of a decade,\
-the first all-sky X-ray survey with high-spatial resolution \citep{Predehl2021}\
-from eROSITA \citep{Predehl2020} also reveals\
-a giant hourglass-shaped structure (eROSITA bubbles hereafter) at the GC,\
-extending about twice as large as the \textit{Fermi} bubbles.\
-The large-scale X-ray structure\
-shows that the intrinsic size of the bubbles is 14 kpc across \citep{Predehl2021},
-and displays morphological symmetry about the Galactic plane as the \textit{Fermi} bubbles.
+Previous attempts \citep{Guo2012,Yang2012,Zhang2020}\
+to model the formation of the symmetric Galactic bubbles by AGN jets have typically\
+assumed that the jets are vertical to the Galactic plane.
+While there are some observational indications of pc-scale jets from Sgr A* that are found to be perpendicular to the Galactic plane \citep{Li, Zhu}, generally speaking, the AGN jet orientation is determined by the black hole spin and the accretion disk in the black-hole vicinity and does not need to align with the rotational axis of the host galaxy.
+Indeed, observationally there is a lack of evidence for the alignment between AGN jets and the disk normal \citep[e.g.,][]{Gallimore2006}.
+The jets are often oblique to the disk normal\
+(e.g. NGC 3079, \citealt{Cecil2001}; NGC 1052, \citealt{Dopita2015}),\
+and there are even cases in which the jets lie in the plane of the disk (e.g. IC 5063, \citealt{Morganti2015}).\
 
-Their symmetry about the GC suggests that they originate\
-from powerful energy injections from the GC, possibly related to nuclear star formation\
-\citep{PhysRevLett.106.101102,Carretti2013}
-or past AGN activity \citep{Guo2012,Li,Yang2017,Zhu}.
-
-Early attempts \citep{Sarkar2015,Yang2017,Zhang2020}\
-to model the symmetric Galactic bubbles\
-assumed that the jets are vertical to the Galactic plane. However,\
-observation \citep{Gallimore2006} has proposed that\
-there is a lack of preferred orientation of jets with respect to the disc normal.\
-In contrast, a number of galaxies in which the jets are oblique to the disc normal\
-(e.g. NGC 3079, \citealt{Cecil2001}; NGC 1052, \citealt{Dopita2015}),\
-including galaxies in which the jets lie in the plane of the disc (e.g. IC 5063, \citealt{Morganti2015}).
-
-To this end, this work introduces a dense, thin disc of ISM\
-around a jet source to deflects and decelerates the oblique jets,\
-in an attempt to resolve the symmetry problem of the Galactic bubbles.\
-
-The main purpose of this study is to use 3D\
-special relativistic hydrodynamics simulations\
-involving CR jet injections from the central SMBH in the Galaxy to investigate\
+To this end, the aim of this work is to remove the assumption on jet orientations in the AGN jet models by introducing a dense, thin ISM disk\
+that can interact with the central oblique jet,\
+in an attempt to resolve the symmetry problem of the Galactic bubbles. More specifically, we use 3D\
+SRHD simulations\
+involving CR jet injections from the central supermassive black hole (SMBH) in the Galaxy to investigate\
 whether the \textit{oblique} jet scenario is able to produce\
-the \textit{symmetric} Galactic bubbles that are\
-consistent with the observed features, including the shape, the\
-surface brightness, and the spectra of \textit{Fermi} bubbles \citep{Ackermann2014}\
-and of microwave haze \citep{Dobler_2008,PlanckCollaborationIX2013}.
+the \textit{symmetric} Galactic bubbles. We will verify whether the oblique jet model is\
+consistent with the observed features of the Galactic bubbles, including the shape, \
+surface brightness, and spectra of the \textit{Fermi} bubbles \citep{Ackermann2014}\
+and microwave haze \citep{Dobler_2008,PlanckCollaborationIX2013}.
 
@@
 and then discuss how the disk affects the formation of the bubbles.\
-We directly compare the morphology and profile of simulated eROSITA bubbles with\
-observred X-ray map in Section \ref{X-ray},\
-and also present the simulated and observed multiwavelength spectra of\
-the \textit{Fermi} bubbles in Section \ref{sec:gamma-ray-microwave}.\
+We compare the morphology and profiles of the simulated eROSITA bubbles with\
+the observed X-ray map in Section \ref{X-ray},\
+and present the simulated and observed multi-wavelength spectra of\
+the \textit{Fermi} bubbles and microwave haze in Section \ref{sec:gamma-ray-microwave}.\
 Finally, the summary and implications of our findings are given in Section \ref{Conclusions}.
@@
 \label{Methodology}
-  We used the GPU-accelerated special relativistic\
-  hydrodynamics AMR code (\textsc{gamer-sr}) developed at the\
+  We use the GPU-accelerated SRHD adaptive-mesh-refinement (AMR) code \textsc{gamer-sr} developed at the\
   National Taiwan University\
   (\citeauthor{gamer-1} \citeyear{gamer-1}, \citeyear{gamer-2}; \citeauthor{tseng2021} \citeyear{tseng2021})\
-  to carry out the simulations of the Galactic bubbles by CR and relativistic fluid injections from the GC.
-
-  As stressed by \citet{Yang2012}, CR diffusion has an insignificant effect\
-  on the overall morphology of the \textit{Fermi} bubbles,\
-  but only sharpens the edges of the simulated bubbles by the interplay between magnetic fields\
-  and anisotropic CR diffusion with suppressed perpendicular diffusion across the bubble surface.
-
-  Moreover, the magnetic fields within the \textit{Fermi} bubbles should be weak due to\
-  adiabatic expansion, and thus the fields has\
-  a little effect on the overall dynamics.
-
-  For these two reasons,\
-  we have ignored the CR diffusion and the magnetic field throughout\
-  the simulation.\
-  Also, we do not simulate the spectral evolution of the CR\
-  and assume the pressure ratio of CR to gas is much less than 1 so that\
-  the contribution of CR pressure gradient to the momentum of the gas can be ignored.\
-  (we will see that the pressure ratio is around 0.1--0.2 throughtout the bubbles formation)\
-  Over and above, we neglect the cooling and heating processes of CRs,\
-  such as energy losses due to synchrotron and inverse Compton emission,\
-  and CR reacceleration in shocks/turbulences.
-
-  In this approach, we treat CRs as a single species without distinction between electrons and protons,\
-  and directly evolve the CR energy density $e_{\text{cr}}$\
-  as a function of \textbf{r} and $t$.\
-  The CRs are advected with the thermal gas, and in return the velocities of gas\
-  can react to the gradients of the CR pressure via the source term\
-  containing spatial divergence of fluid velocities.
-
-  Since the relativistic fluid ejected by the jet source\
-  is quickly stalled off and slowed down by the dense ISM in a short time,\
-  and the relativistic fluid\
-  accounts for a little minority of total mass inside the simulation box,\
-  we still use the Newtonian gravity to attack this problem.
+  to carry out the simulations of the Galactic bubbles formed by CR and relativistic-fluid injections from the GC.
 
@@
   including CR advection, and dynamical coupling between the thermal gas and CRs without CR diffusion\
-  can be written a succinct form as
+  can be written in a succinct form as
 
@@
   $c$ is the speed of light, and $\delta^{ij}$ is the Kronecker delta notation.\
-  Throughout this paper, Latin indices run from 1 to 3, except when stated otherwise.\
-
-  The set of Eq. \ref{governing-eq} is closed by using the Taub-Mathews equation of state \citep{Taub,TM_EOS}\
+  Throughout this paper, Latin indices run from 1 to 3, except when stated otherwise.
+The set of Eq.
+\ref{governing-eq} is closed by using the Taub-Mathews equation of state \citep[EoS;][]{Taub,TM_EOS}\
   that approximates the exact EoS \citep{Synge} for ultra-relativistically\
   hot gases coexisting with non-relativistically cold gases.
+  %Since the relativistic fluid ejected by the jet source\
+  %is quickly stalled off and slowed down by the dense ISM,\
+  %and the relativistic fluid\
+  %accounts for a little minority of total mass inside the simulation box,\
+  %we still use the Newtonian gravity to attack this problem.
 
@@
   primitive ($\rho$, $U^{j}$, $p$) and conserved variables ($D$, $M^{j}$, $\tilde{E}$),\
-  significantly reducing numerical error caused by catastrophic cancellations\
-  that commonly occur within the regions with high Mach number flows. e.g., jet-ISM interaction zones.
-
+  significantly reducing numerical errors caused by catastrophic cancellations\
+  that commonly occur within the regions with high Mach number flows. e.g., jet-ISM interaction zones.\
   \textsc{gamer-sr} also adaptively and locally reduce the min-mod coefficient\
@@
 
-  \subsection{The Galactic and Disk Models}
+  In order to track the evolution of CRs injected by the AGN jets and make predictions of the non-thermal radiation they produce, we adopt the CR hydrodynamic formalism and model the CRs as a second fluid \citep{Zweibel2013}.
+The approach is similar to previous works of \cite{Guo2012} and \cite{Yang2012}, but generalized to CRs that couple with thermal gas moving with relativistic speeds.
+The detailed implementations in \textsc{gamer-sr} and tests of the algorithm can be found in a forthcoming paper \citep[][in prep.]{Chen2022}.
+In this approach, the CRs are treated as a single species without distinctions between CR electrons and protons,\
+  and the CR energy density $e_{\text{cr}}$ is evolved according to Eq. \ref{E evolution}.
+  The CRs are advected with the thermal gas and can have adiabatic compression and expansion with the gas.
+Also, we do not simulate the spectral evolution of the CRs and assume that the CR-to-gas pressure ratio is much less than 1 so that\
+  the contribution of CR pressure gradient to the momentum of the gas can be ignored\
+  (we will see that the pressure ratio is around 0.1--0.2 throughout the simulations).
+Note that, although our later calculations of the non-thermal spectra are based on the leptonic model, only a small fraction of the simulated CRs is required to produce the observed gamma-ray and microwave emission \citep{Yang2013}.
+{\color{red} KY: Is this also true in the current simulations?
+That is, from the simulated CR energy densities, did you have to apply a normalization constant to match with the observed gamma-ray/microwave spectra?} Therefore, in the simulations we have neglected the cooling of CRs because it should have a negligible impact on the overall dynamics.
+  %Over and above, we neglect the cooling and heating processes of CRs,\
+  %such as energy losses due to synchrotron and inverse Compton emission,\
+  %and CR reacceleration in shocks/turbulences.
+
+  As stressed by \citet{Yang2012}, CR diffusion with a canonical diffusion coefficient of $\kappa \sim 3\times 10^{28}$ cm$^2$ s$^{-1}$ in the Galaxy has a minor effect\
+  on the overall morphology of the \textit{Fermi} bubbles as it
+  only acts to smooth the CR distributions on the scales of $l \sim \sqrt{\kappa t} \sim 0.3\ (t/1 {\rm Myr})$ kpc.
+Including anisotropic CR diffusion can also help to sharpen the edges of the bubbles due to interplay between the magnetic field\
+  and anisotropic CR diffusion with suppressed perpendicular diffusion across the bubble surface.
+As for the magnetic field, \cite{Yang2013} has found that the magnetic field within the \textit{Fermi} bubbles needs to be amplified to comparable values to the ambient field in order to reproduce the microwave haze emission.
+We thus directly adopt the exponential model for the magnetic field distribution in our calculation for the haze (see descriptions in Section \ref{sec:model}).
+%  Furthermore, the magnetic field within the \textit{Fermi} bubbles should be weak due to\
+%  adiabatic expansion, and thus the fields has\
+%  a little effect on the overall dynamics.
+   For the above reasons, we have ignored CR diffusion and the magnetic field in the simulations.\
+
+  \subsection{The Galactic and Disk Models} \label{sec:model}
   As a proof-of-concept study, we approximate conventionally axisymmetric stellar potential of Milky Way\
-  by a plane-parallel potential that is symmetric about the mid-plane, or the Galactic plane, $z=0$\
-  in a simulation box size of\
-  $14\times14\times28$ kpc, slightly larger than the size of eROISTA bubbles.
-
-  The plane-parallel potential is fixed throughout our simulations and given by
+  by a plane-parallel potential that is symmetric about the Galactic plane, $z=0$,\
+  in a simulation domain of\
+  $14\times14\times28$ kpc, slightly larger than the size of eROISTA bubbles. The plane-parallel potential is fixed throughout our simulations and given by
   \begin{equation}
@@
   $\Phi_{\text{halo}}(z)=v^2_{\text{halo}}\ln\left(z^2+d^2_{\text{h}}\right)$\
-  is a plane-parallel dark logarithmic halo potential.
+  is a plane-parallel logarithmic dark halo potential.
 
-  With the help of the isothermal and hydrostatic equilibrium conditions,\
-  and assuming the interfaces between the isothermal disc and atmosphere are in thermal pressure equilibrium,\
-  we can write the steady-state gaseous density distribution,\
-  confined in the total potential, of the disc and  Galactic atmosphere as\
+  With the isothermal assumption and the condition of hydrostatic equilibrium within the total potential of the disk and halo, as well as pressure equilibrium between the isothermal disk and the halo gas, we can write down the steady-state gaseous density distribution as\
   \begin{subequations}
@@
   where $m_{\text{p}}$ is the proton mass,\
-  $T_{\text{isoDisk}}$ and $T_{\text{atmp}}$ is the temperature of the isothermal disc and atmosphere,\
-  $\rho_{\text{isoDisk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the peak mass density\
-  of the disc and atmosphere on the mid-plane $z=0$.
+  $T_{\text{isoDisk}}$ and $T_{\text{atmp}}$ are the temperature of the isothermal disk and the ambient atmosphere, and\
+  $\rho_{\text{isoDisk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ are the peak density\
+  of the disk and the atmosphere at $z=0$, respectively.
 
-  We tabulate parameters in the first four\
-  categories of \Cref{table-parameters},\
+  We tabulate parameters adopted for the Galactic model in \Cref{table-parameters},\
   except for $\rho_{\text{atmp}}^{\text{peak}}$ that\
-  can be derived from the other known parameters and thermal pressure equilibrium condition\
-  on the interfaces $(z=\pm z_{0})$ between the disc and atmosphere.\
-
-  The density profile of Eq. \ref{disc-atm-sys} is shown in Fig. \ref{fig__initial-density-profile}.\
-  Beyond the core radius ($\sim 2 \text{ kpc}$) the gaseous density decreases rapidly as a power-law.
+  can be derived from the other known parameters and the pressure equilibrium condition\
+  at the interfaces $(z=\pm z_{0})$ between the disk and the atmosphere. The density profile of Eq. \ref{disc-atm-sys} is shown in Fig. \ref{fig__initial-density-profile}.\
+  Beyond the core radius ($\sim 2 \text{ kpc}$) the gas density decreases rapidly as a power-law.
 
@@
     \includegraphics[width=\columnwidth]{figures/fig__initial-density-profile.png}
-    \caption{The density profile of the isothermal disc (red pluses) and\
-             atmosphere (blue crosses) along the positive z-axis.\
-             The density distribution is derived from hydrostatic equilibrium,\
-             the interface ($z=0.1$) between the isothermal disc\
-             and the atmosphere is pressure balanced.}
+    \caption{The density profile of the isothermal disk (red pluses) and\
+             the ambient atmosphere (blue crosses) along the positive $z$-axis.\
+             The density distribution is derived from the condition of hydrostatic equilibrium.\
+             The gas at the interface between the isothermal disk\
+             and the atmosphere at $z=0.1$ is in pressure equilibrium.}
     \label{fig__initial-density-profile}
@@
 
-  To quantify the synchrotron radiation as a function of position,\
+  To compute the predicted synchrotron radiation as a function of position,\
   we adopt the default exponential magnetic field in \textsc{galprop} \citep{Strong2007}
@@
 
-  A crucial component in our work is the clumpy ISM disc initialized by\
+  A crucial component in our work is the clumpy ISM disk initialized by\
   the publicly available pyFC code
-  \footnote{\url{https://pypi.python.org/pypi/pyFC}}.\
-
+  \footnote{\url{https://pypi.python.org/pypi/pyFC}}.
   pyFC randomly generates dimensionless 3D scalar field $f(\bold{x})$\ % that is clumpy and porous.
@@
   a Nyquist limit $k_{\text{max}}$, and a lower cutoff wave number $k_{\text{min}}$.
-  $k_{\text{max}}$ is one-half of the spatial resolution within the disc,\
-  and $k_{\text{min}}$ is 375.0, corresponding to the maximum size of an individual clump $\sim 20$ pc.\
+  $k_{\text{max}}$ is one-half of the spatial resolution within the disk,\
+  and $k_{\text{min}}$ is 375.0, corresponding to the maximum size of an individual clump of $\sim 20$ pc.\
   \citet{LA2002} and \citet{Wagner2012} have outlined a detailed procedure\
-  for constructing a clumpy scalar field, and we do not repeat here.
+  for constructing a clumpy scalar field, and we refer the readers for more information.
 
-  The density of the clumpy disc can thus be obtained by taking the scalar products of\
-  $f(\bold{x})$ with $\rho_{\text{isoDisk}}(z)$ over all cells within the disc, i.e.,\
+  The density of the clumpy disk can then be obtained by taking the scalar products of\
+  $f(\bold{x})$ with $\rho_{\text{isoDisk}}(z)$ over all cells within the disk, i.e.,\
   $\displaystyle\rho_{\text{ismDisk}}(\bold{x}) =\
   f(\bold{x}) \rho_{\text{isoDisk}}(z)$.\
-  Also, the thermal pressure equilibrium within the clumpy disc implies that the temperature of the disc is
+  Also, the thermal pressure equilibrium within the clumpy disk implies that the temperature of the disk is
   $\displaystyle T_{\text{ismDisk}}(\bold{x}) =\
-  T_{\text{isoDisk}}(z)\rho_{\text{isoDisk}}(z)/\rho_{\text{ismDisk}}(\bold{x})$.
-
-  The last category in \Cref{table-parameters} summarize the parameters of the clumpy disc and their references.
+  T_{\text{isoDisk}}(z)\rho_{\text{isoDisk}}(z)/\rho_{\text{ismDisk}}(\bold{x})$. The last category in \Cref{table-parameters} summarizes the parameters of the clumpy disk and their references.
 
   On the basis of this setup, we cover the AMR base level with\
-  $16\times16\times32$ root cells, refined progressively on the mid-plane $z=0$\
-  based on the gradient of mass density.\
-  We also restrict the refinement level at 7 within the disc so that\
-  a molecular cloud can be adequately resolved by approximately 30 cells along their diameter, 20 pc.
-
-  In this way, we plot the volume filling factor as a function of\
-  initial number density within the disc without the jet source in Fig. \ref{fig__numberDensityHistogram},\
+  $16\times16\times32$ root cells, refined progressively on the mid-plane at $z=0$\
+  based on the gradient of density.\
+  We also restrict the refinement level at 7 within the disk so that\
+  a molecular cloud can be adequately resolved by approximately 30 cells along their diameter of 20 pc. We plot the volume filling factor as a function of\
+  initial number density within the disk without the jet source in Fig. \ref{fig__numberDensityHistogram},\
   and show a close-up view of the\
   pressure, temperature, and number density slices
-  in the y-z plane through the center of the disc in Fig. \ref{fig__zoom-in-disc} .
+  in the $y-z$ plane through the center of the disk in Fig. \ref{fig__zoom-in-disc}.
 
@@
     \caption{The volume filling factor as a function of\
-             initial number density within the disc without jet source.\
+             initial number density within the disk without the jet source.\
              The vertical bands from left to right depict the allowable number densities \citep{peak-ism-density} for\
@@
              pressure (top), temperature (middle), and number density (bottom) slices\
-             in the y-z plane through the center of the disc.
+             in the $y-z$ plane through the center of the disk.
              }
@@
 \raggedright
-\caption{Parameters of the disc, atmosphere, and gravitational potential in the simulations.}
+\caption{Parameters of the disk, atmosphere, and gravitational potential in the simulations.}
 \label{table-parameters}
@@
 {\bf Static stellar potential }       &                                &                                      &                                \\
-$\sigma_{\text{bulge}}$               & Velocity dispersion of bulge   & 100 km$\cdot$s$^{-1}$                & \citep{velocity-dispersion-MW} \\
-$\rho_{\text{bulge}}^{\text{peak}}$   & Peak average density of bulge  & $4\times 10^{-24}$ g$\cdot$cm$^{-3}$ &   N/A                          \\ \hline
+$\sigma_{\text{bulge}}$               & Velocity dispersion of bulge   & 100 km s$^{-1}$                & \citep{velocity-dispersion-MW} \\
+$\rho_{\text{bulge}}^{\text{peak}}$   & Peak average density of bulge  & $4\times 10^{-24}$ g cm$^{-3}$ &   N/A                          \\ \hline
 {\bf Static dark halo potential }     &                                &                                      &                                \\
-$v_{\text{halo}}$                     & Characteristic velocity        & 131.5 km$\cdot$s$^{-1}$              & \citep{Johnston1995}           \\
+$v_{\text{halo}}$                     & Characteristic velocity        & 131.5 km s$^{-1}$              & \citep{Johnston1995}           \\
 $d_{\text{h}}$                        & Core radius                    & 12 kpc                               & \multicolumn{1}{c}{''}         \\ \hline
@@
 $T_{\text{\text{atmp}}}$              & Temperature of atmosphere      & $10^{6}$ K                           & \citep{temperature-MW}         \\ \hline
-{\bf Isothermal disc }                &                                &                                      &                                \\
-$z_{0}$                               & Scale height of disc           & 100 pc                               & \citep{peak-ism-density}       \\
-$T_{\text{\text{isoDisk}}}$           & Temperature of disc            & $10^{3}$ K                           & \multicolumn{1}{c}{''}         \\
-$\rho_{\text{isoDisk}}^{\text{peak}}$ & Peak mass density of disc      & $10^{-23}$ g$\cdot$cm$^{-3}$         & \multicolumn{1}{c}{''}         \\ \hline
-{\bf Clumpy disc }                    &                                &                                      &                                \\
-$\dagger$  $k_{\text{min}}$           & Cutoff wave number             & 375.0                                & \citep{peak-ism-density}       \\
+{\bf Isothermal disk }                &                                &                                      &                                \\
+$z_{0}$                               & Scale height of disk           & 100 pc                               & \citep{peak-ism-density}       \\
+$T_{\text{\text{isoDisk}}}$           & Temperature of disk            & $10^{3}$ K                           & \multicolumn{1}{c}{''}         \\
+$\rho_{\text{isoDisk}}^{\text{peak}}$ & Peak density of disk      & $10^{-23}$ g cm$^{-3}$         & \multicolumn{1}{c}{''}         \\ \hline
+{\bf Clumpy disk }                    &                                &                                      &                                \\
+$k_{\text{min}}^\dagger$            & Cutoff wave number             & 375.0                                & \citep{peak-ism-density}       \\
 $\mu$                                 & Mean of scalar field           & 1.0                                  &   N/A                          \\
-$\ddag$  $\sigma$                     & Dispersion of scalar field     & 5.0                                  & \citep{Federrath2010}          \\
+$\sigma^\ddag$                 & Dispersion of scalar field     & 5.0                                  & \citep{Federrath2010}          \\
 $\beta$                               & Power law index                & -5/3                                 &   N/A                          \\ \midrule
@@
       \raggedright
-      \item  $\dagger$  $k_{\text{min}}=375.0$ leads to the size of an individual molecular cloud $\sim 100$ pc.
+      \item  $\dagger$  $k_{\text{min}}=375.0$ leads to the size of an individual molecular cloud of $\sim 100$ pc.
       \item  $\ddag$ In numerical simulations of turbulence,\
@@
 
-\subsection{Oblique jets injection}
+\subsection{Oblique jets}
 
-  We simulate the jet with an inclination angle\
+  We simulate the jets emanating from the GC with an inclination angle\
   $45^{\circ}$ with respect to the Galactic plane\
-  in order to release the caveat that\
+  in order to alleviate the constraint that\
   the jet direction must be perpendicular to the Galactic plane, and in particular to\
-  investigate how the dense disc affect the bubbles formation.
+  investigate how the dense disk affects the bubble formation.
 
-  A few additional quantities are used to characterize the jets:
-  the density contrast between the thermal gas contained in the jet source and the atmosphere gas,\
+  We use the following quantities to characterize the jets:
+  the density contrast between the thermal gas contained in the jet source and the ambient gas,\
   $\rho_{\text{jet}}/\rho_{\text{amb}}=10^{-3}$,\
   the temperature contrast, $T_{\text{jet}}/T_{\text{amb}}=2\times10^{4}$,\
-  the pressure ratio of CR to gas is 0.18,\
-  and the flow 4-velocity inside the jet source $\beta\gamma = 0.6$\
-  along the symmetric axis of cylinder.\
-  The jet power is thus $3.2\times 10^{42}$ erg/s, resulting in the Eddington ratio 0.008.
-
-  Note that as we inject the jets at the center of the clumpy disc,\
+  the CR-to-gas pressure ratio of 0.18,\
+  and the flow 4-velocity inside the jet source along the jet axis, $\beta\gamma = 0.6$.\
+  The jet power is thus $3.2\times 10^{42}$ erg s$^{-1}$, resulting in an Eddington ratio of 0.008.\
+  Note that since we inject the jets at the center of the clumpy disk,\
   we define the atmosphere gas density by the peak density of\
   the isothermal disc on the mid-plane $z=0$ (i.e. $\rho^{\text{peak}}_{\text{isoDisk}}$),\
-  as opposed to the \textit{clumpy} density around the jet source, to avoid ambiguous definition.
+  as opposed to the \textit{clumpy} density around the jet source.
 
-  The bipolar jets are constantly ejected from a cylindrical source at the beginning of simulation ($t=0$)\
-  and suddenly quenched at $t=1.2$ Myr before fully breaking out the disc.\
-  Without quenching, the Galactic bubbles at the present time will be asymmetric about the Galactic plane.
-  The jet duration allows the total ejected energy to be $1.2\times10^{56}$ erg between\
-  $8\times10^{55}$ erg and $1.3\times10^{56}$ erg, estimated by \citet{Predehl2020}.\
+  The bipolar jets are constantly ejected from a cylindrical source starting from the beginning of simulation ($t=0$)\
+  and suddenly quenched at $t=1.2$ Myr before fully breaking out the disk.\
+  Without quenching, the Galactic bubbles at the present time would be asymmetric about the Galactic plane.
+  The jet duration allows the total ejected energy to be $1.2\times10^{56}$ erg, \
+  within the range of estimates obtained by \citet{Predehl2020} between\
+  $8\times10^{55}$ erg and $1.3\times10^{56}$ erg.
 
   The diameter and height of cylindrical source are 4 pc,\
-  leading to the source volume ($\sim 50 \text{ pc}^{3}$) is\
-  much smaller than that of an individual clump by a factor of about 83.\
+  leading to a source volume ($\sim 50 \text{ pc}^{3}$)\
+  much smaller than that of an individual clump by a factor of $\sim 83$.\
   By intentionally reducing the volume ratio of the jet source to an individual clump,\
   we can mitigate the effect of the randomness of the clumps on the bubbles.\
-  Moreover, we resolve the jet source with the highest refinement level 11,\
+  Moreover, we resolve the jet source with the highest refinement level of 11,\
   bringing the finest spatial resolution up to 0.4 pc.\
@@
  with the initial condition specified in Section \ref{Methodology}\
- shows that the edge of the outermost bubbles is indeed a forward shock,\
- expanding 12.5 kpc above and below the Galactic plane,\
+ shows that the edge of the outermost bubbles is a forward shock,\
+ expanding to 12.5 kpc above and below the Galactic plane,\
  with a semiminor axis about 6.8 kpc on the plane.\
- We note that the overall extent of the outermost bubbles is comparable to\
- the two spherical objects of a radius 6-7 kpc proposed by \citet{Predehl2020}\
- for modeling the eROSITA bubbles\
- based on X-ray emissions.
+ The overall extent of the outermost bubbles is comparable to\
+ the two spherical objects of a radius of 6-7 kpc estimated by \citet{Predehl2020}\
+ for modeling the eROSITA bubbles.\
+ The temperature profile (left middle panel in Fig. \ref{fig__profile}) along the positive $z$-axis in\
+ Fig. \ref{fig__jetI5+ismSeed3-45deg} indicates that\
+ the temperature of the smooth region (purple band in Fig. \ref{fig__profile})\ %emitting X-ray\
+ is around 0.3-0.5 keV, similar to that observed by \citet{Miller2016} and \citet{Kataoka2018}. {\color{red} KY: What did these observations constrain exactly?}
 
- The temperature profile (left middle panel in Fig. \ref{fig__profile}) along the positive z-axis in\
- Fig. \ref{fig__jetI5+ismSeed3-45deg} indicates that\
- the temperature of the smooth region (purple band in Fig. \ref{fig__profile}) emitting X-ray\
- is around 0.3-0.5 keV, similar to that observed by \citet{Miller2016} and \citet{Kataoka2018}.
+ Followed by the forward shock is a turbulent and hot plasma extending to a height of $\sim 8$ kpc (Fig. \ref{fig__profile}).\
+ The extent of the turbulent plasma approximately agrees with\
+ that of the observed \textit{Fermi} bubbles \citep{Su2010}.
+ Also, the temperature of the plasma is around 2 keV,\
+ comparable to few keV inside the \textit{Fermi} bubbles\
+ estimated by observing X-ray absorption lines through the hot\
+ gaseous halo along many different sight lines in the sky \citep{Miller_2013}.\
+ We also note that the turbulent, hot plasma is in pressure balance with the external medium,\
+ suggesting the outer edge of the \textit{Fermi} bubbles\
+ is a contact discontinuity rather than a shock \citep{Zhang2020}.
 
- Followed by the forward shock is a turbulent and hot plasma.\
- As shown in the temperature or density slices of the fiducial run,\
- the full extent of the turbulent plasma is approximately agree with\
- that of the observed \textit{Fermi} bubbles \citep{Su2010}.
- Also, the temperature of the plasma is as high as 2 keV,\
- comparable to few keV inside the \textit{Fermi} bubbles\
- obtained by observing X-ray absorption lines through the hot\
- gaseous halo along many different sight lines in the sky \citep{Miller_2013}.\
- We also note that the turbulence within the hot plasma is in pressure balance with the external medium,\
- suggesting the outer edge of the \textit{Fermi} bubbles\
- is a turbulence rather than a smooth shock \citep{Zhang2020}.
-
- The most interesting finding is that there are innermost bubbles\
+ An interesting feature found in our simulations is that there are a pair of innermost bubbles\
  (dashed box in the top panel of Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
@@
  and underpressured with respect to the turbulent plasma.\
-
- Moreover, the close-up view (right column in Fig. \ref{fig__profile}) of profiles\
+ The close-up view (right column in Fig. \ref{fig__profile}) of the vertical profiles\
  and slices (Fig. \ref{fig__innerbubbles})\
- demonstrate that there is a sharp pressure jump on the edge of the innermost bubbles ($z=3.62$ kpc),\
- indicating that the innermost bubbles are an expanding reverse shock.\
- The high density upstream of the reverse shock requires\
+ demonstrate that there is a sharp pressure jump at the edge of the innermost bubbles at $z=3.62$ kpc,\
+ indicating that the innermost bubbles are an expanding reverse shock.\ {\color{red} KY: Is it verified that the reverse shock is expanding outward?}
+ The high-density upstream of the reverse shock requires\
  an even higher density downstream.\
- Continuing outward, the higher density must match with low density further downstream;\
- thus there exists a dense shell.
-
+ Continuing outward, there exists a dense shell before the gas density drops to values further downstream.
+ %Continuing outward, the higher density must match with low density further downstream;\
+ %thus there exists a dense shell.\
  The turbulent plasma is therefore bracketed between the downstream of reverse shock\
@@
 
- We stressed that either the outermost, turbulent plasma, or innermost bubbles\
- are symmetric about the Galactic plane despite the jet is tilted to the disk normal\
- at an angle $45^{\circ}$.
+ We stress that either the outermost shock, turbulent plasma, or innermost bubbles\
+ are symmetric about the Galactic plane despite that the jets are tilted to the disk normal\
+ at an angle of $45^{\circ}$.
 
- Fig. \ref{fig__jetI5+ismSeed3-45deg} shows the slices of various gas properties at $t=12.39$ Myr,\
- including pressure (top), temperature (middle),\
- density (bottom) with the same jet source as the fiducial run\
- but in different Galactic environments.
-
- We compare the clumpy disk (Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
- with the smooth disc (Fig. \ref{fig__jetI5+ismSeed3-45deg-b}),\
- specified by the initial density profile shown in Fig. \ref{fig__initial-density-profile},\
- in a stratified atmosphere.\
- The results show that the initial density distribution of\
- the dense disc has an insignificant effect\
- on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
- in an uniform atmosphere (Fig. \ref{fig__jetI5+ismSeed3-45deg-c}) is spherical-shape,\
- suggesting the stratification facilitates the outermost bubbles elongation significantly.\
- Also, Fig. \ref{fig__jetI5+ismSeed3-45deg-c} and \ref{fig__jetI5+ismSeed3-45deg-d}\
+ In addition to the fiducial run, in Fig.
+\ref{fig__jetI5+ismSeed3-45deg} we also show the slices of various gas properties at $t=12.39$ Myr in different Galactic environments.
+We compare the clumpy disk (Fig.
+\ref{fig__jetI5+ismSeed3-45deg-a})\
+ with the smooth disk in a stratified atmosphere (Fig. \ref{fig__jetI5+ismSeed3-45deg-b}; the initial density profile is shown in Fig. \ref{fig__initial-density-profile}). \
+ The results show that the clumpiness of\
+ the dense disk has an insignificant effect\
+ on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disk\
+ in a uniform atmosphere (Fig. \ref{fig__jetI5+ismSeed3-45deg-c}) is quasi-spherical,\
+ suggesting that the stratification facilitates the elongation of the outermost bubbles significantly. Fig. \ref{fig__jetI5+ismSeed3-45deg-c} and \ref{fig__jetI5+ismSeed3-45deg-d}\
  reveal that the development of the innermost bubbles\
- is always associated with the disc, without the disc (Fig. \ref{fig__jetI5+ismSeed3-45deg-d}),\
- the outermost bubbles and the turbulent plasma will be oblique,\
- indicating the dense disc is crucial for\
- the symmetry of the Galactic bubbles and for the innermost bubbles formation.
+ is always associated with the disk. Also, without the disk (Fig. \ref{fig__jetI5+ismSeed3-45deg-d}),\
+ the outermost bubbles and the turbulent plasma would be oblique,\
+ indicating that the dense disk is crucial for the production of symmetric Galactic bubbles.\
 
@@
              Comparison between the clumpy (Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
-             and the smooth disc (Fig. \ref{fig__jetI5+ismSeed3-45deg-b}) in a stratified atmosphere\
-             shows that the initial density distribution of the dense disc has an insignificant effect\
+             and the smooth disks (Fig. \ref{fig__jetI5+ismSeed3-45deg-b}) in a stratified atmosphere\
+             shows that the initial density distribution of the dense disk has an insignificant effect\
              on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
-             in an uniform atmosphere (Fig. \ref{fig__jetI5+ismSeed3-45deg-c}) is spherical-shape,\
-             suggesting the stratification facilitates the outermost bubbles elongation significantly.\
+             in an uniform atmosphere (Fig. \ref{fig__jetI5+ismSeed3-45deg-c}) is nearly spherical,\
+             suggesting that the stratification facilitates the elongation of the outermost bubbles significantly.\
              Also, Fig. \ref{fig__jetI5+ismSeed3-45deg-c} and \ref{fig__jetI5+ismSeed3-45deg-d}\
              reveal that the development of the innermost bubbles\
-             is always associated with the disc, without the disc (Fig. \ref{fig__jetI5+ismSeed3-45deg-d}),\
-             the outermost bubbles and the turbulent plasma will be oblique,
-             indicating the dense disc is crucial for\
-             the symmetry of the Galactic bubbles and for the innermost bubbles formation.
+             is always associated with the disk. Also, without the disk (Fig. \ref{fig__jetI5+ismSeed3-45deg-d}),\
+             the outermost bubbles and the turbulent plasma would be oblique,
+             indicating that the dense disk is crucial for the production of symmetric Galactic bubbles.\ {\color{red} KY: Consider reducing the caption as it is essentially the same as the text.}
       }
@@
              and number density (bottom)\
-             along the positive z-axis in Fig. \ref{fig__jetI5+ismSeed3-45deg}.
+             along the positive $z$-axis in Fig. \ref{fig__jetI5+ismSeed3-45deg}.
              Right: the close-up view of the profiles in the yellow band.\
@@
 
-  \subsection{X-ray}
+  \subsection{Morphology and Profiles in X-ray}
   \label{X-ray}
   The X-ray emissivity is computed\
-  for each computational volume cell
+  for each computational cell
   using the MEKAL model \citep{Xray-1,Xray-2,Xray-3}\
   implemented in the utility XSPEC \citep{XSPEC}, assuming solar metallicity.\
-  The X-ray intensity map are then generated by projecting the emissivities\
+  The X-ray intensity map is then generated by projecting the emissivities\
   along lines of sight\
@@
 
-  We point out that the projections throughout this paper is \lq perspective\rq,\
-  which has the effect of making distant object appear smaller than the same object in the near distance,\
-  in order to facilitate a reliable interpretation of simulated all-sky map,\
-  and also that the observed X-ray emission is contributed by all the gas in the Milky Way halo,\
+  We point out that the projections used throughout this paper are \lq perspective\rq,\
+  which has the effect of making a distant object appear smaller than the same object in a closer distance,\
+  in order to facilitate a reliable interpretation of simulated all-sky map.\
+  Also, the observed X-ray emission is contributed by all the gas in the Milky Way halo,\
   which likely extends to a radius of $\sim$250 kpc \citep{halo-radius-1,halo-radius-2},\
-  much bigger than our simulation box.
-
-  We first compute the X-ray emissivity\
+  much bigger than our simulation box. Therefore, we first compute the X-ray emissivity\
   from the simulated gas within a radius of 25 kpc away from the GC.
   Then, beyond 25 kpc the gas is assumed to be isothermal with $T=10^6$ K and\
-  follows out to a radius of 250 kpc the observed density profile of \citep{temperature-MW}.
+  follows the observed density profile of \citep{temperature-MW} out to a radius of 250 kpc.
 
   Fig. \ref{fig__xray_0.8keV_angle_000} shows\
-  the comparison between simulated (top) and observed (bottom) all-sky map\
-  in the range 0.6--1.0 keV at 12.39 Myr and the present time, respectively.\
-  In the simulated map, the red arrow at the center of map represents the direction of the bipolar jet,\
-  constantly ejecting at an angle of $45^{\circ}$ to the disc normal between 0--1.2 Myr.
+  the comparison between the simulated (top) and observed (bottom) all-sky map\
+  in the range 0.6--1.0 keV.\
+  In the simulated map, the red arrow at the center represents the direction of the bipolar jets,\
+  constantly ejecting at an angle of $45^{\circ}$ to the disk normal between 0--1.2 Myr.
+Fig.
+\ref{fig__x-ray-profile-0.8keV-000} displays the simulated X-rray photon count rates as a function of Galactic longitudes (red)\
+  in the same energy band as in Fig. \ref{fig__xray_0.8keV_angle_000}\
+  cut at various Galactic latitudes (as labelled), compared with the observed profiles (black).
 
-  Fig. \ref{fig__x-ray-profile-0.8keV-000} displays the simulated count rate profiles (red)\
-  in the same energy band as Fig. \ref{fig__xray_0.8keV_angle_000}\
-  cut at various galactic latitudes (as labelled), compared with the observation (black).\
-  Fig. \ref{fig_xray-map} is quite revealing in several ways.\
-
+  {\color{red} KY: Please rewrite the following two paragraphs so that (1) the overall agreement between the simulated and observed bubble morphology and profiles are emphasized before discussing about discrepancies, and (2) some of the disagreement for the northern bubble could be due to the North Polar Spur.}
   First, we observe that\
@@
                Throughout this paper we show sky maps\
-               in Galactic coordinates centered on the Galactic center using a Hammer-Aitoff projection,\
-               and observed from the solar system.\
+               in Galactic coordinates centered on the Galactic center using a Hammer-Aitoff projection.\
+               %and observed from the solar system.\
                The red arrow at the center of the\
-               top panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
-               to the disc normal in 1.2 Myr.
+               top panel depicts the direction of the bipolar jets, constantly ejecting at an angle of $45^{\circ}$\
+               to the disk normal for the first 1.2 Myr.
          }%
@@
          \caption{
-               Comparison of simulated (red) and observed (black; \citealt{Predehl2020}) one-dimensional\
-               count rate profiles in the same energy band as Fig. \ref{fig__xray_0.8keV_angle_000},\
-               cut at various galactic latitudes (as labelled).
+               Comparison of the simulated (red) and observed (black; \citealt{Predehl2020}) one-dimensional photon\
+               count-rate profiles in the same energy band as in Fig. \ref{fig__xray_0.8keV_angle_000},\
+               cut at various Galactic latitudes (as labelled).
          }%
@@
 \label{sec:gamma-ray-microwave}
-In this section, we give the constraint on the CRe spectral index by\
+In this section, we obtain the constraint on the CRe spectral index by\
 comparing the simulated gamma-ray and microwave spectra\
@@
 
-The simulated gamma-ray and microwave spectra is based on the\
-IC scattering and synchrotron, respectively, from CRe.\
-The CRe spectrum follows a power-law distribution ranging from\
+We assume the leptonic model for the gamma-ray and microwave emission as previous studies have shown that the bubble and haze spectra can be simulataneously produced by the same population of CRe \citep{Su2010, Ackermann2014, Yang2022}.
+In the leptonic scenario, the gamma-ray and microwave emission come from IC scattering of the ISRF and synchrotron radiation, respectively.\
+Because the evolution of CR spectrum is not modelled in the simulations, we assume that the CRe spectrum is spatially uniform and follows a power-law distribution ranging from\
 $0.5$ MeV to $562.1$ GeV.
@@
 
-where $\sigma_{T}$ is the Thomson cross section, $c$ speed of light,\
-$m_{\text{e}}$ electron mass,\
-$n(\epsilon)$ the energy distribution of the photon number density in ISRF given by \citet{Porter2017},\
-$\gamma$ the Lorentz factor of CRe,\
-$\mathbb{C}$ and $p$ are the normalization constant and spectral index of CRe power-law spectrum.
+where $\sigma_{T}$ is the Thomson cross section, $c$ is the speed of light,\
+$m_{\text{e}}$ is the electron mass,\
+$n(\epsilon)$ is the energy distribution of the photon number density in the ISRF given by \citet{Porter2017},\
+$\gamma$ is the Lorentz factor of CRe, and\
+$\mathbb{C}$ and $p$ are the normalization constant and spectral index of the CRe power-law spectrum.
 $\gamma_{\text{min}}(\epsilon)$ is the minimum Lorentz factor of CRe\
-that allows incident photons to scatter from energy $\epsilon$ to $\epsilon_{1}$.
-$\gamma_{\text{max}}$ is the maximum CRe Lorentz factor in the spectrum.
-
-We perform the double integration in Eq. \ref{gammaray-emissivity} on each cell\
-over the range of CRe Lorentz factor, and\
+that allows the incident photons to be scattered from energy $\epsilon$ to $\epsilon_{1}$, and\
+$\gamma_{\text{max}}$ is the maximum CRe Lorentz factor in the spectrum. To obtain the simulated IC emissivities, we perform the double integration in Eq. \ref{gammaray-emissivity} on each cell\
+over the range of the CRe Lorentz factor and\
 the range of incident photon energy between\
 $\epsilon_{\text{min}}=1.13\times10^{-4}$ eV (cosmic microwave background) and\
-$\epsilon_{\text{max}}=13.59$ eV (optical starlight)\
-to obtain the simulated IC emissivities.
+$\epsilon_{\text{max}}=13.59$ eV (optical starlight).\
 
@@
 
-where $\Gamma$ is the gamma function, $B$ is the magnetic field strength defined in\
-Eq. \ref{magnetic-field}.
-
-For a given longitude and latitude range, the simulated spectra are\
+where $\Gamma$ is the gamma function, and $B$ is the magnetic field strength defined in\
+Eq. \ref{magnetic-field}. For a given longitude and latitude range, the simulated spectra are\
 computed by projecting emissivities\
 as we project X-ray emissivities in Section \ref{X-ray},\
-and then we average the spectra over all the sight lines within the region on sky.
+and then we average the spectra over all the sight lines within the region on the sky.
 
@@
 and gamma-ray (right) spectra averaged over the different patches (shown in the legends) of the sky.\
-The row from top to bottom shows the spectra with different CRe spectral index $2.2, 2.4$ and $2.6$.\
-Several points are worth specific comment.\
+The rows from top to bottom show the spectra with different assumptions of the CRe spectral index, $2.2, 2.4$ and $2.6$.\
+We highlight our findings as follows.\
 
-First, we find that the simulated gamma-ray spectra are well fitted by\
-the CRe spectral index 2.4 (the middle row),\
-despite the simulated microwave spectra are marginally consistent with the observed.
+First, we find that, among the three values of the CR spectral indices assumed, a CRe spectral index of 2.4 (the middle row) provides the best fits for both the the simulated gamma-ray spectra as well as the microwave spectra.
+This value is slightly steeper than the best-fit spectral index of $\sim 2.17$ found by \cite{Ackermann2014}.
+However, we note that our calculation takes into account the 3D variations of the ISRF, whereas the previous constraint was based on the ISRF at a fixed height of 5 kpc away from the Galactic plane.
 
-Second, the simulated and observed gamma-ray spectra is\
-nearly latitude independent, and characterized by a broad bump that roughly peaks around $\sim10$ GeV.\
-However, the high-latitude spectrum tends to be slightly dimmer than low-latitude\
-probably because the optical intensity in ISRF decays with increasing latitude.
+Second, the simulated gamma-ray spectra are\
+nearly latitude independent.
+Note that we have assumed spatially uniform spectrum for the underlying CRe, and hence the simulated gamma-ray spectra at different latitudes mainly reflect how the 3D distribution of the simulated CR number density (see Fig.
+\ref{fig__jetI5+ismSeed3-45deg-CR})  is projected into different latitude bins.
+Overall we find good agreement between the simulated and observed spectra \citep{Ackermann2014}; only the simulated spectrum at high latitudes tends to be slightly dimmer than the lower-latitude spectrum because the optical intensity in the ISRF decays with increasing latitudes.
 
-Third, the gamma-ray spectra for all latitudes indicate a spectral cutoff around energies 400--500 GeV,\
-remarkably consistent with the observed cutoff energy.\
+Third, our assumed range for the CRe spectrum (0.5 MeV to 562.1 GeV) produces gamma-ray spectra with a high-energy cutoff around energies 400--500 GeV,\
+consistent with the observed cutoff energy.\
 This is expected since\
 the upscattered high-energy photons ($\epsilon_{1}\sim450$ GeV) mainly arise from\
-the scatterings between the relativistic CRe ($\gtrapprox 408$ GeV)\
+the scattering between the relativistic CRe ($\gtrapprox 408$ GeV)\
 and optical starlight ($\epsilon \sim 10$ eV).\
@@
 
-Fourth, the good agreement between the simulated and observed gamma-ray/microwave spectra\
+Finally, the good agreement between the simulated and observed gamma-ray/microwave spectra\
 implies that, in the presence of ISRF and magnetic fields, the emission of the Fermi bubbles and\
 the microwave haze can be produced by the same high-energy electrons\
-via inverse Compton scatterings and synchrotron radiations, respectively,\
-as previously suggested \citep{Su2010,Dobler2012}.
+via IC scattering and synchrotron radiation, respectively. Our results thus provide further support for the leptonic model as previously suggested \citep{Su2010, Ackermann2014, Yang2013, Yang2022}.
 
@@
  one can see that the symmetric \textit{Fermi} bubbles\
- can also be realized by oblique jets.\
- However, we find that the simulated surface is not as smooth
- as the observed one. The instabilities at the bubble
+ can also be realized by oblique jets. The extent of the simulated gamma-ray bubbles is also comparable to the observed ones.\
+ However, we find that the simulated bubble surface is not as smooth
+ as the observed bubbles. The instabilities at the bubble
  surface may be suppressed by the magnetic draping
@@
  included in the simulations.
+With magnetic draping, the sharp edges of the observed bubbles \citep{Su2010, Ackermann2014} could also be explained by anisotropic CR diffusion along field lines \citep{Yang2013}.
 
  The simulated gamma-ray intensity
- distribution shown in Fig. \ref{fig__gammaRay-map} does not appear to be
+ distribution is shown in Fig.
+\ref{fig__gammaRay-map}.
+Though the overall size of the simulated gamma-ray bubbles is comparable to that of the observed ones, the gamma-ray intensity does not appear to be
  as uniform as originally found in \citet{Su2012}.
@@
  radiation field at lower latitudes. However, this level
- of brightness variations is consistent with the later
- observational data of \citet{Ackermann2014} and \citet{Selig2015}.
+ of brightness variations appears to be consistent with the later
+ observational data of \citet{Ackermann2014} and \citet{Selig2015}, which shows that there are some substructures in the gamma-ray intensity distribution within the bubbles.
 
- Finally, the comparison between\
+ For completeness, we show the simulated CR energy density at 12.39 Myr in Fig. \ref{fig__jetI5+ismSeed3-45deg-CR}. The comparison between\
  Fig. \ref{fig__jetI5+ismSeed3-45deg}\
@@
  shows that the CR pressure\
- is around 5$\times10^{-15}$--8$\times10^{-15}$ erg/cm$^{3}$,\
- bringing the pressure ratio of CR to gas is 0.1--0.2,
+ is around 5$\times10^{-15}$--8$\times10^{-15}$ erg cm$^{-3}$,\
+ bringing the pressure ratio of CRs to the gas to 0.1--0.2,
  similar to 0.18 at the beginning of the simulation.
@@
 to divert the oblique jets at an angle $45^{\circ}$\
-to the disk normal in the past energetic event of the central SMBH.\
+to the disk normal in the past energetic event of the central SMBH in the Milky Way Galaxy.\
 We investigate the properties of the Galactic bubbles and the microwave\
-haze using 3D special relativistic hydrodynamic simulations of CR injection from\
-the SMBH assuming the leptonic model.
-
-Our findings are as follows.
+haze using 3D SRHD simulations of CR jet injections from\
+the SMBH assuming the leptonic model. The important findings are summarized as follows.
 
@@
       the bipolar jets are at an angle $45^{\circ}$\
-      with respect to the disc normal.\
-      The broad agreement between simulated and observed multiwavelength features\
-      provides supporting evidence for the oblique jet scenario, and also\
-      releases the caveat given by earlier simulation-based studies:\
-      the jets shall be vertical to the disc normal.
-\item The randomness of clumpy disk has a insignificant impact on the overall dynamic of the Galactic bubbles.\
-      The development of the reverse shocks (the innermost bubbles) is always associated with the dense disc,\
-      without the disc, the outermost bubbles and the turbulent plasma will be oblique,\
-      indicating the dense disc is crucial for\
-      the symmetry of the Galactic bubbles and for the innermost bubbles formation.
-\item The edge of the eROSITA bubbles is a forward shock,\
-      originally driven by oblique bipolar jets emanating from the GC 12.39 million years ago,\
-      and significantly stretched by the stratified atmosphere afterwards.\
-      The simulated eROSITA bubbles are not as limb-brightened as the observation.\
-      A possibility to enhance the X-ray emission is to include shock-accelerated CRs near the shock,\
-      in which CRs could increase the compressibility of the fluid,\
-      resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density squared.
-\item Followed by the forward shock is a turbulent and hot plasma ($\sim2$ keV),\
-      which we interpret as the \textit{Fermi} bubbles.\
+      with respect to the disk normal.\
+      We showed that inclusion of the dense ISM disk (regardless of its clumpiness) is a critical component for producing the symmetric Galactic bubbles when the jets are oblique.\
+      The broad agreement between the simulated and observed multi-wavelength features\
+      demonstrates that oblique jets are a plausible scenario of forming the Galactic bubbles, which\
+      releases the caveat of earlier jet models that the jets must be vertical to the Galactic plane.\
+
+%\item The randomness of the clumpy disk has an insignificant impact on the overall dynamic of the Galactic bubbles.\
+%      The development of the reverse shocks (the innermost bubbles) is always associated with the dense disk,\
+%      without the disc, the outermost bubbles and the turbulent plasma will be oblique,\
+%      indicating the dense disc is crucial for\
+%      the symmetry of the Galactic bubbles and for the innermost bubbles formation.
+      {\color{red} KY: I removed the second point about the innermost bubbles for now, because I think the following two points should be separated: (1) inclusion of the disk is critical for forming symmetric Galactic bubbles, (2) we found a pair of innermost bubbles which are reverse shocks (and perhaps comment on their properties and/or observable signatures).}
+\item In the oblique jet scenario, the edge of the eROSITA bubbles is a forward shock,\
+      originally driven by oblique bipolar jets emanating from the GC 12.39 Myr ago for a duration of 1.2 Myr\
+      and significantly expanded within the stratified atmosphere afterwards.\
+      The overall extent of the simulated X-ray bubbles is comparable to that of the eROSITA bubbles, though not as limb-brightened.\
+      Future models including shock-accelerated CRs may help to resolve this issue by increasing the compressibility of the fluid and enhancing the thermal Bremsstrahlung emissivity at the edge of the X-ray bubbles.
+      %The simulated eROSITA bubbles are not as limb-brightened as the observation.\
+      %A possibility to enhance the X-ray emission is to include shock-accelerated CRs near the shock,\
+      %in which CRs could increase the compressibility of the fluid,\
+      %resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density squared.
+\item Followed by the forward shock is a turbulent, hot plasma ($\sim2$ keV) filled with the injected CRs in pressure balance with the shocked medium, which we interpret as the \textit{Fermi} bubbles.\
       The similarity of the morphology, temperature, and gamma-ray spectrum between\
-      simulated and observed \textit{Fermi} bubbles suggests that\
-      the \textit{Fermi} bubbles are essentially a turbulent and\
-      high temperature plasma in pressure balance with external medium.
-      Associated with the Galactic magnetic field\
+      simulated and observed bubbles suggests that\
+      the edge of the \textit{Fermi} bubbles are likely associated with the contact discontinuity between the turbulent, hot plasma and the post-shock medium.
+The surface of the simulated bubbles is not as smooth as the observed ones; inclusion of magnetic fields in the future may help suppress the instabilities at the bubble surface due to the mangetic draping effect.
+\item Assuming a leptonic model with a spatially uniform, power-law CRe spectrum ranging from 0.5 MeV to 562.1 GeV, we showed that the observed gamma-ray and microwave spectra can simultaneously reproduced.
+The best-fit\
+      CRe power-law index is found to be 2.4.
+\item Associated with the Galactic magnetic field\
       will lead to the stochastic acceleration of CRe, possibly in balance with the IC and synchrotron cooling.\
       We will investigate the competition between stochastic acceleration and radiative cooling in a future work.
-\item According to the microwave and leptonic gamma-ray spectra, the best-fitting\
-      CRe power-law index is found to be 2.4.
-\item The same leptotonic CRe can simultaneously\
-      account for the \textit{Fermi} bubbles and haze emission suggested that\
-      they are physically related around the GC,\
-      and that the magnetic fields within the bubbles are close to the exponentially distributed\
-      Galactic magnetic field.
+{\color{red} KY: This item is to be modified according to the newly added text in the Discussion section.}
 \end{itemize}

### 2022-03-24 paper.tex
update

@@
 %has thus released a caveat:\
-%the jets shall be vertical to the disc normal.
+%the jets shall be vertical to the disk normal.
 \end{abstract}
@@
 of $\sim$1--100 GeV and has an almost spatially uniform hard\
-spectrum, sharp edges and an approximately flat brightness distribution (see \cite{Yang2018} for a review).
+spectrum, sharp edges and an approximately flat brightness distribution (see \citealt{Yang2018} for a review).
 Recently, the newly launched eROSITA \citep{Predehl2021} conducted an all-sky X-ray survey with high-spatial resolution and revealed two gigantic bubbles (eROSITA bubbles hereafter) extending to $\sim 80$ degrees in Galactic latitudes, corresponding to an intrinsic size of 14 kpc across \citep{Predehl2020}.\
@@
   we define the atmosphere gas density by the peak density of\
-  the isothermal disc on the mid-plane $z=0$ (i.e. $\rho^{\text{peak}}_{\text{isoDisk}}$),\
+  the isothermal disk on the mid-plane $z=0$ (i.e. $\rho^{\text{peak}}_{\text{isoDisk}}$),\
   as opposed to the \textit{clumpy} density around the jet source.
@@
              shows that the initial density distribution of the dense disk has an insignificant effect\
-             on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
+             on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disk\
              in an uniform atmosphere (Fig. \ref{fig__jetI5+ismSeed3-45deg-c}) is nearly spherical,\
@@
            panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
-           to the disc normal in 1.2 Myr.
+           to the disk normal in 1.2 Myr.
   }

### 2022-03-25 paper.tex
update

@@
   the contribution of CR pressure gradient to the momentum of the gas can be ignored\
-  (we will see that the pressure ratio is around 0.1--0.2 throughout the simulations).
+  (we will see that the ratio is around 0.1--0.2 throughout the simulations).
 Note that, although our later calculations of the non-thermal spectra are based on the leptonic model, only a small fraction of the simulated CRs is required to produce the observed gamma-ray and microwave emission \citep{Yang2013}.
 {\color{red} KY: Is this also true in the current simulations?
-That is, from the simulated CR energy densities, did you have to apply a normalization constant to match with the observed gamma-ray/microwave spectra?} Therefore, in the simulations we have neglected the cooling of CRs because it should have a negligible impact on the overall dynamics.
+That is, from the simulated CR energy densities, did you have to apply a normalization constant to match with the observed gamma-ray/microwave spectra?
+PH: We have reached a consensus on this matter on Slack!}
+Therefore, in the simulations we have neglected the cooling of CRs because it should have a negligible impact on the overall dynamics.
   %Over and above, we neglect the cooling and heating processes of CRs,\
@@
  the temperature of the smooth region (purple band in Fig. \ref{fig__profile})\ %emitting X-ray\
- is around 0.3-0.5 keV, similar to that observed by \citet{Miller2016} and \citet{Kataoka2018}. {\color{red} KY: What did these observations constrain exactly?}
+ is around 0.3-0.5 keV, similar to 0.3 keV observed by \citet{Miller2016} and \citet{Kataoka2018}. {\color{red} (KY: What did these observations constrain exactly?
+PH: It is 0.3 keV.
+I have added this number in the context.
+See: ``...follows from the Rankine-Hugoniot condition for the temperature increase from about 0.2 keV outside the bubbles to around 0.3 keV inside$^{7,19}$" in \citealt{Predehl2020})}
 
@@
  demonstrate that there is a sharp pressure jump at the edge of the innermost bubbles at $z=3.62$ kpc,\
- indicating that the innermost bubbles are an expanding reverse shock.\ {\color{red} KY: Is it verified that the reverse shock is expanding outward?}
+ indicating that the innermost bubbles are an expanding reverse shock.\ {\color{red} KY: Is it verified that the reverse shock is expanding outward?
+PH: Yes.
+I have checked that with multiple slices in different time.
+The reverse shock is expanding outward.}
  The high-density upstream of the reverse shock requires\
@@
              suggesting that the stratification facilitates the elongation of the outermost bubbles significantly.\
-             Also, Fig. \ref{fig__jetI5+ismSeed3-45deg-c} and \ref{fig__jetI5+ismSeed3-45deg-d}\
+             Fig. \ref{fig__jetI5+ismSeed3-45deg-c} and \ref{fig__jetI5+ismSeed3-45deg-d}\
              reveal that the development of the innermost bubbles\
@@
              the outermost bubbles and the turbulent plasma would be oblique,
-             indicating that the dense disk is crucial for the production of symmetric Galactic bubbles.\ {\color{red} KY: Consider reducing the caption as it is essentially the same as the text.}
+             indicating that the dense disk is crucial for the production of symmetric Galactic bubbles.\ {\color{red} KY: Consider reducing the caption as it is essentially the same as the text.
+PH: Thanks!
+I would say figures and captions must be self-explanatory i.e.
+always summarize the key conclusions of this figure instead of just describing how this figure is plotted.
+This is the reason why the caption is a little long...
+\textasciicircum\textasciicircum"}
       }
@@
 Fig.
-\ref{fig__x-ray-profile-0.8keV-000} displays the simulated X-rray photon count rates as a function of Galactic longitudes (red)\
+\ref{fig__x-ray-profile-0.8keV-000} displays the simulated X-ray photon count rates as a function of Galactic longitudes (red)\
   in the same energy band as in Fig. \ref{fig__xray_0.8keV_angle_000}\
@@
 
-  {\color{red} KY: Please rewrite the following two paragraphs so that (1) the overall agreement between the simulated and observed bubble morphology and profiles are emphasized before discussing about discrepancies, and (2) some of the disagreement for the northern bubble could be due to the North Polar Spur.}
-  First, we observe that\
-  the simulated eROSITA bubbles are not as limb-brightened as the observation.\
-  A possibility to enhance the X-ray emission is to include shock-accelerated CRs near the shock,\
-  in which CRs could increase the compressibility of the fluid,\
-  resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density squared.
-  The broad agreement between simulated and observed X-ray maps hints that\
-  the full vertical extent of the eROSITA bubbles can be properly formed by an oblique jet within a thin disk\
-  of dense ISM.
+  {\color{red} KY: Please rewrite the following two paragraphs so that (1) the overall agreement between the simulated and observed bubble morphology and profiles are emphasized before discussing about discrepancies, and (2) some of the disagreement for the northern bubble could be due to the North Polar Spur.
+PH: done!}
 
-  Second, as shown in Fig. \ref{fig__jetI5+ismSeed3-45deg-a},\
+  First, as shown in Fig. \ref{fig__jetI5+ismSeed3-45deg-a},\
   the half-width of the outermost bubbles is around 7 kpc,\
@@
   that have been driven into the northern and the southern Galactic halo,
-  as previously proposed by \citet{Predehl2020}.
+  as previously proposed by \citet{Predehl2020} and \citet{Yang2022}.
+The broad agreement between simulated and observed X-ray maps hints that the full vertical extent of the eROSITA bubbles can be properly formed by an oblique jet within a thin disk of dense ISM.
+
+  Second, we observe that\
+  the simulated eROSITA bubbles are not as limb-brightened as the observation.\
+  A possibility to enhance the X-ray emission is to include shock-accelerated CRs near the shock,\
+  in which CRs could increase the compressibility of the fluid,\
+  resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density squared.
+Also, the disagreement for the northern bubble is expected as the North Polar Spur is generally thought to be caused by a remnant of a local supernova \citep{Egger1995}, which is not included in our simulations.
 
@@
 Because the evolution of CR spectrum is not modelled in the simulations, we assume that the CRe spectrum is spatially uniform and follows a power-law distribution ranging from\
-$0.5$ MeV to $562.1$ GeV.
+$0.5$ MeV ($\sim m_{\text{e}}c^2$) to $562.1$ GeV. The choice of $562.1$ GeV is motivated by\
+the observed cutoff gamma-ray energy shown in Fig. \ref{fig__gammaRaySynchtronSpectrum}\
+as most of the CRe energy is carried away by the up-scattered photons in the Klein-Nishina limit.
 
@@
  is around 5$\times10^{-15}$--8$\times10^{-15}$ erg cm$^{-3}$,\
- bringing the pressure ratio of CRs to the gas to 0.1--0.2,
+ bringing the CR-to-gas pressure ratio is 0.1--0.2,
  similar to 0.18 at the beginning of the simulation.
@@
      is around 5$\times10^{-15}$--8$\times10^{-15}$ erg/cm$^{3}$,\
-     bringing the pressure ratio of CR to gas is 0.1--0.2,
+     bringing the CR-to-gas pressure ratio is 0.1--0.2,
      similar to 0.18 at the beginning of the simulation.

### 2022-03-25 paper.tex
update

@@
       {\color{red} KY: I removed the second point about the innermost bubbles for now, because I think the following two points should be separated: (1) inclusion of the disk is critical for forming symmetric Galactic bubbles, (2) we found a pair of innermost bubbles which are reverse shocks (and perhaps comment on their properties and/or observable signatures).}
+\item The development of the expanding forward-reverse shock pair is always associated with the dense disk.
+Also, without the thin disk, only forward shocks exist.
+The forward-reverse shock pair heats the turbulent plasma up considerably ($\sim2$ keV) as the plasma is bracketed between their downstream.
+There exists a dense shell that fits closely to the reverse shock because the gas is immediately compressed as it passes outward through the reverse shock while coinciding with the low gas density further downstream.
+
 \item In the oblique jet scenario, the edge of the eROSITA bubbles is a forward shock,\

### 2022-03-26 paper.tex
update

@@
   \begin{equation}
-    D(\bold{k})=\int k^{2} \hat{f}(\bold{k})\hat{f}^{*}(\bold{k})d\Omega \propto k^{-\beta},
+    D(\bold{k})=\int k^{2} \hat{f}(\bold{k})\hat{f}^{*}(\bold{k})d\Omega \propto k^{-\delta},
     \label{Kolmogorov-spectrum}
@@
   where $\hat{f}(\bold{k})$ is the Fourier transform of $f(\bold{x})$.\
-  The spectrum $D(\bold{k})$ in the Fourier space is characterized by a power-law index $\beta=5/3$,\
+  The spectrum $D(\bold{k})$ in the Fourier space is characterized by a power-law index $\delta=5/3$,\
   a Nyquist limit $k_{\text{max}}$, and a lower cutoff wave number $k_{\text{min}}$.
@@
 $\sigma^\ddag$                        & Dispersion of scalar field     & 5.0                                  & \citep{Federrath2010}          \\
-$\beta$                               & Power law index                & -5/3                                 &   N/A                          \\ \midrule
+$\delta$                              & Power law index                & -5/3                                 &   N/A                          \\ \midrule
 \end{tabular}
@@
   the CR-to-gas pressure ratio of 0.18,\
-  and the flow 4-velocity inside the jet source along the jet axis, $\beta\gamma = 0.6$.\
+  and the flow 4-velocity ($\beta\gamma = 0.6$) inside the jet source along the jet axis.\
   The jet power is thus $3.2\times 10^{42}$ erg s$^{-1}$, resulting in an Eddington ratio of 0.008.\
@@
   The jet duration allows the total ejected energy to be $1.2\times10^{56}$ erg, \
-  within the range of estimates obtained by \citet{Predehl2020} between\
+  within the range of enclosed energy estimated by \citet{Predehl2020} between\
   $8\times10^{55}$ erg and $1.3\times10^{56}$ erg.
@@
 %      the symmetry of the Galactic bubbles and for the innermost bubbles formation.
-      {\color{red} KY: I removed the second point about the innermost bubbles for now, because I think the following two points should be separated: (1) inclusion of the disk is critical for forming symmetric Galactic bubbles, (2) we found a pair of innermost bubbles which are reverse shocks (and perhaps comment on their properties and/or observable signatures).}
+      {\color{red} KY: I removed the second point about the innermost bubbles for now, because I think the following two points should be separated: (1) inclusion of the disk is critical for forming symmetric Galactic bubbles, (2) we found a pair of innermost bubbles which are reverse shocks (and perhaps comment on their properties and/or observable signatures).
+PH: done!
+}
 \item The development of the expanding forward-reverse shock pair is always associated with the dense disk.
@@
 The authors thank Mateusz Ruszkowski and Ellen G. Zweibel for insightful comments.\
+We thank Henry Zovaro for discussions about the innermost bubbles\
+during the final stages of this work.\
 We thank Peter Predehl for providing the range of observed X-ray intensity in Fig. \ref{fig__xray_0.8keV_angle_000}.\
@@
 
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+\begin{table*}
+\raggedright
+\caption{Jet parameters.}
+\label{tablb-jet-parameters}
+\begin{tabular}{@{}llllllll@{}}
+\toprule[1pt]\midrule[0.3pt]
+                  & A          & B          & C          & D          & E          & F          & G          \\ \midrule
+$k_{B}T$ (MeV)    & 1.720      & 17.200     & 1.720      & 0.172      & 1.720      & 1.720      & 1.720      \\
+$\rho$ (g/cm$^3$) & $10^{-26}$ & $10^{-26}$ & $10^{-26}$ & $10^{-26}$ & $10^{-25}$ & $10^{-27}$ & $10^{-26}$ \\
+$\beta\gamma$     & 1.2        & 0.6        & 0.6        & 0.6        & 0.6        & 0.6        & 0.3        \\ \midrule
+\end{tabular}
+\end{table*}
+
+\begin{figure*}
+  \includegraphics[width=\textwidth]{figures/fig__jet_parameters.png}
+  \caption
+   {
+    Jets parameters variation around the fiducial run:\
+    $\beta\gamma=1.2$ (left), $\beta\gamma=0.6$ (middle), and $\beta\gamma=0.3$ (right).
+   }
+  \label{fig__jet_parameters}
+\end{figure*}
+
+\begin{figure*}
+  \includegraphics[width=\textwidth]{figures/fig__slice-compare.png}
+  \caption
+   {
+    Simulation results based on the jets parameters in Fig. \ref{fig__jet_parameters}.
+   }
+  \label{fig__slice-compare}
+\end{figure*}
+
 %%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

### 2022-03-26 figures/plot.py

@@ -1,0 +1,73 @@
+import matplotlib.pyplot as plt
+import numpy as np
+from matplotlib.pyplot import figure
+
+BoltzConst = 8.617333262145e-5
+
+
+A = [1.2, 1e-26, 2e10*BoltzConst/1e6]
+B = [0.6, 1e-26, 2e11*BoltzConst/1e6]
+C = [0.6, 1e-26, 2e10*BoltzConst/1e6]
+D = [0.6, 1e-26, 2e09*BoltzConst/1e6]
+E = [0.6, 1e-25, 2e10*BoltzConst/1e6]
+F = [0.6, 1e-27, 2e10*BoltzConst/1e6]
+G = [0.3, 1e-26, 2e10*BoltzConst/1e6]
+
+ms = 10
+area = 200
+colors = 'red'
+
+
+fig, ax = plt.subplots(1,3, figsize=(20,5))
+
+plt.subplots_adjust(wspace = 0.02)
+
+ax[1].scatter( B[2], B[1], s=area, c=colors, marker='o')
+ax[1].scatter( C[2], C[1], s=area, c=colors, marker='o')
+ax[1].scatter( D[2], D[1], s=area, c=colors, marker='o')
+ax[1].scatter( E[2], E[1], s=area, c=colors, marker='o')
+ax[1].scatter( F[2], F[1], s=area, c=colors, marker='o')
+
+ax[0].scatter( A[2], A[1], s=area, c=colors, marker='o')
+ax[2].scatter( G[2], G[1], s=area, c=colors, marker='o')
+
+txt = ['A', 'B', 'C (fiducial)', 'D', 'E', 'F', 'G']
+
+font = {"fontsize": 20}
+ax[1].annotate(txt[1], (B[2]*1.1, B[1]*1.1), **font)
+ax[1].annotate(txt[2], (C[2]*1.1, C[1]*1.1), **font)
+ax[1].annotate(txt[3], (D[2]*1.1, D[1]*1.1), **font)
+ax[1].annotate(txt[4], (E[2]*1.1, E[1]*1.1), **font)
+ax[1].annotate(txt[5], (F[2]*1.1, F[1]*1.1), **font)
+
+ax[0].annotate(txt[0], (A[2]*1.1, A[1]*1.1), **font)
+ax[2].annotate(txt[6], (G[2]*1.1, G[1]*1.1), **font)
+
+
[…]

### 2022-03-27 paper.tex
update

@@
 \section{jets parameter variations}
+
 \textcolor{red}{KY: Please also add a section (either in the Discussion
@@
 
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
+In this section, we present the simulation results using exactly same parameters\
+except for the density ($\rho$), temperature ($k_{B}T$),\
+and four-velocity ($\beta\gamma$) within the jet source.\
+These variable parameters, including the fiducial run (C), are\
+tabulated in Table \ref{tablb-jet-parameters} and visualized in Fig. \ref{fig__jet_parameters}.
+
 \begin{table*}
 \raggedright
-\caption{Jet parameters.}
+\caption{The list of runs showing different injected jet parameters.\
+         The fiducial run (C) has been pointed out by an asterisk in the list. }
 \label{tablb-jet-parameters}
@@
 \toprule[1pt]\midrule[0.3pt]
-                  & A          & B          & C          & D          & E          & F          & G          \\ \midrule
-$k_{B}T$ (MeV)    & 1.720      & 17.200     & 1.720      & 0.172      & 1.720      & 1.720      & 1.720      \\
+                  & A          & B          & C*         & D           & E          & F          & G          \\ \midrule
+$k_{B}T$ (MeV)    & 1.720      & 0.172      & 1.720      & 17.200      & 1.720      & 1.720      & 1.720      \\
 $\rho$ (g/cm$^3$) & $10^{-26}$ & $10^{-26}$ & $10^{-26}$ & $10^{-26}$  & $10^{-25}$ & $10^{-27}$ & $10^{-26}$ \\

### 2022-03-27 figures/plot.py

@@ -6,9 +6,9 @@ BoltzConst = 8.617333262145e-5
 
 
 A = [1.2, 1e-26, 2e10*BoltzConst/1e6]
-B = [0.6, 1e-26, 2e11*BoltzConst/1e6]
+B = [0.6, 1e-26, 2e09*BoltzConst/1e6]
 C = [0.6, 1e-26, 2e10*BoltzConst/1e6]
-D = [0.6, 1e-26, 2e09*BoltzConst/1e6]
+D = [0.6, 1e-26, 2e11*BoltzConst/1e6]
 E = [0.6, 1e-25, 2e10*BoltzConst/1e6]
 F = [0.6, 1e-27, 2e10*BoltzConst/1e6]
 G = [0.3, 1e-26, 2e10*BoltzConst/1e6]
@@ -56,9 +56,9 @@ ax[0].set_yscale('log')
 ax[1].set_yscale('log')
 ax[2].set_yscale('log')
 
-ax[0].set_xlim(D[2]*0.8, B[2]*1.5)
-ax[1].set_xlim(D[2]*0.8, B[2]*1.5)
-ax[2].set_xlim(D[2]*0.8, B[2]*1.5)
+ax[0].set_xlim(B[2]*0.8, D[2]*1.5)
+ax[1].set_xlim(B[2]*0.8, D[2]*1.5)
+ax[2].set_xlim(B[2]*0.8, D[2]*1.5)
 ax[0].set_ylim(F[1]*0.8, E[1]*1.7)
 ax[1].set_ylim(F[1]*0.8, E[1]*1.7)
 ax[2].set_ylim(F[1]*0.8, E[1]*1.7)

### 2022-03-27 paper.tex
update

--- 2022-03-26 paper.tex
@@
 
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
+In this section, we present the simulation results (Fig. \ref{fig__slice-compare})\
+using exactly same parameters\
+except for the density ($\rho$), temperature ($k_{B}T$),\
+and four-velocity ($\beta\gamma$) within the jet source.\
+The parameters of jet models, including the fiducial run (C),\
+covered in this appendix are given in Table \ref{tablb-jet-parameters}.
+
+Three points are worth highlighting:
+\begin{itemize}
+   \item Increase density only (F$\rightarrow$C$\rightarrow$E):\\
+   The runs F, C, and E demonstrate that an increase in density,
+   causes a rise in the intensity of the shocks driven into the atmosphere,\
+   and makes the post-shocked region hotter,\
+   as well as leads the bubbles to be more asymmetric about the disk.
+   Since the jets with higher denisty are more likely to\
+   break through the thin disk in a short time\
+   and more difficult to be elongated by stratified atmosphere afterward.
+
+   \item Increase velocity only (G$\rightarrow$C$\rightarrow$A):\\
+   Increasing magnitude of velocity also gives the hotter and asymmetric bubbles as increasing density.
+   The temperature of the bubbles caused by increasing velocity\
+   is closely similar to that of increasing density when kinetic energy is fixed.\
+
+   \item Increase thermal energy only (B$\rightarrow$C$\rightarrow$D):\\
+   These demonstrates that increasing thermal energy cannot affect\
+   the morphology of bubbles significantly
+\end{itemize}
+
+   This shows that the morphology/dynamic of bubbles is mainly determined by\
+   a kinetic energy of a jet flow. Jets with higher kinetic energy are more likely to\
+   break through the thin disk in a short time\
+   and more difficult to be elongated by stratified atmosphere afterward.
+
 \begin{table*}
 \raggedright
-\caption{Jet parameters.}
+\caption{The list of runs showing different injected jet parameters.\
+         The fiducial run (C) has been pointed out by an asterisk in the list. }
 \label{tablb-jet-parameters}
@@
 \toprule[1pt]\midrule[0.3pt]
-                  & A          & B          & C          & D          & E          & F          & G          \\ \midrule
-$k_{B}T$ (MeV)    & 1.720      & 17.200     & 1.720      & 0.172      & 1.720      & 1.720      & 1.720      \\
+                  & A          & B          & C*         & D           & E          & F          & G          \\ \midrule
+$k_{B}T$ (MeV)    & 1.720      & 0.172      & 1.720      & 17.200      & 1.720      & 1.720      & 1.720      \\
 $\rho$ (g/cm$^3$) & $10^{-26}$ & $10^{-26}$ & $10^{-26}$ & $10^{-26}$  & $10^{-25}$ & $10^{-27}$ & $10^{-26}$ \\
-$\beta\gamma$     & 1.2        & 0.6        & 0.6        & 0.6        & 0.6        & 0.6        & 0.3        \\ \midrule
+$\beta\gamma$     & 1.40       & 0.60       & 0.60       & 0.60        & 0.60       & 0.60       & 0.28       \\ \midrule
 \end{tabular}
@@
 
-\begin{figure*}
-  \includegraphics[width=\textwidth]{figures/fig__jet_parameters.png}
-  \caption
-   {
-    Jets parameters variation around the fiducial run:\
-    $\beta\gamma=1.2$ (left), $\beta\gamma=0.6$ (middle), and $\beta\gamma=0.3$ (right).
-   }
-  \label{fig__jet_parameters}
-\end{figure*}
+%  A    G
+% 1.4 0.28
+
+%\begin{figure*}
+%  \includegraphics[width=\textwidth]{figures/fig__jet_parameters.png}
+%  \caption
+%   {
+%    Jets parameters variation around the fiducial run:\
+%    $\beta\gamma=1.2$ (left), $\beta\gamma=0.6$ (middle), and $\beta\gamma=0.3$ (right).
+%   }
+%  \label{fig__jet_parameters}
+%\end{figure*}
 

### 2022-03-27 paper.tex
update

--- 2022-03-26 paper.tex
@@
 \section{jets parameter variations}
-\textcolor{red}{KY: Please also add a section (either in the Discussion
-or Appendix) to discuss about the parameter variations.
-I think the figures you showed me are very important
-and informative.}
-
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
+
+It is instructive to compare the simulation results (Fig. \ref{fig__slice-compare})\
+using exactly same parameters\
+except for the density ($\rho$), temperature ($k_{B}T$),\
+and four-velocity ($\beta\gamma$) within the jet source.\
+The parameters of jet source, including the fiducial run (C),\
+covered in this appendix are given in Table \ref{tablb-jet-parameters}.
+
+We observe that higher density (F$\rightarrow$C$\rightarrow$E) of the source\
+can enhance the intensity of the shocks driven into the atmosphere,\
+and makes the post-shock region hotter,\
+as well as leads the bubbles to be more asymmetric about the GC.
+This is because the denser jets are more likely to\
+break through the thin disk in a short time\
+and more difficult to be elongated by stratified atmosphere afterward.
+
+On the other hand, when we increase the magnitude of velocity\
+(G$\rightarrow$C$\rightarrow$A) such that\
+the corresponding kinetic energies are the same as when increasing\
+density, the bubble morphology of two will be similar.\
+This demonstrates that the morphology/dynamic of bubbles is mainly determined by\
+kinetic energy of a jet flow.
+
+Finally, when we increase the thermal energy (B$\rightarrow$C$\rightarrow$D)\
+of the jet source such that the thermal energy increase by\
+the same amount as the kinetic energy,\
+we find that the morphology of bubbles is basically unchanged,\
+but the evolution of bubbles can be slightly accelerated.
+
 \begin{table*}
 \raggedright
-\caption{Jet parameters.}
+\caption{The list of runs showing different injected jet parameters.\
+         The fiducial run (C) has been pointed out by an asterisk in the list. }
 \label{tablb-jet-parameters}

### 2022-03-28 paper.tex
update

@@
                &\frac{3}{4}\sigma_{T}c\mathbb{C}\epsilon_{1}\int^{\epsilon_{\text{max}}}_{\epsilon_{\text{min}}}
-               \frac{n(\epsilon)}{\epsilon}d\epsilon\int^{\gamma_{\text{max}}}_{\gamma_{\text{min}}\left(\epsilon\right)}
-               \gamma^{-(p+2)}f(q, \Gamma)d\gamma,\\
+               \frac{n(\epsilon)}{\epsilon}d\epsilon\int^{\gamma_{\text{e,max}}}_{\gamma_{\text{e,min}}\left(\epsilon\right)}
+               \gamma_{\text{e}}^{-(p+2)}f(q, \Gamma)d\gamma_{\text{e}},\\
   \nonumber\\
@@
                &2q\ln q+(1+2q)(1-q)+0.5(1-q)\frac{\left(\Gamma q\right)^2}{1+\Gamma q},\\
-  &q=\frac{\epsilon_{1}/\gamma\
-               m_{\text{e}}c^{2}}{\Gamma\left(1-\epsilon_{1}/\gamma m_{\text{e}}c^{2}\right)},\\
-  &\Gamma=\frac{4\epsilon \gamma}{m_{\text{e}}c^2},\\
-  &\gamma_{\text{min}}(\epsilon)=\
+  &q=\frac{\epsilon_{1}/\gamma_{\text{e}}\
+               m_{\text{e}}c^{2}}{\Gamma\left(1-\epsilon_{1}/\gamma_{\text{e}} m_{\text{e}}c^{2}\right)},\\
+  &\Gamma=\frac{4\epsilon \gamma_{\text{e}}}{m_{\text{e}}c^2},\\
+  &\gamma_{\text{e,min}}(\epsilon)=\
    0.5\left(\frac{\epsilon_{1}}{m_{\text{e}}c^2}+\sqrt{\left(\frac{\epsilon_{1}}{m_{\text{e}}c^2}\right)^2+\
@@
 $n(\epsilon)$ is the energy distribution of the photon number density in the ISRF given by \citet{Porter2017},\
-$\gamma$ is the Lorentz factor of CRe, and\
+$\gamma_{\text{e}}$ is the Lorentz factor of CRe, and\
 $\mathbb{C}$ and $p$ are the normalization constant and spectral index of the CRe power-law spectrum.
-$\gamma_{\text{min}}(\epsilon)$ is the minimum Lorentz factor of CRe\
+$\gamma_{\text{e,min}}(\epsilon)$ is the minimum Lorentz factor of CRe\
 that allows the incident photons to be scattered from energy $\epsilon$ to $\epsilon_{1}$, and\
-$\gamma_{\text{max}}$ is the maximum CRe Lorentz factor in the spectrum. To obtain the simulated IC emissivities, we perform the double integration in Eq. \ref{gammaray-emissivity} on each cell\
+$\gamma_{\text{e,max}}$ is the maximum CRe Lorentz factor in the spectrum. To obtain the simulated IC emissivities, we perform the double integration in Eq. \ref{gammaray-emissivity} on each cell\
 over the range of the CRe Lorentz factor and\
@@
 Our modeled gamma-ray and microwave spectra assumed that
-the underlying CRe spectrum is spatially uniform.
-Therefore our results imply that, whatever the true re-acceleration and cooling mechanisms are,
+the underlying CRe spectrum is spatially uniform with hard spectral index 2.4;
+however, the high energy CRe severely suffer from synchrotron and IC losses,
+during their passage through the magnetic and radiation fields, respectively.
+
+The typical synchrotron and IC cooling time scale of high energy ($\sim100$ GeV) CRe
+in Milky Way is $\sim$ 1 Myr \citep{Yang2017}, ten times shorter than
+12.39 Myr required for the simulated bubbles to reach the desired morphology.
+
+Therefore, the CRe generating the gamma-ray emission would need to be re-accelerated
+by in-situ acceleration mechanisms such as shocks or turbulence.
+Since the forward shock is rather far away from the gamma-ray bubbles,
+re-acceleration is more likely associated with turbulence \citep{Mertsch2011,Mertsch2019},
+possibly in balance with the IC and synchrotron cooling. We will investigate the competition between stochastic acceleration and radiative cooling
+in a future work.
+
+Overall, our results imply that, whatever the true re-acceleration and cooling mechanisms are,
 the CRe spectrum at the present time has to be spatially uniform with
 a spectral index of 2.4 in order to fit the observed spectra.
+
+%\begin{equation}
+%   \frac{dE}{dt}
+%     = -\frac{4}{3}\sigma_{T}c\beta_{\text{e}}^2\gamma_{\text{e}}^2
+%     \left(U_{\text{photon}}+U_{B}\right),
+%\end{equation}
+%where $\beta_{\text{e}}=v_{\text{e}}/c$, $U_{\text{photon}}$ and $U_{B}$ are
+%energy density of ISRF and magnetic field, respectively.
 
@@
 \item Associated with the Galactic magnetic field\
-      will lead to the stochastic acceleration of CRe, possibly in balance with the IC and synchrotron cooling.\
-      We will investigate the competition between stochastic acceleration and radiative cooling in a future work.
+      will lead to the stochastic acceleration of CRe,
+      possibly in balance with the IC and synchrotron cooling.\
+      We will investigate the competition between stochastic acceleration and radiative cooling
+      in a future work.
       {\color{red} KY: This item is to be modified according to the newly added text in the Discussion section.}
@@
    {
-    Simulation results based on the jets parameters in Fig. \ref{fig__jet_parameters}.
+    Simulation results based on the jets parameters in Table. \ref{tablb-jet-parameters}.
    }

### 2022-03-30 paper.tex
update

@@
 however, the high energy CRe severely suffer from synchrotron and IC losses,
-during their passage through the magnetic and radiation fields, respectively.
+during their passage through the magnetic and radiation fields, respectively, within the Galaxy.
 

### 2022-03-30 paper.tex
update

@@
       CRe power-law index is found to be 2.4.
-\item Associated with the Galactic magnetic field\
-      will lead to the stochastic acceleration of CRe,
-      possibly in balance with the IC and synchrotron cooling.\
+\item The elapsed time of 12.39 Myr required for the simulated bubbles
+      to reach the desired morphology
+      is ten times longer than the typical synchrotron and IC cooling time scale of
+      high energy ($\sim100$ GeV) CRe. Thus, re-acceleration of CRe must be considered
+      in this model. As opposed to shock acceleration,
+      the acceleration of CRe that can compete with IC and synchrotron cooling
+      may be dominated by the stochastic acceleration associated with the Galactic magnetic field,
+      since the forward shock is rather far away from the gamma-ray bubbles.
       We will investigate the competition between stochastic acceleration and radiative cooling

### 2022-03-30 paper.tex
update

@@
   resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density squared.
-Also, the disagreement for the northern bubble is expected as the North Polar Spur is generally thought to be caused by a remnant of a local supernova \citep{Egger1995}, which is not included in our simulations.
+Also, the disagreement of the northeastern bubble is expected as the North Polar Spur, which is a giant ridge of bright X-ray emission that rises roughly perpendicularly out of the plane of the galaxy, might be a superposition of the GC structure and a remnant of the local supernova \citep{berkhuijsen1971galactic,Das2020,Panopoulou2021}, which is not included in our simulations, whereas analyses based on X-ray data tend to suggest a GC origin \citep{kataoka2018x,sofue2000bipolar,larocca2020analysis}.
 

### 2022-03-31 KY-3.31.tex
update

--- 2022-03-30 paper.tex
@@
   (we will see that the ratio is around 0.1--0.2 throughout the simulations).
-Note that, although our later calculations of the non-thermal spectra are based on the leptonic model, only a small fraction of the simulated CRs is required to produce the observed gamma-ray and microwave emission \citep{Yang2013}.
-{\color{red} KY: Is this also true in the current simulations?
+%Note that, although our later calculations of the non-thermal spectra are based on the leptonic model, only a small fraction of the simulated CRs is required to produce the observed gamma-ray and microwave emission \citep{Yang2013}.
+%{\color{red} KY: Is this also true in the current simulations?
 That is, from the simulated CR energy densities, did you have to apply a normalization constant to match with the observed gamma-ray/microwave spectra?
@@
  the temperature of the smooth region (purple band in Fig. \ref{fig__profile})\ %emitting X-ray\
- is around 0.3-0.5 keV, similar to 0.3 keV observed by \citet{Miller2016} and \citet{Kataoka2018}. {\color{red} (KY: What did these observations constrain exactly?
+ is around 0.3-0.5 keV, similar to 0.3 keV observed by \citet{Miller2016} and \citet{Kataoka2018}.
+%{\color{red} (KY: What did these observations constrain exactly?
 PH: It is 0.3 keV.
@@
  demonstrate that there is a sharp pressure jump at the edge of the innermost bubbles at $z=3.62$ kpc,\
- indicating that the innermost bubbles are an expanding reverse shock.\ {\color{red} KY: Is it verified that the reverse shock is expanding outward?
+ indicating that the innermost bubbles are an expanding reverse shock.\ %{\color{red} KY: Is it verified that the reverse shock is expanding outward?
 PH: Yes.
@@
              the outermost bubbles and the turbulent plasma would be oblique,
-             indicating that the dense disk is crucial for the production of symmetric Galactic bubbles.\ {\color{red} KY: Consider reducing the caption as it is essentially the same as the text.
+             indicating that the dense disk is crucial for the production of symmetric Galactic bubbles.\ %{\color{red} KY: Consider reducing the caption as it is essentially the same as the text.
 PH: Thanks!
@@
 
-  {\color{red} KY: Please rewrite the following two paragraphs so that (1) the overall agreement between the simulated and observed bubble morphology and profiles are emphasized before discussing about discrepancies, and (2) some of the disagreement for the northern bubble could be due to the North Polar Spur.
+%  {\color{red} KY: Please rewrite the following two paragraphs so that (1) the overall agreement between the simulated and observed bubble morphology and profiles are emphasized before discussing about discrepancies, and (2) some of the disagreement for the northern bubble could be due to the North Polar Spur.
 PH: done!}
@@
 possibly in balance with the IC and synchrotron cooling. We will investigate the competition between stochastic acceleration and radiative cooling
-in a future work.
-
-Overall, our results imply that, whatever the true re-acceleration and cooling mechanisms are,
+in future work.
+
+Overall, our results imply that in the oblique-jet scenario, whatever the true re-acceleration and cooling mechanisms are,
 the CRe spectrum at the present time has to be spatially uniform with
@@
 %      the symmetry of the Galactic bubbles and for the innermost bubbles formation.
-      {\color{red} KY: I removed the second point about the innermost bubbles for now, because I think the following two points should be separated: (1) inclusion of the disk is critical for forming symmetric Galactic bubbles, (2) we found a pair of innermost bubbles which are reverse shocks (and perhaps comment on their properties and/or observable signatures).
+%      {\color{red} KY: I removed the second point about the innermost bubbles for now, because I think the following two points should be separated: (1) inclusion of the disk is critical for forming symmetric Galactic bubbles, (2) we found a pair of innermost bubbles which are reverse shocks (and perhaps comment on their properties and/or observable signatures).
 PH: done!
@@
       is ten times longer than the typical synchrotron and IC cooling time scale of
-      high energy ($\sim100$ GeV) CRe. Thus, re-acceleration of CRe must be considered
-      in this model. As opposed to shock acceleration,
-      the acceleration of CRe that can compete with IC and synchrotron cooling
-      may be dominated by the stochastic acceleration associated with the Galactic magnetic field,
-      since the forward shock is rather far away from the gamma-ray bubbles.
+      high energy ($\sim100$ GeV) CRe. Thus, re-acceleration of CRe by shocks or turbulence must be considered
+      in this model. Since the forward shock is rather far away from the gamma-ray bubbles, stochastic acceleration of CRs by turbulence appears to be more plausible.\
       We will investigate the competition between stochastic acceleration and radiative cooling
       in a future work.
-      {\color{red} KY: This item is to be modified according to the newly added text in the Discussion section.}
+      %{\color{red} KY: This item is to be modified according to the newly added text in the Discussion section. PH: done!}
 \end{itemize}
@@
 break through the thin disk in a short time\
-and more difficult to be elongated by stratified atmosphere afterward.
+and {\color{red} KY: or doesn't have enough time to interact with disk to change its orientations?} more difficult to be elongated by stratified atmosphere afterward.
 
@@
 the corresponding kinetic energies are the same as when increasing\
-density, the bubble morphology of two will be similar.\
+density, the bubble morphology of two will be similar.{\color{red} KY: The meaning of this sentence is a bit unclear.
+You mean changing the source density and changing the velocity will give similar results, right?}\
 This demonstrates that the morphology/dynamic of bubbles is mainly determined by\
@@
 we find that the morphology of bubbles is basically unchanged,\
-but the evolution of bubbles can be slightly accelerated.
+but the evolution of bubbles can be slightly accelerated.{\color{red} KY: Is it true that Run B and C look essentially identical even if their jet thermal density is quite different?}
 

### 2022-04-02 paper.tex
update

@@
 
-We observe that higher density (F$\rightarrow$C$\rightarrow$E) of the source\
+We observe that either higher density (F$\rightarrow$C$\rightarrow$E)\
+or higher velocity (G$\rightarrow$C$\rightarrow$A) of the source\
 can enhance the intensity of the shocks driven into the atmosphere,\
@@
 as well as leads the bubbles to be more asymmetric about the GC.
-This is because the denser jets are more likely to\
-break through the thin disk in a short time\
-and more difficult to be elongated by stratified atmosphere afterward.
-
-On the other hand, when we increase the magnitude of velocity\
-(G$\rightarrow$C$\rightarrow$A) such that\
-the corresponding kinetic energies are the same as when increasing\
-density, the bubble morphology of two will be similar.\
-This demonstrates that the morphology/dynamic of bubbles is mainly determined by\
-kinetic energy of a jet flow.
-
-Finally, when we increase the thermal energy (B$\rightarrow$C$\rightarrow$D)\
-of the jet source such that the thermal energy increase by\
-the same amount as the kinetic energy,\
-we find that the morphology of bubbles is basically unchanged,\
-but the evolution of bubbles can be slightly accelerated.
+This is because the denser/faster jets are more likely to\
+break through the thin disk in a short time, resulting in\
+the jets have inadequate time to interact with the disk to change its orientations,
+and therefore more difficult to be vertically elongated by stratified atmosphere.
+{\color{red} KY: or doesn't have enough time to interact with disk to change its orientations?
+PH: Thanks! I have added this point of view to the text above.}
+
+{\color{red} KY: The meaning of this sentence is a bit unclear.
+You mean changing the source density and changing the velocity will give similar results, right?
+PH: I have deleted the unclear sentence since I feel it is pointless.}
+
+Finally, when increasing the temperature (B$\rightarrow$C$\rightarrow$D)\
+of the jet source, we find that the morphology and multi-wavelength spectrum of bubbles is basically unchanged,\
+but the evolution can be slightly accelerated.
+Thus, the similarity between them shows that we cannot tightly constrain the source temperature
+only by comparing their morphologies/spectra.
+
+{\color{red} KY: Is it true that Run B and C look essentially identical even if their jet thermal density is quite different?
+PH: Yes, I am sure.
+The dynamics of bubbles seem to be sensitive to kinetic energy rather than thermal energy.}
 
@@
 $\rho$ (g/cm$^3$) & $10^{-26}$ & $10^{-26}$ & $10^{-26}$ & $10^{-26}$  & $10^{-25}$ & $10^{-27}$ & $10^{-26}$ \\
-$\beta\gamma$     & 1.40       & 0.60       & 0.60       & 0.60        & 0.60       & 0.60       & 0.28       \\ \midrule
+$\beta\gamma$     & 1.20       & 0.60       & 0.60       & 0.60        & 0.60       & 0.60       & 0.3       \\ \midrule
 \end{tabular}

### 2022-04-11 paper.tex
update

@@
 and therefore more difficult to be vertically elongated by stratified atmosphere.
-{\color{red} KY: or doesn't have enough time to interact with disk to change its orientations?
-PH: Thanks! I have added this point of view to the text above.}
-
-{\color{red} KY: The meaning of this sentence is a bit unclear.
-You mean changing the source density and changing the velocity will give similar results, right?
-PH: I have deleted the unclear sentence since I feel it is pointless.}
-
-Finally, when increasing the temperature (B$\rightarrow$C$\rightarrow$D)\
-of the jet source, we find that the morphology and multi-wavelength spectrum of bubbles is basically unchanged,\
-but the evolution can be slightly accelerated.
-Thus, the similarity between them shows that we cannot tightly constrain the source temperature
-only by comparing their morphologies/spectra.
-
-{\color{red} KY: Is it true that Run B and C look essentially identical even if their jet thermal density is quite different?
-PH: Yes, I am sure.
-The dynamics of bubbles seem to be sensitive to kinetic energy rather than thermal energy.}
+{\color{red} KY: or doesn't have enough time to interact with disk to change its orientations?}
+{\color{blue} PH: Thanks! I have added this point to the text above.}
+
+{\color{red} KY: The meaning of this sentence is a bit unclear. You mean changing the source density and changing the velocity will give similar results, right?}
+{\color{blue} PH: I have deleted the unclear sentence since I feel it is pointless.}
+
+Finally, we find that increasing the source temperature (B$\rightarrow$C$\rightarrow$D)\
+not only improves the symmetry of the bubbles but also increases the temperature
+inside the bubbles at the present time. This result implies that a high-temperature source
+helps the jets ablate the clumpy dense gas away and pours into the atmosphere
+through the intercloud channels of the clumpy disk. In contrast,
+if source temperature is not high enough,
+the jets cannot effectively ablate the high-density cloud within 12.39 Myr,
+resulting in the formation of asymmetrical bubbles (the run B).
+
+{\color{red} KY: Is it true that Run B and C look essentially identical even if their jet thermal density is quite different?}
+{\color{blue} PH: Yes. To make the difference more obvious,
+I have expanded the temperature range by a factor of 5. i.e. $T_{D}/T_{C}=T_{C}/T_{B}\sim50$.}
 
@@
                   & A          & B          & C*         & D           & E          & F          & G          \\ \midrule
-$k_{B}T$ (MeV)    & 1.720      & 0.172      & 1.720      & 17.200      & 1.720      & 1.720      & 1.720      \\
+$k_{B}T$ (MeV)    & 1.720      & 0.034      & 1.720      & 86.100      & 1.720      & 1.720      & 1.720      \\
 $\rho$ (g/cm$^3$) & $10^{-26}$ & $10^{-26}$ & $10^{-26}$ & $10^{-26}$  & $10^{-25}$ & $10^{-27}$ & $10^{-26}$ \\

### 2022-04-13 KY-4.14.tex
update

--- 2022-04-11 paper.tex
@@
 This is because the denser/faster jets are more likely to\
-break through the thin disk in a short time, resulting in\
-the jets have inadequate time to interact with the disk to change its orientations,
-and therefore more difficult to be vertically elongated by stratified atmosphere.
-{\color{red} KY: or doesn't have enough time to interact with disk to change its orientations?}
-{\color{blue} PH: Thanks! I have added this point to the text above.}
-
-{\color{red} KY: The meaning of this sentence is a bit unclear. You mean changing the source density and changing the velocity will give similar results, right?}
-{\color{blue} PH: I have deleted the unclear sentence since I feel it is pointless.}
+break through the thin disk in a short time, so that\
+the jets have insufficient time to interact with the disk to change their orientations and then be vertically elongated by the stratified atmosphere.
 
@@
 if source temperature is not high enough,
-the jets cannot effectively ablate the high-density cloud within 12.39 Myr,
-resulting in the formation of asymmetrical bubbles (the run B).
-
-{\color{red} KY: Is it true that Run B and C look essentially identical even if their jet thermal density is quite different?}
-{\color{blue} PH: Yes. To make the difference more obvious,
-I have expanded the temperature range by a factor of 5. i.e. $T_{D}/T_{C}=T_{C}/T_{B}\sim50$.}
+the jets cannot effectively ablate the high-density clouds within 12.39 Myr,
+resulting in the formation of asymmetric bubbles (case B).
 

### 2022-04-14 paper.tex
update

@@
 The approach is similar to previous works of \cite{Guo2012} and \cite{Yang2012}, but generalized to CRs that couple with thermal gas moving with relativistic speeds.
-The detailed implementations in \textsc{gamer-sr} and tests of the algorithm can be found in a forthcoming paper \citep[][in prep.]{Chen2022}.
+The detailed implementations in \textsc{gamer-sr} and tests of the algorithm can be found in a forthcoming paper (Chen et al.
+in prep).
 In this approach, the CRs are treated as a single species without distinctions between CR electrons and protons,\
@@
 
-%\item The randomness of the clumpy disk has an insignificant impact on the overall dynamic of the Galactic bubbles.\
-%      The development of the reverse shocks (the innermost bubbles) is always associated with the dense disk,\
-%      without the disc, the outermost bubbles and the turbulent plasma will be oblique,\
-%      indicating the dense disc is crucial for\
-%      the symmetry of the Galactic bubbles and for the innermost bubbles formation.
+%\item The clumpiness of the ISM disk has an insignificant impact on the\
+%      overall dynamic of the Galactic bubbles.\
+%      The development of the reverse shocks (the innermost bubbles) is always
+%      associated with the dense disk,\
+%      without the disc, only asymmetric forward shocks exist.
 %      {\color{red} KY: I removed the second point about the innermost bubbles for now, because I think the following two points should be separated: (1) inclusion of the disk is critical for forming symmetric Galactic bubbles, (2) we found a pair of innermost bubbles which are reverse shocks (and perhaps comment on their properties and/or observable signatures).
@@
 }
-\item The development of the expanding forward-reverse shock pair is always associated with the dense disk.
-Also, without the thin disk, only forward shocks exist.
-The forward-reverse shock pair heats the turbulent plasma up considerably ($\sim2$ keV) as the plasma is bracketed between their downstream.
+{\color{blue}
+\item The development of the expanding forward-reverse shock pair is always associated with\
+the dense disk, although the clumpiness of the disk has an insignificant impact on the\
+overall dynamic of the Galactic bubbles.
+Furthermore, in the absence of the disk, only forward shocks are present,
+indicating the inclusion of the disk is critical for forming the innermost bubbles.
+
+\item The forward-reverse shock pair heats the turbulent plasma up considerably ($\sim2$ keV) as the plasma is bracketed between their downstream.
 There exists a dense shell that fits closely to the reverse shock because the gas is immediately compressed as it passes outward through the reverse shock while coinciding with the low gas density further downstream.
-
+}
 \item In the oblique jet scenario, the edge of the eROSITA bubbles is a forward shock,\

### 2022-04-14 paper.tex
update

@@
  extending out from the GC on either side of the thin disk.\
+ {\color{blue}
  The innermost bubbles are cold (1-10 eV), dense ($10^{-4}$--$10^{-2}$ cm$^{-3}$),\
- and underpressured with respect to the turbulent plasma.\
+ and underpressured with respect to the turbulent plasma\
+ and probably not related to the X-ray chimneys \citep{Ponti2019}\
+ and radio bubbles \citep{Heywood2019}\
+ due to their enormous difference in length (the total major-axis length of the X-ray chimneys
+ and radio bubbles is 320 pc and 430 pc, respectively; however, the innermost bubbles
+ is up to 4 kpc in length).
+ }
  The close-up view (right column in Fig. \ref{fig__profile}) of the vertical profiles\

### 2022-04-14 paper.tex
update

@@
        thus there exists a dense shell\
-       (the turbulent region outside the black dashed line on density slice).
+       (the turbulent region outside the black dashed line in the left panel).
      }

### 2022-04-14 paper.tex
update

@@
  extending out from the GC on either side of the thin disk.\
- {\color{blue}
  The innermost bubbles are cold (1-10 eV), dense ($10^{-4}$--$10^{-2}$ cm$^{-3}$),\
@@
  is up to 4 kpc in length).
- }
  The close-up view (right column in Fig. \ref{fig__profile}) of the vertical profiles\
@@
 }
-{\color{blue}
 \item The development of the expanding forward-reverse shock pair is always associated with\
@@
 There exists a dense shell that fits closely to the reverse shock because the gas is immediately compressed as it passes outward through the reverse shock while coinciding with the low gas density further downstream.
-}
+
 \item In the oblique jet scenario, the edge of the eROSITA bubbles is a forward shock,\

### 2022-04-23 TC-4.18.tex
update

--- 2022-04-14 paper.tex
@@
 \begin{keywords}
-editorials, notices -- miscellaneous
+Relativistic hydrodynamics, \textit{Fermi} bubbles, eROSITA bubbles, cosmic rays
 \end{keywords}
@@
  and underpressured with respect to the turbulent plasma\
- and probably not related to the X-ray chimneys \citep{Ponti2019}\
+ but probably not related to the X-ray chimneys \citep{Ponti2019}\
  and radio bubbles \citep{Heywood2019}\

### 2022-04-24 paper.tex
update

@@
 % Keep the title short and informative.
-\title[]{Can the symmetric \textit{Fermi} and eROSITA bubbles be produced by tilted jets: a proof-of-concept study}
+\title[]{Can the symmetric \textit{Fermi} and eROSITA bubbles be produced by tilted jets?}
 
@@
 \orcidlink{https://orcid.org/0000-0002-1249-279X}%
-\quad Chun-Yen Chen$^{8}, $
 \quad Tzihong Chiueh$^{1,5,6}$%
@@
 $^{7}$Center for Theoretical Physics, National Taiwan University, Taipei 10617, Taiwan\\
-$^{8}$Institute of physics, National Taiwan University, Taipei 10617, Taiwan\\
 }
@@
 which extend nearly symmetrically $\sim50^{\circ}$ above and below the Galactic center (GC).\
-The recent discovery of giant eROSITA bubbles also shows such a symmetry about the GC, suggesting that they may originate from a single GC activity.\
+The recent discovery of giant eROSITA bubbles also shows such a symmetry about the GC,
+suggesting that they may originate from a single GC activity.\
 Previous simulations of bubble formation that invoke active galactic nucleus (AGN) jets\
 have assumed that the jets are vertical to the Galactic plane;\
-however, in general there does not need to be a correlation between the jet orientation and the rotational axis of the Galactic disk.\
+however, in general there does not need to be a correlation between
+the jet orientation and the rotational axis of the Galactic disk.\
 Using three-dimensional (3D) special relativistic hydrodynamic (SRHD) simulations that\
-include cosmic rays (CRs) and thermal gas, we show that the interaction between the AGN jets and the thin interstellar medium (ISM) disk is crucial for producing the symmetric \textit{Fermi} and eROSITA bubbles (collectively, Galactic bubbles).\
-%We also produce simulated gamma-ray and\
-%microwave spectra from the inverse Compton (IC) scattering and synchrotron,\
-%and compare them with the observed counterparts in order to verify\
-%an oblique AGN jets model.
+include cosmic rays (CRs) and thermal gas, we show that {\color{red}the clumpy gas within ISM\
+disrupts jets collimation and confinement (``failed jets" hereafter),
+which in turn causes the failed jets to form
+hot bubbles and subsequent bouyancy makes it vertical to produce
+the symmetric \textit{Fermi} and eROSITA bubbles (collectively, Galactic bubbles).}
 Specifically, we find that\
@@
 (2) the edge of the eROSITA bubbles corresponds to a forward shock,\
-originally driven by oblique bipolar jets emanating from the GC 12.39 million years ago; %,\
-%and significantly stretched by the stratified atmosphere afterwards.\
+originally driven by oblique bipolar jets emanating from the GC around 12 million years ago; %,\
 (3) followed by the forward shock is a tangling contact discontinuity,\
@@
 plasma in pressure balance with the external medium;
-(4) assuming a leptonic model with spatially uniform CR electron spectrum, we find that the observed gamma-ray and microwave spectra can be reproduced with a best-fit CR power-law index of 2.4.\
-The broad agreement between simulated and observed multi-wavelength features suggests that forming the Galactic bubbles by oblique AGN jets is a plausible scenario.
-%has thus released a caveat:\
-%the jets shall be vertical to the disk normal.
+(4) assuming a leptonic model with spatially uniform CR electron spectrum,
+we find that the observed gamma-ray and microwave spectra can be reproduced with
+a best-fit CR power-law index of 2.4. The broad agreement between simulated and
+observed multi-wavelength features suggests that forming the Galactic bubbles by
+oblique AGN failed jets is a plausible scenario.
 \end{abstract}
@@
 \section{Discussion}
-Our modeled gamma-ray and microwave spectra assumed that
+{\color{red}
+As a past violent event at the GC must destroy the Central Molecular Zone (CMZ)
+but the CMZ is currently either in a quasi-steady state or
+presently increasing \citep{Crocker2012,Krumholz2015,Sormani2019};
+we conclude that the time since the violent event must be ``slightly" shorter
+than the reconstruction time of CMZ on a timescale of
+$M_{\text{CMZ}}/\dot{M}_{\text{inflow}}$, where $M_{\text{CMZ}}$ is
+the total mass of molecular gas within $R\sim300$ pc,
+and $\dot{M}_{\text{inflow}}$ is the gas inflow rate from the Galactic disc at
+$R\sim3$ kpc down to the outskirts of the CMZ.
+Since $M_{\text{CMZ}}$ and $\dot{M}_{\text{inflow}}$ have been reported to be in the range
+$2-6\times10^{7}$ M$_{\odot}$ \citep{Dahmen1998,Ferrire2007} and
+$0.4-2.7$ M$_{\odot}$ yr$^{-1}$ \citep{Sormani2019,Crocker2012}, respectively;
+we estimate that the CMZ formation is about a couple of 10 Myrs, similar to
+12 Myr required for our simulated bubbles to reach the desired morphology.
+}
+
+On the other hand, our modeled gamma-ray and microwave spectra assumed that
 the underlying CRe spectrum is spatially uniform with hard spectral index 2.4;
@@
 in Milky Way is $\sim$ 1 Myr \citep{Yang2017}, ten times shorter than
-12.39 Myr required for the simulated bubbles to reach the desired morphology.
-
+12 Myr suggested by our simulation.
 Therefore, the CRe generating the gamma-ray emission would need to be re-accelerated
@@
 re-acceleration is more likely associated with turbulence \citep{Mertsch2011,Mertsch2019},
-possibly in balance with the IC and synchrotron cooling. We will investigate the competition between stochastic acceleration and radiative cooling
-in future work.
-
-Overall, our results imply that in the oblique-jet scenario, whatever the true re-acceleration and cooling mechanisms are,
+possibly in balance with the IC and synchrotron cooling. We will investigate the
+competition between stochastic acceleration and radiative cooling in future work.
+
+Overall, our results imply that in the oblique-jet scenario,
+whatever the true re-acceleration and cooling mechanisms are,
 the CRe spectrum at the present time has to be spatially uniform with
@@
 \item In the oblique jet scenario, the edge of the eROSITA bubbles is a forward shock,\
-      originally driven by oblique bipolar jets emanating from the GC 12.39 Myr ago for a duration of 1.2 Myr\
+      originally driven by oblique bipolar jets emanating from the GC around 12 Myr ago for a duration of 1.2 Myr\
       and significantly expanded within the stratified atmosphere afterwards.\
@@
       CRe power-law index is found to be 2.4.
-\item The elapsed time of 12.39 Myr required for the simulated bubbles
+\item The elapsed time of 12 Myr required for the simulated bubbles
       to reach the desired morphology
@@
 We thank Peter Predehl for providing the range of observed X-ray intensity in Fig. \ref{fig__xray_0.8keV_angle_000}.\
+We further thank Chen Chun-Yen provides the code module solving the cosmic ray convection equation.
 A part of the simulations are performed and analyzed using computing resources\
@@
 if source temperature is not high enough,
-the jets cannot effectively ablate the high-density clouds within 12.39 Myr,
+the jets cannot effectively ablate the high-density clouds within 12 Myr,
 resulting in the formation of asymmetric bubbles (case B).

### 2022-04-24 paper.tex
update

@@
 $2-6\times10^{7}$ M$_{\odot}$ \citep{Dahmen1998,Ferrire2007} and
-$0.4-2.7$ M$_{\odot}$ yr$^{-1}$ \citep{Sormani2019,Crocker2012}, respectively;
+$0.4-2.7$ M$_{\odot}$ yr$^{-1}$ \citep{Crocker2012,Sormani2019}, respectively;
 we estimate that the CMZ formation is about a couple of 10 Myrs, similar to

### 2022-05-07 TC-5.07.tex
update

--- 2022-04-24 paper.tex
@@
 Specifically, we find that\
-(1) the simulated Galactic bubbles are nearly symmetric about the GC albeit\
+(1) despite the relativistic jets emanated from the GC 12 Myr ago are at various angles
+$\leq 45^{\circ}$ with respect to
+the rotational axis of the Galaxy, the Galactic bubbles nonetheless appear aligned with the axis;
+the simulated Galactic bubbles are nearly symmetric about the GC albeit\
 the bipolar jets are at an angle $45^{\circ}$ with respect to\
 the rotational axis of the Galaxy;\
-(2) the edge of the eROSITA bubbles corresponds to a forward shock,\
-originally driven by oblique bipolar jets emanating from the GC around 12 million years ago; %,\
-(3) followed by the forward shock is a tangling contact discontinuity,\
-which we interpret as the edge of the \textit{Fermi} bubbles\
+(2) the edge of the eROSITA bubbles corresponds to a forward shock, driven by the hot bubble;
+(3) followed by the forward shock is a tangling contact discontinuity at the edge of the \textit{Fermi} bubbles
 composed of turbulent and high-temperature ($\sim2$ keV)\
 plasma in pressure balance with the external medium;
-(4) assuming a leptonic model with spatially uniform CR electron spectrum,
-we find that the observed gamma-ray and microwave spectra can be reproduced with
-a best-fit CR power-law index of 2.4. The broad agreement between simulated and
+(4) assuming a leptonic model we find that the observed gamma-ray bubbles and microwave haze can be reproduced with
+a best-fit CR power-law index of 2.4;
+(5) the 12 Myr time span between the present and the launch of short-lived jets appears to be the appropriate time
+scale for the observed GC Central Molecular Zone to form.
+The broad agreement between the simulated and the
 observed multi-wavelength features suggests that forming the Galactic bubbles by

### 2022-05-07 paper.tex
update

@@
 Using three-dimensional (3D) special relativistic hydrodynamic (SRHD) simulations that\
-include cosmic rays (CRs) and thermal gas, we show that {\color{red}the clumpy gas within ISM\
+include cosmic rays (CRs) and thermal gas, we show that the dense clumpy gas within disk ISM\
 disrupts jets collimation and confinement (``failed jets" hereafter),
 which in turn causes the failed jets to form
-hot bubbles and subsequent bouyancy makes it vertical to produce
-the symmetric \textit{Fermi} and eROSITA bubbles (collectively, Galactic bubbles).}
+hot bubbles. Subsequent bouyancy in the stratified atmosphere renders them vertical to form
+the symmetric \textit{Fermi} and eROSITA bubbles (collectively, Galactic bubbles).
 Specifically, we find that\
-(1) the simulated Galactic bubbles are nearly symmetric about the GC albeit\
+(1) despite the relativistic jets emanated from the GC 12 Myr ago are at various angles
+$\leq 45^{\circ}$ with respect to
+the rotational axis of the Galaxy, the Galactic bubbles nonetheless appear aligned with the axis;
+the simulated Galactic bubbles are nearly symmetric about the GC albeit\
 the bipolar jets are at an angle $45^{\circ}$ with respect to\
 the rotational axis of the Galaxy;\
-(2) the edge of the eROSITA bubbles corresponds to a forward shock,\
-originally driven by oblique bipolar jets emanating from the GC around 12 million years ago; %,\
-(3) followed by the forward shock is a tangling contact discontinuity,\
-which we interpret as the edge of the \textit{Fermi} bubbles\
+(2) the edge of the eROSITA bubbles corresponds to a forward shock, driven by the hot bubble;
+(3) followed by the forward shock is a tangling contact discontinuity at the edge of the \textit{Fermi} bubbles
 composed of turbulent and high-temperature ($\sim2$ keV)\
 plasma in pressure balance with the external medium;
-(4) assuming a leptonic model with spatially uniform CR electron spectrum,
-we find that the observed gamma-ray and microwave spectra can be reproduced with
-a best-fit CR power-law index of 2.4. The broad agreement between simulated and
+(4) assuming a leptonic model we find that the observed gamma-ray bubbles and microwave haze can be reproduced with
+a best-fit CR power-law index of 2.4;
+(5) the 12 Myr time span between the present and the launch of short-lived jets appears to be the appropriate time
+scale for the observed GC Central Molecular Zone to form.
+The broad agreement between the simulated and the
 observed multi-wavelength features suggests that forming the Galactic bubbles by
@@
 
-  \textsc{gamer-sr} adopts a new algorithm \citep{tseng2021} to convert between\
-  primitive ($\rho$, $U^{j}$, $p$) and conserved variables ($D$, $M^{j}$, $\tilde{E}$),\
-  significantly reducing numerical errors caused by catastrophic cancellations\
-  that commonly occur within the regions with high Mach number flows. e.g., jet-ISM interaction zones.\
+  \textsc{gamer-sr} adopts a new SRHD solver \citep{tseng2021}, which significantly reduce numerical errors
+  in non- and ultra-relativistic limits caused by catastrophic cancellations
+  in the conversion between primitive ($\rho$, $U^{j}$, $p$) and conserved variables ($D$, $M^{j}$, $\tilde{E}$).
+  %that commonly occur within the regions with high Mach number flows. e.g., jet-ISM interaction zones.\
   \textsc{gamer-sr} also adaptively and locally reduce the min-mod coefficient\
@@
 \section{Discussion}
-{\color{red}
 As a past violent event at the GC must destroy the Central Molecular Zone (CMZ)
@@
 12 Myr required for our simulated bubbles to reach the desired morphology.
-}
 
@@
 In this work, we introduce a thin, dense disk composed of clumpy ISM\
-to divert the oblique jets at an angle $45^{\circ}$\
-to the disk normal in the past energetic event of the central SMBH in the Milky Way Galaxy.\
+to stall and thermalize the oblique jets for an outburst event from
+the central SMBH in the Milky Way Galaxy 12 Myrs ago.
 We investigate the properties of the Galactic bubbles and the microwave\
@@
 \begin{itemize}
-
-\item The Galactic bubbles are nearly symmetric about the Galactic plane albeit\
-      the bipolar jets are at an angle $45^{\circ}$\
-      with respect to the disk normal.\
-      We showed that inclusion of the dense ISM disk (regardless of its clumpiness) is a critical component for producing the symmetric Galactic bubbles when the jets are oblique.\
-      The broad agreement between the simulated and observed multi-wavelength features\
-      demonstrates that oblique jets are a plausible scenario of forming the Galactic bubbles, which\
-      releases the caveat of earlier jet models that the jets must be vertical to the Galactic plane.\
 
@@
 }
-\item The development of the expanding forward-reverse shock pair is always associated with\
-the dense disk, although the clumpiness of the disk has an insignificant impact on the\
-overall dynamic of the Galactic bubbles.
-Furthermore, in the absence of the disk, only forward shocks are present,
+\item The development of the expanding forward-reverse shock pair is always associated with the dense disk.
+%the dense disk, although the clumpiness of the disk has an insignificant impact on the\
+%overall dynamic of the Galactic bubbles.
+%Furthermore,
+In the absence of the disk, only forward shocks are present,
 indicating the inclusion of the disk is critical for forming the innermost bubbles.
 
-\item The forward-reverse shock pair heats the turbulent plasma up considerably ($\sim2$ keV) as the plasma is bracketed between their downstream.
-There exists a dense shell that fits closely to the reverse shock because the gas is immediately compressed as it passes outward through the reverse shock while coinciding with the low gas density further downstream.
-
-\item In the oblique jet scenario, the edge of the eROSITA bubbles is a forward shock,\
-      originally driven by oblique bipolar jets emanating from the GC around 12 Myr ago for a duration of 1.2 Myr\
-      and significantly expanded within the stratified atmosphere afterwards.\
-      The overall extent of the simulated X-ray bubbles is comparable to that of the eROSITA bubbles, though not as limb-brightened.\
-      Future models including shock-accelerated CRs may help to resolve this issue by increasing the compressibility of the fluid and enhancing the thermal Bremsstrahlung emissivity at the edge of the X-ray bubbles.
+\item The forward-reverse shock pair heats the turbulent plasma considerably ($\sim2$ keV).
+%as the plasma is bracketed between their downstream.
+There exists a
+%dense shell that fits closely to the reverse shock because the gas is
+%immediately compressed as it passes outward through the reverse shock while coinciding with the low gas density further downstream.
+dense shell immediately downstream of the reverse shock, a situation reminiscent of a supernova shell.
+
+\item The edge of the eROSITA bubbles is a forward shock,
+      originally driven by bipolar jets emanating from the GC around 12 Myr ago
+      for a duration of 1.2 Myr,
+      and significantly expanded in the stratified atmosphere afterwards.
+      The overall extent of the simulated X-ray bubbles is comparable to
+      that of the eROSITA bubbles, though not as limb-brightened.
+      Future models including shock-accelerated CRs may help to resolve this issue by
+      increasing the compressibility of the fluid and enhancing the thermal Bremsstrahlung emissivity
+      at the edge of the X-ray bubbles.
       %The simulated eROSITA bubbles are not as limb-brightened as the observation.\
@@
       %resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density squared.
-\item Followed by the forward shock is a turbulent, hot plasma ($\sim2$ keV) filled with the injected CRs in pressure balance with the shocked medium, which we interpret as the \textit{Fermi} bubbles.\
-      The similarity of the morphology, temperature, and gamma-ray spectrum between\
-      simulated and observed bubbles suggests that\
-      the edge of the \textit{Fermi} bubbles are likely associated with the contact discontinuity between the turbulent, hot plasma and the post-shock medium.
-The surface of the simulated bubbles is not as smooth as the observed ones; inclusion of magnetic fields in the future may help suppress the instabilities at the bubble surface due to the mangetic draping effect.
-\item Assuming a leptonic model with a spatially uniform, power-law CRe spectrum ranging from 0.5 MeV to 562.1 GeV, we showed that the observed gamma-ray and microwave spectra can simultaneously reproduced.
-The best-fit\
-      CRe power-law index is found to be 2.4.
-\item The elapsed time of 12 Myr required for the simulated bubbles
-      to reach the desired morphology
-      is ten times longer than the typical synchrotron and IC cooling time scale of
+%\item Followed by the forward shock is a turbulent, hot plasma ($\sim2$ keV) filled
+      %with the injected CRs in pressure balance with the shocked medium,
+      %which we interpret as the \textit{Fermi} bubbles.\
+      %The similarity of the morphology, temperature, and gamma-ray spectrum between\
+      %simulated and observed bubbles suggests that\
+      %the edge of the \textit{Fermi} bubbles are likely associated with the contact discontinuity between
+      %the turbulent, hot plasma and the post-shock medium.
+\item Downstream of the reverse shock is filled with hot ($\sim2$ keV) and highly turbulent
+      plasma brought from the disk. The interface between the downstream materials of reverse and
+      forward shocks lies a contact discontinuity, which defines the edge of the Fermi bubble.
+      The surface of the simulated bubbles is
+      not as smooth as the observed ones; inclusion of magnetic fields in the future may help suppress
+      the instabilities at the bubble surface due to the mangetic draping effect.
+\item Assuming a leptonic model with a spatially uniform, power-law CRe spectrum
+      ranging from 0.5 MeV to 562.1 GeV, we showed that the observed gamma-ray and microwave spectra
+      can simultaneously reproduced. The best-fit CRe power-law index is found to be 2.4.
+\item The elapsed time of 12 Myr is required for the simulated bubbles to reach the desired morphology.
+      This time scale is appropriate for the observed Central Molecular Zone, 200 pc
+      in radius surrounding the GC, to form. However, it is 10 times longer than
+      %The elapsed time of 12 Myr required for the simulated bubbles
+      %to reach the desired morphology is ten times longer than
+      the typical synchrotron and IC cooling time scale of
       high energy ($\sim100$ GeV) CRe. Thus, re-acceleration of CRe by shocks or turbulence must be considered
-      in this model. Since the forward shock is rather far away from the gamma-ray bubbles, stochastic acceleration of CRs by turbulence appears to be more plausible.\
+      in this model. Since the forward shock is rather far away from the gamma-ray bubbles,
+      stochastic acceleration of CRs by turbulence appears to be more plausible.\
       We will investigate the competition between stochastic acceleration and radiative cooling
@@
       %{\color{red} KY: This item is to be modified according to the newly added text in the Discussion section. PH: done!}
+\item The Galactic bubbles are nearly symmetric about the Galactic plane albeit\
+      the bipolar jets are oblique with respect to the disk normal.\
+      We showed that inclusion of the dense ISM disk (regardless of its clumpiness)
+      is an essential ingredient for producing the symmetric Galactic bubbles when the jets are oblique.\
+      The broad agreement between the simulated and observed multi-wavelength features\
+      demonstrates that oblique failed jets are a plausible
+      %scenario of forming the Galactic bubbles,
+      scenario for the formation of the Galactic bubbles,
+      which release the caveat of earlier jet models where jets need to be vertical.
+      %that the jets must be vertical to the Galactic plane.\
+
 \end{itemize}

### 2022-05-11 paper.tex
update

@@
 %Furthermore,
-In the absence of the disk, only forward shocks are present,
+In the absence of the disk, the reverse shock is absent,
 indicating the inclusion of the disk is critical for forming the innermost bubbles.
@@
 
-\item The edge of the eROSITA bubbles is a forward shock,
-      originally driven by bipolar jets emanating from the GC around 12 Myr ago
-      for a duration of 1.2 Myr,
-      and significantly expanded in the stratified atmosphere afterwards.
+\item eROSITA bubbles coincide with the forward shock front
+      originally driven by short-lived bipolar jets
+      for a duration of 1.2 Myr, where the bubbles later significantly
+      expanded into the stratified atmosphere to reach the present 12kpc height.
       The overall extent of the simulated X-ray bubbles is comparable to
@@
       Future models including shock-accelerated CRs may help to resolve this issue by
-      increasing the compressibility of the fluid and enhancing the thermal Bremsstrahlung emissivity
+      increasing the compressibility of the fluid and
+      enhancing the thermal Bremsstrahlung emissivity
       at the edge of the X-ray bubbles.
@@
       the instabilities at the bubble surface due to the mangetic draping effect.
-\item Assuming a leptonic model with a spatially uniform, power-law CRe spectrum
-      ranging from 0.5 MeV to 562.1 GeV, we showed that the observed gamma-ray and microwave spectra
+\item Assuming a power-law CRe energy spectrum ranging from 0.5 MeV to 560 GeV,
+      where the spectrum is space-independent,
+      %Assuming a leptonic model with a spatially uniform, power-law CRe spectrum
+      %ranging from 0.5 MeV to 562.1 GeV,
+      we showed that the observed gamma-ray and microwave spectra
       can simultaneously reproduced. The best-fit CRe power-law index is found to be 2.4.
-\item The elapsed time of 12 Myr is required for the simulated bubbles to reach the desired morphology.
+\item The elapsed time of 12 Myr is required for the simulated bubbles
+      to reach the desired morphology.
       This time scale is appropriate for the observed Central Molecular Zone, 200 pc
@@
       %{\color{red} KY: This item is to be modified according to the newly added text in the Discussion section. PH: done!}
-\item The Galactic bubbles are nearly symmetric about the Galactic plane albeit\
+\item The Galactic bubbles are observed nearly symmetric about the Galactic plane albeit\
       the bipolar jets are oblique with respect to the disk normal.\
@@
       scenario for the formation of the Galactic bubbles,
-      which release the caveat of earlier jet models where jets need to be vertical.
+      which relieve the caveat of earlier jet models where jets need to be vertical.
       %that the jets must be vertical to the Galactic plane.\

### 2022-06-28 paper.tex
update

@@
 which in turn causes the failed jets to form
-hot bubbles. Subsequent bouyancy in the stratified atmosphere renders them vertical to form
+hot bubbles. Subsequent buoyancy in the stratified atmosphere renders them vertical to form
 the symmetric \textit{Fermi} and eROSITA bubbles (collectively, Galactic bubbles).
@@
 the rotational axis of the Galaxy, the Galactic bubbles nonetheless appear aligned with the axis;
-the simulated Galactic bubbles are nearly symmetric about the GC albeit\
-the bipolar jets are at an angle $45^{\circ}$ with respect to\
-the rotational axis of the Galaxy;\
+%the simulated Galactic bubbles are nearly symmetric about the GC albeit\
+%the bipolar jets are at an angle $45^{\circ}$ with respect to\
+%the rotational axis of the Galaxy;\
 (2) the edge of the eROSITA bubbles corresponds to a forward shock, driven by the hot bubble;
@@
      &\partial_{t} \left(\gamma e_{\text{cr}}\right) + \partial_{j} \left(e_{\text{cr}}U^{j}\right)=\
-     -p_{\text{cr}} \partial_{j} U^{j},\label{E evolution}
+     -p_{\text{cr}} \partial_{j} U^{j},\\
+     &\partial_{i}\partial^{i}\Phi=4\pi G \rho,
+    \label{E evolution}
     \end{align}
@@
   as we have assumed $p_{\text{cr}}\ll p_{\text{gas}}$.\
-  $\Phi$ is a gravitational potential.\
+  $\Phi$ is a gravitational potential, and $G$ is the gravitational constant.\
   $c$ is the speed of light, and $\delta^{ij}$ is the Kronecker delta notation.\
@@
              on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disk\
-             in an uniform atmosphere (Fig. \ref{fig__jetI5+ismSeed3-45deg-c}) is nearly spherical,\
+             in a uniform atmosphere (Fig. \ref{fig__jetI5+ismSeed3-45deg-c}) are nearly spherical,\
              suggesting that the stratification facilitates the elongation of the outermost bubbles significantly.\
@@
 
-We assume the leptonic model for the gamma-ray and microwave emission as previous studies have shown that the bubble and haze spectra can be simulataneously produced by the same population of CRe \citep{Su2010, Ackermann2014, Yang2022}.
+We assume the leptonic model for the gamma-ray and microwave emission as previous studies have shown that the bubble and haze spectra can be simultaneously produced by the same population of CRe \citep{Su2010, Ackermann2014, Yang2022}.
 In the leptonic scenario, the gamma-ray and microwave emission come from IC scattering of the ISRF and synchrotron radiation, respectively.\
@@
 
-First, we find that, among the three values of the CR spectral indices assumed, a CRe spectral index of 2.4 (the middle row) provides the best fits for both the the simulated gamma-ray spectra as well as the microwave spectra.
+First, we find that, among the three values of the CR spectral indices assumed, a CRe spectral index of 2.4 (the middle row) provides the best fits for both the simulated gamma-ray spectra as well as the microwave spectra.
 This value is slightly steeper than the best-fit spectral index of $\sim 2.17$ found by \cite{Ackermann2014}.
@@
       not as smooth as the observed ones; inclusion of magnetic fields in the future may help suppress
-      the instabilities at the bubble surface due to the mangetic draping effect.
+      the instabilities at the bubble surface due to the magnetic draping effect.
 \item Assuming a power-law CRe energy spectrum ranging from 0.5 MeV to 560 GeV,
